### 2023-05-05 paper1.tex
Add work in progress paper 1

\documentclass{article}
\input{preamble}
\begin{document}

\author{\and{Luke Thomas Smith} \and{Eun-Jung Holden} \and{Tom Horrocks} \and{Daniel Wedge} \and{Naveed Akhtar}}
\title{Magnetic grid resolution enhancement using machine learning: A case study from the Eastern Goldfields Superterrane}
\date{2022-09-21}
\maketitle{}

\begin{abstract}
    Densely sampled geophysical surveys are a key driver for mineral exploration, but sample density, and therefore grid resolution, is limited by survey cost.
    Consequently, computational methods are resorted to for upsampling, or `super-resolving', of gridded geophysical survey data.
    However, existing approaches such as interpolation filters do not leverage high-resolution detail from pre-existing geophysical surveys.
    Through the application of state-of-the-art deep learning super-resolution architectures, accurate high-resolution grids are predicted from corresponding low-resolution grid priors.
    Specifically, the RDN and ESRGAN+ neural network architectures, which were originally developed for enhancing images, are applied to enhance magnetic surveys and trained with high-resolution and low-resolution magnetic grids of the same extent.
    \SI{80}{\metre} cell size magnetic grids are upsampled to \SI{20}{\metre} cell size using this method, and predicted value and structural accuracy comparisons to the corresponding ground truth \SI{20}{\metre} grids are presented over two test sites in the Eastern Goldfields Superterrane, Western Australia.
    The method based on RDN achieves 53\% lower error compared to Bicubic interpolation.
    The case study demonstrates that the deep learning approach can improve the resolution and frequency content of geophysical surveys without requiring additional sampling expense, while remaining accurate against known ground truth surveys.
    Super-resolution may assist in the interpretation of low-resolution survey grids, however these upsampled grids cannot perfectly recreate the accuracy of highly sampled surveys gridded at their optimal cell size.
\end{abstract}

\section{Introduction}
\subsection{Resolution in geophysics}
\label{resingeo}
Surveys of the spatial distribution of physical properties of the Earth, such as the magnetic potential field, are common in geoscience.
These point-sampled surveys are typically interpolated onto a grid raster, and when a raster covers a known spatial extent, its resolution can be referred to as spatial resolution, indicating that each pixel covers a quantified area.
Often referred to as high resolution, a fine spatial resolution is critical for representing high frequency components in a gridded raster.
These high frequency components reveal localised variations in the surveyed potential field, which provide additional detail on subsurface geological structures and the potential for mineralisation.
An example of the additional detail provided by a high-resolution grid is provided in \cref{lrandhr}, which shows an \SI{80}{\metre} cell size Total Magnetic Intensity (TMI) grid (a) compared to a \SI{20}{\metre} TMI grid of the same \SI{2560}{\metre} \texttimes\ \SI{2560}{\metre} extent (b), gridded from the same potential field samples, but interpolated to different resolutions.
The increased density of pixels in the high-resolution \SI{20}{\metre} grid allows higher frequencies in the sampled magnetic potential field to be displayed.
These frequencies are irretrievably lost when the high-resolution grid is downsampled to \SI{80}{\metre}.

\begin{figure}[hbt]
    \includegraphics[width=\textwidth]{fig/p1/fig1.jpg}
    \caption[Comparison of different resolution grids]{Low resolution \SI{80}{\metre} cell size (a), and high-resolution \SI{20}{\metre} cell size (b) TMI grids over the same extent.
    Each tile is \SI{2560}{\metre} \texttimes\ \SI{2560}{\metre}.
    The additional detail shown in the high-resolution grid is made available by the finer cell size, which can convey higher frequency detail, if present in the sampled data.}
    \label{lrandhr}
\end{figure}

Geophysical rasters are created through a process of survey point sampling, grid interpolation, and usually post-process filtering.
During these processes, the sampled potential field may be subject to destructive Nyquist sampling principles \parencite[16]{dentithGeophysicsMineralExploration2014}, especially due to the original point sampling interval and the cell size (pixel spatial extent) selected for the grid interpolation.
The optimal grid cell size is dependent on the sampling interval, and because of this, the highest frequency component preserved in gridded geophysical potential fields is intrinsically limited by the original sampling interval.
This could be summarised as; high frequency components that may be sampled in surveys with close line sampling will be preserved in high-resolution grids with fine cell size.
Typically, cell sizes as fine as one fifth of the line sampling interval can be useful for gridding airborne geophysics \parencite{reidAeromagneticSurveyDesign1980}.
Selecting a cell size finer than one fifth will increase the number of pixels in the image raster, achieving a higher resolution, however no additional geophysical frequencies exist in the point sampled data to be displayed and no detail will be gained.

\subsection{Resolution and frequency}
As discussed in \cref{resingeo}, a finer spatial resolution grid (fewer metres per pixel) can convey higher frequency information, due to the higher spatial sampling rate.
Indeed, a gridded raster with regularly spaced square cells $\Delta x$ has an intrinsic Nyquist wavelength $\lambda _N$, at twice the cell size \labelcref{eq:nyq}.

\begin{equation}
    \lambda N = 2 \Delta x
    \label{eq:nyq}
\end{equation}

This corresponds to the shortest wavelength the grid can adequately display, which can be observed as the finest details resolvable in the grid raster.
For example, a high-resolution grid with \SI{20}{\metre} spatial resolution (HR) has a Nyquist wavelength of \SI{40}{\metre}.
In comparison, a low-resolution \SI{80}{\metre} grid (LR) has a Nyquist wavelength of \SI{160}{\metre}.
Note the Nyquist wavelength is proportional between different cell size grids according to the scale factor S \labelcref{eq:hrn}.

\begin{equation}
    \lambda N_{HR} = \lambda N_{LR} \div S
    \label{eq:hrn}
\end{equation}

Because the highest frequency component preserved in a grid is limited by the grid cell size, any operation that coarsens the cell size is a low pass filter.

\subsection{Improving resolution}
Given the value of higher detail when viewing images, there has been significant research into improving image resolution.
The most straightforward method is to simply sample at a higher rate, which for airborne geophysics means increasing the density of line sampling over a given area.
However, increasing sampling density increases total sampling cost, and cannot easily be done for existing grids.
This paper will investigate a new method for enhancing the resolution of grids by predicting high frequency components in geophysics without requiring additional sampling or cost, based on machine learning methods for image super-resolution.

Recent advances in machine learning techniques for image super-resolution (SR) have been shown to successfully increase image resolution for photographs and other image rasters, while also improving perceptual image quality.
These modern techniques belong to a family of methods known as deep learning, where features learnt early in the network are leveraged to develop a higher understanding of later features.
Notable published examples include SRCNN \parencite{dongLearningDeepConvolutional2014}, VDSR \parencite{kimAccurateImageSuperresolution2016}, SRGAN \parencite{ledigPhotorealisticSingleImage2017}, EDSR \parencite{limEnhancedDeepResidual2017}, RDN \parencite{zhangResidualDenseNetwork2018}, and the current state-of-the-art methods, ESRGAN \parencite{wangESRGANEnhancedSuperResolution2018} and ESRGAN+ \parencite{rakotonirinaESRGANFurtherImproving2020}.
SRGAN and ESRGAN are similar in design to their contemporary counterparts but implement a Generative Adversarial Network (GAN) framework.
In a GAN framework, the upsampling network (termed generator) is trained in an adversarial manner against another network (termed discriminator).
Adversarial training of upsampling networks can help in learning a better model for the task at hand.
For example, ESRGAN uses an analogous upsampling network design to RDN (Residual Dense Network) \cref{fig:rdn}, with the addition of a discriminator network.
This will be further discussed in \cref{sec:nnsr}.
For a review on super-resolution networks, the reader is referred to \cite{anwarDeepJourneySuperresolution2020}.

Neural network based super-resolution has seen recent success across many scientific disciplines on data other than natural images.
It is popular in satellite remote sensing \parencite[e.g.][]{lanarasSuperresolutionSentinel2Images2018b,wangUltradenseGANSatellite2019}, and has been applied to astrophysics \parencite[e.g.][]{jungbluthSingleframeSuperresolutionSolar2019,salvatelliUsingUNetsCreate2019}, fluid dynamics \parencite{bodeUsingPhysicsinformedEnhanced2021}, elevation models \parencite{leongDeepBedMapDeepNeural2020}, hyperspectral data \parencite[e.g.][]{arunCNNBasedSuperResolutionHyperspectral2020}, and seismic geophysics data \parencite[e.g.][]{liDeepLearningSimultaneous2021,wangDeeplearningbasedSeismicData2018,wangAdaptingResidualDense2022,yuDeepLearningDenoising2019}.
These authors typically report a lower error between the super-resolution upsampled product and ground truth data when compared to a bicubic upsampled product and the ground truth data, as well as improved perceptual quality.
Critically, super-resolution for these applications was able to create realistic high frequency information during upsampling, which could be validated against existing high-resolution surveys of the same extent.
While there are pre-trained models to super-resolve image data (such as ImageNet), the smooth and continuously differentiable nature of potential field data makes it difficult to directly apply such pre-trained models.
For example, it may enhance the appearance of gridding artifacts, instead of supressing them.
While several of the aforementioned works investigate deep learning super-resolution for geospatial data, low resolution in potential field geophysics is a result of under sampling and naïve best-effort interpolation of the potential field, distinct from low-resolution data previously studied in those works.

\begin{figure}
    % \includegraphics[width=\textwidth]{fig/p1/}
    \caption[The RDN architecture]{The RDN architecture, which acts as the ESRGAN generator.
    Twenty-three Basic Blocks are stacked sequentially to form the main convolution path.
    Upsampling to the target output size is performed after the main convolution sequence.
    Adapted from \cite{wangESRGANEnhancedSuperResolution2018}.
    }
    \label{fig:rdn}
\end{figure}

Resolution enhancement in potential field geophysics (occasionally referred to as downward continuation in this context) is performed numerically.
\cite{chenPotentialFieldData2022} use Taylor series expansion, while \cite{xuGravityAnomalyReconstruction2019} interpolate randomly sampled gravity point data using the nonequispaced Discrete Fourier Transform (nDFT), which leverages compressed sensing theory \parencite{candesIntroductionCompressiveSampling2008}.
While high quality results from under sampled data are attained with the non-equispaced Discrete Fourier Transform, the grid line sampling methodology of airborne geophysical surveys is highly regular, and unlikely to satisfy the coherency constraints required for compressive sensing.
This maintains true for data from published grids, which are regularised onto a uniform grid.
To the best of our knowledge, detailed studies on applying and comparing deep learning approaches for geophysical potential field super-resolution has not been previously reported.

\begin{figure}[hbt]
    % \includegraphics[width=\textwidth]{fig/p1/}
    \caption[Basic Blocks]{Each Basic Block (\cref{fig:rdn}, orange) comprises three weighted Residual Dense Blocks (\cref{fig:convs}).
    ESRGAN+ extends ESRGAN with the addition of Gaussian Noise after each basic RDB block (black vectors).
    Weight factors are indicated by $\beta$ and $\gamma$.
    Noise injection is not used in RDN\@.
    Adapted from \cite{rakotonirinaESRGANFurtherImproving2020}.
    }
    \label{fig:rdb}
\end{figure}

\begin{figure}[hbt]
    % \includegraphics[width=\textwidth]{fig/p1/}
    \caption[RDB convolutional layers]{Each Residual Dense Block (\cref{fig:rdb}, purple) comprises four convolutional layers, with additional learning pathways present as residual connections (black), and dense connections (green).
    LReLU refers to the Leaky-ReLU activation function.
    Adapted from \cite{rakotonirinaESRGANFurtherImproving2020}.
    }
    \label{fig:convs}
\end{figure}

\subsection{Interplation}
Increasing the resolution of an image is achievable through computationally inexpensive interpolating filters, such as nearest neighbour or bicubic interpolation.
These algorithms increase the number of pixels comprising the image raster and predict values for the interpolated pixels.
The nearest neighbour algorithm makes a simple prediction that the value of an interpolated pixel is equal to the nearest ground truth pixel, while the bicubic filter predicts values at interpolated pixels using a cubic function fit to the neighbouring ground truth pixels.
Bicubic interpolation results in a smoothing effect \parencite{keysCubicConvolutionInterpolation1981}, which means it is of limited value for adding higher frequencies to geophysics without additional input data.
It is however suitable as a baseline method to compare upsampling performance against deep learning methods.
It is typical for super-resolution algorithms to use a nearest neighbour upsampling step during their process to achieve the desired output image size, but the upsampled grid is subsequently processed by the neural network to incorporate additional information.
Importantly, basic interpolation is capable of increasing the number of pixels in a grid, but has limited predictive power for high frequency components.
Simply selecting a finer cell size when gridding line sampled data is likely to equal or outperform post-gridding interpolation.

\subsection{Neural network super-resolution}
\label{sec:nnsr}
Convolutional neural network (CNN) upsampling methods use features learned during their training to accurately upscale novel features during inference on novel data.
Learning from an extensive and varied training dataset is a primary driver for the improved performance of CNN methods over simple interpolation methods.
We apply the architectures of two CNN techniques in this work for geophysics super-resolution.
Namely, ESRGAN+ \parencite{rakotonirinaESRGANFurtherImproving2020} which exploits a GAN framework, and a non-GAN variant of the same method which does not rely on the discriminator component of the GAN framework.
The latter has a close resemblance to Residual Dense Network \parencite{zhangResidualDenseNetwork2018} in its architecture.
These CNN models are designed for natural images containing three channel inputs, whereas magnetic and other scientific grids use single channel floating point values.
Hence, for each network it was necessary to change the input array channel count from 3 to 1, and adjust the normalisation method to suit magnetic anomaly values.
We compare these methods to bicubic interpolation to demonstrate the predictive power of the deep learning approaches.

Residual Dense Network (RDN) \parencite{zhangResidualDenseNetwork2018} is a deep learning super-resolution method which consists of a series of residual dense blocks (\cref{fig:rdb,fig:convs}), which combine the performant residual connections and dense connections (\cref{fig:convs}) of earlier architectures for state-of-the-art performance.
Residual and dense connections provide additional learning capacity to a CNN, where features learnt in early layers can be fully utilised in later layers.
Following a series of these residual dense blocks, image enlargement is achieved using a simple nearest neighbour interpolation process followed by additional convolution operations.
In this case, enlargement is performed on an intermediate representation of the input, which has gained information during the main network path.
RDN is trained to reduce the Mean Absolute Error L1-norm loss, which corresponds to minimising the absolute difference between the super-resolution prediction and the high-resolution ground truth grid.
RDN was selected as a comparison against ESRGAN+ because RDN is structurally similar to the generator network in ESRGAN, allowing for analysis of the performance of GANs for super-resolution geophysics.
The RDN implementation used here adopts some improvements from ESRGAN+ and will henceforth be referred to as RDN\textdaggerdbl{}.

ESRGAN+, based on ESRGAN \parencite{wangESRGANEnhancedSuperResolution2018}, was chosen as the primary super-resolution CNN architecture for this task due to its reported success in other super-resolution tasks (especially \cite{bodeUsingPhysicsInformedSuperResolution2019} and \cite{leongDeepBedMapDeepNeural2020}) and state of the art results for its original application in image super-resolution.
As a Generative Adversarial Network (GAN), it comprises two iteratively trained neural networks, a Generator (G) used to upscale low-resolution inputs, and Discriminator (D), which is trained to improve the performance of the generator.

G is analogous in design to the RDN architecture described above (\cref{fig:rdn}), and is trained to upscale a low-resolution input, creating a super-resolution prediction.
The Discriminator network used in ESRGAN is based on a prevalent image classification architecture known as VGG \parencite{simonyanVeryDeepConvolutional2015}.
D is trained to classify its inputs as being either an example of the super-resolved G prediction, or high-resolution ground truth data.
This is used to provide a loss-feedback to G based on G's ability to create realistic SR predictions.
The two networks are trained concurrently, with the contemporaneous D network being used to calculate an adversarial loss for G at each iteration.
The adversarial loss calculated by D is incorporated with the generator's L1 loss as used in RDN, and training continues until D stabilises at 50 \% accuracy where the discriminator is unable to distinguish generated images from real images better than random chance.
At this point, training has converged, and the trained generator model can be used to independently upscale novel inputs.

The specific variant of ESRGAN applied in this work is that of ESRGAN+ \parencite{rakotonirinaESRGANFurtherImproving2020}, which incorporates modern GAN performance improving techniques, including generator noise injection (noted in \cref{fig:rdb}), and additional dense and residual connections (noted in \cref{fig:convs}).
These additional connections are used in RDN\textdaggerdbl{}.

The prediction of grid cell values for interpolation is common practice in geophysics.
Existing methods, including nearest neighbour and bicubic filtering, have limited capacity to predict high frequency details to incorporate in upsampled grids, limiting the amount of detail these grids can capture and display.
Recent super-resolution machine learning methods have demonstrated capacity to accurately predict high frequency components in grids from a variety of scientific disciplines, and application of these methods to geophysical potential fields will be investigated here.

\section{Materials and Methods}
\subsection{Geophysical context}
The Eastern Goldfields Superterrane of Western Australia is extensively covered by aeromagnetic surveys of \SI{400}{\metre} line spacing or better, especially over its South-Western extent.
Large survey extents are government sponsored through the Exploration Incentive Scheme \parencite[e.g.][]{griffinStimulatingGreenfieldsExploration2010}, with these low-resolution regional surveys serving to identify prospective areas to undertake surveys at higher resolution.
A number of these higher resolution surveys have been publicly released to open file.
In the Eastern Goldfields the driver for this extensive magnetic coverage is the prominence of highly susceptible BIF and ultramafic formations, which host several major resource projects including Mt Mason (iron ore), Mt Ida and Comet Vale (gold/silver), and Goongarrie (nickel/copper).
A long geological history provides our test region with a variety of magnetic features and textures to test super-resolution performance with, including structurally complex high intensity formations (BIF and ultramafic units), broad textural regions (granites), and extensive linear features (dykes).
Shear zones and fault systems provide further variation to these structures.
Overall, the selected test region in the Eastern Goldfields Superterrane contains sufficient variety of features on which to examine the effect and value of super-resolution upsampling, and determine the suitability of the method for application in other regions.

\subsection{Data}
In typical image SR networks, training data typically take the form of image pairs; the original high-resolution (HR) image, and a low-resolution (LR) image generated on-the-fly by bicubically downsampling the HR image, typically at a scale factor of four.
A similar technique could be used in geophysics SR by applying a low pass filter with a suitable cut-off to a HR grid to simulate the LR counterpart.
However, here we use data from existing grids published at the appropriate four times resolution difference, namely the Magnetic merged grid of Western Australia 2020 at \SI{20}{\metre} (HR) and \SI{80}{\metre} (LR) cell sizes \parencite{brett80MagneticMerged2020}.
When these grids were created, the best available resolution of all grids across the state were compiled at \SI{20}{\metre} cell size, and interpolated to \SI{80}{\metre} using a 4th order Newton polynomial interpolation process \parencite[][personal communication]{brett80MagneticMerged2020}.
This is similar to bicubic interpolation, in that both methods are examples of localised polynomial based interpolation algorithms.
While the cell size is uniform for each respective state grid, the sampling interval of the contributing line surveys varies across the state, which affects the extent of coverage of high frequency components across each grid.
To ensure that the HR ground truth has additional high frequency detail to the LR during training, data were only selected from areas of the Goldfields area of the state grid with contributing survey line spacing \SI{300}{\metre} or closer (optimal cell size strictly finer than \SI{80}{\metre}).
Training and validation data were extracted independent to a reserved test area, outlined in \cref{fig:trainvaldata}.
By selecting mixed line spacing data in this way, transforms between different scales of frequency loss are captured in the training data.
That is, the same model can learn from fine optimal cell size extents that lose many component frequencies when interpolated to \SI{80}{\metre}, as well as coarse cell size extents which may only lose few or none.
These data were extracted as square tiles, each covering \SI{2560}{\metre} by \SI{2560}{\metre} at 32 \texttimes{} 32 pixels for LR, and 128 \texttimes{} 128 pixels for HR, with no overlap.
This resulted in \num{5290} training tile pairs (used to train the model), \num{512} validation tile pairs (used to select the best performing model), and \num{2415} test tile pairs (used to independently verify the performance of the selected model).
These magnetic grid tiles differ notably from standard colour image tiles, in that they contain 32-bit floating-point values in a single channel, corresponding to the TMI value at each grid cell location.
These values were min-max scaled to a range of 0 to 1 using the global minimum and maximum values of the HR training data.
In summary, the single channel high- and low-resolution state TMI grids were filtered according to a database of their component surveys to extract areas of \SI{300}{\metre} line spacing or less.
These data were normalised according to the statistics of the HR training set, and split into small patches suitable for the hardware limitations.
After application of the architecture under investigation, the data are returned to predicted TMI values, and recompiled into a contiguous spatial extent.

\begin{figure}[hbt]
    % \includegraphics[width=\textwidth]{fig/p1/}
    \caption[Dataset context]{Reserved training/validation and test areas of Eastern Goldfields Superterrane magnetic grid, and their tectonic context.
    Background: \SI{20}{\metre} merged magnetic grid of Western Australia, \parencite{brett40MagneticMerged2020}.
}
    \label{fig:trainvaldata}
\end{figure}

\subsection{Training and inference implementation}
Training of the RDN\textdaggerdbl{} and ESRGAN+ networks was performed with Pytorch \parencite{paszkePyTorchImperativeStyle2019} using an Nvidia RTX 3090 with 24 GB memory, on a desktop computer with an Intel i9-10900KF CPU and 64 GB RAM\@.
Both networks were trained with minibatch size of 64 image patch pairs for \num{602} epochs (\num{17.6} h for RDN\textdaggerdbl{}, \num{21.8} h for ESRGAN+), at which point the PSNR plateaued.
Training samples were augmented using random 90-degree rotations and flips to encourage a model with rotational and symmetrical invariance to the input images, and their order per epoch was shuffled to improve regularisation and supress overfitting.
Further measures for the suppression of overfitting inherent to each of the applied architectures are described in their respective manuscripts \parencite{wangESRGANEnhancedSuperResolution2018,zhangResidualDenseNetwork2018}.
The optimiser used was Adam \parencite{kingmaAdamMethodStochastic2015}.
The learning rate was adjusted over the course of the experiment using the Pytorch implementation of One Cycle Learning Rate scheduler \parencite{smithSuperconvergenceVeryFast2018}, which provides a “warm up” period to stabilise early predictions, and a “cool down” period where the loss minima is fine tuned.
Following the generator implementation from ESRGAN+, twenty-three Residual Dense Blocks were ordered sequentially to form the main network, followed by two nearest neighbour upsampling filters at two times scale each.
The ESRGAN+ discriminator followed that of \cite{rakotonirinaESRGANFurtherImproving2020} which is an implementation of a VGG style classification network \parencite{simonyanVeryDeepConvolutional2015}.
For ESRGAN+ the peak learning rate was \num{6e-4}, and the feature loss, pixel loss (MAE), and adversarial loss parameters were weighted at \num{1}, \num{0.01}, and \num{0.005} respectively.
RDN\textdaggerdbl{} had a peak learning rate of \num{3e-4} and did not require loss component weighting because only L1 pixel loss is used.
Bicubic interpolation was carried out using the implementation provided in Pillow \parencite{vankemenadePythonpillowPillow2021}, a ubiquitous open source Python imaging library.
Inference is carried out using the frozen weights of the trained upsampling models, and takes approximately \num{0.1} s per 32 \texttimes{} 32 pixel tile.
Inference is performed on a tiled basis due to the size of input grids being too large for GPU RAM, and the results may be patched together for full extent visualisation and analysis, or displayed as single tiles.
Predicted outputs are inverse normalised to return the cell values to appropriately scaled TMI units.

\subsection{Accuracy Metrics}
The functional aim of super-resolution geophysics is to accurately predict realistic high frequency details to add to a low-resolution grid.
To quantify this, we calculate root mean square error (RMSE) and structural similarity metrics (SSIM and MS-SSIM), on TMI, high pass filtered TMI, and first vertical derivative (1VD) filtered TMI results for each upsampling method across several sample extents.
Euclidean accuracy measures like RMSE quantify the per-pixel accuracy of a predicted grid compared to its corresponding high-resolution ground truth grid.
For this metric, quality improves as the error value approaches \num{0}.
The Structural Similarity (SSIM) \parencite{wangImageQualityAssessment2004} and Multi-Scale Structural Similarity (MSSSIM) \parencite{wangMultiscaleStructuralSimilarity2003} image quality metrics use sliding windows to quantify image perceptual similarity based on localised structural information.
MS-SSIM extends SSIM by performing a weighted sum of the measure at several different scales.
In both structural metrics, the result is a combination of localised image luminance, contrast, and structural information.
A SSIM value of 1 indicates perfect similarity, and values approaching 0 indicate increasing dissimilarity.

\section{Results}
Results are presented to compare the three methods described above, with the metrics of RMSE, SSIM and MS-SSIM, as well as observed perceptual quality.
In addition to unfiltered TMI comparisons, high pass filtered and first vertical derivative TMI grids are also shown.
These products are commonly used in geophysics to investigate high frequency components in grids.

\subsection{Test dataset}
We first present a visual comparison of a selected feature rich \SI{80}{\metre} cell size LR tile, its counterpart \SI{20}{\metre} HR ground truth tile, and the result of; the bicubic upscaling filter, the RDN\textdaggerdbl{} upsampling network, and the ESRGAN+ upsampling network as applied to the LR tile (\cref{fig:resultsvis}).
This tile was selected from the reserved test region in the Eastern Goldfields Superterrane, and neither of the low- or high-resolution samples were seen during training.
The result of bicubic interpolation (\cref{fig:resultsvis} c) demonstrates the smoothing effect of the bicubic filter, while the Residual Dense Network (\cref{fig:resultsvis} d) and ESRGAN+ network (\cref{fig:resultsvis} e) show added detail.
The two neural network methods more closely match the ground truth \SI{20}{\metre} tile than the bicubic upsampled image does, when observing feature edges and textural detail.

\begin{figure}[hbt]
    % \includegraphics[width=\textwidth]{fig/p1/}
    \caption[Visual inference results]{Visual comparisons of a selected tile from the reserved test region.
    The \SI{80}{\metre} low-resolution input (a) is shown at equivalent size to the \SI{20}{\metre} high-resolution ground truth (b) using nearest neighbour interpolation.
    The colourmap is shared between subfigures.
    }
    \label{fig:resultsvis}
\end{figure}

\Cref{fig:residuals} demonstrates the error residuals between the predicted TMI grids for each upsampling method and the HR ground truth.
For the selected tile, the RMSE is best minimised using RDN\textdaggerdbl{}, which also shows the best structural metric performance.
ESRGAN+ outperforms the bicubic method in RMSE and MSSIM\@.

\begin{figure}[hbt]
    % \includegraphics[width=\textwidth]{fig/p1/}
    \caption[Error residuals map for a selected tile]{Error residuals map for the selected test tile, for each upsampling method; Bicubic (a), RDN\textdaggerdbl{} (b), and ESRGAN+ (c).
    Image quality metrics are reported for each upsampled tile, calculated against the groundtruth HR\@.}
    \label{fig:residuals}
\end{figure}

The prediction of higher frequencies can be quantified using the Radially Averaged Power Spectral Density.
In the Fourier domain, the amplitudes of an array's component frequencies are mapped to coordinates representing their orientation.
The Radially Averaged Power Spectral Density (RAPSD) \parencite{ulichneyDitheringBlueNoise1988} is a one-dimensional representation of the cumulative power of each frequency component, in any orientation within the image.
\cref{fig:rapsd} shows the RAPSD for the different methods over the test extent shown in \cref{fig:trainvaldata}. The deep learning methods have consistently superior power in predicted wavelengths between approximately \SI{640}{\metre} and \SI{120}{\metre}, with RDN\textdaggerdbl{} closely matching the groundtruth spectra, while ESRGAN+ tends to exaggerate.

\begin{figure}[hbt]
    % \includegraphics[width=\textwidth]{fig/p1/}
    \caption[short]{Radially Averaged Power Spectra for the complete test extent shown in \cref{fig:trainvaldata}.
    The Nyquist wavelengths for the high-resolution (and upsampled) rasters and low-resolution raster are also shown.
    The frequency axis has been transformed to wavelength, and the spectra have been normalised for direct comparison.
    Note the complete test extent is covered by surveys with a range of line spacings from \SI{100}{\metre} to \SI{20}{\metre}, with \SI{100}{\metre} being the most extensive.
    The Nyquist wavelength of the \SI{100}{\metre} surveys (optimal grid cell size approximately \SI{20}{\metre}) likely causes the reduction in power at \SI{55}{\metre} and \SI{220}{\metre}.
    }
    \label{fig:rapsd}
\end{figure}

To visualise the contribution of these enhanced high frequencies in the resulting grid, the super-resolved output from each method is high pass filtered, with a cut-off wavelength equivalent to the Nyquist wavelength of the LR grid.
By filtering at this wavelength, only frequencies added by the upsampling process will be shown in the output (\cref{fig:filtered}). Bicubic interpolation (\cref{fig:filtered} c) fails to add significant high frequency components.
RDN\textdaggerdbl{} (\cref{fig:filtered} d) appears to approximate similar high frequencies to the HR tile (\cref{fig:filtered} b), while ESRGAN+ (\cref{fig:filtered} e) shows potentially excessive predicted high frequency components.
Finally, metrics for the full set of test tiles are reported in \cref{tab:metrics}.
The non-GAN CNN approach of RDN\textdaggerdbl{} remains the most accurate method for the entire test grid.
Several routinely occurring artefacts are observed in the two super-resolution products, especially in ESRGAN+ which incorporates details it has learned from the Discriminator network loss.
The First Vertical Derivative filter is used in \cref{fig:jhillvis} to demonstrate the ability to perform common geophysical filters on super resolved grids, and to emphasise examples of these artefacts.
The most apparent artefact arises from the inference implementation when upsampling a grid larger than fits in memory, where visible edges appear around individual tiles in the compiled inference grid (e.g. \cref{fig:jhillvis}, *).
This could be reduced by adjusting the size of inference tiles, or slightly overlapping adjacent input tiles.
Predictions from ESRGAN+ commonly show a ripple-like texture (\cref{fig:jhillvis}, \^{ }), especially around pronounced high TMI features.
The effect of this texture occasionally reveals features matching the high-resolution groundtruth that are not predicted by the bicubic or RDN\textdaggerdbl{} upsampling, but the excess of “noisy” features present in ESRGAN+ predictions will likely limit its applicability when interpreting low-resolution grids with no corresponding groundtruth.

\begin{figure}[hbt]
    % \includegraphics[width=\textwidth]{fig/p1/}
    \caption[High Pass filtered results]{High Pass filtered test tile and its upsampled counterparts.
    The cut-off for the high pass Butterworth filter was selected with wavelength equal to the Nyquist wavelength of the LR grid, i.e. four times the HR Nyquist wavelength
    }
    \label{fig:filtered}
\end{figure}

\begin{table}
    \begin{tabularray}
    \end{tabularray}
    % \begin{tabularray}{l|ll|ll|ll}
    %             & Bicubic        &                          & RDN\textdaggerdbl{}     &                          & ESRGAN+       &                    \\
    %             & Mean           & Standard Deviation       & Mean                    & StandardDeviation       & Mean          & Standard Deviation \\
    %     \hline{}
    %     RMSE       & \num{13.545}   & \num{26.576}             & \num{7.265}             & \num{13.741}             & \num{11.120}  & \num{21.670}             \\
    %     SISM       &  \num{0.924}   &  \num{0.047}             & \num{0.959}             &  \num{0.037}             &  \num{0.922}  &  \num{0.054}             \\
    %     MS-SSIM    &  \num{0.971}   &  \num{0.018}             & \num{0.988}             &  \num{0.012}             &  \num{0.976}  &  \num{0.020}             \\
    %     \noalign{}

    % \end{tabularray}
    \caption[Accuracy Metrics]{
        Accuracy metrics for each upsampling method.
        The best performing method for each metric is bolded.
     }
    \label{tab:metrics}
\end{table}

\subsection{Jasper Hill / Lord Byron super-resolution}
A low-resolution TMI extent from the \SI{80}{\metre} state map over the Jasper Hill major resource project was selected for detailed investigation.
This extent was surveyed at \SI{50}{\metre} (optimal cell size of \SI{10}{\metre}), and is outside of both the defined training and test extents.
A zoomed result for each upsampling method is shown in \cref{fig:jhilldykes}.
The bicubic filter produces a smooth interpolation with limited magnetic intensity enhancement of the features, while both neural network methods produce a more accurate value prediction.
East-West striking features, like those that have been associated with gold mineralisation in the region \parencite[p.~283]{salierTimingSourceGoldbearing2003} are better delineated when using RDN\textdaggerdbl{} and ESRGAN+, and nearly unobservable with bicubic interpolation.
This can be seen in the line profile (\cref{fig:jhilldykes}, f), where a series of East-West striking features have a total magnitude of approximately \SI{100}nT in the low-resolution and bicubic grids, versus approximately \SI{200}nT in the Residual Dense Network prediction and HR groundtruth.
The ESRGAN+ prediction profile shows two distinct low TMI features, but they are poorly located and incoherent in the TMI grid (\cref{fig:jhilldykes} e), which shows an example of the ripple-mark artefact previously noted.

\begin{figure}[hbt]
    % \includegraphics[width=\textwidth]{fig/p1/}
    \caption[First Vertical Derivative SR TMI over the Mt Mason resource project]{First Vertical Derivative TMI over the Mt Mason resource project, with the super-resolution predictions (d, e) showing a variety of inference artefacts.
    Red asterisks (*) show a vertical tile boundary present as a 3--4 pixel-wide error in predicted TMI value.
    Red caret (\^{ }) indicates a region of subtle ripple-mark textural artefact, only present in ESRGAN+ predictions.
    }
    \label{fig:jhillvis}
\end{figure}

\begin{figure}[hbt]
    % \includegraphics[width=\textwidth]{fig/p1/}
    \caption[Jasper Hills Project TMI grids and line profile]{Jasper Hills Project TMI grids (a--e) and line profile (f).
    Bicubic interpolation of the low-resolution grid closely matches the low-resolution grid, while both super-resolution methods better approximate the magnitude of the features present in the HR profile, between \SI{650}{\metre} and \SI{1020}{\metre}.
    }
    \label{fig:jhilldykes}
\end{figure}

\section{Discussion}
These results demonstrate that a neural network approach is suitable for high quality super-resolution of geophysics data, surpassing bicubic interpolation in each metric and better resolving structural features.
Importantly, mineralisation controlling structural features that are unresolvable in low-resolution grids become observable in super-resolved grids using a Residual Dense Network.
RDN\textdaggerdbl{} outperforms ESRGAN+ in both accuracy and structural metrics, and most closely visually matches the high resolution groundtruth.
However, ESRGAN+ occasionally appears to better reconstruct features present in the high-resolution ground truth when compared to RDN\textdaggerdbl{}, but at the cost of significant textural noise.
Based on this, RDN\textdaggerdbl{} shows the best performance for super-resolution CNN upsampling of magnetic grids, to assist in the interpretation of low-resolution grids.
The deep learning methods used here can be trained with data from other geospatial extents, either from scratch or by initialising the training with pre-existing model weights \parencite[][e.g.]{wangMineGANEffectiveKnowledge2020}.
The existing models can also be applied to other extents of \SI{80}{\metre} TMI grids without further training.
However, the training data used here are solely \SI{80}{\metre} TMI grids interpolated from high-resolution \SI{20}{\metre} state map extents in the southwest Eastern Goldfields Superterrane.
Magnetic anomalies and features that are dissimilar from those represented in the Superterrane (for example, different geological settings, or regions with different magnetic inclination) are likely to suffer from reduced performance.
This applies also to grids that do not have a cell size of \SI{80}{\metre}.
An example use case for either the method or trained models is super-resolving the Total Magnetic Intensity (TMI) Grid of Australia 2019 - seventh edition which is published by Geoscience Australia in only \SI{80}{\metre} and \SI{40}{\metre} cell size.
The trained \SI{80}{\metre} models in this work could be applied to the \SI{80}{\metre} TMI grid, or the method used with existing state map data to train a two times scale model to super-resolve the \SI{40}{\metre} grid to \SI{20}{\metre}.
Transferability of the model used in this study to other geological settings and magnetic inclinations requires further investigation, with the aim of developing a single multi-domain potential field upscaling model.

The use of the state magnetic map at \SI{80}{\metre} and \SI{20}{\metre} for training data serves as a ready-made analogue for a low pass filter process, which the super-resolution networks successfully learnt to reverse.
While the result presented here demonstrates the strong applicability of performing super-resolution with grids containing magnetic textures and features, it does not yet demonstrate a capability to super-resolve widely spaced line surveys as if they had been surveyed at closer line spacing.
Such grids include artifacts from the gridding process that do not occur in low pass filtered or interpolated high-resolution grids, and will present an additional challenge to super-resolve.
These challenges remain for future work.
Finally, the current models show good performance at a scale factor of \num{4}, which is a typically investigated scale factor in super-resolution research.
Provided with sufficient training data, super-resolution geophysics at other factors would be beneficial, especially targeting typical scale factors between regional and district-scale exploration surveys.

\section{Conclusions}
Convolutional neural network architectures, such as RDN and ESRGAN, are capable of super-resolution upsampling low-resolution magnetic grids into realistic high-resolution grids.
These super-resolved grids contain structural features and textural information that are accurate against ground truth high-resolution grids, that were otherwise unrecoverable through existing interpolation methods.
The method and existing trained models can be applied to other magnetic grid extents, in the Eastern Goldfields Superterrane and beyond.

\section{Declaration of Competing Interest}
The authors declare the following financial interests / personal relationships which may be considered as potential competing interests: This work was supported by a Rio Tinto Iron Ore PhD scholarship.

\printbibliography{}

\end{document}

### 2023-07-20 paper1.tex
Include figures and tables

@@
 \begin{figure}[hbt]
-    \includegraphics[width=\textwidth]{fig/p1/fig1.jpg}
+    \includegraphics[width=\textwidth]{fig/p1/image1.png}
     \caption[Comparison of different resolution grids]{Low resolution \SI{80}{\metre} cell size (a), and high-resolution \SI{20}{\metre} cell size (b) TMI grids over the same extent.
@@
 Neural network based super-resolution has seen recent success across many scientific disciplines on data other than natural images.
-It is popular in satellite remote sensing \parencite[e.g.][]{lanarasSuperresolutionSentinel2Images2018b,wangUltradenseGANSatellite2019}, and has been applied to astrophysics \parencite[e.g.][]{jungbluthSingleframeSuperresolutionSolar2019,salvatelliUsingUNetsCreate2019}, fluid dynamics \parencite{bodeUsingPhysicsinformedEnhanced2021}, elevation models \parencite{leongDeepBedMapDeepNeural2020}, hyperspectral data \parencite[e.g.][]{arunCNNBasedSuperResolutionHyperspectral2020}, and seismic geophysics data \parencite[e.g.][]{liDeepLearningSimultaneous2021,wangDeeplearningbasedSeismicData2018,wangAdaptingResidualDense2022,yuDeepLearningDenoising2019}.
+It is popular in satellite remote sensing \parencite[e.g.][]{lanarasSuperresolutionSentinel2Images2018,wangUltradenseGANSatellite2019}, and has been applied to astrophysics \parencite[e.g.][]{jungbluthSingleframeSuperresolutionSolar2019,salvatelliUsingUNetsCreate2019}, fluid dynamics \parencite{bodeUsingPhysicsinformedEnhanced2021}, elevation models \parencite{leongDeepBedMapDeepNeural2020}, hyperspectral data \parencite[e.g.][]{arunCNNBasedSuperResolutionHyperspectral2020}, and seismic geophysics data \parencite[e.g.][]{liDeepLearningSimultaneous2021,wangDeeplearningbasedSeismicData2018,wangAdaptingResidualDense2022,yuDeepLearningDenoising2019}.
 These authors typically report a lower error between the super-resolution upsampled product and ground truth data when compared to a bicubic upsampled product and the ground truth data, as well as improved perceptual quality.
@@
 \begin{figure}
-    % \includegraphics[width=\textwidth]{fig/p1/}
+    \includegraphics[width=\textwidth]{fig/p1/image2.png}
     \caption[The RDN architecture]{The RDN architecture, which acts as the ESRGAN generator.
@@
 \begin{figure}[hbt]
-    % \includegraphics[width=\textwidth]{fig/p1/}
+    \includegraphics[width=\textwidth]{fig/p1/image3.png}
     \caption[Basic Blocks]{Each Basic Block (\cref{fig:rdn}, orange) comprises three weighted Residual Dense Blocks (\cref{fig:convs}).
@@
 \begin{figure}[hbt]
-    % \includegraphics[width=\textwidth]{fig/p1/}
+    \includegraphics[width=\textwidth]{fig/p1/image4.png}
     \caption[RDB convolutional layers]{Each Residual Dense Block (\cref{fig:rdb}, purple) comprises four convolutional layers, with additional learning pathways present as residual connections (black), and dense connections (green).
@@
 
-\begin{figure}[hbt]
-    % \includegraphics[width=\textwidth]{fig/p1/}
+\begin{figure}[]
+    \includegraphics[width=\textwidth]{fig/p1/image5.png}
     \caption[Dataset context]{Reserved training/validation and test areas of Eastern Goldfields Superterrane magnetic grid, and their tectonic context.
@@
 
-\begin{figure}[hbt]
-    % \includegraphics[width=\textwidth]{fig/p1/}
+\begin{figure}
+    \includegraphics[width=\textwidth]{fig/p1/image6.png}
     \caption[Visual inference results]{Visual comparisons of a selected tile from the reserved test region.
@@
 
-\begin{figure}[hbt]
-    % \includegraphics[width=\textwidth]{fig/p1/}
+\begin{figure}
+    \includegraphics[width=\textwidth]{fig/p1/image7.png}
     \caption[Error residuals map for a selected tile]{Error residuals map for the selected test tile, for each upsampling method; Bicubic (a), RDN\textdaggerdbl{} (b), and ESRGAN+ (c).
@@
 
-\begin{figure}[hbt]
-    % \includegraphics[width=\textwidth]{fig/p1/}
+% TODO USE REVISED MANUSCRIPT FIGURES
+
+\begin{figure}
+    \includegraphics[width=\textwidth]{fig/p1/image8.png}
     \caption[short]{Radially Averaged Power Spectra for the complete test extent shown in \cref{fig:trainvaldata}.
@@
 \begin{figure}[hbt]
-    % \includegraphics[width=\textwidth]{fig/p1/}
+    \includegraphics[width=\textwidth]{fig/p1/image9.png}
     \caption[High Pass filtered results]{High Pass filtered test tile and its upsampled counterparts.
@@
 \begin{table}
-    \begin{tabularray}
-    \end{tabularray}
-    % \begin{tabularray}{l|ll|ll|ll}
-    %             & Bicubic        &                          & RDN\textdaggerdbl{}     &                          & ESRGAN+       &                    \\
-    %             & Mean           & Standard Deviation       & Mean                    & StandardDeviation       & Mean          & Standard Deviation \\
-    %     \hline{}
-    %     RMSE       & \num{13.545}   & \num{26.576}             & \num{7.265}             & \num{13.741}             & \num{11.120}  & \num{21.670}             \\
-    %     SISM       &  \num{0.924}   &  \num{0.047}             & \num{0.959}             &  \num{0.037}             &  \num{0.922}  &  \num{0.054}             \\
-    %     MS-SSIM    &  \num{0.971}   &  \num{0.018}             & \num{0.988}             &  \num{0.012}             &  \num{0.976}  &  \num{0.020}             \\
-    %     \noalign{}
+    \begin{tblr}{
+        colspec={
+            r
+            Q[si={table-format=2.3},r]
+            Q[si={table-format=2.3},l]
+            Q[si={table-format=2.3},r]
+            Q[si={table-format=2.3},l]
+            Q[si={table-format=2.3},r]
+            Q[si={table-format=2.3},l]
+            },
+        row{1-2} = {guard}
+    }
+    & Bicubic & & RDN\textdaggerdbl{} & & ESRGAN+ & \\
+    \hline{}
+    & Mean & {Standard \\ Deviation} & Mean & {Standard \\ Deviation} & Mean & {Standard \\ Deviation} \\
+    RMSE   & 13.545 & 26.576 & 7.265 & 13.741 & 11.120 & 21.670 \\
+    SISM    & 0.924 &  0.047 & 0.959 &  0.037 &  0.922 &  0.054 \\
+    MS-SSIM & 0.971 &  0.018 & 0.988 &  0.012 &  0.976 &  0.020 \\
+    \end{tblr}
 
-    % \end{tabularray}
     \caption[Accuracy Metrics]{
@@
 \begin{figure}[hbt]
-    % \includegraphics[width=\textwidth]{fig/p1/}
+    \includegraphics[width=\textwidth]{fig/p1/image10.png}
     \caption[First Vertical Derivative SR TMI over the Mt Mason resource project]{First Vertical Derivative TMI over the Mt Mason resource project, with the super-resolution predictions (d, e) showing a variety of inference artefacts.
@@
 \begin{figure}[hbt]
-    % \includegraphics[width=\textwidth]{fig/p1/}
+    \includegraphics[width=\textwidth]{fig/p1/image11.png}
+    \includegraphics[width=\textwidth]{fig/p1/image12.png}
     \caption[Jasper Hills Project TMI grids and line profile]{Jasper Hills Project TMI grids (a--e) and line profile (f).

### 2023-07-20 paper2.tex
Transcribe paper 2 draft from Word

\documentclass{article}
\input{preamble}
\begin{document}

\author{\and{Luke Thomas Smith} \and{Eun-Jung Holden} \and{Tom Horrocks} \and{Daniel Wedge} \and{Naveed Akhtar}}
\title{Super-Resolving Geophysical Surveys with Implicit Functions}
\date{\today}
\maketitle{}

\begin{abstract}
    Hi
\end{abstract}

\section{Introduction}
The analysis of potential field geophysical surveys relies on gridded sample data.
Sampling density and subsequent gridding processes impose limits on the observable detail in these data.
Recent work with both images and geophysical data has shown that these limits can be partially overcome using deep learning \parencite{moserHitchhikerGuideSuperResolution2023,smithMagneticGridResolution2022}.
However, the extent to which low-resolution geophysical data can be enhanced, the maximum useful upscaling factor, and characteristics of the resulting features remain to be fully explored.
These can be examined using the current generation of super-resolution networks, using arbitrary resolution, Multi-Layer Perceptron implicit functoin neural networks.

The first generation of super-resolution neural networks, starting with SRCNN \parencite{dongLearningDeepConvolutional2014}, were capable of upscaling at fixed factos with encouraging performance.
However, a separate trained model is required for each upscaling factor of interest, and performance beyond four time upscaling is modest.
Contemporary super-resolution can achieve arbitrary upscaling at larger factors using MLP implicit function super-resolution.
Implicit functions parameterise a function with a neural network analogue, which can be queried for information that fits the learnt function but was not represented by the training data.

One application of implicit neural networks is super-resolution (SR), the task of predicting interpolating values to resolve data in a higher resolution.
This task has previously been perfomed predominantly in the domain of Convolutional Neural Networks (CNN).
When compared to numerical methods such as bicubic filters, existing CNN based super-resolution methods for geophysical grids can predict infill pixels that add high frequency information which is repoted to be more accurate when compared to a ground trugh target \parencite{smithMagneticGridResolution2022}.
However, MLP based implicit networks can surpass CNNs for continuous domain super-resoltion with their explicit use of spatial coordinate features, such as pixel indices.
Be learning a signal as a function of its coordinates, arbitrary and continuous super-resolution is made possible bu predicting cell values at arbitrarily fine grid cell spacings.
While earlier CNN based SR methods can achieve upscaling at any trained scale factor, they require a bespoke model for inference at each different scale.
Using implicit functions, a single trained model is capable of high quality, arbitrary interpolation of the geophysical potential field, including at scales that were not seen during training.

\subsection{Resolution in geophysical surveys}
In exploration geophysics, the earth's naturally occurring magnetic or gravitational potential fields can be used to survey the petrophysical expression of the underlying geology.
Depending on the scale of investigation, surveys may be carried out from ground or airborne sensors, in a range of sampling regimes.
Detailed ground-based surveys can be sampled at point spacings of tens of metres while avoiding local obstacles, but at a regional scale, aircraft are used to provide rapid and uniform coverage regardless of access constraints.
These airborne surveys collect data at wider line spacing to minimise cost, typically between \SI{100}{\metre} and \SI{1000}{\metre}, but detailed surveys with line spacing closer than \SI{100}{\metre} are increasingly common.
Sampling along line is typically performed at \SI{10}{\hertz} or faster, which corresponds to several meters at a nominal flight speed of \SI{70}{\metre/\second} \parencite{goodwinAirborneMagneticRadiometric2023}.
Despite the use of precise navigation systems and skilled operators, these data are not collected in perfectly uniform lines at constant height, and the field samples also contain noise components.
Transforming these irregularly distributed line data to a uniformly spaced array is the challenge of regularisation.
Regularisation is performed by gridding, of which there are several distinct methods.
Minimum Curvature gridding \parencite{briggsMachineContouringUsing1974} is routinely applied in industry applications, as it gives good quality results in rapid time, with minimal manual intervention.
A comprehensive review of spatial interpolation methods is presented by \parencite{liReviewComparativeStudies2011}.
Each method of gridding has characteristic interpolation traits (which when undesired are termed artifacts), but irrespective of the gridding process, the detail resolvable in the output grid is a product of the final cell size.
Gridding at finer cell sizes preserves greater detail contained in the sampled data.

When the cell size covers a quantified distance, the maximum resolvable detail can be expressed as a wavelength.
This is the grids Nyquist wavelength, and is equal to twice the gridded cell size.
This is also known as the Nyquist frequency, the well-known limit at which sampled signals may be incorrectly resolved due to under sampling.
For example, a potential field that lacks significant wavelength components shorter than \SI{200}{\metre} will be adequately resolved by a grid with a cell size of \SI{100}{\metre}, without spurious features known as aliasing.

Extending this concept, arbitrarily shrinking the cell size will not resolve additional detail, without also predicting features with wavelengths shorter than those already present in the data.
These are limited by the sample spacing during acquisition.
As an additional constraint on the observable detail in sampled potential fields, the power of shorter wavelengths diminishes with increasing distances from the source.
Thus, potential fields grow smoother at larger source-sensor separation.

Considering all the factors that the limit the representation of short wavelength features in geophysical grids, accurately reconstructing or rediscovering any geologically significant features that have been lost during the survey and gridding process appears challenging.

\subsection{The benefit of higher resolution}
The nominal target resolution for different mapping scales depends on a survey's objectives, but in the absence of logistical constraints, higher resolution is preferred.
From visual observation, the benefits of higher resolution gridded geophysical data are obvious.
Details confined to short wavelengths such as near surface magnetic sources or small-scale structures are better localised and made more apparent in high resolution.
These features may provide important geological context, or better delineate structures manifested in the data.
In addition to human interpretation, machine processing of geophysical data is benefitted by using higher resolution data, with the typically negligible cost of increased computational load \parencite[e.g.][]{fitzgeraldArtificialIntelligenceTechniques2021}.

\subsection{Enhancing grid detail}
In order to resolve additional detail without additional sampling, it is required to predict the values of missing sample points.
Numerically, this can be done by interpolating functions, such as splines \parencite{keysCubicConvolutionInterpolation1981} or nearest neighbour methods.
These methods are limited in their performance by the quality of their neighbouring observed values, and their distance.
Deep learning methods also use their spatial neighbours, but do so in the context of trainable filters, and across larger extents of the input.
In this way, deep learning super-resolution upscaling models are supported by latent information retained from the training dataset, in addition to information contained within the input being upscaled.
For photographs and natural image rasters with large representative training corpuses available, such as ImageNet \parencite{dengImageNetLargescaleHierarchical2009} and DIV2K \parencite{agustssonNTIRE2017Challenge2017}, super-resolution methods have progressed to the point that high quality enhancement at four times scale in each axis is readily accessible to end-users \parencite[e.g.][]{wangRealESRGANTrainingRealWorld2021}.

Photographs and other rasters of interest to computer vision are typically created by capturing light from an image sensor or are explicitly mapped on a grid using a raster graphics program.
These data are encoded to regular arrays of pixel values, commonly as three-channel rasters representing the red, green, and blue intensities of each pixel.
In these rasters, each pixel is regularly distributed, and the resolution is isotropic and solely a factor of the pixel density of the sampling or constructed grid.
Contrastingly, geophysical grid rasters are created by point sample regularisation.
These point samples are irregularly spaced and often directionally dependent, especially in the case of airborne flight line sampling.
The resulting grid rasters may have isotropic cell size, but the frequency content in each axis is anisotropic, being a factor of the sample spacing and direction.
These grids also single channel, storing measurements of the geophysical property of interest.

A property of potential fields is that the power in high frequencies decreases with greater distance from the source.
At large source-sensor separations, higher frequencies are diminished below the noise floor to the point of unobservability, resulting in grids that show only broad scale features --- typically representing spatially extensive features deeper in the crust.
One method of restoring high frequency information to these grids is to calculate the potential as if it were sampled at a smaller source-sensor distance.
This is known as downward continuation \parencite{bullardDeterminationMassesNecessary1948}.
It is common for noise in the sampled grid product to be significantly worsened in the downward continued product, limiting the useful vertical extent of the method 6 times the cell size \parencite{dampneyEquivalentSourceTechnique1969,zuoDownwardContinuationTransformation2020}.
Once an independent signal has vanished below the noise floor, it is impossible to recover separately from noise components.
Downward continuation can be performed with field- or source-based methods \parencite{pilkingtonPotentialFieldContinuation2017}.

Recently, resolution enhancement with short wavelength prediction has been performed with deep learning super-resolution \parencite{smithMagneticGridResolution2022}.
While this method is capable of predicting short wavelengths and accurately super-resolving low-resolution magnetic grids, the data resolution was not limited by sample spacing, but rather a polynomial filter that supressed high frequencies.
Additionally, the trained network was limited to \num{4} times upscaling during inference.

\subsection{Convolutional neural networks for super-resolution}
Convolutional Neural Network (CNN) methods have long been well suited for computer vision tasks such as image classification and, more recently, super-resolution.
CNNs excel in deep learning tasks for raster data, due in part to the receptive field of the network.
The receptive field is formed from stacked layers of small convolutional kernels, typically with a size of 3x3 cells for modern CNNs.
These low-level kernels learn simple functions, which are convolved with deeper layers to learn increasingly complex filters across a larger image extent, widening the receptive field.
In an image, local features define important structures, which, as the network deepens, combine in the wider receptive field to define more global features.
Once trained, these filters are conditioned to transform low-resolution features into high-resolution features, using the neighbouring input values of the low-resolution grid in the context of filters learnt from the training data.

\begin{figure}[hbt]
    % \includegraphics[width=\textwidth]{fig/p2/image1.png}
    \caption[An example CNN]{
        An example deep learning Convolutional Neural Network (specifically RDN (Zhang et al., 2018)), showing a variety of convolution operations (blue rectangles), activation functions (orange), and intermediate pathways (green, blue, or black arrows).
        }
    \label{fig:egcnn}
\end{figure}

The earliest application of deep learning super-resolution was demonstrated by \parencite{dongLearningDeepConvolutional2014,dongImageSuperresolutionUsing2016}, which uses convolutional layers for low-resolution patch extraction, mapping, and reconstruction of high-resolution images.
These layers are analogous to hand-crafted processes in contemporary example-based super-resolution methods, but are fully trainable with the deep learning approach.
Following the success of \cite{dongLearningDeepConvolutional2014}, many iterative improvements have been made to CNN based SR\@.
These include SRCNN \parencite{dongImageSuperresolutionUsing2016}, RDN \parencite{zhangResidualDenseNetwork2018}, ESRGAN \parencite{wangESRGANEnhancedSuperresolution2018}, and others \parencite{ledigPhotorealisticSingleImage2017,limEnhancedDeepResidual2017}.
While each of these works contributes unique features to CNN based super-resolution, they follow a common design.
This comprises a set of initial input feature extraction convolutions, a sequence of convolutional blocks with activations (neurons), some number and arrangement of intermediate residual learning pathways (skip connections), and an upsampling block for feature upscaling and convolving latent features back to image space e.g. \cref{fig:egcnn}.
Additionally, a majority of contemporary super-resolution networks investigate upscaling at a fixed scale, typically 4x.
While these networks can be trained for different factors using an appropriately scaled training dataset, they are constrained during inference to factor they are trained for.
Arbitrary scale super-resolution has been achieved using convolutional networks, notably Meta-SR \parencite{huMetaSRMagnificationarbitraryNetwork2019} and scale-arbitrary SR \parencite{wangLearningSingleNetwork2021}.
However, these methods perform poorly on novel data outside of their training scale distribution \parencite{chenLearningContinuousImage2021}.

\subsection{Multi-layer Perceptron neural networks}
While Multi-layer Perceptron networks (MLP) have been used in science for decades, until recently networks partly or entirely comprising fully connected layers were not known for super-resolution.
\cite{tangDeepResidualNetworks2020} use stacked convolutional blocks for feature extraction, with a final fully connected layer for reconstructing a super-resolved image from the extracted features.
They suggest an MLP layer performs better for image reconstruction than a convolutional layer due to the wider receptive field of the MLP\@.
In an MLP, all neurons in each layer are connected to all neurons in the adjacent layer.
This contrasts with convolutional neural networks, where array elements are combined by the convolutional kernel as it feeds into deeper layers, which causes them to be sparsely connected.
A 1x1 convolutional kernel is occasionally considered analogous to an MLP\@.
Only in recent years have MLP based networks become a state-of-the-art alternative for super-resolution.

\begin{figure}[hbt]
    % \includegraphics[width=\textwidth]{fig/p2/image1.png}
    \caption[An example deep learning Multi-layer Perceptron]{
        The encoder, $E_\Phi$, can be implemented as a feature extractor based on RDN prior its upsampling layer \cref{fig:egcnn} or SwinIR \parencite[per][]{leeLocalTextureEstimator2022}.
        $f_\theta$ is an MLP network used as the decoder for image reconstruction.
        A long-range skip connection with simple upscaling allows low-resolution information to bypass the network.
        }
    \label{fig:egmlp}
\end{figure}

\subsection{Implicit functions with multi-layer perceptron neural networks}
Implicit functions aim to learn a specific function parameterised entirely by the weights of a neural network.
In an image or geophysical grid context, the function maps grid coordinates to the value at those coordinates.
While extensively developed for point cloud and other 3D data \parencite[e.g.][]{jiangLocalImplicitGrid2020}, there have been numerous examples for super-resolution.
These include SIREN \parencite{sitzmann2019siren}, LIIF \parencite{chenLearningContinuousImage2021}, and LTE \parencite{leeLocalTextureEstimator2022}.
Notably in these networks, the learnt function has continuous domain, despite the discretised input.
Super-resolution can be achieved by sampling the learnt function at any arbitrary grid cell size smaller than the original input \parencite{chenLearningContinuousImage2021}.
While a stand-alone MLP such as SIREN is capable of parameterising a single function, when used in an autoencoder framework (such as with LIIF and LTE), an arbitrary input can be encoded using a CNN, upscaled, and reconstructed using fully connected layers \cref{fig:egmlp}.
This approach generalises MLP based super-resolution to any image or grid, even those not seen in the training set.

\subsection{Local Texture Encoder}
Examples of MLP based autoencoders for for learning continuous image representation super-resolution are LIIF \cite{chenLearningContinuousImage2021} and  LTE \cite{leeLocalTextureEstimator2022}.
While both are structured as autoencoders, with a CNN or transformer-based encoder followed by an MLP decoder, LTE is selected for its higher performance in the image super-resolution domain compared to LIIF\@.
The CNN encoder in these networks can use the feature extraction capacity of traditional SR CNNs such as EDSR \parencite{limEnhancedDeepResidual2017} or RDN \parencite{zhangResidualDenseNetwork2018}, without their upscaling blocks.
Lee and Jin find LTE achieves higher performance when using a SwinIR transformer based encoder.
In the original implementation of these CNN SR networks, the extracted image features are upscaled and returned to “image-space” by convolutional layers to reshape to image dimensions.
In LTE and LIIF, the extracted features become latent features with identical dimension as the original input image and are further processed by the network, before reconstruction to image space by an MLP\@.
Additionally, of interest to geophysics, a significant proportion of the LTE super-resolution network is trained on features in the Fourier domain.
The encoder extracts image features, but these are immediately transformed to the frequency domain by fully trainable convolution layers, which output amplitude and frequency features.
Phase features are also extracted from the image by a fully connected network, and is used during image reconstruction.
Nearest neighbour upsampling is performed in the frequency domain to achieve the required output scale.
A long-range skip connection passes low-frequency image content to the output of the network, in order to emphasise the learning of high-frequency content within the network.

\section{Material and Methods}
\subsection{Synthetic dataset}
%TODO

\section{Declaration of Competing Interest}
The authors declare the following financial interests / personal relationships which may be considered as potential competing interests: This work was supported by a Rio Tinto Iron Ore PhD scholarship.

\printbibliography{}

\end{document}

### 2023-07-20 paper3.tex
Add outline of paper 3

\documentclass{article}
\input{preamble}
\begin{document}

\author{\and{Luke Thomas Smith} \and{Tom Horrocks} \and {Eun-Jung Holden} \and{Daniel Wedge} \and{Naveed Akhtar}}
\title{Implicit Neural Representation Case Studies for Potential Field Geophysics}
\date{\today}
\maketitle{}

\begin{abstract}

\end{abstract}

\section{Introduction}
    The advent of periodic activation functions for the well known multilayer perceptron (or fully connected network) has created a new research field, known as Implicit Neural Representation.
    Implicit Neural Representation (INR) is the task of representing a signal as a function of its coordinates.
    Such functions are known as coordinate multilayer perceptrons, or Coordinate MLPs.
    By parameterising the function in coordinate space, novel values of the function can be queried at coordinates within the continuous spatial domain.
    Periodic activation functions differ from standard linear activations, such as ReLU, by comprising the neuron with a function that repeats periodically.
    Such functions include sinusoids \parencite{sitzmann2019siren}, Gaussian \parencite{ramasinghePeriodicityUnifyingFramework2022}, and most recently, wavelets \parencite{saragadamWIREWaveletImplicit2023}.

    Geophysical potential fields are continuous functions in three dimensions, and are of importance to mineral exploration and geoscience.
    When surveying these fields for exploration geophysics, sample locations are scattered in x, y, and z, despite best efforts to conform to a regular grid or line sample regime.
    Regularising these samples to a two dimensional grid for interpretation, storage, and further machine processing is a well studied process with many methods available.
    After regularisation, the grid arrays can be subject to a large number of widely used filters, such as horizontal and vertical gradient calculation and their derivatives.
    These filters operate on the grid product, a representation of the potential field quantised by the cell spacing defined during the regularisation process.

    If a potential field survey could instead be encoded within an Implicit Neural Network as an INR, filters could be calculated analytically in the continuous three dimensional domain.
    With this representation the extraction of regularised two dimensional slices, namely grids, could be performed \emph{a posteri} of gridding.
    This would allow the use of all available original sample data in calculation of filters, and reduce the manual intervention required during the gridding process.
    Additionally, due to the continuous representation, grid resolution is not constrained by cell size selection.

\subsection{Implicit Neural Representation}
\label{sec:inr}
Realising their power in implicit representation for natural images, many works quicky investigated 
\begin{enumerate}
    \item MLPs
    \item Periodic activations
    \item Storage weights not cells
\end{enumerate}

\subsection{Geophysical Sampling}
\label{sec:geo_sampling}
Here, I discuss sampling in geophysics

\section{Method}
\subsection{SIREN}
\begin{enumerate}
    \item SIREN (or WIRE, if it improves)
    \item Regularisation loss
    \item Parameter opt
\end{enumerate}

\subsection{Training Particulars}
Performed on an Intel i5-12400 CPU with 32 GB RAM, and an Nvidia 3060 12 GB GPU.

ADAM, One Cycle LR, 1000 iter/epochs.

MSE loss.

\subsection{Data}
GADDS Wolfe Creek impact survey netCDF

Noddyverse

tba

\section{Results}
\subsection{Implicit gridding}
\begin{enumerate}
    \item Best attempt at recreating grid as gridded by GA.
    \item Demonstration of the range of altitude slices
\end{enumerate}

\subsection{Spatial gradients and filters}
\begin{enumerate}
    \item Horizontal Gradients
    \item Vertical Gradients
    \item Combinations and filters
\end{enumerate}

\section{Discussion}
\begin{enumerate}
    \item Limitations: Capacity of Network
    \item RAM usage (if I can't do batched C-MLP training)
    \item Accuracy of learnt x,y and z gradients
\end{enumerate}

\section{Conclusions}

\section{Acknowledgements}
This project is funded by a Rio Tinto Iron Ore PhD scholarship.

\printbibliography{}

\end{document}

### 2023-07-30 paper3.tex
Add physics sections and format

@@
 \input{preamble}
+\usepackage{amssymb}
 \begin{document}
@@
 \author{\and{Luke Thomas Smith} \and{Tom Horrocks} \and {Eun-Jung Holden} \and{Daniel Wedge} \and{Naveed Akhtar}}
-\title{Implicit Neural Representation Case Studies for Potential Field Geophysics}
+\title{Physics-informed Implicit Neural Representation for Potential Field Geophysics}
 \date{\today}
@@
 \label{sec:inr}
+Seminal work by \parencite{mildenhallNeRFRepresentingScenes2020} demonstrated the capacity for learning continuous functions from a set of coordinates.
+However, it was not until they were combined with periodic activation functions \parencite{sitzmann2019siren} that the implicit representations could adequately recreate high frequency signal.
+Following investigation by \parencite{ramasinghePeriodicityUnifyingFramework2022} shows that it is the magnitude of the first and second derivatives that enhance high-frequency capacity, rather than periodicity.
+
 Realising their power in implicit representation for natural images, many works quicky investigated
@@
 
-\subsection{Geophysical Sampling}
+\subsection{Automatic Differentiation}
+Automatic differentiation (AD) refers to one of several methods for computing derivatives, specifically to the accumulation of derivatives during function evaluation \parencite{baydin2018automatic}.
+This method underpins modern machine learning frameworks such as Pytorch \parencite{paszkePyTorchImperativeStyle2019}.
+In these frameworks, when evaluating a set of inputs against the models weight parameters, the derivatives with respect to the parameters are used to perform backpropogation when evaluating an objective function (loss).
+These derivative inform weight updates in the direction of the negative gradient, toward a minima in the objective function (for example, L2 norm between predictions and targets).
+However, automatic differentiation can also evaluate the derivatives with respect to the inputs.
+The gradient provides partial derivatives $\frac{\partial f}{\partial x}$, $\frac{\partial f}{\partial y}$, $\frac{\partial f}{\partial z}$.
+
+\subsection{Physics-Informed Neural Networks}
+\parencite{raissiPhysicsinformedNeuralNetworks2019} introduced Physics-informed neural networks (PINNs).
+When dealing with samples of phenomena which obey natural laws, there also exists \emph{a priori} constraints on those samples.
+These constrains can be used to regularise neural networks, vastly reducing the search space for physically possible solutions.
+
+\parencite{liImplicitStochasticGradient2023} replace the ubiquitous stochastic gradient descent optimiser \emph{Adam} with an implicit stochastic gradient descent (ISGD) method:
+$$\theta_{n+1} = \theta_{n} - \alpha \cdot \nabla L (\theta_{n+1})$$
+
+\parencite{sethiHardEnforcementPhysicsinformed2023} demonstrate that this regularisation does not have to be implemented as a loss function, but instead can be a \emph{hard} constraint embedded within the network.
+This hard constraint takes the form of a function, which satisfies the \emph{a priori} laws, applied to the output of the network prior PDE and regularisation.
+
+Potential fields in an airborne exploration context are constrained by a number of physical laws.
+From \parencite{blakelyPotentialTheoryGravity1996}, potential fields satisfy \emph{Laplace's equation},
+$$\nabla^2 \phi = 0$$
+This indicates the function lacks curvature, in three dimensions $\phi(x,y,z)$:
+$$\frac{\partial^2\phi}{\partial x^2} + \frac{\partial^2\phi}{\partial y^2} + \frac{\partial^2\phi}{\partial z^2} = 0$$
+
+\subsection{Geophysical Sampling and Continuation}
 \label{sec:geo_sampling}
-Here, I discuss sampling in geophysics
+Potential fields in geophysics are vector fields, but are typically sampled as a scalar in one direction.
+A scalar field can be parameterised with a single dimension at each spatial coordinate, while a vector field requires three orthogonal components at each coordinate \parencite{blakelyPotentialTheoryGravity1996}.
+
+$F = \nabla \phi$ for the gravity potential, $F = - \nabla \phi$ for the Magnetic potential.
+
+$\phi(x,y,z) = constant$ is an equipotential surface.
+If Laplaces equation: $\nabla^2 \phi = 0$ is satisfied, it is harmonic, and has continuous single valued first derivatives, and has second derivatives.
 
 \section{Method}
+\subsection{Notation}
+$\mathbb{R}^n$ Real n-dimensional vectors, named using lower-case letters, e.g. \boldmath{x}.
+
+$\mathbb{R}^{m\times{}n}$ $m*n$ dimensional matrices, named using upper-case letters, e.g. \boldmath{A}.
+
+\subsection{Differentiation}
+A Numerical Differentiation approach to gradient calculation here would be to evaluate $\frac{\partial{U}}{\partial{(x, y, z)}}$ at a set of randomly sampled coordinates $(x, y, z)_1 ... (x,y,z)_n$.
+However, using Automatic Differentiation within Pytorch, the continuous implicit represenation can be differentiated to provide gradients without being constrained by numerical precision or quantisation.
+These are also unstable, recognised in the geophysical community by divergence and noise in predictions depending on numerical methods.
+
 \subsection{SIREN}
@@
     \item Accuracy of learnt x,y and z gradients
+    \item Forward looking at the field of INR
 \end{enumerate}
+
+Implicit neural representation is a rapidly evolving field of research with many advances occuring within each year, borrowing contemporary deep learning improvements from related fields.
+In addition to constant work on improving the high-frequency learning capacity, the inclusion of additional dimensions or
 

### 2023-07-30 intro.tex
Improve manuscript workspace
Add siunitx and ignore compiled pdf
Ignore zotero managed bib
Rename style document

\documentclass[manuscript.tex]{subfiles}
\begin{document}

Then we wrote the entire thesis.

Are geophysical grids natural signals?
-   Lipschitz smoothness
-   Fourier power spectra fall-off

\end{document}

### 2023-07-30 manuscript.tex
Improve manuscript workspace
Add siunitx and ignore compiled pdf
Ignore zotero managed bib
Rename style document

% \includeonly{intro}
\documentclass[12pt,a4paper,twocolumn]{report}
\usepackage{thesisstyle}
\begin{document}
\author{Luke Thomas Smith}
\title{Deep learning for geophysics}
\date{\today}
\maketitle{}
\tableofcontents
\listoffigures
\listoftables
\subfile{intro}
% \subfile{paper1}
% \subfile{paper2}
% \subfile{paper3}
\clearpage
% \include{bibliography}
\end{document}

### 2023-08-16 paper3.tex
Update preamble
Work on introduction

--- 2023-07-20 paper3.tex
@@
-\documentclass{article}
-\input{preamble}
+\documentclass[manuscript.tex]{subfiles}
 \begin{document}
-
-\author{\and{Luke Thomas Smith} \and{Tom Horrocks} \and {Eun-Jung Holden} \and{Daniel Wedge} \and{Naveed Akhtar}}
-\title{Implicit Neural Representation Case Studies for Potential Field Geophysics}
+\setcounter{chapter}{1}
+\author{\and{Luke Thomas Smith} \and{Tom Horrocks} \and{Eun-Jung Holden} \and{Daniel Wedge} \and{Naveed Akhtar}}
+\title{Physics-informed Implicit Neural Representation for Potential Field Geophysics}
 \date{\today}
@@
 \begin{abstract}
-
+    The recent use of spatial coordinate features in multilayer perceptron neural networks provides exigient opportunities for potential field geophysics.
+    So called coordinate MLP networks allow for implicit learning of potential field samples as a function of their recorded sample locations.
+    Using this new paradigm of encoding spatial information within a neural network enables new methods for working with high-resolution potential field survey data.
+    We demonstrate the quality of the learnt implicit potential field function by encoding real airborne geophysical survey line data, and predicting constant level grids of arbitrary cell size.
+    We further demonstrate the potential for additional processing of the learnt function in the continuous domain using automatic differentiation, with the same tool used to train the neural network.
+    For example, directional gradients and subsequent filters are calculated prior grid quantisation, and therefore without the associated loss of high-resolution content during gridding.
+    The training process requires only the sample coordinates and recorded potential field for a single survey extent, and can be applied to various geophysical techniqes including magnetics and gravity, as well as radiometric or other grids.
 \end{abstract}
@@
 \section{Introduction}
-    The advent of periodic activation functions for the well known multilayer perceptron (or fully connected network) has created a new research field, known as Implicit Neural Representation.
-    Implicit Neural Representation (INR) is the task of representing a signal as a function of its coordinates.
-    Such functions are known as coordinate multilayer perceptrons, or Coordinate MLPs.
-    By parameterising the function in coordinate space, novel values of the function can be queried at coordinates within the continuous spatial domain.
-    Periodic activation functions differ from standard linear activations, such as ReLU, by comprising the neuron with a function that repeats periodically.
-    Such functions include sinusoids \parencite{sitzmann2019siren}, Gaussian \parencite{ramasinghePeriodicityUnifyingFramework2022}, and most recently, wavelets \parencite{saragadamWIREWaveletImplicit2023}.
+Geophysical potential fields are continuous function in three dimensions, and are of importance to geoscience and mineral exploration.
+When surveying these fields for exploration geophysics, sample locations are scattered in x, y, and z, despite best efforts to conform to a regular grid or line sample structure.
+These scattered data are typically regularised to a quantised grid, which loses high frequency information and gives rise to spurious artefacts that are a product of the survey and gridding, as opposed to the surveyed field.
+If a representation of the potential field could instead be encoded within a neural network, it is possible that high frequency information would be preserved in a continuous domain.
+With this continuous representation, grid resolution would not be constrained by an initial cell size selection, and further processing and filters could be calculated analytically in the continuous spatial domain.
+This would allow the use of all available original sample data in calculation of filters, and reduce the manual intervention required during the gridding process.
 
-    Geophysical potential fields are continuous functions in three dimensions, and are of importance to mineral exploration and geoscience.
-    When surveying these fields for exploration geophysics, sample locations are scattered in x, y, and z, despite best efforts to conform to a regular grid or line sample regime.
-    Regularising these samples to a two dimensional grid for interpretation, storage, and further machine processing is a well studied process with many methods available.
-    After regularisation, the grid arrays can be subject to a large number of widely used filters, such as horizontal and vertical gradient calculation and their derivatives.
-    These filters operate on the grid product, a representation of the potential field quantised by the cell spacing defined during the regularisation process.
+Encoding a potential field into a neural network can be performed using the recent technique of implicit neural represenation.
+Implicit neural representation (INR) is the task of representing a signal as a function of its coordinates.
+Networks designed to learn such functions are known as coordinate multilayer perceptrons, or coordinate MLPs.
+By parameterising the neural function in coordinate space, novel values of the function can be queried at arbitrary coordinates within the learnt continuous spatial domain.
+Coordinate MLPs have recently benefit from high frequency representation improvements through the use of periodic activations.
+Periodic activations such as sinusoids are continuously differentiable through the depth of the network, supporting high quality learning of implicit functions.
 
-    If a potential field survey could instead be encoded within an Implicit Neural Network as an INR, filters could be calculated analytically in the continuous three dimensional domain.
-    With this representation the extraction of regularised two dimensional slices, namely grids, could be performed \emph{a posteri} of gridding.
-    This would allow the use of all available original sample data in calculation of filters, and reduce the manual intervention required during the gridding process.
-    Additionally, due to the continuous representation, grid resolution is not constrained by cell size selection.
+Furthermore, these cordinate MLP networks can be constrained to obey geophysical laws, using physics-informed neural network regularisation.
+Imposing restrictions such as Laplace's equation on the network reduces the model search space, stabilising and speeding up training and returing inference results that obey these laws.
 
-\subsection{Implicit Neural Representation}
+The proposed method leverages recent approaches in the literature to learn a continuous volume of potential field geophysics, using a novel combination of physics-informed networks and implicit neural representation.
+This implicit represenation is used to generate levelled 2D grids directly from scattered sample data, as well as calculate gradients and further filters.
+These are compared against industry standard grids and filters.
+
+\subsection{Geophysical sampling and regularisation}
+\label{sec:geo_airborne}
+Airborne or ground-based potential field surveys sample a magnetic (or gravitational) scalar field on a three-dimensional drape surface.
+Cultural obstructions or topography within the survey extent cause this drape surface to be irregular, with the sample points scattered.
+The resolvable detail within the sampled field is a function of the sampling density, and the distance from the source.
+% It is common to define a nominally regular drape surface with these parameters in mind, while respecting the cost of acquisition.
+To enable digital processing and storage of the sample data following acquisition, the scattered points are regularised to a quantised grid.
+The Nyquist wavelength inherent to the selected grid cell size during regularisation limits the high-resolution information representable by the grid.
+Because grid regularisation is one of the earliest steps in processing geopysical surveys, this information fails to be utilised in any subsequent processing.
+% Subsequent processes such as frequency filtering or directional gradients are similary constrained by the parameters of the regularisation.
+% Additionally, storing the grid product requires amount of memory, to represent the value with adequate precision at each cell in the resulting grid.
+
+\label{sec:geo_physics}
+Potential fields in geophysics are vector fields, but are typically sampled as a scalar field in one direction.
+A vector field requires three orthogonal components at each coordinate, while a scalar field can be parameterised with a single component \parencite{blakelyPotentialTheoryGravity1996}.
+Therefore, a potential field survey can be parameterised as
+\begin{equation}
+    u = \phi\left(x,y,z\right)
+\end{equation}
+
+Potential fields in an airborne sampling context are constrained by a number of physical laws, including \emph{Laplace's equation},
+\[
+    \nabla^2 \phi = 0
+\]
+Or in three dimensions \( \phi\left(x,y,z\right) \):
+\begin{equation}
+    \label{eqn:Laplace}
+    \frac{\partial{}^2\phi}{\partial{}x^2} + \frac{\partial{}^2\phi}{\partial{}y^2} + \frac{\partial{}^2\phi}{\partial{}z^2} = 0
+\end{equation}
+%TODO Confirm logic here: % If Laplace's equation:\( \nabla^2 \phi = 0 \) is satisfied, it is harmonic, and has continuous single valued first derivatives, and has second derivatives.
+% This indicates the function lacks curvature.
+
+% Blakely:
+% A force field \(F\) is the gradient (or negative gradient) of the potential energy.
+% \( F = \nabla\phi \) for the gravity potential, \(F = - \nabla \phi\) for the Magnetic potential.
+% \( \phi(x,y,z) = constant \) is an equipotential surface.
+
+\subsection{Implicit neural representation}
 \label{sec:inr}
-Realising their power in implicit representation for natural images, many works quicky investigated 
+Multilayer perceptron (MLP) networks are fully connected networks, which have been ubiquitous in machine learning for several decades.
+An MLP comprises a sequence of layers of neurons, densely connected to all neurons in each adjacent layer.
+Each neuron is a discrete trainable function, comprising a weight multiplied by the input vector, an added bias term, and a subsequent scaling function termed the activation function.
+The structure of an MLP can be described by the number of neurons in each layer (features) the number of layers between the input and output (hidden layers), and the class of activation function used.
+
+A classic example MLP is an input vector of image pixel intensities \(u\), and an output vector of class labels \(l\). %, scaled by a function that transforms the output to a class probability.
+Training this example network with a large number of different images with class labels produces a model capable of predicting the class of novel input image vectors.
+A Coordinate MLP (CMLP) instead takes an input of explicitly stated pixel coordinates \(x,y\), and an output vector of image pixel intensities \(u\) at those coordinates.
+Training the CMLP requires a set of input coordinates and intensities from a single image, and results in a model capable of predicting the intensity of any arbitrary continuous coordinate within the input domain.
+Both tasks may use similar images and an MLP network structure with \(n\) hidden layers and \(m\) hidden features, but the predictive task is different.
+Coordinate MLP networks are a class of neural networks \(f\) which train \(u = f(x,y,z)\), with \(u\in\mathbb{R}^n\) and \((x,y,z)\in\mathbb{R}^3\), depending on the number of spatial dimensions used.
+
+Seminal work by \parencite{mildenhallNeRFRepresentingScenes2020} demonstrated implicit neural represenation of volume density and colour dimensions, learnt from five dimensions of radiance and spatial coordinates.
+However, it was not until the use of periodic activation functions \parencite{sitzmann2019siren} that implicit representation with CMLP networks could adequately recreate high frequency signals.
+Periodic activation functions differ from non-linear activations such as ReLU by comprising the neuron with a function which repeats periodically.
+Such functions include sinusoids \parencite{sitzmann2019siren}, Gaussians \parencite{ramasinghePeriodicityUnifyingFramework2022}, and most recently, wavelets \parencite{saragadamWIREWaveletImplicit2023}.
+Work by \parencite{ramasinghePeriodicityUnifyingFramework2022} revealed that it is the magnitude of the first and second derivatives of the activation that enhance high-frequency capacity, rather than periodicity.
+Periodic activations are important in enabling continuous differentiation throughout the depth of the network.
+%TODO Confirm re: blakely % ReLU has constant second derivative of zero, rendering it incapable of representing a harmonic function such as a potential field.
+
+Coordinate MLPs can be used for a variety of computer vision tasks, including three-dimensional point cloud represenation \parencite{qiPointNetDeepHierarchical2017}, and two-dimensional natural image representation tasks such as super-resolution and infilling \parencite{leeLocalTextureEstimator2022,chenLearningContinuousImage2021}.
+Resolution in these tasks is not limited by quantisation of the representation, but rather the capacity of the network architecture used.
+Increasing this capacity is currently the subject of very high interest in the machine learning research community, for example by leveraging new activation functions \parencite{saragadamWIREWaveletImplicit2023}, transforming the input space \parencite[e.g.][]{benbarkaSeeingImplicitNeural2022}, or using additional constraints on the search space such as physics-informed neural networks \parencite{raissiPhysicsinformedNeuralNetworks2019}.
+
+\subsection{Physics-informed neural networks}
+Physics-informed neural networks (PINNs) recognise that if the inputs to a neural network are samples of a function which follows some physical law, outputs from the model should similarly be constrained by that law.
+By regularising the network with an objective function which penalises solutions that don't fit the partial differential equations describing the law, it is possible to vastly reduce the physically valid solution search space.
+Examples of physics-informed constraints include enforcing initial or boundary conditions, or adherence to known properties of the modelled signal.
+As described in \cref{sec:geo_physics}, potential fields in geophysics obey \emph{Laplace's equation}, that the sum of partial second derivates is 0.
+Because CMLP networks with periodic activations are continuously differentiable, it is possible to enforce this constrain as an element of the overall loss function within the network.
+In addition to \(L^2\) (Mean Square Error) loss between the input and predicted coordinate values, a geophysics informed network could include a Laplace criterion \cref*{eqn:cri_laplace}.
+
+\begin{equation}
+    \label{eqn:cri_laplace}
+    \mathcal{L}_{PDE} = \beta{}\lVert{}\frac{\partial{}^2\phi}{\partial{}x^2} + \frac{\partial{}^2\phi}{\partial{}y^2} + \frac{\partial{}^2\phi}{\partial{}z^2}\rVert{}_{2}
+\end{equation}
+
+As denoted by the \(L^2\) operator \(\lVert{}\cdot{}\rVert{}_{2}\) and weighting \(\beta{}\), this criterion additionally penalises predictions that are not close to zero.
+
+\Textcite{sethiHardEnforcementPhysicsinformed2023} demonstrate that this regularisation does not have to be implemented as a loss function, but instead can be a hard constraint embedded within the network.
+This hard constraint takes the form of a function, which satisfies the \emph{a priori} laws, applied to the output of the network prior PDE and regularisation.
+Another approach \parencite{liImplicitStochasticGradient2023} replaces the ubiquitous stochastic gradient descent optimiser \emph{Adam} with an implicit stochastic gradient descent (ISGD) method.
+However, only the approach of \textcite{benbarkaSeeingImplicitNeural2022} is implemented for this work.
+% This method reduces the importance of batch size and learning rate
+% \[\theta_{n+1} = \theta_{n} - \alpha \cdot \nabla L (\theta_{n+1})\]
+
+\subsection{Automatic Differentiation}
+Automatic differentiation (AD) refers to one of several methods for computing derivatives, specifically to the accumulation of derivatives during function evaluation \parencite{baydin2018automatic}.
+This method underpins modern machine learning frameworks such as Pytorch \parencite{paszkePyTorchImperativeStyle2019}, which the framework used to construct the network architecture and perform training in this work.
+In these frameworks, training is performed by evaluating the result of a set of inputs using the current model weight parameters during a forward pass, accumulating the partial derivatives with respect to the parameters, and minimising an objective (loss) function using those gradients.
+These gradients inform weight updates in the direction of the negative gradient, toward a minima in the objective function. 
+However, automatic differentiation can also evaluate the derivatives with respect to the inputs, using the same high-performance AD framework (e.g. Pytorch).
+This can provide the partial derivatives \(\frac{\partial f}{\partial x}, \frac{\partial f}{\partial y}, \frac{\partial f}{\partial z}\), as well as higher order derivatives.
+
+\section{Method}
+\subsection{Notation}
+\(\mathbb{R}^n\) Real n-dimensional vectors, named using lower-case letters, e.g. \boldmath{u}.
+
+\(\mathbb{R}^{m\times{}n}\) \(m*n\) dimensional matrices, named using upper-case letters, e.g. \boldmath{A}.
+
+\subsection{Differentiation}
+A Numerical Differentiation approach to gradient calculation here would be to evaluate \(\frac{\partial{U}}{\partial{(x, y, z)}}\) at a set of randomly sampled coordinates \({(x, y, z)}_1 \dots {(x,y,z)}_n\).
+However, using Automatic Differentiation within Pytorch, the continuous implicit represenation can be differentiated to provide gradients without being constrained by numerical precision or quantisation.
+These are also unstable, recognised in the geophysical community by divergence and noise in predictions depending on numerical methods.
+
+\subsection{SIREN}
 \begin{enumerate}
-    \item MLPs
-    \item Periodic activations
-    \item Storage weights not cells
+    \item{SIREN (or WIRE, if it improves)}
+    \item{Regularisation loss}
+    \item{Parameter opt}
 \end{enumerate}
 
-\subsection{Geophysical Sampling}
-\label{sec:geo_sampling}
-Here, I discuss sampling in geophysics
-
-\section{Method}
-\subsection{SIREN}
-\begin{enumerate}
-    \item SIREN (or WIRE, if it improves)
-    \item Regularisation loss
-    \item Parameter opt
-\end{enumerate}
-
-\subsection{Training Particulars}
-Performed on an Intel i5-12400 CPU with 32 GB RAM, and an Nvidia 3060 12 GB GPU.
-
-ADAM, One Cycle LR, 1000 iter/epochs.
-
-MSE loss.
-
 \subsection{Data}
-GADDS Wolfe Creek impact survey netCDF
+The case study dataset used here is the 2002 Wolfe Creek meteorite impact magnetic survey (Geophysical Acquisition \& Processing Section \cite*{wolfecreek2019}).
+The high-resolution survey contains 402 line-kilometres of data at 50m line spacing with a nominal terrain clearance of 40 m.
+Both line data netCDF and grid raster products were downloaded from the Geoscience Australia Geophysical Archive Data Delivery System and used without further processing.
+The line data netCDF contains tie-levelled, micro-levelled, and AWAGS levelled magnetic variables, in respective order of processing levels.
 
@@
 
-tba
+\subsection{Training Particulars}
+% Performed on an Intel i5-12400 CPU with 32 GB RAM, and an Nvidia 3060 12 GB GPU.
+
+Implicit functions are trained using coordinate-value pairs, and for low-resolution images the entire cell value and cell coordinate dataset fits within GPU memory for batch gradient descent.
+The Wolfe Creek meteorite impact crater case study survey has 76,420 sample points, with the Geoscience Australia provided grid product having a resolution of 446 \(\times\) 445 cells.
+This coordinate dataset easily fits into available graphics memory, and can be trained using batch gradient descent.
+%However, training on large scattered aeromagnetic surveys with more than one million samples, memory becomes a constraint and mini-batch training is required.
+Training was performed on an Intel i9-10900KF workstation with an Nvidia RTX 3090 24 GB GPU\@.
+A highly accurate represenation can be learned in 1000 epochs using the Adam optimiser, for a duration of 90 seconds.
+The OneCycle learning rate scheduler \parencite{smithSuperconvergenceVeryFast2018} is used to provide fine tuning toward the end of training.
+
+MSE loss.
 
@@
 \begin{enumerate}
-    \item Best attempt at recreating grid as gridded by GA.
-    \item Demonstration of the range of altitude slices
+    \item{} Best attempt at recreating grid as gridded by GA.
+    \item{} Demonstration of the range of altitude slices
 \end{enumerate}
@@
 \begin{enumerate}
-    \item Horizontal Gradients
-    \item Vertical Gradients
-    \item Combinations and filters
+    \item{} Horizontal Gradients
+    \item{} Vertical Gradients
+    \item{} Combinations and filters
 \end{enumerate}
@@
 \begin{enumerate}
-    \item Limitations: Capacity of Network
-    \item RAM usage (if I can't do batched C-MLP training)
-    \item Accuracy of learnt x,y and z gradients
+    \item{} Limitations: Capacity of Network
+    \item{} RAM usage (if I can't do batched C-MLP training)
+    \item{} Accuracy of learnt x,y and z gradients
+    \item{} Forward looking at the field of INR
 \end{enumerate}
+
+% With this representation the extraction of regularised two dimensional slices, namely grids, could be performed \emph{a posteri} of gridding.
+% Regularising these samples to a two dimensional grid for interpretation, storage, and further machine processing is a well studied process with many methods available.
+% After regularisation, the grid arrays can be subject to a large number of widely used filters, such as horizontal and vertical gradient calculation and their derivatives.
+% These filters operate on the grid product, a representation of the potential field quantised by the cell spacing defined during the regularisation process.
+
+Implicit neural representation is a rapidly evolving field of research with many advances occuring within each year, borrowing contemporary deep learning improvements from related fields.
+In addition to constant work on improving the high-frequency learning capacity, the inclusion of additional dimensions or
 

### 2023-08-16 paper3.tex
Write methods section

@@
 \begin{abstract}
-    The recent use of spatial coordinate features in multilayer perceptron neural networks provides exigient opportunities for potential field geophysics.
+    The recent use of spatial coordinate features in multilayer perceptron (MLP) neural networks provides exigient opportunities for potential field geophysics.
     So called coordinate MLP networks allow for implicit learning of potential field samples as a function of their recorded sample locations.
@@
     We demonstrate the quality of the learnt implicit potential field function by encoding real airborne geophysical survey line data, and predicting constant level grids of arbitrary cell size.
-    We further demonstrate the potential for additional processing of the learnt function in the continuous domain using automatic differentiation, with the same tool used to train the neural network.
-    For example, directional gradients and subsequent filters are calculated prior grid quantisation, and therefore without the associated loss of high-resolution content during gridding.
-    The training process requires only the sample coordinates and recorded potential field for a single survey extent, and can be applied to various geophysical techniqes including magnetics and gravity, as well as radiometric or other grids.
+    We further demonstrate the potential for additional processing of the learnt function in the continuous domain using automatic differentiation, with the same framework used to train the neural network.
+    For example, directional gradients and subsequent filters are calculated prior grid quantisation, and therefore without the associated loss of high-resolution content imposed by gridding.
+    The training process requires only the sample coordinates and recorded potential field for a single survey extent, and can be applied to various geophysical techniqes including magnetics and gravity.
+%, as well as radiometric or other grids.
 \end{abstract}
@@
 
+Numerical methods for potential field continuation are unstable, recognised in the geophysical community by solution divergence and noise in predictions.
+
 \subsection{Implicit neural representation}
@@
 \subsection{Physics-informed neural networks}
+\label{sec:pinn}
 Physics-informed neural networks (PINNs) recognise that if the inputs to a neural network are samples of a function which follows some physical law, outputs from the model should similarly be constrained by that law.
@@
 \section{Method}
-\subsection{Notation}
-\(\mathbb{R}^n\) Real n-dimensional vectors, named using lower-case letters, e.g. \boldmath{u}.
-
-\(\mathbb{R}^{m\times{}n}\) \(m*n\) dimensional matrices, named using upper-case letters, e.g. \boldmath{A}.
-
-\subsection{Differentiation}
-A Numerical Differentiation approach to gradient calculation here would be to evaluate \(\frac{\partial{U}}{\partial{(x, y, z)}}\) at a set of randomly sampled coordinates \({(x, y, z)}_1 \dots {(x,y,z)}_n\).
-However, using Automatic Differentiation within Pytorch, the continuous implicit represenation can be differentiated to provide gradients without being constrained by numerical precision or quantisation.
-These are also unstable, recognised in the geophysical community by divergence and noise in predictions depending on numerical methods.
-
-\subsection{SIREN}
-\begin{enumerate}
-    \item{SIREN (or WIRE, if it improves)}
-    \item{Regularisation loss}
-    \item{Parameter opt}
-\end{enumerate}
+% \subsection{Notation}
+% Real n-dimensional vectors, named using lower-case letters are noted \(\mathbb{R}^n\), e.g. \boldmath{u}.
+% \(\mathbb{R}^{m\times{}n}\) \(m*n\) dimensional matrices, named using upper-case letters, e.g. \boldmath{A}.
 
 \subsection{Data}
-The case study dataset used here is the 2002 Wolfe Creek meteorite impact magnetic survey (Geophysical Acquisition \& Processing Section \cite*{wolfecreek2019}).
-The high-resolution survey contains 402 line-kilometres of data at 50m line spacing with a nominal terrain clearance of 40 m.
-Both line data netCDF and grid raster products were downloaded from the Geoscience Australia Geophysical Archive Data Delivery System and used without further processing.
+A case study dataset is made using the 2002 Wolfe Creek meteorite impact magnetic survey (Geophysical Acquisition \& Processing Section \cite*{wolfecreek2019}).
+This high-resolution survey contains \SI{402}{line-kilometres} of data at \SI{50}{\m} line spacing with a nominal terrain clearance of \SI{40}{\m}.
+The data used for implicit representation include the survey tie lines, standard in airborne geophysical surveys to reduce inter-line levelling noise.
+The standard deviation of the drape surface, including tie lines, is \SI{5}{\m}.
+
+Both line data netCDF and grid raster product for the Wolfe Creek survey were downloaded from the Geoscience Australia Geophysical Archive Data Delivery System and used without further processing.
 The line data netCDF contains tie-levelled, micro-levelled, and AWAGS levelled magnetic variables, in respective order of processing levels.
+% Tie-levelling is applied using only line data, while micro-levelling uses parameters calculated on an intermediate grid product of the line data.
+% AWAGS levelling is a final continuation of the microlevelled dataset to an Australian common datum, termed the \emph{AWAGS} datum.
+For the Wolfe Creek survey, the microlevelled magnetic data are used.
+Both geographic and projected coordinate systems can be used, provided the query coordinates for inference match those used during training.
+The three spatial coordinate dimensions are independently linearly min-max normalised between -1 and 1.
+While this means the latent spatial domain may be compressed relative to each other axis, the inverse normalisation process returns proportionality between axes.
+Magnetic field data are min-max normalised across the global values within the survey, and NaN values in any dimension are dropped from the training data.
 
-Noddyverse
+In order to validate the model performance during training, a random \qty{20}{\percent} of the survey sample points are reserved.
+% Not currently doing this % Testing of the model is performed on a randomly selected \qty{10}{\percent} of the sample points. 
+Inference is performed by querying novel coordinates within the learnt domain, specifically a regularly spaced grid for comparison with typical grid regularisation methods.
+
+\subsection{Network architecture}
+The Coordinate MLP architecture used comprises a simple fully connected network with \(N\) layers, each with \(m\) features.
+High quality implicit represenation has been achieved in contemporary INR research with only several hidden layers, typically between 3 and 8, and these depths are used here.
+The sinusoidal activation of \parencite{sitzmann2019siren} is used and comparison can be made to Gaussian and wavelet activations.
+Figure \cref{fig:arch} shows the structure of the architecture.
+
+\begin{figure}
+    \label{fig:arch}
+\end{figure}
 
@@
 Implicit functions are trained using coordinate-value pairs, and for low-resolution images the entire cell value and cell coordinate dataset fits within GPU memory for batch gradient descent.
-The Wolfe Creek meteorite impact crater case study survey has 76,420 sample points, with the Geoscience Australia provided grid product having a resolution of 446 \(\times\) 445 cells.
+The Wolfe Creek meteorite impact crater case study survey has \SI{76420}{} sample points, with the Geoscience Australia provided grid product having a resolution of 446 \(\times{}\) 445 cells.
 This coordinate dataset easily fits into available graphics memory, and can be trained using batch gradient descent.
@@
 A highly accurate represenation can be learned in 1000 epochs using the Adam optimiser, for a duration of 90 seconds.
-The OneCycle learning rate scheduler \parencite{smithSuperconvergenceVeryFast2018} is used to provide fine tuning toward the end of training.
+The OneCycle learning rate scheduler \parencite{smithSuperconvergenceVeryFast2018} is used to provide fine tuning at low learning rates toward the end of training.
 
-MSE loss.
+As described in \cref{sec:pinn}, the objective function comprises \(L^2\) loss between input and predicted field values, summed with weighted Laplace's equation loss, \cref{eqn:cri}.
+\begin{equation}
+    \label{eqn:cri}
+    \mathcal{L}_{Total} = \lVert{}u_{input} - u_{pred}\rVert{}_{2} + \beta{} \lVert{}\frac{\partial^{2}{u_{pred}}}{\partial{}\phi{}_{pred}^{2}}\rVert{}_{2}
+\end{equation}
+
+\subsection{Differentiation}
+A naive approach would be to evaluate the implicit represenation \(u = \phi{}(x, y, z)\) at a set of regular coordinates \({(x, y, z)}_1 \dots {(x,y,z)}_n\), and use numerical differentiation methods to calculate derivatives.
+However, using Automatic Differentiation within Pytorch, the implicit represenation can be differentiated with respect to its inputs to provide gradients without being constrained by quantisation.
+This is to directly sample \(\frac{\partial{u}}{\partial{\phi{}{(x,y,z)}}}\) at \({(x, y, z)}_1 \dots {(x,y,z)}_n\).
+Higher order derivatives can be also calculated using AD\@.
 
@@
 \subsection{Implicit gridding}
+\begin{figure}
+    \label{fig:grid}
+    \caption[]{Constant level grid predicted at the survey nominal terrain clearance \SI{40}{m}}
+\end{figure}
+
 \begin{enumerate}
-    \item{} Best attempt at recreating grid as gridded by GA.
+    \item{} Best attempt at recreating grid as gridded by GA\@.
     \item{} Demonstration of the range of altitude slices

### 2023-08-19 paper3.tex
Add results text

@@
 \subsection{Implicit gridding}
-\begin{figure}
+Querying a learnt implicit neural represenation (INR) using a regularly spaced \(x,y\) grid at a specific \(z\) height is a novel method for gridding geophysical potential field surveys.
+\Cref{fig:grid} shows the INR queried at \(z=\SI{40}{\meter}\), which is the nominal terrain clearance of the survey.
+Notably, the cell size can be selected by fining or coarsening the \(x,y\) spacing, including variable or anisotropic cell sizes.
+For natural images, using finer cell sizes accomplishes the computer vision task of super-resolution.
+However, for the potential field representation task, no additional high-frequency information is predicted by the MLP network and resolution remains limited by the survey sample spacing and neural network capacity.
+
+\begin{figure}[hbt]
+    \includegraphics[width=\textwidth]{fig/p3/grid_comparison.pdf}
+    \caption[Grid prediction]{Comparison between the ground-truth grid processed by Geoscience Australia (left) and the constant level grid queried from the INR at \SI{40}{\m} (right).}
     \label{fig:grid}
-    \caption[]{Constant level grid predicted at the survey nominal terrain clearance \SI{40}{m}}
 \end{figure}
 
+The INR can be queried at any continuous coordinate, including out-of-range values beyond the training domain.
+The predicted field becomes unstable beyond this boundary, which can be seen in the periphery of \cref{fig:grid}.
+
+Constant level grids can be queried from the INR at any height.
+\Cref{fig:grid35} shows the case study extent queried at \SI{35}{m}.
+While comparable features can still be interpreted within this level grid, the represenation learnt here fails to represent physically realistic continuation of the field.
+
+\begin{figure}[hbt]
+    %TODO query at AWAGS height and compare GA AWAGS grid.
+    % TODO check if provided grid is AWAGS or MICRO levelled - maybe grid data myself.
+    \includegraphics[width=\textwidth]{fig/p3/grid_comparison_35m.pdf}
+    \caption[Grid prediction]{A constant level grid queried from the INR at the AWAGS datum height of \SI{35}{m} (right).}
+    \label{fig:grid35}
+\end{figure}
+
+% The strong performance of the model is retained even when using a subsampled training dataset, here shown at \qty{30}{\percent} and \qty{10}{\percent} (\cref{fig:gridpct}) of the total available data.
+% % In both cases, the validaiton and test sets remain identical to the initial training split.
+
+% \begin{figure}[hbt]
+%     % \includegraphics[width=\textwidth]{fig/p3/grid_subpct.pdf}
+%     \caption[Grid subsampled]{Performance of level grid prediction shown at \qty{30}{\percent} and \qty{10}{\percent} random sampling of training data.}
+%     \label{fig:gridpct}
+% \end{figure}
+
+\subsection{Spatial derivatives and filters}
+Using AD, derivatives can be calculated between the input spatial coordinates and the output potential field represenation.
+While the horizontal derivatives correspond well to numerical derivatives calculated on the Wolfe Creek ground truth grid (\cref{fig:hori_grad}), the vertical derivative suffers poor performance (\cref{fig:vert_grad}).
+This correlates with the poor continuation performance of model when predicting level grids several meters or more beyond the nominal sample height.
+This is inrepreted as the model learning a poor represenation of the vertical component of the potential field.
+
+\begin{figure}[hbt]
+    % \includegraphics[width=\textwidth]{fig/p3/hori_grad.pdf}
+    \caption[Horizontal derivatives]{AD calculated horizontal derivatives of the INR\@. Left: Northing derivative, right: easting derivative}
+    \label{fig:hori_grad}
+\end{figure}
+
+\begin{figure}[hbt]
+    % \includegraphics[width=\textwidth]{fig/p3/vert_grad.pdf}
+    \caption[Vertical derivative]{AD calculated vertical derivative of the INR.}
+    \label{fig:vert_grad}
+\end{figure}
+
+Using the implicit representation, a selection of common geophysical filters are calculated prior to quantisation.
+
 \begin{enumerate}
-    \item{} Best attempt at recreating grid as gridded by GA\@.
-    \item{} Demonstration of the range of altitude slices
-\end{enumerate}
-
-\subsection{Spatial gradients and filters}
-\begin{enumerate}
-    \item{} Horizontal Gradients
-    \item{} Vertical Gradients
-    \item{} Combinations and filters
+    \item ASIG
+    \item tilt?
+    \item idk?
 \end{enumerate}
@@
 \section{Discussion}
-\begin{enumerate}
-    \item{} Limitations: Capacity of Network
-    \item{} RAM usage (if I can't do batched C-MLP training)
-    \item{} Accuracy of learnt x,y and z gradients
-    \item{} Forward looking at the field of INR
-\end{enumerate}
+The implicit represenation has strong representive capacity for the horizontal components of the potential field, generating level grids which are accurate against the ground truth grid.
+Level grids can be generated at any height, with best performance achieved near the realised nominal survey altitude.
+Performance worsens within approximately one standard deviation from that height (\SI{35} to \SI{45}{\m}), with gradual failure of the model outisde of that height range.
+% Even when using a small subset of the dataset, this performance is retained.
+It is interpreted from the poor quality of the vertical gradients and out-of-range predictions that the model is relying on learning a function between horizontally coplanar points, as opposed to a realistic vertical continuation function.
+While quantised grids can be queried at any cell size, short wavelength information beyond the Nyquist limit of the survey line sampling is not predicted.
+% TODO The addition of a PINN term for objective function ...
 
-% With this representation the extraction of regularised two dimensional slices, namely grids, could be performed \emph{a posteri} of gridding.
-% Regularising these samples to a two dimensional grid for interpretation, storage, and further machine processing is a well studied process with many methods available.
-% After regularisation, the grid arrays can be subject to a large number of widely used filters, such as horizontal and vertical gradient calculation and their derivatives.
-% These filters operate on the grid product, a representation of the potential field quantised by the cell spacing defined during the regularisation process.
+The case study survey presented is very small compared to typical regional aeromagnetic surveys.
+A demonstration of the method on a large aeromagnetic survey, requiring minibatch training, is included in \cref{app:menzies}.
+Training of this representation follows the parameters outlined in \cref{sec:training}, which were optimised for the Wolfe Creek case study, with the addition of a shuffled minibatch size of \SI{1024000}.
+Attempts to train the CMLP with small batch sizes did not converge.%, reflecting the non-convergance result found for training on very large subsampling factors of the line dataset.
 
-Implicit neural representation is a rapidly evolving field of research with many advances occuring within each year, borrowing contemporary deep learning improvements from related fields.
-In addition to constant work on improving the high-frequency learning capacity, the inclusion of additional dimensions or
+Implicit neural representation is a rapidly evolving field of research, and draws on contemporary deep learning improvements within related fields.
+In addition to improving the high-frequency learning capacity, physics informed loss functions promise higher quality vertical continuation performance. 
+The current method could trivially include additional target dimensions, which would allow representation learning of vector fields \(\mathbb{R}^{3}\) in three dimensions \(\mathbb{R}^{3}\).
+This has potential application in tensor fields and associated predictive tasks.
+These remain for future work.
 
 \section{Conclusions}
+High-resolution implicit neural represenation of potential field geophysics surveys is achieved with the use of coordinate MLP neural networks.
+Resolution in the represenation is limited by network capacity, rather than initial grid cell size selection during regularisation.
+Gradients and spatial filters can be caluclated using the full resolution of the learnt represenation, and gridded \emph{a posteri} of gradient or filter calculation.
 

### 2023-08-19 paper3.tex
Self review

@@
     So called coordinate MLP networks allow for implicit learning of potential field samples as a function of their recorded sample locations.
-    Using this new paradigm of encoding spatial information within a neural network enables new methods for working with high-resolution potential field survey data.
+    Using this new paradigm of encoding spatial information within a neural network enables new methods for working with potential field survey data.
     We demonstrate the quality of the learnt implicit potential field function by encoding real airborne geophysical survey line data, and predicting constant level grids of arbitrary cell size.
-    We further demonstrate the potential for additional processing of the learnt function in the continuous domain using automatic differentiation, with the same framework used to train the neural network.
+    We further demonstrate the potential for processing the learnt function in the continuous domain using automatic differentiation, with the same framework used to train the neural network.
     For example, directional gradients and subsequent filters are calculated prior grid quantisation, and therefore without the associated loss of high-resolution content imposed by gridding.
@@
 \section{Introduction}
-Geophysical potential fields are continuous function in three dimensions, and are of importance to geoscience and mineral exploration.
+Geophysical potential fields are continuous functions in three dimensions, and are of importance to geoscience and mineral exploration.
 When surveying these fields for exploration geophysics, sample locations are scattered in x, y, and z, despite best efforts to conform to a regular grid or line sample structure.
-These scattered data are typically regularised to a quantised grid, which loses high frequency information and gives rise to spurious artefacts that are a product of the survey and gridding, as opposed to the surveyed field.
+These scattered data are typically regularised to a quantised grid, which reduces high frequency information and gives rise to spurious artefacts that are a product of the gridding process, not the surveyed field.
 If a representation of the potential field could instead be encoded within a neural network, it is possible that high frequency information would be preserved in a continuous domain.
-With this continuous representation, grid resolution would not be constrained by an initial cell size selection, and further processing and filters could be calculated analytically in the continuous spatial domain.
-This would allow the use of all available original sample data in calculation of filters, and reduce the manual intervention required during the gridding process.
+Within the continuous representation, grid resolution is not constrained by an initial cell size selection, and further processing and filters can be calculated analytically in the continuous spatial domain.
+This allows the use of all available sample information in the calculation of filters, and reduces the manual intervention required during the gridding process.
 
@@
 Furthermore, these cordinate MLP networks can be constrained to obey geophysical laws, using physics-informed neural network regularisation.
-Imposing restrictions such as Laplace's equation on the network reduces the model search space, stabilising and speeding up training and returing inference results that obey these laws.
+Imposing restrictions such as Laplace's equation on the network reduces the model search space, stabilising and speeding up training and predicting solutions that obey these laws.
 
@@
 This implicit represenation is used to generate levelled 2D grids directly from scattered sample data, as well as calculate gradients and further filters.
-These are compared against industry standard grids and filters.
+These are compared against industry standard gridding methods and numerical filters.
 
@@
 Airborne or ground-based potential field surveys sample a magnetic (or gravitational) scalar field on a three-dimensional drape surface.
-Cultural obstructions or topography within the survey extent cause this drape surface to be irregular, with the sample points scattered.
+Cultural obstructions or topography within the survey extent cause this drape surface to be irregular, and the sample points scattered.
 The resolvable detail within the sampled field is a function of the sampling density, and the distance from the source.
@@
 The Nyquist wavelength inherent to the selected grid cell size during regularisation limits the high-resolution information representable by the grid.
-Because grid regularisation is one of the earliest steps in processing geopysical surveys, this information fails to be utilised in any subsequent processing.
+Because grid regularisation is one of the earliest steps in interpreting geophysical surveys, this information fails to be utilised in any subsequent task.
 % Subsequent processes such as frequency filtering or directional gradients are similary constrained by the parameters of the regularisation.
@@
 \]
-Or in three dimensions \( \phi\left(x,y,z\right) \):
+In three dimensions \( \phi\left(x,y,z\right) \):
 \begin{equation}
@@
 
-Numerical methods for potential field continuation are unstable, recognised in the geophysical community by solution divergence and noise in predictions.
+% Numerical methods for potential field continuation are unstable, recognised in the geophysical community by solution divergence and noise in predictions.
 
@@
 Training this example network with a large number of different images with class labels produces a model capable of predicting the class of novel input image vectors.
-A Coordinate MLP (CMLP) instead takes an input of explicitly stated pixel coordinates \(x,y\), and an output vector of image pixel intensities \(u\) at those coordinates.
+A Coordinate MLP (CMLP) instead takes an input of explicitly stated pixel coordinates \((x,y)\), and an output vector of image pixel intensities \(u\) at those coordinates.
 Training the CMLP requires a set of input coordinates and intensities from a single image, and results in a model capable of predicting the intensity of any arbitrary continuous coordinate within the input domain.
-Both tasks may use similar images and an MLP network structure with \(n\) hidden layers and \(m\) hidden features, but the predictive task is different.
-Coordinate MLP networks are a class of neural networks \(f\) which train \(u = f(x,y,z)\), with \(u\in\mathbb{R}^n\) and \((x,y,z)\in\mathbb{R}^3\), depending on the number of spatial dimensions used.
+Both tasks may use similar images and an MLP network structure with the same \(n\) hidden layers and \(m\) hidden features, but the use of coordinates as inputs and intensities as outputs changes the predictive task.
+Coordinate MLP networks for predicting scalar fields are a class of neural networks \(f\) which train \(u = f(x,y,z)\), with \(u\in\mathbb{R}^1\) and \((x,y,z)\in\mathbb{R}^3\).
 
@@
 
-Both line data netCDF and grid raster product for the Wolfe Creek survey were downloaded from the Geoscience Australia Geophysical Archive Data Delivery System and used without further processing.
+Both the line data netCDF and grid raster for the Wolfe Creek survey were downloaded from the Geoscience Australia Geophysical Archive Data Delivery System and used without further processing.
 The line data netCDF contains tie-levelled, micro-levelled, and AWAGS levelled magnetic variables, in respective order of processing levels.
@@
 % Not currently doing this % Testing of the model is performed on a randomly selected \qty{10}{\percent} of the sample points. 
-Inference is performed by querying novel coordinates within the learnt domain, specifically a regularly spaced grid for comparison with typical grid regularisation methods.
+Inference can be performed by querying novel coordinates within the learnt domain, here at regularly spaced grid intervals for comparison with standard grid regularisation methods.
 
 \subsection{Network architecture}
-The Coordinate MLP architecture used comprises a simple fully connected network with \(N\) layers, each with \(m\) features.
-High quality implicit represenation has been achieved in contemporary INR research with only several hidden layers, typically between 3 and 8, and these depths are used here.
-The sinusoidal activation of \parencite{sitzmann2019siren} is used and comparison can be made to Gaussian and wavelet activations.
+The Coordinate MLP architecture comprises a simple fully connected network with \(N\) hidden layers, each with \(m\) features.
+The sinusoidal activation of \parencite{sitzmann2019siren} is used. % for a baseline, and comparison is made to Gaussian and wavelet activations.
+High quality implicit represenation has been achieved in contemporary INR research with only several hidden layers, typically between 3 and 8, and \(N = 8\) is used here.
+The number of hidden features is set \(m = 256\).
 Figure \cref{fig:arch} shows the structure of the architecture.
 
-\begin{figure}
+\begin{figure}[hbt]
     \label{fig:arch}
+    \caption[Network Architecture]{The Coordinate MLP architecture used for the implicit neural represenation task.}
 \end{figure}
@@
 \subsection{Training Particulars}
+\label{sec:training}
 % Performed on an Intel i5-12400 CPU with 32 GB RAM, and an Nvidia 3060 12 GB GPU.
 
-Implicit functions are trained using coordinate-value pairs, and for low-resolution images the entire cell value and cell coordinate dataset fits within GPU memory for batch gradient descent.
-The Wolfe Creek meteorite impact crater case study survey has \SI{76420}{} sample points, with the Geoscience Australia provided grid product having a resolution of 446 \(\times{}\) 445 cells.
-This coordinate dataset easily fits into available graphics memory, and can be trained using batch gradient descent.
+Implicit functions are trained using coordinate-value pairs, and for low-resolution images the entire cell coordinate and cell value dataset fits within GPU memory for batch gradient descent.
+The Wolfe Creek meteorite impact crater case study line data has \SI{76420}{} sample points, with the Geoscience Australia provided grid product having a resolution of 446 \(\times{}\) 445 cells.
+The line coordinate dataset easily fits into available graphics memory, and can be trained using batch gradient descent.
 %However, training on large scattered aeromagnetic surveys with more than one million samples, memory becomes a constraint and mini-batch training is required.
 Training was performed on an Intel i9-10900KF workstation with an Nvidia RTX 3090 24 GB GPU\@.
-A highly accurate represenation can be learned in 1000 epochs using the Adam optimiser, for a duration of 90 seconds.
+A highly accurate represenation can be learned within 1000 epochs using the Adam optimiser, for a duration in the order of 60 seconds.
 The OneCycle learning rate scheduler \parencite{smithSuperconvergenceVeryFast2018} is used to provide fine tuning at low learning rates toward the end of training.
 
-As described in \cref{sec:pinn}, the objective function comprises \(L^2\) loss between input and predicted field values, summed with weighted Laplace's equation loss, \cref{eqn:cri}.
+As described in \cref{sec:pinn}, the objective function comprises \(L^2\) loss between the input and predicted field values.
+It does not include the Laplace loss as described above. %, summed with weighted Laplace's equation loss, \cref{eqn:cri}.
 \begin{equation}
     \label{eqn:cri}
-    \mathcal{L}_{Total} = \lVert{}u_{input} - u_{pred}\rVert{}_{2} + \beta{} \lVert{}\frac{\partial^{2}{u_{pred}}}{\partial{}\phi{}_{pred}^{2}}\rVert{}_{2}
+    \mathcal{L}_{Total} = \lVert{}u_{input} - u_{pred}\rVert{}_{2} % + \beta{} \lVert{}\frac{\partial^{2}{u_{pred}}}{\partial{}\phi{}_{pred}^{2}}\rVert{}_{2}
 \end{equation}
 
-\subsection{Differentiation}
-A naive approach would be to evaluate the implicit represenation \(u = \phi{}(x, y, z)\) at a set of regular coordinates \({(x, y, z)}_1 \dots {(x,y,z)}_n\), and use numerical differentiation methods to calculate derivatives.
-However, using Automatic Differentiation within Pytorch, the implicit represenation can be differentiated with respect to its inputs to provide gradients without being constrained by quantisation.
+\subsection{Derivative calculation}
+A naive approach to calculating gradients with the INR would be to evaluate the represenation \(u = \phi{}(x, y, z)\) at a set of regular coordinates \({(x, y, z)}_1 \dots {(x,y,z)}_n\), and use numerical differentiation to calculate derivatives.
+However, using Automatic Differentiation within Pytorch, the implicit represenation can be differentiated with respect to its inputs to provide gradients prior to being constrained by choice of quantisation.
 This is to directly sample \(\frac{\partial{u}}{\partial{\phi{}{(x,y,z)}}}\) at \({(x, y, z)}_1 \dots {(x,y,z)}_n\).
-Higher order derivatives can be also calculated using AD\@.
+Higher order derivatives can be also calculated using AD in this manner.
 

### 2023-08-26 paper3.tex
Improve figures and minor text
As sent to supervisor for rough draft.

@@
 The Nyquist wavelength inherent to the selected grid cell size during regularisation limits the high-resolution information representable by the grid.
-Because grid regularisation is one of the earliest steps in interpreting geophysical surveys, this information fails to be utilised in any subsequent task.
+Because grid regularisation is one of the earliest steps in interpreting geophysical surveys, this information fails to be utilised in most tasks.
 % Subsequent processes such as frequency filtering or directional gradients are similary constrained by the parameters of the regularisation.
@@
 
-As denoted by the \(L^2\) operator \(\lVert{}\cdot{}\rVert{}_{2}\) and weighting \(\beta{}\), this criterion additionally penalises predictions that are not close to zero.
+As denoted by the \(L^2\) operator \(\lVert{}\cdot{}\rVert{}_{2}\) and weighting \(\beta{}\), this criterion penalises predictions that are not close to zero.
 
@@
 The number of hidden features is set \(m = 256\).
-Figure \cref{fig:arch} shows the structure of the architecture.
+% Figure \cref{fig:arch} shows the structure of the architecture.
 
-\begin{figure}[hbt]
-    \label{fig:arch}
-    \caption[Network Architecture]{The Coordinate MLP architecture used for the implicit neural represenation task.}
-\end{figure}
+% \begin{figure}[hbt]
+%     \label{fig:arch}
+%     \caption[Network Architecture]{The Coordinate MLP architecture used for the implicit neural represenation task.}
+% \end{figure}
 
@@
 A highly accurate represenation can be learned within 1000 epochs using the Adam optimiser, for a duration in the order of 60 seconds.
-The OneCycle learning rate scheduler \parencite{smithSuperconvergenceVeryFast2018} is used to provide fine tuning at low learning rates toward the end of training.
+The OneCycle learning rate scheduler \parencite{smithSuperconvergenceVeryFast2018} with a maximum rate of \(3\times{}10^{-4}\) is used which provides fine tuning at low learning rates toward the end of training.
 
 As described in \cref{sec:pinn}, the objective function comprises \(L^2\) loss between the input and predicted field values.
-It does not include the Laplace loss as described above. %, summed with weighted Laplace's equation loss, \cref{eqn:cri}.
+It does not use the Laplace loss discussed above. %, summed with weighted Laplace's equation loss, \cref{eqn:cri}.
 \begin{equation}
@@
 A naive approach to calculating gradients with the INR would be to evaluate the represenation \(u = \phi{}(x, y, z)\) at a set of regular coordinates \({(x, y, z)}_1 \dots {(x,y,z)}_n\), and use numerical differentiation to calculate derivatives.
-However, using Automatic Differentiation within Pytorch, the implicit represenation can be differentiated with respect to its inputs to provide gradients prior to being constrained by choice of quantisation.
-This is to directly sample \(\frac{\partial{u}}{\partial{\phi{}{(x,y,z)}}}\) at \({(x, y, z)}_1 \dots {(x,y,z)}_n\).
+However, using Automatic Differentiation within Pytorch, the implicit represenation can be differentiated with respect to its inputs to provide gradients prior to being queried with a quantised grid.
+That is, directly sample \(\frac{\partial{u}}{\partial{\phi{}{(x,y,z)}}}\) at \({(x, y, z)}_1 \dots {(x,y,z)}_n\).
 Higher order derivatives can be also calculated using AD in this manner.
@@
 \begin{figure}[hbt]
-    \includegraphics[width=\textwidth]{fig/p3/grid_comparison.pdf}
+    \centering{}
+    \includegraphics[width=1.\linewidth]{fig/p3/grid_comparison.pdf}
     \caption[Grid prediction]{Comparison between the ground-truth grid processed by Geoscience Australia (left) and the constant level grid queried from the INR at \SI{40}{\m} (right).}
@@
 Constant level grids can be queried from the INR at any height.
-\Cref{fig:grid35} shows the case study extent queried at \SI{35}{m}.
+\Cref{fig:grid35} shows the case study extent queried at \SI{35}{\m}.
 While comparable features can still be interpreted within this level grid, the represenation learnt here fails to represent physically realistic continuation of the field.
+It is conjectured that implementing a PINN criterion such as Laplacian loss \cref{eqn:cri_laplace} would improve the performance these upward or downward extracted slices.
 
 \begin{figure}[hbt]
-    %TODO query at AWAGS height and compare GA AWAGS grid.
+    \centering{}
+    % TODO query at AWAGS height and compare GA AWAGS grid.
     % TODO check if provided grid is AWAGS or MICRO levelled - maybe grid data myself.
-    \includegraphics[width=\textwidth]{fig/p3/grid_comparison_35m.pdf}
-    \caption[Grid prediction]{A constant level grid queried from the INR at the AWAGS datum height of \SI{35}{m} (right).}
+    \includegraphics[width=1.\linewidth]{fig/p3/grid_comparison_35m.pdf}
+    \caption[Grid prediction]{A constant level grid queried from the INR at the height of \SI{35}{\m} (right).}
+    % AWAGS is 80 m, but we see nothing useful at 80m
     \label{fig:grid35}
@@
 % \begin{figure}[hbt]
-%     % \includegraphics[width=\textwidth]{fig/p3/grid_subpct.pdf}
+%     % \includegraphics[]{fig/p3/grid_subpct.pdf}
 %     \caption[Grid subsampled]{Performance of level grid prediction shown at \qty{30}{\percent} and \qty{10}{\percent} random sampling of training data.}
@@
 Using AD, derivatives can be calculated between the input spatial coordinates and the output potential field represenation.
-While the horizontal derivatives correspond well to numerical derivatives calculated on the Wolfe Creek ground truth grid (\cref{fig:hori_grad}), the vertical derivative suffers poor performance (\cref{fig:vert_grad}).
+While horizontal derivatives queried from the INR correspond well to numerical derivatives calculated on the 40 m level grid (\cref{fig:hori_grad}), the vertical derivative suffers poor performance (\cref{fig:vert_grad}).
 This correlates with the poor continuation performance of model when predicting level grids several meters or more beyond the nominal sample height.
-This is inrepreted as the model learning a poor represenation of the vertical component of the potential field.
+This is interpreted as the model learning a poor represenation of the vertical component of the potential field.
 
 \begin{figure}[hbt]
-    % \includegraphics[width=\textwidth]{fig/p3/hori_grad.pdf}
-    \caption[Horizontal derivatives]{AD calculated horizontal derivatives of the INR\@. Left: Northing derivative, right: easting derivative}
+    \centering
+    \includegraphics[width=1.\linewidth]{fig/p3/dh_comparison.pdf}
+    \caption[Horizontal derivatives]{AD (left column) and numerical (middle column) horizontal derivatives of the INR\@. Residuals are shown in the right column.}
     \label{fig:hori_grad}
@@
 \begin{figure}[hbt]
-    % \includegraphics[width=\textwidth]{fig/p3/vert_grad.pdf}
-    \caption[Vertical derivative]{AD calculated vertical derivative of the INR.}
+    \centering
+    \includegraphics[width=1.\linewidth]{fig/p3/dv_comparison.pdf}
+    \caption[Vertical derivative]{AD (left) and numerical (right) vertical derivatives of the INR\@.}
     \label{fig:vert_grad}
@@
 
-Using the implicit representation, a selection of common geophysical filters are calculated prior to quantisation.
+% Using the implicit representation, a selection of common geophysical filters are calculated prior to quantisation.
 
-\begin{enumerate}
-    \item ASIG
-    \item tilt?
-    \item idk?
-\end{enumerate}
+% \begin{enumerate}
+%     \item ASIG
+%     \item tilt?
+%     \item idk?
+% \end{enumerate}
 
 \section{Discussion}
-The implicit represenation has strong representive capacity for the horizontal components of the potential field, generating level grids which are accurate against the ground truth grid.
+The implicit represenation has strong representative capacity for the horizontal components of the potential field, allowing extraction of level grids which are accurate against the ground truth grid.
 Level grids can be generated at any height, with best performance achieved near the realised nominal survey altitude.
@@
 
-The case study survey presented is very small compared to typical regional aeromagnetic surveys.
-A demonstration of the method on a large aeromagnetic survey, requiring minibatch training, is included in \cref{app:menzies}.
-Training of this representation follows the parameters outlined in \cref{sec:training}, which were optimised for the Wolfe Creek case study, with the addition of a shuffled minibatch size of \SI{1024000}.
-Attempts to train the CMLP with small batch sizes did not converge.%, reflecting the non-convergance result found for training on very large subsampling factors of the line dataset.
+% The case study survey presented is very small compared to typical regional aeromagnetic surveys.
+% A demonstration of the method on a large aeromagnetic survey, requiring minibatch training, is included in \cref{app:menzies}.
+% Training of this representation follows the parameters outlined in \cref{sec:training}, which were optimised for the Wolfe Creek case study, with the addition of a shuffled minibatch size of \SI{1024000}\@.
+% Attempts to train the CMLP with small batch sizes did not converge.%, reflecting the non-convergance result found for training on very large subsampling factors of the line dataset.
 
 Implicit neural representation is a rapidly evolving field of research, and draws on contemporary deep learning improvements within related fields.
-In addition to improving the high-frequency learning capacity, physics informed loss functions promise higher quality vertical continuation performance. 
+In addition to improving the high-frequency learning capacity, physics informed loss functions may allow higher quality vertical continuation performance. 
 The current method could trivially include additional target dimensions, which would allow representation learning of vector fields \(\mathbb{R}^{3}\) in three dimensions \(\mathbb{R}^{3}\).
-This has potential application in tensor fields and associated predictive tasks.
-These remain for future work.
+This has potential application in tensor fields and associated predictive tasks, and these remain for future work.
 
@@
 Resolution in the represenation is limited by network capacity, rather than initial grid cell size selection during regularisation.
+Level grids can be extracted from these represenations, emerging as a novel method for regularising scatter geophysical sample data.
 Gradients and spatial filters can be caluclated using the full resolution of the learnt represenation, and gridded \emph{a posteri} of gradient or filter calculation.
@@
 
+% \section{Appendix A}
+% \label{app:menzies} %TODO format as "Appendix"
+% The Menzies South ... Pxxxx survey contains xxx sample points across yyyy line kilometres, and was flown at a nominal terrain clearance of zz m.
+% While a high-quality result is attainable using batch gradient descent on a subset of the survey points, minibatch gradient descent is demonstrated for the CMLP used to learn the full survey INR\@.
+
+\begin{figure}[hbt]
+    % \includegraphics[width=\textwidth]{fig/p3/menzies.pdf}
+    \caption[Menzies INR]{Level grid represenation using minibatch gradient descent.}
+    \label{fig:vert_grad}
+\end{figure}
+
 \end{document}

### 2023-08-29 paper3.tex
Address TH feedback

@@
 \begin{abstract}
-    The recent use of spatial coordinate features in multilayer perceptron (MLP) neural networks provides exigient opportunities for potential field geophysics.
+    The recent use of spatial coordinate features in multilayer perceptron (MLP) neural networks provides opportunities for novel applications in potential field geophysics.
     So called coordinate MLP networks allow for implicit learning of potential field samples as a function of their recorded sample locations.
@@
 
-Encoding a potential field into a neural network can be performed using the recent technique of implicit neural represenation.
+Encoding a potential field into a neural network can be performed using the recent technique of implicit neural representation.
 Implicit neural representation (INR) is the task of representing a signal as a function of its coordinates.
@@
 The proposed method leverages recent approaches in the literature to learn a continuous volume of potential field geophysics, using a novel combination of physics-informed networks and implicit neural representation.
-This implicit represenation is used to generate levelled 2D grids directly from scattered sample data, as well as calculate gradients and further filters.
+This implicit representation is used to generate levelled 2D grids directly from scattered sample data, as well as calculate gradients and further filters.
 These are compared against industry standard gridding methods and numerical filters.
@@
 \label{sec:geo_physics}
-Potential fields in geophysics are vector fields, but are typically sampled as a scalar field in one direction.
-A vector field requires three orthogonal components at each coordinate, while a scalar field can be parameterised with a single component \parencite{blakelyPotentialTheoryGravity1996}.
-Therefore, a potential field survey can be parameterised as
+Magnetic and gravitational fields in geophysics are conservative vector fields, but are typically sampled as a scalar potential field in a single direction.
+Representing a vector field requires three orthogonal components at each spatial coordinate, while a scalar field can be parameterised with a single component \parencite{blakelyPotentialTheoryGravity1996}.
+A potential field survey can be parameterised as
 \begin{equation}
@@
 
-Seminal work by \parencite{mildenhallNeRFRepresentingScenes2020} demonstrated implicit neural represenation of volume density and colour dimensions, learnt from five dimensions of radiance and spatial coordinates.
-However, it was not until the use of periodic activation functions \parencite{sitzmann2019siren} that implicit representation with CMLP networks could adequately recreate high frequency signals.
-Periodic activation functions differ from non-linear activations such as ReLU by comprising the neuron with a function which repeats periodically.
-Such functions include sinusoids \parencite{sitzmann2019siren}, Gaussians \parencite{ramasinghePeriodicityUnifyingFramework2022}, and most recently, wavelets \parencite{saragadamWIREWaveletImplicit2023}.
-Work by \parencite{ramasinghePeriodicityUnifyingFramework2022} revealed that it is the magnitude of the first and second derivatives of the activation that enhance high-frequency capacity, rather than periodicity.
-Periodic activations are important in enabling continuous differentiation throughout the depth of the network.
+Seminal work by \parencite{mildenhallNeRFRepresentingScenes2020} demonstrated implicit neural representation of volume density and colour dimensions, learnt from five dimensions of radiance and spatial coordinates.
+However, it was not until the use of periodic activation functions such as the sinusoid \parencite{sitzmann2019siren} that implicit representation with CMLP networks could adequately recreate high frequency signals.
+Periodic activation functions differ from non-linear activations such as ReLU by comprising the neuron with a function which repeats periodically, which allows for continuous differentiation throughout the depth of the network.
+Work by \parencite{ramasinghePeriodicityUnifyingFramework2022} revealed that it is the magnitude of the first and second derivatives of the activation that enhance high-frequency capacity, rather than periodicity, leading to Gaussian \parencite{ramasinghePeriodicityUnifyingFramework2022} and wavelet \parencite{saragadamWIREWaveletImplicit2023} activation functions for CMLP\@.
 %TODO Confirm re: blakely % ReLU has constant second derivative of zero, rendering it incapable of representing a harmonic function such as a potential field.
 
-Coordinate MLPs can be used for a variety of computer vision tasks, including three-dimensional point cloud represenation \parencite{qiPointNetDeepHierarchical2017}, and two-dimensional natural image representation tasks such as super-resolution and infilling \parencite{leeLocalTextureEstimator2022,chenLearningContinuousImage2021}.
+Coordinate MLPs can be used for a variety of computer vision tasks, including three-dimensional point cloud representation \parencite{qiPointNetDeepHierarchical2017}, and two-dimensional natural image representation tasks such as super-resolution and infilling \parencite{leeLocalTextureEstimator2022,chenLearningContinuousImage2021}.
 Resolution in these tasks is not limited by quantisation of the representation, but rather the capacity of the network architecture used.
@@
 While this means the latent spatial domain may be compressed relative to each other axis, the inverse normalisation process returns proportionality between axes.
-Magnetic field data are min-max normalised across the global values within the survey, and NaN values in any dimension are dropped from the training data.
+The case study data do not span a large or magnetically varying geological extent, hence it is sufficient to use simple min-max normalisation for the magnetic field data within the global extent of the survey samples, here between -1 and 1.
+If extensive or complexly varying magnetic provinces were present within the dataset, a normalisation method more robust to outliers may be required.
 
@@
 \subsection{Network architecture}
-The Coordinate MLP architecture comprises a simple fully connected network with \(N\) hidden layers, each with \(m\) features.
-The sinusoidal activation of \parencite{sitzmann2019siren} is used. % for a baseline, and comparison is made to Gaussian and wavelet activations.
-High quality implicit represenation has been achieved in contemporary INR research with only several hidden layers, typically between 3 and 8, and \(N = 8\) is used here.
-The number of hidden features is set \(m = 256\).
+The Coordinate MLP architecture comprises a simple fully connected network with \(N\) hidden layers, each with \(m\) neurons.
+The sinusoidal activation of \cite{sitzmann2019siren} is used. % for a baseline, and comparison is made to Gaussian and wavelet activations.
+High quality implicit representation has been achieved in contemporary INR research with only several hidden layers, typically between 3 and 8, with \(N = 8\) is used here.
+The number of neurons per layer is set \(m = 256\).
 % Figure \cref{fig:arch} shows the structure of the architecture.
@@
 %     \label{fig:arch}
-%     \caption[Network Architecture]{The Coordinate MLP architecture used for the implicit neural represenation task.}
+%     \caption[Network Architecture]{The Coordinate MLP architecture used for the implicit neural representation task.}
 % \end{figure}
@@
 Training was performed on an Intel i9-10900KF workstation with an Nvidia RTX 3090 24 GB GPU\@.
-A highly accurate represenation can be learned within 1000 epochs using the Adam optimiser, for a duration in the order of 60 seconds.
-The OneCycle learning rate scheduler \parencite{smithSuperconvergenceVeryFast2018} with a maximum rate of \(3\times{}10^{-4}\) is used which provides fine tuning at low learning rates toward the end of training.
+A highly accurate representation can be learned within 1000 epochs using the Adam optimiser, for a duration in the order of 60 seconds.
+The OneCycle learning rate scheduler \parencite{smithSuperconvergenceVeryFast2018} with a maximum rate of \(3\times{}10^{-4}\) is used to provide fine tuning at low learning rates toward the end of training.
+Convergence of the network is shown in \cref{fig:convergence}
+
+\begin{figure}[hbt]
+    \centering{}
+    \includegraphics[width=0.5\linewidth]{fig/p3/loss_plot.pdf}
+    \caption[Training convergence]{Train and validation loss for the duration of the experiment.}
+    \label{fig:convergence}
+\end{figure}
 
 As described in \cref{sec:pinn}, the objective function comprises \(L^2\) loss between the input and predicted field values.
-It does not use the Laplace loss discussed above. %, summed with weighted Laplace's equation loss, \cref{eqn:cri}.
+It does not use the Laplace loss discussed in \cref{sec:pinn}, which fails to converge. %, summed with weighted Laplace's equation loss, \cref{eqn:cri}.
 \begin{equation}
@@
 \subsection{Derivative calculation}
-A naive approach to calculating gradients with the INR would be to evaluate the represenation \(u = \phi{}(x, y, z)\) at a set of regular coordinates \({(x, y, z)}_1 \dots {(x,y,z)}_n\), and use numerical differentiation to calculate derivatives.
-However, using Automatic Differentiation within Pytorch, the implicit represenation can be differentiated with respect to its inputs to provide gradients prior to being queried with a quantised grid.
-That is, directly sample \(\frac{\partial{u}}{\partial{\phi{}{(x,y,z)}}}\) at \({(x, y, z)}_1 \dots {(x,y,z)}_n\).
+A naive approach to calculating gradients with the INR would be to evaluate the representation \(\phi{}_{(x, y, z)}\) at a set of regular coordinates \({(x, y, z)}_1 \dots {(x,y,z)}_n\), and use numerical differentiation to calculate derivatives.
+However, using Automatic Differentiation with Pytorch, the implicit representation can be differentiated with respect to its inputs to provide gradients, prior to being queried at the nodes of a quantised grid.
+That is, directly sample \(\nabla{}\phi{}_{(x,y,z)}\) at \({(x, y, z)}_1 \dots {(x,y,z)}_n\).
 Higher order derivatives can be also calculated using AD in this manner.
@@
 \subsection{Implicit gridding}
-Querying a learnt implicit neural represenation (INR) using a regularly spaced \(x,y\) grid at a specific \(z\) height is a novel method for gridding geophysical potential field surveys.
+Querying a learnt implicit neural representation (INR) using a regularly spaced \(x,y\) grid at a specific \(z\) height is a novel method for gridding geophysical potential field surveys.
 \Cref{fig:grid} shows the INR queried at \(z=\SI{40}{\meter}\), which is the nominal terrain clearance of the survey.
 Notably, the cell size can be selected by fining or coarsening the \(x,y\) spacing, including variable or anisotropic cell sizes.
-For natural images, using finer cell sizes accomplishes the computer vision task of super-resolution.
-However, for the potential field representation task, no additional high-frequency information is predicted by the MLP network and resolution remains limited by the survey sample spacing and neural network capacity.
+Contemporary super-resolution research can leverage this continual representation as a framework for high quality arbitrary scale factor high-frequency component prediciton \parencite[e.g][]{chenLearningContinuousImage2021}.
+However, the potential field representation task here does not attempt to predict additional high-frequency information and resolution remains limited by the survey sample spacing and neural network capacity.
 
@@
     \centering{}
-    \includegraphics[width=1.\linewidth]{fig/p3/grid_comparison.pdf}
+    \includegraphics[width=1.0\linewidth]{fig/p3/grid_comparison_40m.pdf}
     \caption[Grid prediction]{Comparison between the ground-truth grid processed by Geoscience Australia (left) and the constant level grid queried from the INR at \SI{40}{\m} (right).}
@@
 \Cref{fig:grid35} shows the case study extent queried at \SI{35}{\m}.
-While comparable features can still be interpreted within this level grid, the represenation learnt here fails to represent physically realistic continuation of the field.
+While comparable features can still be interpreted within this level grid, the representation learnt here fails to represent physically realistic continuation of the field.
 It is conjectured that implementing a PINN criterion such as Laplacian loss \cref{eqn:cri_laplace} would improve the performance these upward or downward extracted slices.
@@
     % TODO check if provided grid is AWAGS or MICRO levelled - maybe grid data myself.
-    \includegraphics[width=1.\linewidth]{fig/p3/grid_comparison_35m.pdf}
+    \includegraphics[width=1.0\linewidth]{fig/p3/grid_comparison_35m.pdf}
     \caption[Grid prediction]{A constant level grid queried from the INR at the height of \SI{35}{\m} (right).}
@@
 \subsection{Spatial derivatives and filters}
-Using AD, derivatives can be calculated between the input spatial coordinates and the output potential field represenation.
+Using AD, derivatives can be calculated between the input spatial coordinates and the output potential field representation.
 While horizontal derivatives queried from the INR correspond well to numerical derivatives calculated on the 40 m level grid (\cref{fig:hori_grad}), the vertical derivative suffers poor performance (\cref{fig:vert_grad}).
 This correlates with the poor continuation performance of model when predicting level grids several meters or more beyond the nominal sample height.
-This is interpreted as the model learning a poor represenation of the vertical component of the potential field.
+This is interpreted as the model learning a poor representation of the vertical component of the potential field.
 
 \begin{figure}[hbt]
-    \centering
-    \includegraphics[width=1.\linewidth]{fig/p3/dh_comparison.pdf}
+    \centering{}
+    \includegraphics[width=1.0\linewidth]{fig/p3/dh_comparison.pdf}
     \caption[Horizontal derivatives]{AD (left column) and numerical (middle column) horizontal derivatives of the INR\@. Residuals are shown in the right column.}
@@
 \begin{figure}[hbt]
-    \centering
-    \includegraphics[width=1.\linewidth]{fig/p3/dv_comparison.pdf}
+    \centering{}
+    \includegraphics[width=1.0\linewidth]{fig/p3/dv_comparison.pdf}
     \caption[Vertical derivative]{AD (left) and numerical (right) vertical derivatives of the INR\@.}
@@
 \section{Discussion}
-The implicit represenation has strong representative capacity for the horizontal components of the potential field, allowing extraction of level grids which are accurate against the ground truth grid.
+The implicit representation has strong representative capacity for the horizontal components of the potential field, allowing extraction of level grids which are accurate against the ground truth grid.
 Level grids can be generated at any height, with best performance achieved near the realised nominal survey altitude.
@@
 % Training of this representation follows the parameters outlined in \cref{sec:training}, which were optimised for the Wolfe Creek case study, with the addition of a shuffled minibatch size of \SI{1024000}\@.
-% Attempts to train the CMLP with small batch sizes did not converge.%, reflecting the non-convergance result found for training on very large subsampling factors of the line dataset.
+% Attempts to train the CMLP with small batch sizes did not converge.%, reflecting the non-convergence result found for training on very large subsampling factors of the line dataset.
 
@@
 \section{Conclusions}
-High-resolution implicit neural represenation of potential field geophysics surveys is achieved with the use of coordinate MLP neural networks.
-Resolution in the represenation is limited by network capacity, rather than initial grid cell size selection during regularisation.
-Level grids can be extracted from these represenations, emerging as a novel method for regularising scatter geophysical sample data.
-Gradients and spatial filters can be caluclated using the full resolution of the learnt represenation, and gridded \emph{a posteri} of gradient or filter calculation.
+High-resolution implicit neural representation of potential field geophysics surveys is achieved with the use of coordinate MLP neural networks.
+Resolution in the representation is limited by network capacity, rather than initial grid cell size selection during regularisation.
+Level grids can be extracted from these representations, emerging as a novel method for regularising scatter geophysical sample data.
+Gradients and spatial filters can be caluclated using the full resolution of the learnt representation, and gridded \emph{a posteri} of gradient or filter calculation.
 
@@
 
-\begin{figure}[hbt]
-    % \includegraphics[width=\textwidth]{fig/p3/menzies.pdf}
-    \caption[Menzies INR]{Level grid represenation using minibatch gradient descent.}
-    \label{fig:vert_grad}
-\end{figure}
+% \begin{figure}[hbt]
+%     % \includegraphics[width=\textwidth]{fig/p3/menzies.pdf}
+%     \caption[Menzies INR]{Level grid representation using minibatch gradient descent.}
+%     \label{fig:vert_grad}
+% \end{figure}
 

### 2023-09-11 paper3.tex
Update to address supervisor feedback

@@
 \setcounter{chapter}{1}
-\author{\and{Luke Thomas Smith} \and{Tom Horrocks} \and{Eun-Jung Holden} \and{Daniel Wedge} \and{Naveed Akhtar}}
-\title{Physics-informed Implicit Neural Representation for Potential Field Geophysics}
+\author{{Luke Thomas Smith} \and{Tom Horrocks} \and{Eun-Jung Holden} \and{Daniel Wedge} \and{Naveed Akhtar}}
+\title{Implicit Neural Representation for Potential Field Geophysics }
 \date{\today}
@@
     The recent use of spatial coordinate features in multilayer perceptron (MLP) neural networks provides opportunities for novel applications in potential field geophysics.
-    So called coordinate MLP networks allow for implicit learning of potential field samples as a function of their recorded sample locations.
+    So-called coordinate MLP networks allow for learning a representative function of potential fields from their surveyed samples and locations.
     Using this new paradigm of encoding spatial information within a neural network enables new methods for working with potential field survey data.
-    We demonstrate the quality of the learnt implicit potential field function by encoding real airborne geophysical survey line data, and predicting constant level grids of arbitrary cell size.
-    We further demonstrate the potential for processing the learnt function in the continuous domain using automatic differentiation, with the same framework used to train the neural network.
-    For example, directional gradients and subsequent filters are calculated prior grid quantisation, and therefore without the associated loss of high-resolution content imposed by gridding.
-    The training process requires only the sample coordinates and recorded potential field for a single survey extent, and can be applied to various geophysical techniqes including magnetics and gravity.
-%, as well as radiometric or other grids.
+
+    We present a novel application of implicit neural representation to potential fields, demonstrate the quality of the learnt implicit function by encoding real airborne geophysical survey line data, predict constant level grids, and compare the result to grid data processed with a traditional workflow.
+    We further demonstrate processing the learnt function directly in the continuous domain using automatic differentiation, with the same framework used to train the neural network.
+    For example, directional gradients are calculated in the continuous domain prior to grid quantisation, and therefore without the associated loss of high-resolution content imposed by gridding.
+    The training process requires only the sample coordinates and recorded potential field for a single survey extent and can be applied to various geophysical techniques including magnetics and gravity.
 \end{abstract}
@@
 \section{Introduction}
-Geophysical potential fields are continuous functions in three dimensions, and are of importance to geoscience and mineral exploration.
-When surveying these fields for exploration geophysics, sample locations are scattered in x, y, and z, despite best efforts to conform to a regular grid or line sample structure.
+Geophysical potential fields are routinely collected and used to assist the understanding of the subsurface for geoscience and mineral exploration.
+When surveying these fields, which are continuous functions in three dimensions, sample locations are scattered in x, y, and z, despite best efforts to conform to a regular grid or line sample regime.
 These scattered data are typically regularised to a quantised grid, which reduces high frequency information and gives rise to spurious artefacts that are a product of the gridding process, not the surveyed field.
-If a representation of the potential field could instead be encoded within a neural network, it is possible that high frequency information would be preserved in a continuous domain.
-Within the continuous representation, grid resolution is not constrained by an initial cell size selection, and further processing and filters can be calculated analytically in the continuous spatial domain.
-This allows the use of all available sample information in the calculation of filters, and reduces the manual intervention required during the gridding process.
 
-Encoding a potential field into a neural network can be performed using the recent technique of implicit neural representation.
-Implicit neural representation (INR) is the task of representing a signal as a function of its coordinates.
-Networks designed to learn such functions are known as coordinate multilayer perceptrons, or coordinate MLPs.
-By parameterising the neural function in coordinate space, novel values of the function can be queried at arbitrary coordinates within the learnt continuous spatial domain.
-Coordinate MLPs have recently benefit from high frequency representation improvements through the use of periodic activations.
-Periodic activations such as sinusoids are continuously differentiable through the depth of the network, supporting high quality learning of implicit functions.
+Neural networks can be considered as universal function approximators.
+The recent technique of deep learning implicit neural representation (INR) \parencite{mildenhallNeRFRepresentingScenes2020} represents a signal as a function of its coordinates, built on a network architecture known as a coordinate multilayer perceptron (CMLP) (see \cite{ramasinghePeriodicityUnifyingFramework2022} for a recent introduction).
+By parameterising the function in coordinate space, novel values of the function can be queried at arbitrary coordinates within the learnt continuous spatial domain.
+Recent advances in CMLPs by using periodic activations such as sinusoids have demonstrated that high frequency information can be modelled by CMLP networks, while being continuously differentiable through the depth of the network to facilitate rapid training.
 
-Furthermore, these cordinate MLP networks can be constrained to obey geophysical laws, using physics-informed neural network regularisation.
-Imposing restrictions such as Laplace's equation on the network reduces the model search space, stabilising and speeding up training and predicting solutions that obey these laws.
+We present a novel method of encoding a representation of a geophysical potential field using INR\@.
+This method is used to demonstrate a novel method of creating level grids from scattered aeromagnetic data.
+Due to using a continuous coordinate representation, there is no dependency on grid quantisation from an initial cell size selection.
+It also provides for further processing that can be calculated analytically in the continuous spatial domain, allowing the use of all available sample information in these calculations.
 
-The proposed method leverages recent approaches in the literature to learn a continuous volume of potential field geophysics, using a novel combination of physics-informed networks and implicit neural representation.
-This implicit representation is used to generate levelled 2D grids directly from scattered sample data, as well as calculate gradients and further filters.
-These are compared against industry standard gridding methods and numerical filters.
+For the task of level grid prediction, the PSNR similarity between a case study reference grid and the proposed method is \SI{40}{\dB}.
+Additionally, directional derivatives of the implicit representation calculated numerically and using automatic differentiation are shown, with average residuals of \SI{0.4} and \SI{0.8}{nT/m} for the easting and northing derivatives respectively, albeit vertical derivative performance remains limited.
+
+The method is still in its infancy, but stands to benefit from ongoing research in the highly active fields of deep learning and INR\@.
 
@@
 The resolvable detail within the sampled field is a function of the sampling density, and the distance from the source.
-% It is common to define a nominally regular drape surface with these parameters in mind, while respecting the cost of acquisition.
 To enable digital processing and storage of the sample data following acquisition, the scattered points are regularised to a quantised grid.
-The Nyquist wavelength inherent to the selected grid cell size during regularisation limits the high-resolution information representable by the grid.
-Because grid regularisation is one of the earliest steps in interpreting geophysical surveys, this information fails to be utilised in most tasks.
+The Nyquist wavelength inherent to the selected grid cell size during initial regularisation limits the high-resolution information representable by the grid.
+Because grid regularisation is one of the earliest steps in interpreting geophysical surveys, this information fails to be utilised in most subsequent processing and interpretation tasks.
 % Subsequent processes such as frequency filtering or directional gradients are similary constrained by the parameters of the regularisation.
@@
 \label{sec:geo_physics}
-Magnetic and gravitational fields in geophysics are conservative vector fields, but are typically sampled as a scalar potential field in a single direction.
+Magnetic and gravitational fields in geophysics are conservative vector fields but are typically sampled as a scalar potential field in a single direction.
 Representing a vector field requires three orthogonal components at each spatial coordinate, while a scalar field can be parameterised with a single component \parencite{blakelyPotentialTheoryGravity1996}.
-A potential field survey can be parameterised as
+A potential field survey can be parameterised as \cref{eqn:potential}.
 \begin{equation}
-    u = \phi\left(x,y,z\right)
+    \label{eqn:potential}
+    \phi\left(x,y,z\right)
 \end{equation}
-
-Potential fields in an airborne sampling context are constrained by a number of physical laws, including \emph{Laplace's equation},
-\[
-    \nabla^2 \phi = 0
-\]
-In three dimensions \( \phi\left(x,y,z\right) \):
-\begin{equation}
-    \label{eqn:Laplace}
-    \frac{\partial{}^2\phi}{\partial{}x^2} + \frac{\partial{}^2\phi}{\partial{}y^2} + \frac{\partial{}^2\phi}{\partial{}z^2} = 0
-\end{equation}
-%TODO Confirm logic here: % If Laplace's equation:\( \nabla^2 \phi = 0 \) is satisfied, it is harmonic, and has continuous single valued first derivatives, and has second derivatives.
-% This indicates the function lacks curvature.
-
-% Blakely:
-% A force field \(F\) is the gradient (or negative gradient) of the potential energy.
-% \( F = \nabla\phi \) for the gravity potential, \(F = - \nabla \phi\) for the Magnetic potential.
-% \( \phi(x,y,z) = constant \) is an equipotential surface.
-
-% Numerical methods for potential field continuation are unstable, recognised in the geophysical community by solution divergence and noise in predictions.
 
@@
 \label{sec:inr}
-Multilayer perceptron (MLP) networks are fully connected networks, which have been ubiquitous in machine learning for several decades.
+CMLP networks are fully connected networks, which have been ubiquitous in machine learning for several decades.
 An MLP comprises a sequence of layers of neurons, densely connected to all neurons in each adjacent layer.
@@
 
-A classic example MLP is an input vector of image pixel intensities \(u\), and an output vector of class labels \(l\). %, scaled by a function that transforms the output to a class probability.
+A classic example of an MLP is using an input vector of image pixel intensities \(u\), and an output vector of class labels \(l\).
 Training this example network with a large number of different images with class labels produces a model capable of predicting the class of novel input image vectors.
-A Coordinate MLP (CMLP) instead takes an input of explicitly stated pixel coordinates \((x,y)\), and an output vector of image pixel intensities \(u\) at those coordinates.
-Training the CMLP requires a set of input coordinates and intensities from a single image, and results in a model capable of predicting the intensity of any arbitrary continuous coordinate within the input domain.
-Both tasks may use similar images and an MLP network structure with the same \(n\) hidden layers and \(m\) hidden features, but the use of coordinates as inputs and intensities as outputs changes the predictive task.
-Coordinate MLP networks for predicting scalar fields are a class of neural networks \(f\) which train \(u = f(x,y,z)\), with \(u\in\mathbb{R}^1\) and \((x,y,z)\in\mathbb{R}^3\).
+A CMLP for representing images instead takes an input of explicitly stated pixel coordinates \((x,y)\), and an output vector of image pixel intensities \(u\) at those coordinates.
+Thus training of a CMLP network requires a set of input coordinates and intensities from a single image, and results in a model capable of predicting the intensity of any arbitrary continuous coordinate within the input domain.
+Both tasks may use similar images and an MLP network structure with the same \(n\) hidden layers and \(m\) features, but the use of coordinates as inputs and intensities as outputs changes the predictive task.
+CMLP networks for predicting 3D scalar fields are a class of neural networks \(f\) which train \(u = f(x,y,z)\), with \(u\in\mathbb{R}^1\) and \((x,y,z)\in\mathbb{R}^3\).
 
-Seminal work by \parencite{mildenhallNeRFRepresentingScenes2020} demonstrated implicit neural representation of volume density and colour dimensions, learnt from five dimensions of radiance and spatial coordinates.
-However, it was not until the use of periodic activation functions such as the sinusoid \parencite{sitzmann2019siren} that implicit representation with CMLP networks could adequately recreate high frequency signals.
-Periodic activation functions differ from non-linear activations such as ReLU by comprising the neuron with a function which repeats periodically, which allows for continuous differentiation throughout the depth of the network.
-Work by \parencite{ramasinghePeriodicityUnifyingFramework2022} revealed that it is the magnitude of the first and second derivatives of the activation that enhance high-frequency capacity, rather than periodicity, leading to Gaussian \parencite{ramasinghePeriodicityUnifyingFramework2022} and wavelet \parencite{saragadamWIREWaveletImplicit2023} activation functions for CMLP\@.
-%TODO Confirm re: blakely % ReLU has constant second derivative of zero, rendering it incapable of representing a harmonic function such as a potential field.
+Seminal work by \cite{mildenhallNeRFRepresentingScenes2020} demonstrated INR of volume density and colour radiance, learnt from five dimensions of spatial coordinates and orientation.
+Their approach uses positional encoding to improve the learning capacity of high-frequency content, addressing the issue of spectral bias in deep learning \parencite{rahamanSpectralBiasNeural2019}.
+When replacing positional encoding and the ReLU activation with periodic activation functions such as the sinusoid \parencite{sitzmann2019siren} the high frequency representation of CMLP networks is significantly enhanced.
+Periodic activation functions differ from typical non-linear activations by comprising the neuron with a function that repeats periodically, which allows for continuous differentiation throughout the depth of the network.
+Work by \cite{ramasinghePeriodicityUnifyingFramework2022} revealed that it is the magnitude of the first and second derivatives of the activation that enhance high-frequency representation learning capacity, rather than periodicity, leading to Gaussian \parencite{ramasinghePeriodicityUnifyingFramework2022} and wavelet \parencite{saragadamWIREWaveletImplicit2023} activation functions for CMLP\@.
 
-Coordinate MLPs can be used for a variety of computer vision tasks, including three-dimensional point cloud representation \parencite{qiPointNetDeepHierarchical2017}, and two-dimensional natural image representation tasks such as super-resolution and infilling \parencite{leeLocalTextureEstimator2022,chenLearningContinuousImage2021}.
+CMLPs can be used for a variety of computer vision tasks, including three-dimensional point cloud representation \parencite{qiPointNetDeepHierarchical2017}, and two-dimensional natural image representation tasks such as super-resolution and infilling \parencite{leeLocalTextureEstimator2022, chenLearningContinuousImage2021}.
 Resolution in these tasks is not limited by quantisation of the representation, but rather the capacity of the network architecture used.
-Increasing this capacity is currently the subject of very high interest in the machine learning research community, for example by leveraging new activation functions \parencite{saragadamWIREWaveletImplicit2023}, transforming the input space \parencite[e.g.][]{benbarkaSeeingImplicitNeural2022}, or using additional constraints on the search space such as physics-informed neural networks \parencite{raissiPhysicsinformedNeuralNetworks2019}.
+Increasing this capacity is currently the subject of very high interest in the machine learning research community, for example by leveraging new activation functions \parencite{saragadamWIREWaveletImplicit2023}, transforming the input space \parencite[e.g.][]{benbarkaSeeingImplicitNeural2022} or using additional constraints on the search space such as physics-informed neural networks \parencite{raissiPhysicsinformedNeuralNetworks2019}.
 
-\subsection{Physics-informed neural networks}
-\label{sec:pinn}
-Physics-informed neural networks (PINNs) recognise that if the inputs to a neural network are samples of a function which follows some physical law, outputs from the model should similarly be constrained by that law.
-By regularising the network with an objective function which penalises solutions that don't fit the partial differential equations describing the law, it is possible to vastly reduce the physically valid solution search space.
-Examples of physics-informed constraints include enforcing initial or boundary conditions, or adherence to known properties of the modelled signal.
-As described in \cref{sec:geo_physics}, potential fields in geophysics obey \emph{Laplace's equation}, that the sum of partial second derivates is 0.
-Because CMLP networks with periodic activations are continuously differentiable, it is possible to enforce this constrain as an element of the overall loss function within the network.
-In addition to \(L^2\) (Mean Square Error) loss between the input and predicted coordinate values, a geophysics informed network could include a Laplace criterion \cref*{eqn:cri_laplace}.
+CMLP networks for INR can be compared to compressed sensing \parencite{candesIntroductionCompressiveSampling2008} for its ability to recover accurate grids from sparsely sampled geophysics samples.
+While recovery of potential field grids using a compressed sensing approach is often framed as a numerical optimisation problems \parencite[e.g.][]{yangAirborneGravimetryData2015,xuGravityAnomalyReconstruction2019}, these are not equivalent to modern deep learning approaches.
+Compressed sensing relies on the theory that a signal has a sparse representation in some transform domain, and a deeper exploration of the comparison between INR and compressed sensing remains to be performed.
 
-\begin{equation}
-    \label{eqn:cri_laplace}
-    \mathcal{L}_{PDE} = \beta{}\lVert{}\frac{\partial{}^2\phi}{\partial{}x^2} + \frac{\partial{}^2\phi}{\partial{}y^2} + \frac{\partial{}^2\phi}{\partial{}z^2}\rVert{}_{2}
-\end{equation}
+\section{Automatic Differentiation}
+Automatic differentiation (AD) refers to one of several methods for computing derivatives, specifically to the method of accumulating derivatives during function evaluation \parencite{baydinAutomaticDifferentiationMachine2018}.
+This method underpins modern machine learning frameworks such as Pytorch \parencite{paszkePyTorchImperativeStyle2019}, which is the framework used to construct the network architecture and perform training in this work.
+In these frameworks, training is performed by evaluating a set of inputs using the current model weight parameters during a forward pass, while accumulating the partial derivatives of the result with respect to those parameters, to navigate an objective (loss) function using those gradients.
+These gradients inform weight updates in the direction of the negative gradient, toward a minimum in the objective function.
+However, automatic differentiation can also evaluate the derivatives of the network output with respect to the inputs, using the same high-performance AD framework.
+This can directly provide the partial derivatives of the potential field \(\frac{\partial\phi{}}{\partial x}, \frac{\partial \phi{}}{\partial y}, \frac{\partial \phi{}}{\partial z}\) with respect to its coordinates, as well as higher order derivatives, and without first requiring gridding.
 
-As denoted by the \(L^2\) operator \(\lVert{}\cdot{}\rVert{}_{2}\) and weighting \(\beta{}\), this criterion penalises predictions that are not close to zero.
+\subsection{Overview of the proposed method}
+\label{sec:overview}
+The proposed method leverages recent approaches in the literature to learn a continuous three-dimensional representation of potential field geophysics extents, using INR\@.
+This implicit representation is used to generate two-dimensional levelled grids directly from scattered sample data, by querying the representation with regularly spaced grid nodes at a constant level.
+Partial derivatives can be calculated on the representation itself, remaining in the continuous coordinate domain.
+These are compared against a case study reference grid from Geoscience Australia, with gradients from numerical derivative calculation.
+An overview diagram is presented in \cref{fig:overview}.
 
-\Textcite{sethiHardEnforcementPhysicsinformed2023} demonstrate that this regularisation does not have to be implemented as a loss function, but instead can be a hard constraint embedded within the network.
-This hard constraint takes the form of a function, which satisfies the \emph{a priori} laws, applied to the output of the network prior PDE and regularisation.
-Another approach \parencite{liImplicitStochasticGradient2023} replaces the ubiquitous stochastic gradient descent optimiser \emph{Adam} with an implicit stochastic gradient descent (ISGD) method.
-However, only the approach of \textcite{benbarkaSeeingImplicitNeural2022} is implemented for this work.
-% This method reduces the importance of batch size and learning rate
-% \[\theta_{n+1} = \theta_{n} - \alpha \cdot \nabla L (\theta_{n+1})\]
+\begin{figure}[hbt]
+    \centering{}
+    % \includegraphics[width=0.5\linewidth]{fig/p3/overview.pdf}
+    \caption[Overview of the proposed method]{Overview}
 
-\subsection{Automatic Differentiation}
-Automatic differentiation (AD) refers to one of several methods for computing derivatives, specifically to the accumulation of derivatives during function evaluation \parencite{baydin2018automatic}.
-This method underpins modern machine learning frameworks such as Pytorch \parencite{paszkePyTorchImperativeStyle2019}, which the framework used to construct the network architecture and perform training in this work.
-In these frameworks, training is performed by evaluating the result of a set of inputs using the current model weight parameters during a forward pass, accumulating the partial derivatives with respect to the parameters, and minimising an objective (loss) function using those gradients.
-These gradients inform weight updates in the direction of the negative gradient, toward a minima in the objective function.
-However, automatic differentiation can also evaluate the derivatives with respect to the inputs, using the same high-performance AD framework (e.g. Pytorch).
-This can provide the partial derivatives \(\frac{\partial f}{\partial x}, \frac{\partial f}{\partial y}, \frac{\partial f}{\partial z}\), as well as higher order derivatives.
+    \label{fig:overview}
+\end{figure}
 
 \section{Method}
-% \subsection{Notation}
-% Real n-dimensional vectors, named using lower-case letters are noted \(\mathbb{R}^n\), e.g. \boldmath{u}.
-% \(\mathbb{R}^{m\times{}n}\) \(m*n\) dimensional matrices, named using upper-case letters, e.g. \boldmath{A}.
 
 \subsection{Data}
-A case study dataset is made using the 2002 Wolfe Creek meteorite impact magnetic survey (Geophysical Acquisition \& Processing Section \cite*{wolfecreek2019}).
-This high-resolution survey contains \SI{402}{line-kilometres} of data at \SI{50}{\m} line spacing with a nominal terrain clearance of \SI{40}{\m}.
-The data used for implicit representation include the survey tie lines, standard in airborne geophysical surveys to reduce inter-line levelling noise.
-The standard deviation of the drape surface, including tie lines, is \SI{5}{\m}.
+A case study uses data from the 2002 Wolfe Creek meteorite impact magnetic survey \parencite{wolfecreek2019}.
+This high-resolution survey contains \SI{402}{line-kilometres} of data at \SI{50}{\m} line spacing with a nominal terrain clearance of \SI{40}{\m}, with line data collected on North-South transects.
+Prominently featured in the survey are the circular crater rim, and two East-West trending linear dunes to the North of the survey extent.
+The data used for implicit representation excludes the survey tie lines, typically used in airborne geophysical surveys to reduce inter-line levelling noise.
+The mean altitude of the drape surface excluding tie lines is \SI{39.5}{\m}, with a standard deviation of \SI{4.5}{\m}.
+The sample locations and recorded altitudes are shown in \cref{fig:samples}, where it can be seen the crater rim topography causes large deviations to the flown drape.
 
-Both the line data netCDF and grid raster for the Wolfe Creek survey were downloaded from the Geoscience Australia Geophysical Archive Data Delivery System and used without further processing.
+\begin{figure}[hbt]
+    \centering{}
+    \includegraphics[width=0.5\linewidth]{fig/p3/P864_sample_locs.pdf}
+    \caption[Point samples]{Sample altitudes for the Wolfe Creek survey lines. The diverging colourmap has been centred at the nominal survey terrain clearance of \SI{40}{\m}.}
+    \label{fig:samples}
+\end{figure}
+
+Both the line data and grid raster netCDFs for the Wolfe Creek survey were downloaded from Geoscience Australia \footnote{https://pid.geoscience.gov.au/dataset/ga/142694} (GA) and used without further processing.
 The line data netCDF contains tie-levelled, micro-levelled, and AWAGS levelled magnetic variables, in respective order of processing levels.
-% Tie-levelling is applied using only line data, while micro-levelling uses parameters calculated on an intermediate grid product of the line data.
-% AWAGS levelling is a final continuation of the microlevelled dataset to an Australian common datum, termed the \emph{AWAGS} datum.
-For the Wolfe Creek survey, the microlevelled magnetic data are used.
+The micro-levelled magnetic data are used in this case study. % and the additional surveys presented in Appendix A.
 Both geographic and projected coordinate systems can be used, provided the query coordinates for inference match those used during training.
-The three spatial coordinate dimensions are independently linearly min-max normalised between -1 and 1.
-While this means the latent spatial domain may be compressed relative to each other axis, the inverse normalisation process returns proportionality between axes.
+The three spatial coordinate dimensions are independently and linearly min-max normalised between -1 and 1.
+While this means the axes in the latent spatial domain may be compressed relative to each other axis, the inverse normalisation process returns proportionality between axes.
 The case study data do not span a large or magnetically varying geological extent, hence it is sufficient to use simple min-max normalisation for the magnetic field data within the global extent of the survey samples, here between -1 and 1.
@@
 
-In order to validate the model performance during training, a random \qty{20}{\percent} of the survey sample points are reserved.
-% Not currently doing this % Testing of the model is performed on a randomly selected \qty{10}{\percent} of the sample points. 
+\qty{70}{\percent} of the sample data are used for training, and a random \qty{20}{\percent} of the remaining survey sample points are reserved to validate the model performance during training.
 Inference can be performed by querying novel coordinates within the learnt domain, here at regularly spaced grid intervals for comparison with standard grid regularisation methods.
@@
 \subsection{Network architecture}
-The Coordinate MLP architecture comprises a simple fully connected network with \(N\) hidden layers, each with \(m\) neurons.
-The sinusoidal activation of \cite{sitzmann2019siren} is used. % for a baseline, and comparison is made to Gaussian and wavelet activations.
-High quality implicit representation has been achieved in contemporary INR research with only several hidden layers, typically between 3 and 8, with \(N = 8\) is used here.
-The number of neurons per layer is set \(m = 256\).
-% Figure \cref{fig:arch} shows the structure of the architecture.
-
-% \begin{figure}[hbt]
-%     \label{fig:arch}
-%     \caption[Network Architecture]{The Coordinate MLP architecture used for the implicit neural representation task.}
-% \end{figure}
+The CMLP architecture comprises a simple fully connected network with \(N\) hidden layers, each with \(M\) neurons, presented within \cref{fig:overview}.
+The sinusoidal activation of \cite{sitzmann2019siren} is used.
+High quality implicit representation has been achieved in contemporary INR research with only several hidden layers, typically between 3 and 8.
+The presented method uses 8 hidden layers and 256 neurons per layer.
 
@@
 \label{sec:training}
-% Performed on an Intel i5-12400 CPU with 32 GB RAM, and an Nvidia 3060 12 GB GPU.
 
-Implicit functions are trained using coordinate-value pairs, and for low-resolution images the entire cell coordinate and cell value dataset fits within GPU memory for batch gradient descent.
-The Wolfe Creek meteorite impact crater case study line data has \SI{76420}{} sample points, with the Geoscience Australia provided grid product having a resolution of 446 \(\times{}\) 445 cells.
-The line coordinate dataset easily fits into available graphics memory, and can be trained using batch gradient descent.
+Implicit functions are trained using coordinate-value pairs.
+For low-resolution inputs the entire cell coordinate and cell value dataset fits within GPU memory for batch gradient descent.
+The Wolfe Creek meteorite impact crater case study line data has \SI{76420}{} sample points, and the Geoscience Australia provided reference grid has a resolution of 446 \(\times{}\) 445 cells.
+The case study line data easily fit into available graphics memory, and can be trained using batch gradient descent.
+
+Training was performed on an Intel i9-10900KF workstation with an Nvidia RTX 3090 24 GB GPU\@.
+A highly accurate representation can be learned within \SI{5000}{epochs} using the Adam optimiser, for a duration in the order of \SI{60}{seconds}.
+The objective function comprises \(L^2\) loss between the input and predicted field values (\cref{eqn:cri}).
+
+\begin{equation}
+    \label{eqn:cri}
+    \mathcal{L}_{Total} = \lVert{}u_{input} - u_{pred}\rVert{}_{2} % + \beta{} \lVert{}\frac{\partial^{2}{u_{pred}}}{\partial{}\phi{}_{pred}^{2}}\rVert{}_{2}
+\end{equation}
+
+The OneCycle learning rate scheduler \parencite{smithSuperconvergenceVeryFast2018} with a maximum rate of \(1\times{}10^{-4}\) is used to provide fine tuning at low learning rates toward the end of training.
+Convergence of the network is shown in \cref{fig:convergence}.
 %However, training on large scattered aeromagnetic surveys with more than one million samples, memory becomes a constraint and mini-batch training is required.
-Training was performed on an Intel i9-10900KF workstation with an Nvidia RTX 3090 24 GB GPU\@.
-A highly accurate representation can be learned within 1000 epochs using the Adam optimiser, for a duration in the order of 60 seconds.
-The OneCycle learning rate scheduler \parencite{smithSuperconvergenceVeryFast2018} with a maximum rate of \(3\times{}10^{-4}\) is used to provide fine tuning at low learning rates toward the end of training.
-Convergence of the network is shown in \cref{fig:convergence}
 
@@
 
-As described in \cref{sec:pinn}, the objective function comprises \(L^2\) loss between the input and predicted field values.
-It does not use the Laplace loss discussed in \cref{sec:pinn}, which fails to converge. %, summed with weighted Laplace's equation loss, \cref{eqn:cri}.
-\begin{equation}
-    \label{eqn:cri}
-    \mathcal{L}_{Total} = \lVert{}u_{input} - u_{pred}\rVert{}_{2} % + \beta{} \lVert{}\frac{\partial^{2}{u_{pred}}}{\partial{}\phi{}_{pred}^{2}}\rVert{}_{2}
-\end{equation}
-
 \subsection{Derivative calculation}
-A naive approach to calculating gradients with the INR would be to evaluate the representation \(\phi{}_{(x, y, z)}\) at a set of regular coordinates \({(x, y, z)}_1 \dots {(x,y,z)}_n\), and use numerical differentiation to calculate derivatives.
-However, using Automatic Differentiation with Pytorch, the implicit representation can be differentiated with respect to its inputs to provide gradients, prior to being queried at the nodes of a quantised grid.
-That is, directly sample \(\nabla{}\phi{}_{(x,y,z)}\) at \({(x, y, z)}_1 \dots {(x,y,z)}_n\).
+A naive approach to calculating gradients with the trained INR would be to evaluate the representation \(f(x, y, z)\) at a set of coordinates \({(x, y, z)}_1 \dots {(x,y,z)}_n\), and use numerical differentiation with the output grid to calculate derivatives.
+However, using AD with Pytorch, the implicit representation can be differentiated with respect to its coordinate inputs to provide spatial gradients, prior to being queried at the nodes of a quantised grid.
+That is, to directly sample \(\nabla{}\phi{}_{(x,y,z)}\) at \({(x, y, z)}_1 \dots {(x,y,z)}_n\).
 Higher order derivatives can be also calculated using AD in this manner.
@@
 \section{Results}
-\subsection{Implicit gridding}
-Querying a learnt implicit neural representation (INR) using a regularly spaced \(x,y\) grid at a specific \(z\) height is a novel method for gridding geophysical potential field surveys.
+\subsection{Level grid prediction from INR}
+Querying a learnt INR using a regularly spaced \(x,y\) grid at a specific \(z\) height is a novel method for producing level grids from geophysical potential field surveys.
+The cell size can be selected using a finer or coarser \(x,y\) spacing, including variable or anisotropic cell sizes.
+Contemporary super-resolution research can leverage this continual representation as a framework for high quality arbitrary scale factor high-frequency signal prediction \parencite[e.g][]{chenLearningContinuousImage2021}.
+However, the potential field representation task here does not attempt to predict additional high-frequency information and resolution remains determined by the survey sample spacing and neural network capacity.
+
 \Cref{fig:grid} shows the INR queried at \(z=\SI{40}{\meter}\), which is the nominal terrain clearance of the survey.
-Notably, the cell size can be selected by fining or coarsening the \(x,y\) spacing, including variable or anisotropic cell sizes.
-Contemporary super-resolution research can leverage this continual representation as a framework for high quality arbitrary scale factor high-frequency component prediciton \parencite[e.g][]{chenLearningContinuousImage2021}.
-However, the potential field representation task here does not attempt to predict additional high-frequency information and resolution remains limited by the survey sample spacing and neural network capacity.
+A good qualitative match is achieved between the GA reference grid and the grid queried from the implicit representation, which successfully reconstructs the linear dune features and circular rim features.
+This high performance is quantified by the residuals and peak signal to noise ratio (PSNR) of \SI{40.12}{\dB}.
+% Further level grids from other survey extents are included in Appendix A.
 
@@
     \centering{}
-    \includegraphics[width=1.0\linewidth]{fig/p3/grid_comparison_40m.pdf}
-    \caption[Grid prediction]{Comparison between the ground-truth grid processed by Geoscience Australia (left) and the constant level grid queried from the INR at \SI{40}{\m} (right).}
+    \includegraphics[width=1.0\linewidth]{fig/p3/P864_grid_comparison_40m.pdf}
+    \caption[Grid prediction (40 m)]{Comparison between the reference grid processed by Geoscience Australia (left) and the constant level grid queried from the INR at \SI{40}{\m} (middle).
+The residuals are shown for areas containing reference data (right), with a range of ±2 standard deviations of values in the reference grid.}
     \label{fig:grid}
@@
 
-The INR can be queried at any continuous coordinate, including out-of-range values beyond the training domain.
-The predicted field becomes unstable beyond this boundary, which can be seen in the periphery of \cref{fig:grid}.
+The INR can be queried at arbitrary continuous coordinates, including out-of-range values beyond the training domain.
+As expected, the predicted field becomes unrealistic when extrapolating beyond this boundary, which can be seen in the periphery of the INR grid in \cref{fig:grid}.
+This boundary region (indicated by solid white in the reference grid) is excluded from PSNR calculation.
 
 Constant level grids can be queried from the INR at any height.
-\Cref{fig:grid35} shows the case study extent queried at \SI{35}{\m}.
-While comparable features can still be interpreted within this level grid, the representation learnt here fails to represent physically realistic continuation of the field.
-It is conjectured that implementing a PINN criterion such as Laplacian loss \cref{eqn:cri_laplace} would improve the performance these upward or downward extracted slices.
+\Cref{fig:grid35} shows the case study INR queried at \SI{35}{\m}, which is \SI{5}{\m} lower than the nominal survey altitude.
+While the rim feature can still be interpreted within this lower level grid, the INR fails to demonstrate physically realistic continuation of the field.
+% It is conjectured that successfully training a PINN criterion such as Laplace’s equation loss (equation 1.3) would improve the accuracy of these upward or downward extracted slices.
 
@@
     \centering{}
-    % TODO query at AWAGS height and compare GA AWAGS grid.
-    % TODO check if provided grid is AWAGS or MICRO levelled - maybe grid data myself.
-    \includegraphics[width=1.0\linewidth]{fig/p3/grid_comparison_35m.pdf}
-    \caption[Grid prediction]{A constant level grid queried from the INR at the height of \SI{35}{\m} (right).}
+    \includegraphics[width=1.0\linewidth]{fig/p3/P864_grid_comparison_35m.pdf}
+    \caption[Grid prediction (35 m)]{A constant level grid queried from the INR at the height of \SI{35}{\m} (middle).}
     % AWAGS is 80 m, but we see nothing useful at 80m
@@
 Using AD, derivatives can be calculated between the input spatial coordinates and the output potential field representation.
-While horizontal derivatives queried from the INR correspond well to numerical derivatives calculated on the 40 m level grid (\cref{fig:hori_grad}), the vertical derivative suffers poor performance (\cref{fig:vert_grad}).
+While horizontal derivatives queried from the INR correspond well to numerical derivatives calculated on the \SI{40}{\m} level grid \cref{fig:hori_grad}, the vertical derivative suffers poor performance \cref{fig:vert_grad}.
 This correlates with the poor continuation performance of model when predicting level grids several meters or more beyond the nominal sample height.
-This is interpreted as the model learning a poor representation of the vertical component of the potential field.
+This is interpreted as the presented model having a limited capacity to extrapolate, and learning a poor representation of the vertical component of the potential field, which we further discuss in \cref{sec:discussion}
 
@@
     \centering{}
-    \includegraphics[width=1.0\linewidth]{fig/p3/dh_comparison.pdf}
-    \caption[Horizontal derivatives]{AD (left column) and numerical (middle column) horizontal derivatives of the INR\@. Residuals are shown in the right column.}
+    \includegraphics[width=1.0\linewidth]{fig/p3/P864_dh_comparison.pdf}
+    \caption[Horizontal derivatives]{Horizontal gradients calculated using the proposed method and the reference numerical method.
+        Both numerical differentiaion (left column) and AD INR (middle column) are calculated on the INR level grid or INR respectively.
+        Residuals are calculated between the numerical and AD gradient grids (right column).}
     \label{fig:hori_grad}
@@
     \centering{}
-    \includegraphics[width=1.0\linewidth]{fig/p3/dv_comparison.pdf}
-    \caption[Vertical derivative]{AD (left) and numerical (right) vertical derivatives of the INR\@.}
+    \includegraphics[width=1.0\linewidth]{fig/p3/P864_dv_comparison.pdf}
+    \caption[Vertical derivative]{Vertical derivative grids queried from AD differentiated INR (left) and calculated numerically (right) on the \SI{40}{m} level grid queried from the INR\@.}
     \label{fig:vert_grad}
@@
 
-% Using the implicit representation, a selection of common geophysical filters are calculated prior to quantisation.
+\section{Discussion}
+\label{sec:discussion}
+INR has strong learning capacity for the potential field samples in the horizontal plane near the nominal survey altitude, allowing extraction of level grids which are accurate against the reference grid.
+Level grids can be queried at arbitrary heights and cell sizes, with the highest accuracy achieved at the realised nominal survey altitude.
+Performance decreases within approximately one standard deviation from that height (\SI{35} to \SI{45}{\m}), with gradual failure of the model outside of that range.
+It is interpreted from the poor quality of the vertical gradients and out-of-range level grid predictions that the model is learning a function between horizontally coplanar points, and not an accurate vertical continuation function.
+This is conjectured to be caused by aeromagnetic sampling being carried out on a nominally horizontal planar drape surface, without sufficient repeat measurements at other heights to train the network for the vertical field component.
 
-% \begin{enumerate}
-%     \item ASIG
-%     \item tilt?
-%     \item idk?
-% \end{enumerate}
+While quantised grids can be queried at any cell size, short wavelength information beyond the Nyquist limit of the survey line sampling is not predicted.
 
-\section{Discussion}
-The implicit representation has strong representative capacity for the horizontal components of the potential field, allowing extraction of level grids which are accurate against the ground truth grid.
-Level grids can be generated at any height, with best performance achieved near the realised nominal survey altitude.
-Performance worsens within approximately one standard deviation from that height (\SI{35} to \SI{45}{\m}), with gradual failure of the model outisde of that height range.
+The current method could include additional target dimensions, which would allow representation learning of vector fields \(\mathbb{R}^{3}\) in three dimensions \(\mathbb{R}^{3}\).
+This has applications in tensor fields and data integration tasks, and these remain for future work.
+
+INR is a rapidly evolving field of research, and draws on contemporary established deep learning improvements within related fields.
+In addition to improving the high-frequency learning capacity with novel activation functions and regularisation methods, fundamental neural network research and hardware development is ongoing.
+
 % Even when using a small subset of the dataset, this performance is retained.
-It is interpreted from the poor quality of the vertical gradients and out-of-range predictions that the model is relying on learning a function between horizontally coplanar points, as opposed to a realistic vertical continuation function.
-While quantised grids can be queried at any cell size, short wavelength information beyond the Nyquist limit of the survey line sampling is not predicted.
-% TODO The addition of a PINN term for objective function ...
 
@@
 
-Implicit neural representation is a rapidly evolving field of research, and draws on contemporary deep learning improvements within related fields.
-In addition to improving the high-frequency learning capacity, physics informed loss functions may allow higher quality vertical continuation performance.
-The current method could trivially include additional target dimensions, which would allow representation learning of vector fields \(\mathbb{R}^{3}\) in three dimensions \(\mathbb{R}^{3}\).
-This has potential application in tensor fields and associated predictive tasks, and these remain for future work.
+\subsection{Future Work}
+\label{sec:future}
+The outputs of neural networks can be constrained to obey geophysical laws, using physics-informed neural networks (PINNs) \parencite{raissiPhysicsinformedNeuralNetworks2019}.
+PINNs recognise that if the inputs to a neural network are samples of a function which follows some physical law, outputs from the model should similarly be constrained by that law.
+By regularising the network with an objective function which penalises solutions that don't fit the partial differential equations describing the law, it is possible to vastly reduce the physically valid solution search space \parencite{raissiPhysicsinformedNeuralNetworks2019}.
+Because CMLP networks with periodic activations are continuously differentiable, it is possible to enforce this constraint as an element of the overall loss function within the network.
+\Textcite{sethiHardEnforcementPhysicsinformed2023} demonstrate that this regularisation does not have to be implemented as a loss function, but instead can be a hard constraint embedded within the network.
+Another approach \parencite{liImplicitStochasticGradient2023} replaces the ubiquitous stochastic gradient descent optimiser \emph{Adam} with an implicit stochastic gradient descent (ISGD) method.
+
+Examples of physics-informed constraints include enforcing initial or boundary conditions, or conforming to known properties of the modelled signal.
+Potential fields in an airborne sampling context are constrained by a number of physical laws, including \emph{Laplace's equation};
+\[
+    \nabla^2 \phi = 0
+\]
+In three dimensions, \cref{eqn:Laplace};
+\begin{equation}
+    \label{eqn:Laplace}
+    \frac{\partial{}^2\phi}{\partial{}x^2} + \frac{\partial{}^2\phi}{\partial{}y^2} + \frac{\partial{}^2\phi}{\partial{}z^2} = 0
+\end{equation}
+
+%TODO Confirm logic here: % If Laplace's equation:\( \nabla^2 \phi = 0 \) is satisfied, it is harmonic, and has continuous single valued first derivatives, and has second derivatives.
+% This indicates the function lacks curvature.
+
+% Blakely:
+% A force field \(F\) is the gradient (or negative gradient) of the potential energy.
+% \( F = \nabla\phi \) for the gravity potential, \(F = - \nabla \phi\) for the Magnetic potential.
+% \( \phi(x,y,z) = constant \) is an equipotential surface.
+
+% Numerical methods for potential field continuation are unstable, recognised in the geophysical community by solution divergence and noise in predictions.
+A geophysics informed network could include a Laplace criterion, \cref{eqn:cri_laplace}.
+
+\begin{equation}
+    \label{eqn:cri_laplace}
+    \mathcal{L}_{PDE} = \beta{}\lVert{}\frac{\partial{}^2f}{\partial{}x^2} + \frac{\partial{}^2f}{\partial{}y^2} + \frac{\partial{}^2f}{\partial{}z^2}\rVert{}_{2}
+\end{equation}
+
+As denoted by the \(L^2\) operator \(\lVert{}\cdot{}\rVert{}_{2}\) and weighting \(\beta{}\), this criterion penalises outputs where the sum of partial derivatives is not close to zero.
+
+Initial attempts using the objective function approach were trialled in this work, but failed to converge and remain for future work.
+Other geophysical formulae may present avenues for PINN implementation, such as vertical continuation described in \cite{blakelyPotentialTheoryGravity1996}.
 
 \section{Conclusions}
-High-resolution implicit neural representation of potential field geophysics surveys is achieved with the use of coordinate MLP neural networks.
+High-resolution implicit neural representation of potential field geophysics surveys is achieved with the use of coordinate MLP neural networks for INR.
 Resolution in the representation is limited by network capacity, rather than initial grid cell size selection during regularisation.
-Level grids can be extracted from these representations, emerging as a novel method for regularising scatter geophysical sample data.
-Gradients and spatial filters can be caluclated using the full resolution of the learnt representation, and gridded \emph{a posteri} of gradient or filter calculation.
+Level grids can be extracted from these representations, emerging as a novel method for regularising scattered geophysical sample data.
+Gradients can be calculated using the learnt representation, and gridded \emph{a posteri} of gradient calculation.
 
@@
 % \label{app:menzies} %TODO format as "Appendix"
-% The Menzies South ... Pxxxx survey contains xxx sample points across yyyy line kilometres, and was flown at a nominal terrain clearance of zz m.
+% The Menzies North P864 survey contains xxx sample points across yyyy line kilometres, and was flown at a nominal terrain clearance of zz m.
 % While a high-quality result is attainable using batch gradient descent on a subset of the survey points, minibatch gradient descent is demonstrated for the CMLP used to learn the full survey INR\@.

### 2023-09-12 manuscript.tex
Move bib include to fix bug
Defining the bib location in manuscript rather than style allows bibtex autocomplete in vscode.
Prepare front matter

@@
 % \includeonly{intro}
-\documentclass[12pt,a4paper,twocolumn]{report}
+\documentclass[12pt,a4paper]{report} %,openright,twoside
 \usepackage{thesisstyle}
+\addbibresource{bib/PhD.bib}
 \begin{document}
-\author{Luke Thomas Smith}
-\title{Deep learning for geophysics}
-\date{\today}
-\maketitle{}
-\tableofcontents
-\listoffigures
-\listoftables
+
+\begin{titlepage}
+
+    \begin{center}
+        \large{\textbf{Potential Field Geophysics Enhancement Using Contemporary Deep Learning Approaches}}
+
+        \vspace{15 mm}
+        {\large{Luke Thomas Smith, BSc, MRes}}
+
+        \vspace{15 mm}
+        This thesis is presented for the degree of
+
+        \vspace{5 mm}
+        \textbf{Doctor of Philosophy}
+
+        of
+
+        \textbf{The University of Western Australia}
+
+        \vspace{5 mm}
+        School of Earth Sciences
+
+        \vspace{10 mm}
+        \begin{figure}[h]
+            \centering{}
+            \includegraphics[scale=0.65]{fig/UWA_FORMAL_PORTRAIT_CMYK}
+        \end{figure}
+
+        \vspace*{\fill}
+        2023
+    \end{center}
+\end{titlepage}
+
+\clearpage{}
+
+\pagenumbering{roman}
+\setcounter{page}{1}
+\renewcommand{\thesection}{\Roman{section}}
+
+\section{Thesis Declaration}
+I, Luke Thomas Smith, certify that:
+\begin{itemize}
+    \item{}This thesis has been substantially accomplished during enrolment in this degree.
+    \item{}This thesis is my own work and does not contain any material previously published or written by another person, except where due reference has been made in the text or Authorship Declaration.
+    \item{}This thesis does not contain material which has been submitted for the award of any other degree or diploma in my name, in any university or other tertiary institution.
+    \item{}In the future, no part of this thesis will be used in a submission in my name, for any other degree or diploma in any university or other tertiary institution without the prior approval of The University of Western Australia and where applicable, any partner institution responsible for the joint-award of this degree.
+    \item{}This thesis does not violate or infringe any copyright, trademark, patent, or other rights whatsoever of any person.
+\end{itemize}
+
+\vspace*{20 mm}
+\noindent\begin{tabular}{ll}
+                               &                           \\[8ex]
+    \makebox[100 mm]{\dotfill} & \makebox[30 mm]{\dotfill} \\
+    Student Signature          & Date                      \\
+\end{tabular}
+
+\newpage{}
+
+\section{Abstract}
+In the contemporary age of deep learning, namely the frantic and now forever advancing activity emerging from the mid 2010's, geoscience stands to embrace its own big data challenges.
+A small but critical component of the geophysical method is the practice of potential field surveying from aircraft, for rapid and extensive coverage of target geology.
+Airborne geophysical surveys are routinely conducted as pre-competitive regional data acquisition to stimulate exploration, or as targeted investigations by the mineral exploration industry.
+The collected data may contain millions of discrete samples scattered in three dimensions, and their interpretation often relies on regularisation to a quantised grid, allowing digital processing and human or machine interpretation.
+A ubiquitous constraint on the usefulness of these data is the data resolution, or more exactly, the Nyquist frequency of the grid.
+This limit on the high-frequency content available within the grid results directly from the spatial sampling density of the originating survey, and the density of cells used to represent the grid.
+The well known geophysics rule of thumb, \emph{a grids cell size should equal one quarter to one fifth of the line spacing}, has long informed the achievable detail in these survey products.
+
+This thesis reports on two topics in geophysics; enhancing the high-frequency content of survey data using \emph{super-resolution}; and, learning a representative function of a potential field extent using \emph{implicit neural representation}.
+The first has application in enhancing the value of geophysical surveys by extracting greater information from necessarily sparsely sampled potential fields.
+The second topic stands to benefit from ongoing research in deep learning, but may present a straightforward neural network framework for high quality grid regularisation, processing, storage, and data integration.
+For each chapter, real-world geophysical case studies are presented, in order to demonstrate the challenges and effectiveness of the method with currently available open file data.
+
+Chapter one establishes that deep learning can effectively enhance the resolution of real magnetic textures at a fixed four times scale.
+This is further explored in chapter two, explicitly using data gridded from both synthetic and real line data at increasingly wider spacings to achieve both super-resolution on real-world low-resolution data and to investigate the useful limits of upscaling.
+
+Chapter two quantifies the upscaling performance at line spacings between \SI{80}{\m} and \SI{480}{\m} and successfully enhances the resolution of unseen real world survey grids.
+
+Finally, chapter three presents successful representation learning of scattered real-world potential field samples by a neural network, in a framework that allows the extraction of high-resolution level grids and for rapid analytical calculation of spatial gradients.
+
+Similar outcomes to those presented throughout this thesis have been attempted by at-times surprisingly antique machine learning practices, as well as persistently effective numerical methods in the literature.
+However, the deep learning methods adopted within the component chapters of this manuscript have each been selected for their contemporaneity.
+Each chapter investigates the use of deep learning methods from the literature, published in the same year as the drafting of their respective geophysical application chapter.
+The rapid and increasing pace of advancement in deep learning research demands this adherance to the cutting-edge, in order to address the growing magnitudes of data collected and processed within geoscience to address current global challenges.
+
+\tableofcontents{}
+% \listoffigures{}
+% \listoftables{}
+
+\section{Acknowledgements}
+\dots{}
+
+This research was supported by a Rio Tinto Iron Ore PhD Scholarship.
+
+\section{Authorship Declaration}
+This thesis contains material that has been published or prepared for publication.
+The extent of the candidate's contribution toward publication is outlined below.
+
+\smallskip{}
+\noindent{}All software development was performed by L. Smith.
+
+\noindent{}The possible application of super-resolution for geophysical grid data was suggested by E.J. Holden.
+
+\medskip{}
+\noindent{}Sections comprising published journal articles:
+\begin{itemize}
+    \item{}\textbf{Section}: Chapter 1
+
+    \textbf{Publication}: Smith, L., Horrocks, T., Holden, E.J., Wedge, D., Akhtar, N., 2022.
+Magnetic grid resolution enhancement using machine learning: A case study from the Eastern Goldfields Superterrane.
+Ore Geology Reviews 150, 105119.
+https://doi.org/10.1016/j.oregeorev.2022.105119
+
+    \textbf{Contribution}: The method for was researched, developed, and drafted by L.
+Smith, who also performed revision based on manuscript review from co-authors EJ Holden, D.
+Wedge, T.
+Horrocks and N.
+Akhtar.
+    As a published manuscript, further revision was provided by the journal editor and peer reviewers.
+\end{itemize}
+
+\noindent{}Sections comprising manuscripts prepared for publication:
+\begin{itemize}
+    \item{}
+    \textbf{Section}: Chapter 2
+
+    \textbf{Contribution}: Further investigation of super-resolution was initiated, developed, analysed, and drafted by L. Smith, with guidance on manuscript direction from co-authors.
+
+    \item{}
+    \textbf{Section}: Chapter 3
+
+    \textbf{Contribution}: The concept and development of implicit neural representation for geophysics was initiated by L.
+Smith, who performed the subsequent development, analysis, and manuscript authorship with review from co-authors.
+
+\end{itemize}
+
+\noindent{}The contributions of the author have been truthfully stated, and permission from
+each author has been sought to include the published material in this thesis.
+
+% \vspace*{20 mm}
+
+\noindent\begin{tabular}{ll}
+                                          &                           \\[8ex]
+    \makebox[100 mm]{\dotfill}            & \makebox[30 mm]{\dotfill} \\
+    Eun-Jung Holden                       & Date                      \\
+    Principal and Coordinating Supervisor &                           \\[8ex]
+    \makebox[100 mm]{\dotfill}            & \makebox[30 mm]{\dotfill} \\
+    Daniel Wedge                          & Date                      \\
+    Co-supervisor                         &                           \\[8ex]
+    \makebox[100 mm]{\dotfill}            & \makebox[30 mm]{\dotfill} \\
+    Tom Horrocks                          & Date                      \\
+    Co-supervisor                         &                           \\[8ex]
+    \makebox[100 mm]{\dotfill}            & \makebox[30 mm]{\dotfill} \\
+    Naveed Akhtar                         & Date                      \\
+    Co-supervisor                         &                           \\
+\end{tabular}
+
+\clearpage{}
+\pagenumbering{arabic}
+\setcounter{page}{1}
+\setcounter{section}{0}
+\renewcommand{\thesection}{\arabic{section}}
+
 \subfile{intro}
+\dots{}
 % \subfile{paper1}
-% \subfile{paper2}
+% % \subfile{paper2}
 % \subfile{paper3}
-\clearpage
-% \include{bibliography}
+\clearpage{}
+\include{bibliography}
 \end{document}

### 2023-09-13 paper3.tex
Add notes from N.A. review

@@
 \setcounter{chapter}{1}
-\author{{Luke Thomas Smith} \and{Tom Horrocks} \and{Eun-Jung Holden} \and{Daniel Wedge} \and{Naveed Akhtar}}
+\author{{Luke Thomas Smith} \and{Tom Horrocks} \and{Naveed Akhtar} \and{Eun-Jung Holden} \and{Daniel Wedge}}
 \title{Implicit Neural Representation for Potential Field Geophysics }
@@
     Using this new paradigm of encoding spatial information within a neural network enables new methods for working with potential field survey data.
-
     We present a novel application of implicit neural representation to potential fields, demonstrate the quality of the learnt implicit function by encoding real airborne geophysical survey line data, predict constant level grids, and compare the result to grid data processed with a traditional workflow.
     We further demonstrate processing the learnt function directly in the continuous domain using automatic differentiation, with the same framework used to train the neural network.
+    %TODO too much detail in abstract here
     For example, directional gradients are calculated in the continuous domain prior to grid quantisation, and therefore without the associated loss of high-resolution content imposed by gridding.
@@
 By parameterising the function in coordinate space, novel values of the function can be queried at arbitrary coordinates within the learnt continuous spatial domain.
-Recent advances in CMLPs by using periodic activations such as sinusoids have demonstrated that high frequency information can be modelled by CMLP networks, while being continuously differentiable through the depth of the network to facilitate rapid training.
+Recent advances in CMLPs by using periodic activations such as sinusoids have demonstrated that high frequency information can be modelled well by CMLP networks, while being continuously differentiable throughout the depth of the network.
 
 We present a novel method of encoding a representation of a geophysical potential field using INR\@.
+%TODO "used to demonstrate" poor
 This method is used to demonstrate a novel method of creating level grids from scattered aeromagnetic data.
-Due to using a continuous coordinate representation, there is no dependency on grid quantisation from an initial cell size selection.
-It also provides for further processing that can be calculated analytically in the continuous spatial domain, allowing the use of all available sample information in these calculations.
+In our method, due to using a continuous coordinate representation, there is no dependency on grid quantisation from an initial cell size selection.
+The proposed technique also provides for further processing that can be calculated analytically in the continuous spatial domain, allowing the use of all available sample information in these calculations.
 
+%TODO - a bit abrupt
 For the task of level grid prediction, the PSNR similarity between a case study reference grid and the proposed method is \SI{40}{\dB}.
@@
 
-The method is still in its infancy, but stands to benefit from ongoing research in the highly active fields of deep learning and INR\@.
+INR and CMLP have recently emerged in the literature, so our proposed method stands to benefit from ongoing research in these highly active fields.
 
@@
     \label{eqn:potential}
-    \phi\left(x,y,z\right)
+    \phi\left(x,y,z\right),
 \end{equation}
+where \(\phi{}\) is the potential, and \({(x,y,z)}\) are the three spatial dimensions.
 
@@
 \label{sec:inr}
-CMLP networks are fully connected networks, which have been ubiquitous in machine learning for several decades.
+Coordinate Multilayer Perceptron (CMLP) networks are fully connected networks, which have been ubiquitous in machine learning for several decades.
 An MLP comprises a sequence of layers of neurons, densely connected to all neurons in each adjacent layer.
 Each neuron is a discrete trainable function, comprising a weight multiplied by the input vector, an added bias term, and a subsequent scaling function termed the activation function.
-The structure of an MLP can be described by the number of neurons in each layer (features) the number of layers between the input and output (hidden layers), and the class of activation function used.
+The structure of an MLP can be described by the number of neurons in each layer (features), the number of layers between the input and output (hidden layers), and the class of activation function used.
 
@@
 Periodic activation functions differ from typical non-linear activations by comprising the neuron with a function that repeats periodically, which allows for continuous differentiation throughout the depth of the network.
-Work by \cite{ramasinghePeriodicityUnifyingFramework2022} revealed that it is the magnitude of the first and second derivatives of the activation that enhance high-frequency representation learning capacity, rather than periodicity, leading to Gaussian \parencite{ramasinghePeriodicityUnifyingFramework2022} and wavelet \parencite{saragadamWIREWaveletImplicit2023} activation functions for CMLP\@.
+Work by \cite{ramasinghePeriodicityUnifyingFramework2022} revealed that it is the magnitude of the first and second derivatives of the activation that enhanced high-frequency representation learning capacity, rather than periodicity, leading to Gaussian \parencite{ramasinghePeriodicityUnifyingFramework2022} and wavelet \parencite{saragadamWIREWaveletImplicit2023} activation functions for CMLP\@.
 
@@
 Resolution in these tasks is not limited by quantisation of the representation, but rather the capacity of the network architecture used.
-Increasing this capacity is currently the subject of very high interest in the machine learning research community, for example by leveraging new activation functions \parencite{saragadamWIREWaveletImplicit2023}, transforming the input space \parencite[e.g.][]{benbarkaSeeingImplicitNeural2022} or using additional constraints on the search space such as physics-informed neural networks \parencite{raissiPhysicsinformedNeuralNetworks2019}.
+Increasing this capacity is currently the subject of high interest in the machine learning research community.
+Research directions include leveraging new activation functions \parencite{saragadamWIREWaveletImplicit2023}, transforming the input space \parencite[e.g.][]{benbarkaSeeingImplicitNeural2022} or using additional constraints on the search space such as physics-informed neural networks \parencite{raissiPhysicsinformedNeuralNetworks2019}.
 
-CMLP networks for INR can be compared to compressed sensing \parencite{candesIntroductionCompressiveSampling2008} for its ability to recover accurate grids from sparsely sampled geophysics samples.
+CMLP networks for INR can be compared to compressed sensing \parencite{candesIntroductionCompressiveSampling2008} for their ability to recover accurate grids from sparsely sampled geophysics samples.
 While recovery of potential field grids using a compressed sensing approach is often framed as a numerical optimisation problems \parencite[e.g.][]{yangAirborneGravimetryData2015,xuGravityAnomalyReconstruction2019}, these are not equivalent to modern deep learning approaches.
 Compressed sensing relies on the theory that a signal has a sparse representation in some transform domain, and a deeper exploration of the comparison between INR and compressed sensing remains to be performed.
+%per Naveed
+Compressed sensing recovers the signal through linear transformations.
+Because neural networks allow convenient modelling of non-linear transformations, they have an inherent advantage over compressed sensing for potential field grid recovery.
 
@@
 Automatic differentiation (AD) refers to one of several methods for computing derivatives, specifically to the method of accumulating derivatives during function evaluation \parencite{baydinAutomaticDifferentiationMachine2018}.
-This method underpins modern machine learning frameworks such as Pytorch \parencite{paszkePyTorchImperativeStyle2019}, which is the framework used to construct the network architecture and perform training in this work.
-In these frameworks, training is performed by evaluating a set of inputs using the current model weight parameters during a forward pass, while accumulating the partial derivatives of the result with respect to those parameters, to navigate an objective (loss) function using those gradients.
-These gradients inform weight updates in the direction of the negative gradient, toward a minimum in the objective function.
+This method underpins modern machine learning frameworks such as Pytorch \parencite{paszkePyTorchImperativeStyle2019}, which is used to construct the network architecture and perform training in this work.
+In these frameworks, training is performed by evaluating a set of inputs using the current model parameters during a forward pass, while accumulating the partial derivatives of the result with respect to those parameters, to optimise an objective (loss) function.
+These gradients inform parameter update operations to minimise the model loss.
 However, automatic differentiation can also evaluate the derivatives of the network output with respect to the inputs, using the same high-performance AD framework.
@@
 
+% Per naveed - > start of sec 1.3?
 \subsection{Overview of the proposed method}
@@
 \subsection{Data}
-A case study uses data from the 2002 Wolfe Creek meteorite impact magnetic survey \parencite{wolfecreek2019}.
+The case study is performed using data from the 2002 Wolfe Creek meteorite impact magnetic survey \parencite{wolfecreek2019}.
 This high-resolution survey contains \SI{402}{line-kilometres} of data at \SI{50}{\m} line spacing with a nominal terrain clearance of \SI{40}{\m}, with line data collected on North-South transects.
@@
 
-\qty{70}{\percent} of the sample data are used for training, and a random \qty{20}{\percent} of the remaining survey sample points are reserved to validate the model performance during training.
-Inference can be performed by querying novel coordinates within the learnt domain, here at regularly spaced grid intervals for comparison with standard grid regularisation methods.
+The \SI{76420}{} sample points contained within the case study line data are split, with \qty{70}{\percent} used for training, and a random \qty{20}{\percent} of the remaining points are reserved to validate the model performance during training.
+Inference is performed by querying novel coordinates within the learnt domain, here at regularly spaced grid intervals for comparison with standard grid regularisation methods.
 
 \subsection{Network architecture}
-The CMLP architecture comprises a simple fully connected network with \(N\) hidden layers, each with \(M\) neurons, presented within \cref{fig:overview}.
+The CMLP architecture comprises a simple fully connected network with \(n\) hidden layers, each with \(m\) neurons, presented within \cref{fig:overview}.
+Comparison of recently proposed activatons for CMLP is performed in \cref{saragadamWIREWaveletImplicit2023}, where increasing both \(n\) and \(m\) increases the capacity of the model, at the cost of computational requirements.
+
 The sinusoidal activation of \cite{sitzmann2019siren} is used.
@@
 The presented method uses 8 hidden layers and 256 neurons per layer.
+%per naveed: Why choose these? Why choose the specific input output layer sizes?
 
-\subsection{Training Particulars}
+\subsection{Training setup}
 \label{sec:training}
@@
 For low-resolution inputs the entire cell coordinate and cell value dataset fits within GPU memory for batch gradient descent.
-The Wolfe Creek meteorite impact crater case study line data has \SI{76420}{} sample points, and the Geoscience Australia provided reference grid has a resolution of 446 \(\times{}\) 445 cells.
+The Wolfe Creek meteorite impact crater case study line data has , and the Geoscience Australia provided reference grid has a resolution of 446 \(\times{}\) 445 cells.
 The case study line data easily fit into available graphics memory, and can be trained using batch gradient descent.
@@
 That is, to directly sample \(\nabla{}\phi{}_{(x,y,z)}\) at \({(x, y, z)}_1 \dots {(x,y,z)}_n\).
-Higher order derivatives can be also calculated using AD in this manner.
+%TODO we dont show these Higher orders - should we?
+Higher order derivatives are calculated using AD in the same manner.
 
@@
 Using AD, derivatives can be calculated between the input spatial coordinates and the output potential field representation.
-While horizontal derivatives queried from the INR correspond well to numerical derivatives calculated on the \SI{40}{\m} level grid \cref{fig:hori_grad}, the vertical derivative suffers poor performance \cref{fig:vert_grad}.
+While horizontal derivatives queried from the INR correspond well to numerical derivatives calculated on the \SI{40}{\m} level grid in \cref{fig:hori_grad}, the vertical derivative suffers poor performance \cref{fig:vert_grad}.
 This correlates with the poor continuation performance of model when predicting level grids several meters or more beyond the nominal sample height.
@@
     \includegraphics[width=1.0\linewidth]{fig/p3/P864_dv_comparison.pdf}
-    \caption[Vertical derivative]{Vertical derivative grids queried from AD differentiated INR (left) and calculated numerically (right) on the \SI{40}{m} level grid queried from the INR\@.}
+    \caption[Vertical derivative]{Vertical derivative grids queried from AD differentiated INR (left) and calculated numerically (right) on the \SI{40}{m} level grid queried from the INR\@.
+The proposed method has poor vertical gradient representation, possibly due to the nature of aeromagnetic survey design.}
     \label{fig:vert_grad}
@@
 \label{sec:discussion}
-INR has strong learning capacity for the potential field samples in the horizontal plane near the nominal survey altitude, allowing extraction of level grids which are accurate against the reference grid.
+The proposed method has strong learning capacity for the potential field samples in the horizontal plane near the nominal survey altitude, allowing extraction of level grids which are accurate against the reference grid.
 Level grids can be queried at arbitrary heights and cell sizes, with the highest accuracy achieved at the realised nominal survey altitude.
@@
 While quantised grids can be queried at any cell size, short wavelength information beyond the Nyquist limit of the survey line sampling is not predicted.
-
 The current method could include additional target dimensions, which would allow representation learning of vector fields \(\mathbb{R}^{3}\) in three dimensions \(\mathbb{R}^{3}\).
@@
 \[
-    \nabla^2 \phi = 0
+    \nabla^2 \phi = 0,
 \]
-In three dimensions, \cref{eqn:Laplace};
+or denoted in three dimensions,
 \begin{equation}
     \label{eqn:Laplace}
-    \frac{\partial{}^2\phi}{\partial{}x^2} + \frac{\partial{}^2\phi}{\partial{}y^2} + \frac{\partial{}^2\phi}{\partial{}z^2} = 0
+    \frac{\partial{}^2\phi}{\partial{}x^2} + \frac{\partial{}^2\phi}{\partial{}y^2} + \frac{\partial{}^2\phi}{\partial{}z^2} = 0.
 \end{equation}
+Inspired by the approach of \cite{raissiPhysicsinformedNeuralNetworks2019}, a geophysics informed network could include a Laplace criterion,
 
+\begin{equation}
+    \label{eqn:cri_laplace}
+    \mathcal{L}_{PDE} = \frac{1}{S_i}\sum_{i=1}^{S_i} \left(\frac{\partial{}^2f}{\partial{}x^2} + \frac{\partial{}^2f}{\partial{}y^2} + \frac{\partial{}^2f}{\partial{}z^2}\right)^2,
+\end{equation}
+where \(S_i\) indicates the \(i^{th}\) sample point of the field survey \(\phi(x, y, z)\).
+This criterion penalises outputs where Laplace's equation is not satisfied because the sum of partial second derivatives is not close to zero.
+
+%     \mathcal{L}_{PDE} = \lVert{}\frac{\partial{}^2f}{\partial{}x^2} + \frac{\partial{}^2f}{\partial{}y^2} + \frac{\partial{}^2f}{\partial{}z^2}\rVert{}_{2}
 %TODO Confirm logic here: % If Laplace's equation:\( \nabla^2 \phi = 0 \) is satisfied, it is harmonic, and has continuous single valued first derivatives, and has second derivatives.
 % This indicates the function lacks curvature. 
-
 % Blakely:
@@
 % \( \phi(x,y,z) = constant \) is an equipotential surface.
-
 % Numerical methods for potential field continuation are unstable, recognised in the geophysical community by solution divergence and noise in predictions.
-A geophysics informed network could include a Laplace criterion, \cref{eqn:cri_laplace}.
-
-\begin{equation}
-    \label{eqn:cri_laplace}
-    \mathcal{L}_{PDE} = \beta{}\lVert{}\frac{\partial{}^2f}{\partial{}x^2} + \frac{\partial{}^2f}{\partial{}y^2} + \frac{\partial{}^2f}{\partial{}z^2}\rVert{}_{2}
-\end{equation}
-
-As denoted by the \(L^2\) operator \(\lVert{}\cdot{}\rVert{}_{2}\) and weighting \(\beta{}\), this criterion penalises outputs where the sum of partial derivatives is not close to zero.
 

### 2023-09-15 manuscript.tex
Fix bibnames for et al. and logo size
Update abstract and front matter

@@
 \usepackage{thesisstyle}
+\usepackage{unnumberedtotoc}
 \addbibresource{bib/PhD.bib}
@@
         \textbf{The University of Western Australia}
+        \vspace{5 mm}
 
-        \vspace{5 mm}
         School of Earth Sciences
+        \vspace{15 mm}
 
-        \vspace{10 mm}
         \begin{figure}[h]
             \centering{}
-            \includegraphics[scale=0.65]{fig/UWA_FORMAL_PORTRAIT_CMYK}
+            \includegraphics[scale=0.6]{fig/UWA_FORMAL_PORTRAIT_CMYK}
         \end{figure}
@@
 
-\clearpage{}
+% \clearpage{}
 
@@
 \setcounter{page}{1}
-\renewcommand{\thesection}{\Roman{section}}
 
-\section{Thesis Declaration}
+\addsec{\centering{}Abstract}
+Geophysics examines the petrophysical expression of geology within the Earth and is vital for exploring and understanding mineral systems under cover.
+The growing global demand for resources drives new data acquisition, with sensors that return more and higher quality data.
+The challenges and opportunities of big data are not unique to the geosciences, and the development of methods and computing to address these are ubiquitous in the contemporary age of deep learning.
+
+A small but critical component of the geophysical method is the practice of potential field surveying from aircraft, for rapid and extensive coverage of target geology.
+Airborne geophysical surveys are routinely conducted as pre-competitive regional data acquisition to stimulate exploration, or as targeted investigations by the exploration industry.
+% Surveys are also routinely collected on the ground or by satellite, with processing methods and interpretation shared between all forms of acquisition.
+The collected data may contain millions of discrete samples scattered in three dimensions, and their interpretation often relies on regularisation to a quantised grid, allowing digital processing and human or machine interpretation.
+% A constraint on the usefulness of these data is the data resolution, or more precisely, the Nyquist frequency of the grid.
+The limit on information available within gridded data results directly from the spatial sampling density of the originating survey, and the density of cells used to represent the grid raster.
+% The well known geophysics rule of thumb, \emph{a grids cell size should be specified as one-quarter to one-fifth of the line spacing}, has long informed the achievable detail in these survey products.
+However, sampling density is constrained by cultural obstructions and financial constraints, leading to the need to fly the fewest number of lines that can still meet the resolution required to interpret target geological features.
+
+This thesis reports on contributions to two topics in geophysics; enhancing the high-frequency content of gridded potential field data using \emph{super-resolution}; and, learning a representative function of a potential field extent using \emph{implicit neural representation}.
+The first topic enhances the value of geophysical surveys by predicting high-frequency components in sparsely sampled potential field grids.
+The second presents a straightforward neural network framework for high quality grid regularisation, processing, and data integration.
+For each body of work in these topics, real-world geophysical case studies are presented in order to demonstrate the effectiveness and challenges of the method with open access data.
+Each body of work extends deep learning methods described in computer science literature the same year as the development of each respective geophysical method, to keep pace with rapid advances in the field of machine learning.
+
+In the topic of super-resolution frequency enhancement, the first method uses convolutional neural networks to enhance the resolution of real magnetic textures at a fixed four times scale.
+The second method continues to explore the topic of super-resolution, using data gridded from both synthetic and real line data at different line spacings.
+It quantifies the performance of super-resolution upscaling on real-world low-resolution grids with line spacings between \SI{80}{\m} and \SI{480}{\m}, and investigates the useful limits of upscaling using the method.
+
+The second topic explores a method for learning a representation of a potential field extent from scattered real-world survey data by a contemporary neural network.
+The data-driven approach allows the extraction of high-resolution level grids from the learn representation, as well as the rapid analytical calculation of spatial gradients.
+Grid rasters and horizontal gradients calculated with the method very closely match their numerical counterparts, however vertical gradients are not represented well.
+
+Individually the methods developed in this thesis enhance the information extractable from potential field surveys. 
+However, in combination they reflect ongoing advances in deep learning and their extension to challenges and opportunities in geophysics.
+
+\newpage{}
+\addsec{Acknowledgements}
+\dots{}
+
+This research was supported by a Rio Tinto Iron Ore PhD Scholarship.
+
+\newpage{}
+\tableofcontents{}
+% \listoffigures{}
+% \listoftables{}
+
+\newpage{}
+\addsec{Thesis Declaration}
 I, Luke Thomas Smith, certify that:
@@
 \newpage{}
-
-\section{Abstract}
-In the contemporary age of deep learning, namely the frantic and now forever advancing activity emerging from the mid 2010's, geoscience stands to embrace its own big data challenges.
-A small but critical component of the geophysical method is the practice of potential field surveying from aircraft, for rapid and extensive coverage of target geology.
-Airborne geophysical surveys are routinely conducted as pre-competitive regional data acquisition to stimulate exploration, or as targeted investigations by the mineral exploration industry.
-The collected data may contain millions of discrete samples scattered in three dimensions, and their interpretation often relies on regularisation to a quantised grid, allowing digital processing and human or machine interpretation.
-A ubiquitous constraint on the usefulness of these data is the data resolution, or more exactly, the Nyquist frequency of the grid.
-This limit on the high-frequency content available within the grid results directly from the spatial sampling density of the originating survey, and the density of cells used to represent the grid.
-The well known geophysics rule of thumb, \emph{a grids cell size should equal one quarter to one fifth of the line spacing}, has long informed the achievable detail in these survey products.
-
-This thesis reports on two topics in geophysics; enhancing the high-frequency content of survey data using \emph{super-resolution}; and, learning a representative function of a potential field extent using \emph{implicit neural representation}.
-The first has application in enhancing the value of geophysical surveys by extracting greater information from necessarily sparsely sampled potential fields.
-The second topic stands to benefit from ongoing research in deep learning, but may present a straightforward neural network framework for high quality grid regularisation, processing, storage, and data integration.
-For each chapter, real-world geophysical case studies are presented, in order to demonstrate the challenges and effectiveness of the method with currently available open file data.
-
-Chapter one establishes that deep learning can effectively enhance the resolution of real magnetic textures at a fixed four times scale.
-This is further explored in chapter two, explicitly using data gridded from both synthetic and real line data at increasingly wider spacings to achieve both super-resolution on real-world low-resolution data and to investigate the useful limits of upscaling.
-
-Chapter two quantifies the upscaling performance at line spacings between \SI{80}{\m} and \SI{480}{\m} and successfully enhances the resolution of unseen real world survey grids.
-
-Finally, chapter three presents successful representation learning of scattered real-world potential field samples by a neural network, in a framework that allows the extraction of high-resolution level grids and for rapid analytical calculation of spatial gradients.
-
-Similar outcomes to those presented throughout this thesis have been attempted by at-times surprisingly antique machine learning practices, as well as persistently effective numerical methods in the literature.
-However, the deep learning methods adopted within the component chapters of this manuscript have each been selected for their contemporaneity.
-Each chapter investigates the use of deep learning methods from the literature, published in the same year as the drafting of their respective geophysical application chapter.
-The rapid and increasing pace of advancement in deep learning research demands this adherance to the cutting-edge, in order to address the growing magnitudes of data collected and processed within geoscience to address current global challenges.
-
-\tableofcontents{}
-% \listoffigures{}
-% \listoftables{}
-
-\section{Acknowledgements}
-\dots{}
-
-This research was supported by a Rio Tinto Iron Ore PhD Scholarship.
-
-\section{Authorship Declaration}
+\addsec{Authorship Declaration}
 This thesis contains material that has been published or prepared for publication.
@@
 \begin{itemize}
-    \item{}\textbf{Section}: Chapter 1
+    \item{}\textbf{Location in thesis}: Chapter 1
 
@@
           \textbf{Contribution}: The method for was researched, developed, and drafted by L.
-Smith, who also performed revision based on manuscript review from co-authors EJ Holden, D.
+Smith, who also performed revision based on manuscript review from co-authors E.J.
+Holden, D.
 Wedge, T.
-Horrocks and N.
+Horrocks, and N.
 Akhtar.
@@
     \item{}
-    \textbf{Section}: Chapter 2
+          \textbf{Location in thesis}: Chapter 2
 
-    \textbf{Contribution}: Further investigation of super-resolution was initiated, developed, analysed, and drafted by L. Smith, with guidance on manuscript direction from co-authors.
+          \textbf{Contribution}: Further investigation of super-resolution was initiated, developed, analysed, and drafted by L.
+Smith, with guidance on manuscript direction from co-authors E.J.
+Holden, D.
+Wedge, T.
+Horrocks, and N.
+Akhtar.
 
     \item{}
-    \textbf{Section}: Chapter 3
+          \textbf{Location in thesis}: Chapter 3
 
           \textbf{Contribution}: The concept and development of implicit neural representation for geophysics was initiated by L.
-Smith, who performed the subsequent development, analysis, and manuscript authorship with review from co-authors.
+Smith, who performed the subsequent development, analysis, and drafting with manuscript review from co-authors E.J.
+Holden, D.
+Wedge, T.
+Horrocks, and N.
+Akhtar.
 
@@
 
-\subfile{intro}
-\dots{}
+% \subfile{intro}
+% \dots{}
 % \subfile{paper1}
-% % \subfile{paper2}
+% \subfile{paper2}
 % \subfile{paper3}
+% \subfile{conclusions}
 \clearpage{}

### 2023-09-15 paper1.tex
Update preamble
Tweak for manuscript

@@
-\documentclass{article}
-\input{preamble}
+\documentclass[manuscript.tex]{subfiles}
 \begin{document}
-
+\setcounter{chapter}{1}
 \author{\and{Luke Thomas Smith} \and{Eun-Jung Holden} \and{Tom Horrocks} \and{Daniel Wedge} \and{Naveed Akhtar}}
@@
     \SI{80}{\metre} cell size magnetic grids are upsampled to \SI{20}{\metre} cell size using this method, and predicted value and structural accuracy comparisons to the corresponding ground truth \SI{20}{\metre} grids are presented over two test sites in the Eastern Goldfields Superterrane, Western Australia.
-    The method based on RDN achieves 53\% lower error compared to Bicubic interpolation.
+    The method based on RDN achieves \qty{53}{\percent} lower error compared to Bicubic interpolation.
     The case study demonstrates that the deep learning approach can improve the resolution and frequency content of geophysical surveys without requiring additional sampling expense, while remaining accurate against known ground truth surveys.
@@
 \subsection{Resolution in geophysics}
-\label{resingeo}
+\label{sec:resingeo}
 Surveys of the spatial distribution of physical properties of the Earth, such as the magnetic potential field, are common in geoscience.
@@
 These high frequency components reveal localised variations in the surveyed potential field, which provide additional detail on subsurface geological structures and the potential for mineralisation.
-An example of the additional detail provided by a high-resolution grid is provided in \cref{lrandhr}, which shows an \SI{80}{\metre} cell size Total Magnetic Intensity (TMI) grid (a) compared to a \SI{20}{\metre} TMI grid of the same \SI{2560}{\metre} \texttimes\ \SI{2560}{\metre} extent (b), gridded from the same potential field samples, but interpolated to different resolutions.
+An example of the additional detail provided by a high-resolution grid is provided in \cref{fig:lrandhr}, which shows an \SI{80}{\metre} cell size Total Magnetic Intensity (TMI) grid (a) compared to a \SI{20}{\metre} TMI grid of the same \SI{2560}{\metre} \texttimes\ \SI{2560}{\metre} extent (b), gridded from the same potential field samples, but interpolated to different resolutions.
 The increased density of pixels in the high-resolution \SI{20}{\metre} grid allows higher frequencies in the sampled magnetic potential field to be displayed.
@@
         The additional detail shown in the high-resolution grid is made available by the finer cell size, which can convey higher frequency detail, if present in the sampled data.}
-    \label{lrandhr}
+    \label{fig:lrandhr}
 \end{figure}
@@
 \subsection{Resolution and frequency}
-As discussed in \cref{resingeo}, a finer spatial resolution grid (fewer metres per pixel) can convey higher frequency information, due to the higher spatial sampling rate.
-Indeed, a gridded raster with regularly spaced square cells $\Delta x$ has an intrinsic Nyquist wavelength $\lambda _N$, at twice the cell size \labelcref{eq:nyq}.
+As discussed in \cref{sec:resingeo}, a finer spatial resolution grid (fewer metres per pixel) can convey higher frequency information, due to the higher spatial sampling rate.
+Indeed, a gridded raster with regularly spaced square cells \(\Delta x\) has an intrinsic Nyquist wavelength \(\lambda _N\), at twice the cell size \cref{eqn:nyq}.
 
 \begin{equation}
-    \lambda N = 2 \Delta x
-    \label{eq:nyq}
+    \label{eqn:nyq}
+    \lambda{}N = 2 \Delta{}x
 \end{equation}
@@
 In comparison, a low-resolution \SI{80}{\metre} grid (LR) has a Nyquist wavelength of \SI{160}{\metre}.
-Note the Nyquist wavelength is proportional between different cell size grids according to the scale factor S \labelcref{eq:hrn}.
+Note the Nyquist wavelength is proportional between different cell size grids according to the scale factor \(S\) \cref{eqn:hrn}.
 
 \begin{equation}
-    \lambda N_{HR} = \lambda N_{LR} \div S
-    \label{eq:hrn}
+    \label{eqn:hrn}
+    \lambda{}N_{HR} = \lambda{}N_{LR} \div{}S
 \end{equation}
@@
 These modern techniques belong to a family of methods known as deep learning, where features learnt early in the network are leveraged to develop a higher understanding of later features.
-Notable published examples include SRCNN \parencite{dongLearningDeepConvolutional2014}, VDSR \parencite{kimAccurateImageSuperresolution2016}, SRGAN \parencite{ledigPhotorealisticSingleImage2017}, EDSR \parencite{limEnhancedDeepResidual2017}, RDN \parencite{zhangResidualDenseNetwork2018}, and the current state-of-the-art methods, ESRGAN \parencite{wangESRGANEnhancedSuperResolution2018} and ESRGAN+ \parencite{rakotonirinaESRGANFurtherImproving2020}.
+Notable published examples include SRCNN \parencite{dongLearningDeepConvolutional2014}, VDSR \parencite{kimAccurateImageSuperresolution2016}, SRGAN \parencite{ledigPhotorealisticSingleImage2017}, EDSR \parencite{limEnhancedDeepResidual2017}, RDN \parencite{zhangResidualDenseNetwork2018}, and the current state-of-the-art methods, ESRGAN \parencite{wangESRGANEnhancedSuperresolution2018} and ESRGAN+ \parencite{rakotonirinaESRGANFurtherImproving2020}.
 SRGAN and ESRGAN are similar in design to their contemporary counterparts but implement a Generative Adversarial Network (GAN) framework.
@@
         Upsampling to the target output size is performed after the main convolution sequence.
-    Adapted from \cite{wangESRGANEnhancedSuperResolution2018}.
+        Adapted from \cite{wangESRGANEnhancedSuperresolution2018}.
     }
@@
         ESRGAN+ extends ESRGAN with the addition of Gaussian Noise after each basic RDB block (black vectors).
-    Weight factors are indicated by $\beta$ and $\gamma$.
+        Weight factors are indicated by \(\beta{}\) and \(\gamma{}\).
         Noise injection is not used in RDN\@.
@@
 LReLU refers to the Leaky-ReLU activation function.
-    Adapted from \cite{rakotonirinaESRGANFurtherImproving2020}.
-    }
+Adapted from \cite{rakotonirinaESRGANFurtherImproving2020}.}
     \label{fig:convs}
@@
 
-\subsection{Interplation}
+\subsection{Interpolation}
 Increasing the resolution of an image is achievable through computationally inexpensive interpolating filters, such as nearest neighbour or bicubic interpolation.
@@
 
-ESRGAN+, based on ESRGAN \parencite{wangESRGANEnhancedSuperResolution2018}, was chosen as the primary super-resolution CNN architecture for this task due to its reported success in other super-resolution tasks (especially \cite{bodeUsingPhysicsInformedSuperResolution2019} and \cite{leongDeepBedMapDeepNeural2020}) and state of the art results for its original application in image super-resolution.
+ESRGAN+, based on ESRGAN \parencite{wangESRGANEnhancedSuperresolution2018}, was chosen as the primary super-resolution CNN architecture for this task due to its reported success in other super-resolution tasks (especially \cite{bodeUsingPhysicsInformedSuperResolution2019} and \cite{leongDeepBedMapDeepNeural2020}) and state of the art results for its original application in image super-resolution.
 As a Generative Adversarial Network (GAN), it comprises two iteratively trained neural networks, a Generator (G) used to upscale low-resolution inputs, and Discriminator (D), which is trained to improve the performance of the generator.
@@
 
-\begin{figure}[]
+\begin{figure}[hbt]
     \includegraphics[width=\textwidth]{fig/p1/image5.png}
@@
 Training samples were augmented using random 90-degree rotations and flips to encourage a model with rotational and symmetrical invariance to the input images, and their order per epoch was shuffled to improve regularisation and supress overfitting.
-Further measures for the suppression of overfitting inherent to each of the applied architectures are described in their respective manuscripts \parencite{wangESRGANEnhancedSuperResolution2018,zhangResidualDenseNetwork2018}.
+Further measures for the suppression of overfitting inherent to each of the applied architectures are described in their respective manuscripts \parencite{wangESRGANEnhancedSuperresolution2018,zhangResidualDenseNetwork2018}.
 The optimiser used was Adam \parencite{kingmaAdamMethodStochastic2015}.
@@
 In both structural metrics, the result is a combination of localised image luminance, contrast, and structural information.
-A SSIM value of 1 indicates perfect similarity, and values approaching 0 indicate increasing dissimilarity.
+A SSIM value of 1 indicates perfect similarity, and values approaching \num{0} indicate increasing dissimilarity.
 
@@
 
-\begin{figure}
+\begin{figure}[hbt]
     \includegraphics[width=\textwidth]{fig/p1/image6.png}
@@
 
-\Cref{fig:residuals} demonstrates the error residuals between the predicted TMI grids for each upsampling method and the HR ground truth.
+\cref{fig:residuals} demonstrates the error residuals between the predicted TMI grids for each upsampling method and the HR ground truth.
 For the selected tile, the RMSE is best minimised using RDN\textdaggerdbl{}, which also shows the best structural metric performance.
@@
 
-\begin{figure}
+\begin{figure}[hbt]
     \includegraphics[width=\textwidth]{fig/p1/image7.png}
@@
 
-\begin{figure}
+\begin{figure}[hbt]
     \includegraphics[width=\textwidth]{fig/p1/image8.png}
@@
 
-    \caption[Accuracy Metrics]{
-        Accuracy metrics for each upsampling method.
-        The best performing method for each metric is bolded.
-     }
+    \caption[Accuracy Metrics]{Accuracy metrics for each upsampling method. The best performing method for each metric is bolded.}
     \label{tab:metrics}

### 2023-09-18 manuscript.tex
Update abstract
From EJ comments

@@
-% \includeonly{intro}
 \documentclass[12pt,a4paper]{report} %,openright,twoside
 \usepackage{thesisstyle}
-\usepackage{unnumberedtotoc}
 \addbibresource{bib/PhD.bib}
@@
 
-A small but critical component of the geophysical method is the practice of potential field surveying from aircraft, for rapid and extensive coverage of target geology.
-Airborne geophysical surveys are routinely conducted as pre-competitive regional data acquisition to stimulate exploration, or as targeted investigations by the exploration industry.
+Potential field surveying from aircraft provides rapid and extensive coverage of target geology.
+These surveys are routinely conducted as pre-competitive regional data acquisition to stimulate exploration, or as targeted investigations by the exploration industry.
 % Surveys are also routinely collected on the ground or by satellite, with processing methods and interpretation shared between all forms of acquisition.
@@
 % The well known geophysics rule of thumb, \emph{a grids cell size should be specified as one-quarter to one-fifth of the line spacing}, has long informed the achievable detail in these survey products.
-However, sampling density is constrained by cultural obstructions and financial constraints, leading to the need to fly the fewest number of lines that can still meet the resolution required to interpret target geological features.
+However, sampling density suffers various constraints such as cultural obstructions and budget, leading to the need to fly the fewest number of lines that can still meet the resolution required to interpret target geological features.
 
-This thesis reports on contributions to two topics in geophysics; enhancing the high-frequency content of gridded potential field data using \emph{super-resolution}; and, learning a representative function of a potential field extent using \emph{implicit neural representation}.
+This thesis reports on three bodies of work across two topics in geophysics; enhancing the high-frequency content of gridded potential field data using \emph{super-resolution}; and, learning a representative function of a potential field extent using \emph{implicit neural representation}.
 The first topic enhances the value of geophysical surveys by predicting high-frequency components in sparsely sampled potential field grids.
@@
 
-In the topic of super-resolution frequency enhancement, the first method uses convolutional neural networks to enhance the resolution of real magnetic textures at a fixed four times scale.
-The second method continues to explore the topic of super-resolution, using data gridded from both synthetic and real line data at different line spacings.
+In the topic of super-resolution, the first method uses convolutional neural networks to enhance the resolution of real magnetic textures in state magnetic grids at a fixed four times scale.
+This is further explored in the second body of work, where synthetic potential field line data are used for model pretraining, to address the lack of survey data with sufficient line spacing variability.
 It quantifies the performance of super-resolution upscaling on real-world low-resolution grids with line spacings between \SI{80}{\m} and \SI{480}{\m}, and investigates the useful limits of upscaling using the method.
@@
 
-% \subfile{intro}
-% \dots{}
+\subfile{intro}
 % \subfile{paper1}
@@
 % \subfile{paper3}
-% \subfile{conclusions}
-\clearpage{}
-\include{bibliography}
+\subfile{conclusions}
 \end{document}

### 2023-09-18 paper1.tex
Adjust spacings

@@
 \begin{figure}[hbt]
-    \includegraphics[width=\textwidth]{fig/p1/image1.png}
+    \includegraphics[width=\linewidth]{fig/p1/image1.png}
     \caption[Comparison of different resolution grids]{Low resolution \SI{80}{\metre} cell size (a), and high-resolution \SI{20}{\metre} cell size (b) TMI grids over the same extent.
@@
 \begin{figure}
-    \includegraphics[width=\textwidth]{fig/p1/image2.png}
+    \includegraphics[width=\linewidth]{fig/p1/image2.png}
     \caption[The RDN architecture]{The RDN architecture, which acts as the ESRGAN generator.
@@
 \begin{figure}[hbt]
-    \includegraphics[width=\textwidth]{fig/p1/image3.png}
+    \includegraphics[width=\linewidth]{fig/p1/image3.png}
     \caption[Basic Blocks]{Each Basic Block (\cref{fig:rdn}, orange) comprises three weighted Residual Dense Blocks (\cref{fig:convs}).
@@
 \begin{figure}[hbt]
-    \includegraphics[width=\textwidth]{fig/p1/image4.png}
+    \includegraphics[width=\linewidth]{fig/p1/image4.png}
     \caption[RDB convolutional layers]{Each Residual Dense Block (\cref{fig:rdb}, purple) comprises four convolutional layers, with additional learning pathways present as residual connections (black), and dense connections (green).
@@
 \begin{figure}[hbt]
-    \includegraphics[width=\textwidth]{fig/p1/image5.png}
+    \includegraphics[width=\linewidth]{fig/p1/image5.png}
     \caption[Dataset context]{Reserved training/validation and test areas of Eastern Goldfields Superterrane magnetic grid, and their tectonic context.
@@
 \begin{figure}[hbt]
-    \includegraphics[width=\textwidth]{fig/p1/image6.png}
+    \includegraphics[width=\linewidth]{fig/p1/image6.png}
     \caption[Visual inference results]{Visual comparisons of a selected tile from the reserved test region.
@@
 \begin{figure}[hbt]
-    \includegraphics[width=\textwidth]{fig/p1/image7.png}
+    \includegraphics[width=\linewidth]{fig/p1/image7.png}
     \caption[Error residuals map for a selected tile]{Error residuals map for the selected test tile, for each upsampling method; Bicubic (a), RDN\textdaggerdbl{} (b), and ESRGAN+ (c).
@@
 \begin{figure}[hbt]
-    \includegraphics[width=\textwidth]{fig/p1/image8.png}
+    \includegraphics[width=\linewidth]{fig/p1/image8.png}
     \caption[short]{Radially Averaged Power Spectra for the complete test extent shown in \cref{fig:trainvaldata}.
@@
 \begin{figure}[hbt]
-    \includegraphics[width=\textwidth]{fig/p1/image9.png}
+    \includegraphics[width=\linewidth]{fig/p1/image9.png}
     \caption[High Pass filtered results]{High Pass filtered test tile and its upsampled counterparts.
-        The cut-off for the high pass Butterworth filter was selected with wavelength equal to the Nyquist wavelength of the LR grid, i.e. four times the HR Nyquist wavelength
+        The cut-off for the high pass Butterworth filter was selected with wavelength equal to the Nyquist wavelength of the LR grid, i.e.,\ four times the HR Nyquist wavelength
     }
@@
 \begin{figure}[hbt]
-    \includegraphics[width=\textwidth]{fig/p1/image10.png}
+    \includegraphics[width=\linewidth]{fig/p1/image10.png}
     \caption[First Vertical Derivative SR TMI over the Mt Mason resource project]{First Vertical Derivative TMI over the Mt Mason resource project, with the super-resolution predictions (d, e) showing a variety of inference artefacts.
@@
 \begin{figure}[hbt]
-    \includegraphics[width=\textwidth]{fig/p1/image11.png}
-    \includegraphics[width=\textwidth]{fig/p1/image12.png}
+    \includegraphics[width=\linewidth]{fig/p1/image11.png}
+    \includegraphics[width=\linewidth]{fig/p1/image12.png}
     \caption[Jasper Hills Project TMI grids and line profile]{Jasper Hills Project TMI grids (a--e) and line profile (f).

### 2023-09-19 paper1.tex
Fix figures

@@
 \setcounter{chapter}{1}
-\author{\and{Luke Thomas Smith} \and{Eun-Jung Holden} \and{Tom Horrocks} \and{Daniel Wedge} \and{Naveed Akhtar}}
+\author{\and{Luke Thomas Smith} \and{Tom Horrocks} \and{Eun-Jung Holden} \and{Daniel Wedge} \and{Naveed Akhtar}}
 \title{Magnetic grid resolution enhancement using machine learning: A case study from the Eastern Goldfields Superterrane}
@@
 \maketitle{}
+\label{paper1}
 
@@
     Through the application of state-of-the-art deep learning super-resolution architectures, accurate high-resolution grids are predicted from corresponding low-resolution grid priors.
-    Specifically, the RDN and ESRGAN+ neural network architectures, which were originally developed for enhancing images, are applied to enhance magnetic surveys and trained with high-resolution and low-resolution magnetic grids of the same extent.
+    Specifically, the \emph{RDN} and \emph{ESRGAN+} neural network architectures, which were originally developed for enhancing images, are applied to enhance magnetic surveys and trained with high-resolution and low-resolution magnetic grids of the same extent.
     \SI{80}{\metre} cell size magnetic grids are upsampled to \SI{20}{\metre} cell size using this method, and predicted value and structural accuracy comparisons to the corresponding ground truth \SI{20}{\metre} grids are presented over two test sites in the Eastern Goldfields Superterrane, Western Australia.
-    The method based on RDN achieves \qty{53}{\percent} lower error compared to Bicubic interpolation.
+    The method based on \emph{RDN} achieves \qty{53}{\percent} lower error compared to Bicubic interpolation.
     The case study demonstrates that the deep learning approach can improve the resolution and frequency content of geophysical surveys without requiring additional sampling expense, while remaining accurate against known ground truth surveys.
@@
 \begin{figure}[hbt]
-    \includegraphics[width=\linewidth]{fig/p1/image1.png}
+    \includegraphics[width=\linewidth]{fig/p1/lrandhr.jpg}
     \caption[Comparison of different resolution grids]{Low resolution \SI{80}{\metre} cell size (a), and high-resolution \SI{20}{\metre} cell size (b) TMI grids over the same extent.
@@
 Geophysical rasters are created through a process of survey point sampling, grid interpolation, and usually post-process filtering.
-During these processes, the sampled potential field may be subject to destructive Nyquist sampling principles \parencite[16]{dentithGeophysicsMineralExploration2014}, especially due to the original point sampling interval and the cell size (pixel spatial extent) selected for the grid interpolation.
+During these processes, the sampled potential field may be subject to destructive Nyquist sampling principles \parencite[26]{dentithGeophysicsMineralExploration2014}, especially due to the original point sampling interval and the cell size (pixel spatial extent) selected for the grid interpolation.
 The optimal grid cell size is dependent on the sampling interval, and because of this, the highest frequency component preserved in gridded geophysical potential fields is intrinsically limited by the original sampling interval.
@@
 
-\begin{figure}
-    \includegraphics[width=\linewidth]{fig/p1/image2.png}
+\begin{figure}[hbt]
+    \includegraphics[width=\linewidth]{fig/p1/rdn.png}
     \caption[The RDN architecture]{The RDN architecture, which acts as the ESRGAN generator.
@@
 \begin{figure}[hbt]
-    \includegraphics[width=\linewidth]{fig/p1/image3.png}
+    \includegraphics[width=\linewidth]{fig/p1/rdb.png}
     \caption[Basic Blocks]{Each Basic Block (\cref{fig:rdn}, orange) comprises three weighted Residual Dense Blocks (\cref{fig:convs}).
@@
 \begin{figure}[hbt]
-    \includegraphics[width=\linewidth]{fig/p1/image4.png}
+    \includegraphics[width=\linewidth]{fig/p1/convs.png}
     \caption[RDB convolutional layers]{Each Residual Dense Block (\cref{fig:rdb}, purple) comprises four convolutional layers, with additional learning pathways present as residual connections (black), and dense connections (green).
@@
 \begin{figure}[hbt]
-    \includegraphics[width=\linewidth]{fig/p1/image5.png}
+    \centering{}
+    \includegraphics[width=0.75\linewidth]{fig/p1/trainvaldata.png}
     \caption[Dataset context]{Reserved training/validation and test areas of Eastern Goldfields Superterrane magnetic grid, and their tectonic context.
@@
 \begin{figure}[hbt]
-    \includegraphics[width=\linewidth]{fig/p1/image6.png}
+    \includegraphics[width=\linewidth,trim={0 0 0 5mm},clip]{fig/p1/resultsvis.png}
     \caption[Visual inference results]{Visual comparisons of a selected tile from the reserved test region.
@@
 
-\cref{fig:residuals} demonstrates the error residuals between the predicted TMI grids for each upsampling method and the HR ground truth.
+\Cref{fig:residuals} demonstrates the error residuals between the predicted TMI grids for each upsampling method and the HR ground truth.
 For the selected tile, the RMSE is best minimised using RDN\textdaggerdbl{}, which also shows the best structural metric performance.
@@
 \begin{figure}[hbt]
-    \includegraphics[width=\linewidth]{fig/p1/image7.png}
+    \includegraphics[width=\linewidth,trim={0 10mm 0 5mm},clip]{fig/p1/residuals.png}
     \caption[Error residuals map for a selected tile]{Error residuals map for the selected test tile, for each upsampling method; Bicubic (a), RDN\textdaggerdbl{} (b), and ESRGAN+ (c).
@@
 \begin{figure}[hbt]
-    \includegraphics[width=\linewidth]{fig/p1/image8.png}
+    \includegraphics[width=\linewidth]{fig/p1/rapsd.jpg}
     \caption[short]{Radially Averaged Power Spectra for the complete test extent shown in \cref{fig:trainvaldata}.
@@
 \begin{figure}[hbt]
-    \includegraphics[width=\linewidth]{fig/p1/image9.png}
+    \includegraphics[width=\linewidth]{fig/p1/filtered.png}
     \caption[High Pass filtered results]{High Pass filtered test tile and its upsampled counterparts.
@@
 \begin{figure}[hbt]
-    \includegraphics[width=\linewidth]{fig/p1/image10.png}
+    \includegraphics[width=\linewidth,trim={0 0 0 0},clip]{fig/p1/jhillvis.jpg}
     \caption[First Vertical Derivative SR TMI over the Mt Mason resource project]{First Vertical Derivative TMI over the Mt Mason resource project, with the super-resolution predictions (d, e) showing a variety of inference artefacts.
@@
 \begin{figure}[hbt]
-    \includegraphics[width=\linewidth]{fig/p1/image11.png}
-    \includegraphics[width=\linewidth]{fig/p1/image12.png}
+    \includegraphics[width=\linewidth,trim={0 0 0 5mm},clip]{fig/p1/jhilldykes.png}
+    \centering
+    \includegraphics[width=0.7\linewidth]{fig/p1/transectp.png}
     \caption[Jasper Hills Project TMI grids and line profile]{Jasper Hills Project TMI grids (a--e) and line profile (f).
@@
 
-\section{Declaration of Competing Interest}
-The authors declare the following financial interests / personal relationships which may be considered as potential competing interests: This work was supported by a Rio Tinto Iron Ore PhD scholarship.
+% \section{Declaration of Competing Interest}
+% The authors declare the following financial interests / personal relationships which may be considered as potential competing interests: This work was supported by a Rio Tinto Iron Ore PhD scholarship.
 

### 2023-09-19 intro.tex
Prepare front matter
Begin drafting introduction

@@
 
-Then we wrote the entire thesis.
+\section{Introduction} %  indicates that an original and coherent argument is being developed and that the research is making a contribution to existing literature
+% outline the topic, justify the research, identify research aims and outline thesis structure
+\subsection{Big geodata}
+(2 pg)
+%% Airborne surveys are routinely conducted as pre-competitive regional data acquisition to stimulate exploration, or as targeted investigations by the exploration industry.
+%% Surveys are also routinely collected on the ground or by satellite, with processing methods and interpretation shared between all forms of acquisition.
+%% The collected data may contain millions of discrete samples scattered in three dimensions,
+%% Interpretation often relies on regularisation to a quantised grid, allowing digital processing and human or machine interpretation.
+The subsurface continuation of exposed geology can be extrapolated and interpolated using structures in the magnetic responses.
+For this reason, magnetic field survey grids remain a standard tool in the geological mapping and interpration toolbox. 
+Open file data from government or publicly released commercial surveys form part of the greenfields exploration.
+Case studies on open file data are presented throughout to develop the method.
+%% Budgets: Flying, handling, storage,
 
-Are geophysical grids natural signals?
--   Lipschitz smoothness
--   Fourier power spectra fall-off
+% Enhance the information extractable from potential field surveys.
+% In combination they reflect ongoing advances in deep learning and,
+% their extension to challenges and opportunities in geophysics.
+
+\subsection{Research Contributions and Thesis Structure}
+% paper or series of papers suitable for publication in scholarly journals; or a combination of published and unpublished work
+This thesis is presented as a series of papers which are published or in-preparation for publication in scholarly journals.
+Chapter 1 presents a published manuscript, typefaced for consistency with the remaining thesis.
+Chapters 2 and 3 present original research in preparation as articles for publication.
+A discussion arising from these works is provided in chapter 4, and a brief overview of the content and contributions of each chapter is given here.
+
+Chapters 2 and 3
 

### 2023-09-19 manuscript.tex
Begin drafting introduction

--- 2023-09-15 manuscript.tex
@@
 \addsec{Authorship Declaration}
+This research was carried out at the University of Western Australia.
 This thesis contains material that has been published or prepared for publication.
@@
 
-          \textbf{Contribution}: The method for was researched, developed, and drafted by L.
-Smith, who also performed revision based on manuscript review from co-authors E.J.
+          \textbf{Contribution}: The method was researched, developed, analysed and drafted by L.
+Smith, who performed revision based on manuscript review from co-authors E.J.
 Holden, D.
@@
 
-\noindent{}Sections comprising manuscripts prepared for publication:
+\noindent{}Sections comprising manuscripts in preparation:
 \begin{itemize}
@@
 
-% \subfile{intro}
-% \dots{}
-% \subfile{paper1}
+\subfile{intro}
+\subfile{paper1}
 % \subfile{paper2}
 % \subfile{paper3}
-% \subfile{conclusions}
-\clearpage{}
-\include{bibliography}
+\subfile{discussion}
 \end{document}

### 2023-09-19 discussion.tex

\documentclass[manuscript.tex]{subfiles}
\begin{document}

\section{Discussion} %brings together the key findings and contributions of the research as a whole
% provide a synthesis of the work as a whole presented in the body of the thesis.
% It is important that this final chapter demonstrates the collective contribution to knowledge provided by the research described in the thesis and provide overall conclusions that address the research aims.

One of the challenges identified in \cref{paper1} was the need for large extents of suitable training data.
During the initiation of \cref{paper2}, a large amount of geologically varied synthetic training data was released as \emph{the Noddyverse} \parencite{jessellNoddyverseMassiveData2022}.
The method for creating synthetically sampled line profiles form potential field grids, like those available in the Noddyverse, can be extended and used to train the networks described in \cref{paper1}

Throughout this thesis, methods developed in computer vision research for natural images have been extended to geophysical grid rasters.
Despite the success of the contributed methods, an important question has remained unaddressed.
Do grid rasters in potential field geophysics share the same properties as natural images?
More precisely, \emph{Are potential field grids natural signals?}
If so, it can be expected that future methods in deep learning developed for natural images will be readily extensible to Geophysics.
\Textcite{donohoCompressedSensing2006}

\subsection{Are potential field grids natural signals?}
% Questions:
% Are geophysical grids natural signals?
% -   Lipschitz smoothness
% -   Fourier power spectra fall-off
% -   There's a citation in Compressed sensing 2006 about natural signals, from Donohan or something.

\end{document}

### 2023-09-19 manuscript.tex

--- 2023-09-18 manuscript.tex
@@
 \subfile{intro}
-% \subfile{paper1}
+\subfile{paper1}
 % \subfile{paper2}
 % \subfile{paper3}
-\subfile{conclusions}
+\subfile{discussion}
 \end{document}

### 2023-09-19 intro.tex
Structure heading levels and titles

@@
 
-\section{Introduction} %  indicates that an original and coherent argument is being developed and that the research is making a contribution to existing literature
+% \section{Introduction} %  indicates that an original and coherent argument is being developed and that the research is making a contribution to existing literature
 % outline the topic, justify the research, identify research aims and outline thesis structure
-\subsection{Big geodata}
-(2 pg)
+\section{Big geodata} %(2 pg)
 %% Airborne surveys are routinely conducted as pre-competitive regional data acquisition to stimulate exploration, or as targeted investigations by the exploration industry.
@@
 
-\subsection{Research Contributions and Thesis Structure}
+\section{Research Contributions and Thesis Structure}
 % paper or series of papers suitable for publication in scholarly journals; or a combination of published and unpublished work
 This thesis is presented as a series of papers which are published or in-preparation for publication in scholarly journals.
-Chapter 1 presents a published manuscript, typefaced for consistency with the remaining thesis.
-Chapters 2 and 3 present original research in preparation as articles for publication.
-A discussion arising from these works is provided in chapter 4, and a brief overview of the content and contributions of each chapter is given here.
+\Cref{paper1} presents a published manuscript, typefaced for consistency with the remaining thesis.
+cref{paper2, paper3} present original research in preparation as articles for publication.
+A discussion arising from these works is provided in \cref{discussion}, and a brief overview of the content and contributions of each chapter is given here.
 
-Chapters 2 and 3
+Cref{paper2, paper3}
 

### 2023-09-19 manuscript.tex
Use subdirectory for non-chapter figures
Structure heading levels and titles

@@
             \centering{}
-            \includegraphics[scale=0.6]{fig/UWA_FORMAL_PORTRAIT_CMYK}
+            \includegraphics[scale=0.6]{fig/etc/UWA_FORMAL_PORTRAIT_CMYK}
         \end{figure}
@@
 
+\chapter{Introduction}
 \subfile{intro}
+
+\chapter{Magnetic Grid Resolution Enhancement using Machine Learning}
+This chapter has been reproduced from the following peer reviewed publication. Formatting has been adjusted for consistency.
+
+Smith, L., Horrocks, T., Holden, E.-J., Wedge, D., Akhtar, N., 2022.
+Magnetic grid resolution enhancement using machine learning: A case study from the Eastern Goldfields Superterrane.
+Ore Geology Reviews 150, 105119.
+https://doi.org/10.1016/j.oregeorev.2022.105119 
 \subfile{paper1}
+
+\chapter{A Line Spacing Method for Super-resolution of Geophysical Surveys}
 % \subfile{paper2}
+
+\chapter{Implicit Neural Representation for Potential Field Geophysics}
 % \subfile{paper3}
+
+\chapter{Discussion}
 \subfile{discussion}
+
 \end{document}

### 2023-09-19 discussion.tex

@@
 \begin{document}
-
-\section{Discussion} %brings together the key findings and contributions of the research as a whole
+\label{discussion}
+\section{Contemporary Advances in Machine Learning} %brings together the key findings and contributions of the research as a whole
 % provide a synthesis of the work as a whole presented in the body of the thesis.
@@
 One of the challenges identified in \cref{paper1} was the need for large extents of suitable training data.
-During the initiation of \cref{paper2}, a large amount of geologically varied synthetic training data was released as \emph{the Noddyverse} \parencite{jessellNoddyverseMassiveData2022}.
-The method for creating synthetically sampled line profiles form potential field grids, like those available in the Noddyverse, can be extended and used to train the networks described in \cref{paper1}
+During the initiation of cref{paper2}, a large amount of geologically varied synthetic training data was released as \emph{the Noddyverse} \parencite{jessellNoddyverseMassiveData2022}.
 
+\section{RDN and ESRGAN for super-resolution with line spacing varied data}
+The method for creating synthetically sampled line profiles form potential field grids, like those available in the Noddyverse, can be extended and used to train the networks described in \cref{paper1}.
+The resulting RDN and ESRGAN models can be compared (at 4 times scale) with the LTE model.
+
+\section{Are potential field grids natural signals?}
 Throughout this thesis, methods developed in computer vision research for natural images have been extended to geophysical grid rasters.
@@
 
-\subsection{Are potential field grids natural signals?}
 % Questions:

### 2023-09-20 paper3.tex
Continue to address NA comments

@@
     The recent use of spatial coordinate features in multilayer perceptron (MLP) neural networks provides opportunities for novel applications in potential field geophysics.
-    So-called coordinate MLP networks allow for learning a representative function of potential fields from their surveyed samples and locations.
-    Using this new paradigm of encoding spatial information within a neural network enables new methods for working with potential field survey data.
-    We present a novel application of implicit neural representation to potential fields, demonstrate the quality of the learnt implicit function by encoding real airborne geophysical survey line data, predict constant level grids, and compare the result to grid data processed with a traditional workflow.
-    We further demonstrate processing the learnt function directly in the continuous domain using automatic differentiation, with the same framework used to train the neural network.
-    %TODO too much detail in abstract here
-    For example, directional gradients are calculated in the continuous domain prior to grid quantisation, and therefore without the associated loss of high-resolution content imposed by gridding.
-    The training process requires only the sample coordinates and recorded potential field for a single survey extent and can be applied to various geophysical techniques including magnetics and gravity.
+    So-called coordinate MLP networks allow for learning a representative function of potential fields from their surveyed samples.
+    % Using this new paradigm of encoding spatial information within a neural network enables new methods for working with potential field survey data.
+    We present a novel method for implicit neural representation for potential fields, demonstrate the quality of the learnt implicit function by encoding real airborne geophysical survey line data, predict constant level grids, and compare the result to grid data processed with a traditional workflow.
+    We further demonstrate the analytical calculation of gradients directly in the continuous domain using automatic differentiation, with the same framework used to train the neural network representation.
+    Level grids queried from the learnt representation closely match the reference grid product, with a peak signal to noise ratio of 40 dB.
+    Horizontal gradients calculated with this method are accurate against numerically derived gradients, while the vertical gradient is a poor match.
+    The training process is rapid, and only requires recorded samples from a single survey extent.
 \end{abstract}
@@
 Geophysical potential fields are routinely collected and used to assist the understanding of the subsurface for geoscience and mineral exploration.
-When surveying these fields, which are continuous functions in three dimensions, sample locations are scattered in x, y, and z, despite best efforts to conform to a regular grid or line sample regime.
-These scattered data are typically regularised to a quantised grid, which reduces high frequency information and gives rise to spurious artefacts that are a product of the gridding process, not the surveyed field.
+When surveying these fields, which are continuous functions in three dimensions, sample locations are scattered in x, y, and z, despite best efforts to conform to a regularly spaced line or grid acquisition plan.
+These scattered data are typically regularised to a quantised grid for subsequent interpretation, which imposes a new limit on high frequency content and gives rise to spurious artefacts that are a product of the gridding process, not the surveyed field.
+% The interpolation process may
 
@@
 We present a novel method of encoding a representation of a geophysical potential field using INR\@.
-%TODO "used to demonstrate" poor
-This method is used to demonstrate a novel method of creating level grids from scattered aeromagnetic data.
+This method contributes a novel method of creating level grids from scattered aeromagnetic data.
 In our method, due to using a continuous coordinate representation, there is no dependency on grid quantisation from an initial cell size selection.
@@
 For the task of level grid prediction, the PSNR similarity between a case study reference grid and the proposed method is \SI{40}{\dB}.
-Additionally, directional derivatives of the implicit representation calculated numerically and using automatic differentiation are shown, with average residuals of \SI{0.4} and \SI{0.8}{nT/m} for the easting and northing derivatives respectively, albeit vertical derivative performance remains limited.
+Additionally, directional derivatives of the implicit representation calculated numerically and using automatic differentiation are shown, with average residuals of \SI{0.4} and \SI{0.8}{\nano\tesla\per\m} for the easting and northing derivatives respectively, albeit vertical derivative performance remains limited.
 
-INR and CMLP have recently emerged in the literature, so our proposed method stands to benefit from ongoing research in these highly active fields.
+INR and CMLP have recently emerged in the literature, and our proposed method stands to benefit from ongoing research in these highly active fields.
 
@@
 
+In geoscience, INR has been used for geological modelling \parencite{hillierGeoINRImplicitNeural2023}, where the existing implicit interpolation approaches.
+
 CMLP networks for INR can be compared to compressed sensing \parencite{candesIntroductionCompressiveSampling2008} for their ability to recover accurate grids from sparsely sampled geophysics samples.
@@
     \caption[Overview of the proposed method]{Overview}
-
     \label{fig:overview}
@@
 The case study is performed using data from the 2002 Wolfe Creek meteorite impact magnetic survey \parencite{wolfecreek2019}.
-This high-resolution survey contains \SI{402}{line-kilometres} of data at \SI{50}{\m} line spacing with a nominal terrain clearance of \SI{40}{\m}, with line data collected on North-South transects.
+This high-resolution survey contains \qty{402}{line-kilometres} of data at \SI{50}{\m} line spacing with a nominal terrain clearance of \SI{40}{\m}, with line data collected on North-South transects.
 Prominently featured in the survey are the circular crater rim, and two East-West trending linear dunes to the North of the survey extent.
@@
 Both geographic and projected coordinate systems can be used, provided the query coordinates for inference match those used during training.
-The three spatial coordinate dimensions are independently and linearly min-max normalised between -1 and 1.
+The three spatial coordinate dimensions are independently and linearly min-max normalised between \num{-1} and \num{1}.
 While this means the axes in the latent spatial domain may be compressed relative to each other axis, the inverse normalisation process returns proportionality between axes.
-The case study data do not span a large or magnetically varying geological extent, hence it is sufficient to use simple min-max normalisation for the magnetic field data within the global extent of the survey samples, here between -1 and 1.
+The case study data do not span a large or magnetically varying geological extent, hence it is sufficient to use simple min-max normalisation for the magnetic field data within the global extent of the survey samples, here between \num{-1} and \num{1}.
 If extensive or complexly varying magnetic provinces were present within the dataset, a normalisation method more robust to outliers may be required.
-
-The \SI{76420}{} sample points contained within the case study line data are split, with \qty{70}{\percent} used for training, and a random \qty{20}{\percent} of the remaining points are reserved to validate the model performance during training.
+The \num{76420} sample points contained within the case study line data are split, with \qty{70}{\percent} used for training, and a random \qty{20}{\percent} of the remaining points are reserved to validate the model performance during training.
 Inference is performed by querying novel coordinates within the learnt domain, here at regularly spaced grid intervals for comparison with standard grid regularisation methods.
@@
 The CMLP architecture comprises a simple fully connected network with \(n\) hidden layers, each with \(m\) neurons, presented within \cref{fig:overview}.
-Comparison of recently proposed activatons for CMLP is performed in \cref{saragadamWIREWaveletImplicit2023}, where increasing both \(n\) and \(m\) increases the capacity of the model, at the cost of computational requirements.
-
-The sinusoidal activation of \cite{sitzmann2019siren} is used.
-High quality implicit representation has been achieved in contemporary INR research with only several hidden layers, typically between 3 and 8.
-The presented method uses 8 hidden layers and 256 neurons per layer.
-%per naveed: Why choose these? Why choose the specific input output layer sizes?
+Comparison of recently proposed activatons and hyperparameters for CMLP is performed by \textcite{saragadamWIREWaveletImplicit2023}, where increasing both \(n\) and \(m\) increases the capacity of the model, at the cost of computational requirements.
+High quality implicit representation is typically achievable with the number hidden layers between \num{3} and \num{8}, and number of neurons per layer up to \num{256}.
+Empirically, the quality of the high-resolution representation continued to improve with increasing both \(n\) and \(m\).
+Therefore, the presented method uses \num{8} hidden layers and \num{256} neurons per layer, which achieves good quality results in rapid time and within the system memory constraints.
+The sinusoidal activation of \textcite{sitzmann2019siren} is used.
+The WIRE or Gaussian activations were empirically less robust to hyperparameter selection, and did not return high-quality representation for the magnetic geophysics grids.
 
@@
 For low-resolution inputs the entire cell coordinate and cell value dataset fits within GPU memory for batch gradient descent.
-The Wolfe Creek meteorite impact crater case study line data has , and the Geoscience Australia provided reference grid has a resolution of 446 \(\times{}\) 445 cells.
+The Wolfe Creek meteorite impact crater case study line data has \num{76420} sample points, and the Geoscience Australia provided reference grid has a resolution of \numproduct{446 x 445} cells.
 The case study line data easily fit into available graphics memory, and can be trained using batch gradient descent.
@@
 Training was performed on an Intel i9-10900KF workstation with an Nvidia RTX 3090 24 GB GPU\@.
-A highly accurate representation can be learned within \SI{5000}{epochs} using the Adam optimiser, for a duration in the order of \SI{60}{seconds}.
-The objective function comprises \(L^2\) loss between the input and predicted field values (\cref{eqn:cri}).
+A highly accurate representation can be learned within \qty{5000}{epochs} using the Adam optimiser, for a duration in the order of \qty{60}{seconds}.
+The objective function comprises \(L^2\) loss between the input and predicted field values \(u\),
 
@@
     \label{eqn:cri}
-    \mathcal{L}_{Total} = \lVert{}u_{input} - u_{pred}\rVert{}_{2} % + \beta{} \lVert{}\frac{\partial^{2}{u_{pred}}}{\partial{}\phi{}_{pred}^{2}}\rVert{}_{2}
+    \mathcal{L}_{Total} = \lVert{}u_{input} - u_{pred}\rVert{}_{2}. % + \beta{} \lVert{}\frac{\partial^{2}{u_{pred}}}{\partial{}\phi{}_{pred}^{2}}\rVert{}_{2}
 \end{equation}
 
-The OneCycle learning rate scheduler \parencite{smithSuperconvergenceVeryFast2018} with a maximum rate of \(1\times{}10^{-4}\) is used to provide fine tuning at low learning rates toward the end of training.
+The OneCycle learning rate scheduler \parencite{smithSuperconvergenceVeryFast2018} with a maximum rate of \num{1e-4} is used to provide fine tuning at low learning rates toward the end of training.
+The very low learning rates in the late stages of training significantly contribute to the quality of the representation when compared to a constant learning rate.
 Convergence of the network is shown in \cref{fig:convergence}.
@@
 That is, to directly sample \(\nabla{}\phi{}_{(x,y,z)}\) at \({(x, y, z)}_1 \dots {(x,y,z)}_n\).
-%TODO we dont show these Higher orders - should we?
-Higher order derivatives are calculated using AD in the same manner.
+Higher order derivatives can be calculated using AD in the same manner, but are not presented here.
 
@@
 
-\Cref{fig:grid} shows the INR queried at \(z=\SI{40}{\meter}\), which is the nominal terrain clearance of the survey.
+\Cref{fig:grid} shows the INR queried at \(z=\SI{40}{\m}\), which is the nominal terrain clearance of the survey.
 A good qualitative match is achieved between the GA reference grid and the grid queried from the implicit representation, which successfully reconstructs the linear dune features and circular rim features.
@@
     \includegraphics[width=1.0\linewidth]{fig/p3/P864_grid_comparison_40m.pdf}
-    \caption[Grid prediction (40 m)]{Comparison between the reference grid processed by Geoscience Australia (left) and the constant level grid queried from the INR at \SI{40}{\m} (middle).
+    \caption[Grid prediction at the nominal altitude]{Comparison between the reference grid processed by Geoscience Australia (left) and the constant level grid queried from the INR at \SI{40}{\m} (middle).
 The residuals are shown for areas containing reference data (right), with a range of ±2 standard deviations of values in the reference grid.}
@@
     \includegraphics[width=1.0\linewidth]{fig/p3/P864_grid_comparison_35m.pdf}
-    \caption[Grid prediction (35 m)]{A constant level grid queried from the INR at the height of \SI{35}{\m} (middle).}
+    \caption[Grid prediction outside the nominal altitude]{A constant level grid queried from the INR at the height of \SI{35}{\m} (middle).}
     % AWAGS is 80 m, but we see nothing useful at 80m
@@
 While horizontal derivatives queried from the INR correspond well to numerical derivatives calculated on the \SI{40}{\m} level grid in \cref{fig:hori_grad}, the vertical derivative suffers poor performance \cref{fig:vert_grad}.
-This correlates with the poor continuation performance of model when predicting level grids several meters or more beyond the nominal sample height.
+This correlates with the poor continuation performance of model when predicting level grids several metres or more beyond the nominal sample height.
 This is interpreted as the presented model having a limited capacity to extrapolate, and learning a poor representation of the vertical component of the potential field, which we further discuss in \cref{sec:discussion}
@@
     \includegraphics[width=1.0\linewidth]{fig/p3/P864_dv_comparison.pdf}
-    \caption[Vertical derivative]{Vertical derivative grids queried from AD differentiated INR (left) and calculated numerically (right) on the \SI{40}{m} level grid queried from the INR\@.
+    \caption[Vertical derivative]{Vertical derivative grids queried from AD differentiated INR (left) and calculated numerically (right) on the \SI{40}{\m} level grid queried from the INR\@.
 The proposed method has poor vertical gradient representation, possibly due to the nature of aeromagnetic survey design.}
@@
 \end{equation}
+
 Inspired by the approach of \cite{raissiPhysicsinformedNeuralNetworks2019}, a geophysics informed network could include a Laplace criterion,
-
 \begin{equation}
@@
 \section{Conclusions}
-High-resolution implicit neural representation of potential field geophysics surveys is achieved with the use of coordinate MLP neural networks for INR.
+High-resolution implicit neural representation of potential field geophysics surveys is achieved with the use of coordinate MLP neural networks for INR\@.
 Resolution in the representation is limited by network capacity, rather than initial grid cell size selection during regularisation.

### 2023-09-21 discussion.tex
Add chapter labels and progress discussion

@@
 
-One of the challenges identified in \cref{paper1} was the need for large extents of suitable training data.
+One of the challenges identified in cref{paper1} was the need for large extents of suitable training data.
 During the initiation of cref{paper2}, a large amount of geologically varied synthetic training data was released as \emph{the Noddyverse} \parencite{jessellNoddyverseMassiveData2022}.
@@
 The resulting RDN and ESRGAN models can be compared (at 4 times scale) with the LTE model.
+
+\section{Informed Neural Networks}
+Cref{paper3} introduced to the thesis the concept of physics informed neural networks, however the .
+The mechanism of informing a network is the design a criterion to impose a specific condition, which matches \emph{a priori} property of the output.
+Indeed, we can extend the concept of informing a network to the use of generative adversarial networks in cref{paper1}.
+A criterion is calculated, in this case \emph{discriminator loss}, using a classification network preconditioned to arbitrarily identify images as `realistic' or `not realistic'.
+Using bespoke or learnt criterions greatly assists with learning high quality models, and assists with the paucity of ground truth samples in geoscience.
 

### 2023-09-22 manuscript.tex
Merge branch 'main' into paper2

@@
 \chapter{Magnetic Grid Resolution Enhancement using Machine Learning}
+\label{paper1}
 This chapter has been reproduced from the following peer reviewed publication. Formatting has been adjusted for consistency.
@@
 \chapter{A Line Spacing Method for Super-resolution of Geophysical Surveys}
+\label{paper2}
 % \subfile{paper2}
@@
 \chapter{Implicit Neural Representation for Potential Field Geophysics}
+\label{paper3}
 % \subfile{paper3}

### 2023-09-29 discussion.tex
Work on intro and discussion

--- 2023-09-19 discussion.tex
@@
 
-\section{Discussion} %brings together the key findings and contributions of the research as a whole
+%brings together the key findings and contributions of the research as a whole
 % provide a synthesis of the work as a whole presented in the body of the thesis.
-% It is important that this final chapter demonstrates the collective contribution to knowledge provided by the research described in the thesis and provide overall conclusions that address the research aims.
+% It is important that this final chapter demonstrates the collective contribution to knowledge provided by the research described in the thesis,
+% and provide overall conclusions that address the research aims.
 
-One of the challenges identified in \cref{paper1} was the need for large extents of suitable training data.
-During the initiation of \cref{paper2}, a large amount of geologically varied synthetic training data was released as \emph{the Noddyverse} \parencite{jessellNoddyverseMassiveData2022}.
-The method for creating synthetically sampled line profiles form potential field grids, like those available in the Noddyverse, can be extended and used to train the networks described in \cref{paper1}
+\section{Summary}
+This thesis presented contemporary methods in deep learning to address the need for modern data driven applications in geoscience.
+By including both synthetic and real survey data for training and case studies, it was established that the methods could generalise to real-world applications.
 
-Throughout this thesis, methods developed in computer vision research for natural images have been extended to geophysical grid rasters.
+The proposed super-resolution (SR) method explored in cref{paper1, paper2} significantly enhanced gridded low-resolution survey data by predicting grid values that contain accurate high-frequency information.
+After establishing the feasibility of geophysics super-resolution in cref{paper1}, an updated neural network and new dataset were developed in cref{paper2}, where simulated line profile surveys create training data with the low-resolution transform encountered in real world exploration geophysics.
+The use of synthetic data to train a baseline model addresses the cost of training data acquisition, as well as opens avenues for targeted geological domain specific applications.
+
+Cref{paper3} used coordinate multilayer pereceptron neural networks to learn a representation of the function that describes a surveyed potential field extent.
+These networks are highly suited for processing spatial data such as point sampled geophysics surveys.
+The applications developed in cref{paper3} were predicting a regularly spaced grid from scattered point data, and calculating derivatives of the potential field representation, both fundamental to interpretation and processing in geophysics.
+By commencing the methods from point sample data, the number of individual processing steps is reduced, and the application is fully trainable.
+The neural network approach developed in cref{paper3} uses coordinate MLP for implicit representation, a currently burgeoning field of research in computer science, and it is hoped that the proposed trainable approach for geophysics point data will prompt further development of geoscience applications in the implicit neural network domain.
+
+\section{The case for super-resolution}
+As ever, all models are wrong, but some models are useful, and this extends to super-resolution imputation.
+I envision one use-case for SR is to increase confidence in interpreting low-resolution magnetic features for geological mapping. 
+When a cautious domain expert encounters low-resolution grid data, they may interpret which gridding method was used, the line spacing and direction, and form their understanding of potential aliasing and spurious anomalies in the grid accordingly.
+Assisted by this understanding, they can infer geological features with varying degrees of confidence.
+Low confidence features which are obscured by low-resolution data will be alterered, constructively or destructively, by the SR method.
+The domain expert can then use this information to reassure or reassess the original low-resolution grid.
+Because it shares the same modality, super-resolution data can be readily trialed in place of existing low-resolution data used in automated analysis and machine processing tools.
+It is expected that the enhanced appearance of features will generally improve the performance of subsequent analysis tasks on the grid raster.
+
+At the same time, it was seen in both cref{paper1, paper2} that super-resolution predictions can be misleading or entirely incorrect.
+The examples being the additional noise and implementation artefacts common in SR inferenece, as well as the enhancement of incorrect features in low-resolution data such as the aliased geological strike.
+Used blindly or without characterisation, these tools may inspire false confidence in the interpreter.
+I recommend a cautious approach in the use of SR\@; begin with a detailed interpretation of the low-resolution data, then enhance that understanding with the super-resolution product.
+
+\section{Revisiting Chapter 1}
+The method developed in cref{paper2} for creating sampled line profiles from potential field grids can be extended and used to train the networks described in cref{paper1}.
+The resulting RDN and ESRGAN models can be compared with the LTE model described in cref{paper2}, although the fixed factor upscaling block in the earlier networks limits this comparison to 4x scale.
+\Cref{fig:rdncomp} shows that RDN and ESRGAN are both highly performant for the task of predicting accurate features when upscaling \SI{320}{\m} data to \SI{40}{\m} line spacing.
+It can be inferred that the challenge of super-resolution is predominantly a question of suitable and sufficient training data, and less constrained to neural network choices.
+
+\begin{figure}[hbt]
+    \includegraphics[width=\linewidth]{fig/etc/TMI Comparison_23.pdf} % TODO Update for RDN, ESRGAN, LTE, ~3 hours ea.
+    \caption{}
+    \label{fig:rdncomp}
+\end{figure}
+
+\section{Synthetic data in geoscience}
+One of the challenges identified in cref{paper1} was the need for large extents of suitable training data.
+This applies to many machine learning tasks in geoscience.
+During the preparation of cref{paper2}, a large and varied synthetic geology training dataset was released \parencite{jessellNoddyverseMassiveData2022}.
+This collection of labelled petrophysical voxel models and associated geophysical forward models provides many opportunities beyond those explored in this thesis.
+When taking advantage of transfer learning for pre-training, synthetic data can increase the generalisability of models for real data, as seen in cref{paper2}.
+
+\section{Informed Neural Networks}
+There are controls on the learning of a neural network beyond the training data samples.
+Cref{paper3} introduced to the thesis the concept of physics informed neural networks, in the form of a criterion to impose a specific constraint.
+For PINNs, this criterion enforces \emph{a priori} physical properties of the approximated function.
+It is possible to broaden the definition and extend the concept of informed networks to the use of generative adversarial networks in cref{paper1}.
+In these networks, the informing method is termed \emph{discriminator loss}, and is performed by a classification network preconditioned to identify images as `realistic' or `not realistic'.
+Using crafted or learnt criterions to inform a neural network greatly assists with learning high quality models, and there is a stark contrast between the well-understood physical principles and the paucity of ground truth samples in geoscience.
+
+\section{Are potential field grids natural signals?}
+Throughout this thesis, the methods developed for geophysical data have been extended from computer vision research developed for natural images.
 Despite the success of the contributed methods, an important question has remained unaddressed.
-Do grid rasters in potential field geophysics share the same properties as natural images?
-More precisely, \emph{Are potential field grids natural signals?}
-If so, it can be expected that future methods in deep learning developed for natural images will be readily extensible to Geophysics.
-\Textcite{donohoCompressedSensing2006}
+\emph{Are potential field grids natural images?}
+If so, it can be predicted that future methods developed in computer vision for natural images will be readily extensible to geophysics.
+Studies into the statistics of natural images have been performed \parencite{simoncelliNaturalImageStatistics2001,rudermanStatisticsNaturalImages1994,tolhurstAmplitudeSpectraNatural1992}.
+\Textcite{lecunDeepLearning2015} - CNN take advantage of ... natural signals.
 
-\subsection{Are potential field grids natural signals?}
 % Questions:

### 2023-09-29 intro.tex
Work on intro and discussion

@@
 \section{Big geodata} %(2 pg)
+
+The subsurface continuation of exposed geology can be extrapolated and interpolated using structures delineated by a regions magnetic potential field anomaly.
+For this reason, magnetic field survey grids are commonly used by geophysicists for geological mapping and interpretation.
+Aircraft are used in exploration geophysics to undertake rapid and extensive surveys, with a predictable cost.
+
 %% Airborne surveys are routinely conducted as pre-competitive regional data acquisition to stimulate exploration, or as targeted investigations by the exploration industry.
@@
 %% Interpretation often relies on regularisation to a quantised grid, allowing digital processing and human or machine interpretation.
-The subsurface continuation of exposed geology can be extrapolated and interpolated using structures in the magnetic responses.
-For this reason, magnetic field survey grids remain a standard tool in the geological mapping and interpration toolbox. 
 Open file data from government or publicly released commercial surveys form part of the greenfields exploration.
@@
 cref{paper2, paper3} present original research in preparation as articles for publication.
-A discussion arising from these works is provided in \cref{discussion}, and a brief overview of the content and contributions of each chapter is given here.
+A discussion arising from these works is provided in cref{discussion}, and a brief overview of the content and contributions of each chapter is given here.
 

### 2023-10-01 authorship_declaration.tex
Move authorship declaration to separate file
This make is easier to get signatures and include.

--- 2023-09-19 manuscript.tex
@@
-\documentclass[12pt,a4paper]{report} %,openright,twoside
-\usepackage{thesisstyle}
-\addbibresource{bib/PhD.bib}
+\documentclass[manuscript.tex]{subfiles}
 \begin{document}
 
-\begin{titlepage}
-
-    \begin{center}
-        \large{\textbf{Potential Field Geophysics Enhancement Using Contemporary Deep Learning Approaches}}
-
-        \vspace{15 mm}
-        {\large{Luke Thomas Smith, BSc, MRes}}
-
-        \vspace{15 mm}
-        This thesis is presented for the degree of
-
-        \vspace{5 mm}
-        \textbf{Doctor of Philosophy}
-
-        of
-
-        \textbf{The University of Western Australia}
-        \vspace{5 mm}
-
-        School of Earth Sciences
-        \vspace{15 mm}
-
-        \begin{figure}[h]
-            \centering{}
-            \includegraphics[scale=0.6]{fig/UWA_FORMAL_PORTRAIT_CMYK}
-        \end{figure}
-
-        \vspace*{\fill}
-        2023
-    \end{center}
-\end{titlepage}
-
-% \clearpage{}
-
-\pagenumbering{roman}
-\setcounter{page}{1}
-
-\addsec{\centering{}Abstract}
-Geophysics examines the petrophysical expression of geology within the Earth and is vital for exploring and understanding mineral systems under cover.
-The growing global demand for resources drives new data acquisition, with sensors that return more and higher quality data.
-The challenges and opportunities of big data are not unique to the geosciences, and the development of methods and computing to address these are ubiquitous in the contemporary age of deep learning.
-
-Potential field surveying from aircraft provides rapid and extensive coverage of target geology.
-These surveys are routinely conducted as pre-competitive regional data acquisition to stimulate exploration, or as targeted investigations by the exploration industry.
-% Surveys are also routinely collected on the ground or by satellite, with processing methods and interpretation shared between all forms of acquisition.
-The collected data may contain millions of discrete samples scattered in three dimensions, and their interpretation often relies on regularisation to a quantised grid, allowing digital processing and human or machine interpretation.
-% A constraint on the usefulness of these data is the data resolution, or more precisely, the Nyquist frequency of the grid.
-The limit on information available within gridded data results directly from the spatial sampling density of the originating survey, and the density of cells used to represent the grid raster.
-% The well known geophysics rule of thumb, \emph{a grids cell size should be specified as one-quarter to one-fifth of the line spacing}, has long informed the achievable detail in these survey products.
-However, sampling density suffers various constraints such as cultural obstructions and budget, leading to the need to fly the fewest number of lines that can still meet the resolution required to interpret target geological features.
-
-This thesis reports on three bodies of work across two topics in geophysics; enhancing the high-frequency content of gridded potential field data using \emph{super-resolution}; and, learning a representative function of a potential field extent using \emph{implicit neural representation}.
-The first topic enhances the value of geophysical surveys by predicting high-frequency components in sparsely sampled potential field grids.
-The second presents a straightforward neural network framework for high quality grid regularisation, processing, and data integration.
-For each body of work in these topics, real-world geophysical case studies are presented in order to demonstrate the effectiveness and challenges of the method with open access data.
-Each body of work extends deep learning methods described in computer science literature the same year as the development of each respective geophysical method, to keep pace with rapid advances in the field of machine learning.
-
-In the topic of super-resolution, the first method uses convolutional neural networks to enhance the resolution of real magnetic textures in state magnetic grids at a fixed four times scale.
-This is further explored in the second body of work, where synthetic potential field line data are used for model pretraining, to address the lack of survey data with sufficient line spacing variability.
-It quantifies the performance of super-resolution upscaling on real-world low-resolution grids with line spacings between \SI{80}{\m} and \SI{480}{\m}, and investigates the useful limits of upscaling using the method.
-
-The second topic explores a method for learning a representation of a potential field extent from scattered real-world survey data by a contemporary neural network.
-The data-driven approach allows the extraction of high-resolution level grids from the learn representation, as well as the rapid analytical calculation of spatial gradients.
-Grid rasters and horizontal gradients calculated with the method very closely match their numerical counterparts, however vertical gradients are not represented well.
-
-Individually the methods developed in this thesis enhance the information extractable from potential field surveys.
-However, in combination they reflect ongoing advances in deep learning and their extension to challenges and opportunities in geophysics.
-
-\newpage{}
-\addsec{Acknowledgements}
-\dots{}
-
-This research was supported by a Rio Tinto Iron Ore PhD Scholarship.
-
-\newpage{}
-\tableofcontents{}
-% \listoffigures{}
-% \listoftables{}
-
-\newpage{}
-\addsec{Thesis Declaration}
-I, Luke Thomas Smith, certify that:
-\begin{itemize}
-    \item{}This thesis has been substantially accomplished during enrolment in this degree.
-    \item{}This thesis is my own work and does not contain any material previously published or written by another person, except where due reference has been made in the text or Authorship Declaration.
-    \item{}This thesis does not contain material which has been submitted for the award of any other degree or diploma in my name, in any university or other tertiary institution.
-    \item{}In the future, no part of this thesis will be used in a submission in my name, for any other degree or diploma in any university or other tertiary institution without the prior approval of The University of Western Australia and where applicable, any partner institution responsible for the joint-award of this degree.
-    \item{}This thesis does not violate or infringe any copyright, trademark, patent, or other rights whatsoever of any person.
-\end{itemize}
-
-\vspace*{20 mm}
-\noindent\begin{tabular}{ll}
-                               &                           \\[8ex]
-    \makebox[100 mm]{\dotfill} & \makebox[30 mm]{\dotfill} \\
-    Student Signature          & Date                      \\
-\end{tabular}
-
-\newpage{}
 \addsec{Authorship Declaration}
@@
             \textbf{Contribution}: The method was researched, developed, analysed and drafted by L.
-Smith, who performed revision based on manuscript review from co-authors E.J.
+Smith, who revised the manuscript with feedback from co-authors E.J.
 Holden, D.
@@
 Akhtar.
-          As a published manuscript, further revision was provided by the journal editor and peer reviewers.
+            As a published manuscript, further revision was undertaken prompted by peer review.
 \end{itemize}
@@
 
-          \textbf{Contribution}: Further investigation of super-resolution was initiated, developed, analysed, and drafted by L.
-Smith, with guidance on manuscript direction from co-authors E.J.
-Holden, D.
-Wedge, T.
-Horrocks, and N.
-Akhtar.
+            \textbf{Contribution}: Further investigation of super-resolution was initiated, developed, analysed, and prepared by L.
+Smith, with critical manuscript review from N.
+Akhtar, E.J.
+Holden, T.
+Horrocks, and D.
+Wedge.
 
@@
             \textbf{Contribution}: The concept and development of implicit neural representation for geophysics was initiated by L.
-Smith, who performed the subsequent development, analysis, and drafting with manuscript review from co-authors E.J.
-Holden, D.
-Wedge, T.
-Horrocks, and N.
-Akhtar.
+Smith, who performed the subsequent research, development, analysis, and drafting.
+The manuscript was assisted by review from N.
+Akhtar, E.J.
+Holden, T.
+Horrocks, and D.
+Wedge.
 
@@
 
-\clearpage{}
-\pagenumbering{arabic}
-\setcounter{page}{1}
-\setcounter{section}{0}
-\renewcommand{\thesection}{\arabic{section}}
-
-\subfile{intro}
-\subfile{paper1}
-% \subfile{paper2}
-% \subfile{paper3}
-\subfile{discussion}
 \end{document}

### 2023-10-01 manuscript.tex
Add quote
Not sure if I'm 100% sold on it

@@
 
-% \clearpage{}
+\shipout\null
 
@@
 
+\vfill{}
+\epigraph{All collected data had come to a final end. Nothing was left to be collected.}{}
+
 \newpage{}
@@
 This research was supported by a Rio Tinto Iron Ore PhD Scholarship.
+
+\vfill{}
+\epigraph{But all collected data had yet to be completely correlated and put together in all possible relationships.}{Isaac Asimov}
 
@@
 \newpage{}
-\addsec{Authorship Declaration}
-This research was carried out at the University of Western Australia.
-This thesis contains material that has been published or prepared for publication.
-The extent of the candidate's contribution toward publication is outlined below.
+\subfile{authorship_declaration}
 
-\smallskip{}
-\noindent{}All software development was performed by L. Smith.
-
-\noindent{}The possible application of super-resolution for geophysical grid data was suggested by E.J. Holden.
-
-\medskip{}
-\noindent{}Sections comprising published journal articles:
-\begin{itemize}
-    \item{}\textbf{Location in thesis}: Chapter 1
-
-          \textbf{Publication}: Smith, L., Horrocks, T., Holden, E.J., Wedge, D., Akhtar, N., 2022.
-Magnetic grid resolution enhancement using machine learning: A case study from the Eastern Goldfields Superterrane.
-Ore Geology Reviews 150, 105119.
-https://doi.org/10.1016/j.oregeorev.2022.105119
-
-          \textbf{Contribution}: The method was researched, developed, analysed and drafted by L.
-Smith, who performed revision based on manuscript review from co-authors E.J.
-Holden, D.
-Wedge, T.
-Horrocks, and N.
-Akhtar.
-          As a published manuscript, further revision was provided by the journal editor and peer reviewers.
-\end{itemize}
-
-\noindent{}Sections comprising manuscripts in preparation:
-\begin{itemize}
-    \item{}
-          \textbf{Location in thesis}: Chapter 2
-
-          \textbf{Contribution}: Further investigation of super-resolution was initiated, developed, analysed, and drafted by L.
-Smith, with guidance on manuscript direction from co-authors E.J.
-Holden, D.
-Wedge, T.
-Horrocks, and N.
-Akhtar.
-
-    \item{}
-          \textbf{Location in thesis}: Chapter 3
-
-          \textbf{Contribution}: The concept and development of implicit neural representation for geophysics was initiated by L.
-Smith, who performed the subsequent development, analysis, and drafting with manuscript review from co-authors E.J.
-Holden, D.
-Wedge, T.
-Horrocks, and N.
-Akhtar.
-
-\end{itemize}
-
-\noindent{}The contributions of the author have been truthfully stated, and permission from
-each author has been sought to include the published material in this thesis.
-
-% \vspace*{20 mm}
-
-\noindent\begin{tabular}{ll}
-                                          &                           \\[8ex]
-    \makebox[100 mm]{\dotfill}            & \makebox[30 mm]{\dotfill} \\
-    Eun-Jung Holden                       & Date                      \\
-    Principal and Coordinating Supervisor &                           \\[8ex]
-    \makebox[100 mm]{\dotfill}            & \makebox[30 mm]{\dotfill} \\
-    Daniel Wedge                          & Date                      \\
-    Co-supervisor                         &                           \\[8ex]
-    \makebox[100 mm]{\dotfill}            & \makebox[30 mm]{\dotfill} \\
-    Tom Horrocks                          & Date                      \\
-    Co-supervisor                         &                           \\[8ex]
-    \makebox[100 mm]{\dotfill}            & \makebox[30 mm]{\dotfill} \\
-    Naveed Akhtar                         & Date                      \\
-    Co-supervisor                         &                           \\
-\end{tabular}
-
-\clearpage{}
 \pagenumbering{arabic}

### 2023-10-02 paper3.tex
Fix incorrect word
Work on revisions

@@
 Neural networks can be considered as universal function approximators.
-The recent technique of deep learning implicit neural representation (INR) \parencite{mildenhallNeRFRepresentingScenes2020} represents a signal as a function of its coordinates, built on a network architecture known as a coordinate multilayer perceptron (CMLP) (see \cite{ramasinghePeriodicityUnifyingFramework2022} for a recent introduction).
+The recent technique of deep learning implicit neural representation (INR) \parencite{mildenhallNeRFRepresentingScenes2020} represents a signal as a function of its coordinates, built on a network architecture known as a coordinate multilayer perceptron (CMLP) (see \textcite{ramasinghePeriodicityUnifyingFramework2022} for a recent introduction).
 By parameterising the function in coordinate space, novel values of the function can be queried at arbitrary coordinates within the learnt continuous spatial domain.
@@
 The resolvable detail within the sampled field is a function of the sampling density, and the distance from the source.
-To enable digital processing and storage of the sample data following acquisition, the scattered points are regularised to a quantised grid.
-The Nyquist wavelength inherent to the selected grid cell size during initial regularisation limits the high-resolution information representable by the grid.
-Because grid regularisation is one of the earliest steps in interpreting geophysical surveys, this information fails to be utilised in most subsequent processing and interpretation tasks.
+To enable digital processing of the sample data following acquisition, the scattered points are regularised to a quantised grid.
+The Nyquist wavelength inherent to the selected grid cell size during regularisation limits the high-resolution information representable by the grid.
+Because this regularisation is one of the earliest steps in preparing data for subsequent interpretation and processing tasks, the information lost cannot be used in these later tasks.
 % Subsequent processes such as frequency filtering or directional gradients are similary constrained by the parameters of the regularisation.
@@
 Representing a vector field requires three orthogonal components at each spatial coordinate, while a scalar field can be parameterised with a single component \parencite{blakelyPotentialTheoryGravity1996}.
-A potential field survey can be parameterised as \cref{eqn:potential}.
+A potential field survey can be parameterised as
 \begin{equation}
@@
 
-Seminal work by \cite{mildenhallNeRFRepresentingScenes2020} demonstrated INR of volume density and colour radiance, learnt from five dimensions of spatial coordinates and orientation.
+Seminal work by \textcite{mildenhallNeRFRepresentingScenes2020} demonstrated INR of volume density and colour radiance, learnt from five dimensions of spatial coordinates and orientation.
 Their approach uses positional encoding to improve the learning capacity of high-frequency content, addressing the issue of spectral bias in deep learning \parencite{rahamanSpectralBiasNeural2019}.
@@
 Periodic activation functions differ from typical non-linear activations by comprising the neuron with a function that repeats periodically, which allows for continuous differentiation throughout the depth of the network.
-Work by \cite{ramasinghePeriodicityUnifyingFramework2022} revealed that it is the magnitude of the first and second derivatives of the activation that enhanced high-frequency representation learning capacity, rather than periodicity, leading to Gaussian \parencite{ramasinghePeriodicityUnifyingFramework2022} and wavelet \parencite{saragadamWIREWaveletImplicit2023} activation functions for CMLP\@.
+Work by \textcite{ramasinghePeriodicityUnifyingFramework2022} revealed that it is the magnitude of the first and second derivatives of the activation that enhanced high-frequency representation learning capacity, rather than periodicity, leading to Gaussian \parencite{ramasinghePeriodicityUnifyingFramework2022} and wavelet \parencite{saragadamWIREWaveletImplicit2023} activation functions for CMLP\@.
 
@@
 Research directions include leveraging new activation functions \parencite{saragadamWIREWaveletImplicit2023}, transforming the input space \parencite[e.g.][]{benbarkaSeeingImplicitNeural2022} or using additional constraints on the search space such as physics-informed neural networks \parencite{raissiPhysicsinformedNeuralNetworks2019}.
-
-In geoscience, INR has been used for geological modelling \parencite{hillierGeoINRImplicitNeural2023}, where the existing implicit interpolation approaches.
+In geoscience, INR has been used for numerical modelling \parencite{hillierGeoINRImplicitNeural2023}.
 
@@
 Compressed sensing relies on the theory that a signal has a sparse representation in some transform domain, and a deeper exploration of the comparison between INR and compressed sensing remains to be performed.
-%per Naveed
-Compressed sensing recovers the signal through linear transformations.
-Because neural networks allow convenient modelling of non-linear transformations, they have an inherent advantage over compressed sensing for potential field grid recovery.
+Compressed sensing recovers the signal through linear transformations, while neural networks allow convenient modelling of non-linear transformations.
 
@@
 However, automatic differentiation can also evaluate the derivatives of the network output with respect to the inputs, using the same high-performance AD framework.
-This can directly provide the partial derivatives of the potential field \(\frac{\partial\phi{}}{\partial x}, \frac{\partial \phi{}}{\partial y}, \frac{\partial \phi{}}{\partial z}\) with respect to its coordinates, as well as higher order derivatives, and without first requiring gridding.
+This can directly provide the partial derivatives of the potential field with respect to its coordinates \(\frac{\partial\phi{}}{\partial x}, \frac{\partial \phi{}}{\partial y}, \frac{\partial \phi{}}{\partial z}\), as well as higher order derivatives, without first requiring gridding.
 
@@
 These are compared against a case study reference grid from Geoscience Australia, with gradients from numerical derivative calculation.
-An overview diagram is presented in \cref{fig:overview}.
+% An overview diagram is presented in \Cref{fig:overview}.
 
-\begin{figure}[hbt]
-    \centering{}
-    % \includegraphics[width=0.5\linewidth]{fig/p3/overview.pdf}
-    \caption[Overview of the proposed method]{Overview}
-    \label{fig:overview}
-\end{figure}
+% \begin{figure}[hbt]
+%     \centering{}
+%     % \includegraphics[width=0.5\linewidth]{fig/p3/overview.pdf}
+%     \caption[Overview of the proposed method]{Overview}
+%     \label{fig:overview}
+% \end{figure}
 
@@
 The mean altitude of the drape surface excluding tie lines is \SI{39.5}{\m}, with a standard deviation of \SI{4.5}{\m}.
-The sample locations and recorded altitudes are shown in \cref{fig:samples}, where it can be seen the crater rim topography causes large deviations to the flown drape.
+The sample locations and recorded altitudes are shown in \Cref{fig:samples}, where it can be seen the crater rim topography causes large deviations to the flown drape.
 
@@
 The line data netCDF contains tie-levelled, micro-levelled, and AWAGS levelled magnetic variables, in respective order of processing levels.
-The micro-levelled magnetic data are used in this case study. % and the additional surveys presented in Appendix A.
+The micro-levelled magnetic data are used in this case study because the exact sample altitude is uncertain following the available levelling processes.
 Both geographic and projected coordinate systems can be used, provided the query coordinates for inference match those used during training.
@@
 \subsection{Network architecture}
-The CMLP architecture comprises a simple fully connected network with \(n\) hidden layers, each with \(m\) neurons, presented within \cref{fig:overview}.
+The CMLP architecture comprises a simple fully connected network with \(n\) hidden layers, each with \(m\) neurons. %, presented within \Cref{fig:overview}.
+The number of input features is 3, for each spatial dimension, and the number of output features is 1, for the predicted potential field value at those coordinates.
 Comparison of recently proposed activatons and hyperparameters for CMLP is performed by \textcite{saragadamWIREWaveletImplicit2023}, where increasing both \(n\) and \(m\) increases the capacity of the model, at the cost of computational requirements.
@@
 The case study line data easily fit into available graphics memory, and can be trained using batch gradient descent.
+Each sample in the batch is a single 3D survey point with the associated 1D target potential field value.
 
@@
 The very low learning rates in the late stages of training significantly contribute to the quality of the representation when compared to a constant learning rate.
-Convergence of the network is shown in \cref{fig:convergence}.
+Convergence of the network is shown in \Cref{fig:convergence}.
 %However, training on large scattered aeromagnetic surveys with more than one million samples, memory becomes a constraint and mini-batch training is required.
@@
 The INR can be queried at arbitrary continuous coordinates, including out-of-range values beyond the training domain.
-As expected, the predicted field becomes unrealistic when extrapolating beyond this boundary, which can be seen in the periphery of the INR grid in \cref{fig:grid}.
+As expected, the predicted field becomes unrealistic when extrapolating beyond this boundary, which can be seen in the periphery of the INR grid in \Cref{fig:grid}.
 This boundary region (indicated by solid white in the reference grid) is excluded from PSNR calculation.
@@
 
-% The strong performance of the model is retained even when using a subsampled training dataset, here shown at \qty{30}{\percent} and \qty{10}{\percent} (\cref{fig:gridpct}) of the total available data.
+% The strong performance of the model is retained even when using a subsampled training dataset, here shown at \qty{30}{\percent} and \qty{10}{\percent} (\Cref{fig:gridpct}) of the total available data.
 % % In both cases, the validaiton and test sets remain identical to the initial training split.
@@
 
-\subsection{Spatial derivatives and filters}
+\subsection{Spatial derivatives}
 Using AD, derivatives can be calculated between the input spatial coordinates and the output potential field representation.
-While horizontal derivatives queried from the INR correspond well to numerical derivatives calculated on the \SI{40}{\m} level grid in \cref{fig:hori_grad}, the vertical derivative suffers poor performance \cref{fig:vert_grad}.
+For comparison, the derivatives calculated with AD are compared with numerical derivatives calculated on the level grid queried from the same INR model. 
+While horizontal derivatives queried from the INR correspond well to numerical derivatives calculated on the \SI{40}{\m} level grid in \Cref{fig:hori_grad}, the vertical derivative suffers poor performance (\Cref{fig:vert_grad}).
 This correlates with the poor continuation performance of model when predicting level grids several metres or more beyond the nominal sample height.
-This is interpreted as the presented model having a limited capacity to extrapolate, and learning a poor representation of the vertical component of the potential field, which we further discuss in \cref{sec:discussion}
+This is interpreted as the presented model having a limited capacity to extrapolate, and learning a poor representation of the vertical component of the potential field, which we further discuss in \Cref{sec:discussion}
 
@@
 % The case study survey presented is very small compared to typical regional aeromagnetic surveys.
-% A demonstration of the method on a large aeromagnetic survey, requiring minibatch training, is included in \cref{app:menzies}.
-% Training of this representation follows the parameters outlined in \cref{sec:training}, which were optimised for the Wolfe Creek case study, with the addition of a shuffled minibatch size of \SI{1024000}\@.
+% A demonstration of the method on a large aeromagnetic survey, requiring minibatch training, is included in \Cref{app:menzies}.
+% Training of this representation follows the parameters outlined in \Cref{sec:training}, which were optimised for the Wolfe Creek case study, with the addition of a shuffled minibatch size of \SI{1024000}\@.
 % Attempts to train the CMLP with small batch sizes did not converge.%, reflecting the non-convergence result found for training on very large subsampling factors of the line dataset.
@@
 
-Inspired by the approach of \cite{raissiPhysicsinformedNeuralNetworks2019}, a geophysics informed network could include a Laplace criterion,
+Inspired by the approach of \textcite{raissiPhysicsinformedNeuralNetworks2019}, a geophysics informed network could include a Laplace criterion,
 \begin{equation}
@@
 
-Initial attempts using the objective function approach were trialled in this work, but failed to converge and remain for future work.
-Other geophysical formulae may present avenues for PINN implementation, such as vertical continuation described in \cite{blakelyPotentialTheoryGravity1996}.
+Initial attempts using the objective function approach were trialled in this work, but struggled to converge and remain for future work.
+It may be worth investigating other geophysical formulae for PINN implementation, such as vertical continuation described in \textcite{blakelyPotentialTheoryGravity1996}.
 
@@
 Level grids can be extracted from these representations, emerging as a novel method for regularising scattered geophysical sample data.
-Gradients can be calculated using the learnt representation, and gridded \emph{a posteri} of gradient calculation.
+Gradients calculated using the learnt representation are , and gridded after gradient calculation.
 

### 2023-10-02 authorship_declaration.tex
State percentage contribution

@@
 \smallskip{}
-\noindent{}All software development was performed by L. Smith.
+\noindent{}All software development for the research was performed by L. Smith.
 
@@
 
-            \textbf{Contribution}: The method was researched, developed, analysed and drafted by L.
-Smith, who revised the manuscript with feedback from co-authors E.J.
-Holden, D.
-Wedge, T.
-Horrocks, and N.
-Akhtar.
+            \textbf{Contribution}: The proportion of original work by the student is \qty{80}{\percent}.
+            The method was researched, developed, analysed and drafted by L. Smith, who revised the manuscript with feedback from co-authors E.J. Holden, D. Wedge, T. Horrocks, and N. Akhtar.
             As a published manuscript, further revision was undertaken prompted by peer review.
@@
 
-            \textbf{Contribution}: Further investigation of super-resolution was initiated, developed, analysed, and prepared by L.
+            \textbf{Contribution}: The proportion of original work by the student is \qty{80}{\percent}.
+            Further investigation of super-resolution was initiated, developed, analysed, and prepared by L.
 Smith, with critical manuscript review from N.
@@
 
-            \textbf{Contribution}: The concept and development of implicit neural representation for geophysics was initiated by L.
-Smith, who performed the subsequent research, development, analysis, and drafting.
+            \textbf{Contribution}: The proportion of original work by the student is \qty{90}{\percent}.
+            The concept and development of implicit neural representation for geophysics was initiated by L.
+Smith, who performed the subsequent research, development, analysis, and writing.
 The manuscript was assisted by review from N.
@@
 
+\newpage{}
 \noindent{}The contributions of the author have been truthfully stated, and permission from

### 2023-10-06 discussion.tex

@@
 % and provide overall conclusions that address the research aims.
+\setcounter{chapter}{1}
 
@@
 This thesis presented contemporary methods in deep learning to address the need for modern data driven applications in geoscience.
-By including both synthetic and real survey data for training and case studies, it was established that the methods could generalise to real-world applications.
+By including both synthetic and real survey data for training and case studies, it was established that these methods could generalise to real-world applications.
 
-The proposed super-resolution (SR) method explored in cref{paper1, paper2} significantly enhanced gridded low-resolution survey data by predicting grid values that contain accurate high-frequency information.
-After establishing the feasibility of geophysics super-resolution in cref{paper1}, an updated neural network and new dataset were developed in cref{paper2}, where simulated line profile surveys create training data with the low-resolution transform encountered in real world exploration geophysics.
-The use of synthetic data to train a baseline model addresses the cost of training data acquisition, as well as opens avenues for targeted geological domain specific applications.
+The proposed super-resolution (SR) method explored in Chapter 1 and Chapter 2 significantly enhanced gridded low-resolution survey data by predicting grid values that contain accurate high-frequency information.
+After establishing the feasibility of geophysics super-resolution in Chapter 1, an updated neural network and new dataset were developed in Chapter 2, where simulated line profile surveys create training data with the low-resolution transform encountered in real world exploration geophysics.
+The use of synthetic data to train a baseline model addresses the challenge of training data acquisition, as well as opens avenues for targeted geological domain specific applications.
 
-Cref{paper3} used coordinate multilayer pereceptron neural networks to learn a representation of the function that describes a surveyed potential field extent.
+The contribution in Chapter 3 used coordinate multilayer perceptron neural networks to learn a representation of the function that describes a surveyed potential field extent.
 These networks are highly suited for processing spatial data such as point sampled geophysics surveys.
-The applications developed in cref{paper3} were predicting a regularly spaced grid from scattered point data, and calculating derivatives of the potential field representation, both fundamental to interpretation and processing in geophysics.
+The applications contributed were predicting a regularly spaced grid from scattered survey point data, and a novel method using the representation to calculate derivatives of a potential field, both fundamental to interpretation and processing in geophysics.
 By commencing the methods from point sample data, the number of individual processing steps is reduced, and the application is fully trainable.
-The neural network approach developed in cref{paper3} uses coordinate MLP for implicit representation, a currently burgeoning field of research in computer science, and it is hoped that the proposed trainable approach for geophysics point data will prompt further development of geoscience applications in the implicit neural network domain.
+The neural network approach developed in Chapter 3 uses coordinate MLP for implicit representation, a currently burgeoning field of research in computer science, and it is hoped that the proposed trainable approach for geophysics point data will prompt further development of geoscience applications in the implicit neural network domain.
 
@@
 Assisted by this understanding, they can infer geological features with varying degrees of confidence.
-Low confidence features which are obscured by low-resolution data will be alterered, constructively or destructively, by the SR method.
+Low confidence features which are obscured by low-resolution data will be altered, constructively or destructively, by the SR method.
 The domain expert can then use this information to reassure or reassess the original low-resolution grid.
-Because it shares the same modality, super-resolution data can be readily trialed in place of existing low-resolution data used in automated analysis and machine processing tools.
+Because it shares the same modality, super-resolution data can be readily trialled in place of existing low-resolution data used in automated analysis and machine processing tools.
 It is expected that the enhanced appearance of features will generally improve the performance of subsequent analysis tasks on the grid raster.
 
-At the same time, it was seen in both cref{paper1, paper2} that super-resolution predictions can be misleading or entirely incorrect.
-The examples being the additional noise and implementation artefacts common in SR inferenece, as well as the enhancement of incorrect features in low-resolution data such as the aliased geological strike.
+At the same time, it was seen in both Chapter 1, paper2 that super-resolution predictions can be misleading or entirely incorrect.
+The examples being the additional noise and implementation artefacts common in SR inference, as well as the enhancement of incorrect features in low-resolution data such as the aliased geological strike.
 Used blindly or without characterisation, these tools may inspire false confidence in the interpreter.
@@
 \section{Revisiting Chapter 1}
-The method developed in cref{paper2} for creating sampled line profiles from potential field grids can be extended and used to train the networks described in cref{paper1}.
-The resulting RDN and ESRGAN models can be compared with the LTE model described in cref{paper2}, although the fixed factor upscaling block in the earlier networks limits this comparison to 4x scale.
+The method developed in Chapter 2 for creating sampled line profiles from potential field grids can be extended and used to train the networks described in Chapter 1.
+The resulting RDN and ESRGAN models can be compared with the LTE model described in Chapter 2, although the fixed factor upscaling block in the earlier networks limits this comparison to 4x scale.
 \Cref{fig:rdncomp} shows that RDN and ESRGAN are both highly performant for the task of predicting accurate features when upscaling \SI{320}{\m} data to \SI{40}{\m} line spacing.
-It can be inferred that the challenge of super-resolution is predominantly a question of suitable and sufficient training data, and less constrained to neural network choices.
+It can be inferred that the challenge of super-resolution is predominantly a question of providing suitable and sufficient training data, and less constrained to neural network choices.
 
@@
 \section{Synthetic data in geoscience}
-One of the challenges identified in cref{paper1} was the need for large extents of suitable training data.
+One of the challenges identified in Chapter 1 was the need for large extents of suitable training data.
 This applies to many machine learning tasks in geoscience.
-During the preparation of cref{paper2}, a large and varied synthetic geology training dataset was released \parencite{jessellNoddyverseMassiveData2022}.
+During the preparation of Chapter 2, a large and varied synthetic geology training dataset was released \parencite{jessellNoddyverseMassiveData2022}.
 This collection of labelled petrophysical voxel models and associated geophysical forward models provides many opportunities beyond those explored in this thesis.
-When taking advantage of transfer learning for pre-training, synthetic data can increase the generalisability of models for real data, as seen in cref{paper2}.
+When taking advantage of transfer learning for pre-training, synthetic data can increase the generalisability of models for real data, as seen in Chapter 2.
 
@@
 There are controls on the learning of a neural network beyond the training data samples.
-Cref{paper3} introduced to the thesis the concept of physics informed neural networks, in the form of a criterion to impose a specific constraint.
+Chapter 3 introduced to the thesis the concept of physics informed neural networks, in the form of a criterion to impose a specific constraint.
 For PINNs, this criterion enforces \emph{a priori} physical properties of the approximated function.
-It is possible to broaden the definition and extend the concept of informed networks to the use of generative adversarial networks in cref{paper1}.
+It is possible to broaden the definition and extend the concept of informed networks to the use of generative adversarial networks in Chapter 1.
 In these networks, the informing method is termed \emph{discriminator loss}, and is performed by a classification network preconditioned to identify images as `realistic' or `not realistic'.

### 2023-10-06 paper2.tex
Transcribe paper 2 draft
Still has unresolved comments and changes to be made.

@@
-\documentclass{article}
-\input{preamble}
+\documentclass[manuscript.tex]{subfiles}
 \begin{document}
-
-\author{\and{Luke Thomas Smith} \and{Eun-Jung Holden} \and{Tom Horrocks} \and{Daniel Wedge} \and{Naveed Akhtar}}
-\title{Super-Resolving Geophysical Surveys with Implicit Functions}
+\setcounter{chapter}{1}
+\title{Super-resolution of Aeromagnetic Survey Data}
+\author[1*]{Luke Thomas Smith}
+\author[1]{Tom Horrocks}
+\author[1]{Eun-Jung Holden}
+\author[1]{Daniel Wedge}
+\author[2]{Naveed Akhtar}
+\affil{Centre for Data-Driven Geoscience, School of Earth Sciences, The University of Western Australia (M006), 35 Stirling Highway, 6009 Perth, Australia}
+\affil{Department of Computer Science and Software Engineering, The University of Western Australia (M002), 35 Stirling Highway, 6009 Perth, Australia}
 \date{\today}
@@
 \begin{abstract}
-    Hi
+    Contemporary super-resolution is a deep learning technique to increase the resolution and high-frequency details of raster data.
+    However, despite the widespread success of super-resolution upscaling of natural photographs, its application to low-resolution geophysical surveys remains to be fully investigated.
+    Previous applications to geophysical survey data generate training data pairs of low- and high-resolution grids by downsampling the high-resolution grid with standard image filters, which is a poor approximation to real-world low-resolution aeromagnetic grids constructed from sparsely sampled survey data.
+    Moreover, the structural variation within the survey data depends entirely on the geological domain which is surveyed.
+    This paper proposes an approach to super-resolution of aeromagnetic survey data that uses realistic high-resolution and low-resolution pairs of gridded survey data, obtained by densely and sparsely `sampling' forward modelled magnetic grids from a suite of synthetic geological models.
+    The model then incorporates real-world survey data to improve accuracy through a secondary fine-tuning step, using a non-standard low-resolution transform that incorporates the survey line structure of the underlying data.
+    The Local Texture Estimator neural network architecture was used, and qualitative and quantitative measures of the super-resolution performance are reported.
+    The results demonstrate that the proposed method is capable of transforming regional scale aeromagnetic surveys to high-resolution for a wide range of geological features.
 \end{abstract}
@@
 \section{Introduction}
-The analysis of potential field geophysical surveys relies on gridded sample data.
+Deep learning techniques for single image super-resolution typically use paired high- and low-resolution image data, with the objective to learn the transform from low resolution to high.
+This is an ill posed challenge, because many high-resolution images may share the same low-resolution representation.
+For natural images, a common approach to generating low-resolution data is to interpolate the high-resolution image to a smaller size using a low-resolution transform such as bicubic resizing.
+
+The analysis of potential field geophysics relies on gridded survey data.
 Sampling density and subsequent gridding processes impose limits on the observable detail in these data.
-Recent work with both images and geophysical data has shown that these limits can be partially overcome using deep learning \parencite{moserHitchhikerGuideSuperResolution2023,smithMagneticGridResolution2022}.
-However, the extent to which low-resolution geophysical data can be enhanced, the maximum useful upscaling factor, and characteristics of the resulting features remain to be fully explored.
-These can be examined using the current generation of super-resolution networks, using arbitrary resolution, Multi-Layer Perceptron implicit functoin neural networks.
+Contemporary work with low-resolution transforms for natural images \parencite[reviewed in][]{moserHitchhikerGuideSuperResolution2023} has well characterised the research space and expected performance for upscaling photographs and digital images.
+Geophysical data are distinct from these image rasters due to the potential field sampling and grid interpolation process, and the extent to which widely spaced low-resolution geophysical line data can be enhanced, and characteristics of the resulting super-resolved grids remain to be fully explored.
+These can be examined using the current generation super-resolution neural networks and a combination of synthetic and real geophysical datasets.
 
-The first generation of super-resolution neural networks, starting with SRCNN \parencite{dongLearningDeepConvolutional2014}, were capable of upscaling at fixed factos with encouraging performance.
-However, a separate trained model is required for each upscaling factor of interest, and performance beyond four time upscaling is modest.
-Contemporary super-resolution can achieve arbitrary upscaling at larger factors using MLP implicit function super-resolution.
-Implicit functions parameterise a function with a neural network analogue, which can be queried for information that fits the learnt function but was not represented by the training data.
+When compared to numerical upsampling methods such as the bicubic filter, deep learning SR methods for geophysical textures can predict infill cells that add high frequency information which is reported to be more accurate when compared to a ground truth target \parencite{smithMagneticGridResolution2022}.
+However, the data used by \textcite{smithMagneticGridResolution2022} do not reflect real-world low-resolution geophysical survey data.
+Low-resolution aeromagnetic survey data are the result of wide line spacings during acquisition, with the resulting grid cells predominantly being those predicted by interpolation between sparse sample points.
+Achieving higher resolution traditionally requires additional sampling to increase the grid resolution, which refines structures in the response and reduces blocky textures and other gridding artifacts.
+We propose a method that simulates the line sampling of both synthetic and real data, thereby more closely reflecting a real-world geophysical low-resolution transform.
+%TODO refactor contrib. is investigating geo domain variance
+Synthetic data are used in the proposed method to address the low amount of suitable real training data, making use of a recently released extensive and geologically varied synthetic dataset \parencite{jessellNoddyverseMassiveData2022}.
+Thus, the two contributions made in this study are addressing the challenges of training a deep learning model with limited suitable geophysical data and describing a methodology for a realistic low-resolution transform for potential field survey grids.
 
-One application of implicit neural networks is super-resolution (SR), the task of predicting interpolating values to resolve data in a higher resolution.
-This task has previously been perfomed predominantly in the domain of Convolutional Neural Networks (CNN).
-When compared to numerical methods such as bicubic filters, existing CNN based super-resolution methods for geophysical grids can predict infill pixels that add high frequency information which is repoted to be more accurate when compared to a ground trugh target \parencite{smithMagneticGridResolution2022}.
-However, MLP based implicit networks can surpass CNNs for continuous domain super-resoltion with their explicit use of spatial coordinate features, such as pixel indices.
-Be learning a signal as a function of its coordinates, arbitrary and continuous super-resolution is made possible bu predicting cell values at arbitrarily fine grid cell spacings.
-While earlier CNN based SR methods can achieve upscaling at any trained scale factor, they require a bespoke model for inference at each different scale.
-Using implicit functions, a single trained model is capable of high quality, arbitrary interpolation of the geophysical potential field, including at scales that were not seen during training.
+%TODO
+The remainder of this paper is structured as follows.
+In Section 1.1 we introduce geophysical grids and their differences to image rasters, and introduce synthetic data as a source of training data with geological domain variation.
+In Section 1.2, we review
 
 \subsection{Resolution in geophysical surveys}
-In exploration geophysics, the earth's naturally occurring magnetic or gravitational potential fields can be used to survey the petrophysical expression of the underlying geology.
-Depending on the scale of investigation, surveys may be carried out from ground or airborne sensors, in a range of sampling regimes.
+\label{sec:resinsurveys}
+In exploration geophysics, the Earth's naturally occurring magnetic or gravitational potential fields can be used to survey the petrophysical expression of underlying geology.
+Depending on the scale of investigation, surveys may be carried out from ground or airborne sensors.
 Detailed ground-based surveys can be sampled at point spacings of tens of metres while avoiding local obstacles, but at a regional scale, aircraft are used to provide rapid and uniform coverage regardless of access constraints.
-These airborne surveys collect data at wider line spacing to minimise cost, typically between \SI{100}{\metre} and \SI{1000}{\metre}, but detailed surveys with line spacing closer than \SI{100}{\metre} are increasingly common.
-Sampling along line is typically performed at \SI{10}{\hertz} or faster, which corresponds to several meters at a nominal flight speed of \SI{70}{\metre/\second} \parencite{goodwinAirborneMagneticRadiometric2023}.
-Despite the use of precise navigation systems and skilled operators, these data are not collected in perfectly uniform lines at constant height, and the field samples also contain noise components.
+These airborne surveys collect data at wide line spacing to minimise cost, with lines in Western Australian low-resolution regional surveys typically \qty{400}{\m} apart, however, open access high-resolution surveys with line spacings of \qty{100}{\m} or closer are increasingly common.
+Sampling along line is typically performed at \qty{10}{\Hz} or faster, which corresponds to several meters between samples at a nominal flight speed of \qty{70}{\m\per\s} \parencite{goodwinAirborneMagneticRadiometric2023}.
+Despite the use of precise navigation systems and skilled operators, these data are not collected in perfectly uniform lines at constant height, and the samples also contain noise components.
+
 Transforming these irregularly distributed line data to a uniformly spaced array is the challenge of regularisation.
-Regularisation is performed by gridding, of which there are several distinct methods.
+Regularisation is performed by gridding, of which there are several classes of methods.
 Minimum Curvature gridding \parencite{briggsMachineContouringUsing1974} is routinely applied in industry applications, as it gives good quality results in rapid time, with minimal manual intervention.
-A comprehensive review of spatial interpolation methods is presented by \parencite{liReviewComparativeStudies2011}.
-Each method of gridding has characteristic interpolation traits (which when undesired are termed artifacts), but irrespective of the gridding process, the detail resolvable in the output grid is a product of the final cell size.
-Gridding at finer cell sizes preserves greater detail contained in the sampled data.
 
-When the cell size covers a quantified distance, the maximum resolvable detail can be expressed as a wavelength.
+A comprehensive review of spatial interpolation methods is presented by \textcite{liReviewComparativeStudies2011}.
+Each method of gridding has characteristic interpolation traits (which when undesired are termed artifacts), but irrespective of the gridding process the detail resolvable in the output grid is a product of the final cell size, termed resolution.
+Gridding at a finer cell size preserves higher frequencies present in the sampled data.
+When the cell size covers a quantified distance, the smallest resolvable detail can be expressed in terms of wavelength.
 This is the grids Nyquist wavelength, and is equal to twice the gridded cell size.
-This is also known as the Nyquist frequency, the well-known limit at which sampled signals may be incorrectly resolved due to under sampling.
-For example, a potential field that lacks significant wavelength components shorter than \SI{200}{\metre} will be adequately resolved by a grid with a cell size of \SI{100}{\metre}, without spurious features known as aliasing.
+This is also known as the Nyquist frequency, the well-known limit at which bandwidth-limited signals may be incorrectly resolved due to sampling below the Nyquist frequency, at half the sampling frequency.
+For example, a potential field which lacks significant wavelength components shorter than \qty{200}{\m} will be adequately resolved by a grid with a cell size of \qty{100}{\m}, without spurious features known as aliasing.
+Extending this concept, arbitrarily shrinking the cell size will not resolve additional detail unless also predicting features with wavelengths shorter than those present in the sample data.
+These are limited by the sample spacing during acquisition.
+As an additional constraint on the observable detail in sampled potential fields, the power of shorter wavelengths diminishes with increasing distances from the source, such that potential fields lose high-frequency details at larger source-sensor separation.
 
-Extending this concept, arbitrarily shrinking the cell size will not resolve additional detail, without also predicting features with wavelengths shorter than those already present in the data.
-These are limited by the sample spacing during acquisition.
-As an additional constraint on the observable detail in sampled potential fields, the power of shorter wavelengths diminishes with increasing distances from the source.
-Thus, potential fields grow smoother at larger source-sensor separation.
+Magnetic potential field grids are highly distinct from photographs and other image rasters.
+Being sampled as a single component of the vector potential field, these data contain a single channel, and the data contain multiple sources of noise components.
+Furthermore, the features present in these data are dependent on the subsurface geology, varying between smooth domains without significant near-surface magnetisation, through to highly deformed igneous stratigraphic units with complex high-intensity structures.
+The recorded intensity values have high dynamic range, spanning tens of thousands of nanotesla, while contextually important features may be defined by tens of nanotesla \parencite{kovesiPhasePreservingTone2012}.
+Regularisation of the scattered sample data introduces spurious features, which depend on a variety of parameters intrinsic to both the data and the gridding method.
+Most critically, aeromagnetic data are highly sampled in the direction of flight lines but are under-sampled in the line perpendicular direction.
+When widely spaced line data are interpolated, features are overly smoothed in the line perpendicular direction, leading to the appearance of smearing or string-of-beads aliasing textures.
+Details defined by short wavelengths such as near surface magnetic sources or small-scale structures are better localised and made more apparent in high resolution data.
+These features may help delineate additional structures that are manifested in the data which are contextually important to geological interpretation.
+In addition to human interpretation, machine processing of geophysical data is benefitted by using higher resolution data, with the negligible cost of increased computational load.
 
-Considering all the factors that the limit the representation of short wavelength features in geophysical grids, accurately reconstructing or rediscovering any geologically significant features that have been lost during the survey and gridding process appears challenging.
+Regions covered by high-resolution aeromagnetic surveys are biased toward prospective geological terranes.
+In order to improve the generalisation of the method for regions without high-resolution coverage, transfer learning \parencite{tanSurveyDeepTransfer2018} from synthetic data is used to establish a baseline model on a broad set of geological domains, which is then fine-tuned with high-resolution survey grid data.
+Transfer learning assists with the challenge of costly data acquisition common in geoscience \parencite{dawsonImpactDatasetSize2023} by pre-training a neural network on a larger source dataset that shares properties with the target dataset.
+The synthetic geophysical data \parencite{jessellNoddyverseMassiveData2022} are forward modelled from stratigraphic voxel models with varied geological histories which can provide a diverse set of features, but these lack truly realistic characteristics.
+In the case of the synthetic data used here, this includes a lack of high frequency near surface magnetisation and features from complex geological processes such as metasomatism.
 
-\subsection{The benefit of higher resolution}
-The nominal target resolution for different mapping scales depends on a survey's objectives, but in the absence of logistical constraints, higher resolution is preferred.
-From visual observation, the benefits of higher resolution gridded geophysical data are obvious.
-Details confined to short wavelengths such as near surface magnetic sources or small-scale structures are better localised and made more apparent in high resolution.
-These features may provide important geological context, or better delineate structures manifested in the data.
-In addition to human interpretation, machine processing of geophysical data is benefitted by using higher resolution data, with the typically negligible cost of increased computational load \parencite[e.g.][]{fitzgeraldArtificialIntelligenceTechniques2021}.
+\subsection{Survey Grid Imputation}
+In order to fill in missing high-resolution data without additional sampling, it is required to predict values at new sample points.
+Numerically, this can be done using interpolating functions, such as splines \parencite{keysCubicConvolutionInterpolation1981}, kriging \parencite{hansenInterpretiveGriddingAnisotropic1993} or other methods.
+These methods are limited in their performance by the quality of their neighbouring observed values, and their distance.
+Deep learning methods similarly use their spatial neighbours, but do so in the context of trainable filters, and across larger extents of the input.
+In this way, deep learning super-resolution upscaling models are supported by latent information retained from the training dataset, in addition to information contained within the input being upscaled.
 
-\subsection{Enhancing grid detail}
-In order to resolve additional detail without additional sampling, it is required to predict the values of missing sample points.
-Numerically, this can be done by interpolating functions, such as splines \parencite{keysCubicConvolutionInterpolation1981} or nearest neighbour methods.
-These methods are limited in their performance by the quality of their neighbouring observed values, and their distance.
-Deep learning methods also use their spatial neighbours, but do so in the context of trainable filters, and across larger extents of the input.
-In this way, deep learning super-resolution upscaling models are supported by latent information retained from the training dataset, in addition to information contained within the input being upscaled.
-For photographs and natural image rasters with large representative training corpuses available, such as ImageNet \parencite{dengImageNetLargescaleHierarchical2009} and DIV2K \parencite{agustssonNTIRE2017Challenge2017}, super-resolution methods have progressed to the point that high quality enhancement at four times scale in each axis is readily accessible to end-users \parencite[e.g.][]{wangRealESRGANTrainingRealWorld2021}.
-
+For photographs and natural image rasters with large representative training corpuses available, such as ImageNet \parencite{dengImageNetLargescaleHierarchical2009} and DIV2K \parencite{agustssonNTIRE2017Challenge2017}, super-resolution methods have progressed to the point that high quality enhancement at four times scale is readily accessible to end-users \parencite[e.g.][]{wangRealESRGANTrainingRealWorld2021}.
 Photographs and other rasters of interest to computer vision are typically created by capturing light from an image sensor or are explicitly mapped on a grid using a raster graphics program.
 These data are encoded to regular arrays of pixel values, commonly as three-channel rasters representing the red, green, and blue intensities of each pixel.
-In these rasters, each pixel is regularly distributed, and the resolution is isotropic and solely a factor of the pixel density of the sampling or constructed grid.
-Contrastingly, geophysical grid rasters are created by point sample regularisation.
-These point samples are irregularly spaced and often directionally dependent, especially in the case of airborne flight line sampling.
-The resulting grid rasters may have isotropic cell size, but the frequency content in each axis is anisotropic, being a factor of the sample spacing and direction.
-These grids also single channel, storing measurements of the geophysical property of interest.
+In these rasters, each pixel is regularly distributed, and the resolution is isotropic and a factor of the pixel density of the sampling sensor or the software defined grid.
 
-A property of potential fields is that the power in high frequencies decreases with greater distance from the source.
-At large source-sensor separations, higher frequencies are diminished below the noise floor to the point of unobservability, resulting in grids that show only broad scale features --- typically representing spatially extensive features deeper in the crust.
-One method of restoring high frequency information to these grids is to calculate the potential as if it were sampled at a smaller source-sensor distance.
-This is known as downward continuation \parencite{bullardDeterminationMassesNecessary1948}.
-It is common for noise in the sampled grid product to be significantly worsened in the downward continued product, limiting the useful vertical extent of the method 6 times the cell size \parencite{dampneyEquivalentSourceTechnique1969,zuoDownwardContinuationTransformation2020}.
-Once an independent signal has vanished below the noise floor, it is impossible to recover separately from noise components.
+Contrastingly, geophysical grid rasters are created by point sample regularisation and interpolation.
+These point sample locations are irregularly spaced and directionally dependent, especially in the case of airborne flight line sampling.
+The resulting grid rasters may have isotropic cell size, but the frequency content in each axis is anisotropic, being a factor of the sample spacing in the line-perpendicular and line-parallel directions.
+These grids are also single channel, storing measurements of the geophysical property of interest.
+Crucially, the resolution of a geophysical grid refers to the underlying frequency content of the regularised survey data, which may not be directly linked to the dimensions of the raster in which they are rendered.
+% Because of these and the differences outlined in \Cref{sec:resinsurveys}, pre-existing super-resolution models trained on large image corpuses are not suitable for predicting higher frequency signals in geophysical grids.
+
+Frequency content in potential field grids can also be enhanced by calculating the potential as if it were sampled at a smaller source-sensor distance, in a process known as downward continuation \parencite{bullardDeterminationMassesNecessary1948}.
+At large source-sensor distances, high frequencies are diminished below the noise floor to the point of unobservability, resulting in grids that show only broad scale features, typically representing spatially extensive features deep in the crust.
+It is common for noise in the sampled grid product to be significantly increased in the downward continued product, limiting the useful vertical extent of the method to six times the cell size \parencite{dampneyEquivalentSourceTechnique1969,zuoDownwardContinuationTransformation2020}.
 Downward continuation can be performed with field- or source-based methods \parencite{pilkingtonPotentialFieldContinuation2017}.
+Resolution enhancement through neural network approaches to downward continuation \parencite{liStableDownwardContinuation2023,yeHighprecisionDownwardContinuation2022} is a promising research direction in super-resolution geophysics, but is distinct from the proposed line-spacing based method due to its use of paired vertically continued training data rather than paired line spacing differing data.
 
-Recently, resolution enhancement with short wavelength prediction has been performed with deep learning super-resolution \parencite{smithMagneticGridResolution2022}.
-While this method is capable of predicting short wavelengths and accurately super-resolving low-resolution magnetic grids, the data resolution was not limited by sample spacing, but rather a polynomial filter that supressed high frequencies.
-Additionally, the trained network was limited to \num{4} times upscaling during inference.
+Recently, aeromagnetic resolution enhancement has been performed with deep learning SR \parencite{bavandsavadkoohiHighresolutionAeromagneticMap2023,smithMagneticGridResolution2022}.
+Both methods operate on regional aeromagnetic data at four times scale, using variants of the SRGAN convolutional neural network originally by \textcite{ledigPhotorealisticSingleImage2017}.
+The method of \textcite{smithMagneticGridResolution2022} is capable of predicting short wavelengths and accurately super-resolving low-resolution magnetic textures, however, the low-resolution transform was a polynomial filter that supressed high frequencies, rather than the proposed line spacing method.
+The method of \textcite{bavandsavadkoohiHighresolutionAeromagneticMap2023} uses low- and high-resolution aeromagnetic data from regional surveys, with a realistic low-resolution transform from line spacing and sample altitude differences.
+However, the dataset used contains only \qty{267} samples from surveys in Quebec, Canada, with side lengths of \qty{14400}{\m} over \qty{48} cells in each axis.
+The proposed method is distinct from these prior works with its use of synthetic data in coordination with real survey data to improve generalisation, and the use of a modern MLP-based SR network.
 
-\subsection{Convolutional neural networks for super-resolution}
+\subsection{Neural networks for super-resolution}
+Super-resolution (SR) is the task of predicting interpolating values to resolve rasters with a higher resolution, and has been predominantly performed in the domain of Convolutional Neural Networks (CNN) following the success of SRCNN \parencite{dongLearningDeepConvolutional2014}.
+Recently, CNNs have been surpassed by coordinate multilayer perceptron (CMLP) neural networks for the task of SR \parencite{chenLearningContinuousImage2021}.
+CMLP networks learn a signal as a function of its coordinates, and SR is performed by predicting pixel values on the continuum of coordinates in the domain of the learnt function, including at scales that were not seen during training.
+Key to the performance of these networks are implicit functions, which parameterise a function learned from training dataset with a neural network analogue.
+The network analogue can then be queried for information that fits the learnt function but was not included in the training data.
+
 Convolutional Neural Network (CNN) methods have long been well suited for computer vision tasks such as image classification and, more recently, super-resolution.
-CNNs excel in deep learning tasks for raster data, due in part to the receptive field of the network.
-The receptive field is formed from stacked layers of small convolutional kernels, typically with a size of 3x3 cells for modern CNNs.
+In an image raster, neighbouring pixels define simple features, and these features combine in the wider image to define complex features.
+CNNs excel in deep learning tasks for these data, due in part to the structure of the receptive field of the network.
+The receptive field is formed from stacked layers of small convolutional kernels, typically with a size of \numproduct{3 x 3} cells for SR CNNs.
 These low-level kernels learn simple functions, which are convolved with deeper layers to learn increasingly complex filters across a larger image extent, widening the receptive field.
-In an image, local features define important structures, which, as the network deepens, combine in the wider receptive field to define more global features.
-Once trained, these filters are conditioned to transform low-resolution features into high-resolution features, using the neighbouring input values of the low-resolution grid in the context of filters learnt from the training data.
+Once trained, the learnt functions are conditioned to transform low-resolution features into high-resolution features, using the neighbouring input values of the low-resolution grid in the context of filters learnt from the training data.
+
+The earliest application of CNN SR was demonstrated by \parencite{dongLearningDeepConvolutional2014}, where convolutional layers are used for low-resolution patch extraction, feature mapping, and reconstruction of high-resolution images.
+The outputs of each convolutional layer are similar to hand-crafted filters or feature dictionaries in earlier example-based super-resolution methods \parencite{freemanExamplebasedSuperresolution2002}, but the learnt filters are more numerous and fully trainable with the deep learning approach.
+Following the success of \parencite{dongLearningDeepConvolutional2014}, many iterative improvements have been made to CNN based SR\@.
+These include SRCNN \parencite{dongImageSuperresolutionUsing2016}, RDN \parencite{zhangResidualDenseNetwork2018}, ESRGAN \parencite{wangESRGANEnhancedSuperresolution2018}, and others \parencite{ledigPhotorealisticSingleImage2017,limEnhancedDeepResidual2017}.
+While each of these works contribute unique features to CNN-based super-resolution, they follow a common stacked block design.
+This comprises a set of initial input feature extraction convolutions, a sequence of convolutional blocks with activations (neurons), some number and arrangement of intermediate residual learning pathways (skip connections), and an upsampling block for feature upscaling and convolving latent features back to image space.
+
+Recently, multi-layer perceptrons (MLPs) have become a state-of-the-art alternative for SR\@.
+In an MLP (also known as a fully connected network), all neurons in a given layer are connected to all neurons in the immediately adjacent layers.
+This contrasts with CNNs, where spatially related neurons are sparsely connected between layers via a convolutional kernel.
+Fully connected MLP networks have been described for several decades, however, networks partly or entirely comprising fully connected layers saw little interest for SR following the success of SRCNN \parencite{dongLearningDeepConvolutional2014}.
+It was noted in \parencite{arjovskyWassersteinGAN2017} that MLP networks were known to be a poor backbone in generative adversarial networks, an architecture which was seeing wide application in contemporaneous computer vision tasks.
+One early SR network featuring fully connected layers was for multi-frame video super-resolution \parencite{chengFastVideoSuperresolution2012}, while another was used to investigate depth images \parencite{chenSingleDepthImage2018}.
+\Textcite{tanFeatureSuperResolutionMake2018} aimed to create high-resolution feature maps for machine interpretation rather than subsequent visual observation.
+Among the first image SR networks incorporating an MLP for human perception was by \parencite{tangDeepResidualNetworks2020}, who replace convolution operations in their network's final image reconstruction with a fully connected layer.
+They suggest a fully connected layer outperforms convolutions for image reconstruction due to the wider receptive field of the MLP\@.
+
+One limitation of these CNN-based networks is the challenge of upscaling data at non-integer scales, and scales beyond those in the training dataset.
+This was achieved by \parencite{huMetaSRMagnificationarbitraryNetwork2019,wangLearningSingleNetwork2021}, however recent approaches using implicit function based networks have improved performance.
+Implicit functions aim to learn a specific function parameterised entirely by the weights of a neural network.
+In an image or geophysical grid context, the function may map grid coordinates to the value at those coordinates.
+While extensively developed for point cloud and other 3D data \parencite[e.g.][]{jiangLocalImplicitGrid2020} there have been numerous examples for super-resolution.
+These include SIREN \parencite{sitzmann2019siren}, LIIF \parencite{chenLearningContinuousImage2021}, and LTE \parencite{leeLocalTextureEstimator2022}.
+Notably in these networks, the learnt function has continuous domain, despite the discontinuous grid input.
+Super-resolution can be achieved by sampling the learnt function at any arbitrary grid cell size smaller than the original input \parencite{chenLearningContinuousImage2021}.
+% While a stand-alone MLP such as SIREN is capable of parameterising a single function, when used in an autoencoder framework (such as with LIIF or LTE), an arbitrary input can be encoded using a CNN, upscaled, and subsequently reconstructed using fully connected layers \Cref{fig:ltenet}.
+This approach generalises MLP based super-resolution to any image or grid not seen in the training set.
+MLP-based autoencoders for super-resolution have been shown in LIIF \parencite{chenLearningContinuousImage2021} and LTE \parencite{leeLocalTextureEstimator2022}.
+While both are structured as autoencoders with a CNN or transformer-based encoder followed by an MLP decoder, LTE is implemented here for its higher performance in the task of image super-resolution.
+
+The encoder in these networks can use the feature extraction capability of traditional SR CNNs such as EDSR \parencite{limEnhancedDeepResidual2017} or RDN \parencite{zhangResidualDenseNetwork2018}, or a SwinIR \parencite{liangSwinIRImageRestoration2021} transformer-based encoder.
+In the original implementation of the CNN SR networks, the extracted image features are upscaled and returned to the image domain by convolutional layers.
+In LTE, the latent extracted features are further processed by the LTE network component before reconstruction to image space by an MLP\@.
+% An overview of the structure of the LTE network is shown in \Cref{fig:ltenet}.
+The LTE component of the LTE network transforms the encoded latent features to frequency and amplitude features using trainable convolutions.
+Both the amplitude and frequency features are then upscaled using nearest neighbour filter interpolation.
+The frequency components are combined with phase information, which is extracted from the input by an additional MLP, and the resulting features are passed through a sinusoidal activation function before being combined with the amplitude features.
+Finally, the decoding MLP restores these frequency domain features to the spatial image domain.
+To precondition the network toward learning high-resolution features, a long-range skip connection with bilinear upscaling passes low-resolution content common between the upscaled LR and the HR counterpart to the output of the MLP\@.
 
@@
     % \includegraphics[width=\textwidth]{fig/p2/image1.png}
-    \caption[An example CNN]{
-        An example deep learning Convolutional Neural Network (specifically RDN (Zhang et al., 2018)), showing a variety of convolution operations (blue rectangles), activation functions (orange), and intermediate pathways (green, blue, or black arrows).
+    \caption[The LTE network]{
+        A simplified representation of the super-resolution LTE network.
+        The encoder is marked as \(E_\phi{}\).
+        \(f_\Theta{}\) is an MLP network used as the decoder for image reconstruction.
+        A long-range skip connection with simple upscaling is marked with an arrow.
+        The LTE network block performs high-resolution upscaling of extracted features in the Frequency domain.
+        Simplified from \textcite{leeLocalTextureEstimator2022}.
     }
-    \label{fig:egcnn}
+    \label{fig:ltenet}
 \end{figure}
 
-The earliest application of deep learning super-resolution was demonstrated by \parencite{dongLearningDeepConvolutional2014,dongImageSuperresolutionUsing2016}, which uses convolutional layers for low-resolution patch extraction, mapping, and reconstruction of high-resolution images.
-These layers are analogous to hand-crafted processes in contemporary example-based super-resolution methods, but are fully trainable with the deep learning approach.
-Following the success of \cite{dongLearningDeepConvolutional2014}, many iterative improvements have been made to CNN based SR\@.
-These include SRCNN \parencite{dongImageSuperresolutionUsing2016}, RDN \parencite{zhangResidualDenseNetwork2018}, ESRGAN \parencite{wangESRGANEnhancedSuperresolution2018}, and others \parencite{ledigPhotorealisticSingleImage2017,limEnhancedDeepResidual2017}.
-While each of these works contributes unique features to CNN based super-resolution, they follow a common design.
-This comprises a set of initial input feature extraction convolutions, a sequence of convolutional blocks with activations (neurons), some number and arrangement of intermediate residual learning pathways (skip connections), and an upsampling block for feature upscaling and convolving latent features back to image space e.g.
-\cref{fig:egcnn}.
-Additionally, a majority of contemporary super-resolution networks investigate upscaling at a fixed scale, typically 4x.
-While these networks can be trained for different factors using an appropriately scaled training dataset, they are constrained during inference to factor they are trained for.
-Arbitrary scale super-resolution has been achieved using convolutional networks, notably Meta-SR \parencite{huMetaSRMagnificationarbitraryNetwork2019} and scale-arbitrary SR \parencite{wangLearningSingleNetwork2021}.
-However, these methods perform poorly on novel data outside of their training scale distribution \parencite{chenLearningContinuousImage2021}.
+\section{Data and Experimental Methods}
+A realistic geophysical low-resolution transform is developed by simulating aeromagnetic sampling of high-resolution survey grid datasets, and re-gridding the resulting samples.
+The proposed dataset methodology uses synthetic forward modelled potential field data to train a selected performant super-resolution network, and the resulting baseline model is subsequently used for transfer learning to fine-tune train the model with real aeromagnetic survey grid data.
+The performance of the method is qualitatively described on real survey grid extents, and quantitatively described with standard image quality metrics.
 
-\subsection{Multi-layer Perceptron neural networks}
-While Multi-layer Perceptron networks (MLP) have been used in science for decades, until recently networks partly or entirely comprising fully connected layers were not known for super-resolution.
-\cite{tangDeepResidualNetworks2020} use stacked convolutional blocks for feature extraction, with a final fully connected layer for reconstructing a super-resolved image from the extracted features.
-They suggest an MLP layer performs better for image reconstruction than a convolutional layer due to the wider receptive field of the MLP\@.
-In an MLP, all neurons in each layer are connected to all neurons in the adjacent layer.
-This contrasts with convolutional neural networks, where array elements are combined by the convolutional kernel as it feeds into deeper layers, which causes them to be sparsely connected.
-A 1x1 convolutional kernel is occasionally considered analogous to an MLP\@.
-Only in recent years have MLP based networks become a state-of-the-art alternative for super-resolution.
+\subsection{Synthetic potential fields}
+A novel synthetic dataset is used to train and validate the initial model.
+This is based on the Noddyverse \parencite{jessellNoddyverseMassiveData2022}, a suite of one million geologically realistic petrophysical voxel models with accompanying forward modelled geophysics.
+The block models are constructed as a sequence of realistic geological histories with an initial stratigraphy and tilt, followed by a three randomly selected deformation events of fold, fault, unconformity, dyke, plug, shear-zone, or tilt.
+Each model in the suite records the parameters of the deformation history, the complete final 3D subsurface geology voxel model with associated petrophysics, and final forward models of the magnetic and gravity potential fields.
+All data are modelled at \qty{20}{\m} spacing in each direction for \qty{4000}{\m} (\qty{200} cells) in each axis, and the potential field forward models are calculated at \qty{100}{\m} above the flat model surface.
+Only the magnetic forward model is used in this work, however the described method can be followed to train a model capable of super-resolving grids of the gravity potential field.
+
+Included in the published dataset \parencite{jessellNoddyverseMassiveData2022} are a complete list of all models, and a separate list comprising a randomly selected subset of \qty{10000} models.
+The first \qty{960000} models from the full list are used for training, and the last \qty{8000} models are used for validation.
+In both cases, this excludes models present in the list of \qty{10000} models, which are reserved as a test data set.
+The \numproduct{200 x 200} cell forward models are cropped to \numproduct{180 x 180} cells, subsequently referred to as the ground truth (GT) models.
+
+\subsection{Simulated surveys}
+To simulate the acquisition of aeromagnetic data, the \qtyproduct{20 x 20}{\m} total magnetic intensity (TMI) forward models are line sampled at a factor of \(4n\)  (i.e., \(4n x 20\) m sampling in x, \(1 x 20\) m sampling in y).
+The line direction is nominally ``North-South'' such that entire array columns are sampled or unsampled.
+The \(n = 1\) case is the high-resolution target (HR) with every fourth line of GT sampled at a nominal line spacing of \qty{80}{\m}, similar to real-world regional high-resolution airborne geophysical surveys.
+These sampled line data are gridded at a cell size of \qty{20}{\m} using the cubic method from Verde \parencite{uieda2018}, which is one quarter of the line spacing, following the convention of \textcite{reidAeromagneticSurveyDesign1980}.
+It is important to note that while the HR grid has a cell size of \qty{20}{\m}, it is not equivalent to the \qty{20}{\m} cell size GT grid, because unsampled cells are interpolated during the gridding process.
+The result is a loss of high frequency detail in the line perpendicular direction, as well as the loss of features present only in the unsampled lines.
+
+The low-resolution input data (LR) are sampled from GT at \(n = 4\).
+At this scale the LR line spacing is \qty{320}{\m}, the cell size is \qty{80}{\m}, and the array shape is \numproduct{45 x 45} cells, covering the same extent as HR\@.
+Subsampling and gridding of the pre-generated Noddyverse data is performed on-the-fly during training.
+The cubic method of Verde (itself implemented by Scipy Clough-Tocher 2D interpolation \parencite{2020SciPy-NMeth}) produces a \(C^1\) smooth grid with minimised curvature.
+This type of gridding is common for regularising geophysical data and creates a variety of typical low-resolution artefacts such as aliasing and bullseye artifacts.
+% \Cref{fig:lrdata} shows an example of the resulting high- and low-resolution grids for the proposed line sampling and gridding process.
+
+This method of generating low-resolution training data is distinct from computer-vision image super-resolution, where a three-channel colour image is downsampled using an interpolating filter such as nearest neighbour or cubic splines operating on all pixels in the original image.
+It is also distinct from previous geophysical deep-learning super-resolution work \textcite{smithMagneticGridResolution2022} where the raster data used are extracts from regional compilation TMI maps, created using a third order Newton polynomial filter, similar in effect to cubic spline interpolation.
+The downsampling method used here is representative of low-resolution airborne sampling and subsequent gridding processes in real world geophysics.
+
+The distribution of magnetic anomaly values within both the magnetic merged grid of Western Australia and the Noddyverse dataset is unimodal and centred near \qty{0}{\nano\tesla}, with a standard deviation of approximately \qty{500}{\nano\tesla}.
+Despite this, the HR and LR grids are clipped between \qty{-10000} and \qty{10000}{\nano\tesla}, then min-max normalised to the range 0 to 1.
+This wide clipping range is selected to ensure adequate reconstruction of structures with high magnitude intensities, which are important to geological interpretation.
+Any predictions made outside of this range during inference are also clipped.
+
+% \Cref{fig:lrdata} presents data generated with the proposed low-resolution transform for a range of geological histories.
+% \Cref{fig:lrdata}A shows a synthetic tile with the geological history ``stratigraphy, tilt, fold, tilt, fold''.
+% The forward model contains a long-wavelength linear magnetic structure, and a sharply defined high intensity magnetic unit.
+% The high frequencies required to define the second feature are not captured by the LR grid sampling, resulting in aliasing.
+% \Cref{fig:lrdata}B is recorded with a geological history of ``stratigraphy, tilt, fold, fold, fold'', and presents two folded negative anomalies that converge to the south.
+% Insufficient sampling in the LR grid causes the spatial relation to be incorrectly interpreted as converging in the centre of the figure, which may be interpreted differently than in the target high-resolution grid.
 
@@
     % \includegraphics[width=\textwidth]{fig/p2/image1.png}
-    \caption[An example deep learning Multi-layer Perceptron]{
-        The encoder, $E_\Phi$, can be implemented as a feature extractor based on RDN prior its upsampling layer \cref{fig:egcnn} or SwinIR \parencite[per][]{leeLocalTextureEstimator2022}.
-        $f_\theta$ is an MLP network used as the decoder for image reconstruction.
-        A long-range skip connection with simple upscaling allows low-resolution information to bypass the network.
+    \caption[Low-resolution geophysics grids]{
+        The result of the proposed sampling and gridding on a selection of synthetic tiles loaded from the collection of \parencite{jessellNoddyverseMassiveData2022} at 4x scale.
+        Note the coloured lines and accompanying tick marks in the ground-truth grid (GT, left) indicate cells which are sampled and used for gridding in the low-resolution grid (LR, right).
+        High-resolution (HR, middle) is sampled and gridded from GT, with survey lines indicated by minor tick marks.
+        The minimum curvature gridding process results creates a variety of low-resolution degradations.
     }
-    \label{fig:egmlp}
+    \label{fig:lrdata}
 \end{figure}
-
-\subsection{Implicit functions with multi-layer perceptron neural networks}
-Implicit functions aim to learn a specific function parameterised entirely by the weights of a neural network.
-In an image or geophysical grid context, the function maps grid coordinates to the value at those coordinates.
-While extensively developed for point cloud and other 3D data \parencite[e.g.][]{jiangLocalImplicitGrid2020}, there have been numerous examples for super-resolution.
-These include SIREN \parencite{sitzmann2019siren}, LIIF \parencite{chenLearningContinuousImage2021}, and LTE \parencite{leeLocalTextureEstimator2022}.
-Notably in these networks, the learnt function has continuous domain, despite the discretised input.
-Super-resolution can be achieved by sampling the learnt function at any arbitrary grid cell size smaller than the original input \parencite{chenLearningContinuousImage2021}.
-While a stand-alone MLP such as SIREN is capable of parameterising a single function, when used in an autoencoder framework (such as with LIIF and LTE), an arbitrary input can be encoded using a CNN, upscaled, and reconstructed using fully connected layers \cref{fig:egmlp}.
-This approach generalises MLP based super-resolution to any image or grid, even those not seen in the training set.
-
-\subsection{Local Texture Encoder}
-Examples of MLP based autoencoders for for learning continuous image representation super-resolution are LIIF \cite{chenLearningContinuousImage2021} and  LTE \cite{leeLocalTextureEstimator2022}.
-While both are structured as autoencoders, with a CNN or transformer-based encoder followed by an MLP decoder, LTE is selected for its higher performance in the image super-resolution domain compared to LIIF\@.
-The CNN encoder in these networks can use the feature extraction capacity of traditional SR CNNs such as EDSR \parencite{limEnhancedDeepResidual2017} or RDN \parencite{zhangResidualDenseNetwork2018}, without their upscaling blocks.
-Lee and Jin find LTE achieves higher performance when using a SwinIR transformer based encoder.
-In the original implementation of these CNN SR networks, the extracted image features are upscaled and returned to “image-space” by convolutional layers to reshape to image dimensions.
-In LTE and LIIF, the extracted features become latent features with identical dimension as the original input image and are further processed by the network, before reconstruction to image space by an MLP\@.
-Additionally, of interest to geophysics, a significant proportion of the LTE super-resolution network is trained on features in the Fourier domain.
-The encoder extracts image features, but these are immediately transformed to the frequency domain by fully trainable convolution layers, which output amplitude and frequency features.
-Phase features are also extracted from the image by a fully connected network, and is used during image reconstruction.
-Nearest neighbour upsampling is performed in the frequency domain to achieve the required output scale.
-A long-range skip connection passes low-frequency image content to the output of the network, in order to emphasise the learning of high-frequency content within the network.
-
-\section{Material and Methods}
-\subsection{Synthetic dataset}
 %TODO
 
-\section{Declaration of Competing Interest}
-The authors declare the following financial interests / personal relationships which may be considered as potential competing interests: This work was supported by a Rio Tinto Iron Ore PhD scholarship.
+\subsection{Synthetic dataset training setup}
+While each of the models in the synthetic training dataset have unique petrophysical parameters, there are only \qty{343} distinct sequences of deformation events.
+This leads to feature similarities between many samples within the dataset, varying in rotation, scale, locality, and magnitude.
+For this reason, augmentation is unnecessary, and the line sampling direction is kept nominally north-south.
+Due to this similarity and the \qty{960000} samples used from the Noddyverse dataset, only one epoch is used.
+The batch size is set to 8. The Adam optimiser is used with an initial learning rate of \num{0.0001}, and this is successively halved at 50\%, 70\%, and 90\% of the overall training progress.
+Training was undertaken on a Nvidia RTX 3090 with \qty{24}{\giga\byte} of VRAM, in an Intel i9-10900KF workstation with \qty{64}{\giga\byte} of RAM\@.
+The duration for the single epoch was approximately \qty{10}{\hour}.
+
+%TODO
+
+\subsection{Fine-tuning with aeromagnetic survey data}
+To improve the performance of the model on real world geophysical data, the synthetic-trained model is subsequently trained on data re-gridded from the \qty{20}{\m} magnetic merged grid of Western Australia 2020 \parencite{brett20MagneticMerged2020}.
+These data are selected from extents of the state grid where surveys were performed at \qty{100}{\m} line spacing or closer, which when gridded at \qty{20}{\m} cell size, support the same Nyquist wavelength as the \qty{20}{\m} cell size of the Noddyverse dataset.
+Small holes and gaps in overlapping survey coverage were closed to ensure sufficient contiguous coverage.
+These data are initially extracted as approximately \num{10000} “ground truth” patches of \numroduct{200 x 200} cells at \qty{20}{\m} cell size, equivalent to the synthetic dataset.
+High- and low-resolution training pairs are created from these data using the same line sampling process as described in \Cref{sec:2.2}.
+Due to the smaller number of patches, these data are augmented during training.
+The first augmentation is extracting three additional sets of repeat patches, offset in both directions by 53, 107, and 150 cells.
+The geological features present in these offset patches are shifted compared to the original, and entirely different cells are subsampled in each offset.
+Across all four sets of offsets, there are \num{37726} unique samples.
+The second augmentation is a randomly applied 90-degree rotation of the ground-truth grid prior subsampling and gridding, resulting in grid data with features that are sampled perpendicular to the unaugmented lines.
+The remaining augmentations are each randomly applied with \qty{50}{\percent} chance, and are flips and 90-degree rotations of the high- and low- resolution grids after gridding.
+
+Training the real survey model is performed after loading initial weights from the synthetic-trained baseline model.
+All hyperparameters remain identical to those used for synthetic baseline training, including the learning rate schedule and initial rate of \num{0.0001}.
+Because of the smaller dataset and use of augmentations, \num{10} epochs were used, increasing the training duration by approximately one hour.
+
+\subsection{    Network selection }
+Local Texture Estimator \parencite{leeLocalTextureEstimator2022} is implemented to super-resolve synthetic and real potential field geophysical data with low resolution resulting from line spacing.
+Because total magnetic intensity data are single channel, the input and output channel count are set to one.
+The SwinIR feature encoder implementation by is used, and the MLP decoder retains the same configuration as the authors.
+
+\subsection{}
+Quantitative Measure
+
+Due to the dynamic range of magnetic anomaly grids and the relative importance of structural accuracy for gridded data, image quality assessment such as peak signal-to-noise ratio or mean-squared error are an inadequate quantitative measure of upscaling performance for geophysics.
+Instead, Feature Similarity \parencite{lin{Zhang et al 2011zhangFSIMFeatureSimilarity2011} was selected to quantify the quality of the super-resolved image, because it is a full reference image similarity metric that quantifies structural similarity using phase and local gradient magnitude components.
+
+\section{Results}
+Model performance is quantified using FSIM, and it is seen that fine-tune training increases FSIM score for the task of super-resolution for aeromagnetic grids over the baseline model.
+Qualitative results are shown to compare the outputs from the two models, the baseline model that is trained with synthetic data and the fine-tuned model trained with open access survey data.
+Each figure follows the following layout for the grids from left to right; the ground truth (GT) \numproduct{200 x 200} cell tile is presented with low-resolution sampled data indicated in colour.
+The target high-resolution grid (HR), created from sampling and gridding GT at \qty{80}{\m} line spacing, is shown for comparison.
+The \numproduct{45 x 45} cell low-resolution grid (LR) shows the result of the described sampling and gridding method at \qty{320}{m} line spacing, and is upscaled for display using bicubic interpolation.
+The model prediction (SR), using an input of LR with the proposed method, is shown with the corresponding FSIM metric between HR and SR\@.
+
+\Cref{fig:3} contains open access grid data from the Eastern Goldfields Superterrane of Western Australia, and prepared using the proposed method.
+Strong line-perpendicular smearing in LR is reduced in both SR predictions, and fine structural divisions are better delineated.
+NW striking features around in HR are aliased in LR and subsequently incorrectly rotated by 90 degrees in the baseline SR prediction (\Cref{fig:3}A).
+The fine-tuned model (\Cref{fig:3}B) resolves the correct strike, and separates the two features present.
+The enhanced structural similarity is reflected by the higher FSIM score in the fine-tuned model.
+\begin{figure}[hbt]
+    % \includegraphics[width=\textwidth]{fig/p2/image1.png}
+    \caption[Super-resolution geophysics grid results]{
+    }
+    \label{fig:lrdata}
+\end{figure}
+%TODO
+
+\section{Discussion}
+The Noddyverse synthetic training dataset comprises geology models with a variety of realistic petrophysics and geological histories, and was sampled using simple but realistic airborne survey methodology.
+Furthermore, real survey data used to fine tune the model were extracted from extents across a range of different terranes in Western Australia.
+As such, the method and trained models generalise to the geological terranes represented in the Noddyverse and high-resolution state grid extents.
+Granitic textures in real grid data are not represented in the synthetic Noddyverse training set, and show the least improvement by the method.
+Different geological units present different features in magnetic potential field grids, with deformed igneous units typically causing abundant contextually important short-wavelength content.
+These features, such as faulted or folded dykes, tend to show the most perceptual improvement in their structure following super-resolution upscaling.
+This is due to the high performance of the method for reducing aliasing effects from the gridding process, and is apparent in the accurate reconstruction of linear features from discrete “string of beads” aliased features.
+Long-wavelength features and smooth gradients, such as those present in sedimentary units or areas of cover are accurately upscaled in the proposed method, however these are also adequately upscaled with simple cubic spline interpolation of the low-resolution grid because they do not require predicted high frequency components.
+The exception for super-resolution having higher quality is in areas of low magnitude TMI of only a few nanoTesla across the entire extent.
+In these cases, the otherwise minor noise introduced by the super-resolution process dominates the residual.
+
+The synthetic forward models are associated with geological history class labels, providing an opportunity for more targeted fine-tuning by event history.
+It is possible to filter the data to contain only the events of interest, which would prepare a baseline model targeting a single geological domain.
+The baseline model prepared in this work demonstrated good performance across a range of geological domains, but may be improved for targeted domains using the filtered approach.
+
+\section{Conclusion}
+An approach for upscaling geologically diverse geophysical survey grid data is proposed, which adopts transfer learning from synthetic data to better generalise super-resolution across different geological domains.
+Using the preeminent LTE neural network, synthetic magnetic forward models were used to prepare a baseline model capable of upscaling survey grids at four times scale.
+Further, this baseline model was fine-tuned with open access survey grid data, prepared with a low-resolution transform appropriate for aeromagnetic geophysics.
+Low-resolution features incorrectly enhanced by the synthetic baseline model were correctly resolved following fine-tune training with these data, and the model is capable of upscaling grids with \qty{320}{\m} line spacing to \qty{80}{\m} line spacing with an average FSIM score of \num{0.9731}.
+% \section{Declaration of Competing Interest}
+% The authors declare the following financial interests / personal relationships which may be considered as potential competing interests: This work was supported by a Rio Tinto Iron Ore PhD scholarship.
 

### 2023-10-06 paper1.tex
Merge branch 'main' into paper2
Add affiliations

@@
 \begin{document}
-\setcounter{chapter}{1}
-\author{\and{Luke Thomas Smith} \and{Tom Horrocks} \and{Eun-Jung Holden} \and{Daniel Wedge} \and{Naveed Akhtar}}
+% \setcounter{chapter}{1}
 \title{Magnetic grid resolution enhancement using machine learning: A case study from the Eastern Goldfields Superterrane}
+\author[1*]{Luke Thomas Smith}
+\author[1]{Tom Horrocks}
+\author[1]{Eun-Jung Holden}
+\author[1]{Daniel Wedge}
+\author[2]{Naveed Akhtar}
+\affil{Centre for Data-Driven Geoscience, School of Earth Sciences, The University of Western Australia (M006), 35 Stirling Highway, 6009 Perth, Australia}
+\affil{Department of Computer Science and Software Engineering, The University of Western Australia (M002), 35 Stirling Highway, 6009 Perth, Australia}
 \date{2022-09-21}
 \maketitle{}
-\label{paper1}
 

### 2023-10-06 paper3.tex
Add affiliations

@@
 \setcounter{chapter}{1}
-\author{{Luke Thomas Smith} \and{Tom Horrocks} \and{Naveed Akhtar} \and{Eun-Jung Holden} \and{Daniel Wedge}}
 \title{Implicit Neural Representation for Potential Field Geophysics }
+\author[1*]{Luke Thomas Smith}
+\author[1]{Tom Horrocks}
+\author[2]{Naveed Akhtar}
+\author[1]{Eun-Jung Holden}
+\author[1]{Daniel Wedge}
+\affil{Centre for Data-Driven Geoscience, School of Earth Sciences, The University of Western Australia (M006), 35 Stirling Highway, 6009 Perth, Australia}
+\affil{Department of Computer Science and Software Engineering, The University of Western Australia (M002), 35 Stirling Highway, 6009 Perth, Australia}
 \date{\today}
@@
 %TODO - a bit abrupt
-For the task of level grid prediction, the PSNR similarity between a case study reference grid and the proposed method is \SI{40}{\dB}.
-Additionally, directional derivatives of the implicit representation calculated numerically and using automatic differentiation are shown, with average residuals of \SI{0.4} and \SI{0.8}{\nano\tesla\per\m} for the easting and northing derivatives respectively, albeit vertical derivative performance remains limited.
+For the task of level grid prediction, the PSNR similarity between a case study reference grid and the proposed method is \qty{40}{\dB}.
+Additionally, directional derivatives of the implicit representation calculated numerically and using automatic differentiation are shown, with average residuals of \qty{0.4} and \qty{0.8}{\nano\tesla\per\m} for the easting and northing derivatives respectively, albeit vertical derivative performance remains limited.
 
@@
 The case study is performed using data from the 2002 Wolfe Creek meteorite impact magnetic survey \parencite{wolfecreek2019}.
-This high-resolution survey contains \qty{402}{line-kilometres} of data at \SI{50}{\m} line spacing with a nominal terrain clearance of \SI{40}{\m}, with line data collected on North-South transects.
+This high-resolution survey contains \qty{402}{line-kilometres} of data at \qty{50}{\m} line spacing with a nominal terrain clearance of \qty{40}{\m}, with line data collected on North-South transects.
 Prominently featured in the survey are the circular crater rim, and two East-West trending linear dunes to the North of the survey extent.
 The data used for implicit representation excludes the survey tie lines, typically used in airborne geophysical surveys to reduce inter-line levelling noise.
-The mean altitude of the drape surface excluding tie lines is \SI{39.5}{\m}, with a standard deviation of \SI{4.5}{\m}.
+The mean altitude of the drape surface excluding tie lines is \qty{39.5}{\m}, with a standard deviation of \qty{4.5}{\m}.
 The sample locations and recorded altitudes are shown in \Cref{fig:samples}, where it can be seen the crater rim topography causes large deviations to the flown drape.
@@
     \includegraphics[width=0.5\linewidth]{fig/p3/P864_sample_locs.pdf}
-    \caption[Point samples]{Sample altitudes for the Wolfe Creek survey lines. The diverging colourmap has been centred at the nominal survey terrain clearance of \SI{40}{\m}.}
+    \caption[Point samples]{Sample altitudes for the Wolfe Creek survey lines. The diverging colourmap has been centred at the nominal survey terrain clearance of \qty{40}{\m}.}
     \label{fig:samples}
@@
 
-\Cref{fig:grid} shows the INR queried at \(z=\SI{40}{\m}\), which is the nominal terrain clearance of the survey.
+\Cref{fig:grid} shows the INR queried at \(z=\qty{40}{\m}\), which is the nominal terrain clearance of the survey.
 A good qualitative match is achieved between the GA reference grid and the grid queried from the implicit representation, which successfully reconstructs the linear dune features and circular rim features.
-This high performance is quantified by the residuals and peak signal to noise ratio (PSNR) of \SI{40.12}{\dB}.
+This high performance is quantified by the residuals and peak signal to noise ratio (PSNR) of \qty{40.12}{\dB}.
 % Further level grids from other survey extents are included in Appendix A.
@@
     \includegraphics[width=1.0\linewidth]{fig/p3/P864_grid_comparison_40m.pdf}
-    \caption[Grid prediction at the nominal altitude]{Comparison between the reference grid processed by Geoscience Australia (left) and the constant level grid queried from the INR at \SI{40}{\m} (middle).
+    \caption[Grid prediction at the nominal altitude]{Comparison between the reference grid processed by Geoscience Australia (left) and the constant level grid queried from the INR at \qty{40}{\m} (middle).
 The residuals are shown for areas containing reference data (right), with a range of ±2 standard deviations of values in the reference grid.}
@@
 Constant level grids can be queried from the INR at any height.
-\Cref{fig:grid35} shows the case study INR queried at \SI{35}{\m}, which is \SI{5}{\m} lower than the nominal survey altitude.
+\Cref{fig:grid35} shows the case study INR queried at \qty{35}{\m}, which is \qty{5}{\m} lower than the nominal survey altitude.
 While the rim feature can still be interpreted within this lower level grid, the INR fails to demonstrate physically realistic continuation of the field.
@@
     \includegraphics[width=1.0\linewidth]{fig/p3/P864_grid_comparison_35m.pdf}
-    \caption[Grid prediction outside the nominal altitude]{A constant level grid queried from the INR at the height of \SI{35}{\m} (middle).}
+    \caption[Grid prediction outside the nominal altitude]{A constant level grid queried from the INR at the height of \qty{35}{\m} (middle).}
     % AWAGS is 80 m, but we see nothing useful at 80m
@@
 For comparison, the derivatives calculated with AD are compared with numerical derivatives calculated on the level grid queried from the same INR model. 
-While horizontal derivatives queried from the INR correspond well to numerical derivatives calculated on the \SI{40}{\m} level grid in \Cref{fig:hori_grad}, the vertical derivative suffers poor performance (\Cref{fig:vert_grad}).
+While horizontal derivatives queried from the INR correspond well to numerical derivatives calculated on the \qty{40}{\m} level grid in \Cref{fig:hori_grad}, the vertical derivative suffers poor performance (\Cref{fig:vert_grad}).
 This correlates with the poor continuation performance of model when predicting level grids several metres or more beyond the nominal sample height.
@@
     \includegraphics[width=1.0\linewidth]{fig/p3/P864_dv_comparison.pdf}
-    \caption[Vertical derivative]{Vertical derivative grids queried from AD differentiated INR (left) and calculated numerically (right) on the \SI{40}{\m} level grid queried from the INR\@.
+    \caption[Vertical derivative]{Vertical derivative grids queried from AD differentiated INR (left) and calculated numerically (right) on the \qty{40}{\m} level grid queried from the INR\@.
 The proposed method has poor vertical gradient representation, possibly due to the nature of aeromagnetic survey design.}
@@
 Level grids can be queried at arbitrary heights and cell sizes, with the highest accuracy achieved at the realised nominal survey altitude.
-Performance decreases within approximately one standard deviation from that height (\SI{35} to \SI{45}{\m}), with gradual failure of the model outside of that range.
+Performance decreases within approximately one standard deviation from that height (\qty{35} to \qty{45}{\m}), with gradual failure of the model outside of that range.
 It is interpreted from the poor quality of the vertical gradients and out-of-range level grid predictions that the model is learning a function between horizontally coplanar points, and not an accurate vertical continuation function.
@@
 % A demonstration of the method on a large aeromagnetic survey, requiring minibatch training, is included in \Cref{app:menzies}.
-% Training of this representation follows the parameters outlined in \Cref{sec:training}, which were optimised for the Wolfe Creek case study, with the addition of a shuffled minibatch size of \SI{1024000}\@.
+% Training of this representation follows the parameters outlined in \Cref{sec:training}, which were optimised for the Wolfe Creek case study, with the addition of a shuffled minibatch size of \qty{1024000}\@.
 % Attempts to train the CMLP with small batch sizes did not converge.%, reflecting the non-convergence result found for training on very large subsampling factors of the line dataset.

### 2023-10-07 paper2.tex
Small changes from TH
Prior to restructure

@@
 In Section 1.1 we introduce geophysical grids and their differences to image rasters, and introduce synthetic data as a source of training data with geological domain variation.
-In Section 1.2, we review
+In Section 1.2 we review
 
@@
 Minimum Curvature gridding \parencite{briggsMachineContouringUsing1974} is routinely applied in industry applications, as it gives good quality results in rapid time, with minimal manual intervention.
-
 A comprehensive review of spatial interpolation methods is presented by \textcite{liReviewComparativeStudies2011}.
@@
 
-Regions covered by high-resolution aeromagnetic surveys are biased toward prospective geological terranes.
+Regions covered by high-resolution aeromagnetic surveys are biased toward prospective geological terranes. %TODO Cite
 In order to improve the generalisation of the method for regions without high-resolution coverage, transfer learning \parencite{tanSurveyDeepTransfer2018} from synthetic data is used to establish a baseline model on a broad set of geological domains, which is then fine-tuned with high-resolution survey grid data.
@@
 Deep learning methods similarly use their spatial neighbours, but do so in the context of trainable filters, and across larger extents of the input.
-In this way, deep learning super-resolution upscaling models are supported by latent information retained from the training dataset, in addition to information contained within the input being upscaled.
+In this way, deep learning super-resolution models are supported by latent information retained from the training dataset, in addition to information contained within the input being upscaled.
 
@@
 Crucially, the resolution of a geophysical grid refers to the underlying frequency content of the regularised survey data, which may not be directly linked to the dimensions of the raster in which they are rendered.
-% Because of these and the differences outlined in \Cref{sec:resinsurveys}, pre-existing super-resolution models trained on large image corpuses are not suitable for predicting higher frequency signals in geophysical grids.
+Because of these and the differences outlined in \Cref{sec:resinsurveys}, pre-existing super-resolution models trained on large image corpuses are not suitable for predicting higher frequency signals in geophysical grids.
 
@@
 Super-resolution can be achieved by sampling the learnt function at any arbitrary grid cell size smaller than the original input \parencite{chenLearningContinuousImage2021}.
-% While a stand-alone MLP such as SIREN is capable of parameterising a single function, when used in an autoencoder framework (such as with LIIF or LTE), an arbitrary input can be encoded using a CNN, upscaled, and subsequently reconstructed using fully connected layers \Cref{fig:ltenet}.
+While a stand-alone MLP such as SIREN is capable of parameterising a single function, when used in an autoencoder framework (such as with LIIF or LTE), an arbitrary input can be encoded using a CNN, upscaled, and subsequently reconstructed using fully connected layers \Cref{fig:ltenet}.
 This approach generalises MLP based super-resolution to any image or grid not seen in the training set.
+
 MLP-based autoencoders for super-resolution have been shown in LIIF \parencite{chenLearningContinuousImage2021} and LTE \parencite{leeLocalTextureEstimator2022}.
 While both are structured as autoencoders with a CNN or transformer-based encoder followed by an MLP decoder, LTE is implemented here for its higher performance in the task of image super-resolution.
-
 The encoder in these networks can use the feature extraction capability of traditional SR CNNs such as EDSR \parencite{limEnhancedDeepResidual2017} or RDN \parencite{zhangResidualDenseNetwork2018}, or a SwinIR \parencite{liangSwinIRImageRestoration2021} transformer-based encoder.
@@
 In LTE, the latent extracted features are further processed by the LTE network component before reconstruction to image space by an MLP\@.
-% An overview of the structure of the LTE network is shown in \Cref{fig:ltenet}.
+An overview of the structure of the LTE network is shown in \Cref{fig:ltenet}.
 The LTE component of the LTE network transforms the encoded latent features to frequency and amplitude features using trainable convolutions.
@@
 \subsection{Simulated surveys}
-To simulate the acquisition of aeromagnetic data, the \qtyproduct{20 x 20}{\m} total magnetic intensity (TMI) forward models are line sampled at a factor of \(4n\)  (i.e., \(4n x 20\) m sampling in x, \(1 x 20\) m sampling in y).
+\label{sec:simsurveys}
+To simulate the acquisition of aeromagnetic data, the \qtyproduct{20 x 20}{\m} total magnetic intensity (TMI) forward models are line sampled at a factor of \(4n\)  (i.e., \(4n \times 20\) m sampling in x, \(1 \times 20\) m sampling in y).
 The line direction is nominally ``North-South'' such that entire array columns are sampled or unsampled.
+
 The \(n = 1\) case is the high-resolution target (HR) with every fourth line of GT sampled at a nominal line spacing of \qty{80}{\m}, similar to real-world regional high-resolution airborne geophysical surveys.
@@
 This type of gridding is common for regularising geophysical data and creates a variety of typical low-resolution artefacts such as aliasing and bullseye artifacts.
-% \Cref{fig:lrdata} shows an example of the resulting high- and low-resolution grids for the proposed line sampling and gridding process.
+\Cref{fig:lrdata} shows an example of the resulting high- and low-resolution grids for the proposed line sampling and gridding process.
 
@@
 
-% \Cref{fig:lrdata} presents data generated with the proposed low-resolution transform for a range of geological histories.
-% \Cref{fig:lrdata}A shows a synthetic tile with the geological history ``stratigraphy, tilt, fold, tilt, fold''.
-% The forward model contains a long-wavelength linear magnetic structure, and a sharply defined high intensity magnetic unit.
-% The high frequencies required to define the second feature are not captured by the LR grid sampling, resulting in aliasing.
-% \Cref{fig:lrdata}B is recorded with a geological history of ``stratigraphy, tilt, fold, fold, fold'', and presents two folded negative anomalies that converge to the south.
-% Insufficient sampling in the LR grid causes the spatial relation to be incorrectly interpreted as converging in the centre of the figure, which may be interpreted differently than in the target high-resolution grid.
+\Cref{fig:lrdata} presents data generated with the proposed low-resolution transform for a range of geological histories.
+\Cref{fig:lrdata}A shows a synthetic tile with the geological history ``stratigraphy, tilt, fold, tilt, fold''.
+The forward model contains a long-wavelength linear magnetic structure, and a sharply defined high intensity magnetic unit.
+The high frequencies required to define the second feature are not captured by the LR grid sampling, resulting in aliasing.
+\Cref{fig:lrdata}B is recorded with a geological history of ``stratigraphy, tilt, fold, fold, fold'', and presents two folded negative anomalies that converge to the south.
+Insufficient sampling in the LR grid causes the spatial relation to be incorrectly interpreted as converging in the centre of the figure, which may be interpreted differently than in the target high-resolution grid.
 
@@
 
-\subsection{Synthetic dataset training setup}
+\subsection{Synthetic baseline training setup}
 While each of the models in the synthetic training dataset have unique petrophysical parameters, there are only \qty{343} distinct sequences of deformation events.
@@
 Small holes and gaps in overlapping survey coverage were closed to ensure sufficient contiguous coverage.
-These data are initially extracted as approximately \num{10000} “ground truth” patches of \numroduct{200 x 200} cells at \qty{20}{\m} cell size, equivalent to the synthetic dataset.
-High- and low-resolution training pairs are created from these data using the same line sampling process as described in \Cref{sec:2.2}.
+These data are initially extracted as approximately \num{10000} “ground truth” patches of \numproduct{200 x 200} cells at \qty{20}{\m} cell size, equivalent to the synthetic dataset.
+High- and low-resolution training pairs are created from these data using the same line sampling process as described in \Cref{sec:simsurveys}.
 Due to the smaller number of patches, these data are augmented during training.
@@
 
-\subsection{    Network selection }
+\subsection{Network selection}
 Local Texture Estimator \parencite{leeLocalTextureEstimator2022} is implemented to super-resolve synthetic and real potential field geophysical data with low resolution resulting from line spacing.
@@
 
-\subsection{}
-Quantitative Measure
-
+\subsection{Quantitative Measure}
 Due to the dynamic range of magnetic anomaly grids and the relative importance of structural accuracy for gridded data, image quality assessment such as peak signal-to-noise ratio or mean-squared error are an inadequate quantitative measure of upscaling performance for geophysics.
-Instead, Feature Similarity \parencite{lin{Zhang et al 2011zhangFSIMFeatureSimilarity2011} was selected to quantify the quality of the super-resolved image, because it is a full reference image similarity metric that quantifies structural similarity using phase and local gradient magnitude components.
+In addition to mean-square error, Feature Similarity (FSIM) \parencite{linzhangFSIMFeatureSimilarity2011} is used to quantify the quality of the super-resolved image, because it is a full reference image similarity metric that quantifies structural similarity using phase and local gradient magnitude components.
+%TODO complain about FSIM
 
 \section{Results}
-Model performance is quantified using FSIM, and it is seen that fine-tune training increases FSIM score for the task of super-resolution for aeromagnetic grids over the baseline model.
+It is seen that fine-tune training increases FSIM score for the task of super-resolution for aeromagnetic grids over the baseline model.
 Qualitative results are shown to compare the outputs from the two models, the baseline model that is trained with synthetic data and the fine-tuned model trained with open access survey data.
@@
 
-\Cref{fig:3} contains open access grid data from the Eastern Goldfields Superterrane of Western Australia, and prepared using the proposed method.
+\Cref{fig:srdata} contains open access grid data from the Eastern Goldfields Superterrane of Western Australia, and prepared using the proposed method.
 Strong line-perpendicular smearing in LR is reduced in both SR predictions, and fine structural divisions are better delineated.
-NW striking features around in HR are aliased in LR and subsequently incorrectly rotated by 90 degrees in the baseline SR prediction (\Cref{fig:3}A).
-The fine-tuned model (\Cref{fig:3}B) resolves the correct strike, and separates the two features present.
+NW striking features around in HR are aliased in LR and subsequently incorrectly rotated by 90 degrees in the baseline SR prediction (\Cref{fig:srdata}A).
+The fine-tuned model (\Cref{fig:srdata}B) resolves the correct strike, and separates the two features present.
 The enhanced structural similarity is reflected by the higher FSIM score in the fine-tuned model.
+
 \begin{figure}[hbt]
     % \includegraphics[width=\textwidth]{fig/p2/image1.png}
-    \caption[Super-resolution geophysics grid results]{
-    }
-    \label{fig:lrdata}
+    \caption[Super-resolution geophysics grid results]{Super-resolution predictions on open access data, prepared using the proposed method.
+        Explanation in-text.
+        Grid A is the super-resolution prediction using the baseline model, while grid B is the SR prediction using the fine-tuned model.}
+    \label{fig:srdata2}
+\end{figure}
+
+\begin{figure}[hbt]
+    % \includegraphics[width=\textwidth]{fig/p2/image1.png}
+    \caption[Super-resolution geophysics grid results]{Super-resolution predictions on open access data, prepared using the proposed method.
+        Explanation in-text.
+        Grid A is the super-resolution prediction using the baseline model, while grid B is the SR prediction using the fine-tuned model.}
+    \label{fig:srdata4}
 \end{figure}

### 2023-10-07 paper2.tex
Restructure introduction
As per TH comments and own infinite wisdom

@@
 \section{Introduction}
-Deep learning techniques for single image super-resolution typically use paired high- and low-resolution image data, with the objective to learn the transform from low resolution to high.
-This is an ill posed challenge, because many high-resolution images may share the same low-resolution representation.
-For natural images, a common approach to generating low-resolution data is to interpolate the high-resolution image to a smaller size using a low-resolution transform such as bicubic resizing.
+We propose a method for super-resolution (SR) upscaling of aeromagnetic geophysics data from diverse geological provenance.
+This method uses transfer learning \parencite{tanSurveyDeepTransfer2018} from magnetic data forward modelled from a collection of synthetic geological models with varied histories \parencite{jessellNoddyverseMassiveData2022}, and fine tuning with real-world data.
+SR employed in this work leverages a contemporary neural network \parencite{leeLocalTextureEstimator2022}, with a realistic method for sampling high-resolution grids and gridding them to low-resolution.
+The method is suitable for typical low-resolution regional aeromagnetic surveys in Australia.
 
-The analysis of potential field geophysics relies on gridded survey data.
-Sampling density and subsequent gridding processes impose limits on the observable detail in these data.
-Contemporary work with low-resolution transforms for natural images \parencite[reviewed in][]{moserHitchhikerGuideSuperResolution2023} has well characterised the research space and expected performance for upscaling photographs and digital images.
-Geophysical data are distinct from these image rasters due to the potential field sampling and grid interpolation process, and the extent to which widely spaced low-resolution geophysical line data can be enhanced, and characteristics of the resulting super-resolved grids remain to be fully explored.
-These can be examined using the current generation super-resolution neural networks and a combination of synthetic and real geophysical datasets.
-
-When compared to numerical upsampling methods such as the bicubic filter, deep learning SR methods for geophysical textures can predict infill cells that add high frequency information which is reported to be more accurate when compared to a ground truth target \parencite{smithMagneticGridResolution2022}.
-However, the data used by \textcite{smithMagneticGridResolution2022} do not reflect real-world low-resolution geophysical survey data.
-Low-resolution aeromagnetic survey data are the result of wide line spacings during acquisition, with the resulting grid cells predominantly being those predicted by interpolation between sparse sample points.
-Achieving higher resolution traditionally requires additional sampling to increase the grid resolution, which refines structures in the response and reduces blocky textures and other gridding artifacts.
-We propose a method that simulates the line sampling of both synthetic and real data, thereby more closely reflecting a real-world geophysical low-resolution transform.
-%TODO refactor contrib. is investigating geo domain variance
-Synthetic data are used in the proposed method to address the low amount of suitable real training data, making use of a recently released extensive and geologically varied synthetic dataset \parencite{jessellNoddyverseMassiveData2022}.
-Thus, the two contributions made in this study are addressing the challenges of training a deep learning model with limited suitable geophysical data and describing a methodology for a realistic low-resolution transform for potential field survey grids.
-
-%TODO
-The remainder of this paper is structured as follows.
-In Section 1.1 we introduce geophysical grids and their differences to image rasters, and introduce synthetic data as a source of training data with geological domain variation.
-In Section 1.2 we review
-
-\subsection{Resolution in geophysical surveys}
+\subsection{Resolution in geophysical data}
 \label{sec:resinsurveys}
 In exploration geophysics, the Earth's naturally occurring magnetic or gravitational potential fields can be used to survey the petrophysical expression of underlying geology.
+These can be interpreted to inform geological mapping, resource modelling, and enhance the understanding of the subsurface.
 Depending on the scale of investigation, surveys may be carried out from ground or airborne sensors.
@@
 Sampling along line is typically performed at \qty{10}{\Hz} or faster, which corresponds to several meters between samples at a nominal flight speed of \qty{70}{\m\per\s} \parencite{goodwinAirborneMagneticRadiometric2023}.
+Because the power of shorter wavelengths in potential fields diminish with increasing distances from the source, aeromagnetic flights are flown as low as safety and topography permits.
 Despite the use of precise navigation systems and skilled operators, these data are not collected in perfectly uniform lines at constant height, and the samples also contain noise components.
 
-Transforming these irregularly distributed line data to a uniformly spaced array is the challenge of regularisation.
-Regularisation is performed by gridding, of which there are several classes of methods.
-Minimum Curvature gridding \parencite{briggsMachineContouringUsing1974} is routinely applied in industry applications, as it gives good quality results in rapid time, with minimal manual intervention.
-A comprehensive review of spatial interpolation methods is presented by \textcite{liReviewComparativeStudies2011}.
-Each method of gridding has characteristic interpolation traits (which when undesired are termed artifacts), but irrespective of the gridding process the detail resolvable in the output grid is a product of the final cell size, termed resolution.
-Gridding at a finer cell size preserves higher frequencies present in the sampled data.
+The subsequent analysis of surveyed potential fields generally relies on gridded data, and transforming irregularly distributed survey data to a regularised grids is the task of gridding.
+There are several classes of gridding methods available.
+Minimum Curvature gridding \parencite{briggsMachineContouringUsing1974} is routinely applied in industry applications, as it gives well characterised results in rapid time, with minimal manual intervention.
+A comprehensive review of alternative spatial interpolation methods is presented by \textcite{liReviewComparativeStudies2011}.
+Each method of gridding has characteristic interpolation traits (which when undesired are termed artifacts), but irrespective of the gridding process the detail resolvable in the output grid is a product of the sample height, sampling density, and the final cell size at which the grids are rendered.
+Gridding at a finer cell size preserves higher frequencies present in the sampled data, resulting in greater detail.
+This resolvable detail is termed resolution, and high-resoluton details better define structures apparent in the data which are contextually important to interpretation.
 When the cell size covers a quantified distance, the smallest resolvable detail can be expressed in terms of wavelength.
@@
 These are limited by the sample spacing during acquisition.
-As an additional constraint on the observable detail in sampled potential fields, the power of shorter wavelengths diminishes with increasing distances from the source, such that potential fields lose high-frequency details at larger source-sensor separation.
-
-Magnetic potential field grids are highly distinct from photographs and other image rasters.
-Being sampled as a single component of the vector potential field, these data contain a single channel, and the data contain multiple sources of noise components.
-Furthermore, the features present in these data are dependent on the subsurface geology, varying between smooth domains without significant near-surface magnetisation, through to highly deformed igneous stratigraphic units with complex high-intensity structures.
-The recorded intensity values have high dynamic range, spanning tens of thousands of nanotesla, while contextually important features may be defined by tens of nanotesla \parencite{kovesiPhasePreservingTone2012}.
-Regularisation of the scattered sample data introduces spurious features, which depend on a variety of parameters intrinsic to both the data and the gridding method.
-Most critically, aeromagnetic data are highly sampled in the direction of flight lines but are under-sampled in the line perpendicular direction.
-When widely spaced line data are interpolated, features are overly smoothed in the line perpendicular direction, leading to the appearance of smearing or string-of-beads aliasing textures.
-Details defined by short wavelengths such as near surface magnetic sources or small-scale structures are better localised and made more apparent in high resolution data.
-These features may help delineate additional structures that are manifested in the data which are contextually important to geological interpretation.
+% Low-resolution aeromagnetic survey data are the result of wide line spacings during acquisition, with the resulting grid cells predominantly being those predicted by interpolation between sparse sample points.
+Achieving higher resolution traditionally requires additional sampling to increase the grid resolution.
+%, which refines structures in the response and reduces blocky textures and other gridding artifacts.
 In addition to human interpretation, machine processing of geophysical data is benefitted by using higher resolution data, with the negligible cost of increased computational load.
 
-Regions covered by high-resolution aeromagnetic surveys are biased toward prospective geological terranes. %TODO Cite
-In order to improve the generalisation of the method for regions without high-resolution coverage, transfer learning \parencite{tanSurveyDeepTransfer2018} from synthetic data is used to establish a baseline model on a broad set of geological domains, which is then fine-tuned with high-resolution survey grid data.
-Transfer learning assists with the challenge of costly data acquisition common in geoscience \parencite{dawsonImpactDatasetSize2023} by pre-training a neural network on a larger source dataset that shares properties with the target dataset.
-The synthetic geophysical data \parencite{jessellNoddyverseMassiveData2022} are forward modelled from stratigraphic voxel models with varied geological histories which can provide a diverse set of features, but these lack truly realistic characteristics.
-In the case of the synthetic data used here, this includes a lack of high frequency near surface magnetisation and features from complex geological processes such as metasomatism.
+A small number of regions in Western Australia are covered by high-resolution aeromagnetic surveys with a line spacing of 100 m or closer, and these are biased toward prospective geological terranes \parencite{howardAirborneGeophysicalCoverage2004}.
+Therefore, example-based learning methods trained using these aeromagnetic data will be biased for performance in these domains, while lacking in those that have been so far regarded as unprospective.
+Addressing costly data acquisition, common in geoscience \parencite{dawsonImpactDatasetSize2023}, can be done by transfer learning.
+This assists example-based methods by using a larger source dataset which shares properties with the target dataset.
+In order to improve the generalisation of an example-based neural network for regions without high-resolution coverage, we propose transfer learning \parencite{tanSurveyDeepTransfer2018} using a baseline model trained with synthetic data containing a broad set of geological domains, which is then fine-tuned with high-resolution survey grid data.
+The synthetic geophysical data \parencite{jessellNoddyverseMassiveData2022} are forward modelled from 3D petrographic voxel models with varied geological histories.
+These provide a diverse set of features, but these lack truly realistic characteristics, such as high frequency near surface magnetisation, and features from complex geological processes such as metasomatism or remnant magnetisation.
 
-\subsection{Survey Grid Imputation}
-In order to fill in missing high-resolution data without additional sampling, it is required to predict values at new sample points.
-Numerically, this can be done using interpolating functions, such as splines \parencite{keysCubicConvolutionInterpolation1981}, kriging \parencite{hansenInterpretiveGriddingAnisotropic1993} or other methods.
+Thus, the approach made in this study to address the challenges of training an example-based model with limited suitable geophysical data is to make use of geologically diverse synthetic data, with a realistic sampling and gridding method to generate low-resolution data.
+
+\subsection{Prior work}
+Numerically, image interpolation can be done using interpolating functions, such as splines \parencite{keysCubicConvolutionInterpolation1981}, kriging \parencite{hansenInterpretiveGriddingAnisotropic1993} or other methods.
 These methods are limited in their performance by the quality of their neighbouring observed values, and their distance.
@@
 
-For photographs and natural image rasters with large representative training corpuses available, such as ImageNet \parencite{dengImageNetLargescaleHierarchical2009} and DIV2K \parencite{agustssonNTIRE2017Challenge2017}, super-resolution methods have progressed to the point that high quality enhancement at four times scale is readily accessible to end-users \parencite[e.g.][]{wangRealESRGANTrainingRealWorld2021}.
-Photographs and other rasters of interest to computer vision are typically created by capturing light from an image sensor or are explicitly mapped on a grid using a raster graphics program.
-These data are encoded to regular arrays of pixel values, commonly as three-channel rasters representing the red, green, and blue intensities of each pixel.
-In these rasters, each pixel is regularly distributed, and the resolution is isotropic and a factor of the pixel density of the sampling sensor or the software defined grid.
-
-Contrastingly, geophysical grid rasters are created by point sample regularisation and interpolation.
-These point sample locations are irregularly spaced and directionally dependent, especially in the case of airborne flight line sampling.
-The resulting grid rasters may have isotropic cell size, but the frequency content in each axis is anisotropic, being a factor of the sample spacing in the line-perpendicular and line-parallel directions.
-These grids are also single channel, storing measurements of the geophysical property of interest.
-Crucially, the resolution of a geophysical grid refers to the underlying frequency content of the regularised survey data, which may not be directly linked to the dimensions of the raster in which they are rendered.
-Because of these and the differences outlined in \Cref{sec:resinsurveys}, pre-existing super-resolution models trained on large image corpuses are not suitable for predicting higher frequency signals in geophysical grids.
-
-Frequency content in potential field grids can also be enhanced by calculating the potential as if it were sampled at a smaller source-sensor distance, in a process known as downward continuation \parencite{bullardDeterminationMassesNecessary1948}.
+Instead of increasing the sampling density, the detail in potential field grids can be enhanced by calculating the potential as if it were sampled at a smaller source-sensor distance, in a process known as downward continuation \parencite{bullardDeterminationMassesNecessary1948}.
 At large source-sensor distances, high frequencies are diminished below the noise floor to the point of unobservability, resulting in grids that show only broad scale features, typically representing spatially extensive features deep in the crust.
@@
 Both methods operate on regional aeromagnetic data at four times scale, using variants of the SRGAN convolutional neural network originally by \textcite{ledigPhotorealisticSingleImage2017}.
-The method of \textcite{smithMagneticGridResolution2022} is capable of predicting short wavelengths and accurately super-resolving low-resolution magnetic textures, however, the low-resolution transform was a polynomial filter that supressed high frequencies, rather than the proposed line spacing method.
+The method of \textcite{smithMagneticGridResolution2022} compared SR to numerical upsampling methods such as the bicubic filter, and is capable of accurately upsampling low-resolution magnetic textures by predicting short wavelengths.
+However, the low-resolution data were created using a polynomial filter that supressed high frequencies, rather than a real-world low-resolution geophysical sampling process.
 The method of \textcite{bavandsavadkoohiHighresolutionAeromagneticMap2023} uses low- and high-resolution aeromagnetic data from regional surveys, with a realistic low-resolution transform from line spacing and sample altitude differences.
-However, the dataset used contains only \qty{267} samples from surveys in Quebec, Canada, with side lengths of \qty{14400}{\m} over \qty{48} cells in each axis.
-The proposed method is distinct from these prior works with its use of synthetic data in coordination with real survey data to improve generalisation, and the use of a modern MLP-based SR network.
+The dataset contains \qty{267} sample grids from surveys in Quebec, Canada, prepared from surveys with a low-resolution line spacing of \qty{800}{\m}.
+The proposed method is distinct from these prior works with its use of synthetic data in coordination with real survey data to improve generalisation for regional aeromagnetics in Australia, and the use of a modern MLP-based SR network.
 
-\subsection{Neural networks for super-resolution}
-Super-resolution (SR) is the task of predicting interpolating values to resolve rasters with a higher resolution, and has been predominantly performed in the domain of Convolutional Neural Networks (CNN) following the success of SRCNN \parencite{dongLearningDeepConvolutional2014}.
-Recently, CNNs have been surpassed by coordinate multilayer perceptron (CMLP) neural networks for the task of SR \parencite{chenLearningContinuousImage2021}.
-CMLP networks learn a signal as a function of its coordinates, and SR is performed by predicting pixel values on the continuum of coordinates in the domain of the learnt function, including at scales that were not seen during training.
-Key to the performance of these networks are implicit functions, which parameterise a function learned from training dataset with a neural network analogue.
-The network analogue can then be queried for information that fits the learnt function but was not included in the training data.
+Deep learning techniques for SR typically use paired high- and low-resolution image data, with the objective to learn the transform from low resolution to high.
+This is an ill posed challenge, because many high-resolution images share the same low-resolution representation \parencite{dongImageSuperresolutionUsing2016}.
+For photographs and natural image rasters with large representative training corpuses available, such as ImageNet \parencite{dengImageNetLargescaleHierarchical2009} and DIV2K \parencite{agustssonNTIRE2017Challenge2017}, SR methods have progressed to the point that high quality enhancement at four times scale is readily accessible to end-users \parencite[e.g.][]{wangRealESRGANTrainingRealWorld2021}.
+Contemporary work with low-resolution transforms for natural images \parencite[reviewed in][]{moserHitchhikerGuideSuperResolution2023} has well characterised the research space and expected performance for upscaling photographs and digital images.
+Prior work specific to this study are reviewed in \Cref{sec:2nnsr}.
 
-Convolutional Neural Network (CNN) methods have long been well suited for computer vision tasks such as image classification and, more recently, super-resolution.
-In an image raster, neighbouring pixels define simple features, and these features combine in the wider image to define complex features.
-CNNs excel in deep learning tasks for these data, due in part to the structure of the receptive field of the network.
-The receptive field is formed from stacked layers of small convolutional kernels, typically with a size of \numproduct{3 x 3} cells for SR CNNs.
-These low-level kernels learn simple functions, which are convolved with deeper layers to learn increasingly complex filters across a larger image extent, widening the receptive field.
-Once trained, the learnt functions are conditioned to transform low-resolution features into high-resolution features, using the neighbouring input values of the low-resolution grid in the context of filters learnt from the training data.
+Photographs and other natural images of interest to computer vision are typically created by capturing light from an image sensor or are explicitly mapped on a grid using a raster graphics program.
+In these rasters, each pixel is regularly distributed, and the resolution is isotropic and a factor of the pixel density of the sampling sensor or the software defined grid.
+These data are encoded to regular arrays of pixel values, commonly as three-channel rasters representing the red, green, and blue intensities of each pixel.
+For natural images, a common approach to generating low-resolution data is to interpolate the high-resolution image to a smaller size using a transform such as bicubic downsampling.
+Aerogeophysical grids are distinct from these image rasters due to the potential field sampling and grid interpolation process outlined in \Cref{sec:resinsurveys}, and the extent to which widely spaced low-resolution geophysical line data can be enhanced, and characteristics of the resulting super-resolved grids remain to be fully explored.
+Most critically, aeromagnetic data are highly sampled in the direction of flight lines but are under-sampled in the line perpendicular direction.
+The resulting grid rasters may have isotropic cell size, but the frequency content in each axis is anisotropic, being a factor of the sampling frequency in the line-perpendicular (low) and line-parallel (high) directions.
+Being sampled as a single component of the vector potential field, these data contain a single channel, and the data contain multiple sources of noise components.
+Furthermore, the features present in these data are dependent on the subsurface geology, varying between smooth domains without significant near-surface magnetisation, through to highly deformed igneous stratigraphic units with complex high-intensity structures.
+The recorded intensity values have high dynamic range, spanning tens of thousands of nanotesla, while contextually important features may be defined by tens of nanotesla \parencite{kovesiPhasePreservingTone2012}.
+Because of these differences, pre-existing super-resolution models trained on large image corpuses are not suitable for predicting higher frequency signals in geophysical grids.
 
-The earliest application of CNN SR was demonstrated by \parencite{dongLearningDeepConvolutional2014}, where convolutional layers are used for low-resolution patch extraction, feature mapping, and reconstruction of high-resolution images.
-The outputs of each convolutional layer are similar to hand-crafted filters or feature dictionaries in earlier example-based super-resolution methods \parencite{freemanExamplebasedSuperresolution2002}, but the learnt filters are more numerous and fully trainable with the deep learning approach.
-Following the success of \parencite{dongLearningDeepConvolutional2014}, many iterative improvements have been made to CNN based SR\@.
-These include SRCNN \parencite{dongImageSuperresolutionUsing2016}, RDN \parencite{zhangResidualDenseNetwork2018}, ESRGAN \parencite{wangESRGANEnhancedSuperresolution2018}, and others \parencite{ledigPhotorealisticSingleImage2017,limEnhancedDeepResidual2017}.
-While each of these works contribute unique features to CNN-based super-resolution, they follow a common stacked block design.
-This comprises a set of initial input feature extraction convolutions, a sequence of convolutional blocks with activations (neurons), some number and arrangement of intermediate residual learning pathways (skip connections), and an upsampling block for feature upscaling and convolving latent features back to image space.
+We propose a method that simulates the line sampling of both synthetic and real data, thereby more closely reflecting a real-world geophysical low-resolution transform, at scales typical of those in exploration in Australia.
 
+\subsection{Neural network super-resolution}
+\label{sec:2nnsr}
+Deep learning super-resolution (SR) is the task of predicting interpolating values to resolve rasters with a higher resolution, and has been predominantly performed in the domain of Convolutional Neural Networks (CNN) following the success of SRCNN \parencite{dongLearningDeepConvolutional2014}.
 Recently, multi-layer perceptrons (MLPs) have become a state-of-the-art alternative for SR\@.
@@
 
-One limitation of these CNN-based networks is the challenge of upscaling data at non-integer scales, and scales beyond those in the training dataset.
-This was achieved by \parencite{huMetaSRMagnificationarbitraryNetwork2019,wangLearningSingleNetwork2021}, however recent approaches using implicit function based networks have improved performance.
 Implicit functions aim to learn a specific function parameterised entirely by the weights of a neural network.
@@
 These include SIREN \parencite{sitzmann2019siren}, LIIF \parencite{chenLearningContinuousImage2021}, and LTE \parencite{leeLocalTextureEstimator2022}.
-Notably in these networks, the learnt function has continuous domain, despite the discontinuous grid input.
+Notably in these networks, the learnt function has continuous domain, despite the discretised grid input.
 Super-resolution can be achieved by sampling the learnt function at any arbitrary grid cell size smaller than the original input \parencite{chenLearningContinuousImage2021}.
-While a stand-alone MLP such as SIREN is capable of parameterising a single function, when used in an autoencoder framework (such as with LIIF or LTE), an arbitrary input can be encoded using a CNN, upscaled, and subsequently reconstructed using fully connected layers \Cref{fig:ltenet}.
-This approach generalises MLP based super-resolution to any image or grid not seen in the training set.
+While a stand-alone MLP such as SIREN is capable of parameterising a single function, when used in an autoencoder framework (such as with LIIF or LTE), an arbitrary input can be encoded, upscaled, and subsequently reconstructed using fully connected layers \Cref{fig:ltenet}.
+An autoencoder approach generalises MLP based super-resolution to any image or grid not seen in the training set.
 
-MLP-based autoencoders for super-resolution have been shown in LIIF \parencite{chenLearningContinuousImage2021} and LTE \parencite{leeLocalTextureEstimator2022}.
-While both are structured as autoencoders with a CNN or transformer-based encoder followed by an MLP decoder, LTE is implemented here for its higher performance in the task of image super-resolution.
-The encoder in these networks can use the feature extraction capability of traditional SR CNNs such as EDSR \parencite{limEnhancedDeepResidual2017} or RDN \parencite{zhangResidualDenseNetwork2018}, or a SwinIR \parencite{liangSwinIRImageRestoration2021} transformer-based encoder.
-In the original implementation of the CNN SR networks, the extracted image features are upscaled and returned to the image domain by convolutional layers.
+LTE \parencite{leeLocalTextureEstimator2022} is implemented in this work for its higher performance in the task of image super-resolution.
+The encoder in LTE can use the feature extraction capability of traditional SR CNNs such as EDSR \parencite{limEnhancedDeepResidual2017} or RDN \parencite{zhangResidualDenseNetwork2018}, or a SwinIR \parencite{liangSwinIRImageRestoration2021} transformer-based encoder.
+In the original implementation of the CNN SR networks, the extracted image features are upsampled and returned to the image domain by convolutional layers.
 In LTE, the latent extracted features are further processed by the LTE network component before reconstruction to image space by an MLP\@.
@@
 The LTE component of the LTE network transforms the encoded latent features to frequency and amplitude features using trainable convolutions.
-Both the amplitude and frequency features are then upscaled using nearest neighbour filter interpolation.
+Both the amplitude and frequency features are then upsampled using nearest neighbour filter interpolation.
 The frequency components are combined with phase information, which is extracted from the input by an additional MLP, and the resulting features are passed through a sinusoidal activation function before being combined with the amplitude features.
 Finally, the decoding MLP restores these frequency domain features to the spatial image domain.
-To precondition the network toward learning high-resolution features, a long-range skip connection with bilinear upscaling passes low-resolution content common between the upscaled LR and the HR counterpart to the output of the MLP\@.
+To precondition the network toward learning high-resolution features, a long-range skip connection with bilinear upscaling passes low-resolution content common between the upsampled LR and the HR counterpart to the output of the MLP\@.
+Specifics of the LTE implementation to investigate the performance of SR for geophysical grids from a range of geological domains are detailed in \Cref{sec:2lte}.
 
@@
 
+The remainder of this paper is structured as follows.
+\Cref{sec:2methods} describes the experimental design to generate low-resolution aeromagnetic survey grids from synthetic and real-world data, where \Cref{sec:baseline,sec:finetune} specifically describe the training approach for the neural network model.
+Results are presented in \Cref{sec:2results} and are discussed in \Cref{sec:discussion}.
+Conclusions are drawn in \Cref{sec:2conclusion}.
+
 \section{Data and Experimental Methods}
+\label{sec:2methods}
 A realistic geophysical low-resolution transform is developed by simulating aeromagnetic sampling of high-resolution survey grid datasets, and re-gridding the resulting samples.
@@
 All data are modelled at \qty{20}{\m} spacing in each direction for \qty{4000}{\m} (\qty{200} cells) in each axis, and the potential field forward models are calculated at \qty{100}{\m} above the flat model surface.
-Only the magnetic forward model is used in this work, however the described method can be followed to train a model capable of super-resolving grids of the gravity potential field.
+Only the magnetic forward model is used in this work.
 
@@
 \subsection{Synthetic baseline training setup}
+\label{sec:baseline}
 While each of the models in the synthetic training dataset have unique petrophysical parameters, there are only \qty{343} distinct sequences of deformation events.
@@
 \subsection{Fine-tuning with aeromagnetic survey data}
+\label{sec:finetune}
 To improve the performance of the model on real world geophysical data, the synthetic-trained model is subsequently trained on data re-gridded from the \qty{20}{\m} magnetic merged grid of Western Australia 2020 \parencite{brett20MagneticMerged2020}.
@@
 \subsection{Network selection}
+\label{sec:2lte}
 Local Texture Estimator \parencite{leeLocalTextureEstimator2022} is implemented to super-resolve synthetic and real potential field geophysical data with low resolution resulting from line spacing.
@@
 \section{Results}
+\label{sec:2results}
 It is seen that fine-tune training increases FSIM score for the task of super-resolution for aeromagnetic grids over the baseline model.
@@
 
-\Cref{fig:srdata} contains open access grid data from the Eastern Goldfields Superterrane of Western Australia, and prepared using the proposed method.
+\Cref{fig:srdata1,fig:srdata2,fig:srdata3} contain open access grid data from the Eastern Goldfields Superterrane of Western Australia, prepared using the proposed method.
+
 Strong line-perpendicular smearing in LR is reduced in both SR predictions, and fine structural divisions are better delineated.
-NW striking features around in HR are aliased in LR and subsequently incorrectly rotated by 90 degrees in the baseline SR prediction (\Cref{fig:srdata}A).
-The fine-tuned model (\Cref{fig:srdata}B) resolves the correct strike, and separates the two features present.
+NW striking features around in HR are aliased in LR and subsequently incorrectly rotated by 90 degrees in the baseline SR prediction (\Cref{fig:srdata1}A).
+The fine-tuned model (\Cref{fig:srdata1}B) resolves the correct strike, and separates the two features present.
 The enhanced structural similarity is reflected by the higher FSIM score in the fine-tuned model.
+
+\begin{figure}[hbt]
+    % \includegraphics[width=\textwidth]{fig/p2/image1.png}
+    \caption[Super-resolution geophysics grid results]{Super-resolution predictions on open access data, prepared using the proposed method.
+        Explanation in-text.
+        Grid A is the super-resolution prediction using the baseline model, while grid B is the SR prediction using the fine-tuned model.}
+    \label{fig:srdata1}
+\end{figure}
 
@@
 \end{figure}
+%TODO
 
@@
         Grid A is the super-resolution prediction using the baseline model, while grid B is the SR prediction using the fine-tuned model.}
-    \label{fig:srdata4}
+    \label{fig:srdata3}
 \end{figure}
@@
 \section{Discussion}
+\label{sec:discussion}
 The Noddyverse synthetic training dataset comprises geology models with a variety of realistic petrophysics and geological histories, and was sampled using simple but realistic airborne survey methodology.
@@
 \section{Conclusion}
+\label{sec:2conclusion}
 An approach for upscaling geologically diverse geophysical survey grid data is proposed, which adopts transfer learning from synthetic data to better generalise super-resolution across different geological domains.
@@
 Low-resolution features incorrectly enhanced by the synthetic baseline model were correctly resolved following fine-tune training with these data, and the model is capable of upscaling grids with \qty{320}{\m} line spacing to \qty{80}{\m} line spacing with an average FSIM score of \num{0.9731}.
+
 % \section{Declaration of Competing Interest}

### 2023-10-07 paper2.tex
Add some result figures

@@
 Qualitative results are shown to compare the outputs from the two models, the baseline model that is trained with synthetic data and the fine-tuned model trained with open access survey data.
-Each figure follows the following layout for the grids from left to right; the ground truth (GT) \numproduct{200 x 200} cell tile is presented with low-resolution sampled data indicated in colour.
-The target high-resolution grid (HR), created from sampling and gridding GT at \qty{80}{\m} line spacing, is shown for comparison.
-The \numproduct{45 x 45} cell low-resolution grid (LR) shows the result of the described sampling and gridding method at \qty{320}{m} line spacing, and is upscaled for display using bicubic interpolation.
-The model prediction (SR), using an input of LR with the proposed method, is shown with the corresponding FSIM metric between HR and SR\@.
 
-\Cref{fig:srdata1,fig:srdata2,fig:srdata3} contain open access grid data from the Eastern Goldfields Superterrane of Western Australia, prepared using the proposed method.
+\Cref{fig:srdata23,fig:srdata14,fig:srdata17,fig:srdata18} contain open access grid data from the Eastern Goldfields Superterrane of Western Australia, prepared using the proposed method.
+Each figure follows the following layout for the grids; a) the ground truth (GT) \numproduct{200 x 200} cell tile is presented with low-resolution sampled data indicated in colour.
+The target high-resolution grid (HR), created from sampling and gridding GT at \qty{80}{\m} line spacing, is shown in b) for comparison.
+The \numproduct{45 x 45} cell low-resolution grid (LR) shows the result of the described sampling and gridding method at \qty{320}{m} line spacing, and is upscaled for display using bicubic interpolation in c).
+The baseline model prediction (Baseline SR), using an input of LR with the proposed method, is shown in d) with the corresponding SSIM metric between HR and SR\@.
+The fine-tuned model prediction is shown in e).
 
 Strong line-perpendicular smearing in LR is reduced in both SR predictions, and fine structural divisions are better delineated.
-NW striking features around in HR are aliased in LR and subsequently incorrectly rotated by 90 degrees in the baseline SR prediction (\Cref{fig:srdata1}A).
-The fine-tuned model (\Cref{fig:srdata1}B) resolves the correct strike, and separates the two features present.
-The enhanced structural similarity is reflected by the higher FSIM score in the fine-tuned model.
+NW striking features around in HR are aliased in LR and subsequently incorrectly rotated by 90 degrees in the baseline SR prediction (\Cref{fig:srdata23} d).
+The fine-tuned model (\Cref{fig:srdata23} e) resolves the correct strike, and separates the two features present.
+The enhanced structural similarity is reflected by the higher SSIM score in the fine-tuned model.
 
 \begin{figure}[hbt]
-    % \includegraphics[width=\textwidth]{fig/p2/image1.png}
+    \includegraphics[width=\textwidth]{fig/p2/srcomp_23.pdf}
     \caption[Super-resolution geophysics grid results]{Super-resolution predictions on open access data, prepared using the proposed method.
@@
         Grid A is the super-resolution prediction using the baseline model, while grid B is the SR prediction using the fine-tuned model.}
-    \label{fig:srdata1}
+    \label{fig:srdata23}
 \end{figure}
@@
 \begin{figure}[hbt]
-    % \includegraphics[width=\textwidth]{fig/p2/image1.png}
+    \includegraphics[width=\textwidth]{fig/p2/srcomp_14.pdf}
     \caption[Super-resolution geophysics grid results]{Super-resolution predictions on open access data, prepared using the proposed method.
@@
         Grid A is the super-resolution prediction using the baseline model, while grid B is the SR prediction using the fine-tuned model.}
-    \label{fig:srdata2}
+    \label{fig:srdata14}
 \end{figure}
-%TODO
 
 \begin{figure}[hbt]
-    % \includegraphics[width=\textwidth]{fig/p2/image1.png}
+    \includegraphics[width=\textwidth]{fig/p2/srcomp_17.pdf}
     \caption[Super-resolution geophysics grid results]{Super-resolution predictions on open access data, prepared using the proposed method.
@@
         Grid A is the super-resolution prediction using the baseline model, while grid B is the SR prediction using the fine-tuned model.}
-    \label{fig:srdata3}
+    \label{fig:srdata17}
 \end{figure}
-%TODO
+
+\begin{figure}[hbt]
+    \includegraphics[width=\textwidth]{fig/p2/srcomp_18.pdf}
+    \caption[Super-resolution geophysics grid results]{Super-resolution predictions on open access data, prepared using the proposed method.
+        Explanation in-text.
+        Grid A is the super-resolution prediction using the baseline model, while grid B is the SR prediction using the fine-tuned model.}
+    \label{fig:srdata18}
+\end{figure}
 

### 2023-10-08 paper1.tex
Use updated commands

@@
     Specifically, the \emph{RDN} and \emph{ESRGAN+} neural network architectures, which were originally developed for enhancing images, are applied to enhance magnetic surveys and trained with high-resolution and low-resolution magnetic grids of the same extent.
-    \SI{80}{\metre} cell size magnetic grids are upsampled to \SI{20}{\metre} cell size using this method, and predicted value and structural accuracy comparisons to the corresponding ground truth \SI{20}{\metre} grids are presented over two test sites in the Eastern Goldfields Superterrane, Western Australia.
+    \qty{80}{\metre} cell size magnetic grids are upsampled to \qty{20}{\metre} cell size using this method, and predicted value and structural accuracy comparisons to the corresponding ground truth \qty{20}{\metre} grids are presented over two test sites in the Eastern Goldfields Superterrane, Western Australia.
     The method based on \emph{RDN} achieves \qty{53}{\percent} lower error compared to Bicubic interpolation.
@@
 These high frequency components reveal localised variations in the surveyed potential field, which provide additional detail on subsurface geological structures and the potential for mineralisation.
-An example of the additional detail provided by a high-resolution grid is provided in \cref{fig:lrandhr}, which shows an \SI{80}{\metre} cell size Total Magnetic Intensity (TMI) grid (a) compared to a \SI{20}{\metre} TMI grid of the same \SI{2560}{\metre} \texttimes\ \SI{2560}{\metre} extent (b), gridded from the same potential field samples, but interpolated to different resolutions.
-The increased density of pixels in the high-resolution \SI{20}{\metre} grid allows higher frequencies in the sampled magnetic potential field to be displayed.
-These frequencies are irretrievably lost when the high-resolution grid is downsampled to \SI{80}{\metre}.
+An example of the additional detail provided by a high-resolution grid is provided in \Cref{fig:lrandhr}, which shows an \qty{80}{\metre} cell size Total Magnetic Intensity (TMI) grid (a) compared to a \qty{20}{\metre} TMI grid of the same \qtyproduct{2560 x 2560}{\metre} extent (b), gridded from the same potential field samples, but interpolated to different resolutions.
+The increased density of pixels in the high-resolution \qty{20}{\metre} grid allows higher frequencies in the sampled magnetic potential field to be displayed.
+These frequencies are irretrievably lost when the high-resolution grid is downsampled to \qty{80}{\metre}.
 
@@
     \includegraphics[width=\linewidth]{fig/p1/lrandhr.jpg}
-    \caption[Comparison of different resolution grids]{Low resolution \SI{80}{\metre} cell size (a), and high-resolution \SI{20}{\metre} cell size (b) TMI grids over the same extent.
-        Each tile is \SI{2560}{\metre} \texttimes\ \SI{2560}{\metre}.
+    \caption[Comparison of different resolution grids]{Low resolution \qty{80}{\metre} cell size (a), and high-resolution \qty{20}{\metre} cell size (b) TMI grids over the same extent.
+        Each tile is \qtyproduct{2560 x 2560}{\metre}.
         The additional detail shown in the high-resolution grid is made available by the finer cell size, which can convey higher frequency detail, if present in the sampled data.}
@@
 \subsection{Resolution and frequency}
-As discussed in \cref{sec:resingeo}, a finer spatial resolution grid (fewer metres per pixel) can convey higher frequency information, due to the higher spatial sampling rate.
-Indeed, a gridded raster with regularly spaced square cells \(\Delta x\) has an intrinsic Nyquist wavelength \(\lambda _N\), at twice the cell size \cref{eqn:nyq}.
+As discussed in \Cref{sec:resingeo}, a finer spatial resolution grid (fewer metres per pixel) can convey higher frequency information, due to the higher spatial sampling rate.
+Indeed, a gridded raster with regularly spaced square cells \(\Delta x\) has an intrinsic Nyquist wavelength \(\lambda _N\), at twice the cell size,
 
@@
     \label{eqn:nyq}
-    \lambda{}N = 2 \Delta{}x
+    \lambda{}N = 2 \Delta{}x.
 \end{equation}
@@
 This corresponds to the shortest wavelength the grid can adequately display, which can be observed as the finest details resolvable in the grid raster.
-For example, a high-resolution grid with \SI{20}{\metre} spatial resolution (HR) has a Nyquist wavelength of \SI{40}{\metre}.
-In comparison, a low-resolution \SI{80}{\metre} grid (LR) has a Nyquist wavelength of \SI{160}{\metre}.
-Note the Nyquist wavelength is proportional between different cell size grids according to the scale factor \(S\) \cref{eqn:hrn}.
+For example, a high-resolution grid with \qty{20}{\metre} spatial resolution (HR) has a Nyquist wavelength of \qty{40}{\metre}.
+In comparison, a low-resolution \qty{80}{\metre} grid (LR) has a Nyquist wavelength of \qty{160}{\metre}.
+Note the Nyquist wavelength is proportional between different cell size grids according to the scale factor \(S\),
 
@@
     \label{eqn:hrn}
-    \lambda{}N_{HR} = \lambda{}N_{LR} \div{}S
+    \lambda{}N_{HR} = \lambda{}N_{LR} \div{}S.
 \end{equation}
@@
 Adversarial training of upsampling networks can help in learning a better model for the task at hand.
-For example, ESRGAN uses an analogous upsampling network design to RDN (Residual Dense Network) \cref{fig:rdn}, with the addition of a discriminator network.
-This will be further discussed in \cref{sec:nnsr}.
+For example, ESRGAN uses an analogous upsampling network design to RDN (Residual Dense Network) \Cref{fig:rdn}, with the addition of a discriminator network.
+This will be further discussed in \Cref{sec:nnsr}.
 For a review on super-resolution networks, the reader is referred to \cite{anwarDeepJourneySuperresolution2020}.
@@
 While there are pre-trained models to super-resolve image data (such as ImageNet), the smooth and continuously differentiable nature of potential field data makes it difficult to directly apply such pre-trained models.
-For example, it may enhance the appearance of gridding artifacts, instead of supressing them.
+For example, it may enhance the appearance of gridding artefacts, instead of supressing them.
 While several of the aforementioned works investigate deep learning super-resolution for geospatial data, low resolution in potential field geophysics is a result of under sampling and naïve best-effort interpolation of the potential field, distinct from low-resolution data previously studied in those works.
@@
     \includegraphics[width=\linewidth]{fig/p1/rdb.png}
-    \caption[Basic Blocks]{Each Basic Block (\cref{fig:rdn}, orange) comprises three weighted Residual Dense Blocks (\cref{fig:convs}).
+    \caption[Basic Blocks]{Each Basic Block (\Cref{fig:rdn}, orange) comprises three weighted Residual Dense Blocks (\Cref{fig:convs}).
         ESRGAN+ extends ESRGAN with the addition of Gaussian Noise after each basic RDB block (black vectors).
@@
     \includegraphics[width=\linewidth]{fig/p1/convs.png}
-    \caption[RDB convolutional layers]{Each Residual Dense Block (\cref{fig:rdb}, purple) comprises four convolutional layers, with additional learning pathways present as residual connections (black), and dense connections (green).
+    \caption[RDB convolutional layers]{Each Residual Dense Block (\Cref{fig:rdb}, purple) comprises four convolutional layers, with additional learning pathways present as residual connections (black), and dense connections (green).
 LReLU refers to the Leaky-ReLU activation function.
@@
 
-Residual Dense Network (RDN) \parencite{zhangResidualDenseNetwork2018} is a deep learning super-resolution method which consists of a series of residual dense blocks (\cref{fig:rdb,fig:convs}), which combine the performant residual connections and dense connections (\cref{fig:convs}) of earlier architectures for state-of-the-art performance.
+Residual Dense Network (RDN) \parencite{zhangResidualDenseNetwork2018} is a deep learning super-resolution method which consists of a series of residual dense blocks (\Cref{fig:rdb,fig:convs}), which combine the performant residual connections and dense connections (\Cref{fig:convs}) of earlier architectures for state-of-the-art performance.
 Residual and dense connections provide additional learning capacity to a CNN, where features learnt in early layers can be fully utilised in later layers.
@@
 
-G is analogous in design to the RDN architecture described above (\cref{fig:rdn}), and is trained to upscale a low-resolution input, creating a super-resolution prediction.
+G is analogous in design to the RDN architecture described above (\Cref{fig:rdn}), and is trained to upscale a low-resolution input, creating a super-resolution prediction.
 The Discriminator network used in ESRGAN is based on a prevalent image classification architecture known as VGG \parencite{simonyanVeryDeepConvolutional2015}.
@@
 
-The specific variant of ESRGAN applied in this work is that of ESRGAN+ \parencite{rakotonirinaESRGANFurtherImproving2020}, which incorporates modern GAN performance improving techniques, including generator noise injection (noted in \cref{fig:rdb}), and additional dense and residual connections (noted in \cref{fig:convs}).
+The specific variant of ESRGAN applied in this work is that of ESRGAN+ \parencite{rakotonirinaESRGANFurtherImproving2020}, which incorporates modern GAN performance improving techniques, including generator noise injection (noted in \Cref{fig:rdb}), and additional dense and residual connections (noted in \Cref{fig:convs}).
 These additional connections are used in RDN\textdaggerdbl{}.
@@
 \subsection{Geophysical context}
-The Eastern Goldfields Superterrane of Western Australia is extensively covered by aeromagnetic surveys of \SI{400}{\metre} line spacing or better, especially over its South-Western extent.
+The Eastern Goldfields Superterrane of Western Australia is extensively covered by aeromagnetic surveys of \qty{400}{\metre} line spacing or better, especially over its South-Western extent.
 Large survey extents are government sponsored through the Exploration Incentive Scheme \parencite[e.g.][]{griffinStimulatingGreenfieldsExploration2010}, with these low-resolution regional surveys serving to identify prospective areas to undertake surveys at higher resolution.
@@
 A similar technique could be used in geophysics SR by applying a low pass filter with a suitable cut-off to a HR grid to simulate the LR counterpart.
-However, here we use data from existing grids published at the appropriate four times resolution difference, namely the Magnetic merged grid of Western Australia 2020 at \SI{20}{\metre} (HR) and \SI{80}{\metre} (LR) cell sizes \parencite{brett80MagneticMerged2020}.
-When these grids were created, the best available resolution of all grids across the state were compiled at \SI{20}{\metre} cell size, and interpolated to \SI{80}{\metre} using a 4th order Newton polynomial interpolation process \parencite[][personal communication]{brett80MagneticMerged2020}.
+However, here we use data from existing grids published at the appropriate four times resolution difference, namely the Magnetic merged grid of Western Australia 2020 at \qty{20}{\metre} (HR) and \qty{80}{\metre} (LR) cell sizes \parencite{brett80MagneticMerged2020}.
+When these grids were created, the best available resolution of all grids across the state were compiled at \qty{20}{\metre} cell size, and interpolated to \qty{80}{\metre} using a 4th order Newton polynomial interpolation process \parencite[][personal communication]{brett80MagneticMerged2020}.
 This is similar to bicubic interpolation, in that both methods are examples of localised polynomial based interpolation algorithms.
 While the cell size is uniform for each respective state grid, the sampling interval of the contributing line surveys varies across the state, which affects the extent of coverage of high frequency components across each grid.
-To ensure that the HR ground truth has additional high frequency detail to the LR during training, data were only selected from areas of the Goldfields area of the state grid with contributing survey line spacing \SI{300}{\metre} or closer (optimal cell size strictly finer than \SI{80}{\metre}).
-Training and validation data were extracted independent to a reserved test area, outlined in \cref{fig:trainvaldata}.
+To ensure that the HR ground truth has additional high frequency detail to the LR during training, data were only selected from areas of the Goldfields area of the state grid with contributing survey line spacing \qty{300}{\metre} or closer (optimal cell size strictly finer than \qty{80}{\metre}).
+Training and validation data were extracted independent to a reserved test area, outlined in \Cref{fig:trainvaldata}.
 By selecting mixed line spacing data in this way, transforms between different scales of frequency loss are captured in the training data.
-That is, the same model can learn from fine optimal cell size extents that lose many component frequencies when interpolated to \SI{80}{\metre}, as well as coarse cell size extents which may only lose few or none.
-These data were extracted as square tiles, each covering \SI{2560}{\metre} by \SI{2560}{\metre} at 32 \texttimes{} 32 pixels for LR, and 128 \texttimes{} 128 pixels for HR, with no overlap.
+That is, the same model can learn from fine optimal cell size extents that lose many component frequencies when interpolated to \qty{80}{\metre}, as well as coarse cell size extents which may only lose few or none.
+These data were extracted as square tiles, each covering \qty{2560}{\metre} by \qty{2560}{\metre} at 32 \texttimes{} 32 pixels for LR, and 128 \texttimes{} 128 pixels for HR, with no overlap.
 This resulted in \num{5290} training tile pairs (used to train the model), \num{512} validation tile pairs (used to select the best performing model), and \num{2415} test tile pairs (used to independently verify the performance of the selected model).
@@
 These values were min-max scaled to a range of 0 to 1 using the global minimum and maximum values of the HR training data.
-In summary, the single channel high- and low-resolution state TMI grids were filtered according to a database of their component surveys to extract areas of \SI{300}{\metre} line spacing or less.
+In summary, the single channel high- and low-resolution state TMI grids were filtered according to a database of their component surveys to extract areas of \qty{300}{\metre} line spacing or less.
 These data were normalised according to the statistics of the HR training set, and split into small patches suitable for the hardware limitations.
@@
     \caption[Dataset context]{Reserved training/validation and test areas of Eastern Goldfields Superterrane magnetic grid, and their tectonic context.
-        Background: \SI{20}{\metre} merged magnetic grid of Western Australia, \parencite{brett40MagneticMerged2020}.
+        Background: \qty{20}{\metre} merged magnetic grid of Western Australia, \parencite{brett40MagneticMerged2020}.
     }
@@
 \subsection{Test dataset}
-We first present a visual comparison of a selected feature rich \SI{80}{\metre} cell size LR tile, its counterpart \SI{20}{\metre} HR ground truth tile, and the result of; the bicubic upscaling filter, the RDN\textdaggerdbl{} upsampling network, and the ESRGAN+ upsampling network as applied to the LR tile (\cref{fig:resultsvis}).
+We first present a visual comparison of a selected feature rich \qty{80}{\metre} cell size LR tile, its counterpart \qty{20}{\metre} HR ground truth tile, and the result of; the bicubic upscaling filter, the RDN\textdaggerdbl{} upsampling network, and the ESRGAN+ upsampling network as applied to the LR tile (\Cref{fig:resultsvis}).
 This tile was selected from the reserved test region in the Eastern Goldfields Superterrane, and neither of the low- or high-resolution samples were seen during training.
-The result of bicubic interpolation (\cref{fig:resultsvis} c) demonstrates the smoothing effect of the bicubic filter, while the Residual Dense Network (\cref{fig:resultsvis} d) and ESRGAN+ network (\cref{fig:resultsvis} e) show added detail.
-The two neural network methods more closely match the ground truth \SI{20}{\metre} tile than the bicubic upsampled image does, when observing feature edges and textural detail.
+The result of bicubic interpolation (\Cref{fig:resultsvis} c) demonstrates the smoothing effect of the bicubic filter, while the Residual Dense Network (\Cref{fig:resultsvis} d) and ESRGAN+ network (\Cref{fig:resultsvis} e) show added detail.
+The two neural network methods more closely match the ground truth \qty{20}{\metre} tile than the bicubic upsampled image does, when observing feature edges and textural detail.
 
@@
     \caption[Visual inference results]{Visual comparisons of a selected tile from the reserved test region.
-        The \SI{80}{\metre} low-resolution input (a) is shown at equivalent size to the \SI{20}{\metre} high-resolution ground truth (b) using nearest neighbour interpolation.
+        The \qty{80}{\metre} low-resolution input (a) is shown at equivalent size to the \qty{20}{\metre} high-resolution ground truth (b) using nearest neighbour interpolation.
         The colourmap is shared between subfigures.
@@
 The Radially Averaged Power Spectral Density (RAPSD) \parencite{ulichneyDitheringBlueNoise1988} is a one-dimensional representation of the cumulative power of each frequency component, in any orientation within the image.
-\cref{fig:rapsd} shows the RAPSD for the different methods over the test extent shown in \cref{fig:trainvaldata}.
-The deep learning methods have consistently superior power in predicted wavelengths between approximately \SI{640}{\metre} and \SI{120}{\metre}, with RDN\textdaggerdbl{} closely matching the groundtruth spectra, while ESRGAN+ tends to exaggerate.
+\Cref{fig:rapsd} shows the RAPSD for the different methods over the test extent shown in \Cref{fig:trainvaldata}.
+The deep learning methods have consistently superior power in predicted wavelengths between approximately \qty{640}{\metre} and \qty{120}{\metre}, with RDN\textdaggerdbl{} closely matching the groundtruth spectra, while ESRGAN+ tends to exaggerate.
 
@@
     \includegraphics[width=\linewidth]{fig/p1/rapsd.jpg}
-    \caption[short]{Radially Averaged Power Spectra for the complete test extent shown in \cref{fig:trainvaldata}.
+    \caption[short]{Radially Averaged Power Spectra for the complete test extent shown in \Cref{fig:trainvaldata}.
         The Nyquist wavelengths for the high-resolution (and upsampled) rasters and low-resolution raster are also shown.
         The frequency axis has been transformed to wavelength, and the spectra have been normalised for direct comparison.
-        Note the complete test extent is covered by surveys with a range of line spacings from \SI{100}{\metre} to \SI{20}{\metre}, with \SI{100}{\metre} being the most extensive.
-        The Nyquist wavelength of the \SI{100}{\metre} surveys (optimal grid cell size approximately \SI{20}{\metre}) likely causes the reduction in power at \SI{55}{\metre} and \SI{220}{\metre}.
+        Note the complete test extent is covered by surveys with a range of line spacings from \qty{100}{\metre} to \qty{20}{\metre}, with \qty{100}{\metre} being the most extensive.
+        The Nyquist wavelength of the \qty{100}{\metre} surveys (optimal grid cell size approximately \qty{20}{\metre}) likely causes the reduction in power at \qty{55}{\metre} and \qty{220}{\metre}.
     }
@@
 To visualise the contribution of these enhanced high frequencies in the resulting grid, the super-resolved output from each method is high pass filtered, with a cut-off wavelength equivalent to the Nyquist wavelength of the LR grid.
-By filtering at this wavelength, only frequencies added by the upsampling process will be shown in the output (\cref{fig:filtered}).
-Bicubic interpolation (\cref{fig:filtered} c) fails to add significant high frequency components.
-RDN\textdaggerdbl{} (\cref{fig:filtered} d) appears to approximate similar high frequencies to the HR tile (\cref{fig:filtered} b), while ESRGAN+ (\cref{fig:filtered} e) shows potentially excessive predicted high frequency components.
-Finally, metrics for the full set of test tiles are reported in \cref{tab:metrics}.
+By filtering at this wavelength, only frequencies added by the upsampling process will be shown in the output (\Cref{fig:filtered}).
+Bicubic interpolation (\Cref{fig:filtered} c) fails to add significant high frequency components.
+RDN\textdaggerdbl{} (\Cref{fig:filtered} d) appears to approximate similar high frequencies to the HR tile (\Cref{fig:filtered} b), while ESRGAN+ (\Cref{fig:filtered} e) shows potentially excessive predicted high frequency components.
+Finally, metrics for the full set of test tiles are reported in \Cref{tab:metrics}.
 The non-GAN CNN approach of RDN\textdaggerdbl{} remains the most accurate method for the entire test grid.
 Several routinely occurring artefacts are observed in the two super-resolution products, especially in ESRGAN+ which incorporates details it has learned from the Discriminator network loss.
-The First Vertical Derivative filter is used in \cref{fig:jhillvis} to demonstrate the ability to perform common geophysical filters on super resolved grids, and to emphasise examples of these artefacts.
+The First Vertical Derivative filter is used in \Cref{fig:jhillvis} to demonstrate the ability to perform common geophysical filters on super resolved grids, and to emphasise examples of these artefacts.
 The most apparent artefact arises from the inference implementation when upsampling a grid larger than fits in memory, where visible edges appear around individual tiles in the compiled inference grid (e.g.
-\cref{fig:jhillvis}, *).
+\Cref{fig:jhillvis}, *).
 This could be reduced by adjusting the size of inference tiles, or slightly overlapping adjacent input tiles.
-Predictions from ESRGAN+ commonly show a ripple-like texture (\cref{fig:jhillvis}, \^{ }), especially around pronounced high TMI features.
+Predictions from ESRGAN+ commonly show a ripple-like texture (\Cref{fig:jhillvis}, \^{ }), especially around pronounced high TMI features.
 The effect of this texture occasionally reveals features matching the high-resolution groundtruth that are not predicted by the bicubic or RDN\textdaggerdbl{} upsampling, but the excess of “noisy” features present in ESRGAN+ predictions will likely limit its applicability when interpreting low-resolution grids with no corresponding groundtruth.
@@
         \hline{}
-                & Mean    & {Standard                                                   \\ Deviation} & Mean & {Standard \\ Deviation} & Mean & {Standard \\ Deviation} \\
-        RMSE    & 13.545  & 26.576    & 7.265               & 13.741 & 11.120  & 21.670 \\
-        SISM    & 0.924   & 0.047     & 0.959               & 0.037  & 0.922   & 0.054  \\
-        MS-SSIM & 0.971   & 0.018     & 0.988               & 0.012  & 0.976   & 0.020  \\
+                & Mean    & {Standard                                                            \\Deviation} & Mean & {Standard\\Deviation} & Mean & {Standard\\Deviation}                                                                         \\
+        RMSE    & 13.545  & 26.576    & \textbf{7.265}      & \textbf{13.741} & 11.120  & 21.670 \\
+        SISM    & 0.924   & 0.047     & \textbf{0.959}      & \textbf{0.037}  & 0.922   & 0.054  \\
+        MS-SSIM & 0.971   & 0.018     & \textbf{0.988}      & \textbf{0.012}  & 0.976   & 0.020  \\
     \end{tblr}
@@
 \subsection{Jasper Hill / Lord Byron super-resolution}
-A low-resolution TMI extent from the \SI{80}{\metre} state map over the Jasper Hill major resource project was selected for detailed investigation.
-This extent was surveyed at \SI{50}{\metre} (optimal cell size of \SI{10}{\metre}), and is outside of both the defined training and test extents.
-A zoomed result for each upsampling method is shown in \cref{fig:jhilldykes}.
+A low-resolution TMI extent from the \qty{80}{\metre} state map over the Jasper Hill major resource project was selected for detailed investigation.
+This extent was surveyed at \qty{50}{\metre} (optimal cell size of \qty{10}{\metre}), and is outside of both the defined training and test extents.
+A zoomed result for each upsampling method is shown in \Cref{fig:jhilldykes}.
 The bicubic filter produces a smooth interpolation with limited magnetic intensity enhancement of the features, while both neural network methods produce a more accurate value prediction.
 East-West striking features, like those that have been associated with gold mineralisation in the region \parencite[p.~283]{salierTimingSourceGoldbearing2003} are better delineated when using RDN\textdaggerdbl{} and ESRGAN+, and nearly unobservable with bicubic interpolation.
-This can be seen in the line profile (\cref{fig:jhilldykes}, f), where a series of East-West striking features have a total magnitude of approximately \SI{100}nT in the low-resolution and bicubic grids, versus approximately \SI{200}nT in the Residual Dense Network prediction and HR groundtruth.
-The ESRGAN+ prediction profile shows two distinct low TMI features, but they are poorly located and incoherent in the TMI grid (\cref{fig:jhilldykes} e), which shows an example of the ripple-mark artefact previously noted.
+This can be seen in the line profile (\Cref{fig:jhilldykes}, f), where a series of East-West striking features have a total magnitude of approximately \qty{100}nT in the low-resolution and bicubic grids, versus approximately \qty{200}nT in the Residual Dense Network prediction and HR groundtruth.
+The ESRGAN+ prediction profile shows two distinct low TMI features, but they are poorly located and incoherent in the TMI grid (\Cref{fig:jhilldykes} e), which shows an example of the ripple-mark artefact previously noted.
 
@@
     \caption[Jasper Hills Project TMI grids and line profile]{Jasper Hills Project TMI grids (a--e) and line profile (f).
-        Bicubic interpolation of the low-resolution grid closely matches the low-resolution grid, while both super-resolution methods better approximate the magnitude of the features present in the HR profile, between \SI{650}{\metre} and \SI{1020}{\metre}.
+        Bicubic interpolation of the low-resolution grid closely matches the low-resolution grid, while both super-resolution methods better approximate the magnitude of the features present in the HR profile, between \qty{650}{\metre} and \qty{1020}{\metre}.
     }
@@
 The deep learning methods used here can be trained with data from other geospatial extents, either from scratch or by initialising the training with pre-existing model weights \parencite[][e.g.]{wangMineGANEffectiveKnowledge2020}.
-The existing models can also be applied to other extents of \SI{80}{\metre} TMI grids without further training.
-However, the training data used here are solely \SI{80}{\metre} TMI grids interpolated from high-resolution \SI{20}{\metre} state map extents in the southwest Eastern Goldfields Superterrane.
+The existing models can also be applied to other extents of \qty{80}{\metre} TMI grids without further training.
+However, the training data used here are solely \qty{80}{\metre} TMI grids interpolated from high-resolution \qty{20}{\metre} state map extents in the southwest Eastern Goldfields Superterrane.
 Magnetic anomalies and features that are dissimilar from those represented in the Superterrane (for example, different geological settings, or regions with different magnetic inclination) are likely to suffer from reduced performance.
-This applies also to grids that do not have a cell size of \SI{80}{\metre}.
-An example use case for either the method or trained models is super-resolving the Total Magnetic Intensity (TMI) Grid of Australia 2019 - seventh edition which is published by Geoscience Australia in only \SI{80}{\metre} and \SI{40}{\metre} cell size.
-The trained \SI{80}{\metre} models in this work could be applied to the \SI{80}{\metre} TMI grid, or the method used with existing state map data to train a two times scale model to super-resolve the \SI{40}{\metre} grid to \SI{20}{\metre}.
+This applies also to grids that do not have a cell size of \qty{80}{\metre}.
+An example use case for either the method or trained models is super-resolving the Total Magnetic Intensity (TMI) Grid of Australia 2019 - seventh edition which is published by Geoscience Australia in only \qty{80}{\metre} and \qty{40}{\metre} cell size.
+The trained \qty{80}{\metre} models in this work could be applied to the \qty{80}{\metre} TMI grid, or the method used with existing state map data to train a two times scale model to super-resolve the \qty{40}{\metre} grid to \qty{20}{\metre}.
 Transferability of the model used in this study to other geological settings and magnetic inclinations requires further investigation, with the aim of developing a single multi-domain potential field upscaling model.
 
-The use of the state magnetic map at \SI{80}{\metre} and \SI{20}{\metre} for training data serves as a ready-made analogue for a low pass filter process, which the super-resolution networks successfully learnt to reverse.
+The use of the state magnetic map at \qty{80}{\metre} and \qty{20}{\metre} for training data serves as a ready-made analogue for a low pass filter process, which the super-resolution networks successfully learnt to reverse.
 While the result presented here demonstrates the strong applicability of performing super-resolution with grids containing magnetic textures and features, it does not yet demonstrate a capability to super-resolve widely spaced line surveys as if they had been surveyed at closer line spacing.
-Such grids include artifacts from the gridding process that do not occur in low pass filtered or interpolated high-resolution grids, and will present an additional challenge to super-resolve.
+Such grids include artefacts from the gridding process that do not occur in low pass filtered or interpolated high-resolution grids, and will present an additional challenge to super-resolve.
 These challenges remain for future work.

### 2023-10-08 discussion.tex
Work toward whole compilation

@@
 % and provide overall conclusions that address the research aims.
-\setcounter{chapter}{1}
+% \setcounter{chapter}{1}
 
@@
 The resulting RDN and ESRGAN models can be compared with the LTE model described in Chapter 2, although the fixed factor upscaling block in the earlier networks limits this comparison to 4x scale.
-\Cref{fig:rdncomp} shows that RDN and ESRGAN are both highly performant for the task of predicting accurate features when upscaling \SI{320}{\m} data to \SI{40}{\m} line spacing.
+\Cref{fig:rdncomp} shows that RDN and ESRGAN are both highly performant for the task of predicting accurate features when upscaling \qty{320}{\m} data to \qty{40}{\m} line spacing.
 It can be inferred that the challenge of super-resolution is predominantly a question of providing suitable and sufficient training data, and less constrained to neural network choices.
@@
 
+\chapter{Conclusion}
+Hello I am the conclusion
+
 \end{document}

### 2023-10-08 manuscript.tex
Add affiliations
Work toward whole compilation

@@
         School of Earth Sciences
-        \vspace{15 mm}
+        \vspace{20 mm}
 
@@
             \centering{}
-            \includegraphics[scale=0.6]{fig/etc/UWA_FORMAL_PORTRAIT_CMYK}
+            \includegraphics[scale=0.5]{fig/etc/UWA_FORMAL_PORTRAIT_CMYK}
         \end{figure}
@@
 \vfill{}
-\epigraph{All collected data had come to a final end. Nothing was left to be collected.}{}
+\epigraph{\emph{All collected data had come to a final end. Nothing was left to be collected.}}{}
 
@@
 \vfill{}
-\epigraph{But all collected data had yet to be completely correlated and put together in all possible relationships.}{Isaac Asimov}
+\epigraph{\emph{But all collected data had yet to be completely correlated and put together in all possible relationships.}}{Isaac Asimov}
 
@@
 \tableofcontents{}
-% \listoffigures{}
-% \listoftables{}
+\listoffigures{}
+\listoftables{}
 
@@
 \newpage{}
-\subfile{authorship_declaration}
+% \subfile{authorship_declaration}
+\includepdf[pages=-]{authorship_declaration_signed.pdf}
 
@@
 \chapter{Introduction}
+\label{ch:intro}
 \subfile{intro}
@@
 \chapter{Magnetic Grid Resolution Enhancement using Machine Learning}
-\label{paper1}
+\label{ch:paper1}
 This chapter has been reproduced from the following peer reviewed publication. Formatting has been adjusted for consistency.
@@
 
-\chapter{A Line Spacing Method for Super-resolution of Geophysical Surveys}
-\label{paper2}
-% \subfile{paper2}
+\chapter{Super-resolution of Aeromagnetic Survey Data}
+\label{ch:paper2}
+\subfile{paper2}
 
 \chapter{Implicit Neural Representation for Potential Field Geophysics}
-\label{paper3}
+\label{ch:paper3}
 % \subfile{paper3}
@@
 \chapter{Discussion}
+\label{ch:discussion}
 \subfile{discussion}

### 2023-10-08 paper2.tex
Work toward whole compilation

@@
 \begin{document}
-\setcounter{chapter}{1}
+% \setcounter{chapter}{1}
 \title{Super-resolution of Aeromagnetic Survey Data}
@@
 A comprehensive review of alternative spatial interpolation methods is presented by \textcite{liReviewComparativeStudies2011}.
-Each method of gridding has characteristic interpolation traits (which when undesired are termed artifacts), but irrespective of the gridding process the detail resolvable in the output grid is a product of the sample height, sampling density, and the final cell size at which the grids are rendered.
+Each method of gridding has characteristic interpolation traits (which when undesired are termed artefacts), but irrespective of the gridding process the detail resolvable in the output grid is a product of the sample height, sampling density, and the final cell size at which the grids are rendered.
 Gridding at a finer cell size preserves higher frequencies present in the sampled data, resulting in greater detail.
@@
 Achieving higher resolution traditionally requires additional sampling to increase the grid resolution.
-%, which refines structures in the response and reduces blocky textures and other gridding artifacts.
+%, which refines structures in the response and reduces blocky textures and other gridding artefacts.
 In addition to human interpretation, machine processing of geophysical data is benefitted by using higher resolution data, with the negligible cost of increased computational load.
@@
 \Cref{sec:2methods} describes the experimental design to generate low-resolution aeromagnetic survey grids from synthetic and real-world data, where \Cref{sec:baseline,sec:finetune} specifically describe the training approach for the neural network model.
-Results are presented in \Cref{sec:2results} and are discussed in \Cref{sec:discussion}.
+Results are presented in \Cref{sec:2results} and are discussed in \Cref{sec:2discussion}.
 Conclusions are drawn in \Cref{sec:2conclusion}.
@@
 The cubic method of Verde (itself implemented by Scipy Clough-Tocher 2D interpolation \parencite{2020SciPy-NMeth}) produces a \(C^1\) smooth grid with minimised curvature.
-This type of gridding is common for regularising geophysical data and creates a variety of typical low-resolution artefacts such as aliasing and bullseye artifacts.
+This type of gridding is common for regularising geophysical data and creates a variety of typical low-resolution artefacts such as aliasing and bullseye artefacts.
 \Cref{fig:lrdata} shows an example of the resulting high- and low-resolution grids for the proposed line sampling and gridding process.
@@
 \section{Discussion}
-\label{sec:discussion}
+\label{sec:2discussion}
 The Noddyverse synthetic training dataset comprises geology models with a variety of realistic petrophysics and geological histories, and was sampled using simple but realistic airborne survey methodology.

### 2023-10-08 paper3.tex
Work toward whole compilation

@@
 \begin{document}
-\setcounter{chapter}{1}
-\title{Implicit Neural Representation for Potential Field Geophysics }
+% \setcounter{chapter}{1}
+\title{Implicit Neural Representation for Potential Field Geophysics}
 \author[1*]{Luke Thomas Smith}
@@
 
-\Cref{fig:grid} shows the INR queried at \(z=\qty{40}{\m}\), which is the nominal terrain clearance of the survey.
+\Cref{fig:grid40} shows the INR queried at \(z=\qty{40}{\m}\), which is the nominal terrain clearance of the survey.
 A good qualitative match is achieved between the GA reference grid and the grid queried from the implicit representation, which successfully reconstructs the linear dune features and circular rim features.
@@
 The residuals are shown for areas containing reference data (right), with a range of ±2 standard deviations of values in the reference grid.}
-    \label{fig:grid}
+    \label{fig:grid40}
 \end{figure}
@@
 The INR can be queried at arbitrary continuous coordinates, including out-of-range values beyond the training domain.
-As expected, the predicted field becomes unrealistic when extrapolating beyond this boundary, which can be seen in the periphery of the INR grid in \Cref{fig:grid}.
+As expected, the predicted field becomes unrealistic when extrapolating beyond this boundary, which can be seen in the periphery of the INR grid in \Cref{fig:grid40}.
 This boundary region (indicated by solid white in the reference grid) is excluded from PSNR calculation.
@@
 This correlates with the poor continuation performance of model when predicting level grids several metres or more beyond the nominal sample height.
-This is interpreted as the presented model having a limited capacity to extrapolate, and learning a poor representation of the vertical component of the potential field, which we further discuss in \Cref{sec:discussion}
+This is interpreted as the presented model having a limited capacity to extrapolate, and learning a poor representation of the vertical component of the potential field, which we further discuss in \Cref{sec:3discussion}
 
@@
 \section{Discussion}
-\label{sec:discussion}
+\label{sec:3discussion}
 The proposed method has strong learning capacity for the potential field samples in the horizontal plane near the nominal survey altitude, allowing extraction of level grids which are accurate against the reference grid.
@@
 Level grids can be extracted from these representations, emerging as a novel method for regularising scattered geophysical sample data.
-Gradients calculated using the learnt representation are , and gridded after gradient calculation.
+Gradients calculated using the learnt representation are near-identical to those calculated by existing numerical methods, and benefit from being gridded after gradient calculation.
 

### 2023-10-08 intro.tex
Revise introduction: Part 1

--- 2023-09-19 intro.tex
@@
 \begin{document}
+\setcounter{chapter}{1}
 
-\section{Introduction} %  indicates that an original and coherent argument is being developed and that the research is making a contribution to existing literature
+% indicates that an original and coherent argument is being developed and that the research is making a contribution to existing literature
 % outline the topic, justify the research, identify research aims and outline thesis structure
-\subsection{Big geodata}
-(2 pg)
-%% Airborne surveys are routinely conducted as pre-competitive regional data acquisition to stimulate exploration, or as targeted investigations by the exploration industry.
-%% Surveys are also routinely collected on the ground or by satellite, with processing methods and interpretation shared between all forms of acquisition.
-%% The collected data may contain millions of discrete samples scattered in three dimensions,
-%% Interpretation often relies on regularisation to a quantised grid, allowing digital processing and human or machine interpretation.
-The subsurface continuation of exposed geology can be extrapolated and interpolated using structures in the magnetic responses.
-For this reason, magnetic field survey grids remain a standard tool in the geological mapping and interpration toolbox. 
-Open file data from government or publicly released commercial surveys form part of the greenfields exploration.
-Case studies on open file data are presented throughout to develop the method.
-%% Budgets: Flying, handling, storage,
 
-% Enhance the information extractable from potential field surveys.
-% In combination they reflect ongoing advances in deep learning and,
-% their extension to challenges and opportunities in geophysics.
+% Ensure acronyms correctly used
 
-\subsection{Research Contributions and Thesis Structure}
-% paper or series of papers suitable for publication in scholarly journals; or a combination of published and unpublished work
-This thesis is presented as a series of papers which are published or in-preparation for publication in scholarly journals.
-Chapter 1 presents a published manuscript, typefaced for consistency with the remaining thesis.
-Chapters 2 and 3 present original research in preparation as articles for publication.
-A discussion arising from these works is provided in chapter 4, and a brief overview of the content and contributions of each chapter is given here.
+\section{Potential field geophysics in exploration geoscience}
+\label{sec:introgeo}
+%- what are they used for (summary) 
+The subsurface continuation of exposed geology can be extrapolated and interpolated using structures mapped in surveys of the Earth's naturally occuring potential fields.
+Mapping methods using these fields are routinely used in geoscience for low-cost investigations of the subsurface over a large spatial volume.
+For this reason, magnetic field surveys are commonly used by geophysicists for geological mapping and interpretation \parencite{nabighian75thAnniversaryHistorical2005}.
+In addition, potential field data are used as inputs to computer processing tasks such as numerical modelling and inversion.
+In these tasks, various dimensions of geoscience data are integrated to make predictions regarding the subsurface.
+These and other geophysical methods are becoming more important to exploration as resources are increasingly sought from below sedimentary cover.
 
-Chapters 2 and 3
+\subsection{Aeromagnetic surveys}
+% how are they gathered (surveys)
+One of the fundamental methods routinely used for mineral exploration are aerogeophysical surveys of the Earth's magnetic or gravitational potential fields.
+Airborne surveys are acquired at a range of scales at different stages of exploration, from pre-competitive regional data to stimulate exploration \parencite{howardAirborneGeophysicalCoverage2004}, to targeted investigations by the exploration industry at the prospect scale of up to several square kilometres.
+Surveys are also routinely collected on the ground, or less commonly in exploration, by ship or satellite, with most processing methods and interpretation shared between all forms of acquisition.
+Aeromagnetic surveys are among the lowest cost geophysical method \parencite{dentithGeophysicsMineralExploration2014}, however the cost rapidly increases when surveying at higher resolution due to overheads in flight line sampling.
+When collecting data, aircraft fly straight transect lines at a nominal safe elevation above topography, known as the topography drape.
+Surveys are flown with a nominal heading for the direction that data will be acquired along line.
+For regional surveys this is recommended to be North-South, however early practice was perpendicular to the dominant geological strike, under the expectation of sampling the greatest frequency of change in magnetic intensity \parencite{islesGeologicalInterpretationAeromagnetic2018}.
+Because the power in higher frequencies diminishes with increasing source-sensor distance, the lower the height, the more high-frequency components will be captured by the sensor, a fact which will become important in subsequent sections.
+Acquisition along flight lines is sampled at a rate of \qty{10}{\hertz} or greater, which corresponds to an interval of \qty{7}{\m} or shorter at nominal flight speeds of \qty{70}{\m\per\s} \parencite{goodwinAirborneMagneticRadiometric2023}.
+The spacing between lines is a factor of the scale of investigation and cost, and regional pre-competitive data in Australia targets state-wide coverage at \qty{400}{\m}, which is generally regarded as the upper limit of usefulness to exploration \parencite{howardAirborneGeophysicalCoverage2004}.
+These low-resolution surveys, funded by government geoscience agencies, are a key driver in greenfields exploration and are released as open file data.
+Higher-resolution surveys over prospective areas fly lines at closer line spacings, of the order \qty{100}{\m}, in order to resolve greater detail.
+The importance of these parameters in relation to resolvable detail will be outlined shortly.
+The collected data may contain millions of samples scattered in three dimensions, and interpretation or processing often relies on regularisation to a quantised grid.
+
+\subsection{Survey data regularisation}
+% - how are they transformed (gridding)
+Survey data can be interpreted as one dimensional transects, but more commonly they are regularised to a two-dimensional grid raster for interpretation in a process termed gridding.
+The resulting interpolated array contains uniformly spaced nodes and is referred to as a grid.
+Grids are raster data, where each pixel stores a scalar measurement of a specific property.
+In geophysics and throughout this manuscript, these are referred to as cells, and the property is a measure of the strength of the magnetic field at a specific location.
+The field strength measured is the Total Magnetic Intensity (TMI), which is the vector sum of each directional vector of the potential \parencite{blakelyPotentialTheoryGravity1996}.
+This scalar value is recorded in nanoTesla and may be negative with an unbounded range that can exceed \qty{50,000}{\nano\tesla} in the Earth's environment.
+The location recorded at a sample point is the geographic latitude and longitude, and altitude, acquired with high-precision differential GPS, alongside radar altimeter elevation.
+These data may be transformed to a flat projected system, where spatial dimensions are expressed in meters, used throughout this manuscript.
+There are numerous well-established gridding methods, and novel methods are frequently proposed in the literature.
+The simplest is known as nearest neighbour interpolation, where each node is set to equal to the closest sample value.
+Of those most commonly used in potential field geophysics, these are minimum curvature \parencite{briggsMachineContouringUsing1974}, splines \parencite{bhattacharyyaBicubicSplineInterpolation1969,shureHarmonicSplinesGeomagnetic1982,smithGriddingContinuousCurvature1990}, and equivalent sources \parencite{dampneyEquivalentSourceTechnique1969, solerBetterStrategyInterpolating2020}.
+Splines are used in bi-directional gridding, which is well-suited for aeromagnetic surveys, where the sample data are first interpolated in the line parallel direction, and the intermediate product is interpolated in the line perpendicular direction \parencite{dentithGeophysicsMineralExploration2014}.
+In other areas of geoscience, a statistical interpolator is frequently used, known as kriging \parencite{hansenInterpretiveGriddingAnisotropic1993,davis1986statistics}.
+Some recently proposed gridding methods include the methods of \textcite{naprstekNewMethodInterpolating2019}, \textcite{xuGravityAnomalyReconstruction2019}, or \textcite{chenPotentialFieldData2022}.
+Each interpolation method attempts to predict regularly spaced grids by leveraging properties intrinsic to the data, with the possible explicit integration of \emph{a priori} knowledge such as geophysical laws or geological context.
+A review of spatial interpolation methods is provided in \textcite{liReviewComparativeStudies2011}
+
+\subsection{A definition for geophysical resolution}
+In all interpolated grids, the spatial dimension of each cell is referred to as the cell size, with the unit of metre used in this manuscript.
+As stated above, resolvable detail in geophysical surveys is a product of the distance between the causative magnetic body and sensor (height), and the line spacing \parencite{islesRelationshipsGeologicalResolution1992,islesGeologicalInterpretationAeromagnetic2018,dentithGeophysicsMineralExploration2014}.
+Height is easily controlled by flying the lowest safe and sufficiently smooth topography drape, and along-line sampling is performed at a constant high rate, so the key factor controlling resolution in aeromagnetic survey design is the line spacing.
+Further survey design considerations for airborne geophysics are outlined in \textcite{goodwinAirborneMagneticRadiometric2023,islesGeologicalInterpretationAeromagnetic2018,reidAeromagneticSurveyDesign1980}.
+Each gridding method includes a final cell size parameter selectable by the geophysicist, with a long-standing guideline of one third to one fifth the line spacing.
+This sufficiently preserves detail in areas of high sampling, while avoiding excessive interpolated cells in areas of low sampling, which may lead to artefacts.
+Because of the sampling frequency of nominally \qty{7}{\m} in the flight line direction, and  up to \qty{400}{\m} in the line perpendicular direction, the resulting grid resolution will be anisotropic at best, and uniformly low-resolution at worst.
+An important property of sampled data is the Nyquist frequency, \[f_{Nyquist} = f_{sampling} / 2.\]
+This is the lowest frequency at which a bandwidth limited signal may be sufficiently sampled, beyond which higher frequencies will be incorrectly recorded as aliasing.
+An aliased signal contains spurious low-frequency features caused by the sampling, not the underlying signal.
+This limiting frequency applies to each sampling direction in surveys, as well as the cell size of the grid.
+The smallest resolvable feature in each of these can be spatially described by wavelength, as the inverse of frequency.
+In low-resolution aeromagnetic surveys of \qty{400}{\m} line spacing, strong variations of magnetic intensity in the line-perpendicular direction  that occur over a distance shorter than \qty{800}{\m} will be aliased.
+When gridded at \qty{80}{\m} cell size, the corresponding limit on resolvable detail is features as small as \qty{160}{\m}.
+% This choice of cell size will effectively filter out features in the line-parallel direction that vary strongly, from those possibly present at \qty{14}{\m} through to \qty{160}{\m}.
+Depending on the complexity of the geological domain, this may cause spatial aliasing in one direction.
+This is visible in grids where features take on a blocky or stepped appearance, referred to as a beading artefact, or generally in this manuscript as a low-resolution artefact.
+Low-resolution gridded aeromagnetic data refers to surveys with a wide line spacing causing a lack of high-frequency details in the line-perpendicular direction, resulting in potential artefacts or missing features in grid data.
+
+Here, we arrive at the definition of resolution adopted throughout this thesis.
+
+\emph{Resolution in potential field geophysics refers to the sampling of high-frequencies present in the potential field caused by a geological source.
+    Resolution is further defined by the preservation of these frequencies in gridded potential field data.}
+
+% - How are they used (geo interp, modelling, filtering) (detailed)
+% levelling
+% geological interpretation
+% modellin
+%
+
+\section{Geophysics data in machine learning}
+\label{sec:introdata}
+% e.g. limited training data to deal with diverse geological features, geology various regionally - different potential fields features and range, etc....
+Natural image raster data are ubiquitous in computer vision machine learning.
+These are most commonly three channel arrays containing normalised brightness values in the red, green and blue channels.
+Resolution in these rasters is typically a product of an imaging system or software defined grid with regular sampling.
+Like in geophysics, these raster data have an array height and width, which is referred to as resolution.
+However, the lack of spatial quantification for the size of natural images confuses the term with its definition for geophysical resolution.
+
+Resulting from the processes described in \Cref{sec:introgeo}, geophysical rasters are highly distinct from the image data used widely in computer vision.
+This includes the number of channels (3 in natural images, 1 in aeromagnetics), range (255 compared to 50,000 or more), and anisotropy of resolution.
+Additionally, the features present within these data are highly dissimilar.
+While natural images may contain common objects which share high-level features such as eyes, faces, or complex geometry, these data only share low-level features with aeromagnetic data, such as simple line and curve components.
+This fact limits the applicability of transfer learning from methods in computer vision machine learning \parencite{tanSurveyDeepTransfer2018} to geoscience data.
+These points also raise the uncertainty of methods developed for natural images to be  applicable to geoscience data.
+
+Geoscience data faces a number of challenges distinct from natural images. These have been outlined in \textcite{karpatneMachineLearningGeosciences2019}, and relevant to this work are:
+
+\begin{itemize}
+    \item{} Spatio-Temporal Structure: Aeromagnetic grids are spatially corellated, neighbouring cells contain similar values arising from the same causative volume.
+    \item{} Multi-Source Multi-Resolution Data: One location may be covered by mutiple aeromagnetic surveys with different resolutions, or the same survey may be presented with different levels of processing.
+    \item{} Poor Quality of Data: Sample data are subject to numerous sources of noise, which combine to become a significant fraction of the gridded data value, or be present as aliased frequencies.
+    \item{} Small Sample Size: While total aeromagnetic coverage in Australia is high, the high-resolution extents are spatially limited and biased by geological domain.
+\end{itemize}
+
+One approach to overcoming the challenges faced in real-world geoscience data is to use synthetic data.
+During this thesis, a large collection of synthetic data became available, containing realistic 3D geological voxel models and 2D geophysical forward models \parencite{jessellNoddyverseMassiveData2022}.
+These data present a large amount of uniformly sampled and noise free grids from an unbiased set of geological domains.
+
+\section{Traditional methods for enhancing resolution}
+As outlined in \Cref{sec:introgeo}, resolution is a product of sample distance and density, and gridded rasters have a specific number of cells in each axis depending on the spatial extent.
+Upsampling raster data to larger height and width dimensions is commonplace, and generally performed by numerical image filters such as the cubic spline \parencite{keysCubicConvolutionInterpolation1981} or Lanczos filter \parencite{lanczos1988applied}.
+Some of these interpolation methods are the basis of the gridding methods previously outlined, and simply selecting a smaller cell size during gridding is sufficient to achieve a larger image raster.
+These filters are adept at imputing the required cell values while preserving the frequency content of the original raster.
+However, no attempt is made at accurately increasing the high-frequency components of the raster, which are required by our definition for high-resolution geophysics.
+Without sampling at a smaller separation or closer line spacing, it is still possible to increase the high-frequency content of aeromagnetic grids.
+
+The rate at which the power of the component frequencies of the potential field diminish with increasing distance is well known.
+Back-calculation can be made to predict the power of these frequencies at a smaller separation, and this is termed downward continuation \textcite{bullardDeterminationMassesNecessary1948,blakelyPotentialTheoryGravity1996}.
+The inverse using a larger distance is termed upward continuation, and is useful for reducing potentially unwanted near-surface magnetic detail, or levelling data to a common datum \parencite[e.g.\ open file magnetic data in Australia is available levelled to AWAGS][]{mintyAirborneGeophysicalMapping2011}.
+Downward continuation offers the benefit of high-resolution data from low-resolution sampling, and is therefore highly studied \parencite{zuoDownwardContinuationTransformation2020,liStableDownwardContinuation2023,fediStableDownwardContinuation2002,yeHighprecisionDownwardContinuation2022,zhangNumericalSolutionsMeanValue2018a,guoPotentialFieldContinuation2020,gangImprovedStableDownward2018,pilkingtonPotentialFieldContinuation2017}.
+However, due to the inclusion of sensor noise, the practicable limit of numerical methods is six times the low-resolution cell size.
+Recent approaches in machine learning that overcome this limit will be discussed in \Cref{sec:introml}, alongside alternative methods for enhancing aeromagnetic survey resolution.
+
+\section{Machine learning for enhancing resolution}
+Representation learning...
+
+\label{sec:introml}
+Deep learning is a field of contemporary machine learning, where additional levels of learning are undertaken between the input and output.
+The current generation of deep learning today began in ernest in 2006 \parencite[as defined by][]{dengDeepLearningMethods2014,Goodfellow-et-al-2016}, and has pervaded many if not all industries and research fields.
+The network architectures encountered in this manuscript include convolutional neural networks (CNN), multilayer perceptrons (MLP), and generative adversarial networks (GAN).
+
+CNN methods have long been well suited for computer vision tasks such as image classification and, more recently, super-resolution.
+In an image raster, neighbouring pixels define simple features, and these features combine in the wider image to define complex features.
+CNNs excel in deep learning tasks for these data, due in part to the structure of the receptive field of the network.
+The receptive field is formed from stacked layers of small convolutional kernels, typically with a size of \numproduct{3 x 3} cells for SR CNNs.
+These low-level kernels learn simple functions, which are convolved with deeper layers to learn increasingly complex filters across a larger image extent, and widening the receptive field.
+A review of deep learning CNN is provided in \textcite{goodfellowDeepLearning2016}.
+% Once trained, the learnt functions are conditioned to transform low-resolution features into high-resolution features, using the neighbouring input values of the low-resolution grid in the context of filters learnt from the training data.
+
+Recently, CNNs have been surpassed by coordinate multilayer perceptron (CMLP) neural networks for the task of SR \parencite{chenLearningContinuousImage2021}.
+CMLP networks learn a signal as a function of its coordinates, and SR is performed by predicting pixel values on the continuum of coordinates in the domain of the learnt function, including at scales that were not seen during training.
+Key to the performance of these networks are implicit functions, which parameterise a function learned from training dataset with a neural network analogue.
+The network analogue can then be queried for information that fits the learnt function but was not included in the training data.
+
+% GANs are an architecture making use of two competing neural networks.
+
+% Introduce different types of networks and their applications in geoscience and adjacent areas
+
+There has been active area of computer vision research in developing various deep learning network architectures (*refs) to enhance the resolution of images (super-resolution) based on previously seen patterns.
+% * talk about different superresolution methods that have been effective for some applications with refs*, and introduce learning implicit representation from imagery and their application for improving resolution *** I think it's useful to link this resolution improvement in geophysics as imputation problem.
+
+%  deep learning methods that consider the characteristics of geophysics potential fields data.
+
+*needs a bit of literature review on what's been done before in this space in geoscience***
+to the best of my knowledge, this use of super-resolution ***
+
+\section{}
+\label{sec:introgeoml}
+
+The earliest application of CNN SR was demonstrated by \parencite{dongLearningDeepConvolutional2014}, where convolutional layers are used for low-resolution patch extraction, feature mapping, and reconstruction of high-resolution images.
+
+The outputs of each convolutional layer are similar to hand-crafted filters or feature dictionaries in earlier example-based super-resolution methods \parencite{freemanExamplebasedSuperresolution2002}, but the learnt filters are more numerous and fully trainable with the deep learning approach.
+Following the success of \parencite{dongLearningDeepConvolutional2014}, many iterative improvements have been made to CNN based SR\@.
+These include SRCNN \parencite{dongImageSuperresolutionUsing2016}, RDN \parencite{zhangResidualDenseNetwork2018}, ESRGAN \parencite{wangESRGANEnhancedSuperresolution2018}, and others \parencite{ledigPhotorealisticSingleImage2017,limEnhancedDeepResidual2017}.
+While each of these works contribute unique features to CNN-based super-resolution, they follow a common stacked block design.
+This comprises a set of initial input feature extraction convolutions, a sequence of convolutional blocks with activations (neurons), some number and arrangement of intermediate residual learning pathways (skip connections), and an upsampling block for feature upscaling and convolving latent features back to image space.
+
+- MLP SR
+% One limitation of these CNN-based networks is the challenge of upscaling data at non-integer scales, and scales beyond those in the training dataset.
+% This was achieved by \parencite{huMetaSRMagnificationarbitraryNetwork2019,wangLearningSingleNetwork2021}, however recent approaches using implicit function based networks have improved performance.
+
+- Deep learning downward continuation
+
+This thesis, explores the applications of
+And the potential field has frequency based details to interpet sources at varying depth, etc...
+how this is directly relevant to implicit neural representation learning....
+This needs to set the scence of what is to come...
+
+\section{Research Aims}
+The overall aim of this thesis is to adapt and extend the use of deep learning to improve the enhancement and processing of geophysics data. The three aims of this thesis are as follows:
+
+\begin{itemize}
+    \item{} how different deep learning based super-resolution methods previously developed for natural imagery are applicable to magnetic potential fields grids that has different in dynamic value range in a single channel.
+
+    \item{}Extending the understanding of effectiveness of a super-resolution technique in terms of resolution scale specifically in relation to survey line spacing; and the model construction framework to ensure the model is trained for diverse types of geological features manifested in magnetic data.
+
+    \item{}Evaluating the use of implicit neural representation technique that performs representation learning of potential field survey point and line data, which can generate a grid directly from survey data by learning *** within data, and their analytical gradient calculation from the network.
+\end{itemize}
+
+The above aims are achieved using case studies using open access aeromagnetic data provided by Geoscience Australia.
+Case studies are critical in promoting the adoption of applications in geophysics, by demonstrating a methods suitability to the data and task of interest.
+Inference on real-world data is generally the aim of machine learning applications, however these data present many challenges \parencite{nikolenkoSyntheticDataDeep2021,tremblayTrainingDeepNetworks2018}.
+Especially in the case of geophysics, these challenges include the paucity of ground truth, high dimensionality, and measurement noise and uncertainty \parencite{karpatneMachineLearningGeosciences2019}.
+
+\section{Research Contributions and Thesis Structure}
+This thesis is presented as a series of papers which are published or in-preparation for publication.
+These are presented in Cref{ch:paper1,ch:paper2,ch:paper3}, each with a brief contextual introduction.
+Key findings and contributions of the research are discussed in Cref{ch:discussion}, followed by overall thesis conclusions in Cref{ch:conclusion}.
+
+Cref{ch:paper1} presents published work on an initial investigation into the technique of deep learning super-resolution for magnetic potential field data.
+To our knowledge, this chapter presents the first investigation of deep learning super-resolution of gridded magnetic potential field data within the literature.
+Two convolutional neural network models namely RDN and ESRGAN from the contemporary literature are implemented \parencite{zhangResidualDenseNetwork2018,limEnhancedDeepResidual2017}.
+With uncertainty on the amount of data required to train a SR model for magnetic grids, a dataset comprising readily available high- and low-resolution TMI grid pairs is formed using published state magnetic compilation maps of Western Australia \parencite{brett20MagneticMerged2020}.
+These data contain magnetic features and textures from a range of geological domains.
+The chapter concludes by observing the success of SR on magnetic features, characterising the performance of the two adapted networks, and recommending the method based on RDN as being more reliable for the SR task.
+The primary contribution of Cref{ch:paper1} is establishing the capacity of the SR networks developed for natural images in computer vision to extend to the distinctly different data of low-resolution aeromagnetic geophysics.
+
+Following the findings of the previous chapter, Cref{ch:paper2} addresses the need for more generalisable model training for super-resolution.
+%TODO refactor per paper 2 intro - primary contrbution is diverse geology with synthetci data. Don't say low-resolution data
+It undertakes these aims by developing a resampling and regridding approach for genreating realistic low-resolutoin grids from real-world high-resolution state magnetic data and synthetic data from the contemporaneously published collection of magnetic grids forward modelled from realistic geology \parencite{jessellNoddyverseMassiveData2022}.
+Furthermore, it adopts advances in the machine learning literature by implementing the LTE network \parencite{leeLocalTextureEstimator2022}.
+The proposed low-resolution transform simulates aeromagnetic line sampling of a potential field extent at \qty{320}{\m} and \qty{80}{\m}, which are in the regional and prospect scale respectively.
+Using the transformed synthetic data, a baseline model is trained on data from over \num{300} distinct geological histories.
+While the baseline model can generalise to real-world data, some incorrect reconstructions remain.
+By fine-tune training the model with transformed real-world state map data, these errors are rectified, and the structural accuracy is improved.
+
+Cref{ch:paper3} reports the use of coordinate multilayer perceptron (CMLP) neural networks to transform line data into a grid that eliminating levelling and gridding
+%TODO ensure refer back to aims
+*** learn a representation of the function that describes a surveyed potential field extent.
+These networks are highly suited for processing spatial data such as point sampled geophysics surveys.
+Using the proposed method, regularly spaced grids are directly predicted from scattered survey point data.
+Additionally, automatic differentiation is performed with the representation to calculate derivatives of a potential field.
+Both tasks are fundamental to interpretation and processing in geophysics, and by commencing the methods from point sample data, the number of individual processing steps is reduced, and the application is fully trainable.
+To our knowledge, this research is the first description of deep learning implicit neural representation for aeromagnetic potential field data in the literature.
+
+Cref{ch:discussion} presents a synthesis discussion for the prior chapters.
+Given the recency of deep learning super-resolution and implicit neural representation, multiple avenues of future opportunities are identified.
+These aim to increase the adoption of super-resolution in geophysics by addressing apprehension toward the reliability of interpretation of the outputs.
+A synthesis comparison of the SR networks adapted in Cref{ch:paper1,ch:paper2} is also presented, which prompts questions regarding model and dataset construction.
+The use of a priori information well understood to geophysics is also discussed, with potential application in both super-resolution and implicit neural representation.
+
+Finally, overall conclusions are presented in Cref{ch:conclusion}.
 

### 2023-10-09 intro.tex
Edits and structure per EJ review

@@
 
-\section{Potential field geophysics in exploration geoscience}
+The subsurface continuation of exposed geology can be extrapolated and interpolated using structures mapped in surveys of the Earth's naturally occuring potential fields.
+Potential field surveys offer low-cost investigations over a large spatial extent, and routinely used for geological mapping and interpretation \parencite{nabighian75thAnniversaryHistorical2005}
+For this reason, magnetic field surveys are commonly used by geophysicists for geological mapping and interpretation toward understanding the Earth in three dimensions.
+Scattered surveys are widely used when interpolated to grid rasters, and interpreted individually or integrated with many other datasets for predicting the subsurface for processes such as numerical modelling and inversion.
+In these tasks, the spatial resolution of the grid is a critical factor in their ability to define geological detail \parencite{islesGeologicalInterpretationAeromagnetic2018}.
+The role of high-resolution details in these geophysical methods is becoming more important to exploration as resources are increasingly sought from below sedimentary cover.
+
+\section{Research Aims}
+The overall aim of this thesis is to adapt and extend the use of deep learning to improve the processing and enhancement and geophysics data. The three aims of this thesis are as follows:
+
+\begin{itemize}
+    \item{} Identifying how deep learning resolution enhancement methods previously developed for natural images are applicable to highly distinct magnetic potential fields data;
+
+    \item{} Constructing a model framework to ensure example based models can be trained incorporating diverse types of geological features manifested in magnetic data, and evaluating the effectiveness the framework with a resolution enhancement technique based on survey line spacing;
+
+    \item{} Evaluating a method for representation learning of potential field survey point data, which can predict a grid directly from point located survey data, as well as grids of the directional derivatives calculated of the learnt function using an automatic differentiation framework.
+\end{itemize}
+
+The above aims are achieved using case studies using open access aeromagnetic data provided by Geoscience Australia.
+Inference on real-world data presents many challenges \parencite{nikolenkoSyntheticDataDeep2021,tremblayTrainingDeepNetworks2018}.
+Despite this, case studies are critical in promoting the adoption of applications in geophysics, by demonstrating a methods suitability to the data used within the task of interest.
+
+\section{Aeromagnetic surveys}
 \label{sec:introgeo}
-%- what are they used for (summary) 
-The subsurface continuation of exposed geology can be extrapolated and interpolated using structures mapped in surveys of the Earth's naturally occuring potential fields.
-Mapping methods using these fields are routinely used in geoscience for low-cost investigations of the subsurface over a large spatial volume.
-For this reason, magnetic field surveys are commonly used by geophysicists for geological mapping and interpretation \parencite{nabighian75thAnniversaryHistorical2005}.
-In addition, potential field data are used as inputs to computer processing tasks such as numerical modelling and inversion.
-In these tasks, various dimensions of geoscience data are integrated to make predictions regarding the subsurface.
-These and other geophysical methods are becoming more important to exploration as resources are increasingly sought from below sedimentary cover.
-
-\subsection{Aeromagnetic surveys}
 % how are they gathered (surveys)
-One of the fundamental methods routinely used for mineral exploration are aerogeophysical surveys of the Earth's magnetic or gravitational potential fields.
-Airborne surveys are acquired at a range of scales at different stages of exploration, from pre-competitive regional data to stimulate exploration \parencite{howardAirborneGeophysicalCoverage2004}, to targeted investigations by the exploration industry at the prospect scale of up to several square kilometres.
-Surveys are also routinely collected on the ground, or less commonly in exploration, by ship or satellite, with most processing methods and interpretation shared between all forms of acquisition.
+Airborne surveys of the Earth's magnetic or gravitational potential fields are routinely acquired at a range of scales at different stages of exploration, from pre-competitive regional data to stimulate exploration \parencite{howardAirborneGeophysicalCoverage2004}, to targeted investigations by the exploration industry at the prospect scale of up to several square kilometres.
+Surveys may also be collected on the ground, or less commonly in exploration, by ship or satellite, with most processing methods and interpretation shared between all forms of acquisition.
 Aeromagnetic surveys are among the lowest cost geophysical method \parencite{dentithGeophysicsMineralExploration2014}, however the cost rapidly increases when surveying at higher resolution due to overheads in flight line sampling.
-When collecting data, aircraft fly straight transect lines at a nominal safe elevation above topography, known as the topography drape.
-Surveys are flown with a nominal heading for the direction that data will be acquired along line.
-For regional surveys this is recommended to be North-South, however early practice was perpendicular to the dominant geological strike, under the expectation of sampling the greatest frequency of change in magnetic intensity \parencite{islesGeologicalInterpretationAeromagnetic2018}.
-Because the power in higher frequencies diminishes with increasing source-sensor distance, the lower the height, the more high-frequency components will be captured by the sensor, a fact which will become important in subsequent sections.
+When acquiring data, aircraft fly straight transect lines at a safe elevation above topography, known as the topography drape.
+Surveys are flown with a heading in which data will be acquired along line.
+For regional and contemporary surveys this is recommended to be North-South, however early practice was to survey perpendicular to the dominant geological strike, under the expectation of sampling the greatest frequency of change in magnetic intensity \parencite{islesGeologicalInterpretationAeromagnetic2018}.
+Higher frequencies with these data diminish with increasing source-sensor distance, therefore the lower the height, the more high-frequency components will be captured by the sensor.
 Acquisition along flight lines is sampled at a rate of \qty{10}{\hertz} or greater, which corresponds to an interval of \qty{7}{\m} or shorter at nominal flight speeds of \qty{70}{\m\per\s} \parencite{goodwinAirborneMagneticRadiometric2023}.
-The spacing between lines is a factor of the scale of investigation and cost, and regional pre-competitive data in Australia targets state-wide coverage at \qty{400}{\m}, which is generally regarded as the upper limit of usefulness to exploration \parencite{howardAirborneGeophysicalCoverage2004}.
+The spacing between lines is a factor of the scale of investigation and the cost of acquisition, and regional pre-competitive data in Australia targets state-wide coverage at \qty{400}{\m}, which is generally regarded as the upper limit of usefulness to exploration \parencite{howardAirborneGeophysicalCoverage2004}.
 These low-resolution surveys, funded by government geoscience agencies, are a key driver in greenfields exploration and are released as open file data.
@@
 \subsection{Survey data regularisation}
+\label{sec:introgrids}
 % - how are they transformed (gridding)
@@
 Grids are raster data, where each pixel stores a scalar measurement of a specific property.
-In geophysics and throughout this manuscript, these are referred to as cells, and the property is a measure of the strength of the magnetic field at a specific location.
+In geophysics and throughout this thesis, these are referred to as cells, and the property is a measure of the strength of the magnetic field at a specific location.
 The field strength measured is the Total Magnetic Intensity (TMI), which is the vector sum of each directional vector of the potential \parencite{blakelyPotentialTheoryGravity1996}.
@@
 The location recorded at a sample point is the geographic latitude and longitude, and altitude, acquired with high-precision differential GPS, alongside radar altimeter elevation.
-These data may be transformed to a flat projected system, where spatial dimensions are expressed in meters, used throughout this manuscript.
-There are numerous well-established gridding methods, and novel methods are frequently proposed in the literature.
-The simplest is known as nearest neighbour interpolation, where each node is set to equal to the closest sample value.
+These data may be transformed to a flat projected system, where spatial dimensions are expressed in meters, used throughout this thesis.
+There are numerous conventional gridding methods, and novel methods are frequently proposed in the literature.
+The simplest use surrounding samples for interpolation, such as choosing the closest sample value or applying a transformation function to the neighbouring samples.
 Of those most commonly used in potential field geophysics, these are minimum curvature \parencite{briggsMachineContouringUsing1974}, splines \parencite{bhattacharyyaBicubicSplineInterpolation1969,shureHarmonicSplinesGeomagnetic1982,smithGriddingContinuousCurvature1990}, and equivalent sources \parencite{dampneyEquivalentSourceTechnique1969, solerBetterStrategyInterpolating2020}.
 Splines are used in bi-directional gridding, which is well-suited for aeromagnetic surveys, where the sample data are first interpolated in the line parallel direction, and the intermediate product is interpolated in the line perpendicular direction \parencite{dentithGeophysicsMineralExploration2014}.
-In other areas of geoscience, a statistical interpolator is frequently used, known as kriging \parencite{hansenInterpretiveGriddingAnisotropic1993,davis1986statistics}.
+A method known as kriging is used in other areas of geoscience, such as geochemical mapping, and is an interpolator which makes use of statistical properties of the known distribution \parencite{hansenInterpretiveGriddingAnisotropic1993,davis1986statistics}.
 Some recently proposed gridding methods include the methods of \textcite{naprstekNewMethodInterpolating2019}, \textcite{xuGravityAnomalyReconstruction2019}, or \textcite{chenPotentialFieldData2022}.
 Each interpolation method attempts to predict regularly spaced grids by leveraging properties intrinsic to the data, with the possible explicit integration of \emph{a priori} knowledge such as geophysical laws or geological context.
-A review of spatial interpolation methods is provided in \textcite{liReviewComparativeStudies2011}
+A review of spatial interpolation methods is provided in \textcite{liReviewComparativeStudies2011}.
 
 \subsection{A definition for geophysical resolution}
-In all interpolated grids, the spatial dimension of each cell is referred to as the cell size, with the unit of metre used in this manuscript.
-As stated above, resolvable detail in geophysical surveys is a product of the distance between the causative magnetic body and sensor (height), and the line spacing \parencite{islesRelationshipsGeologicalResolution1992,islesGeologicalInterpretationAeromagnetic2018,dentithGeophysicsMineralExploration2014}.
+In all interpolated grids, the spatial dimension of each cell is referred to as the cell size, with the unit of metre used in this thesis.
+As previously stated, resolvable detail in geophysical surveys is a product of the distance between the causative magnetic body and sensor (height), and the line spacing \parencite{islesRelationshipsGeologicalResolution1992,islesGeologicalInterpretationAeromagnetic2018,dentithGeophysicsMineralExploration2014}.
 Height is easily controlled by flying the lowest safe and sufficiently smooth topography drape, and along-line sampling is performed at a constant high rate, so the key factor controlling resolution in aeromagnetic survey design is the line spacing.
@@
 Depending on the complexity of the geological domain, this may cause spatial aliasing in one direction.
-This is visible in grids where features take on a blocky or stepped appearance, referred to as a beading artefact, or generally in this manuscript as a low-resolution artefact.
-Low-resolution gridded aeromagnetic data refers to surveys with a wide line spacing causing a lack of high-frequency details in the line-perpendicular direction, resulting in potential artefacts or missing features in grid data.
+This is visible in grids where features take on a blocky or stepped appearance, referred to as a beading artefact, or generally in this thesis as a low-resolution artefact.
+Low-resolution gridded aeromagnetic data refers to surveys with a wide line spacing causing a lack of high-frequency details in the line-perpendicular direction, resulting in potential artefacts, and overly smooth or missing details in grid data.
 
-Here, we arrive at the definition of resolution adopted throughout this thesis.
+Here, I state the definition of resolution adopted throughout this thesis.
 
-\emph{Resolution in potential field geophysics refers to the sampling of high-frequencies present in the potential field caused by a geological source.
-    Resolution is further defined by the preservation of these frequencies in gridded potential field data.}
+\bigskip{}
+\noindent{}\emph{Resolution in potential field geophysics refers to the level of geological detail in potential field grids.}
+\bigskip{}
+
+This can be increased by:
+\begin{enumerate}
+    \item{} High frequencies, caused by geology, being present in the potential field,
+    \item{} Capturing these high frequencies during surveying, by sampling at close line spacing and small source-sensor separation,
+    \item{} Interpolating sample data with a small enough spatial cell size to preserve these frequencies.
+\end{enumerate}
 
@@
 
-Resulting from the processes described in \Cref{sec:introgeo}, geophysical rasters are highly distinct from the image data used widely in computer vision.
+Resulting from the processes described in \Cref{sec:introgrids}, geophysical rasters are highly distinct from the image data used widely in computer vision.
 This includes the number of channels (3 in natural images, 1 in aeromagnetics), range (255 compared to 50,000 or more), and anisotropy of resolution.
@@
 \section{Traditional methods for enhancing resolution}
-As outlined in \Cref{sec:introgeo}, resolution is a product of sample distance and density, and gridded rasters have a specific number of cells in each axis depending on the spatial extent.
+As outlined in \Cref{sec:introgrids}, resolution is a product of sample distance and density, and gridded rasters have a specific number of cells in each axis depending on the spatial extent.
 Upsampling raster data to larger height and width dimensions is commonplace, and generally performed by numerical image filters such as the cubic spline \parencite{keysCubicConvolutionInterpolation1981} or Lanczos filter \parencite{lanczos1988applied}.
@@
 \section{Machine learning for enhancing resolution}
-Representation learning...
+% Representation learning...
 
 \label{sec:introml}
-Deep learning is a field of contemporary machine learning, where additional levels of learning are undertaken between the input and output.
-The current generation of deep learning today began in ernest in 2006 \parencite[as defined by][]{dengDeepLearningMethods2014,Goodfellow-et-al-2016}, and has pervaded many if not all industries and research fields.
-The network architectures encountered in this manuscript include convolutional neural networks (CNN), multilayer perceptrons (MLP), and generative adversarial networks (GAN).
+Deep learning is a field of contemporary machine learning, where multiple stages of features learning are undertaken between the input and output.
+The current generation of deep learning is reported to have begun in 2006 \parencite{dengDeepLearningMethods2014,Goodfellow-et-al-2016}, and has pervaded many industries and research fields.
+The network architectures encountered in this thesis include convolutional neural networks (CNN), multilayer perceptrons (MLP), and generative adversarial networks (GAN).
 
@@
 CNNs excel in deep learning tasks for these data, due in part to the structure of the receptive field of the network.
-The receptive field is formed from stacked layers of small convolutional kernels, typically with a size of \numproduct{3 x 3} cells for SR CNNs.
-These low-level kernels learn simple functions, which are convolved with deeper layers to learn increasingly complex filters across a larger image extent, and widening the receptive field.
+The receptive field is formed from stacked layers of small convolutional kernels, typically with a size of \numproduct{3 x 3} cells for super-resolution CNNs.
+These low-level kernels learn simple functions, which are convolved with deeper layers to learn increasingly complex patterns across a larger image extent, while widening the receptive field.
 A review of deep learning CNN is provided in \textcite{goodfellowDeepLearning2016}.
@@
 
-Recently, CNNs have been surpassed by coordinate multilayer perceptron (CMLP) neural networks for the task of SR \parencite{chenLearningContinuousImage2021}.
-CMLP networks learn a signal as a function of its coordinates, and SR is performed by predicting pixel values on the continuum of coordinates in the domain of the learnt function, including at scales that were not seen during training.
+Recently, CNNs have been surpassed by coordinate multilayer perceptron (CMLP) neural networks in some representation learning tasks \parencite[e.g.][]{chenLearningContinuousImage2021}.
 Key to the performance of these networks are implicit functions, which parameterise a function learned from training dataset with a neural network analogue.
 The network analogue can then be queried for information that fits the learnt function but was not included in the training data.
+In this way, CMLP networks learn a signal as a function of its coordinates, and novel signal values can be predicted for coordinates in the continuous domain of the learnt function.
 
-% GANs are an architecture making use of two competing neural networks.
-
-% Introduce different types of networks and their applications in geoscience and adjacent areas
-
-There has been active area of computer vision research in developing various deep learning network architectures (*refs) to enhance the resolution of images (super-resolution) based on previously seen patterns.
-% * talk about different superresolution methods that have been effective for some applications with refs*, and introduce learning implicit representation from imagery and their application for improving resolution *** I think it's useful to link this resolution improvement in geophysics as imputation problem.
-
+% \begin{itemize}
+%     \item GAN    
+%           %  are an architecture making use of two competing neural networks.
+%           % Highly suited for generative modelling, 
+%     \item Introduce different types of networks and their applications in geoscience and adjacent areas
+%           There has been active area of computer vision research in developing various deep learning network architectures (*refs) to enhance the resolution of images (super-resolution) based on previously seen patterns.
+%           These are described in \Cref{sec:introgeoml}
+%     \item * talk about different superresolution methods that have been effective for some applications with refs*, and introduce learning implicit representation from imagery and their application for improving resolution *** I think it's useful to link this resolution improvement in geophysics as imputation problem.
 %           deep learning methods that consider the characteristics of geophysics potential fields data.
-
-*needs a bit of literature review on what's been done before in this space in geoscience***
-to the best of my knowledge, this use of super-resolution ***
+%     \item revisit or move Deep learning downward continuation
+%     \item *needs a bit of literature review on what's been done before in this space in geoscience***
+%     \item to the best of my knowledge, this use of super-resolution ***
+% \end{itemize}
 
@@
 \label{sec:introgeoml}
-
 The earliest application of CNN SR was demonstrated by \parencite{dongLearningDeepConvolutional2014}, where convolutional layers are used for low-resolution patch extraction, feature mapping, and reconstruction of high-resolution images.
-
 The outputs of each convolutional layer are similar to hand-crafted filters or feature dictionaries in earlier example-based super-resolution methods \parencite{freemanExamplebasedSuperresolution2002}, but the learnt filters are more numerous and fully trainable with the deep learning approach.
@@
 This comprises a set of initial input feature extraction convolutions, a sequence of convolutional blocks with activations (neurons), some number and arrangement of intermediate residual learning pathways (skip connections), and an upsampling block for feature upscaling and convolving latent features back to image space.
-
-- MLP SR
 % One limitation of these CNN-based networks is the challenge of upscaling data at non-integer scales, and scales beyond those in the training dataset.
@@
 
-- Deep learning downward continuation
-
-This thesis, explores the applications of
-And the potential field has frequency based details to interpet sources at varying depth, etc...
-how this is directly relevant to implicit neural representation learning....
-This needs to set the scence of what is to come...
-
-\section{Research Aims}
-The overall aim of this thesis is to adapt and extend the use of deep learning to improve the enhancement and processing of geophysics data. The three aims of this thesis are as follows:
-
 \begin{itemize}
-    \item{} how different deep learning based super-resolution methods previously developed for natural imagery are applicable to magnetic potential fields grids that has different in dynamic value range in a single channel.
-
-    \item{}Extending the understanding of effectiveness of a super-resolution technique in terms of resolution scale specifically in relation to survey line spacing; and the model construction framework to ensure the model is trained for diverse types of geological features manifested in magnetic data.
-
-    \item{}Evaluating the use of implicit neural representation technique that performs representation learning of potential field survey point and line data, which can generate a grid directly from survey data by learning *** within data, and their analytical gradient calculation from the network.
+    \item This thesis, explores the applications of
+    \item And the potential field has frequency based details to interpet sources at varying depth, etc...
+    \item how this is directly relevant to implicit neural representation learning....
+    \item This needs to set the scence of what is to come...
 \end{itemize}
-
-The above aims are achieved using case studies using open access aeromagnetic data provided by Geoscience Australia.
-Case studies are critical in promoting the adoption of applications in geophysics, by demonstrating a methods suitability to the data and task of interest.
-Inference on real-world data is generally the aim of machine learning applications, however these data present many challenges \parencite{nikolenkoSyntheticDataDeep2021,tremblayTrainingDeepNetworks2018}.
-Especially in the case of geophysics, these challenges include the paucity of ground truth, high dimensionality, and measurement noise and uncertainty \parencite{karpatneMachineLearningGeosciences2019}.
 
@@
 
-Following the findings of the previous chapter, Cref{ch:paper2} addresses the need for more generalisable model training for super-resolution.
-%TODO refactor per paper 2 intro - primary contrbution is diverse geology with synthetci data. Don't say low-resolution data
-It undertakes these aims by developing a resampling and regridding approach for genreating realistic low-resolutoin grids from real-world high-resolution state magnetic data and synthetic data from the contemporaneously published collection of magnetic grids forward modelled from realistic geology \parencite{jessellNoddyverseMassiveData2022}.
+Following the findings of the previous chapter, Cref{ch:paper2} addresses the need for more generalisable model training for real-world super-resolution.
+It undertakes these aims by training a baseline synthetic model with data from a contemporaneously published collection of magnetic grids forward modelled from realistic geology \parencite{jessellNoddyverseMassiveData2022}, on data from over \num{300} distinct geological histories.
+It subsequently fine-tune trains the baseline model on real-world high-resolution state magnetic data.
 Furthermore, it adopts advances in the machine learning literature by implementing the LTE network \parencite{leeLocalTextureEstimator2022}.
-The proposed low-resolution transform simulates aeromagnetic line sampling of a potential field extent at \qty{320}{\m} and \qty{80}{\m}, which are in the regional and prospect scale respectively.
-Using the transformed synthetic data, a baseline model is trained on data from over \num{300} distinct geological histories.
+The proposed method simulates aeromagnetic line sampling of a potential field extent at \qty{320}{\m} and \qty{80}{\m}, which are in the regional and prospect scale respectively.
 While the baseline model can generalise to real-world data, some incorrect reconstructions remain.
@@
 
-Cref{ch:paper3} reports the use of coordinate multilayer perceptron (CMLP) neural networks to transform line data into a grid that eliminating levelling and gridding
+Cref{ch:paper3} reports the use of coordinate multilayer perceptron (CMLP) neural networks for representation learning of a surveyed potential field extent.
+With the proposed method, scattered line data can be encoded into the grid, and cells queried at interpolating coordinates to predict regularised grids.
+CMLP networks are highly suited for processing spatial data such as point sampled geophysics surveys.
+Additionally, spatial derivatives are calculated on the learnt function directly.
 %TODO ensure refer back to aims
-*** learn a representation of the function that describes a surveyed potential field extent.
-These networks are highly suited for processing spatial data such as point sampled geophysics surveys.
-Using the proposed method, regularly spaced grids are directly predicted from scattered survey point data.
-Additionally, automatic differentiation is performed with the representation to calculate derivatives of a potential field.
 Both tasks are fundamental to interpretation and processing in geophysics, and by commencing the methods from point sample data, the number of individual processing steps is reduced, and the application is fully trainable.

### 2023-10-09 intro.tex
Write ML background

@@
 \setcounter{chapter}{1}
-
-% indicates that an original and coherent argument is being developed and that the research is making a contribution to existing literature
-% outline the topic, justify the research, identify research aims and outline thesis structure
 
@@
 The role of high-resolution details in these geophysical methods is becoming more important to exploration as resources are increasingly sought from below sedimentary cover.
+Resolution enhancement has seen recent success from the use of deep learning \parencite{moserHitchhikerGuideSuperResolution2023}, however it is not understood if these methods could extend to geophysics data, which are highly distinct from natural images.
 
@@
 
-The above aims are achieved using case studies using open access aeromagnetic data provided by Geoscience Australia.
-Inference on real-world data presents many challenges \parencite{nikolenkoSyntheticDataDeep2021,tremblayTrainingDeepNetworks2018}.
-Despite this, case studies are critical in promoting the adoption of applications in geophysics, by demonstrating a methods suitability to the data used within the task of interest.
+The above aims are achieved using case studies with open access aeromagnetic data provided by Geoscience Australia.
 
@@
 \label{sec:introgeo}
-% how are they gathered (surveys)
 Airborne surveys of the Earth's magnetic or gravitational potential fields are routinely acquired at a range of scales at different stages of exploration, from pre-competitive regional data to stimulate exploration \parencite{howardAirborneGeophysicalCoverage2004}, to targeted investigations by the exploration industry at the prospect scale of up to several square kilometres.
@@
 \label{sec:introgrids}
-% - how are they transformed (gridding)
 Survey data can be interpreted as one dimensional transects, but more commonly they are regularised to a two-dimensional grid raster for interpretation in a process termed gridding.
@@
 The field strength measured is the Total Magnetic Intensity (TMI), which is the vector sum of each directional vector of the potential \parencite{blakelyPotentialTheoryGravity1996}.
-This scalar value is recorded in nanoTesla and may be negative with an unbounded range that can exceed \qty{50,000}{\nano\tesla} in the Earth's environment.
+This scalar value is recorded in nanotesla and may be negative with an unbounded range that can exceed \qty{50,000}{\nano\tesla} in the Earth's environment.
 The location recorded at a sample point is the geographic latitude and longitude, and altitude, acquired with high-precision differential GPS, alongside radar altimeter elevation.
@@
 Splines are used in bi-directional gridding, which is well-suited for aeromagnetic surveys, where the sample data are first interpolated in the line parallel direction, and the intermediate product is interpolated in the line perpendicular direction \parencite{dentithGeophysicsMineralExploration2014}.
-A method known as kriging is used in other areas of geoscience, such as geochemical mapping, and is an interpolator which makes use of statistical properties of the known distribution \parencite{hansenInterpretiveGriddingAnisotropic1993,davis1986statistics}.
+A method known as kriging is used in other areas of geoscience, such as geochemical mapping, and makes use of statistical properties of the known distribution \parencite{hansenInterpretiveGriddingAnisotropic1993,davis1986statistics}.
 Some recently proposed gridding methods include the methods of \textcite{naprstekNewMethodInterpolating2019}, \textcite{xuGravityAnomalyReconstruction2019}, or \textcite{chenPotentialFieldData2022}.
@@
 \subsection{A definition for geophysical resolution}
-In all interpolated grids, the spatial dimension of each cell is referred to as the cell size, with the unit of metre used in this thesis.
+In interpolated grids the spatial dimension of each cell is referred to as the cell size, with a unit of metre used in this thesis.
 As previously stated, resolvable detail in geophysical surveys is a product of the distance between the causative magnetic body and sensor (height), and the line spacing \parencite{islesRelationshipsGeologicalResolution1992,islesGeologicalInterpretationAeromagnetic2018,dentithGeophysicsMineralExploration2014}.
@@
 
-This can be increased by:
+Resolution can be increased by:
 \begin{enumerate}
@@
 % geological interpretation
-% modellin
+% modelling
 %
@@
 Geoscience data faces a number of challenges distinct from natural images. These have been outlined in \textcite{karpatneMachineLearningGeosciences2019}, and relevant to this work are:
-
 \begin{itemize}
@@
 
-One approach to overcoming the challenges faced in real-world geoscience data is to use synthetic data.
-During this thesis, a large collection of synthetic data became available, containing realistic 3D geological voxel models and 2D geophysical forward models \parencite{jessellNoddyverseMassiveData2022}.
-These data present a large amount of uniformly sampled and noise free grids from an unbiased set of geological domains.
+Inference on real-world data presents many challenges \parencite{nikolenkoSyntheticDataDeep2021,tremblayTrainingDeepNetworks2018}.
+Despite this, case studies are critical in promoting the adoption of applications in geophysics, by demonstrating a methods suitability to the data used within the task of interest.
+As such, case studies are investigated for each aim within this thesis.
 
@@
 Back-calculation can be made to predict the power of these frequencies at a smaller separation, and this is termed downward continuation \textcite{bullardDeterminationMassesNecessary1948,blakelyPotentialTheoryGravity1996}.
-The inverse using a larger distance is termed upward continuation, and is useful for reducing potentially unwanted near-surface magnetic detail, or levelling data to a common datum \parencite[e.g.\ open file magnetic data in Australia is available levelled to AWAGS][]{mintyAirborneGeophysicalMapping2011}.
-Downward continuation offers the benefit of high-resolution data from low-resolution sampling, and is therefore highly studied \parencite{zuoDownwardContinuationTransformation2020,liStableDownwardContinuation2023,fediStableDownwardContinuation2002,yeHighprecisionDownwardContinuation2022,zhangNumericalSolutionsMeanValue2018a,guoPotentialFieldContinuation2020,gangImprovedStableDownward2018,pilkingtonPotentialFieldContinuation2017}.
+The inverse using a larger distance is termed upward continuation, and is useful for reducing potentially unwanted near-surface magnetic detail, or levelling data to a common datum \parencite[e.g.\ open file magnetic data in Australia is available levelled to the AWAGS datum][]{mintyAirborneGeophysicalMapping2011}.
+Downward continuation offers the benefit of high-resolution data from low-resolution sampling, and is therefore highly studied \parencite{zuoDownwardContinuationTransformation2020,liStableDownwardContinuation2023,fediStableDownwardContinuation2002,yeHighprecisionDownwardContinuation2022,zhangNumericalSolutionsMeanValue2018,guoPotentialFieldContinuation2020,gangImprovedStableDownward2018,pilkingtonPotentialFieldContinuation2017}.
 However, due to the inclusion of sensor noise, the practicable limit of numerical methods is six times the low-resolution cell size.
-Recent approaches in machine learning that overcome this limit will be discussed in \Cref{sec:introml}, alongside alternative methods for enhancing aeromagnetic survey resolution.
+Recent approaches in machine learning have overcome this limit, alongside alternative methods for enhancing aeromagnetic survey resolution.
 
-\section{Machine learning for enhancing resolution}
-% Representation learning...
+\subsection{Deep learning context}
+\label{sec:introml}
+Machine learning (ML) is a very broad family of techniques for learning functions from data.
+Artificial neural networks are a subset of techniques in ML, inspired by a model of the biological neuron \parencite{bishopNeuralNetworksPattern1995}.
+It has been established that if sufficient conditions are met, neural networks can approximate any function \parencite{hornikMultilayerFeedforwardNetworks1989}.
+A mathematical model of a neuron forms the basis of these networks, and the number of neurons within the network and their arrangement are one primary descriptor of a neural network. 
+Neurons are paremeterised by a multiplicative weight term, an added bias term, and an activation function to scale the result.
+Each neuron applies these operations to the input, which may either be the input data, or the output of earlier neurons.
+The objective of training a neural network is to set the values for these for each neuron in the network, such that the trained network (or model) generalises to novel data.
+This is performed by back propogation \parencite{rumelhartLearningRepresentationsBackpropagating1988}, a technique to navigate toward the lowest error solution by calculating the rate of improvement resulting from parameter updates.
+A practical introduction to the practice of training machine learning is available from \textcite{stevensDeepLearningPyTorch2020}, while a more formal introduction is provided in \textcite{bishopPatternRecognitionMachine2006}.
+Many activation functions have been proposed, with the rectified linear unit (ReLU) being used in most tasks throughout this thesis.
+The activation function performs scaling but in many classes of activation function it also performs the important task of scaling the result to zero, which can be interpreted as the lack of a specific feature being present \parencite{williamsLogicActivationFunctions1986}.
+However, recent work on periodic activation functions such as the sinusoid \parencite{sitzmann2019siren} enable the networks used in Cref{ch:paper3}.
+The other primary descriptor of a neural network is its architecture, refering to the configuration of its intermediate layers between the input and output.
+These architectures are described below.
 
-\label{sec:introml}
-Deep learning is a field of contemporary machine learning, where multiple stages of features learning are undertaken between the input and output.
-The current generation of deep learning is reported to have begun in 2006 \parencite{dengDeepLearningMethods2014,Goodfellow-et-al-2016}, and has pervaded many industries and research fields.
-The network architectures encountered in this thesis include convolutional neural networks (CNN), multilayer perceptrons (MLP), and generative adversarial networks (GAN).
+If the network architecture provides the capacity to store and retrieve learning, the data and training architecture provide the actual instruction and delivery.
+There are broadly two classes of training; supervised and unsupervised learning. 
+The super-resolution and representation learning tasks in this thesis are both supervised tasks, where a reference is provided for the network to calculate an objective function of its performance on.
+Unsupervised learning does not have a ground truth or target, and instead learns to identify patterns within the data for tasks in clustering, density estimation, and visualisation \parencite{bishopPatternRecognitionMachine2006}.
 
-CNN methods have long been well suited for computer vision tasks such as image classification and, more recently, super-resolution.
+Deep learning is a field of contemporary machine learning, where multiple layers of feature learning are undertaken between the input to a method and the output.
+The current generation of deep learning is reported in review articles to have begun in 2006 \parencite{dengDeepLearningMethods2014,goodfellowDeepLearning2016a}, and has pervaded many industries and research fields.
+These review articles contain thorough background on the implementation and practice of various architectures for undertaking deep learing, as well as earlier machine learning or numerical models that can address tasks now approached with deep learning.
+The deep learning tasks explored in this thesis are super-resolution (SR) for the objective of upsampling resolution enhancement, and implicit neural representation (INR).
+The network architectures implemented in this thesis to address the tasks include convolutional neural networks (CNN), generative adversarial networks (GAN), and multilayer perceptrons (MLP).
+A brief introduction to these topics is provided here.
+
 In an image raster, neighbouring pixels define simple features, and these features combine in the wider image to define complex features.
-CNNs excel in deep learning tasks for these data, due in part to the structure of the receptive field of the network.
-The receptive field is formed from stacked layers of small convolutional kernels, typically with a size of \numproduct{3 x 3} cells for super-resolution CNNs.
-These low-level kernels learn simple functions, which are convolved with deeper layers to learn increasingly complex patterns across a larger image extent, while widening the receptive field.
-A review of deep learning CNN is provided in \textcite{goodfellowDeepLearning2016}.
+A CNN is formed from stacked layers of small convolutional kernels, commonly in SR with the kernel size of \numproduct{3 x 3} cells.
+While training, these low-level kernels learn simple functions, which are convolved with deeper layers to learn increasingly complex patterns across a larger image extent, while widening the receptive field.
+CNN methods have long been well suited for raster data in computer vision tasks such as image classification \parencite[e.g.][]{simonyanVeryDeepConvolutional2015} and, more recently, resolution enhancement \parencite[e.g.][]{zhangResidualDenseNetwork2018}.
+The earliest application of CNN to SR was demonstrated by \textcite{dongLearningDeepConvolutional2014}, where convolutional layers throughout the depth of a network are used for low-resolution patch extraction, feature mapping, and reconstruction of super-resolved images.
+The outputs of each convolutional layer are similar to hand-crafted filters or the feature dictionaries in earlier example-based super-resolution methods \parencite{freemanExamplebasedSuperresolution2002}, but the learnt filters are more numerous and fully learned from the data with the deep learning approach.
+Following the success of \parencite{dongLearningDeepConvolutional2014}, many iterative improvements have been made to CNN based SR\@.
+These include SRCNN \parencite{dongImageSuperresolutionUsing2016}, RDN \parencite{zhangResidualDenseNetwork2018}, ESRGAN \parencite{wangESRGANEnhancedSuperresolution2018}, and others \parencite{ledigPhotorealisticSingleImage2017,limEnhancedDeepResidual2017}.
+% While each of these works contribute unique features to CNN-based super-resolution, they follow a common stacked layer design.
+% This comprises a set of initial input feature extraction convolutions, a sequence of convolutional blocks with activations (neurons), some number and arrangement of intermediate residual learning pathways (skip connections), and an upsampling block for feature upscaling and convolving latent features back to image space.
 % Once trained, the learnt functions are conditioned to transform low-resolution features into high-resolution features, using the neighbouring input values of the low-resolution grid in the context of filters learnt from the training data.
@@
 
-% \begin{itemize}
-%     \item GAN    
-%           %  are an architecture making use of two competing neural networks.
-%           % Highly suited for generative modelling, 
-%     \item Introduce different types of networks and their applications in geoscience and adjacent areas
-%           There has been active area of computer vision research in developing various deep learning network architectures (*refs) to enhance the resolution of images (super-resolution) based on previously seen patterns.
-%           These are described in \Cref{sec:introgeoml}
+Generative Adversarial Networks \parencite{goodfellowGenerativeAdversarialNets2014} are a learning framework utilising two competing neural networks.
+These are termed the generator and the discriminator, and can be any arbitrary networks linked by objective functions.
+When best overall performance arises when each network is equally capable in its respective task, i.e.\ when the objective functions of each network are linked by the Nash equilibrium \parencite{salimansImprovedTechniquesTraining2016,lucicAreGANsCreated2018}.
+Because the use of a discriminator allows an independent element for predictive capacity, GANs are highly suited for generative modelling, which includes the task of super-resolution.
+However, it was considerably challenging to achieve a stable Nash equilibrium \parencite{salimansImprovedTechniquesTraining2016}, causing difficulty in training these networks, and to produce a diverse range of outputs.
+Noise injection was later used in this framework as a method to drive diversity \parencite{karrasStylebasedGeneratorArchitecture2018,rakotonirinaESRGANFurtherImproving2020}.
+
 %     \item * talk about different superresolution methods that have been effective for some applications with refs*, and introduce learning implicit representation from imagery and their application for improving resolution *** I think it's useful to link this resolution improvement in geophysics as imputation problem.
-%           deep learning methods that consider the characteristics of geophysics potential fields data.
-%     \item revisit or move Deep learning downward continuation
+
+\section{Machine learning in geoscience}
+\label{sec:introgeoml}
 %     \item *needs a bit of literature review on what's been done before in this space in geoscience***
@@
 
+\printbibliography{}
+
 \end{document}

### 2023-10-09 discussion.tex
Update discussion and future work per EJ review.

@@
 
-\section{Summary}
-This thesis presented contemporary methods in deep learning to address the need for modern data driven applications in geoscience.
+\section{Future work}
+\label{sec:futurework}
+The outputs of machine learning models are regarded with apprehension in geophysics practice due to the perceived “black box” of these methods \parencite{delaatAlgorithmicDecisionMakingBased2018,rudinStopExplainingBlack2019}, and the impact these models may have on subsequent interpretation.
+As widely accepted by the geoscience community, all models are wrong, but some models are useful, and this extends to machine learning models.
+
+When a domain expert encounters low-resolution grid data, they may observe which gridding method was used, the line spacing and direction, and form their understanding of potential aliasing and spurious anomalies in the grid accordingly.
+Assisted by this understanding, they can infer geological features with varying degrees of confidence.
+The SR method however does not consider these constraints, because imputation is purely based on features extractable by the model.
+This was demonstrated to introduce noise or artefacts during SR inference, as well as the incorrect enhancement of artifacts in low-resolution data such as aliased geological strike.
+However, given the uncertainty of geological interpretation of geophysics data \parencite{sivarajahIdentifyingEffectiveInterpretation2013} SR outputs may be used as an auxiliary data when interpreting low-resolution magnetic features.
+The domain expert can then use the SR grid to reassure or reassess the original low-resolution grid interpretation and improve their confidence accordingly.
+
+Super-resolution for geophysics is still in its infancy and requires further efforts towards improving reliability before wide-spread adoption in practice.
+This section proposes four avenues for future research:
+\begin{enumerate}
+    \item{} Exploring the outcomes from the use of SR in the task of geological mapping
+    \item{} Understanding the impact of choices in constructing a model and dataset for SR geophysics for a range of geological domains,
+    \item{} Identifying an improved image quality assessment for gridded potential field data.
+    \item{} Investigating the use of a physics informed approach for SR and implicit representation, and,
+\end{enumerate}
+
+\subsection{SR impact on interpretation}
+The super-resolution outputs from the methods presented in this thesis have improved structural accuracy over the low-resolution grids.
+This is likely to have a positive impact on the detection of features such as lineaments and unit boundaries for geological interpretation from magnetic data.
+However, despite the reduction of introduced structural inaccuracies with the use of open access training data in Cref{ch:paper2}, it is likely that some features with specific structural geometries will still be incorrectly super-resolved.
+A domain expert may be able to recognise structures that are inconsistent using auxiliary information and the regional geological context, but machine processed super-resolution grids will use these data as provided.
+In order to improve the adoption of SR for geological interpretation from potential field data, a rigorous study of the impact of SR on interpretation outcomes is required.
+This could be a geological mapping task, such as the reinterpretation of regional geology using super-resolution upscaled regional magnetic TMI grids.
+Comparison could then be made for the accuracy and benefit of a super-resolution method compared to the existing low-resolution interpretation.
+However, such analysis will be difficult to perform with respect to different interpreters' variability in pattern recognition, especially in the context of their confidence in the reliability of the super-resolution product.
+Previously, \textcite{sivarajahIdentifyingEffectiveInterpretation2013} reported significant variability between individuals when detecting geological targets from magnetic geophysics data.
+A more reliable, repeatable and quantifiable approach would use automated pattern recognition methods developed for geophysical features.
+For example, the automated lineament detection technique of \textcite{holdenAutomaticIdentificationResponses2011,holdenAutomatedAnalysisRegional2008} could be applied to low-resolution and SR grids, to compare their delineated features.
+
+\subsection{SR model construction}
+Several models were implemented throughout cref{ch:paper1, ch:paper2}, namely RDN, ESRGAN, and LTE\@.
+% However, the most important choice in developing a performant super-resolution neural network for real-world aeromagnetic survey data was the choice of training data.
+Cref{paper1} was prepared prior the release of a large and varied synthetic geology training dataset \parencite{jessellNoddyverseMassiveData2022}.
+It was seen in cref{paper2} that this data improved model performance for a range of features by using transfer learning for pre-training.
+% This transfer learning approach for training data is also found to be useful for RDN and ESRGAN\@.
+Here, the use of synthetic and real-world line spacing sampled data approach used with LTE in cref{ch:paper2} are adopted for the RDN and ESRGAN models.
+Cref{fig:modcomp} shows RDN and ESRGAN in predicting accurate features when upscaling \qty{320}{\m} data to \qty{80}{\m} line spacing.
+It can be inferred that the challenge of super-resolution for these tasks is predominantly a question of providing suitable and sufficient training data, and is less constrained to neural network choices.
+
+\begin{figure}
+    \includegraphics[width=\linewidth]{fig/etc/TMI Comparison_23.pdf} % TODO Update for RDN, ESRGAN, LTE, ~3 hours ea.
+
+    \caption{A comparison between all deep learning super-resolution methods presented in cref{paper1} and cref{paper2}, using the realistic low-resolution transform developed in cref{paper2}.
+The low-resolution input is presented in the top left, the high-resolution target in the top right.
+From left to right in the lower row; The RDN+ Network, the ESRGAN+ network, and the LTE network.}
+    \label{modcomp}
+\end{figure}
+
+Given the similar performance between the three distinct architectures, instead of investigating novel SR networks for geophysics super-resolution, an important future work would be understanding the data dependencies of a successful model.
+For example, filtering the synthetic dataset by event history label to prepare bespoke models for specific geological domains to improve performance at the cost of generalisation.
+
+Magnetic data in different geological contexts are subject to a mixture of statistical distributions, \parencite{khokhlovCauseNonGaussianDistribution2017}.
+Investigation is also required to identify a robust normalisation method accounting for dynamic range and the structural significance contained in the long tails of the distributions of magnetic intensities.
+
+\subsection{Image quality assessment for potential field grids}
+Model performance is quantified using image quality assessments (IQA) such as peak signal-to-noise ratio (PSNR), structural similarity index (SSIM), feature similarity index (FSIM), or many others.
+For supervised tasks, a full reference metric can be calculated between the super-resolution prediction and the high-resolution target.
+In the Cref{ch:paper1,ch:paper2} work, PSNR and SSIM are used to quantify the performance of the proposed methods in transforming low-resolution grids to high resolution.
+However, properties of magnetic grid data are distinct to the images for which these metrics are designed.
+%   While SSIM uses structural information present in the Fourier transformed input in combination with local gradient magnitude for value accuracy,
+Consistently high SSIM scores are assigned to grids that are perceptually poor matches to the target.
+An investigation to identify a more appropriate IQA for potential field grids is required, which accounts for the distinct nature of these data and reflects the predicted quality of geological interpretation.
+This may be benefit by automated analysis methods described above.
+
+\subsection{Physics informed neural networks}
+Potential fields are constrained by several well understood physical laws, and gridded data ideally conform to these properties for use in inversion applications and further numerical processing.
+Geological interpretation is less reliant on this adherence, however \emph{a priori} information used in physics informed neural networks improve training speed and model performance \parencite{raissiPhysicsinformedNeuralNetworks2019}, and are especially useful in data-constrained domains such as geophysics.
+It is possible to broaden the definition and extend the concept of informed networks to the use of generative adversarial networks in Cref{paper1}.
+In these networks, the informing method is termed discriminator loss, and is performed by a classification network conditioned to identify images as `realistic' or `not realistic', depending on features learnt to be important within the target data by the discriminator.
+Using crafted or learnt criterions to inform a neural network greatly assists with learning high quality models, and either approach may be useful for to geophysics in addressing the paucity of ground truth.
+In addition, demonstrating the enforcement of physical properties of potential fields for model outputs may address apprehension for machine learning in geophysics practice.
+
+\chapter{Conclusion}
+This thesis presented contemporary methods in deep learning to enhance potential field methods in geoscience.
 By including both synthetic and real survey data for training and case studies, it was established that these methods could generalise to real-world applications.
 
-The proposed super-resolution (SR) method explored in Chapter 1 and Chapter 2 significantly enhanced gridded low-resolution survey data by predicting grid values that contain accurate high-frequency information.
-After establishing the feasibility of geophysics super-resolution in Chapter 1, an updated neural network and new dataset were developed in Chapter 2, where simulated line profile surveys create training data with the low-resolution transform encountered in real world exploration geophysics.
-The use of synthetic data to train a baseline model addresses the challenge of training data acquisition, as well as opens avenues for targeted geological domain specific applications.
+To the best of my knowledge, Cref{ch:paper1} presents the first investigation in the literature of super-resolution enhancement of gridded aerogeophysical data.
+Prior to this work, it was unknown how well SR methods developed for natural images in computer vision research would adapt to the features present within magnetic grids, or the challenges faced in developing a training dataset for these data.
+We established that the CNN SR methods RDN and ESRGAN could be trained to upsample low-resolution textures in magnetic grids by four times scale, and that the results were more accurate than bicubic upsampling in the real-world case study region.
+The GAN method used in Cref{ch:paper2} enhanced resolution, however it introduced significant spurious features, masking the enhancement.
+Hence, the method based on RDN was preferred.
+We identified the need for sufficient representative training data, and a realistic method to generate low-resolution training data.
 
-The contribution in Chapter 3 used coordinate multilayer perceptron neural networks to learn a representation of the function that describes a surveyed potential field extent.
+The challenge of training data availibility was addressed in Cref{ch:paper2}, where we investigated the use of geologically varied synthetic data to train a baseline model, fine-tuning with real-world data, and simulating realistic line sampling to create low-resolution data.
+We implemented the contemporary LTE network to perform this investigation, these data sampled at four times wider line spacing showed increased structural accuracy when fine-tuned with real-world data.
+Additionally, spurious features in the baseline model were correctly resolved when fine-tuned.
+We identified opportunities for more detailed investigations using a filtered approach in selecting training data, and these are outlined in \Cref{sec:futurework}.
+
+The contribution in Cref{ch:paper3} used coordinate multilayer perceptron neural networks to learn a representation of the function that describes a surveyed potential field extent.
+To my knowledge, this is the first time implicit neural representation has been reported for use with aerogeophysical survey data in the literature.
 These networks are highly suited for processing spatial data such as point sampled geophysics surveys.
-The applications contributed were predicting a regularly spaced grid from scattered survey point data, and a novel method using the representation to calculate derivatives of a potential field, both fundamental to interpretation and processing in geophysics.
+The contribution is capable of predicting regularly spaced grids from scattered survey point data, and a novel method using the representation to calculate derivatives of a potential field, both fundamental to interpretation and processing in geophysics.
 By commencing the methods from point sample data, the number of individual processing steps is reduced, and the application is fully trainable.
-The neural network approach developed in Chapter 3 uses coordinate MLP for implicit representation, a currently burgeoning field of research in computer science, and it is hoped that the proposed trainable approach for geophysics point data will prompt further development of geoscience applications in the implicit neural network domain.
-
-\section{The case for super-resolution}
-As ever, all models are wrong, but some models are useful, and this extends to super-resolution imputation.
-I envision one use-case for SR is to increase confidence in interpreting low-resolution magnetic features for geological mapping. 
-When a cautious domain expert encounters low-resolution grid data, they may interpret which gridding method was used, the line spacing and direction, and form their understanding of potential aliasing and spurious anomalies in the grid accordingly.
-Assisted by this understanding, they can infer geological features with varying degrees of confidence.
-Low confidence features which are obscured by low-resolution data will be altered, constructively or destructively, by the SR method.
-The domain expert can then use this information to reassure or reassess the original low-resolution grid.
-Because it shares the same modality, super-resolution data can be readily trialled in place of existing low-resolution data used in automated analysis and machine processing tools.
-It is expected that the enhanced appearance of features will generally improve the performance of subsequent analysis tasks on the grid raster.
-
-At the same time, it was seen in both Chapter 1, paper2 that super-resolution predictions can be misleading or entirely incorrect.
-The examples being the additional noise and implementation artefacts common in SR inference, as well as the enhancement of incorrect features in low-resolution data such as the aliased geological strike.
-Used blindly or without characterisation, these tools may inspire false confidence in the interpreter.
-I recommend a cautious approach in the use of SR\@; begin with a detailed interpretation of the low-resolution data, then enhance that understanding with the super-resolution product.
-
-\section{Revisiting Chapter 1}
-The method developed in Chapter 2 for creating sampled line profiles from potential field grids can be extended and used to train the networks described in Chapter 1.
-The resulting RDN and ESRGAN models can be compared with the LTE model described in Chapter 2, although the fixed factor upscaling block in the earlier networks limits this comparison to 4x scale.
-\Cref{fig:rdncomp} shows that RDN and ESRGAN are both highly performant for the task of predicting accurate features when upscaling \qty{320}{\m} data to \qty{40}{\m} line spacing.
-It can be inferred that the challenge of super-resolution is predominantly a question of providing suitable and sufficient training data, and less constrained to neural network choices.
-
-\begin{figure}[hbt]
-    \includegraphics[width=\linewidth]{fig/etc/TMI Comparison_23.pdf} % TODO Update for RDN, ESRGAN, LTE, ~3 hours ea.
-    \caption{}
-    \label{fig:rdncomp}
-\end{figure}
-
-\section{Synthetic data in geoscience}
-One of the challenges identified in Chapter 1 was the need for large extents of suitable training data.
-This applies to many machine learning tasks in geoscience.
-During the preparation of Chapter 2, a large and varied synthetic geology training dataset was released \parencite{jessellNoddyverseMassiveData2022}.
-This collection of labelled petrophysical voxel models and associated geophysical forward models provides many opportunities beyond those explored in this thesis.
-When taking advantage of transfer learning for pre-training, synthetic data can increase the generalisability of models for real data, as seen in Chapter 2.
-
-\section{Informed Neural Networks}
-There are controls on the learning of a neural network beyond the training data samples.
-Chapter 3 introduced to the thesis the concept of physics informed neural networks, in the form of a criterion to impose a specific constraint.
-For PINNs, this criterion enforces \emph{a priori} physical properties of the approximated function.
-It is possible to broaden the definition and extend the concept of informed networks to the use of generative adversarial networks in Chapter 1.
-In these networks, the informing method is termed \emph{discriminator loss}, and is performed by a classification network preconditioned to identify images as `realistic' or `not realistic'.
-Using crafted or learnt criterions to inform a neural network greatly assists with learning high quality models, and there is a stark contrast between the well-understood physical principles and the paucity of ground truth samples in geoscience.
-
-\section{Are potential field grids natural signals?}
-Throughout this thesis, the methods developed for geophysical data have been extended from computer vision research developed for natural images.
-Despite the success of the contributed methods, an important question has remained unaddressed.
-\emph{Are potential field grids natural images?}
-If so, it can be predicted that future methods developed in computer vision for natural images will be readily extensible to geophysics.
-Studies into the statistics of natural images have been performed \parencite{simoncelliNaturalImageStatistics2001,rudermanStatisticsNaturalImages1994,tolhurstAmplitudeSpectraNatural1992}.
-\Textcite{lecunDeepLearning2015} - CNN take advantage of ... natural signals.
-
-% Questions:
-% Are geophysical grids natural signals?
-% -   Lipschitz smoothness
-% -   Fourier power spectra fall-off
-% -   There's a citation in Compressed sensing 2006 about natural signals, from Donohan or something.
-
-\chapter{Conclusion}
-Hello I am the conclusion
+Coordinate MLPs for implicit representation are a currently burgeoning field of research in computer science, and we identify opportunities in extending advances in this research to future applications in geophysics, as outlined in \Cref{sec:futurework}.
 

### 2023-10-09 discussion.tex
Spell check and adjust chapter structure

@@
 % and provide overall conclusions that address the research aims.
-% \setcounter{chapter}{1}
+\setcounter{chapter}{4}
 
-\section{Future work}
-\label{sec:futurework}
+\chapter{Future work}
+\label{ch:futurework}
 The outputs of machine learning models are regarded with apprehension in geophysics practice due to the perceived “black box” of these methods \parencite{delaatAlgorithmicDecisionMakingBased2018,rudinStopExplainingBlack2019}, and the impact these models may have on subsequent interpretation.
@@
 
-\subsection{SR impact on interpretation}
+\section{SR impact on interpretation}
 The super-resolution outputs from the methods presented in this thesis have improved structural accuracy over the low-resolution grids.
@@
 
-\subsection{SR model construction}
+\section{SR model construction}
 Several models were implemented throughout cref{ch:paper1, ch:paper2}, namely RDN, ESRGAN, and LTE\@.
@@
     \includegraphics[width=\linewidth]{fig/etc/TMI Comparison_23.pdf} % TODO Update for RDN, ESRGAN, LTE, ~3 hours ea.
-
-    \caption{A comparison between all deep learning super-resolution methods presented in cref{paper1} and cref{paper2}, using the realistic low-resolution transform developed in cref{paper2}.
-The low-resolution input is presented in the top left, the high-resolution target in the top right.
-From left to right in the lower row; The RDN+ Network, the ESRGAN+ network, and the LTE network.}
+    \caption{
+        A comparison between all deep learning super-resolution methods presented in cref{paper1} and cref{paper2}, using the realistic low-resolution transform developed in cref{paper2}.
+        a) The low-resolution input, b) The high-resolution target, c) The RDN+ Network, d) The ESRGAN+ network, and e) The LTE network.}
     \label{modcomp}
@@
 
-\subsection{Image quality assessment for potential field grids}
+\section{Image quality assessment for potential field grids}
 Model performance is quantified using image quality assessments (IQA) such as peak signal-to-noise ratio (PSNR), structural similarity index (SSIM), feature similarity index (FSIM), or many others.
@@
 
-\subsection{Physics informed neural networks}
+\section{Physics informed neural networks}
 Potential fields are constrained by several well understood physical laws, and gridded data ideally conform to these properties for use in inversion applications and further numerical processing.
@@
 
-The challenge of training data availibility was addressed in Cref{ch:paper2}, where we investigated the use of geologically varied synthetic data to train a baseline model, fine-tuning with real-world data, and simulating realistic line sampling to create low-resolution data.
+The challenge of training data availability was addressed in Cref{ch:paper2}, where we investigated the use of geologically varied synthetic data to train a baseline model, fine-tuning with real-world data, and simulating realistic line sampling to create low-resolution data.
 We implemented the contemporary LTE network to perform this investigation, these data sampled at four times wider line spacing showed increased structural accuracy when fine-tuned with real-world data.
 Additionally, spurious features in the baseline model were correctly resolved when fine-tuned.
-We identified opportunities for more detailed investigations using a filtered approach in selecting training data, and these are outlined in \Cref{sec:futurework}.
+We identified opportunities for more detailed investigations using a filtered approach in selecting training data, and these are outlined in \Cref{ch:futurework}.
 
@@
 By commencing the methods from point sample data, the number of individual processing steps is reduced, and the application is fully trainable.
-Coordinate MLPs for implicit representation are a currently burgeoning field of research in computer science, and we identify opportunities in extending advances in this research to future applications in geophysics, as outlined in \Cref{sec:futurework}.
+Coordinate MLPs for implicit representation are a currently burgeoning field of research in computer science, and we identify opportunities in extending advances in this research to future applications in geophysics, as outlined in \Cref{ch:futurework}.
+
+\printbibliography{}
 

### 2023-10-09 intro.tex
Spell check and adjust chapter structure

@@
 \documentclass[manuscript.tex]{subfiles}
+\setcounter{chapter}{0}
 \begin{document}
-\setcounter{chapter}{1}
 
-% Ensure acronyms correctly used
-
+\chapter{Introduction}
+\label{ch:intro}
 The subsurface continuation of exposed geology can be extrapolated and interpolated using structures mapped in surveys of the Earth's naturally occuring potential fields.
@@
 
-The above aims are achieved using case studies with open access aeromagnetic data provided by Geoscience Australia.
+The above aims are investigated using case studies with open access aeromagnetic data provided by Geoscience Australia.
 
@@
 The location recorded at a sample point is the geographic latitude and longitude, and altitude, acquired with high-precision differential GPS, alongside radar altimeter elevation.
-These data may be transformed to a flat projected system, where spatial dimensions are expressed in meters, used throughout this thesis.
+These data may be transformed to a flat projected system, where spatial dimensions are expressed in metres, used throughout this thesis.
 There are numerous conventional gridding methods, and novel methods are frequently proposed in the literature.
@@
 
+\section{Traditional methods for enhancing resolution}
+As outlined in \Cref{sec:introgrids}, resolution is a product of sample distance and density, and gridded rasters have a specific number of cells in each axis depending on the spatial extent.
+Upsampling raster data to larger height and width dimensions is commonplace, and generally performed by numerical image filters such as the cubic spline \parencite{keysCubicConvolutionInterpolation1981} or Lanczos filter \parencite{lanczos1988applied}.
+Some of these interpolation methods are the basis of the gridding methods previously outlined, and simply selecting a smaller cell size during gridding is sufficient to achieve a larger image raster.
+These filters are adept at imputing the required cell values while preserving the frequency content of the original raster.
+However, no attempt is made at accurately increasing the high-frequency components of the raster, which are required by our definition for high-resolution geophysics.
+Without sampling at a smaller separation or closer line spacing, it is still possible to increase the high-frequency content of aeromagnetic grids.
+
+The rate at which the power of the component frequencies of the potential field diminish with increasing distance is well known.
+Back-calculation can be made to predict the power of these frequencies at a smaller separation, and this is termed downward continuation \textcite{bullardDeterminationMassesNecessary1948,blakelyPotentialTheoryGravity1996}.
+The inverse using a larger distance is termed upward continuation, and is useful for reducing potentially unwanted near-surface magnetic detail, or levelling data to a common datum \parencite[e.g.\ open file magnetic data in Australia is available levelled to the AWAGS datum][]{mintyAirborneGeophysicalMapping2011}.
+Downward continuation offers the benefit of high-resolution data from low-resolution sampling, and is therefore highly studied \parencite{zuoDownwardContinuationTransformation2020,liStableDownwardContinuation2023,fediStableDownwardContinuation2002,yeHighprecisionDownwardContinuation2022,zhangNumericalSolutionsMeanValue2018,guoPotentialFieldContinuation2020,gangImprovedStableDownward2018,pilkingtonPotentialFieldContinuation2017}.
+However, due to the inclusion of sensor noise, the practicable limit of numerical methods is six times the low-resolution cell size.
+Recent approaches in machine learning have overcome this limit, alongside alternative methods for enhancing aeromagnetic survey resolution.
+
 \section{Geophysics data in machine learning}
@@
     \item{} Spatio-Temporal Structure: Aeromagnetic grids are spatially corellated, neighbouring cells contain similar values arising from the same causative volume.
-    \item{} Multi-Source Multi-Resolution Data: One location may be covered by mutiple aeromagnetic surveys with different resolutions, or the same survey may be presented with different levels of processing.
+    \item{} Multi-Source Multi-Resolution Data: One location may be covered by multiple aeromagnetic surveys with different resolutions, or the same survey may be presented with different levels of processing.
     \item{} Poor Quality of Data: Sample data are subject to numerous sources of noise, which combine to become a significant fraction of the gridded data value, or be present as aliased frequencies.
@@
 As such, case studies are investigated for each aim within this thesis.
-
-\section{Traditional methods for enhancing resolution}
-As outlined in \Cref{sec:introgrids}, resolution is a product of sample distance and density, and gridded rasters have a specific number of cells in each axis depending on the spatial extent.
-Upsampling raster data to larger height and width dimensions is commonplace, and generally performed by numerical image filters such as the cubic spline \parencite{keysCubicConvolutionInterpolation1981} or Lanczos filter \parencite{lanczos1988applied}.
-Some of these interpolation methods are the basis of the gridding methods previously outlined, and simply selecting a smaller cell size during gridding is sufficient to achieve a larger image raster.
-These filters are adept at imputing the required cell values while preserving the frequency content of the original raster.
-However, no attempt is made at accurately increasing the high-frequency components of the raster, which are required by our definition for high-resolution geophysics.
-Without sampling at a smaller separation or closer line spacing, it is still possible to increase the high-frequency content of aeromagnetic grids.
-
-The rate at which the power of the component frequencies of the potential field diminish with increasing distance is well known.
-Back-calculation can be made to predict the power of these frequencies at a smaller separation, and this is termed downward continuation \textcite{bullardDeterminationMassesNecessary1948,blakelyPotentialTheoryGravity1996}.
-The inverse using a larger distance is termed upward continuation, and is useful for reducing potentially unwanted near-surface magnetic detail, or levelling data to a common datum \parencite[e.g.\ open file magnetic data in Australia is available levelled to the AWAGS datum][]{mintyAirborneGeophysicalMapping2011}.
-Downward continuation offers the benefit of high-resolution data from low-resolution sampling, and is therefore highly studied \parencite{zuoDownwardContinuationTransformation2020,liStableDownwardContinuation2023,fediStableDownwardContinuation2002,yeHighprecisionDownwardContinuation2022,zhangNumericalSolutionsMeanValue2018,guoPotentialFieldContinuation2020,gangImprovedStableDownward2018,pilkingtonPotentialFieldContinuation2017}.
-However, due to the inclusion of sensor noise, the practicable limit of numerical methods is six times the low-resolution cell size.
-Recent approaches in machine learning have overcome this limit, alongside alternative methods for enhancing aeromagnetic survey resolution.
 
@@
 The objective of training a neural network is to set the values for these for each neuron in the network, such that the trained network (or model) generalises to novel data.
-This is performed by back propogation \parencite{rumelhartLearningRepresentationsBackpropagating1988}, a technique to navigate toward the lowest error solution by calculating the rate of improvement resulting from parameter updates.
+This is performed by back propagation \parencite{rumelhartLearningRepresentationsBackpropagating1988}, a technique to navigate toward the lowest error solution by calculating the rate of improvement resulting from parameter updates.
 A practical introduction to the practice of training machine learning is available from \textcite{stevensDeepLearningPyTorch2020}, while a more formal introduction is provided in \textcite{bishopPatternRecognitionMachine2006}.
@@
 However, recent work on periodic activation functions such as the sinusoid \parencite{sitzmann2019siren} enable the networks used in Cref{ch:paper3}.
-The other primary descriptor of a neural network is its architecture, refering to the configuration of its intermediate layers between the input and output.
+The other primary descriptor of a neural network is its architecture, referring to the configuration of its intermediate layers between the input and output.
 These architectures are described below.
@@
 Deep learning is a field of contemporary machine learning, where multiple layers of feature learning are undertaken between the input to a method and the output.
-The current generation of deep learning is reported in review articles to have begun in 2006 \parencite{dengDeepLearningMethods2014,goodfellowDeepLearning2016a}, and has pervaded many industries and research fields.
+The current generation of deep learning is reported by review articles to have begun in 2006 \parencite{dengDeepLearningMethods2014,goodfellowDeepLearning2016a}, and has pervaded many industries and research fields.
 These review articles contain thorough background on the implementation and practice of various architectures for undertaking deep learing, as well as earlier machine learning or numerical models that can address tasks now approached with deep learning.

### 2023-10-09 paper2.tex
Spell check and adjust chapter structure

@@
 \begin{document}
-% \setcounter{chapter}{1}
+\setcounter{chapter}{2}
 \title{Super-resolution of Aeromagnetic Survey Data}
@@
 These airborne surveys collect data at wide line spacing to minimise cost, with lines in Western Australian low-resolution regional surveys typically \qty{400}{\m} apart, however, open access high-resolution surveys with line spacings of \qty{100}{\m} or closer are increasingly common.
-Sampling along line is typically performed at \qty{10}{\Hz} or faster, which corresponds to several meters between samples at a nominal flight speed of \qty{70}{\m\per\s} \parencite{goodwinAirborneMagneticRadiometric2023}.
+Sampling along line is typically performed at \qty{10}{\Hz} or faster, which corresponds to several metres between samples at a nominal flight speed of \qty{70}{\m\per\s} \parencite{goodwinAirborneMagneticRadiometric2023}.
 Because the power of shorter wavelengths in potential fields diminish with increasing distances from the source, aeromagnetic flights are flown as low as safety and topography permits.
@@
 Long-wavelength features and smooth gradients, such as those present in sedimentary units or areas of cover are accurately upscaled in the proposed method, however these are also adequately upscaled with simple cubic spline interpolation of the low-resolution grid because they do not require predicted high frequency components.
-The exception for super-resolution having higher quality is in areas of low magnitude TMI of only a few nanoTesla across the entire extent.
+The exception for super-resolution having higher quality is in areas of low magnitude TMI of only a few nanotesla across the entire extent.
 In these cases, the otherwise minor noise introduced by the super-resolution process dominates the residual.

### 2023-10-10 discussion.tex
Add geoscience ML background

@@
 For supervised tasks, a full reference metric can be calculated between the super-resolution prediction and the high-resolution target.
-In the Cref{ch:paper1,ch:paper2} work, PSNR and SSIM are used to quantify the performance of the proposed methods in transforming low-resolution grids to high resolution.
+In the Cref{ch:paper1,ch:paper2} works, PSNR and SSIM are used to quantify the performance of the proposed methods in transforming low-resolution grids to high resolution.
 However, properties of magnetic grid data are distinct to the images for which these metrics are designed.
@@
 Consistently high SSIM scores are assigned to grids that are perceptually poor matches to the target.
+High values are noted in other geophysical grid investigations reporting SSIM metrics \parencite{wangDeeplearningbasedSeismicData2018,bavandsavadkoohiHighresolutionAeromagneticMap2023}
 An investigation to identify a more appropriate IQA for potential field grids is required, which accounts for the distinct nature of these data and reflects the predicted quality of geological interpretation.

### 2023-10-10 intro.tex
Add geoscience ML background

@@
 The inverse using a larger distance is termed upward continuation, and is useful for reducing potentially unwanted near-surface magnetic detail, or levelling data to a common datum \parencite[e.g.\ open file magnetic data in Australia is available levelled to the AWAGS datum][]{mintyAirborneGeophysicalMapping2011}.
-Downward continuation offers the benefit of high-resolution data from low-resolution sampling, and is therefore highly studied \parencite{zuoDownwardContinuationTransformation2020,liStableDownwardContinuation2023,fediStableDownwardContinuation2002,yeHighprecisionDownwardContinuation2022,zhangNumericalSolutionsMeanValue2018,guoPotentialFieldContinuation2020,gangImprovedStableDownward2018,pilkingtonPotentialFieldContinuation2017}.
+Downward continuation offers the benefit of high-resolution data from low-resolution sampling, and is therefore highly studied \parencite{zuoDownwardContinuationTransformation2020,fediStableDownwardContinuation2002,zhangNumericalSolutionsMeanValue2018,guoPotentialFieldContinuation2020,gangImprovedStableDownward2018,pilkingtonPotentialFieldContinuation2017}.
 However, due to the inclusion of sensor noise, the practicable limit of numerical methods is six times the low-resolution cell size.
@@
 
-Recently, CNNs have been surpassed by coordinate multilayer perceptron (CMLP) neural networks in some representation learning tasks \parencite[e.g.][]{chenLearningContinuousImage2021}.
+Recently, CNNs have been surpassed by coordinate multilayer perceptron (CMLP) neural networks in some representation learning tasks, including SR \parencite{chenLearningContinuousImage2021}.
+CMLPs specifically use a dataset containing individual input points containing coordinate features, and train to predict individual output feature vectors at those coordinates \parencite[e.g.][]{mildenhallNeRFRepresentingScenes2020}.
 Key to the performance of these networks are implicit functions, which parameterise a function learned from training dataset with a neural network analogue.
@@
 
-%     \item * talk about different superresolution methods that have been effective for some applications with refs*, and introduce learning implicit representation from imagery and their application for improving resolution *** I think it's useful to link this resolution improvement in geophysics as imputation problem.
+%  introduce learning implicit representation from imagery and their application for imputation, I think it's useful to link this resolution improvement in geophysics as imputation problem.
 
@@
 \label{sec:introgeoml}
-%     \item *needs a bit of literature review on what's been done before in this space in geoscience***
-%     \item to the best of my knowledge, this use of super-resolution ***
-% \end{itemize}
 
-\section{}
-\label{sec:introgeoml}
-The earliest application of CNN SR was demonstrated by \parencite{dongLearningDeepConvolutional2014}, where convolutional layers are used for low-resolution patch extraction, feature mapping, and reconstruction of high-resolution images.
-The outputs of each convolutional layer are similar to hand-crafted filters or feature dictionaries in earlier example-based super-resolution methods \parencite{freemanExamplebasedSuperresolution2002}, but the learnt filters are more numerous and fully trainable with the deep learning approach.
-Following the success of \parencite{dongLearningDeepConvolutional2014}, many iterative improvements have been made to CNN based SR\@.
-These include SRCNN \parencite{dongImageSuperresolutionUsing2016}, RDN \parencite{zhangResidualDenseNetwork2018}, ESRGAN \parencite{wangESRGANEnhancedSuperresolution2018}, and others \parencite{ledigPhotorealisticSingleImage2017,limEnhancedDeepResidual2017}.
-While each of these works contribute unique features to CNN-based super-resolution, they follow a common stacked block design.
-This comprises a set of initial input feature extraction convolutions, a sequence of convolutional blocks with activations (neurons), some number and arrangement of intermediate residual learning pathways (skip connections), and an upsampling block for feature upscaling and convolving latent features back to image space.
-% One limitation of these CNN-based networks is the challenge of upscaling data at non-integer scales, and scales beyond those in the training dataset.
-% This was achieved by \parencite{huMetaSRMagnificationarbitraryNetwork2019,wangLearningSingleNetwork2021}, however recent approaches using implicit function based networks have improved performance.
+Geoscience is a diverse science, with ubiquitous use of raster data.
+Machine learning is not new to geoscience, and work has been performed on applications in the field for many years.
+Recent reviews have highlighted a rapid increase in machine learning research contributions to geophysics.
+The aims of this thesis are related to specific findings in these review articles.
+\textcite{bergenMachineLearningDatadriven2019} recommends the development and use of benchmark datasets and identifies opportunities in the use of transfer learning from synthetic data.
+This is echoed by \textcite{karpatneMachineLearningGeosciences2019}, who also identify prospective research avenues in theory guided science using physics-guided neural networks, the concept of directly leveraging \emph{a priori} domain knowledge within machine learning models.
 
-\begin{itemize}
-    \item This thesis, explores the applications of
-    \item And the potential field has frequency based details to interpet sources at varying depth, etc...
-    \item how this is directly relevant to implicit neural representation learning....
-    \item This needs to set the scence of what is to come...
-\end{itemize}
+Early adoption of SR was seen in satellite and airborne remote sensing, where the data share image features with natural images \parencite{lanarasSuperresolutionSentinel2Images2018,arunConvolutionalNetworkArchitectures2019,kawulokTrainingDeepNetworks2019}, and others.
+Hyperspectral data SR are commonly investigated \parencite{yangHyperspectralImageClassification2018,arunCNNBasedSuperResolutionHyperspectral2020}. 
+Rock microscopy images have been upsampled with SR \parencite{niuInnovativeApplicationGenerative2020}, and their accuracy compared using domain specific parameter calculation.
+SR with physics informed learning has been performed by \textcite{bodeUsingPhysicsinformedEnhanced2021,jiangMeshfreeFlowNetPhysicsConstrainedDeep2020} in the field of fluid dynamics, \textcite{leongDeepBedMapDeepNeural2020} in the field of basement topography, and \textcite{jungbluthSingleframeSuperresolutionSolar2019} in astrophysics.
+Additionally, physics informed learning has been performed with multi-physics integration in \textcite{degen3DMultiphysicsUncertainty2022}
+Seismic data SR \parencite{liSuperresolutionSeismicVelocity2021}, and with the removal of noise \parencite{liDeepLearningSimultaneous2021}, 
+Various potential field gridding \parencite{naprstekApplicationsMachineLearning2019,wangDeepLearningGravity2019a} and downward continuation methods \parencite{liStableDownwardContinuation2023,yeHighprecisionDownwardContinuation2022} have been proposed leveraging neural networks.
+And in the recent topic of implicit representation, several applications have been proposed in geoscience, including geological modelling \textcite{hillierGeoINRImplicitNeural2023}.
+
+Beyond the applications investigated in this thesis, many other machine learning methods have been investigated in geoscience.
+These include: clustering of geophysical textures \parencite{grujicGeophysicsNeuralNetworks2019}, prediction of geological map event history \parencite{guo3DGeologicalStructure2021}, automated interpretation of geological data \parencite{waldelandConvolutionalNeuralNetworks2018, babakhinSemisupervisedSegmentationSalt2019,dawsonImpactDatasetSize2023}, seismic data interpolation \parencite{wangDeeplearningbasedSeismicData2018}, and 3D structure, joint inversion, or modelling \parencite{guo3DGeologicalStructure2021,zhihouJointGravityGravity2021},
+
+Additionally, deep learning methods in medical imaging and other scientific disciplines share challenges and modalities with geoscience raster data, including noise, small sample size, multi-source multi-resolution, and others.
+Advances in these fields can be explored and adapted in conjunction with work in geoscience.
+
+Feature identification is a common theme in all fields, using deep learning to detect, classify, or segment features of interest to geoscience research.
+
+These works in geoscience machine learning commonly reiterate the challenge of data acquisition.
+One approach to overcoming the challenges faced in real-world geoscience data is to use synthetic data.
+During this thesis, a large collection of synthetic data became available, containing realistic 3D geological voxel models and 2D geophysical forward models \parencite{jessellNoddyverseMassiveData2022}.
+These data present a large amount of uniformly sampled and noise free grids from an unbiased set of geological domains.
 

### 2023-10-10 discussion.tex
Make compilable
Cleverref and subfiles seem to interact poorly, and I can't cref labels in external files in the way I had set up.

I've moved to using  \include.

@@
-\documentclass[manuscript.tex]{subfiles}
-\begin{document}
+% % \documentclass[manuscript.tex]{subfiles}
+% \documentclass[12pt,a4paper]{report} %,openright,twoside
+% \usepackage{thesisstyle}
+% \addbibresource{bib/PhD.bib}
+% \setcounter{chapter}{4}
+% \begin{document}
 
@@
 % and provide overall conclusions that address the research aims.
-\setcounter{chapter}{4}
 
@@
         a) The low-resolution input, b) The high-resolution target, c) The RDN+ Network, d) The ESRGAN+ network, and e) The LTE network.}
-    \label{modcomp}
+    \label{fig:modcomp}
 \end{figure}
@@
 
-\chapter{Conclusion}
+\printbibliography{}
+
+\chapter{Conclusions}
 This thesis presented contemporary methods in deep learning to enhance potential field methods in geoscience.
@@
 Additionally, spurious features in the baseline model were correctly resolved when fine-tuned.
-We identified opportunities for more detailed investigations using a filtered approach in selecting training data, and these are outlined in \Cref{ch:futurework}.
+We identified opportunities for more detailed investigations using a filtered approach in selecting training data, and these were outlined in \Cref{ch:futurework}.
 
@@
 
-\printbibliography{}
-
-\end{document}
+% \end{document}

### 2023-10-10 intro.tex
Make compilable
Cleverref and subfiles seem to interact poorly, and I can't cref labels in external files in the way I had set up.

I've moved to using  \include.

@@
-\documentclass[manuscript.tex]{subfiles}
-\setcounter{chapter}{0}
-\begin{document}
+% \documentclass[manuscript.tex]{subfiles}
+% \documentclass[12pt,a4paper]{report} %,openright,twoside
+% \usepackage{thesisstyle}
+% \addbibresource{bib/PhD.bib}
+% % \setcounter{chapter}{1}
+% \begin{document}
 
-\chapter{Introduction}
-\label{ch:intro}
 The subsurface continuation of exposed geology can be extrapolated and interpolated using structures mapped in surveys of the Earth's naturally occuring potential fields.
@@
 
-Geoscience is a diverse science, with ubiquitous use of raster data.
+Geoscience is a diverse field, with ubiquitous use of raster data.
 Machine learning is not new to geoscience, and work has been performed on applications in the field for many years.
-Recent reviews have highlighted a rapid increase in machine learning research contributions to geophysics.
+Recent reviews have highlighted a rapid increase in machine learning research contributions to Earth science.
 The aims of this thesis are related to specific findings in these review articles.
@@
 SR with physics informed learning has been performed by \textcite{bodeUsingPhysicsinformedEnhanced2021,jiangMeshfreeFlowNetPhysicsConstrainedDeep2020} in the field of fluid dynamics, \textcite{leongDeepBedMapDeepNeural2020} in the field of basement topography, and \textcite{jungbluthSingleframeSuperresolutionSolar2019} in astrophysics.
-Additionally, physics informed learning has been performed with multi-physics integration in \textcite{degen3DMultiphysicsUncertainty2022}
-Seismic data SR \parencite{liSuperresolutionSeismicVelocity2021}, and with the removal of noise \parencite{liDeepLearningSimultaneous2021}, 
+Additionally, physics informed learning has been performed with multi-physics integration in \textcite{degen3DMultiphysicsUncertainty2022}.
+Seismic data has been investigated with SR \parencite{liSuperresolutionSeismicVelocity2021}, and with the removal of noise \parencite{liDeepLearningSimultaneous2021}.
+
 Various potential field gridding \parencite{naprstekApplicationsMachineLearning2019,wangDeepLearningGravity2019a} and downward continuation methods \parencite{liStableDownwardContinuation2023,yeHighprecisionDownwardContinuation2022} have been proposed leveraging neural networks.
-And in the recent topic of implicit representation, several applications have been proposed in geoscience, including geological modelling \textcite{hillierGeoINRImplicitNeural2023}.
+Finally, in the recent topic of implicit representation there have been several applications proposed, including geological modelling \textcite{hillierGeoINRImplicitNeural2023}.
 
@@
 
-Additionally, deep learning methods in medical imaging and other scientific disciplines share challenges and modalities with geoscience raster data, including noise, small sample size, multi-source multi-resolution, and others.
+Additionally, deep learning methods in medical imaging and other scientific disciplines share challenges and modalities with geoscience raster data, including noise, small sample size, multi-source and multi-resolution, and other properties.
 Advances in these fields can be explored and adapted in conjunction with work in geoscience.
-
 Feature identification is a common theme in all fields, using deep learning to detect, classify, or segment features of interest to geoscience research.
@@
 These works in geoscience machine learning commonly reiterate the challenge of data acquisition.
-One approach to overcoming the challenges faced in real-world geoscience data is to use synthetic data.
+One approach to overcoming this and other challenges faced in real-world geoscience data is to use synthetic data.
 During this thesis, a large collection of synthetic data became available, containing realistic 3D geological voxel models and 2D geophysical forward models \parencite{jessellNoddyverseMassiveData2022}.
-These data present a large amount of uniformly sampled and noise free grids from an unbiased set of geological domains.
+These data present a large amount of uniformly sampled and noise free grids from an unbiased set of geological domains, and may offer a solution to some of these data challenges.
 
@@
 
-\end{document}
+% \end{document}

### 2023-10-10 manuscript.tex
Spell check and adjust chapter structure
Make compilable
Cleverref and subfiles seem to interact poorly, and I can't cref labels in external files in the way I had set up.

I've moved to using  \include.
Update titlepage

@@
 \documentclass[12pt,a4paper]{report} %,openright,twoside
+% \includeonly{}
 \usepackage{thesisstyle}
@@
 \begin{titlepage}
+    \centering
 
-    \begin{center}
-        \large{\textbf{Potential Field Geophysics Enhancement Using Contemporary Deep Learning Approaches}}
+        \vspace*{48 pt}
+        {\large\textbf{Potential Field Geophysics Enhancement Using Contemporary Deep Learning Approaches}}
 
-        \vspace{15 mm}
-        {\large{Luke Thomas Smith, BSc, MRes}}
+        \vspace{48 pt}
+        {\itshape{{\Large Luke Thomas Smith}, BSc, MRes}}
 
-        \vspace{15 mm}
+        \vspace{48 pt}
         This thesis is presented for the degree of
 
-        \vspace{5 mm}
+        \vspace{14 pt}
         \textbf{Doctor of Philosophy}
@@
         \textbf{The University of Western Australia}
-        \vspace{5 mm}
 
+        \vspace{14 pt}
         School of Earth Sciences
-        \vspace{20 mm}
 
-        \begin{figure}[h]
-            \centering{}
-            \includegraphics[scale=0.5]{fig/etc/UWA_FORMAL_PORTRAIT_CMYK}
-        \end{figure}
+        \vspace{72 pt}
+        \includegraphics[scale=0.35]{fig/etc/UWA_FORMAL_PORTRAIT_CMYK}
 
@@
         2023
-    \end{center}
 \end{titlepage}
@@
 \listoffigures{}
-\listoftables{}
+% \listoftables{}
 
@@
 \chapter{Introduction}
-\label{ch:intro}
-\subfile{intro}
+% \subfile{intro}
+% \includepdf[pages=-]{intro.pdf}
+\include{intro}
 
 \chapter{Magnetic Grid Resolution Enhancement using Machine Learning}
-\label{ch:paper1}
+\label{paper1}
 This chapter has been reproduced from the following peer reviewed publication. Formatting has been adjusted for consistency.
@@
 https://doi.org/10.1016/j.oregeorev.2022.105119
-\subfile{paper1}
+% \subfile{paper1}
+% \includepdf[pages=-]{paper1.pdf}
+\include{paper1}
 
 \chapter{Super-resolution of Aeromagnetic Survey Data}
-\label{ch:paper2}
-\subfile{paper2}
+\label{paper2}
+% \includepdf[pages=-]{paper2.pdf}
+% \subfile{paper2}
+\include{paper2}
 
 \chapter{Implicit Neural Representation for Potential Field Geophysics}
-\label{ch:paper3}
+\label{paper3}
+% \includepdf[pages=-]{paper3.pdf}
 % \subfile{paper3}
+\include{paper3}
 
-\chapter{Discussion}
-\label{ch:discussion}
-\subfile{discussion}
+% \includepdf[pages=-]{discussion.pdf}
+% \subfile{discussion}
+\include{discussion}
 

### 2023-10-10 discussion.tex
Further fix cross references

@@
     \item{} Identifying an improved image quality assessment for gridded potential field data.
-    \item{} Investigating the use of a physics informed approach for SR and implicit representation, and,
+    \item{} Investigating the use of a physics-informed approach for SR and implicit representation, and,
 \end{enumerate}
@@
 This is likely to have a positive impact on the detection of features such as lineaments and unit boundaries for geological interpretation from magnetic data.
-However, despite the reduction of introduced structural inaccuracies with the use of open access training data in Cref{ch:paper2}, it is likely that some features with specific structural geometries will still be incorrectly super-resolved.
+However, despite the reduction of introduced structural inaccuracies with the use of open access training data in \Cref{ch:paper2}, it is likely that some features with specific structural geometries will still be incorrectly super-resolved.
 A domain expert may be able to recognise structures that are inconsistent using auxiliary information and the regional geological context, but machine processed super-resolution grids will use these data as provided.
@@
 \section{SR model construction}
-Several models were implemented throughout cref{ch:paper1, ch:paper2}, namely RDN, ESRGAN, and LTE\@.
+Several models were implemented throughout \Cref{ch:paper1,ch:paper2}, namely RDN, ESRGAN+, and LTE\@.
 % However, the most important choice in developing a performant super-resolution neural network for real-world aeromagnetic survey data was the choice of training data.
-Cref{paper1} was prepared prior the release of a large and varied synthetic geology training dataset \parencite{jessellNoddyverseMassiveData2022}.
-It was seen in cref{paper2} that this data improved model performance for a range of features by using transfer learning for pre-training.
+\Cref{ch:paper1} was prepared prior the release of a large and varied synthetic geology training dataset \parencite{jessellNoddyverseMassiveData2022}.
+It was seen in \Cref{ch:paper2} that this data improved model performance for a range of features by using transfer learning for pre-training.
 % This transfer learning approach for training data is also found to be useful for RDN and ESRGAN\@.
-Here, the use of synthetic and real-world line spacing sampled data approach used with LTE in cref{ch:paper2} are adopted for the RDN and ESRGAN models.
-Cref{fig:modcomp} shows RDN and ESRGAN in predicting accurate features when upscaling \qty{320}{\m} data to \qty{80}{\m} line spacing.
+Here, the use of synthetic and real-world line spacing sampled data approach used with LTE in \Cref{ch:paper2} are adopted for the RDN+ and ESRGAN+ models.
+\Cref{fig:modcomp} shows RDN and ESRGAN+ in predicting accurate features when upscaling \qty{320}{\m} data to \qty{80}{\m} line spacing.
 It can be inferred that the challenge of super-resolution for these tasks is predominantly a question of providing suitable and sufficient training data, and is less constrained to neural network choices.
@@
     \caption{
-        A comparison between all deep learning super-resolution methods presented in cref{paper1} and cref{paper2}, using the realistic low-resolution transform developed in cref{paper2}.
+        A comparison between all deep learning super-resolution methods presented in \Cref{ch:paper1} and \Cref{ch:paper2}, using the realistic low-resolution transform developed in \Cref{ch:paper2}.
         a) The low-resolution input, b) The high-resolution target, c) The RDN+ Network, d) The ESRGAN+ network, and e) The LTE network.}
@@
 For supervised tasks, a full reference metric can be calculated between the super-resolution prediction and the high-resolution target.
-In the Cref{ch:paper1,ch:paper2} works, PSNR and SSIM are used to quantify the performance of the proposed methods in transforming low-resolution grids to high resolution.
+In the \Cref{ch:paper1,ch:paper2} works, PSNR and SSIM are used to quantify the performance of the proposed methods in transforming low-resolution grids to high resolution.
 However, properties of magnetic grid data are distinct to the images for which these metrics are designed.
@@
 Consistently high SSIM scores are assigned to grids that are perceptually poor matches to the target.
-High values are noted in other geophysical grid investigations reporting SSIM metrics \parencite{wangDeeplearningbasedSeismicData2018,bavandsavadkoohiHighresolutionAeromagneticMap2023}
+High values are noted in other geophysical grid investigations reporting SSIM metrics \parencite{wangDeeplearningbasedSeismicData2018,bavandsavadkoohiHighresolutionAeromagneticMap2023}.
 An investigation to identify a more appropriate IQA for potential field grids is required, which accounts for the distinct nature of these data and reflects the predicted quality of geological interpretation.
@@
 
-\section{Physics informed neural networks}
+\section{Physics-informed neural networks}
 Potential fields are constrained by several well understood physical laws, and gridded data ideally conform to these properties for use in inversion applications and further numerical processing.
-Geological interpretation is less reliant on this adherence, however \emph{a priori} information used in physics informed neural networks improve training speed and model performance \parencite{raissiPhysicsinformedNeuralNetworks2019}, and are especially useful in data-constrained domains such as geophysics.
-It is possible to broaden the definition and extend the concept of informed networks to the use of generative adversarial networks in Cref{paper1}.
+Geological interpretation is less reliant on this adherence, however \emph{a priori} information used in physics-informed neural networks improve training speed and model performance \parencite{raissiPhysicsinformedNeuralNetworks2019}, and are especially useful in data-constrained domains such as geophysics.
+It is possible to broaden the definition and extend the concept of informed networks to the use of generative adversarial networks in \Cref{ch:paper1}.
 In these networks, the informing method is termed discriminator loss, and is performed by a classification network conditioned to identify images as `realistic' or `not realistic', depending on features learnt to be important within the target data by the discriminator.
@@
 \chapter{Conclusions}
+\label{ch:conclusions}
 This thesis presented contemporary methods in deep learning to enhance potential field methods in geoscience.
@@
 
-To the best of my knowledge, Cref{ch:paper1} presents the first investigation in the literature of super-resolution enhancement of gridded aerogeophysical data.
+To the best of my knowledge, \Cref{ch:paper1} presents the first investigation in the literature of super-resolution enhancement of gridded aerogeophysical data.
 Prior to this work, it was unknown how well SR methods developed for natural images in computer vision research would adapt to the features present within magnetic grids, or the challenges faced in developing a training dataset for these data.
 We established that the CNN SR methods RDN and ESRGAN could be trained to upsample low-resolution textures in magnetic grids by four times scale, and that the results were more accurate than bicubic upsampling in the real-world case study region.
-The GAN method used in Cref{ch:paper2} enhanced resolution, however it introduced significant spurious features, masking the enhancement.
+The GAN method used in \Cref{ch:paper2} enhanced resolution, however it introduced significant spurious features, masking the enhancement.
 Hence, the method based on RDN was preferred.
@@
 
-The challenge of training data availability was addressed in Cref{ch:paper2}, where we investigated the use of geologically varied synthetic data to train a baseline model, fine-tuning with real-world data, and simulating realistic line sampling to create low-resolution data.
+The challenge of training data availability was addressed in \Cref{ch:paper2}, where we investigated the use of geologically varied synthetic data to train a baseline model, fine-tuning with real-world data, and simulating realistic line sampling to create low-resolution data.
 We implemented the contemporary LTE network to perform this investigation, these data sampled at four times wider line spacing showed increased structural accuracy when fine-tuned with real-world data.
@@
 
-The contribution in Cref{ch:paper3} used coordinate multilayer perceptron neural networks to learn a representation of the function that describes a surveyed potential field extent.
+The contribution in \Cref{ch:paper3} used coordinate multilayer perceptron neural networks to learn a representation of the function that describes a surveyed potential field extent.
 To my knowledge, this is the first time implicit neural representation has been reported for use with aerogeophysical survey data in the literature.

### 2023-10-10 intro.tex
Further fix cross references

@@
 These are presented in Cref{ch:paper1,ch:paper2,ch:paper3}, each with a brief contextual introduction.
-Key findings and contributions of the research are discussed in Cref{ch:discussion}, followed by overall thesis conclusions in Cref{ch:conclusion}.
+Key findings and summary conclusions of the research are discussed in \Cref{ch:conclusions}.
 
@@
 The chapter concludes by observing the success of SR on magnetic features, characterising the performance of the two adapted networks, and recommending the method based on RDN as being more reliable for the SR task.
-The primary contribution of Cref{ch:paper1} is establishing the capacity of the SR networks developed for natural images in computer vision to extend to the distinctly different data of low-resolution aeromagnetic geophysics.
+The primary contribution of \Cref{ch:paper1} is establishing the capacity of the SR networks developed for natural images in computer vision to extend to the distinctly different data of low-resolution aeromagnetic geophysics.
 
-Following the findings of the previous chapter, Cref{ch:paper2} addresses the need for more generalisable model training for real-world super-resolution.
+Following the findings of the previous chapter, \Cref{ch:paper2} addresses the need for more generalisable model training for real-world super-resolution.
 It undertakes these aims by training a baseline synthetic model with data from a contemporaneously published collection of magnetic grids forward modelled from realistic geology \parencite{jessellNoddyverseMassiveData2022}, on data from over \num{300} distinct geological histories.
@@
 
-Cref{ch:paper3} reports the use of coordinate multilayer perceptron (CMLP) neural networks for representation learning of a surveyed potential field extent.
+\Cref{ch:paper3} reports the use of coordinate multilayer perceptron (CMLP) neural networks for representation learning of a surveyed potential field extent.
 With the proposed method, scattered line data can be encoded into the grid, and cells queried at interpolating coordinates to predict regularised grids.
@@
 
-Cref{ch:discussion} presents a synthesis discussion for the prior chapters.
+\Cref{ch:futurework} presents a synthesis discussion for the prior chapters.
 Given the recency of deep learning super-resolution and implicit neural representation, multiple avenues of future opportunities are identified.
 These aim to increase the adoption of super-resolution in geophysics by addressing apprehension toward the reliability of interpretation of the outputs.
-A synthesis comparison of the SR networks adapted in Cref{ch:paper1,ch:paper2} is also presented, which prompts questions regarding model and dataset construction.
-The use of a priori information well understood to geophysics is also discussed, with potential application in both super-resolution and implicit neural representation.
+A synthesis comparison of the SR networks adapted in \Cref{ch:paper1,ch:paper2} is also presented, which prompts questions regarding model and dataset construction.
+The use of \emph{a priori} information well understood to geophysics is also discussed, with potential application in both super-resolution and implicit neural representation.
 
-Finally, overall conclusions are presented in Cref{ch:conclusion}.
+Finally, overall conclusions are presented in \Cref{ch:conclusions}.
 

### 2023-10-10 manuscript.tex
Further fix cross references
Fix incorrect inserted page numbering

@@
 % \subfile{authorship_declaration}
-\includepdf[pages=-]{authorship_declaration_signed.pdf}
+% Fix incorrect page numbering
+\includepdf[pages=-,templatesize={595.276pt}{841.89pt},nup=1x1,scale=1,clip,trim=5mm 36.5mm 5mm 20mm,fitpaper=true,pagecommand={\pagestyle{plain}}]{authorship_declaration_signed.pdf}
 
@@
 \chapter{Introduction}
+\label{ch:intro}
 % \subfile{intro}
@@
 \chapter{Super-resolution of Aeromagnetic Survey Data}
-\label{paper2}
+\label{ch:paper2}
 % \includepdf[pages=-]{paper2.pdf}
@@
 \chapter{Implicit Neural Representation for Potential Field Geophysics}
-\label{paper3}
+\label{ch:paper3}
 % \includepdf[pages=-]{paper3.pdf}

### 2023-10-10 intro.tex
Update per DW feedback

@@
 The subsurface continuation of exposed geology can be extrapolated and interpolated using structures mapped in surveys of the Earth's naturally occuring potential fields.
-Potential field surveys offer low-cost investigations over a large spatial extent, and routinely used for geological mapping and interpretation \parencite{nabighian75thAnniversaryHistorical2005}
+Potential field surveys offer low-cost investigations over a large spatial extent, and routinely used for geological mapping and interpretation \parencite{nabighian75thAnniversaryHistorical2005}.
 For this reason, magnetic field surveys are commonly used by geophysicists for geological mapping and interpretation toward understanding the Earth in three dimensions.
@@
 The role of high-resolution details in these geophysical methods is becoming more important to exploration as resources are increasingly sought from below sedimentary cover.
-Resolution enhancement has seen recent success from the use of deep learning \parencite{moserHitchhikerGuideSuperResolution2023}, however it is not understood if these methods could extend to geophysics data, which are highly distinct from natural images.
+Resolution enhancement for natural images has seen recent success from the use of deep learning \parencite{moserHitchhikerGuideSuperResolution2023}, however it is not understood if these methods could extend to geophysics data, which are highly distinct from the natural images used for training in prior enhancement methods.
 
@@
 
-    \item{} Constructing a model framework to ensure example based models can be trained incorporating diverse types of geological features manifested in magnetic data, and evaluating the effectiveness the framework with a resolution enhancement technique based on survey line spacing;
+    \item{} Constructing a model framework to ensure example based models can be trained incorporating diverse types of geological features manifested in magnetic data, and evaluating the effectiveness of the framework with a resolution enhancement technique based on survey line spacing;
 
@@
 For regional and contemporary surveys this is recommended to be North-South, however early practice was to survey perpendicular to the dominant geological strike, under the expectation of sampling the greatest frequency of change in magnetic intensity \parencite{islesGeologicalInterpretationAeromagnetic2018}.
-Higher frequencies with these data diminish with increasing source-sensor distance, therefore the lower the height, the more high-frequency components will be captured by the sensor.
+Higher frequencies within these data diminish with increasing source-sensor distance, therefore the lower the height, the more high-frequency components will be captured by the sensor.
 Acquisition along flight lines is sampled at a rate of \qty{10}{\hertz} or greater, which corresponds to an interval of \qty{7}{\m} or shorter at nominal flight speeds of \qty{70}{\m\per\s} \parencite{goodwinAirborneMagneticRadiometric2023}.
@@
 The field strength measured is the Total Magnetic Intensity (TMI), which is the vector sum of each directional vector of the potential \parencite{blakelyPotentialTheoryGravity1996}.
-This scalar value is recorded in nanotesla and may be negative with an unbounded range that can exceed \qty{50,000}{\nano\tesla} in the Earth's environment.
+This scalar value is recorded in nanotesla (nT) and may be negative with an unbounded range that can exceed \qty{50000}{\nano\tesla} in the Earth's environment.
 The location recorded at a sample point is the geographic latitude and longitude, and altitude, acquired with high-precision differential GPS, alongside radar altimeter elevation.
@@
 Of those most commonly used in potential field geophysics, these are minimum curvature \parencite{briggsMachineContouringUsing1974}, splines \parencite{bhattacharyyaBicubicSplineInterpolation1969,shureHarmonicSplinesGeomagnetic1982,smithGriddingContinuousCurvature1990}, and equivalent sources \parencite{dampneyEquivalentSourceTechnique1969, solerBetterStrategyInterpolating2020}.
-Splines are used in bi-directional gridding, which is well-suited for aeromagnetic surveys, where the sample data are first interpolated in the line parallel direction, and the intermediate product is interpolated in the line perpendicular direction \parencite{dentithGeophysicsMineralExploration2014}.
+Splines are used in bi-directional gridding, which is well-suited for aeromagnetic surveys, where the sample data are first interpolated in the line parallel direction, and the intermediate product is interpolated in the line-perpendicular direction \parencite{dentithGeophysicsMineralExploration2014}.
 A method known as kriging is used in other areas of geoscience, such as geochemical mapping, and makes use of statistical properties of the known distribution \parencite{hansenInterpretiveGriddingAnisotropic1993,davis1986statistics}.
@@
 This sufficiently preserves detail in areas of high sampling, while avoiding excessive interpolated cells in areas of low sampling, which may lead to artefacts.
-Because of the sampling frequency of nominally \qty{7}{\m} in the flight line direction, and  up to \qty{400}{\m} in the line perpendicular direction, the resulting grid resolution will be anisotropic at best, and uniformly low-resolution at worst.
+Because of the sampling frequency of nominally \qty{7}{\m} in the flight line direction, and  up to \qty{400}{\m} in the line-perpendicular direction, the resulting grid resolution will be anisotropic at best, and uniformly low-resolution at worst.
 An important property of sampled data is the Nyquist frequency, \[f_{Nyquist} = f_{sampling} / 2.\]
@@
 
-The rate at which the power of the component frequencies of the potential field diminish with increasing distance is well known.
+The rate at which the power of the component frequencies of the potential field diminish with increasing source-sensor distance is well known.
 Back-calculation can be made to predict the power of these frequencies at a smaller separation, and this is termed downward continuation \textcite{bullardDeterminationMassesNecessary1948,blakelyPotentialTheoryGravity1996}.
-The inverse using a larger distance is termed upward continuation, and is useful for reducing potentially unwanted near-surface magnetic detail, or levelling data to a common datum \parencite[e.g.\ open file magnetic data in Australia is available levelled to the AWAGS datum][]{mintyAirborneGeophysicalMapping2011}.
+The inverse calculation at a larger separation is termed upward continuation, and is useful for reducing potentially unwanted near-surface magnetic detail, or levelling data to a common datum (e.g.\ open file magnetic data in Australia are available levelled to the AWAGS datum \parencite{mintyAirborneGeophysicalMapping2011}).
 Downward continuation offers the benefit of high-resolution data from low-resolution sampling, and is therefore highly studied \parencite{zuoDownwardContinuationTransformation2020,fediStableDownwardContinuation2002,zhangNumericalSolutionsMeanValue2018,guoPotentialFieldContinuation2020,gangImprovedStableDownward2018,pilkingtonPotentialFieldContinuation2017}.
@@
 
-\section{Geophysics data in machine learning}
+\section{Geophysical data in machine learning}
 \label{sec:introdata}
@@
 Resulting from the processes described in \Cref{sec:introgrids}, geophysical rasters are highly distinct from the image data used widely in computer vision.
-This includes the number of channels (3 in natural images, 1 in aeromagnetics), range (255 compared to 50,000 or more), and anisotropy of resolution.
+This includes the number of channels (3 in natural images, 1 in aeromagnetics), range (\qty{255} discrete values compared to \qty{50000} or more), and anisotropy of resolution.
 Additionally, the features present within these data are highly dissimilar.
@@
 \subsection{Deep learning context}
-\label{sec:introml}
 Machine learning (ML) is a very broad family of techniques for learning functions from data.
@@
 A practical introduction to the practice of training machine learning is available from \textcite{stevensDeepLearningPyTorch2020}, while a more formal introduction is provided in \textcite{bishopPatternRecognitionMachine2006}.
-Many activation functions have been proposed, with the rectified linear unit (ReLU) being used in most tasks throughout this thesis.
-The activation function performs scaling but in many classes of activation function it also performs the important task of scaling the result to zero, which can be interpreted as the lack of a specific feature being present \parencite{williamsLogicActivationFunctions1986}.
-However, recent work on periodic activation functions such as the sinusoid \parencite{sitzmann2019siren} enable the networks used in Cref{ch:paper3}.
+
+The activation function performs scaling, but more importantly maps a range of input values to zero, which can be interpreted as the lack of a specific feature being present \parencite{williamsLogicActivationFunctions1986}.
+For example, the rectified linear unit (ReLU) used in most tasks throughout this thesis maps negative input values to zero, and linearly for positive values.
+Many activation functions have been proposed, and recent work on periodic activation functions such as the sinusoid \parencite{sitzmann2019siren} enable the networks used in \Cref{ch:paper3}.
+
 The other primary descriptor of a neural network is its architecture, referring to the configuration of its intermediate layers between the input and output.
-These architectures are described below.
-
+Key architectures used in this thesis are described below.
 If the network architecture provides the capacity to store and retrieve learning, the data and training architecture provide the actual instruction and delivery.
@@
 The current generation of deep learning is reported by review articles to have begun in 2006 \parencite{dengDeepLearningMethods2014,goodfellowDeepLearning2016a}, and has pervaded many industries and research fields.
-These review articles contain thorough background on the implementation and practice of various architectures for undertaking deep learing, as well as earlier machine learning or numerical models that can address tasks now approached with deep learning.
+These review articles contain thorough background on the implementation and practice of various architectures for undertaking deep learning, as well as earlier machine learning or numerical models that can address tasks now approached with deep learning.
 The deep learning tasks explored in this thesis are super-resolution (SR) for the objective of upsampling resolution enhancement, and implicit neural representation (INR).
@@
 Recently, CNNs have been surpassed by coordinate multilayer perceptron (CMLP) neural networks in some representation learning tasks, including SR \parencite{chenLearningContinuousImage2021}.
-CMLPs specifically use a dataset containing individual input points containing coordinate features, and train to predict individual output feature vectors at those coordinates \parencite[e.g.][]{mildenhallNeRFRepresentingScenes2020}.
+CMLPs specifically use a dataset containing individual input values corresponding to coordinate features, and train to predict individual output feature vectors at those coordinates \parencite[e.g.][]{mildenhallNeRFRepresentingScenes2020}.
 Key to the performance of these networks are implicit functions, which parameterise a function learned from training dataset with a neural network analogue.
@@
 Rock microscopy images have been upsampled with SR \parencite{niuInnovativeApplicationGenerative2020}, and their accuracy compared using domain specific parameter calculation.
-SR with physics informed learning has been performed by \textcite{bodeUsingPhysicsinformedEnhanced2021,jiangMeshfreeFlowNetPhysicsConstrainedDeep2020} in the field of fluid dynamics, \textcite{leongDeepBedMapDeepNeural2020} in the field of basement topography, and \textcite{jungbluthSingleframeSuperresolutionSolar2019} in astrophysics.
-Additionally, physics informed learning has been performed with multi-physics integration in \textcite{degen3DMultiphysicsUncertainty2022}.
+SR with physics-informed learning has been performed by \textcite{bodeUsingPhysicsinformedEnhanced2021,jiangMeshfreeFlowNetPhysicsConstrainedDeep2020} in the field of fluid dynamics, \textcite{leongDeepBedMapDeepNeural2020} in the field of basement topography, and \textcite{jungbluthSingleframeSuperresolutionSolar2019} in astrophysics.
+Additionally, physics-informed learning has been performed with multi-physics integration in \textcite{degen3DMultiphysicsUncertainty2022}.
 Seismic data has been investigated with SR \parencite{liSuperresolutionSeismicVelocity2021}, and with the removal of noise \parencite{liDeepLearningSimultaneous2021}.
@@
 Various potential field gridding \parencite{naprstekApplicationsMachineLearning2019,wangDeepLearningGravity2019a} and downward continuation methods \parencite{liStableDownwardContinuation2023,yeHighprecisionDownwardContinuation2022} have been proposed leveraging neural networks.
-Finally, in the recent topic of implicit representation there have been several applications proposed, including geological modelling \textcite{hillierGeoINRImplicitNeural2023}.
+Finally, in the recent topic of implicit representation there have been several applications proposed, including geological modelling \parencite{hillierGeoINRImplicitNeural2023}.
 
@@
 This thesis is presented as a series of papers which are published or in-preparation for publication.
-These are presented in Cref{ch:paper1,ch:paper2,ch:paper3}, each with a brief contextual introduction.
+These are presented in \Cref{ch:paper1,ch:paper2,ch:paper3}, each with a brief contextual introduction.
 Key findings and summary conclusions of the research are discussed in \Cref{ch:conclusions}.
 
-Cref{ch:paper1} presents published work on an initial investigation into the technique of deep learning super-resolution for magnetic potential field data.
+\Cref{ch:paper1} presents published work on an initial investigation into the technique of deep learning super-resolution for magnetic potential field data.
 To our knowledge, this chapter presents the first investigation of deep learning super-resolution of gridded magnetic potential field data within the literature.
-Two convolutional neural network models namely RDN and ESRGAN from the contemporary literature are implemented \parencite{zhangResidualDenseNetwork2018,limEnhancedDeepResidual2017}.
+Two convolutional neural network models, namely RDN and ESRGAN+, from the contemporary literature are implemented \parencite{zhangResidualDenseNetwork2018,limEnhancedDeepResidual2017}.
 With uncertainty on the amount of data required to train a SR model for magnetic grids, a dataset comprising readily available high- and low-resolution TMI grid pairs is formed using published state magnetic compilation maps of Western Australia \parencite{brett20MagneticMerged2020}.

### 2023-10-10 manuscript.tex
Update per DW feedback

@@
 
-This thesis reports on three bodies of work across two topics in geophysics; enhancing the high-frequency content of gridded potential field data using \emph{super-resolution}; and, learning a representative function of a potential field extent using \emph{implicit neural representation}.
+This thesis reports on three bodies of work across two topics in geophysics: enhancing the high-frequency content of gridded potential field data using \emph{super-resolution}; and, learning a representative function of a potential field extent using \emph{implicit neural representation}.
 The first topic enhances the value of geophysical surveys by predicting high-frequency components in sparsely sampled potential field grids.
@@
 \vfill{}
-\epigraph{\emph{All collected data had come to a final end. Nothing was left to be collected.}}{}
+\epigraph{\emph{All collected data had come to a final end. Nothing was left to be collected.} \dots}{}
 

### 2023-10-10 paper2.tex
Make compilable
Cleverref and subfiles seem to interact poorly, and I can't cref labels in external files in the way I had set up.

I've moved to using  \include.
Update per DW feedback

@@
-\documentclass[manuscript.tex]{subfiles}
-\begin{document}
-\setcounter{chapter}{2}
+% % \documentclass[manuscript.tex]{subfiles}
+% \documentclass[12pt,a4paper]{report} %,openright,twoside
+% \usepackage{thesisstyle}
+% \addbibresource{bib/PhD.bib}
+% % \setcounter{chapter}{2}
+% \begin{document}
+
 \title{Super-resolution of Aeromagnetic Survey Data}
@@
 \date{\today}
-\maketitle{}
+% \maketitle{}
 
@@
 Aerogeophysical grids are distinct from these image rasters due to the potential field sampling and grid interpolation process outlined in \Cref{sec:resinsurveys}, and the extent to which widely spaced low-resolution geophysical line data can be enhanced, and characteristics of the resulting super-resolved grids remain to be fully explored.
-Most critically, aeromagnetic data are highly sampled in the direction of flight lines but are under-sampled in the line perpendicular direction.
+Most critically, aeromagnetic data are highly sampled in the direction of flight lines but are under-sampled in the line-perpendicular direction.
 The resulting grid rasters may have isotropic cell size, but the frequency content in each axis is anisotropic, being a factor of the sampling frequency in the line-perpendicular (low) and line-parallel (high) directions.
@@
 \begin{figure}[hbt]
-    % \includegraphics[width=\textwidth]{fig/p2/image1.png}
+    \includegraphics[width=\linewidth]{fig/p2/temp_lte.png}
     \caption[The LTE network]{
@@
 It is important to note that while the HR grid has a cell size of \qty{20}{\m}, it is not equivalent to the \qty{20}{\m} cell size GT grid, because unsampled cells are interpolated during the gridding process.
-The result is a loss of high frequency detail in the line perpendicular direction, as well as the loss of features present only in the unsampled lines.
+The result is a loss of high frequency detail in the line-perpendicular direction, as well as the loss of features present only in the unsampled lines.
 
@@
 
-\begin{figure}[hbt]
-    % \includegraphics[width=\textwidth]{fig/p2/image1.png}
+\begin{figure}[hbt!]
+    \begin{center}
+        \includegraphics[width=0.75\linewidth]{fig/p2/temp_lr1.png}
+        \includegraphics[width=0.75\linewidth]{fig/p2/temp_lr2.png}
+    \end{center}
     \caption[Low-resolution geophysics grids]{
@@
 Due to the dynamic range of magnetic anomaly grids and the relative importance of structural accuracy for gridded data, image quality assessment such as peak signal-to-noise ratio or mean-squared error are an inadequate quantitative measure of upscaling performance for geophysics.
-In addition to mean-square error, Feature Similarity (FSIM) \parencite{linzhangFSIMFeatureSimilarity2011} is used to quantify the quality of the super-resolved image, because it is a full reference image similarity metric that quantifies structural similarity using phase and local gradient magnitude components.
-%TODO complain about FSIM
+In addition to mean-square error, FSIM \parencite{linzhangFSIMFeatureSimilarity2011} is used to quantify the quality of the super-resolved image.
+FSIM is a full reference image similarity metric that quantifies structural similarity, rather than individual cell values.
+%TODO complain about SSIM Structural Similarity (SIM) \parencite{wangImageQualityAssessment2004}
 
@@
 \label{sec:2results}
-It is seen that fine-tune training increases FSIM score for the task of super-resolution for aeromagnetic grids over the baseline model.
+Model performance is quantified using FSIM, and it is seen that fine-tune training increases FSIM score for the task of super-resolution for aeromagnetic grids over the baseline model.
+
+\begin{table}[hbt]
+    \includegraphics[width=\linewidth]{fig/p2/temp_tbl.png}
+    \begin{tabular}{ll}
+                   & Reserved Synthetic Dataset & Reserved Aeromagnetic Dataset \\
+                   & Mean / Standard Dev.       & Mean / Standard Dev.          \\
+        \hline{}
+        Baseline   & 0                          & 0                             \\
+        Fine-Tuned & 0                          & 0                             \\
+    \end{tabular}
+    \caption[Accuracy Metrics]{Accuracy metrics for each upsampling method. The best performing method for each metric is bolded.}
+    \label{tab:3metrics}
+\end{table}
+
 Qualitative results are shown to compare the outputs from the two models, the baseline model that is trained with synthetic data and the fine-tuned model trained with open access survey data.
@@
 \begin{figure}[hbt]
-    \includegraphics[width=\textwidth]{fig/p2/srcomp_23.pdf}
+    \includegraphics[width=0.9\linewidth]{fig/p2/srcomp_23.pdf}
     \caption[Super-resolution geophysics grid results]{Super-resolution predictions on open access data, prepared using the proposed method.
@@
 \begin{figure}[hbt]
-    \includegraphics[width=\textwidth]{fig/p2/srcomp_14.pdf}
+    \includegraphics[width=0.9\linewidth]{fig/p2/srcomp_14.pdf}
     \caption[Super-resolution geophysics grid results]{Super-resolution predictions on open access data, prepared using the proposed method.
@@
 \begin{figure}[hbt]
-    \includegraphics[width=\textwidth]{fig/p2/srcomp_17.pdf}
+    \includegraphics[width=0.9\linewidth]{fig/p2/srcomp_17.pdf}
     \caption[Super-resolution geophysics grid results]{Super-resolution predictions on open access data, prepared using the proposed method.
@@
 \begin{figure}[hbt]
-    \includegraphics[width=\textwidth]{fig/p2/srcomp_18.pdf}
+    \includegraphics[width=0.9\linewidth]{fig/p2/srcomp_18.pdf}
     \caption[Super-resolution geophysics grid results]{Super-resolution predictions on open access data, prepared using the proposed method.

### 2023-10-10 paper3.tex
Spell check and adjust chapter structure
Make compilable
Cleverref and subfiles seem to interact poorly, and I can't cref labels in external files in the way I had set up.

I've moved to using  \include.
Update per DW feedback

@@
-\documentclass[manuscript.tex]{subfiles}
-\begin{document}
-% \setcounter{chapter}{1}
+% % \documentclass[manuscript.tex]{subfiles}
+% \documentclass[12pt,a4paper]{report} %,openright,twoside
+% \usepackage{thesisstyle}
+% \addbibresource{bib/PhD.bib}
+% % \setcounter{chapter}{3}
+% \begin{document}
+
 \title{Implicit Neural Representation for Potential Field Geophysics}
@@
     \centering{}
-    \includegraphics[width=1.0\linewidth]{fig/p3/P864_grid_comparison_35m.pdf}
-    \caption[Grid prediction outside the nominal altitude]{A constant level grid queried from the INR at the height of \qty{35}{\m} (middle).}
+    \includegraphics[width=1.0\linewidth]{fig/p3/35_level_grid.pdf}
+    \caption[Grid prediction outside the nominal altitude]{A constant level grid queried from the INR at the height of \qty{35}{\m}.}
     % AWAGS is 80 m, but we see nothing useful at 80m
@@
 
-Inspired by the approach of \textcite{raissiPhysicsinformedNeuralNetworks2019}, a geophysics informed network could include a Laplace criterion,
+Inspired by the approach of \textcite{raissiPhysicsinformedNeuralNetworks2019}, a geophysics-informed network could include a Laplace criterion,
 \begin{equation}

### 2023-10-10 paper3.tex
Fix non-compiling due to underscore in label
Maybe because I switched to Lualatex, this showed up?

@@
 
-\label{sec:geo_physics}
+% \label{sec:geo_physics}
 Magnetic and gravitational fields in geophysics are conservative vector fields but are typically sampled as a scalar potential field in a single direction.
@@
 \section{Method}
-
 \subsection{Data}
@@
 \begin{figure}[hbt]
-    \centering{}
+    \centering
     \includegraphics[width=0.5\linewidth]{fig/p3/loss_plot.pdf}
@@
 \begin{figure}[hbt]
-    \centering{}
+    \centering
     \includegraphics[width=1.0\linewidth]{fig/p3/P864_grid_comparison_40m.pdf}
@@
 \begin{figure}[hbt]
-    \centering{}
+    \centering
     \includegraphics[width=1.0\linewidth]{fig/p3/35_level_grid.pdf}
@@
 For comparison, the derivatives calculated with AD are compared with numerical derivatives calculated on the level grid queried from the same INR model.
-While horizontal derivatives queried from the INR correspond well to numerical derivatives calculated on the \qty{40}{\m} level grid in \Cref{fig:hori_grad}, the vertical derivative suffers poor performance (\Cref{fig:vert_grad}).
+While horizontal derivatives queried from the INR correspond well to numerical derivatives calculated on the \qty{40}{\m} level grid in \Cref{fig:horigrad}, the vertical derivative suffers poor performance (\Cref{fig:vertgrad}).
 This correlates with the poor continuation performance of model when predicting level grids several metres or more beyond the nominal sample height.
 This is interpreted as the presented model having a limited capacity to extrapolate, and learning a poor representation of the vertical component of the potential field, which we further discuss in \Cref{sec:3discussion}
-
 \begin{figure}[hbt]
@@
         Residuals are calculated between the numerical and AD gradient grids (right column).}
-    \label{fig:hori_grad}
+    \label{fig:horigrad}
 \end{figure}
@@
      The proposed method has poor vertical gradient representation, possibly due to the nature of aeromagnetic survey design.}
-    \label{fig:vert_grad}
+    \label{fig:vertgrad}
 \end{figure}
@@
 \begin{equation}
-    \label{eqn:cri_laplace}
+    \label{eqn:crilaplace}
     \mathcal{L}_{PDE} = \frac{1}{S_i}\sum_{i=1}^{S_i} \left(\frac{\partial{}^2f}{\partial{}x^2} + \frac{\partial{}^2f}{\partial{}y^2} + \frac{\partial{}^2f}{\partial{}z^2}\right)^2,
@@
 %     \caption[Menzies INR]{Level grid representation using minibatch gradient descent.}
-%     \label{fig:vert_grad}
+%     \label{fig:vertgrad}
 % \end{figure}

### 2023-10-10 paper2.tex
Toward fixing paper 2
Uncomment that table at your own peril

@@
 \begin{figure}[hbt!]
-    \begin{center}
+    \centering
     \includegraphics[width=0.75\linewidth]{fig/p2/temp_lr1.png}
     \includegraphics[width=0.75\linewidth]{fig/p2/temp_lr2.png}
-    \end{center}
     \caption[Low-resolution geophysics grids]{
@@
 \label{sec:2results}
-Model performance is quantified using FSIM, and it is seen that fine-tune training increases FSIM score for the task of super-resolution for aeromagnetic grids over the baseline model.
+Model performance is quantified using FSIMi in Cref{tab:2metrics}, and it is seen that fine-tune training increases FSIM score for the task of super-resolution for aeromagnetic grids over the baseline model.
 
-\begin{table}[hbt]
-    \includegraphics[width=\linewidth]{fig/p2/temp_tbl.png}
-    \begin{tabular}{ll}
-                   & Reserved Synthetic Dataset & Reserved Aeromagnetic Dataset \\
-                   & Mean / Standard Dev.       & Mean / Standard Dev.          \\
-        \hline{}
-        Baseline   & 0                          & 0                             \\
-        Fine-Tuned & 0                          & 0                             \\
-    \end{tabular}
-    \caption[Accuracy Metrics]{Accuracy metrics for each upsampling method. The best performing method for each metric is bolded.}
-    \label{tab:3metrics}
-\end{table}
+% \begin{table}[hbt]
+% %     % \includegraphics[width=\linewidth]{fig/p2/temp_tbl.png}
+% % \begin{tblr}{ll}
+% %                 & Reserved Synthetic Dataset & Reserved Aeromagnetic Dataset \\
+% %                 & Mean / Standard Dev.       & Mean / Standard Dev.          \\
+% %     \hline{}
+% %     Baseline   & 0                          & 0                             \\
+% %     Fine-Tuned & 0                          & 0                             \\
+% % \end{tblr}
+%     \caption[Accuracy Metrics]{Accuracy metrics for each upsampling method. The best performing method for each metric is bolded.}
+%     \label{tab:2metrics}
+% \end{table}
 

### 2023-10-10 discussion.tex
Add short headings to suit ToC

@@
 
-\section{SR impact on interpretation}
+\section[Super-resolution impact on interpretation]{SR impact on interpretation}
 The super-resolution outputs from the methods presented in this thesis have improved structural accuracy over the low-resolution grids.
@@
 
-\section{SR model construction}
+\section[Super-resolution model construction]{SR model construction}
 Several models were implemented throughout \Cref{ch:paper1,ch:paper2}, namely RDN, ESRGAN+, and LTE\@.

### 2023-10-10 intro.tex
Add short headings to suit ToC

@@
 
-\section{Traditional methods for enhancing resolution}
+\subsection{Traditional methods for enhancing resolution}
 As outlined in \Cref{sec:introgrids}, resolution is a product of sample distance and density, and gridded rasters have a specific number of cells in each axis depending on the spatial extent.
@@
 
-\section{Geophysical data in machine learning}
+\section{Geophysics and machine learning}
 \label{sec:introdata}
@@
 
-\section{Machine learning in geoscience}
+\subsection{Machine learning in geoscience}
 \label{sec:introgeoml}

### 2023-10-10 paper2.tex
Add short headings to suit ToC

@@
 
-\subsection{Quantitative Measure}
+\section{Results}
+\label{sec:2results}
+\subsubsection{Quantitative Measure}
 Due to the dynamic range of magnetic anomaly grids and the relative importance of structural accuracy for gridded data, image quality assessment such as peak signal-to-noise ratio or mean-squared error are an inadequate quantitative measure of upscaling performance for geophysics.
@@
 %TODO complain about SSIM Structural Similarity (SIM) \parencite{wangImageQualityAssessment2004}
-
-\section{Results}
-\label{sec:2results}
 Model performance is quantified using FSIMi in Cref{tab:2metrics}, and it is seen that fine-tune training increases FSIM score for the task of super-resolution for aeromagnetic grids over the baseline model.
@@
 
-\section{Conclusion}
+\section{Conclusions}
 \label{sec:2conclusion}

### 2023-10-10 paper3.tex
Add short headings to suit ToC

@@
 
-\section{Automatic Differentiation}
+\subsection{Automatic Differentiation}
 Automatic differentiation (AD) refers to one of several methods for computing derivatives, specifically to the method of accumulating derivatives during function evaluation \parencite{baydinAutomaticDifferentiationMachine2018}.

### 2023-10-11 discussion.tex
Update per DW comments, part 2

--- 2023-10-10 discussion.tex
@@
 The SR method however does not consider these constraints, because imputation is purely based on features extractable by the model.
-This was demonstrated to introduce noise or artefacts during SR inference, as well as the incorrect enhancement of artifacts in low-resolution data such as aliased geological strike.
+This was demonstrated to introduce noise or artefacts during SR inference, as well as the incorrect enhancement of artefacts in low-resolution data such as aliased geological strike.
 However, given the uncertainty of geological interpretation of geophysics data \parencite{sivarajahIdentifyingEffectiveInterpretation2013} SR outputs may be used as an auxiliary data when interpreting low-resolution magnetic features.
@@
 \begin{enumerate}
-    \item{} Exploring the outcomes from the use of SR in the task of geological mapping
-    \item{} Understanding the impact of choices in constructing a model and dataset for SR geophysics for a range of geological domains,
-    \item{} Identifying an improved image quality assessment for gridded potential field data.
-    \item{} Investigating the use of a physics-informed approach for SR and implicit representation, and,
+    \item{} Exploring the impact on geological mapping from the use of SR,
+    \item{} Understanding the impact of choices in training super-resolution for domain specific tasks,
+    \item{} Identifying an improved image quality assessment for gridded potential field data and,
+    \item{} Investigating the use of a physics-informed approach for SR and implicit representation.
 \end{enumerate}
 
-\section{SR impact on interpretation}
+\section[Super-resolution impact on geological interpretation]{Super-resolution impact on geological interpretation}
 The super-resolution outputs from the methods presented in this thesis have improved structural accuracy over the low-resolution grids.
@@
 
-\section{SR model construction}
+\section[Super-resolution for domain specific tasks]{A structured approach to training super-resolution for domain specific tasks}
 Several models were implemented throughout \Cref{ch:paper1,ch:paper2}, namely RDN, ESRGAN+, and LTE\@.
 % However, the most important choice in developing a performant super-resolution neural network for real-world aeromagnetic survey data was the choice of training data.
-\Cref{ch:paper1} was prepared prior the release of a large and varied synthetic geology training dataset \parencite{jessellNoddyverseMassiveData2022}.
+The work in \Cref{ch:paper1} was prepared for publication prior the release of a large and varied synthetic geology training dataset \parencite{jessellNoddyverseMassiveData2022}.
 It was seen in \Cref{ch:paper2} that this data improved model performance for a range of features by using transfer learning for pre-training.
@@
 
-Magnetic data in different geological contexts are subject to a mixture of statistical distributions, \parencite{khokhlovCauseNonGaussianDistribution2017}.
+Magnetic data in different geological contexts are subject to a mixture of statistical distributions \parencite{khokhlovCauseNonGaussianDistribution2017}.
 Investigation is also required to identify a robust normalisation method accounting for dynamic range and the structural significance contained in the long tails of the distributions of magnetic intensities.
@@
 
-\section{Physics-informed neural networks}
+\section{Geophysics-informed neural networks}
 Potential fields are constrained by several well understood physical laws, and gridded data ideally conform to these properties for use in inversion applications and further numerical processing.
@@
 
-To the best of my knowledge, \Cref{ch:paper1} presents the first investigation in the literature of super-resolution enhancement of gridded aerogeophysical data.
+To the best of my knowledge, \Cref{ch:paper1} presents the first investigation in the literature of the super-resolution enhancement of gridded aerogeophysical data.
 Prior to this work, it was unknown how well SR methods developed for natural images in computer vision research would adapt to the features present within magnetic grids, or the challenges faced in developing a training dataset for these data.
@@
 Hence, the method based on RDN was preferred.
-We identified the need for sufficient representative training data, and a realistic method to generate low-resolution training data.
+We identified the need for additional representative training data to investigate transferability of the method to other geological domains, and a realistic method to generate low-resolution training data.
 
@@
 The contribution in \Cref{ch:paper3} used coordinate multilayer perceptron neural networks to learn a representation of the function that describes a surveyed potential field extent.
-To my knowledge, this is the first time implicit neural representation has been reported for use with aerogeophysical survey data in the literature.
+To my knowledge, this is the first time implicit neural representation of aerogeophysical survey data has been reported in the literature.
 These networks are highly suited for processing spatial data such as point sampled geophysics surveys.
@@
 By commencing the methods from point sample data, the number of individual processing steps is reduced, and the application is fully trainable.
-Coordinate MLPs for implicit representation are a currently burgeoning field of research in computer science, and we identify opportunities in extending advances in this research to future applications in geophysics, as outlined in \Cref{ch:futurework}.
+Continued advances in the recent field of Coordinate MLPs will improve the capacity of the method for representing high-resolution aeromagnetic data. 
+We identify opportunities in \Cref{ch:futurework} for future work in super-resolution and implicit representation for enhancing potential field methods in geophysics.
 

### 2023-10-11 paper1.tex
Spell check and adjust chapter structure
Make compilable
Cleverref and subfiles seem to interact poorly, and I can't cref labels in external files in the way I had set up.

I've moved to using  \include.
Update per DW feedback
Update per DW comments, part 2

@@
-\documentclass[manuscript.tex]{subfiles}
-\begin{document}
-% \setcounter{chapter}{1}
+% % \documentclass[manuscript.tex]{subfiles}
+% \documentclass[12pt,a4paper]{report} %,openright,twoside
+% \usepackage{thesisstyle}
+% \addbibresource{bib/PhD.bib}
+% % \setcounter{chapter}{1}
+% \begin{document}
+
 \title{Magnetic grid resolution enhancement using machine learning: A case study from the Eastern Goldfields Superterrane}
@@
 \date{2022-09-21}
-\maketitle{}
+% \maketitle{}
 
@@
 
-\begin{figure}[hbt]
+\begin{figure}[hbtp]
     \includegraphics[width=\linewidth]{fig/p1/lrandhr.jpg}
@@
 Adversarial training of upsampling networks can help in learning a better model for the task at hand.
-For example, ESRGAN uses an analogous upsampling network design to RDN (Residual Dense Network) \Cref{fig:rdn}, with the addition of a discriminator network.
+For example, ESRGAN uses an analogous upsampling network design to RDN (Residual Dense Network) shown in \Cref{fig:rdn}, with the addition of a discriminator network.
 This will be further discussed in \Cref{sec:nnsr}.
-For a review on super-resolution networks, the reader is referred to \cite{anwarDeepJourneySuperresolution2020}.
+For a review on super-resolution networks, the reader is referred to \textcite{anwarDeepJourneySuperresolution2020}.
 
@@
 
-\begin{figure}[hbt]
+\begin{figure}[hbtp]
     \includegraphics[width=\linewidth]{fig/p1/rdn.png}
@@
         Upsampling to the target output size is performed after the main convolution sequence.
-        Adapted from \cite{wangESRGANEnhancedSuperresolution2018}.
+        Adapted from \textcite{wangESRGANEnhancedSuperresolution2018}.
     }
@@
 Resolution enhancement in potential field geophysics (occasionally referred to as downward continuation in this context) is performed numerically.
-\cite{chenPotentialFieldData2022} use Taylor series expansion, while \cite{xuGravityAnomalyReconstruction2019} interpolate randomly sampled gravity point data using the nonequispaced Discrete Fourier Transform (nDFT), which leverages compressed sensing theory \parencite{candesIntroductionCompressiveSampling2008}.
+\Textcite{chenPotentialFieldData2022} use Taylor series expansion, while \textcite{xuGravityAnomalyReconstruction2019} interpolate randomly sampled gravity point data using the nonequispaced Discrete Fourier Transform (nDFT), which leverages compressed sensing theory \parencite{candesIntroductionCompressiveSampling2008}.
 While high quality results from under sampled data are attained with the non-equispaced Discrete Fourier Transform, the grid line sampling methodology of airborne geophysical surveys is highly regular, and unlikely to satisfy the coherency constraints required for compressive sensing.
@@
 
-\begin{figure}[hbt]
+\begin{figure}[hbtp]
     \includegraphics[width=\linewidth]{fig/p1/rdb.png}
@@
         Noise injection is not used in RDN\@.
-        Adapted from \cite{rakotonirinaESRGANFurtherImproving2020}.
+        Adapted from \textcite{rakotonirinaESRGANFurtherImproving2020}.
     }
@@
 
-\begin{figure}[hbt]
+\begin{figure}[hbtp]
     \includegraphics[width=\linewidth]{fig/p1/convs.png}
@@
 LReLU refers to the Leaky-ReLU activation function.
-Adapted from \cite{rakotonirinaESRGANFurtherImproving2020}.}
+Adapted from \textcite{rakotonirinaESRGANFurtherImproving2020}.}
     \label{fig:convs}
@@
 
-ESRGAN+, based on ESRGAN \parencite{wangESRGANEnhancedSuperresolution2018}, was chosen as the primary super-resolution CNN architecture for this task due to its reported success in other super-resolution tasks (especially \cite{bodeUsingPhysicsInformedSuperResolution2019} and \cite{leongDeepBedMapDeepNeural2020}) and state of the art results for its original application in image super-resolution.
+ESRGAN+, based on ESRGAN \parencite{wangESRGANEnhancedSuperresolution2018}, was chosen as the primary super-resolution CNN architecture for this task due to its reported success in other super-resolution tasks (especially \textcite{bodeUsingPhysicsInformedSuperResolution2019} and \textcite{leongDeepBedMapDeepNeural2020}) and state of the art results for its original application in image super-resolution.
 As a Generative Adversarial Network (GAN), it comprises two iteratively trained neural networks, a Generator (G) used to upscale low-resolution inputs, and Discriminator (D), which is trained to improve the performance of the generator.
@@
 
-\begin{figure}[hbt]
+\begin{figure}[hbtp]
     \centering{}
@@
 Following the generator implementation from ESRGAN+, twenty-three Residual Dense Blocks were ordered sequentially to form the main network, followed by two nearest neighbour upsampling filters at two times scale each.
-The ESRGAN+ discriminator followed that of \cite{rakotonirinaESRGANFurtherImproving2020} which is an implementation of a VGG style classification network \parencite{simonyanVeryDeepConvolutional2015}.
+The ESRGAN+ discriminator followed that of \textcite{rakotonirinaESRGANFurtherImproving2020} which is an implementation of a VGG style classification network \parencite{simonyanVeryDeepConvolutional2015}.
 For ESRGAN+ the peak learning rate was \num{6e-4}, and the feature loss, pixel loss (MAE), and adversarial loss parameters were weighted at \num{1}, \num{0.01}, and \num{0.005} respectively.
@@
 
-\begin{figure}[hbt]
+\begin{figure}[hbtp]
     \includegraphics[width=\linewidth,trim={0 0 0 5mm},clip]{fig/p1/resultsvis.png}
@@
 
-\begin{figure}[hbt]
+\begin{figure}[hbtp]
     \includegraphics[width=\linewidth,trim={0 10mm 0 5mm},clip]{fig/p1/residuals.png}
@@
 
-\begin{figure}[hbt]
+\begin{figure}[hbtp]
     \includegraphics[width=\linewidth]{fig/p1/rapsd.jpg}
@@
 
-\begin{figure}[hbt]
+\begin{figure}[hbtp]
     \includegraphics[width=\linewidth]{fig/p1/filtered.png}
@@
 
-\begin{figure}[hbt]
+\begin{figure}[hbtp]
     \includegraphics[width=\linewidth,trim={0 0 0 0},clip]{fig/p1/jhillvis.jpg}
@@
 
-\begin{figure}[hbt]
+\begin{figure}[hbtp]
     \includegraphics[width=\linewidth,trim={0 0 0 5mm},clip]{fig/p1/jhilldykes.png}
@@
 Based on this, RDN\textdaggerdbl{} shows the best performance for super-resolution CNN upsampling of magnetic grids, to assist in the interpretation of low-resolution grids.
-The deep learning methods used here can be trained with data from other geospatial extents, either from scratch or by initialising the training with pre-existing model weights \parencite[][e.g.]{wangMineGANEffectiveKnowledge2020}.
+The deep learning methods used here can be trained with data from other geospatial extents, either from scratch or by initialising the training with pre-existing model weights \parencite[e.g.][]{wangMineGANEffectiveKnowledge2020}.
 The existing models can also be applied to other extents of \qty{80}{\metre} TMI grids without further training.
@@
 This applies also to grids that do not have a cell size of \qty{80}{\metre}.
-An example use case for either the method or trained models is super-resolving the Total Magnetic Intensity (TMI) Grid of Australia 2019 - seventh edition which is published by Geoscience Australia in only \qty{80}{\metre} and \qty{40}{\metre} cell size.
+An example use case for either the method or trained models is super-resolving the Total Magnetic Intensity (TMI) Grid of Australia 2019 --- seventh edition which is published by Geoscience Australia in only \qty{80}{\metre} and \qty{40}{\metre} cell size.
 The trained \qty{80}{\metre} models in this work could be applied to the \qty{80}{\metre} TMI grid, or the method used with existing state map data to train a two times scale model to super-resolve the \qty{40}{\metre} grid to \qty{20}{\metre}.

### 2023-10-11 paper2.tex
Update per DW comments, part 2

@@
     Moreover, the structural variation within the survey data depends entirely on the geological domain which is surveyed.
-    This paper proposes an approach to super-resolution of aeromagnetic survey data that uses realistic high-resolution and low-resolution pairs of gridded survey data, obtained by densely and sparsely `sampling' forward modelled magnetic grids from a suite of synthetic geological models.
-    The model then incorporates real-world survey data to improve accuracy through a secondary fine-tuning step, using a non-standard low-resolution transform that incorporates the survey line structure of the underlying data.
+    This paper proposes an approach to super-resolution of aeromagnetic survey data using transfer learning from synthetic data that represents a wide range of realistic geological domains, to imrpove the generalisability of the resulting model.
+    The approach uses realistic high-resolution and low-resolution pairs of gridded survey data, obtained by simulating aeromagnetic surveys of the data at close and wide line spacings.
+    Structural accuracy of the method is improved using a secondary fine-tuning stage incorporating real-world survey data.
     The Local Texture Estimator neural network architecture was used, and qualitative and quantitative measures of the super-resolution performance are reported.
@@
 Gridding at a finer cell size preserves higher frequencies present in the sampled data, resulting in greater detail.
-This resolvable detail is termed resolution, and high-resoluton details better define structures apparent in the data which are contextually important to interpretation.
+This resolvable detail is termed resolution, and high-resolution details better define structures apparent in the data which are contextually important to interpretation.
 When the cell size covers a quantified distance, the smallest resolvable detail can be expressed in terms of wavelength.
-This is the grids Nyquist wavelength, and is equal to twice the gridded cell size.
-This is also known as the Nyquist frequency, the well-known limit at which bandwidth-limited signals may be incorrectly resolved due to sampling below the Nyquist frequency, at half the sampling frequency.
+This is the grid's Nyquist wavelength, and is equal to twice the gridded cell size.
+This corresponds to the widely known Nyquist frequency, i.e.\ the limit at which bandwidth-limited signals may be incorrectly resolved due to sampling below the Nyquist frequency, at half the sampling frequency.
 For example, a potential field which lacks significant wavelength components shorter than \qty{200}{\m} will be adequately resolved by a grid with a cell size of \qty{100}{\m}, without spurious features known as aliasing.
@@
 This assists example-based methods by using a larger source dataset which shares properties with the target dataset.
-In order to improve the generalisation of an example-based neural network for regions without high-resolution coverage, we propose transfer learning \parencite{tanSurveyDeepTransfer2018} using a baseline model trained with synthetic data containing a broad set of geological domains, which is then fine-tuned with high-resolution survey grid data.
+In order to improve the generalisation of an example-based neural network for regions without high-resolution coverage, we propose transfer learning \parencite{tanSurveyDeepTransfer2018} by first training a baseline model trained with synthetic data containing a broad set of geological domains, which is then fine-tuned with high-resolution survey grid data.
 The synthetic geophysical data \parencite{jessellNoddyverseMassiveData2022} are forward modelled from 3D petrographic voxel models with varied geological histories.
@@
 
-Thus, the approach made in this study to address the challenges of training an example-based model with limited suitable geophysical data is to make use of geologically diverse synthetic data, with a realistic sampling and gridding method to generate low-resolution data.
+Thus, the approach made in this study to address the challenges of training an example-based model with limited suitable geophysical data is to make use of geologically diverse synthetic data, with a realistic sampling and gridding method to generate low-resolution data for training.
 
@@
 Downward continuation can be performed with field- or source-based methods \parencite{pilkingtonPotentialFieldContinuation2017}.
-Resolution enhancement through neural network approaches to downward continuation \parencite{liStableDownwardContinuation2023,yeHighprecisionDownwardContinuation2022} is a promising research direction in super-resolution geophysics, but is distinct from the proposed line-spacing based method due to its use of paired vertically continued training data rather than paired line spacing differing data.
+Resolution enhancement through neural network approaches to downward continuation \parencite{liStableDownwardContinuation2023,yeHighprecisionDownwardContinuation2022} is a promising research direction in super-resolution geophysics, but is distinct from the proposed line-spacing based method due to its use of paired vertically continued training data.
 
@@
 Both methods operate on regional aeromagnetic data at four times scale, using variants of the SRGAN convolutional neural network originally by \textcite{ledigPhotorealisticSingleImage2017}.
-The method of \textcite{smithMagneticGridResolution2022} compared SR to numerical upsampling methods such as the bicubic filter, and is capable of accurately upsampling low-resolution magnetic textures by predicting short wavelengths.
-However, the low-resolution data were created using a polynomial filter that supressed high frequencies, rather than a real-world low-resolution geophysical sampling process.
+The method of \textcite{smithMagneticGridResolution2022} demonstated SR methods are capable of upsampling low-resolution magnetic textures and predicting accurate short wavelengths for these data.
+Comparison was made compared with numerical filters such as the bicubic filter.
+However, the low-resolution data were created using a polynomial filter that suppressed high frequencies, rather than a real-world low-resolution geophysical sampling process.
 The method of \textcite{bavandsavadkoohiHighresolutionAeromagneticMap2023} uses low- and high-resolution aeromagnetic data from regional surveys, with a realistic low-resolution transform from line spacing and sample altitude differences.
 The dataset contains \qty{267} sample grids from surveys in Quebec, Canada, prepared from surveys with a low-resolution line spacing of \qty{800}{\m}.
-The proposed method is distinct from these prior works with its use of synthetic data in coordination with real survey data to improve generalisation for regional aeromagnetics in Australia, and the use of a modern MLP-based SR network.
+The proposed method is distinct from these prior works with its use of extensive and geologically varied synthetic data in coordination with real survey data to improve generalisation for regional aeromagnetics in Australia, and the use of a modern MLP-based SR network.
 
@@
 
-We propose a method that simulates the line sampling of both synthetic and real data, thereby more closely reflecting a real-world geophysical low-resolution transform, at scales typical of those in exploration in Australia.
+We propose a method that simulates the line sampling of both synthetic and real data, thereby more closely reflecting real-world low-resolution aeromagnetic data, at scales typical of those in exploration in Australia.
 
@@
 
-LTE \parencite{leeLocalTextureEstimator2022} is implemented in this work for its higher performance in the task of image super-resolution.
+Local texture estimator (LTE) \parencite{leeLocalTextureEstimator2022} is implemented in this work for its higher performance in the task of image super-resolution.
 The encoder in LTE can use the feature extraction capability of traditional SR CNNs such as EDSR \parencite{limEnhancedDeepResidual2017} or RDN \parencite{zhangResidualDenseNetwork2018}, or a SwinIR \parencite{liangSwinIRImageRestoration2021} transformer-based encoder.
@@
 An overview of the structure of the LTE network is shown in \Cref{fig:ltenet}.
-The LTE component of the LTE network transforms the encoded latent features to frequency and amplitude features using trainable convolutions.
-Both the amplitude and frequency features are then upsampled using nearest neighbour filter interpolation.
-The frequency components are combined with phase information, which is extracted from the input by an additional MLP, and the resulting features are passed through a sinusoidal activation function before being combined with the amplitude features.
-Finally, the decoding MLP restores these frequency domain features to the spatial image domain.
-To precondition the network toward learning high-resolution features, a long-range skip connection with bilinear upscaling passes low-resolution content common between the upsampled LR and the HR counterpart to the output of the MLP\@.
 Specifics of the LTE implementation to investigate the performance of SR for geophysical grids from a range of geological domains are detailed in \Cref{sec:2lte}.
 
-\begin{figure}[hbt]
+\begin{figure}[hbtp]
     \includegraphics[width=\linewidth]{fig/p2/temp_lte.png}
@@
 This is based on the Noddyverse \parencite{jessellNoddyverseMassiveData2022}, a suite of one million geologically realistic petrophysical voxel models with accompanying forward modelled geophysics.
-The block models are constructed as a sequence of realistic geological histories with an initial stratigraphy and tilt, followed by a three randomly selected deformation events of fold, fault, unconformity, dyke, plug, shear-zone, or tilt.
+The block models are constructed as a sequence of realistic geological histories with an initial stratigraphy and tilt, followed by three randomly selected deformation events of fold, fault, unconformity, dyke, plug, shear-zone, or tilt.
 Each model in the suite records the parameters of the deformation history, the complete final 3D subsurface geology voxel model with associated petrophysics, and final forward models of the magnetic and gravity potential fields.
@@
 \label{sec:simsurveys}
-To simulate the acquisition of aeromagnetic data, the \qtyproduct{20 x 20}{\m} total magnetic intensity (TMI) forward models are line sampled at a factor of \(4n\)  (i.e., \(4n \times 20\) m sampling in x, \(1 \times 20\) m sampling in y).
+To simulate the acquisition of aeromagnetic data, the \qtyproduct{20 x 20}{\m} total magnetic intensity (TMI) forward models are line sampled at a factor of \(4n\)  (i.e., \(4n \times 20\) m sampling in \(x\), \(1 \times 20\) m sampling in \(y\)).
 The line direction is nominally ``North-South'' such that entire array columns are sampled or unsampled.
@@
 This method of generating low-resolution training data is distinct from computer-vision image super-resolution, where a three-channel colour image is downsampled using an interpolating filter such as nearest neighbour or cubic splines operating on all pixels in the original image.
-It is also distinct from previous geophysical deep-learning super-resolution work \textcite{smithMagneticGridResolution2022} where the raster data used are extracts from regional compilation TMI maps, created using a third order Newton polynomial filter, similar in effect to cubic spline interpolation.
+It is also distinct from previous geophysical deep-learning super-resolution work \parencite{smithMagneticGridResolution2022} where the raster data used are extracts from regional compilation TMI maps, created using a third order Newton polynomial filter, similar in effect to cubic spline interpolation.
 The downsampling method used here is representative of low-resolution airborne sampling and subsequent gridding processes in real world geophysics.
@@
 
-\begin{figure}[hbt!]
+\begin{figure}[hbtp!]
     \centering
@@
 
-\subsection{Synthetic baseline training setup}
+\subsection{Baseline training with synthetic data}
 \label{sec:baseline}
@@
 Local Texture Estimator \parencite{leeLocalTextureEstimator2022} is implemented to super-resolve synthetic and real potential field geophysical data with low resolution resulting from line spacing.
+The LTE component of the LTE network transforms the encoded latent features to frequency and amplitude features using trainable convolutions.
+Both the amplitude and frequency features are then upsampled using nearest neighbour filter interpolation.
+The frequency components are combined with phase information, which is extracted from the input by an additional MLP, and the resulting features are passed through a sinusoidal activation function before being combined with the amplitude features.
+Finally, the decoding MLP restores these frequency domain features to the spatial image domain.
+To precondition the network toward learning high-resolution features, a long-range skip connection with bilinear upscaling passes low-resolution content common between the upsampled LR and the HR counterpart to the output of the MLP\@.
 Because total magnetic intensity data are single channel, the input and output channel count are set to one.
@@
 \subsubsection{Quantitative Measure}
-Due to the dynamic range of magnetic anomaly grids and the relative importance of structural accuracy for gridded data, image quality assessment such as peak signal-to-noise ratio or mean-squared error are an inadequate quantitative measure of upscaling performance for geophysics.
+Due to the dynamic range of magnetic anomaly grids and the relative importance of structural accuracy for gridded data, image quality assessment methods typically used for RGB images such as peak signal-to-noise ratio or mean-squared error are an inadequate quantitative measure of upscaling performance for geophysics.
 In addition to mean-square error, FSIM \parencite{linzhangFSIMFeatureSimilarity2011} is used to quantify the quality of the super-resolved image.
@@
 
-% \begin{table}[hbt]
+% \begin{table}[hbtp]
 % %     % \includegraphics[width=\linewidth]{fig/p2/temp_tbl.png}
@@
 
-\begin{figure}[hbt]
+\begin{figure}[hbtp]
     \includegraphics[width=0.9\linewidth]{fig/p2/srcomp_23.pdf}
@@
 
-\begin{figure}[hbt]
+\begin{figure}[hbtp]
     \includegraphics[width=0.9\linewidth]{fig/p2/srcomp_14.pdf}
@@
 
-\begin{figure}[hbt]
+\begin{figure}[hbtp]
     \includegraphics[width=0.9\linewidth]{fig/p2/srcomp_17.pdf}
@@
 
-\begin{figure}[hbt]
+\begin{figure}[hbtp]
     \includegraphics[width=0.9\linewidth]{fig/p2/srcomp_18.pdf}
@@
 An approach for upscaling geologically diverse geophysical survey grid data is proposed, which adopts transfer learning from synthetic data to better generalise super-resolution across different geological domains.
-Using the preeminent LTE neural network, synthetic magnetic forward models were used to prepare a baseline model capable of upscaling survey grids at four times scale.
+Using the preeminent LTE neural network architecture, synthetic magnetic forward models were used to prepare a baseline model capable of upscaling survey grids at four times scale.
 Further, this baseline model was fine-tuned with open access survey grid data, prepared with a low-resolution transform appropriate for aeromagnetic geophysics.

### 2023-10-11 paper3.tex
Update per DW comments, part 2

@@
 Geophysical potential fields are routinely collected and used to assist the understanding of the subsurface for geoscience and mineral exploration.
-When surveying these fields, which are continuous functions in three dimensions, sample locations are scattered in x, y, and z, despite best efforts to conform to a regularly spaced line or grid acquisition plan.
+When surveying these fields, which are continuous functions in three dimensions, sample locations are scattered in \(x\), \(y\), and \(z\), despite best efforts to conform to a regularly spaced line or grid acquisition plan.
 These scattered data are typically regularised to a quantised grid for subsequent interpretation, which imposes a new limit on high frequency content and gives rise to spurious artefacts that are a product of the gridding process, not the surveyed field.
@@
 %TODO - a bit abrupt
-For the task of level grid prediction, the PSNR similarity between a case study reference grid and the proposed method is \qty{40}{\dB}.
-Additionally, directional derivatives of the implicit representation calculated numerically and using automatic differentiation are shown, with average residuals of \qty{0.4} and \qty{0.8}{\nano\tesla\per\m} for the easting and northing derivatives respectively, albeit vertical derivative performance remains limited.
+For the task of level grid prediction, the PSNR similarity between a case study reference grid and the proposed method is \qty{39.97}{\dB}.
+Additionally, directional derivatives of the implicit representation calculated numerically and using automatic differentiation are shown, with mean residuals of \qty{0.4} and \qty{0.8}{\nano\tesla\per\m} for the easting and northing derivatives respectively, albeit vertical derivative performance remains limited.
 
@@
 
-% \begin{figure}[hbt]
+% \begin{figure}[hbtp]
 %     \centering{}
@@
 The case study is performed using data from the 2002 Wolfe Creek meteorite impact magnetic survey \parencite{wolfecreek2019}.
-This high-resolution survey contains \qty{402}{line-kilometres} of data at \qty{50}{\m} line spacing with a nominal terrain clearance of \qty{40}{\m}, with line data collected on North-South transects.
-Prominently featured in the survey are the circular crater rim, and two East-West trending linear dunes to the North of the survey extent.
+This high-resolution survey contains \qty{402} line-kilometres of data at \qty{50}{\m} line spacing with a nominal terrain clearance of \qty{40}{\m}, with line data collected on North-South transects.
+Prominently featured in the survey are the circular crater rim, and two East-West trending linear dune features to the North of the survey extent.
 The data used for implicit representation excludes the survey tie lines, typically used in airborne geophysical surveys to reduce inter-line levelling noise.
 The mean altitude of the drape surface excluding tie lines is \qty{39.5}{\m}, with a standard deviation of \qty{4.5}{\m}.
-The sample locations and recorded altitudes are shown in \Cref{fig:samples}, where it can be seen the crater rim topography causes large deviations to the flown drape.
+The sample locations and recorded altitudes are shown in \Cref{fig:samples}, where it can be seen the crater rim topography causes large deviations in elevation from the nominal drape.
 
-\begin{figure}[hbt]
+\begin{figure}[hbtp]
     \centering{}
-    \includegraphics[width=0.5\linewidth]{fig/p3/P864_sample_locs.pdf}
+    \includegraphics[width=\linewidth]{fig/p3/P864_sample_locs.pdf}
     \caption[Point samples]{Sample altitudes for the Wolfe Creek survey lines. The diverging colourmap has been centred at the nominal survey terrain clearance of \qty{40}{\m}.}
@@
 Both the line data and grid raster netCDFs for the Wolfe Creek survey were downloaded from Geoscience Australia \footnote{https://pid.geoscience.gov.au/dataset/ga/142694} (GA) and used without further processing.
-The line data netCDF contains tie-levelled, micro-levelled, and AWAGS levelled magnetic variables, in respective order of processing levels.
-The micro-levelled magnetic data are used in this case study because the exact sample altitude is uncertain following the available levelling processes.
-Both geographic and projected coordinate systems can be used, provided the query coordinates for inference match those used during training.
+The line data netCDF contains tie-levelled, micro-levelled, and AWAGS levelled magnetic variables, in increasing stages of processing respectively.
+The micro-levelled magnetic data are used in this case study because the original sample altitude is uncertain in the available levelled data.
+Either a geographic and projected coordinate system can be used, provided the query coordinates for inference match those used during training.
 The three spatial coordinate dimensions are independently and linearly min-max normalised between \num{-1} and \num{1}.
@@
 The Wolfe Creek meteorite impact crater case study line data has \num{76420} sample points, and the Geoscience Australia provided reference grid has a resolution of \numproduct{446 x 445} cells.
-The case study line data easily fit into available graphics memory, and can be trained using batch gradient descent.
+The entire case study line data fit in a single batch within the available graphics memory, and can be trained using batch gradient descent.
 Each sample in the batch is a single 3D survey point with the associated 1D target potential field value.
+% However, if training on larger aeromagnetic surveys, memory becomes a constraint and mini-batch training is required.
 
@@
 Convergence of the network is shown in \Cref{fig:convergence}.
-%However, training on large scattered aeromagnetic surveys with more than one million samples, memory becomes a constraint and mini-batch training is required.
 
-\begin{figure}[hbt]
+\begin{figure}[hbtp]
     \centering
@@
 Contemporary super-resolution research can leverage this continual representation as a framework for high quality arbitrary scale factor high-frequency signal prediction \parencite[e.g][]{chenLearningContinuousImage2021}.
-However, the potential field representation task here does not attempt to predict additional high-frequency information and resolution remains determined by the survey sample spacing and neural network capacity.
+However, the potential field representation task here does not attempt to predict additional high-frequency information and resolution remains determined by the neural network's capacity to represent high frequencies sampled by the survey line spacing.
 
@@
 A good qualitative match is achieved between the GA reference grid and the grid queried from the implicit representation, which successfully reconstructs the linear dune features and circular rim features.
-This high performance is quantified by the residuals and peak signal to noise ratio (PSNR) of \qty{40.12}{\dB}.
+This high performance is quantified by the residuals and peak signal to noise ratio (PSNR) of \qty{40.12}{\dB}, with mean residuals of \qty{0.4} and \qty{0.8}{\nano\tesla\per\m}
 % Further level grids from other survey extents are included in Appendix A.
 
-\begin{figure}[hbt]
+\begin{figure}[hbtp]
     \centering
@@
 
-\begin{figure}[hbt]
+\begin{figure}[hbtp]
     \centering
@@
 
-% \begin{figure}[hbt]
+% \begin{figure}[hbtp]
 %     % \includegraphics[]{fig/p3/grid_subpct.pdf}
@@
 For comparison, the derivatives calculated with AD are compared with numerical derivatives calculated on the level grid queried from the same INR model.
-While horizontal derivatives queried from the INR correspond well to numerical derivatives calculated on the \qty{40}{\m} level grid in \Cref{fig:horigrad}, the vertical derivative suffers poor performance (\Cref{fig:vertgrad}).
+While horizontal derivatives queried from the INR correspond well to numerical derivatives calculated on the \qty{40}{\m} level grid in \Cref{fig:horigrad}, the vertical derivative shown in \Cref{fig:vertgrad} suffers poor performance.
 This correlates with the poor continuation performance of model when predicting level grids several metres or more beyond the nominal sample height.
-This is interpreted as the presented model having a limited capacity to extrapolate, and learning a poor representation of the vertical component of the potential field, which we further discuss in \Cref{sec:3discussion}
-\begin{figure}[hbt]
+This is interpreted as the presented model having a limited capacity to extrapolate beyond the flown data extent, and learning a poor representation of the vertical component of the potential field, which we further discuss in \Cref{sec:3discussion}.
+\begin{figure}[hbtp]
     \centering{}
@@
     \caption[Horizontal derivatives]{Horizontal gradients calculated using the proposed method and the reference numerical method.
-        Both numerical differentiaion (left column) and AD INR (middle column) are calculated on the INR level grid or INR respectively.
+        Both numerical differentiation (left column) and AD INR (middle column) are calculated on the INR level grid or INR respectively.
         Residuals are calculated between the numerical and AD gradient grids (right column).}
@@
     \caption[Vertical derivative]{Vertical derivative grids queried from AD differentiated INR (left) and calculated numerically (right) on the \qty{40}{\m} level grid queried from the INR\@.
-     The proposed method has poor vertical gradient representation, possibly due to the nature of aeromagnetic survey design.}
+     The proposed method has poor vertical gradient representation, possibly due to the single height sampled in aeromagnetic survey design.}
     \label{fig:vertgrad}
@@
 
-While quantised grids can be queried at any cell size, short wavelength information beyond the Nyquist limit of the survey line sampling is not predicted.
+While quantised grids can be queried at any cell size, short wavelength information beyond the Nyquist limit of the survey line sampling are not predicted with this architecture.
+
 The current method could include additional target dimensions, which would allow representation learning of vector fields \(\mathbb{R}^{3}\) in three dimensions \(\mathbb{R}^{3}\).
@@
 Level grids can be extracted from these representations, emerging as a novel method for regularising scattered geophysical sample data.
-Gradients calculated using the learnt representation are near-identical to those calculated by existing numerical methods, and benefit from being gridded after gradient calculation.
+Sptaial gradients can be calculated directly from the learnt representation, and can be queried at arbitrary locations.
+Regularly sampled grids of the gradients are near-identical to those calculated by existing numerical methods, and benefit from being gridded after gradient calculation.
 
@@
 
-% \begin{figure}[hbt]
+% \begin{figure}[hbtp]
 %     % \includegraphics[width=\textwidth]{fig/p3/menzies.pdf}    

### 2023-10-11 manuscript.tex
Fix long bibliography, use pdf 1.6
Add short headings to suit ToC
Tweak headings, refs

@@
-\documentclass[12pt,a4paper]{report} %,openright,twoside
+\directlua{pdf.setminorversion(6)}
+\documentclass[12pt,a4paper,notitlepage]{report} %,openright,twoside scrbook
 % \includeonly{}
@@
 
+\pagenumbering{Alph}
 \begin{titlepage}
@@
 
-\addsec{\centering{}Abstract}
+\addsec[Abstract]{\centering Abstract}
 Geophysics examines the petrophysical expression of geology within the Earth and is vital for exploring and understanding mineral systems under cover.
@@
 \listoffigures{}
-% \listoftables{}
 
 \newpage{}
-\addsec{Thesis Declaration}
+\addsec[Declarations]{Thesis Declaration}
 I, Luke Thomas Smith, certify that:
@@
 \newpage{}
-% \subfile{authorship_declaration}
 % Fix incorrect page numbering
@@
 \label{ch:intro}
-% \subfile{intro}
-% \includepdf[pages=-]{intro.pdf}
+\newrefsection{}
 \include{intro}
 
-\chapter{Magnetic Grid Resolution Enhancement using Machine Learning}
+\chapter[Magnetic Grid Resolution Enhancement using ML]{Magnetic Grid Resolution Enhancement using Machine Learning}
 \label{ch:paper1}
+\newrefsection{}
 This chapter has been reproduced from the following peer reviewed publication. Formatting has been adjusted for consistency.
@@
 https://doi.org/10.1016/j.oregeorev.2022.105119
-% \subfile{paper1}
-% \includepdf[pages=-]{paper1.pdf}
 \include{paper1}
@@
 \label{ch:paper2}
-% \includepdf[pages=-]{paper2.pdf}
-% \subfile{paper2}
+\newrefsection{}
 \include{paper2}
@@
 \label{ch:paper3}
-% \includepdf[pages=-]{paper3.pdf}
-% \subfile{paper3}
+\newrefsection{}
 \include{paper3}
 
-% \includepdf[pages=-]{discussion.pdf}
-% \subfile{discussion}
+\newrefsection{}
 \include{discussion}

### 2023-10-11 discussion.tex
Fix some layout

@@
 
-\section[Super-resolution impact on geological interpretation]{Super-resolution impact on geological interpretation}
+\section[Super-resolution impact on geological interpretation]{The impact of super-resolution on geological interpretation}
 The super-resolution outputs from the methods presented in this thesis have improved structural accuracy over the low-resolution grids.

### 2023-10-11 discussion.tex
Changes from TH review

@@
 It is possible to broaden the definition and extend the concept of informed networks to the use of generative adversarial networks in \Cref{ch:paper1}.
-In these networks, the informing method is termed discriminator loss, and is performed by a classification network conditioned to identify images as `realistic' or `not realistic', depending on features learnt to be important within the target data by the discriminator.
-Using crafted or learnt criterions to inform a neural network greatly assists with learning high quality models, and either approach may be useful for to geophysics in addressing the paucity of ground truth.
+In these networks, the informing method is termed discriminator loss, and is performed by a classification network conditioned to identify images as `realistic' or `not realistic', depending on features learned to be important within the target data by the discriminator.
+Using crafted or learned criterions to inform a neural network greatly assists with learning high quality models, and either approach may be useful for to geophysics in addressing the paucity of ground truth.
 In addition, demonstrating the enforcement of physical properties of potential fields for model outputs may address apprehension for machine learning in geophysics practice.
@@
 Prior to this work, it was unknown how well SR methods developed for natural images in computer vision research would adapt to the features present within magnetic grids, or the challenges faced in developing a training dataset for these data.
-We established that the CNN SR methods RDN and ESRGAN could be trained to upsample low-resolution textures in magnetic grids by four times scale, and that the results were more accurate than bicubic upsampling in the real-world case study region.
+We established that the CNN SR methods RDN and ESRGAN could be trained to upsample low-resolution textures in magnetic grids by a factor of four, and that the results were more accurate than bicubic upsampling in the real-world case study region.
 The GAN method used in \Cref{ch:paper2} enhanced resolution, however it introduced significant spurious features, masking the enhancement.

### 2023-10-11 intro.tex
Changes from TH review

@@
 The subsurface continuation of exposed geology can be extrapolated and interpolated using structures mapped in surveys of the Earth's naturally occuring potential fields.
-Potential field surveys offer low-cost investigations over a large spatial extent, and routinely used for geological mapping and interpretation \parencite{nabighian75thAnniversaryHistorical2005}.
+Potential field surveys offer low-cost investigations over a large spatial extent, and are routinely used for geological mapping and interpretation \parencite{nabighian75thAnniversaryHistorical2005}.
 For this reason, magnetic field surveys are commonly used by geophysicists for geological mapping and interpretation toward understanding the Earth in three dimensions.
@@
 The role of high-resolution details in these geophysical methods is becoming more important to exploration as resources are increasingly sought from below sedimentary cover.
-Resolution enhancement for natural images has seen recent success from the use of deep learning \parencite{moserHitchhikerGuideSuperResolution2023}, however it is not understood if these methods could extend to geophysics data, which are highly distinct from the natural images used for training in prior enhancement methods.
+Resolution enhancement for natural images has seen recent success from the use of deep learning \parencite{moserHitchhikerGuideSuperResolution2023}, however, it is not understood if these methods could extend to geophysics data, which differ significantly to the natural images used for training in prior enhancement methods.
 
 \section{Research Aims}
-The overall aim of this thesis is to adapt and extend the use of deep learning to improve the processing and enhancement and geophysics data. The three aims of this thesis are as follows:
+The overall aim of this thesis is to adapt and extend the use of deep learning to improve the processing and enhancement of potential field geophysics data.
+The three aims of this thesis are as follows:
 
 \begin{itemize}
-    \item{} Identifying how deep learning resolution enhancement methods previously developed for natural images are applicable to highly distinct magnetic potential fields data;
+    \item{} Identify how deep learning resolution enhancement methods previously developed for natural images are applicable to highly distinct magnetic potential field data;
 
-    \item{} Constructing a model framework to ensure example based models can be trained incorporating diverse types of geological features manifested in magnetic data, and evaluating the effectiveness of the framework with a resolution enhancement technique based on survey line spacing;
+    \item{} Construct a model framework to ensure example-based models can be trained while incorporating diverse types of geological features manifested in magnetic data, and evaluate the effectiveness of the framework with a resolution enhancement technique based on survey line spacing;
 
-    \item{} Evaluating a method for representation learning of potential field survey point data, which can predict a grid directly from point located survey data, as well as grids of the directional derivatives calculated of the learnt function using an automatic differentiation framework.
+    \item{} Evaluate a method for representation learning of potential field survey point data, which can predict a grid directly from point located survey data, as well as grids of the directional derivatives calculated of the learned function using an automatic differentiation framework.
 \end{itemize}
@@
 Airborne surveys of the Earth's magnetic or gravitational potential fields are routinely acquired at a range of scales at different stages of exploration, from pre-competitive regional data to stimulate exploration \parencite{howardAirborneGeophysicalCoverage2004}, to targeted investigations by the exploration industry at the prospect scale of up to several square kilometres.
-Surveys may also be collected on the ground, or less commonly in exploration, by ship or satellite, with most processing methods and interpretation shared between all forms of acquisition.
-Aeromagnetic surveys are among the lowest cost geophysical method \parencite{dentithGeophysicsMineralExploration2014}, however the cost rapidly increases when surveying at higher resolution due to overheads in flight line sampling.
+Surveys may also be collected on the ground, or less commonly in exploration by ship or satellite, with most processing methods and interpretation shared between all forms of acquisition.
+Aeromagnetic surveys are among the lowest cost geophysical method \parencite{dentithGeophysicsMineralExploration2014}.
+
+There are many aspects of survey design controlling the resolvable detail within the survey data.
 When acquiring data, aircraft fly straight transect lines at a safe elevation above topography, known as the topography drape.
 Surveys are flown with a heading in which data will be acquired along line.
-For regional and contemporary surveys this is recommended to be North-South, however early practice was to survey perpendicular to the dominant geological strike, under the expectation of sampling the greatest frequency of change in magnetic intensity \parencite{islesGeologicalInterpretationAeromagnetic2018}.
+For regional and contemporary surveys this is recommended to be North-South, however, early practice was to survey perpendicular to the dominant geological strike, under the expectation of sampling the greatest frequency of change in magnetic intensity \parencite{islesGeologicalInterpretationAeromagnetic2018}.
 Higher frequencies within these data diminish with increasing source-sensor distance, therefore the lower the height, the more high-frequency components will be captured by the sensor.
@@
 These low-resolution surveys, funded by government geoscience agencies, are a key driver in greenfields exploration and are released as open file data.
+Survey cost rapidly increases when surveying at higher resolution, due to overheads in flight line sampling.
 Higher-resolution surveys over prospective areas fly lines at closer line spacings, of the order \qty{100}{\m}, in order to resolve greater detail.
@@
 In geophysics and throughout this thesis, these are referred to as cells, and the property is a measure of the strength of the magnetic field at a specific location.
-The field strength measured is the Total Magnetic Intensity (TMI), which is the vector sum of each directional vector of the potential \parencite{blakelyPotentialTheoryGravity1996}.
+The field strength measured is the total magnetic intensity (TMI), which is the magnitude of the vector sum of each directional vector of the potential \parencite{blakelyPotentialTheoryGravity1996}.
 This scalar value is recorded in nanotesla (nT) and may be negative with an unbounded range that can exceed \qty{50000}{\nano\tesla} in the Earth's environment.
 The location recorded at a sample point is the geographic latitude and longitude, and altitude, acquired with high-precision differential GPS, alongside radar altimeter elevation.
-These data may be transformed to a flat projected system, where spatial dimensions are expressed in metres, used throughout this thesis.
+These data may be transformed to a flat projected system, where spatial dimensions are expressed in metres.
+
 There are numerous conventional gridding methods, and novel methods are frequently proposed in the literature.
@@
 Of those most commonly used in potential field geophysics, these are minimum curvature \parencite{briggsMachineContouringUsing1974}, splines \parencite{bhattacharyyaBicubicSplineInterpolation1969,shureHarmonicSplinesGeomagnetic1982,smithGriddingContinuousCurvature1990}, and equivalent sources \parencite{dampneyEquivalentSourceTechnique1969, solerBetterStrategyInterpolating2020}.
-Splines are used in bi-directional gridding, which is well-suited for aeromagnetic surveys, where the sample data are first interpolated in the line parallel direction, and the intermediate product is interpolated in the line-perpendicular direction \parencite{dentithGeophysicsMineralExploration2014}.
+Splines are used in bi-directional gridding, which is well-suited for aeromagnetic surveys, where the sample data are first interpolated in the line-parallel direction, and the intermediate product is interpolated in the line-perpendicular direction \parencite{dentithGeophysicsMineralExploration2014}.
 A method known as kriging is used in other areas of geoscience, such as geochemical mapping, and makes use of statistical properties of the known distribution \parencite{hansenInterpretiveGriddingAnisotropic1993,davis1986statistics}.
@@
 \subsection{A definition for geophysical resolution}
-In interpolated grids the spatial dimension of each cell is referred to as the cell size, with a unit of metre used in this thesis.
-As previously stated, resolvable detail in geophysical surveys is a product of the distance between the causative magnetic body and sensor (height), and the line spacing \parencite{islesRelationshipsGeologicalResolution1992,islesGeologicalInterpretationAeromagnetic2018,dentithGeophysicsMineralExploration2014}.
+In interpolated grids the spatial dimension of each cell is referred to as the cell size.
+As previously stated, resolvable detail in geophysical surveys is a product of the distance between the causative magnetic body and the sensor, and the line spacing \parencite{islesRelationshipsGeologicalResolution1992,islesGeologicalInterpretationAeromagnetic2018,dentithGeophysicsMineralExploration2014}.
 Height is easily controlled by flying the lowest safe and sufficiently smooth topography drape, and along-line sampling is performed at a constant high rate, so the key factor controlling resolution in aeromagnetic survey design is the line spacing.
@@
 Because of the sampling frequency of nominally \qty{7}{\m} in the flight line direction, and  up to \qty{400}{\m} in the line-perpendicular direction, the resulting grid resolution will be anisotropic at best, and uniformly low-resolution at worst.
+
 An important property of sampled data is the Nyquist frequency, \[f_{Nyquist} = f_{sampling} / 2.\]
-This is the lowest frequency at which a bandwidth limited signal may be sufficiently sampled, beyond which higher frequencies will be incorrectly recorded as aliasing.
+This is the lowest frequency at which a bandwidth limited signal may be sufficiently sampled, below which higher frequencies will be incorrectly recorded as aliasing.
 An aliased signal contains spurious low-frequency features caused by the sampling, not the underlying signal.
 This limiting frequency applies to each sampling direction in surveys, as well as the cell size of the grid.
-The smallest resolvable feature in each of these can be spatially described by wavelength, as the inverse of frequency.
+The smallest resolvable feature in each of these can be spatially described by wavelength, as the inverse of Nyquist frequency.
 In low-resolution aeromagnetic surveys of \qty{400}{\m} line spacing, strong variations of magnetic intensity in the line-perpendicular direction  that occur over a distance shorter than \qty{800}{\m} will be aliased.
@@
 
-Here, I state the definition of resolution adopted throughout this thesis.
+The definition of resolution throughout this thesis is:
 
 \bigskip{}
-\noindent{}\emph{Resolution in potential field geophysics refers to the level of geological detail in potential field grids.}
+\noindent{}\emph{Resolution refers to the smallest possible geological detail observable in potential field data. High-resolution refers to high frequencies, caused by geology, being represented.}
+
 \bigskip{}
-
-Resolution can be increased by:
+Resolution in geophysical grids can be increased by:
 \begin{enumerate}
-    \item{} High frequencies, caused by geology, being present in the potential field,
     \item{} Capturing these high frequencies during surveying, by sampling at close line spacing and small source-sensor separation,
@@
 The rate at which the power of the component frequencies of the potential field diminish with increasing source-sensor distance is well known.
-Back-calculation can be made to predict the power of these frequencies at a smaller separation, and this is termed downward continuation \textcite{bullardDeterminationMassesNecessary1948,blakelyPotentialTheoryGravity1996}.
+Back-calculation can be made to predict the power of these frequencies at a smaller separation, and this is termed downward continuation \parencite{bullardDeterminationMassesNecessary1948,blakelyPotentialTheoryGravity1996}.
 The inverse calculation at a larger separation is termed upward continuation, and is useful for reducing potentially unwanted near-surface magnetic detail, or levelling data to a common datum (e.g.\ open file magnetic data in Australia are available levelled to the AWAGS datum \parencite{mintyAirborneGeophysicalMapping2011}).
@@
 
-Resulting from the processes described in \Cref{sec:introgrids}, geophysical rasters are highly distinct from the image data used widely in computer vision.
+Resulting from the processes described in \Cref{sec:introgrids}, geophysical rasters are distinct from the image data used widely in computer vision.
 This includes the number of channels (3 in natural images, 1 in aeromagnetics), range (\qty{255} discrete values compared to \qty{50000} or more), and anisotropy of resolution.
@@
 \begin{itemize}
-    \item{} Spatio-Temporal Structure: Aeromagnetic grids are spatially corellated, neighbouring cells contain similar values arising from the same causative volume.
-    \item{} Multi-Source Multi-Resolution Data: One location may be covered by multiple aeromagnetic surveys with different resolutions, or the same survey may be presented with different levels of processing.
-    \item{} Poor Quality of Data: Sample data are subject to numerous sources of noise, which combine to become a significant fraction of the gridded data value, or be present as aliased frequencies.
-    \item{} Small Sample Size: While total aeromagnetic coverage in Australia is high, the high-resolution extents are spatially limited and biased by geological domain.
+    \item{} Spatio-temporal structure: Aeromagnetic grids are spatially corellated, neighbouring cells contain similar values arising from the same causative volume.
+    \item{} Multi-source multi-resolution data: One location may be covered by multiple aeromagnetic surveys with different resolutions, or the same survey may be presented with different levels of processing.
+    \item{} Poor quality of data: Sample data are subject to numerous sources of noise, which combine to become a significant fraction of the gridded data value, or be present as aliased frequencies.
+    \item{} Small sample size: While total aeromagnetic coverage in Australia is high, the high-resolution extents are spatially limited and biased by geological domain.
 \end{itemize}
@@
 \subsection{Deep learning context}
-Machine learning (ML) is a very broad family of techniques for learning functions from data.
+Machine learning (ML) is a broad family of techniques for learning from data.
 Artificial neural networks are a subset of techniques in ML, inspired by a model of the biological neuron \parencite{bishopNeuralNetworksPattern1995}.
@@
 A mathematical model of a neuron forms the basis of these networks, and the number of neurons within the network and their arrangement are one primary descriptor of a neural network.
-Neurons are paremeterised by a multiplicative weight term, an added bias term, and an activation function to scale the result.
+Neurons are paremeterised by a multiplicative weight term, an additive bias term, and an activation function which transforms the result.
 Each neuron applies these operations to the input, which may either be the input data, or the output of earlier neurons.
-The objective of training a neural network is to set the values for these for each neuron in the network, such that the trained network (or model) generalises to novel data.
+The objective of training a neural network is to set the parameters for each neuron in the network, such that the trained network (or model) generalises to novel data.
 This is performed by back propagation \parencite{rumelhartLearningRepresentationsBackpropagating1988}, a technique to navigate toward the lowest error solution by calculating the rate of improvement resulting from parameter updates.
-A practical introduction to the practice of training machine learning is available from \textcite{stevensDeepLearningPyTorch2020}, while a more formal introduction is provided in \textcite{bishopPatternRecognitionMachine2006}.
+A practical introduction to the practice of training machine learning is available in \textcite{stevensDeepLearningPyTorch2020}, while a more formal introduction is provided in \textcite{bishopPatternRecognitionMachine2006}.
 
-The activation function performs scaling, but more importantly maps a range of input values to zero, which can be interpreted as the lack of a specific feature being present \parencite{williamsLogicActivationFunctions1986}.
+The activation function performs a non-linear transformation, and importantly, maps a range of input values to zero, which can be interpreted as the lack of a specific feature being present \parencite{williamsLogicActivationFunctions1986}.
 For example, the rectified linear unit (ReLU) used in most tasks throughout this thesis maps negative input values to zero, and linearly for positive values.
@@
 The earliest application of CNN to SR was demonstrated by \textcite{dongLearningDeepConvolutional2014}, where convolutional layers throughout the depth of a network are used for low-resolution patch extraction, feature mapping, and reconstruction of super-resolved images.
-The outputs of each convolutional layer are similar to hand-crafted filters or the feature dictionaries in earlier example-based super-resolution methods \parencite{freemanExamplebasedSuperresolution2002}, but the learnt filters are more numerous and fully learned from the data with the deep learning approach.
+The outputs of each convolutional layer are similar to hand-crafted filters or the feature dictionaries in earlier example-based super-resolution methods \parencite{freemanExamplebasedSuperresolution2002}, but the learned filters are more numerous and fully learned from the data with the deep learning approach.
 Following the success of \parencite{dongLearningDeepConvolutional2014}, many iterative improvements have been made to CNN based SR\@.
@@
 % This comprises a set of initial input feature extraction convolutions, a sequence of convolutional blocks with activations (neurons), some number and arrangement of intermediate residual learning pathways (skip connections), and an upsampling block for feature upscaling and convolving latent features back to image space.
-% Once trained, the learnt functions are conditioned to transform low-resolution features into high-resolution features, using the neighbouring input values of the low-resolution grid in the context of filters learnt from the training data.
+% Once trained, the learned functions are conditioned to transform low-resolution features into high-resolution features, using the neighbouring input values of the low-resolution grid in the context of filters learned from the training data.
 
@@
 Key to the performance of these networks are implicit functions, which parameterise a function learned from training dataset with a neural network analogue.
-The network analogue can then be queried for information that fits the learnt function but was not included in the training data.
-In this way, CMLP networks learn a signal as a function of its coordinates, and novel signal values can be predicted for coordinates in the continuous domain of the learnt function.
+The network analogue can then be queried for information that fits the learned function but was not included in the training data.
+In this way, CMLP networks learn a signal as a function of its coordinates, and novel signal values can be predicted for coordinates in the continuous domain of the learned function.
 
 Generative Adversarial Networks \parencite{goodfellowGenerativeAdversarialNets2014} are a learning framework utilising two competing neural networks.
-These are termed the generator and the discriminator, and can be any arbitrary networks linked by objective functions.
-When best overall performance arises when each network is equally capable in its respective task, i.e.\ when the objective functions of each network are linked by the Nash equilibrium \parencite{salimansImprovedTechniquesTraining2016,lucicAreGANsCreated2018}.
+These are termed the generator and the discriminator, and can be any arbitrary networks linked by an objective function.
+The GAN architecture relies on each network gaining capability in its respective task, and informing the objective function of the other.
+These objective functions are linked by the Nash equilibrium \parencite{salimansImprovedTechniquesTraining2016,lucicAreGANsCreated2018}.
 Because the use of a discriminator allows an independent element for predictive capacity, GANs are highly suited for generative modelling, which includes the task of super-resolution.
@@
 Beyond the applications investigated in this thesis, many other machine learning methods have been investigated in geoscience.
-These include: clustering of geophysical textures \parencite{grujicGeophysicsNeuralNetworks2019}, prediction of geological map event history \parencite{guo3DGeologicalStructure2021}, automated interpretation of geological data \parencite{waldelandConvolutionalNeuralNetworks2018, babakhinSemisupervisedSegmentationSalt2019,dawsonImpactDatasetSize2023}, seismic data interpolation \parencite{wangDeeplearningbasedSeismicData2018}, and 3D structure, joint inversion, or modelling \parencite{guo3DGeologicalStructure2021,zhihouJointGravityGravity2021},
+These include: clustering of geophysical textures \parencite{grujicGeophysicsNeuralNetworks2019}, prediction of geological map event history \parencite{guo3DGeologicalStructure2021}, automated interpretation of geological data \parencite{waldelandConvolutionalNeuralNetworks2018, babakhinSemisupervisedSegmentationSalt2019,dawsonImpactDatasetSize2023}, seismic data interpolation \parencite{wangDeeplearningbasedSeismicData2018}, and 3D structure, joint inversion, or modelling \parencite{guo3DGeologicalStructure2021},
 
@@
 During this thesis, a large collection of synthetic data became available, containing realistic 3D geological voxel models and 2D geophysical forward models \parencite{jessellNoddyverseMassiveData2022}.
-These data present a large amount of uniformly sampled and noise free grids from an unbiased set of geological domains, and may offer a solution to some of these data challenges.
+These data present a large amount of uniformly sampled and noise-free grids from an unbiased set of geological domains, and may offer a solution to some of these data challenges.
 
@@
 Furthermore, it adopts advances in the machine learning literature by implementing the LTE network \parencite{leeLocalTextureEstimator2022}.
-The proposed method simulates aeromagnetic line sampling of a potential field extent at \qty{320}{\m} and \qty{80}{\m}, which are in the regional and prospect scale respectively.
+The proposed method simulates aeromagnetic line sampling of a potential field extent at \qty{320}{\m} and \qty{80}{\m}, which are in the regional and prospect scales respectively.
 While the baseline model can generalise to real-world data, some incorrect reconstructions remain.
@@
 CMLP networks are highly suited for processing spatial data such as point sampled geophysics surveys.
-Additionally, spatial derivatives are calculated on the learnt function directly.
+Additionally, spatial derivatives are calculated on the learned function directly.
 %TODO ensure refer back to aims

### 2023-10-11 manuscript.tex
Fix some layout
Changes from TH review

@@
 The first topic enhances the value of geophysical surveys by predicting high-frequency components in sparsely sampled potential field grids.
-The second presents a straightforward neural network framework for high quality grid regularisation, processing, and data integration.
+The second presents a straightforward neural network framework for high quality grid regularisation and processing.
 For each body of work in these topics, real-world geophysical case studies are presented in order to demonstrate the effectiveness and challenges of the method with open access data.
@@
 The second topic explores a method for learning a representation of a potential field extent from scattered real-world survey data by a contemporary neural network.
-The data-driven approach allows the extraction of high-resolution level grids from the learn representation, as well as the rapid analytical calculation of spatial gradients.
-Grid rasters and horizontal gradients calculated with the method very closely match their numerical counterparts, however vertical gradients are not represented well.
+The data-driven approach can extract high-resolution grids from the learned representation, as well as calculate the analytical spatial gradients.
+Grid rasters and horizontal gradients calculated with the method very closely match their numerical counterparts, however, vertical gradients do not.
 
-Individually the methods developed in this thesis enhance the information extractable from potential field surveys.
-However, in combination they reflect ongoing advances in deep learning and their extension to challenges and opportunities in geophysics.
-
-\vfill{}
-\epigraph{\emph{All collected data had come to a final end. Nothing was left to be collected.} \dots}{}
+Individually, the methods developed in this thesis enhance the information extractable from potential field surveys.
+However, in combination, and together they reflect ongoing advances in deep learning and their extension to challenges and opportunities in geophysics.
 
@@
 \newpage{}
-% Fix incorrect page numbering
+% Fix incorrect page numbering on the signed form
 \includepdf[pages=-,templatesize={595.276pt}{841.89pt},nup=1x1,scale=1,clip,trim=5mm 36.5mm 5mm 20mm,fitpaper=true,pagecommand={\pagestyle{plain}}]{authorship_declaration_signed.pdf}
@@
 \newrefsection{}
-\include{intro}
+\input{intro}
 
@@
 https://doi.org/10.1016/j.oregeorev.2022.105119
-\include{paper1}
+\input{paper1}
 
@@
 \newrefsection{}
-\include{paper2}
+\input{paper2}
 
@@
 \newrefsection{}
-\include{paper3}
+\input{paper3}
 
 \newrefsection{}
-\include{discussion}
+\input{discussion}
 

### 2023-10-11 paper1.tex
Changes from TH review

@@
 As discussed in \Cref{sec:resingeo}, a finer spatial resolution grid (fewer metres per pixel) can convey higher frequency information, due to the higher spatial sampling rate.
-Indeed, a gridded raster with regularly spaced square cells \(\Delta x\) has an intrinsic Nyquist wavelength \(\lambda _N\), at twice the cell size,
+Indeed, a gridded raster with regularly spaced square cells \(\Delta x\) has an intrinsic Nyquist wavelength \(\lambda_{Nyquist}\), at twice the cell size,
 
@@
     \label{eqn:nyq}
-    \lambda{}N = 2 \Delta{}x.
+    \lambda{}_{Nyquist} = 2 \Delta{}x.
 \end{equation}
@@
     \label{eqn:hrn}
-    \lambda{}N_{HR} = \lambda{}N_{LR} \div{}S.
+    \lambda{}_{Nyquist {(HR)}} = \frac{\lambda{}_{Nyquist {(LR)}}}{S}.
 \end{equation}
@@
 Recent advances in machine learning techniques for image super-resolution (SR) have been shown to successfully increase image resolution for photographs and other image rasters, while also improving perceptual image quality.
-These modern techniques belong to a family of methods known as deep learning, where features learnt early in the network are leveraged to develop a higher understanding of later features.
+These modern techniques belong to a family of methods known as deep learning, where features learned early in the network are leveraged to develop a higher understanding of later features.
 Notable published examples include SRCNN \parencite{dongLearningDeepConvolutional2014}, VDSR \parencite{kimAccurateImageSuperresolution2016}, SRGAN \parencite{ledigPhotorealisticSingleImage2017}, EDSR \parencite{limEnhancedDeepResidual2017}, RDN \parencite{zhangResidualDenseNetwork2018}, and the current state-of-the-art methods, ESRGAN \parencite{wangESRGANEnhancedSuperresolution2018} and ESRGAN+ \parencite{rakotonirinaESRGANFurtherImproving2020}.
@@
 For example, it may enhance the appearance of gridding artefacts, instead of supressing them.
-While several of the aforementioned works investigate deep learning super-resolution for geospatial data, low resolution in potential field geophysics is a result of under sampling and naïve best-effort interpolation of the potential field, distinct from low-resolution data previously studied in those works.
+While several of the aforementioned works investigate deep learning super-resolution for geospatial data, low resolution in potential field geophysics is a result of under sampling and naive best-effort interpolation of the potential field, distinct from low-resolution data previously studied in those works.
 
@@
 Residual Dense Network (RDN) \parencite{zhangResidualDenseNetwork2018} is a deep learning super-resolution method which consists of a series of residual dense blocks (\Cref{fig:rdb,fig:convs}), which combine the performant residual connections and dense connections (\Cref{fig:convs}) of earlier architectures for state-of-the-art performance.
-Residual and dense connections provide additional learning capacity to a CNN, where features learnt in early layers can be fully utilised in later layers.
+Residual and dense connections provide additional learning capacity to a CNN, where features learned in early layers can be fully utilised in later layers.
 Following a series of these residual dense blocks, image enlargement is achieved using a simple nearest neighbour interpolation process followed by additional convolution operations.
@@
     \includegraphics[width=\linewidth]{fig/p1/filtered.png}
-    \caption[High Pass filtered results]{High Pass filtered test tile and its upsampled counterparts.
-        The cut-off for the high pass Butterworth filter was selected with wavelength equal to the Nyquist wavelength of the LR grid, i.e.,\ four times the HR Nyquist wavelength
+    \caption[High Pass filtered results]{High pass filtered test tile and its upsampled counterparts.
+        The cut-off for the high pass Butterworth filter was selected with wavelength equal to the Nyquist wavelength of the LR grid, i.e.,\ four times the HR Nyquist wavelength.
     }
@@
 
-The use of the state magnetic map at \qty{80}{\metre} and \qty{20}{\metre} for training data serves as a ready-made analogue for a low pass filter process, which the super-resolution networks successfully learnt to reverse.
+The use of the state magnetic map at \qty{80}{\metre} and \qty{20}{\metre} for training data serves as a ready-made analogue for a low pass filter process, which the super-resolution networks successfully learned to reverse.
 While the result presented here demonstrates the strong applicability of performing super-resolution with grids containing magnetic textures and features, it does not yet demonstrate a capability to super-resolve widely spaced line surveys as if they had been surveyed at closer line spacing.
@@
 
-\section{Conclusions}
+\section{Conclusion}
 Convolutional neural network architectures, such as RDN and ESRGAN, are capable of super-resolution upsampling low-resolution magnetic grids into realistic high-resolution grids.

### 2023-10-11 paper2.tex
Changes from TH review

@@
 These include SIREN \parencite{sitzmann2019siren}, LIIF \parencite{chenLearningContinuousImage2021}, and LTE \parencite{leeLocalTextureEstimator2022}.
-Notably in these networks, the learnt function has continuous domain, despite the discretised grid input.
-Super-resolution can be achieved by sampling the learnt function at any arbitrary grid cell size smaller than the original input \parencite{chenLearningContinuousImage2021}.
+Notably in these networks, the learned function has continuous domain, despite the discretised grid input.
+Super-resolution can be achieved by sampling the learned function at any arbitrary grid cell size smaller than the original input \parencite{chenLearningContinuousImage2021}.
 While a stand-alone MLP such as SIREN is capable of parameterising a single function, when used in an autoencoder framework (such as with LIIF or LTE), an arbitrary input can be encoded, upscaled, and subsequently reconstructed using fully connected layers \Cref{fig:ltenet}.
@@
 
-\section{Conclusions}
+\section{Conclusion}
 \label{sec:2conclusion}

### 2023-10-11 paper3.tex
Fix some layout
Changes from TH review

@@
     % Using this new paradigm of encoding spatial information within a neural network enables new methods for working with potential field survey data.
-    We present a novel method for implicit neural representation for potential fields, demonstrate the quality of the learnt implicit function by encoding real airborne geophysical survey line data, predict constant level grids, and compare the result to grid data processed with a traditional workflow.
+    We present a novel method for implicit neural representation of potential fields, demonstrate the quality of the learned implicit function by encoding real airborne geophysical survey line data, predict constant level grids, and compare the result to grid data processed with a traditional workflow.
     We further demonstrate the analytical calculation of gradients directly in the continuous domain using automatic differentiation, with the same framework used to train the neural network representation.
-    Level grids queried from the learnt representation closely match the reference grid product, with a peak signal to noise ratio of 40 dB.
+    Level grids queried from the learned representation closely match the reference grid product, with a peak signal to noise ratio of 40 dB.
     Horizontal gradients calculated with this method are accurate against numerically derived gradients, while the vertical gradient is a poor match.
@@
 
+\clearpage{}
+
 \section{Introduction}
 Geophysical potential fields are routinely collected and used to assist the understanding of the subsurface for geoscience and mineral exploration.
-When surveying these fields, which are continuous functions in three dimensions, sample locations are scattered in \(x\), \(y\), and \(z\), despite best efforts to conform to a regularly spaced line or grid acquisition plan.
+When surveying these fields, which are continuous functions in three dimensions, sample locations are scattered in 3D space, despite best efforts to conform to a regularly spaced line plan.
 These scattered data are typically regularised to a quantised grid for subsequent interpretation, which imposes a new limit on high frequency content and gives rise to spurious artefacts that are a product of the gridding process, not the surveyed field.
@@
 Neural networks can be considered as universal function approximators.
-The recent technique of deep learning implicit neural representation (INR) \parencite{mildenhallNeRFRepresentingScenes2020} represents a signal as a function of its coordinates, built on a network architecture known as a coordinate multilayer perceptron (CMLP) (see \textcite{ramasinghePeriodicityUnifyingFramework2022} for a recent introduction).
-By parameterising the function in coordinate space, novel values of the function can be queried at arbitrary coordinates within the learnt continuous spatial domain.
+The recent technique of deep learning implicit neural representation (INR) \parencite{mildenhallNeRFRepresentingScenes2020} represents a signal as a function of its coordinates, built on a network architecture known as a coordinate multilayer perceptron (CMLP;\ see \textcite{ramasinghePeriodicityUnifyingFramework2022} for a recent introduction).
+By parameterising the function in coordinate space, novel values of the function can be queried at arbitrary coordinates within the learned continuous spatial domain.
 Recent advances in CMLPs by using periodic activations such as sinusoids have demonstrated that high frequency information can be modelled well by CMLP networks, while being continuously differentiable throughout the depth of the network.
@@
     \label{eqn:potential}
-    \phi\left(x,y,z\right),
+    \phi\left(x, y, z\right),
 \end{equation}
-where \(\phi{}\) is the potential, and \({(x,y,z)}\) are the three spatial dimensions.
+where \(\phi{}\) is the potential, and \(x, y, \) and \(z\) are the three spatial dimensions.
 
@@
 Training this example network with a large number of different images with class labels produces a model capable of predicting the class of novel input image vectors.
-A CMLP for representing images instead takes an input of explicitly stated pixel coordinates \((x,y)\), and an output vector of image pixel intensities \(u\) at those coordinates.
+A CMLP for representing images instead takes an input of explicitly stated pixel coordinates \((x, y)\), and an output vector of image pixel intensities \(u\) at those coordinates.
 Thus training of a CMLP network requires a set of input coordinates and intensities from a single image, and results in a model capable of predicting the intensity of any arbitrary continuous coordinate within the input domain.
 Both tasks may use similar images and an MLP network structure with the same \(n\) hidden layers and \(m\) features, but the use of coordinates as inputs and intensities as outputs changes the predictive task.
-CMLP networks for predicting 3D scalar fields are a class of neural networks \(f\) which train \(u = f(x,y,z)\), with \(u\in\mathbb{R}^1\) and \((x,y,z)\in\mathbb{R}^3\).
+CMLP networks for predicting 3D scalar fields are a class of neural networks \(f\) which train \(u = f(x, y, z)\), with \(u\in\mathbb{R}^1\) and \((x, y, z)\in\mathbb{R}^3\).
 
-Seminal work by \textcite{mildenhallNeRFRepresentingScenes2020} demonstrated INR of volume density and colour radiance, learnt from five dimensions of spatial coordinates and orientation.
+Seminal work by \textcite{mildenhallNeRFRepresentingScenes2020} demonstrated INR of volume density and colour radiance, learned from five dimensions of spatial coordinates and orientation.
 Their approach uses positional encoding to improve the learning capacity of high-frequency content, addressing the issue of spectral bias in deep learning \parencite{rahamanSpectralBiasNeural2019}.
@@
 The \num{76420} sample points contained within the case study line data are split, with \qty{70}{\percent} used for training, and a random \qty{20}{\percent} of the remaining points are reserved to validate the model performance during training.
-Inference is performed by querying novel coordinates within the learnt domain, here at regularly spaced grid intervals for comparison with standard grid regularisation methods.
+Inference is performed by querying novel coordinates within the learned domain, here at regularly spaced grid intervals for comparison with standard grid regularisation methods.
 
@@
 \subsection{Derivative calculation}
-A naive approach to calculating gradients with the trained INR would be to evaluate the representation \(f(x, y, z)\) at a set of coordinates \({(x, y, z)}_1 \dots {(x,y,z)}_n\), and use numerical differentiation with the output grid to calculate derivatives.
+A naive approach to calculating gradients with the trained INR would be to evaluate the representation \(f(x, y, z)\) at a set of coordinates \({(x, y, z)}_1 \dots {(x, y, z)}_n\), and use numerical differentiation with the output grid to calculate derivatives.
 However, using AD with Pytorch, the implicit representation can be differentiated with respect to its coordinate inputs to provide spatial gradients, prior to being queried at the nodes of a quantised grid.
-That is, to directly sample \(\nabla{}\phi{}_{(x,y,z)}\) at \({(x, y, z)}_1 \dots {(x,y,z)}_n\).
+That is, to directly sample \(\nabla{}\phi{}_{(x, y, z)}\) at \({(x, y, z)}_1 \dots {(x, y, z)}_n\).
 Higher order derivatives can be calculated using AD in the same manner, but are not presented here.
@@
 \subsection{Level grid prediction from INR}
-Querying a learnt INR using a regularly spaced \(x,y\) grid at a specific \(z\) height is a novel method for producing level grids from geophysical potential field surveys.
-The cell size can be selected using a finer or coarser \(x,y\) spacing, including variable or anisotropic cell sizes.
+Querying a learned INR using a regularly spaced \(x, y\) grid at a specific \(z\) height is a novel method for producing level grids from geophysical potential field surveys.
+The cell size can be selected using a finer or coarser \(x, y\) spacing, including variable or anisotropic cell sizes.
 Contemporary super-resolution research can leverage this continual representation as a framework for high quality arbitrary scale factor high-frequency signal prediction \parencite[e.g][]{chenLearningContinuousImage2021}.
@@
     \label{eqn:crilaplace}
-    \mathcal{L}_{PDE} = \frac{1}{S_i}\sum_{i=1}^{S_i} \left(\frac{\partial{}^2f}{\partial{}x^2} + \frac{\partial{}^2f}{\partial{}y^2} + \frac{\partial{}^2f}{\partial{}z^2}\right)^2,
+    \mathcal{L}_{PDE} = \frac{1}{S}\sum_{i=1}^{S} \left(\frac{\partial{}^2f}{\partial{}x_{i}^2} + \frac{\partial{}^2f}{\partial{}y_{i}^2} + \frac{\partial{}^2f}{\partial{}z_{i}^2}\right)^2,
 \end{equation}
-where \(S_i\) indicates the \(i^{th}\) sample point of the field survey \(\phi(x, y, z)\).
+where \(S_i\) indicates the \(i^{th}\) sample point of the field survey \(\phi(x, y, z)\), implicitly represented by the model \(f\).
 This criterion penalises outputs where Laplace's equation is not satisfied because the sum of partial second derivatives is not close to zero.
@@
 % \( F = \nabla\phi \) for the gravity potential, \(F = - \nabla \phi\) for the Magnetic potential.
-% \( \phi(x,y,z) = constant \) is an equipotential surface.
+% \( \phi(x, y, z) = constant \) is an equipotential surface.
 % Numerical methods for potential field continuation are unstable, recognised in the geophysical community by solution divergence and noise in predictions.
@@
 
-\section{Conclusions}
+\section{Conclusion}
 High-resolution implicit neural representation of potential field geophysics surveys is achieved with the use of coordinate MLP neural networks for INR\@.
@@
 Level grids can be extracted from these representations, emerging as a novel method for regularising scattered geophysical sample data.
-Sptaial gradients can be calculated directly from the learnt representation, and can be queried at arbitrary locations.
+Sptaial gradients can be calculated directly from the learned representation, and can be queried at arbitrary locations.
 Regularly sampled grids of the gradients are near-identical to those calculated by existing numerical methods, and benefit from being gridded after gradient calculation.

### 2023-10-11 manuscript.tex
Add acknowledgements

@@
 \addbibresource{bib/PhD.bib}
+
 \begin{document}
@@
 \addsec{Acknowledgements}
-\dots{}
 
-This research was supported by a Rio Tinto Iron Ore PhD Scholarship.
+I wish to thank a great number of people who have contributed to my ongoing development.
+First, to my supervisors:
+EJ, for bringing together a team of talented and friendly geodata scientists, and caring deeply for them all.
+Tom, who set a high bar with his PhD and immediately set about raising his students to the same level.
+Daniel, for the meticulous, concise, and actionable reviews and suggestions.
+Naveed, whose perspective was invaluable.
+Andie, Dale, and Robert, and the rest of my family in NSW --- I didn't get to visit as much as I had originally planned in 2019, but we made the most of it!
+Thanks for the support and encouragement, and imparting all the passions of rocks, computers, and tinkering that I have today.
+Tasman, for being a good friend and inspirational colleague for most of my academic career --- looking forward to sharing a project again sometime, somewhere in the future!
+Lu, for sharing your incredible amount of geophysics knowledge, incredible cooking, and love of tennis with me.
+Matilda, for being a wonderful friend and the best housemate --- Thanks for being silly with me.
+My first floor colleagues and fellow tech geeks, Daniel, David, Chris, Minh, and Peter --- Your friendship and knowledge has been a wonderful environment to grow as a geodata scientist in.
+And all my SES, CET, and friends beyond: Alex, Anne, Ben, France, Jackson, Jules, Kailah, Lauren, Lauri, Liam, Lilly, Maddie, Maria, Malvina, Nicolas, Ravi, Sean, Sumail, Vickie, and Ze --- Thank you for years of lunches, dinners, beaches, rock climbing, yoga, and all the opportunities to talk rocks that I've been missing.
+And to all the teachers throughout my life, both professional and incidental: Thank you.
+
+I love you all.
+
+\bigskip
+\noindent This research was supported by a Rio Tinto Iron Ore PhD Scholarship.
 
 \vfill{}
-\epigraph{\emph{But all collected data had yet to be completely correlated and put together in all possible relationships.}}{Isaac Asimov}
+\epigraph{
+    \textit{All collected data had come to a final end. Nothing was left to be collected.}
+
+    \smallskip
+    \textit{But all collected data had yet to be completely correlated and put together in all possible relationships.}}{Isaac Asimov}
 

### 2023-10-11 discussion.tex
LS edits from proof read of print copy

@@
 
-Super-resolution for geophysics is still in its infancy and requires further efforts towards improving reliability before wide-spread adoption in practice.
+Super-resolution for geophysics is not yet characterised and requires further efforts towards improving reliability before wide-spread adoption in practice.
 This section proposes four avenues for future research:
@@
 \section[Super-resolution for domain specific tasks]{A structured approach to training super-resolution for domain specific tasks}
-Several models were implemented throughout \Cref{ch:paper1,ch:paper2}, namely RDN, ESRGAN+, and LTE\@.
+Several models were implemented throughout \Cref{ch:paper1,ch:paper2}, namely RDN\textdaggerdbl{}, ESRGAN+, and LTE\@.
 % However, the most important choice in developing a performant super-resolution neural network for real-world aeromagnetic survey data was the choice of training data.
@@
 It was seen in \Cref{ch:paper2} that this data improved model performance for a range of features by using transfer learning for pre-training.
-% This transfer learning approach for training data is also found to be useful for RDN and ESRGAN\@.
-Here, the use of synthetic and real-world line spacing sampled data approach used with LTE in \Cref{ch:paper2} are adopted for the RDN+ and ESRGAN+ models.
-\Cref{fig:modcomp} shows RDN and ESRGAN+ in predicting accurate features when upscaling \qty{320}{\m} data to \qty{80}{\m} line spacing.
+% This transfer learning approach for training data is also found to be useful for RDN\textdaggerdbl{} and ESRGAN\@.
+Here, the use of synthetic and real-world line spacing sampled data approach used with LTE in \Cref{ch:paper2} are adopted for the RDN\textdaggerdbl{} and ESRGAN+ models.
+\Cref{fig:modcomp} shows RDN\textdaggerdbl{} and ESRGAN+ in predicting accurate features when upscaling \qty{320}{\m} data to \qty{80}{\m} line spacing.
 It can be inferred that the challenge of super-resolution for these tasks is predominantly a question of providing suitable and sufficient training data, and is less constrained to neural network choices.
@@
 \begin{figure}
-    \includegraphics[width=\linewidth]{fig/etc/TMI Comparison_23.pdf} % TODO Update for RDN, ESRGAN, LTE, ~3 hours ea.
+    \includegraphics[width=\linewidth]{fig/etc/TMI Comparison_23.pdf} % TODO Update for RDN\textdaggerdbl{}, ESRGAN, LTE, ~3 hours ea.
     \caption{
         A comparison between all deep learning super-resolution methods presented in \Cref{ch:paper1} and \Cref{ch:paper2}, using the realistic low-resolution transform developed in \Cref{ch:paper2}.
-        a) The low-resolution input, b) The high-resolution target, c) The RDN+ Network, d) The ESRGAN+ network, and e) The LTE network.}
+        a) The low-resolution input, b) The high-resolution target, c) The RDN\textdaggerdbl{}+ Network, d) The ESRGAN+ network, and e) The LTE network.}
     \label{fig:modcomp}
@@
 Magnetic data in different geological contexts are subject to a mixture of statistical distributions \parencite{khokhlovCauseNonGaussianDistribution2017}.
-Investigation is also required to identify a robust normalisation method accounting for dynamic range and the structural significance contained in the long tails of the distributions of magnetic intensities.
+Investigation is also required to identify a robust normalisation method accounting for high dynamic range and the structural significance contained in the long tails of the distributions of magnetic intensities.
 
@@
 For supervised tasks, a full reference metric can be calculated between the super-resolution prediction and the high-resolution target.
-In the \Cref{ch:paper1,ch:paper2} works, PSNR and SSIM are used to quantify the performance of the proposed methods in transforming low-resolution grids to high resolution.
+In the works presented in \Cref{ch:paper1,ch:paper2,ch:paper3}, PSNR and SSIM are used to quantify the performance of the proposed methods in transforming low-resolution grids to high resolution.
 However, properties of magnetic grid data are distinct to the images for which these metrics are designed.
@@
 Consistently high SSIM scores are assigned to grids that are perceptually poor matches to the target.
-High values are noted in other geophysical grid investigations reporting SSIM metrics \parencite{wangDeeplearningbasedSeismicData2018,bavandsavadkoohiHighresolutionAeromagneticMap2023}.
-An investigation to identify a more appropriate IQA for potential field grids is required, which accounts for the distinct nature of these data and reflects the predicted quality of geological interpretation.
-This may be benefit by automated analysis methods described above.
+High SSIM values are noted in other geophysical grid investigations which report SSIM metrics \parencite{wangDeeplearningbasedSeismicData2018,bavandsavadkoohiHighresolutionAeromagneticMap2023}.
+An investigation to identify a more appropriate IQA for potential field grids is required, which accounts for the distinct nature of these data and better reflects the predicted quality of geological interpretation.
+This may be benefit by automated analysis methods as mentioned above.
 
@@
 Geological interpretation is less reliant on this adherence, however \emph{a priori} information used in physics-informed neural networks improve training speed and model performance \parencite{raissiPhysicsinformedNeuralNetworks2019}, and are especially useful in data-constrained domains such as geophysics.
+
 It is possible to broaden the definition and extend the concept of informed networks to the use of generative adversarial networks in \Cref{ch:paper1}.
 In these networks, the informing method is termed discriminator loss, and is performed by a classification network conditioned to identify images as `realistic' or `not realistic', depending on features learned to be important within the target data by the discriminator.
-Using crafted or learned criterions to inform a neural network greatly assists with learning high quality models, and either approach may be useful for to geophysics in addressing the paucity of ground truth.
+Using crafted or learned criterions to inform a neural network greatly assists with learning high quality models, and either approach may be useful in geophysics to address the paucity of ground truth.
 In addition, demonstrating the enforcement of physical properties of potential fields for model outputs may address apprehension for machine learning in geophysics practice.
@@
 To the best of my knowledge, \Cref{ch:paper1} presents the first investigation in the literature of the super-resolution enhancement of gridded aerogeophysical data.
-Prior to this work, it was unknown how well SR methods developed for natural images in computer vision research would adapt to the features present within magnetic grids, or the challenges faced in developing a training dataset for these data.
-We established that the CNN SR methods RDN and ESRGAN could be trained to upsample low-resolution textures in magnetic grids by a factor of four, and that the results were more accurate than bicubic upsampling in the real-world case study region.
-The GAN method used in \Cref{ch:paper2} enhanced resolution, however it introduced significant spurious features, masking the enhancement.
-Hence, the method based on RDN was preferred.
+Prior to this work, it was unknown how well SR methods developed for natural images would adapt to the features and high dynamic range present within magnetic grids, or the challenges faced in developing a training dataset for these data.
+We established that the CNN SR methods RDN\textdaggerdbl{} and ESRGAN+ could be trained to upsample low-resolution textures in magnetic grids by a factor of four, and that the results were more accurate than bicubic upsampling in the real-world case study region.
+The ESRGAN+ method used in \Cref{ch:paper2} enhanced resolution, however it introduced significant spurious features, masking the enhancement.
+Hence, the method based on RDN\textdaggerdbl{} was preferred. 
 We identified the need for additional representative training data to investigate transferability of the method to other geological domains, and a realistic method to generate low-resolution training data.
@@
 The challenge of training data availability was addressed in \Cref{ch:paper2}, where we investigated the use of geologically varied synthetic data to train a baseline model, fine-tuning with real-world data, and simulating realistic line sampling to create low-resolution data.
-We implemented the contemporary LTE network to perform this investigation, these data sampled at four times wider line spacing showed increased structural accuracy when fine-tuned with real-world data.
+We implemented the contemporary LTE network to perform this investigation.
+Data sampled at four times wider line spacing showed increased structural accuracy when fine-tuned with real-world data.
 Additionally, spurious features in the baseline model were correctly resolved when fine-tuned.
@@
 To my knowledge, this is the first time implicit neural representation of aerogeophysical survey data has been reported in the literature.
-These networks are highly suited for processing spatial data such as point sampled geophysics surveys.
-The contribution is capable of predicting regularly spaced grids from scattered survey point data, and a novel method using the representation to calculate derivatives of a potential field, both fundamental to interpretation and processing in geophysics.
+It was seen that these networks are highly suited for processing spatial data such as point sampled geophysics surveys.
+The contribution is capable of predicting regularly spaced grids from scattered survey point data, and can be used as a novel method to calculate derivatives of a potential field from the learnt representation, both task which are fundamental to interpretation and processing in geophysics.
 By commencing the methods from point sample data, the number of individual processing steps is reduced, and the application is fully trainable.
-Continued advances in the recent field of Coordinate MLPs will improve the capacity of the method for representing high-resolution aeromagnetic data. 
-We identify opportunities in \Cref{ch:futurework} for future work in super-resolution and implicit representation for enhancing potential field methods in geophysics.
+Continued advances in the recent field of CMLPs will improve the capacity of the method for representing high-resolution aeromagnetic data.
+
+We identify opportunities in \Cref{ch:futurework} for future work stemming from our contribution  of enhancing potential field methods in geophysics.
 

### 2023-10-11 intro.tex
LS edits from proof read of print copy

@@
 For this reason, magnetic field surveys are commonly used by geophysicists for geological mapping and interpretation toward understanding the Earth in three dimensions.
-Scattered surveys are widely used when interpolated to grid rasters, and interpreted individually or integrated with many other datasets for predicting the subsurface for processes such as numerical modelling and inversion.
+Scattered surveys are commonly interpolated to grid rasters, and interpreted individually or integrated with other datasets for predicting the subsurface for processes such as numerical modelling and inversion.
 In these tasks, the spatial resolution of the grid is a critical factor in their ability to define geological detail \parencite{islesGeologicalInterpretationAeromagnetic2018}.
 The role of high-resolution details in these geophysical methods is becoming more important to exploration as resources are increasingly sought from below sedimentary cover.
-Resolution enhancement for natural images has seen recent success from the use of deep learning \parencite{moserHitchhikerGuideSuperResolution2023}, however, it is not understood if these methods could extend to geophysics data, which differ significantly to the natural images used for training in prior enhancement methods.
+Resolution enhancement for natural images has seen recent success from the use of deep learning \parencite{moserHitchhikerGuideSuperResolution2023}, however, it is not understood if these methods can extend to geophysics data, which differ significantly to the natural images used for training in prior enhancement methods.
 
-\section{Research Aims}
+\section{Research aims}
 The overall aim of this thesis is to adapt and extend the use of deep learning to improve the processing and enhancement of potential field geophysics data.
@@
 
-    \item{} Evaluate a method for representation learning of potential field survey point data, which can predict a grid directly from point located survey data, as well as grids of the directional derivatives calculated of the learned function using an automatic differentiation framework.
+    \item{} Evaluate a method for representation learning of potential field survey point data, which can predict a grid directly from point located survey data, as well as grids of the directional derivative of the learned function calculated using an automatic differentiation framework.
 \end{itemize}
@@
 
-There are many aspects of survey design controlling the resolvable detail within the survey data.
+There are many aspects of survey design controlling the resolvable detail within survey data.
 When acquiring data, aircraft fly straight transect lines at a safe elevation above topography, known as the topography drape.
+Higher frequencies within potential field data diminish with increasing source-sensor distance, therefore the lower the height, the more high-frequency components will be captured by the sensor.
 Surveys are flown with a heading in which data will be acquired along line.
 For regional and contemporary surveys this is recommended to be North-South, however, early practice was to survey perpendicular to the dominant geological strike, under the expectation of sampling the greatest frequency of change in magnetic intensity \parencite{islesGeologicalInterpretationAeromagnetic2018}.
-Higher frequencies within these data diminish with increasing source-sensor distance, therefore the lower the height, the more high-frequency components will be captured by the sensor.
 Acquisition along flight lines is sampled at a rate of \qty{10}{\hertz} or greater, which corresponds to an interval of \qty{7}{\m} or shorter at nominal flight speeds of \qty{70}{\m\per\s} \parencite{goodwinAirborneMagneticRadiometric2023}.
@@
 \label{sec:introgrids}
-Survey data can be interpreted as one dimensional transects, but more commonly they are regularised to a two-dimensional grid raster for interpretation in a process termed gridding.
+Survey data can be interpreted as one-dimensional flight line transects, but more commonly they are regularised to a two-dimensional grid raster for interpretation in a process termed gridding.
 The resulting interpolated array contains uniformly spaced nodes and is referred to as a grid.
@@
 There are numerous conventional gridding methods, and novel methods are frequently proposed in the literature.
-The simplest use surrounding samples for interpolation, such as choosing the closest sample value or applying a transformation function to the neighbouring samples.
+The simplest use the surrounding samples for interpolation, such as choosing the closest sample value or applying a transformation function to the neighbouring samples.
 Of those most commonly used in potential field geophysics, these are minimum curvature \parencite{briggsMachineContouringUsing1974}, splines \parencite{bhattacharyyaBicubicSplineInterpolation1969,shureHarmonicSplinesGeomagnetic1982,smithGriddingContinuousCurvature1990}, and equivalent sources \parencite{dampneyEquivalentSourceTechnique1969, solerBetterStrategyInterpolating2020}.
@@
 As previously stated, resolvable detail in geophysical surveys is a product of the distance between the causative magnetic body and the sensor, and the line spacing \parencite{islesRelationshipsGeologicalResolution1992,islesGeologicalInterpretationAeromagnetic2018,dentithGeophysicsMineralExploration2014}.
-Height is easily controlled by flying the lowest safe and sufficiently smooth topography drape, and along-line sampling is performed at a constant high rate, so the key factor controlling resolution in aeromagnetic survey design is the line spacing.
+Height is controlled by flying the lowest safe and sufficiently smooth topography drape, and along-line sampling is performed at a constant high rate, so the key factor controlling resolution in aeromagnetic survey design is the line spacing.
 Further survey design considerations for airborne geophysics are outlined in \textcite{goodwinAirborneMagneticRadiometric2023,islesGeologicalInterpretationAeromagnetic2018,reidAeromagneticSurveyDesign1980}.
@@
 This sufficiently preserves detail in areas of high sampling, while avoiding excessive interpolated cells in areas of low sampling, which may lead to artefacts.
-Because of the sampling frequency of nominally \qty{7}{\m} in the flight line direction, and  up to \qty{400}{\m} in the line-perpendicular direction, the resulting grid resolution will be anisotropic at best, and uniformly low-resolution at worst.
+If the sampling frequency is nominally \qty{7}{\m} in the flight line direction, and up to \qty{400}{\m} in the line-perpendicular direction, the resulting grid resolution will be anisotropic at best, and uniformly low-resolution at worst.
 
 An important property of sampled data is the Nyquist frequency, \[f_{Nyquist} = f_{sampling} / 2.\]
-This is the lowest frequency at which a bandwidth limited signal may be sufficiently sampled, below which higher frequencies will be incorrectly recorded as aliasing.
+This is the lowest frequency \(f\) at which a bandwidth limited signal may be sufficiently sampled, below which higher frequencies will be incorrectly recorded as aliasing.
 An aliased signal contains spurious low-frequency features caused by the sampling, not the underlying signal.
@@
 The smallest resolvable feature in each of these can be spatially described by wavelength, as the inverse of Nyquist frequency.
-In low-resolution aeromagnetic surveys of \qty{400}{\m} line spacing, strong variations of magnetic intensity in the line-perpendicular direction  that occur over a distance shorter than \qty{800}{\m} will be aliased.
+For example, in low-resolution aeromagnetic surveys of \qty{400}{\m} line spacing, strong variations of magnetic intensity in the line-perpendicular direction  that occur over a distance shorter than \qty{800}{\m} will be aliased.
 When gridded at \qty{80}{\m} cell size, the corresponding limit on resolvable detail is features as small as \qty{160}{\m}.
@@
 Depending on the complexity of the geological domain, this may cause spatial aliasing in one direction.
-This is visible in grids where features take on a blocky or stepped appearance, referred to as a beading artefact, or generally in this thesis as a low-resolution artefact.
+This is visible in grids where features take on a blocky or stepped appearance, referred to as  beading, or generally in this thesis, as a low-resolution artefact.
 Low-resolution gridded aeromagnetic data refers to surveys with a wide line spacing causing a lack of high-frequency details in the line-perpendicular direction, resulting in potential artefacts, and overly smooth or missing details in grid data.
@@
 \bigskip{}
-\noindent{}\emph{Resolution refers to the smallest possible geological detail observable in potential field data. High-resolution refers to high frequencies, caused by geology, being represented.}
+\noindent{}\emph{Resolution refers to the smallest possible geological detail observable in potential field data.
+High-resolution refers to high frequencies, caused by geology, being represented in the sampled field.}
 
@@
 \subsection{Traditional methods for enhancing resolution}
-As outlined in \Cref{sec:introgrids}, resolution is a product of sample distance and density, and gridded rasters have a specific number of cells in each axis depending on the spatial extent.
+As outlined in \Cref{sec:introgrids}, resolution is a product of sample distance and sampling density, and gridded rasters have a specific number of cells in each axis depending on the spatial extent.
 Upsampling raster data to larger height and width dimensions is commonplace, and generally performed by numerical image filters such as the cubic spline \parencite{keysCubicConvolutionInterpolation1981} or Lanczos filter \parencite{lanczos1988applied}.
@@
 However, no attempt is made at accurately increasing the high-frequency components of the raster, which are required by our definition for high-resolution geophysics.
+
 Without sampling at a smaller separation or closer line spacing, it is still possible to increase the high-frequency content of aeromagnetic grids.
-
 The rate at which the power of the component frequencies of the potential field diminish with increasing source-sensor distance is well known.
@@
 Like in geophysics, these raster data have an array height and width, which is referred to as resolution.
-However, the lack of spatial quantification for the size of natural images confuses the term with its definition for geophysical resolution.
+However, the lack of spatial quantification for the pixel size of natural images confuses the term with its use in geophysical resolution.
 
@@
 Additionally, the features present within these data are highly dissimilar.
-While natural images may contain common objects which share high-level features such as eyes, faces, or complex geometry, these data only share low-level features with aeromagnetic data, such as simple line and curve components.
+While natural images may contain common objects which share high-level features such as eyes, faces, or the built environment, these data only share low-level features with aeromagnetic data, such as simple line and curve components.
 This fact limits the applicability of transfer learning from methods in computer vision machine learning \parencite{tanSurveyDeepTransfer2018} to geoscience data.
@@
 
-Geoscience data faces a number of challenges distinct from natural images. These have been outlined in \textcite{karpatneMachineLearningGeosciences2019}, and relevant to this work are:
+Geoscience data faces a number of challenges distinct from natural image data. These have been outlined in \textcite{karpatneMachineLearningGeosciences2019}, and relevant to this work are:
 \begin{itemize}
@@
 Inference on real-world data presents many challenges \parencite{nikolenkoSyntheticDataDeep2021,tremblayTrainingDeepNetworks2018}.
-Despite this, case studies are critical in promoting the adoption of applications in geophysics, by demonstrating a methods suitability to the data used within the task of interest.
+Despite this, case studies are critical in promoting the adoption of applications in geophysics, by demonstrating a method's suitability to the data used within the task of interest.
 As such, case studies are investigated for each aim within this thesis.
@@
 Key architectures used in this thesis are described below.
-If the network architecture provides the capacity to store and retrieve learning, the data and training architecture provide the actual instruction and delivery.
+If the network architecture provides the capacity to store and retrieve learning, the data and training architecture provide the actual instruction and mode of delivery.
 There are broadly two classes of training; supervised and unsupervised learning.
@@
 Machine learning is not new to geoscience, and work has been performed on applications in the field for many years.
-Recent reviews have highlighted a rapid increase in machine learning research contributions to Earth science.
-The aims of this thesis are related to specific findings in these review articles.
+Recent reviews have highlighted a rapid increase in machine learning research contributions to Earth science, and the aims of this thesis are related to specific findings in these review articles.
 \textcite{bergenMachineLearningDatadriven2019} recommends the development and use of benchmark datasets and identifies opportunities in the use of transfer learning from synthetic data.
@@
 Additionally, physics-informed learning has been performed with multi-physics integration in \textcite{degen3DMultiphysicsUncertainty2022}.
-Seismic data has been investigated with SR \parencite{liSuperresolutionSeismicVelocity2021}, and with the removal of noise \parencite{liDeepLearningSimultaneous2021}.
+Seismic data has been investigated with SR \parencite{liSuperresolutionSeismicVelocity2021}, and SR with the removal of noise \parencite{liDeepLearningSimultaneous2021}.
 
-Various potential field gridding \parencite{naprstekApplicationsMachineLearning2019,wangDeepLearningGravity2019a} and downward continuation methods \parencite{liStableDownwardContinuation2023,yeHighprecisionDownwardContinuation2022} have been proposed leveraging neural networks.
+Various potential field gridding \parencite{naprstekNewMethodInterpolating2019, wangDeepLearningGravity2019a} and downward continuation methods \parencite{liStableDownwardContinuation2023,yeHighprecisionDownwardContinuation2022} have been proposed leveraging neural networks.
 Finally, in the recent topic of implicit representation there have been several applications proposed, including geological modelling \parencite{hillierGeoINRImplicitNeural2023}.
@@
 
-\section{Research Contributions and Thesis Structure}
+\section{Research contributions and thesis structure}
 This thesis is presented as a series of papers which are published or in-preparation for publication.
-These are presented in \Cref{ch:paper1,ch:paper2,ch:paper3}, each with a brief contextual introduction.
+These are presented in \Cref{ch:paper1,ch:paper2,ch:paper3}, with identification of opportunities for future work described in \Cref{ch:futurework}.
 Key findings and summary conclusions of the research are discussed in \Cref{ch:conclusions}.
@@
 While the baseline model can generalise to real-world data, some incorrect reconstructions remain.
-By fine-tune training the model with transformed real-world state map data, these errors are rectified, and the structural accuracy is improved.
+By fine-tune training the model with real-world state map data, these errors are rectified, and the structural accuracy is improved.
 
@@
 With the proposed method, scattered line data can be encoded into the grid, and cells queried at interpolating coordinates to predict regularised grids.
-CMLP networks are highly suited for processing spatial data such as point sampled geophysics surveys.
+% CMLP networks are highly suited for processing spatial data such as point sampled geophysics surveys.
 Additionally, spatial derivatives are calculated on the learned function directly.
@@
 \Cref{ch:futurework} presents a synthesis discussion for the prior chapters.
-Given the recency of deep learning super-resolution and implicit neural representation, multiple avenues of future opportunities are identified.
-These aim to increase the adoption of super-resolution in geophysics by addressing apprehension toward the reliability of interpretation of the outputs.
+Given the recency of deep learning super-resolution and implicit neural representation for geoscience, multiple avenues of future opportunities are identified.
+These include characterising the practice of super-resolution, and approaches to further enhancement of the methods presented in this thesis.
+% These aim to increase the adoption of super-resolution in geophysics by addressing apprehension toward the reliability of interpretation of the outputs.
 A synthesis comparison of the SR networks adapted in \Cref{ch:paper1,ch:paper2} is also presented, which prompts questions regarding model and dataset construction.

### 2023-10-11 manuscript.tex
LS edits from proof read of print copy

@@
 For each body of work in these topics, real-world geophysical case studies are presented in order to demonstrate the effectiveness and challenges of the method with open access data.
-Each body of work extends deep learning methods described in computer science literature the same year as the development of each respective geophysical method, to keep pace with rapid advances in the field of machine learning.
+Each body of work extends deep learning methods described in computer science literature the same year as the development of the body of work, to keep pace with rapid advances in the field of machine learning.
 
-In the topic of super-resolution, the first method uses convolutional neural networks to enhance the resolution of real magnetic textures in state magnetic grids at a fixed four times scale.
-This is further explored in the second body of work, where synthetic potential field line data are used for model pretraining, to address the lack of survey data with sufficient line spacing variability.
-It quantifies the performance of super-resolution upscaling on real-world low-resolution grids with line spacings between \SI{80}{\m} and \SI{480}{\m}, and investigates the useful limits of upscaling using the method.
+In the topic of super-resolution, the first method uses convolutional neural networks to enhance the resolution of real magnetic textures in state magnetic grids at four times scale.
+This is further explored in the second body of work, where a baseline model is trained with synthetic potential field grid data and fine-tuned with real-world data to address the lack of survey data with sufficient geological representation, and uses a line spacing derived low-resolution transform.
+It quantifies the performance of super-resolution upscaling on real-world low-resolution grids with a line spacing from \SI{320}{\m} to \SI{80}{\m}, and investigates the structural accuracy of the result.
 
 The second topic explores a method for learning a representation of a potential field extent from scattered real-world survey data by a contemporary neural network.
-The data-driven approach can extract high-resolution grids from the learned representation, as well as calculate the analytical spatial gradients.
+The data-driven approach can extract high-resolution grids from the learned representation, as well as calculate analytical spatial gradients.
 Grid rasters and horizontal gradients calculated with the method very closely match their numerical counterparts, however, vertical gradients do not.
@@
 Individually, the methods developed in this thesis enhance the information extractable from potential field surveys.
-However, in combination, and together they reflect ongoing advances in deep learning and their extension to challenges and opportunities in geophysics.
+However, together they reflect ongoing advances in deep learning and their extension to challenges and opportunities in geophysics.
 
@@
 
-I wish to thank a great number of people who have contributed to my ongoing development.
+I wish to thank a great number of people who have contributed to my journey.
+
 First, to my supervisors:
@@
 Naveed, whose perspective was invaluable.
-Andie, Dale, and Robert, and the rest of my family in NSW --- I didn't get to visit as much as I had originally planned in 2019, but we made the most of it!
+
+My family in NSW, Andie, Dale, and Robert --- I didn't get to visit as much as I had originally planned in 2019, but we made the most of it!
 Thanks for the support and encouragement, and imparting all the passions of rocks, computers, and tinkering that I have today.
+
 Tasman, for being a good friend and inspirational colleague for most of my academic career --- looking forward to sharing a project again sometime, somewhere in the future!
@@
 Matilda, for being a wonderful friend and the best housemate --- Thanks for being silly with me.
-My first floor colleagues and fellow tech geeks, Daniel, David, Chris, Minh, and Peter --- Your friendship and knowledge has been a wonderful environment to grow as a geodata scientist in.
+
+My first floor colleagues and fellow tech geeks, David, Daniel, Chris, Minh, and Peter --- Your friendship and knowledge has been a wonderful environment to grow in as a geodata scientist.
 And all my SES, CET, and friends beyond: Alex, Anne, Ben, France, Jackson, Jules, Kailah, Lauren, Lauri, Liam, Lilly, Maddie, Maria, Malvina, Nicolas, Ravi, Sean, Sumail, Vickie, and Ze --- Thank you for years of lunches, dinners, beaches, rock climbing, yoga, and all the opportunities to talk rocks that I've been missing.
+
 And to all the teachers throughout my life, both professional and incidental: Thank you.
@@
 
-\chapter[Magnetic Grid Resolution Enhancement using ML]{Magnetic Grid Resolution Enhancement using Machine Learning}
+\chapter[Magnetic Grid Resolution Enhancement Using ML]{Magnetic Grid Resolution Enhancement Using Machine Learning}
 \label{ch:paper1}

### 2023-10-11 paper1.tex
LS edits from proof read of print copy

@@
 
+\bigskip
 \begin{abstract}
@@
 
-\section{Materials and Methods}
+\section{Materials and methods}
 \subsection{Geophysical context}
@@
 
-\subsection{Accuracy Metrics}
+\subsection{Accuracy metrics}
 The functional aim of super-resolution geophysics is to accurately predict realistic high frequency details to add to a low-resolution grid.
@@
 \begin{figure}[hbtp]
-    \includegraphics[width=\linewidth]{fig/p1/filtered.png}
+    \includegraphics[width=\linewidth,trim={0 0 0 -5mm},clip]{fig/p1/hpfilt.jpg}
     \caption[High Pass filtered results]{High pass filtered test tile and its upsampled counterparts.
@@
 \begin{figure}[hbtp]
-    \includegraphics[width=\linewidth,trim={0 0 0 0},clip]{fig/p1/jhillvis.jpg}
+    \includegraphics[width=\linewidth,trim={0 0 0 0},clip]{fig/p1/1vd.jpg}
     \caption[First Vertical Derivative SR TMI over the Mt Mason resource project]{First Vertical Derivative TMI over the Mt Mason resource project, with the super-resolution predictions (d, e) showing a variety of inference artefacts.
@@
 
-% \section{Declaration of Competing Interest}
+% \section{Declaration of competing interest}
 % The authors declare the following financial interests / personal relationships which may be considered as potential competing interests: This work was supported by a Rio Tinto Iron Ore PhD scholarship.

### 2023-10-11 paper2.tex
LS edits from proof read of print copy

@@
 This method uses transfer learning \parencite{tanSurveyDeepTransfer2018} from magnetic data forward modelled from a collection of synthetic geological models with varied histories \parencite{jessellNoddyverseMassiveData2022}, and fine tuning with real-world data.
-SR employed in this work leverages a contemporary neural network \parencite{leeLocalTextureEstimator2022}, with a realistic method for sampling high-resolution grids and gridding them to low-resolution.
+SR employed in this work leverages a contemporary neural network \parencite{leeLocalTextureEstimator2022}, with a realistic method for sampling and gridding high- and low- resolution data.
 The method is suitable for typical low-resolution regional aeromagnetic surveys in Australia.
@@
 
-\section{Data and Experimental Methods}
+\section{Data and experimental methods}
 \label{sec:2methods}
@@
 \label{sec:2results}
-\subsubsection{Quantitative Measure}
+\subsubsection{Quantitative measure}
 Due to the dynamic range of magnetic anomaly grids and the relative importance of structural accuracy for gridded data, image quality assessment methods typically used for RGB images such as peak signal-to-noise ratio or mean-squared error are an inadequate quantitative measure of upscaling performance for geophysics.

### 2023-10-11 paper3.tex
LS edits from proof read of print copy

@@
 Geophysical potential fields are routinely collected and used to assist the understanding of the subsurface for geoscience and mineral exploration.
-When surveying these fields, which are continuous functions in three dimensions, sample locations are scattered in 3D space, despite best efforts to conform to a regularly spaced line plan.
+When surveying these fields, which are continuous functions in three dimensions, sample locations are scattered in 3D space, despite best efforts to conform to a regularly spaced line survey.
 These scattered data are typically regularised to a quantised grid for subsequent interpretation, which imposes a new limit on high frequency content and gives rise to spurious artefacts that are a product of the gridding process, not the surveyed field.
@@
 Neural networks can be considered as universal function approximators.
-The recent technique of deep learning implicit neural representation (INR) \parencite{mildenhallNeRFRepresentingScenes2020} represents a signal as a function of its coordinates, built on a network architecture known as a coordinate multilayer perceptron (CMLP;\ see \textcite{ramasinghePeriodicityUnifyingFramework2022} for a recent introduction).
+The recent technique of deep learning implicit neural representation (INR) \parencite{mildenhallNeRFRepresentingScenes2020}, built on a network architecture known as a coordinate multilayer perceptron (CMLP;\ see \textcite{ramasinghePeriodicityUnifyingFramework2022} for a recent introduction), represents a signal as a function of its coordinates.
 By parameterising the function in coordinate space, novel values of the function can be queried at arbitrary coordinates within the learned continuous spatial domain.
-Recent advances in CMLPs by using periodic activations such as sinusoids have demonstrated that high frequency information can be modelled well by CMLP networks, while being continuously differentiable throughout the depth of the network.
+Recent advances in CMLPs using periodic activations such as sinusoids have demonstrated that high frequency information can be modelled well by CMLP networks, while being continuously differentiable throughout the depth of the network.
 
 We present a novel method of encoding a representation of a geophysical potential field using INR\@.
-This method contributes a novel method of creating level grids from scattered aeromagnetic data.
-In our method, due to using a continuous coordinate representation, there is no dependency on grid quantisation from an initial cell size selection.
-The proposed technique also provides for further processing that can be calculated analytically in the continuous spatial domain, allowing the use of all available sample information in these calculations.
+This contributes a novel method of creating regular grids from scattered aeromagnetic data.
+Due to the continuous coordinate representation, there is no dependency on grid quantisation from an initial cell size selection.
+Additionally, we use the automatic differentiation package used to train the network to calculate spatial gradients, without the need for gridding.
+% The proposed technique also provides for further processing that can be calculated analytically in the continuous spatial domain, allowing the use of all available sample information in these calculations.
 
@@
 
-INR and CMLP have recently emerged in the literature, and our proposed method stands to benefit from ongoing research in these highly active fields.
+INR and CMLP have recently emerged in the literature, and the capacity of geophysics INR to represent high frequencies stands to improve from ongoing research in these highly active fields.
 
@@
 \end{equation}
-where \(\phi{}\) is the potential, and \(x, y, \) and \(z\) are the three spatial dimensions.
+where \(\phi{}\) is the potential, and \(x,\ y,\ \) and \(z\) are the three spatial dimensions.
 
@@
 
-A classic example of an MLP is using an input vector of image pixel intensities \(u\), and an output vector of class labels \(l\).
+A classic example of an MLP is using a structured input vector of image pixel intensities \(u\), and an output vector of class labels \(l\).
 Training this example network with a large number of different images with class labels produces a model capable of predicting the class of novel input image vectors.
-A CMLP for representing images instead takes an input of explicitly stated pixel coordinates \((x, y)\), and an output vector of image pixel intensities \(u\) at those coordinates.
-Thus training of a CMLP network requires a set of input coordinates and intensities from a single image, and results in a model capable of predicting the intensity of any arbitrary continuous coordinate within the input domain.
-Both tasks may use similar images and an MLP network structure with the same \(n\) hidden layers and \(m\) features, but the use of coordinates as inputs and intensities as outputs changes the predictive task.
+A CMLP for representing images instead takes an input of an explicitly stated pixel coordinate \((x,\ y)\), and an output vector of image pixel intensities \(u\) at that coordinate.
+Training of a CMLP network requires a batch of input coordinates and intensities from a single image, and results in a model capable of predicting the intensity of any arbitrary continuous coordinate within the input domain.
+Both tasks may use similar images and an MLP network structure with the same \(n\) hidden layers and \(m\) features, but the size of the input layer, and use of intensities as outputs changes the predictive task.
 CMLP networks for predicting 3D scalar fields are a class of neural networks \(f\) which train \(u = f(x, y, z)\), with \(u\in\mathbb{R}^1\) and \((x, y, z)\in\mathbb{R}^3\).
@@
 When replacing positional encoding and the ReLU activation with periodic activation functions such as the sinusoid \parencite{sitzmann2019siren} the high frequency representation of CMLP networks is significantly enhanced.
-Periodic activation functions differ from typical non-linear activations by comprising the neuron with a function that repeats periodically, which allows for continuous differentiation throughout the depth of the network.
-Work by \textcite{ramasinghePeriodicityUnifyingFramework2022} revealed that it is the magnitude of the first and second derivatives of the activation that enhanced high-frequency representation learning capacity, rather than periodicity, leading to Gaussian \parencite{ramasinghePeriodicityUnifyingFramework2022} and wavelet \parencite{saragadamWIREWaveletImplicit2023} activation functions for CMLP\@.
+Periodic activation functions differ from typical non-linear activations by comprising the neuron with an activation function that repeats periodically, allowing for continuous differentiation throughout the depth of the network.
+Work by \textcite{ramasinghePeriodicityUnifyingFramework2022} revealed that it is the magnitude of the first and second derivatives of the activation that enhanced high-frequency representation learning capacity, rather than the periodicity, leading to Gaussian \parencite{ramasinghePeriodicityUnifyingFramework2022} and wavelet \parencite{saragadamWIREWaveletImplicit2023} activation functions for CMLP\@.
 
@@
 Research directions include leveraging new activation functions \parencite{saragadamWIREWaveletImplicit2023}, transforming the input space \parencite[e.g.][]{benbarkaSeeingImplicitNeural2022} or using additional constraints on the search space such as physics-informed neural networks \parencite{raissiPhysicsinformedNeuralNetworks2019}.
-In geoscience, INR has been used for numerical modelling \parencite{hillierGeoINRImplicitNeural2023}.
+In geoscience, INR has been used for geological modelling \parencite{hillierGeoINRImplicitNeural2023}.
 
@@
 While recovery of potential field grids using a compressed sensing approach is often framed as a numerical optimisation problems \parencite[e.g.][]{yangAirborneGravimetryData2015,xuGravityAnomalyReconstruction2019}, these are not equivalent to modern deep learning approaches.
+Compressed sensing recovers the signal through linear transformations, while neural networks allow convenient modelling of non-linear transformations.
 Compressed sensing relies on the theory that a signal has a sparse representation in some transform domain, and a deeper exploration of the comparison between INR and compressed sensing remains to be performed.
-Compressed sensing recovers the signal through linear transformations, while neural networks allow convenient modelling of non-linear transformations.
 
-\subsection{Automatic Differentiation}
+\subsection{Automatic differentiation}
 Automatic differentiation (AD) refers to one of several methods for computing derivatives, specifically to the method of accumulating derivatives during function evaluation \parencite{baydinAutomaticDifferentiationMachine2018}.
@@
 In these frameworks, training is performed by evaluating a set of inputs using the current model parameters during a forward pass, while accumulating the partial derivatives of the result with respect to those parameters, to optimise an objective (loss) function.
-These gradients inform parameter update operations to minimise the model loss.
-However, automatic differentiation can also evaluate the derivatives of the network output with respect to the inputs, using the same high-performance AD framework.
+These gradients inform the parameter update operations to minimise the model loss.
+However, AD can also evaluate the derivatives of the network output with respect to the inputs, using the same high-performance AD framework.
 This can directly provide the partial derivatives of the potential field with respect to its coordinates \(\frac{\partial\phi{}}{\partial x}, \frac{\partial \phi{}}{\partial y}, \frac{\partial \phi{}}{\partial z}\), as well as higher order derivatives, without first requiring gridding.
@@
 This implicit representation is used to generate two-dimensional levelled grids directly from scattered sample data, by querying the representation with regularly spaced grid nodes at a constant level.
-Partial derivatives can be calculated on the representation itself, remaining in the continuous coordinate domain.
-These are compared against a case study reference grid from Geoscience Australia, with gradients from numerical derivative calculation.
+Partial derivatives can be calculated of the representation function (the model) itself, remaining in the continuous coordinate domain.
+These are compared against a case study reference grid from Geoscience Australia, and against gradients from numerical derivative calculation.
 % An overview diagram is presented in \Cref{fig:overview}.
@@
 Prominently featured in the survey are the circular crater rim, and two East-West trending linear dune features to the North of the survey extent.
-The data used for implicit representation excludes the survey tie lines, typically used in airborne geophysical surveys to reduce inter-line levelling noise.
-The mean altitude of the drape surface excluding tie lines is \qty{39.5}{\m}, with a standard deviation of \qty{4.5}{\m}.
+The data used for implicit representation excludes the survey tie lines, normally used in airborne geophysical surveys to reduce inter-line levelling noise.
+The mean terrain clearance (altitude) of the drape surface excluding tie lines is \qty{39.5}{\m}, with a standard deviation of \qty{4.5}{\m}.
 The sample locations and recorded altitudes are shown in \Cref{fig:samples}, where it can be seen the crater rim topography causes large deviations in elevation from the nominal drape.
@@
 
-Both the line data and grid raster netCDFs for the Wolfe Creek survey were downloaded from Geoscience Australia \footnote{https://pid.geoscience.gov.au/dataset/ga/142694} (GA) and used without further processing.
+Both the line data and grid raster netCDFs for the Wolfe Creek survey were downloaded from Geoscience Australia (GA) \footnote{https://pid.geoscience.gov.au/dataset/ga/142694} and used without further processing.
 The line data netCDF contains tie-levelled, micro-levelled, and AWAGS levelled magnetic variables, in increasing stages of processing respectively.
-The micro-levelled magnetic data are used in this case study because the original sample altitude is uncertain in the available levelled data.
-Either a geographic and projected coordinate system can be used, provided the query coordinates for inference match those used during training.
+The micro-levelled magnetic data are used in this case study because the originally recorded sample altitude is uncertain in the available levelled data.
+Either a geographic and projected coordinate system can be used, provided for consistency between the query coordinates for inference and those used during training.
 The three spatial coordinate dimensions are independently and linearly min-max normalised between \num{-1} and \num{1}.
@@
 The number of input features is 3, for each spatial dimension, and the number of output features is 1, for the predicted potential field value at those coordinates.
-Comparison of recently proposed activatons and hyperparameters for CMLP is performed by \textcite{saragadamWIREWaveletImplicit2023}, where increasing both \(n\) and \(m\) increases the capacity of the model, at the cost of computational requirements.
-High quality implicit representation is typically achievable with the number hidden layers between \num{3} and \num{8}, and number of neurons per layer up to \num{256}.
+Comparison of recently proposed activations and hyperparameters for CMLP is performed by \textcite{saragadamWIREWaveletImplicit2023}, where increasing both \(n\) and \(m\) increases the capacity of the model, at the cost of computational requirements.
+High quality implicit representation is typically achieved with a number of hidden layers between \num{3} and \num{8}, and a number of neurons per layer up to \num{256}.
 Empirically, the quality of the high-resolution representation continued to improve with increasing both \(n\) and \(m\).
@@
 The entire case study line data fit in a single batch within the available graphics memory, and can be trained using batch gradient descent.
-Each sample in the batch is a single 3D survey point with the associated 1D target potential field value.
+Each sample in the batch is a single \(\mathbb{R}^{3}\) survey point with the associated \(\mathbb{R}^{1}\) target potential field value.
 % However, if training on larger aeromagnetic surveys, memory becomes a constraint and mini-batch training is required.
@@
 \subsection{Derivative calculation}
-A naive approach to calculating gradients with the trained INR would be to evaluate the representation \(f(x, y, z)\) at a set of coordinates \({(x, y, z)}_1 \dots {(x, y, z)}_n\), and use numerical differentiation with the output grid to calculate derivatives.
+A naive approach to calculating gradients with the trained INR would be to evaluate the representation \(f(x, y, z)\) on a regular grid of coordinates \({(x, y, z)}_1 \dots {(x, y, z)}_n\), and use numerical differentiation with the output grid to calculate derivatives.
 However, using AD with Pytorch, the implicit representation can be differentiated with respect to its coordinate inputs to provide spatial gradients, prior to being queried at the nodes of a quantised grid.
@@
 \section{Results}
-\subsection{Level grid prediction from INR}
-Querying a learned INR using a regularly spaced \(x, y\) grid at a specific \(z\) height is a novel method for producing level grids from geophysical potential field surveys.
-The cell size can be selected using a finer or coarser \(x, y\) spacing, including variable or anisotropic cell sizes.
+\subsection{Grid prediction from implicit neural representation}
+Querying a learned INR using a regularly spaced \(x,\ y\) grid at a specific \(z\) height is a novel method for producing regular grids from geophysical potential field surveys.
+The cell size can be selected using a finer or coarser \(x,\ y\) spacing, including variable or anisotropic cell sizes.
 Contemporary super-resolution research can leverage this continual representation as a framework for high quality arbitrary scale factor high-frequency signal prediction \parencite[e.g][]{chenLearningContinuousImage2021}.
@@
 
-\subsection{Future Work}
+\subsection{Future work}
 \label{sec:future}
@@
 Initial attempts using the objective function approach were trialled in this work, but struggled to converge and remain for future work.
-It may be worth investigating other geophysical formulae for PINN implementation, such as vertical continuation described in \textcite{blakelyPotentialTheoryGravity1996}.
+It may be worth investigating other geophysical formulae for PINN implementation, such as vertical continuation, described in \textcite{blakelyPotentialTheoryGravity1996}.
 
@@
 Level grids can be extracted from these representations, emerging as a novel method for regularising scattered geophysical sample data.
-Sptaial gradients can be calculated directly from the learned representation, and can be queried at arbitrary locations.
+Spatial gradients can be calculated directly from the learned representation, and can be queried at arbitrary locations.
 Regularly sampled grids of the gradients are near-identical to those calculated by existing numerical methods, and benefit from being gridded after gradient calculation.

### 2023-10-11 discussion.tex
Short titles for figures, fix cites

@@
     \includegraphics[width=\linewidth]{fig/etc/TMI Comparison_23.pdf} % TODO Update for RDN\textdaggerdbl{}, ESRGAN, LTE, ~3 hours ea.
-    \caption{
+    \caption[Comparison between the three SR architectures]{
         A comparison between all deep learning super-resolution methods presented in \Cref{ch:paper1} and \Cref{ch:paper2}, using the realistic low-resolution transform developed in \Cref{ch:paper2}.

### 2023-10-11 intro.tex
Short titles for figures, fix cites

@@
 Scattered surveys are commonly interpolated to grid rasters, and interpreted individually or integrated with other datasets for predicting the subsurface for processes such as numerical modelling and inversion.
-In these tasks, the spatial resolution of the grid is a critical factor in their ability to define geological detail \parencite{islesGeologicalInterpretationAeromagnetic2018}.
+In these tasks, the spatial resolution of the grid is a critical factor in their ability to define geological detail \parencite{islesGeologicalInterpretationAeromagnetic2013}.
 The role of high-resolution details in these geophysical methods is becoming more important to exploration as resources are increasingly sought from below sedimentary cover.
@@
 Surveys are flown with a heading in which data will be acquired along line.
-For regional and contemporary surveys this is recommended to be North-South, however, early practice was to survey perpendicular to the dominant geological strike, under the expectation of sampling the greatest frequency of change in magnetic intensity \parencite{islesGeologicalInterpretationAeromagnetic2018}.
+For regional and contemporary surveys this is recommended to be North-South, however, early practice was to survey perpendicular to the dominant geological strike, under the expectation of sampling the greatest frequency of change in magnetic intensity \parencite{islesGeologicalInterpretationAeromagnetic2013}.
 Acquisition along flight lines is sampled at a rate of \qty{10}{\hertz} or greater, which corresponds to an interval of \qty{7}{\m} or shorter at nominal flight speeds of \qty{70}{\m\per\s} \parencite{goodwinAirborneMagneticRadiometric2023}.
@@
 In interpolated grids the spatial dimension of each cell is referred to as the cell size.
-As previously stated, resolvable detail in geophysical surveys is a product of the distance between the causative magnetic body and the sensor, and the line spacing \parencite{islesRelationshipsGeologicalResolution1992,islesGeologicalInterpretationAeromagnetic2018,dentithGeophysicsMineralExploration2014}.
+As previously stated, resolvable detail in geophysical surveys is a product of the distance between the causative magnetic body and the sensor, and the line spacing \parencite{islesRelationshipsGeologicalResolution1992,islesGeologicalInterpretationAeromagnetic2013,dentithGeophysicsMineralExploration2014}.
 Height is controlled by flying the lowest safe and sufficiently smooth topography drape, and along-line sampling is performed at a constant high rate, so the key factor controlling resolution in aeromagnetic survey design is the line spacing.
-Further survey design considerations for airborne geophysics are outlined in \textcite{goodwinAirborneMagneticRadiometric2023,islesGeologicalInterpretationAeromagnetic2018,reidAeromagneticSurveyDesign1980}.
+Further survey design considerations for airborne geophysics are outlined in \textcite{goodwinAirborneMagneticRadiometric2023,islesGeologicalInterpretationAeromagnetic2013,reidAeromagneticSurveyDesign1980}.
 Each gridding method includes a final cell size parameter selectable by the geophysicist, with a long-standing guideline of one third to one fifth the line spacing.
@@
 Rock microscopy images have been upsampled with SR \parencite{niuInnovativeApplicationGenerative2020}, and their accuracy compared using domain specific parameter calculation.
-SR with physics-informed learning has been performed by \textcite{bodeUsingPhysicsinformedEnhanced2021,jiangMeshfreeFlowNetPhysicsConstrainedDeep2020} in the field of fluid dynamics, \textcite{leongDeepBedMapDeepNeural2020} in the field of basement topography, and \textcite{jungbluthSingleframeSuperresolutionSolar2019} in astrophysics.
+SR with physics-informed learning has been performed by \textcite{bodeUsingPhysicsinformedEnhanced2021,jiangMeshfreeFlowNetPhysicsconstrainedDeep2020} in the field of fluid dynamics, \textcite{leongDeepBedMapDeepNeural2020} in the field of basement topography, and \textcite{jungbluthSingleframeSuperresolutionSolar2019} in astrophysics.
 Additionally, physics-informed learning has been performed with multi-physics integration in \textcite{degen3DMultiphysicsUncertainty2022}.

### 2023-10-11 paper1.tex
Short titles for figures, fix cites

@@
     \includegraphics[width=\linewidth]{fig/p1/rdb.png}
-    \caption[Basic Blocks]{Each Basic Block (\Cref{fig:rdn}, orange) comprises three weighted Residual Dense Blocks (\Cref{fig:convs}).
+    \caption[Basic blocks]{Each Basic Block (\Cref{fig:rdn}, orange) comprises three weighted Residual Dense Blocks (\Cref{fig:convs}).
         ESRGAN+ extends ESRGAN with the addition of Gaussian Noise after each basic RDB block (black vectors).
@@
 The functional aim of super-resolution geophysics is to accurately predict realistic high frequency details to add to a low-resolution grid.
-To quantify this, we calculate root mean square error (RMSE) and structural similarity metrics (SSIM and MS-SSIM), on TMI, high pass filtered TMI, and first vertical derivative (1VD) filtered TMI results for each upsampling method across several sample extents.
+To quantify this, we calculate root mean square error (RMSE) and structural similarity metrics (SSIM and MS-SSIM), on TMI, high-pass filtered TMI, and first vertical derivative (1VD) filtered TMI results for each upsampling method across several sample extents.
 Euclidean accuracy measures like RMSE quantify the per-pixel accuracy of a predicted grid compared to its corresponding high-resolution ground truth grid.
@@
 Results are presented to compare the three methods described above, with the metrics of RMSE, SSIM and MS-SSIM, as well as observed perceptual quality.
-In addition to unfiltered TMI comparisons, high pass filtered and first vertical derivative TMI grids are also shown.
+In addition to unfiltered TMI comparisons, high-pass filtered and first vertical derivative TMI grids are also shown.
 These products are commonly used in geophysics to investigate high frequency components in grids.
@@
     \includegraphics[width=\linewidth]{fig/p1/rapsd.jpg}
-    \caption[short]{Radially Averaged Power Spectra for the complete test extent shown in \Cref{fig:trainvaldata}.
+    \caption[Power spectra for the test extent]{Radially Averaged Power Spectra for the complete test extent shown in \Cref{fig:trainvaldata}.
         The Nyquist wavelengths for the high-resolution (and upsampled) rasters and low-resolution raster are also shown.
@@
 
-To visualise the contribution of these enhanced high frequencies in the resulting grid, the super-resolved output from each method is high pass filtered, with a cut-off wavelength equivalent to the Nyquist wavelength of the LR grid.
+To visualise the contribution of these enhanced high frequencies in the resulting grid, the super-resolved output from each method is high-pass filtered, with a cut-off wavelength equivalent to the Nyquist wavelength of the LR grid.
 By filtering at this wavelength, only frequencies added by the upsampling process will be shown in the output (\Cref{fig:filtered}).
@@
     \includegraphics[width=\linewidth,trim={0 0 0 -5mm},clip]{fig/p1/hpfilt.jpg}
-    \caption[High Pass filtered results]{High pass filtered test tile and its upsampled counterparts.
-        The cut-off for the high pass Butterworth filter was selected with wavelength equal to the Nyquist wavelength of the LR grid, i.e.,\ four times the HR Nyquist wavelength.
+    \caption[High-pass filtered results]{High-pass filtered test tile and its upsampled counterparts.
+        The cut-off for the high-pass Butterworth filter was selected with wavelength equal to the Nyquist wavelength of the LR grid, i.e.,\ four times the HR Nyquist wavelength.
     }
@@
     \includegraphics[width=\linewidth,trim={0 0 0 0},clip]{fig/p1/1vd.jpg}
-    \caption[First Vertical Derivative SR TMI over the Mt Mason resource project]{First Vertical Derivative TMI over the Mt Mason resource project, with the super-resolution predictions (d, e) showing a variety of inference artefacts.
+    \caption[First vertical derivative over the case study grid]{First Vertical Derivative TMI over the Mt Mason resource project, with the super-resolution predictions (d, e) showing a variety of inference artefacts.
     Red asterisks (*) show a vertical tile boundary present as a 3--4 pixel-wide error in predicted TMI value.
@@
     \includegraphics[width=0.7\linewidth]{fig/p1/transectp.png}
-    \caption[Jasper Hills Project TMI grids and line profile]{Jasper Hills Project TMI grids (a--e) and line profile (f).
+    \caption[Case study TMI grids and line profiles]{Jasper Hills Project TMI grids (a--e) and line profile (f).
         Bicubic interpolation of the low-resolution grid closely matches the low-resolution grid, while both super-resolution methods better approximate the magnitude of the features present in the HR profile, between \qty{650}{\metre} and \qty{1020}{\metre}.

### 2023-10-11 paper2.tex
Short titles for figures, fix cites

@@
     \includegraphics[width=\linewidth]{fig/p2/temp_lte.png}
-    \caption[The LTE network]{
+    \caption[The LTE architecture]{
         A simplified representation of the super-resolution LTE network.
@@
     \includegraphics[width=0.9\linewidth]{fig/p2/srcomp_23.pdf}
-    \caption[Super-resolution geophysics grid results]{Super-resolution predictions on open access data, prepared using the proposed method.
+    \caption[Super-resolution geophysics grid results I]{Super-resolution predictions on open access data, prepared using the proposed method.
         Explanation in-text.
@@
     \includegraphics[width=0.9\linewidth]{fig/p2/srcomp_14.pdf}
-    \caption[Super-resolution geophysics grid results]{Super-resolution predictions on open access data, prepared using the proposed method.
+    \caption[Super-resolution geophysics grid results II]{Super-resolution predictions on open access data, prepared using the proposed method.
         Explanation in-text.
@@
     \includegraphics[width=0.9\linewidth]{fig/p2/srcomp_17.pdf}
-    \caption[Super-resolution geophysics grid results]{Super-resolution predictions on open access data, prepared using the proposed method.
+    \caption[Super-resolution geophysics grid results III]{Super-resolution predictions on open access data, prepared using the proposed method.
         Explanation in-text.
@@
     \includegraphics[width=0.9\linewidth]{fig/p2/srcomp_18.pdf}
-    \caption[Super-resolution geophysics grid results]{Super-resolution predictions on open access data, prepared using the proposed method.
+    \caption[Super-resolution geophysics grid results IV]{Super-resolution predictions on open access data, prepared using the proposed method.
         Explanation in-text.

### 2023-10-12 discussion.tex
Update comparison figure

@@
 Here, the use of synthetic and real-world line spacing sampled data approach used with LTE in \Cref{ch:paper2} are adopted for the RDN\textdaggerdbl{} and ESRGAN+ models.
-\Cref{fig:modcomp} shows RDN\textdaggerdbl{} and ESRGAN+ in predicting accurate features when upscaling \qty{320}{\m} data to \qty{80}{\m} line spacing.
-It can be inferred that the challenge of super-resolution for these tasks is predominantly a question of providing suitable and sufficient training data, and is less constrained to neural network choices.
+\Cref{fig:modcomp} shows RDN\textdaggerdbl{}, ESRGAN+, and LTE predicting accurate structural features when upscaling \qty{320}{\m} data to \qty{80}{\m} line spacing.
+While each model has different hyperparameters due to the different architectures in use, the SR prediction converges toward similar structures, with ESRGAN+ containing additional noise.
+It can be interpreted that the challenge of super-resolution for this tasks is predominantly a question of providing suitable and sufficient training data, and is less constrained to neural network choices.
 
-\begin{figure}
-    \includegraphics[width=\linewidth]{fig/etc/TMI Comparison_23.pdf} % TODO Update for RDN\textdaggerdbl{}, ESRGAN, LTE, ~3 hours ea.
+\begin{landscape}
+    \begin{figure}[hbtp]
+        \includegraphics[width=\linewidth,trim={0 0 0 5mm},clip]{fig/etc/model_comparison_v2.pdf}
         \caption[Comparison between the three SR architectures]{
             A comparison between all deep learning super-resolution methods presented in \Cref{ch:paper1} and \Cref{ch:paper2}, using the realistic low-resolution transform developed in \Cref{ch:paper2}.
-        a) The low-resolution input, b) The high-resolution target, c) The RDN\textdaggerdbl{}+ Network, d) The ESRGAN+ network, and e) The LTE network.}
+            a) The low-resolution input, b) The high-resolution target, c) The RDN\textdaggerdbl{} SR prediction, d) The ESRGAN+ SR prediction, and e) The LTE SR prediction.}
+        The baseline model for c) and d) was trained for 7 hours on the synthetic dataset described in \Cref{sec:2methods}.
+        c) was fine-tuned for 1.5 hours, while d) was fine-tuned for 4.3 hours.
+        The training of e) is described in \Cref{sec:finetune}.
         \label{fig:modcomp}
     \end{figure}
+\end{landscape}
 

### 2023-10-12 paper1.tex
Improve layout of paper 1

@@
 \begin{figure}[hbtp]
+    \centering
     \includegraphics[width=\linewidth]{fig/p1/lrandhr.jpg}
@@
 \begin{figure}[hbtp]
+    \centering
     \includegraphics[width=\linewidth]{fig/p1/rdn.png}
@@
 \begin{figure}[hbtp]
+    \centering
     \includegraphics[width=\linewidth]{fig/p1/rdb.png}
@@
 \begin{figure}[hbtp]
-    \includegraphics[width=\linewidth]{fig/p1/convs.png}
+    \centering
+    \includegraphics[width=0.75\linewidth]{fig/p1/convs.png}
     \caption[RDB convolutional layers]{Each Residual Dense Block (\Cref{fig:rdb}, purple) comprises four convolutional layers, with additional learning pathways present as residual connections (black), and dense connections (green).
@@
 That is, the same model can learn from fine optimal cell size extents that lose many component frequencies when interpolated to \qty{80}{\metre}, as well as coarse cell size extents which may only lose few or none.
+
 These data were extracted as square tiles, each covering \qty{2560}{\metre} by \qty{2560}{\metre} at 32 \texttimes{} 32 pixels for LR, and 128 \texttimes{} 128 pixels for HR, with no overlap.
@@
 These values were min-max scaled to a range of 0 to 1 using the global minimum and maximum values of the HR training data.
+
 In summary, the single channel high- and low-resolution state TMI grids were filtered according to a database of their component surveys to extract areas of \qty{300}{\metre} line spacing or less.
@@
 \begin{figure}[hbtp]
-    \centering{}
+    \centering
     \includegraphics[width=0.75\linewidth]{fig/p1/trainvaldata.png}
@@
 Further measures for the suppression of overfitting inherent to each of the applied architectures are described in their respective manuscripts \parencite{wangESRGANEnhancedSuperresolution2018,zhangResidualDenseNetwork2018}.
+
 The optimiser used was Adam \parencite{kingmaAdamMethodStochastic2015}.
 The learning rate was adjusted over the course of the experiment using the Pytorch implementation of One Cycle Learning Rate scheduler \parencite{smithSuperconvergenceVeryFast2018}, which provides a “warm up” period to stabilise early predictions, and a “cool down” period where the loss minima is fine tuned.
+
 Following the generator implementation from ESRGAN+, twenty-three Residual Dense Blocks were ordered sequentially to form the main network, followed by two nearest neighbour upsampling filters at two times scale each.
@@
 RDN\textdaggerdbl{} had a peak learning rate of \num{3e-4} and did not require loss component weighting because only L1 pixel loss is used.
+
 Bicubic interpolation was carried out using the implementation provided in Pillow \parencite{vankemenadePythonpillowPillow2021}, a ubiquitous open source Python imaging library.
@@
 \subsection{Test dataset}
-We first present a visual comparison of a selected feature rich \qty{80}{\metre} cell size LR tile, its counterpart \qty{20}{\metre} HR ground truth tile, and the result of; the bicubic upscaling filter, the RDN\textdaggerdbl{} upsampling network, and the ESRGAN+ upsampling network as applied to the LR tile (\Cref{fig:resultsvis}).
+We present a visual comparison of a selected feature rich \qty{80}{\metre} cell size LR tile, its counterpart \qty{20}{\metre} HR ground truth tile, and the result of; the bicubic upscaling filter, the RDN\textdaggerdbl{} upsampling network, and the ESRGAN+ upsampling network as applied to the LR tile (\Cref{fig:resultsvis}).
 This tile was selected from the reserved test region in the Eastern Goldfields Superterrane, and neither of the low- or high-resolution samples were seen during training.
@@
 
+\Cref{fig:residuals} demonstrates the error residuals between the predicted TMI grids for each upsampling method and the HR ground truth.
+For the selected tile, the RMSE is best minimised using RDN\textdaggerdbl{}, which also shows the best structural metric performance.
+ESRGAN+ outperforms the bicubic method in RMSE and MSSIM\@.
+
+\begin{landscape}
     \begin{figure}[hbtp]
+        \centering
         \includegraphics[width=\linewidth,trim={0 0 0 5mm},clip]{fig/p1/resultsvis.png}
@@
     \end{figure}
+\end{landscape}
 
-\Cref{fig:residuals} demonstrates the error residuals between the predicted TMI grids for each upsampling method and the HR ground truth.
-For the selected tile, the RMSE is best minimised using RDN\textdaggerdbl{}, which also shows the best structural metric performance.
-ESRGAN+ outperforms the bicubic method in RMSE and MSSIM\@.
-
+\begin{landscape}
     \begin{figure}[hbtp]
+        \centering
         \includegraphics[width=\linewidth,trim={0 10mm 0 5mm},clip]{fig/p1/residuals.png}
@@
     \end{figure}
+\end{landscape}
 
@@
 \begin{figure}[hbtp]
+    \centering
     \includegraphics[width=\linewidth]{fig/p1/rapsd.jpg}
@@
 Finally, metrics for the full set of test tiles are reported in \Cref{tab:metrics}.
+
+\begin{table}[hbtp]
+    \centering
+    \begin{tblr}{
+            colspec={
+                    r |
+                    Q[si={table-format=2.3},r]
+                    Q[si={table-format=2.3},l] |
+                    Q[si={table-format=2.3},r]
+                    Q[si={table-format=2.3},l] |
+                    Q[si={table-format=2.3},r]
+                    Q[si={table-format=2.3},l] |
+                },
+            row{1} = {guard}
+        }
+                & \SetCell[c=2]{c} Bicubic &            & \SetCell[c=2]{c} RDN\textdaggerdbl{} &                 & \SetCell[c=2]{c} ESRGAN+              \\
+        \hline{}
+                & \(\mu\)                  & \(\sigma\) & \(\mu\)                              & \(\sigma\)      & \(\mu\)                  & \(\sigma\) \\
+        RMSE    & 13.545                   & 26.576     & \textbf{7.265}                       & \textbf{13.741} & 11.120                   & 21.670     \\
+        SISM    & 0.924                    & 0.047      & \textbf{0.959}                       & \textbf{0.037}  & 0.922                    & 0.054      \\
+        MS-SSIM & 0.971                    & 0.018      & \textbf{0.988}                       & \textbf{0.012}  & 0.976                    & 0.020      \\
+    \end{tblr}
+
+    \caption[Accuracy Metrics]{Accuracy metrics for each upsampling method.
+\(\mu\) indicates the mean, \(\sigma\) indicates the standard deviation.
+The best performing method for each metric is bolded.}
+    \label{tab:metrics}
+\end{table}
+
 The non-GAN CNN approach of RDN\textdaggerdbl{} remains the most accurate method for the entire test grid.
@@
 
+\begin{landscape}
     \begin{figure}[hbtp]
+        \centering
         \includegraphics[width=\linewidth,trim={0 0 0 -5mm},clip]{fig/p1/hpfilt.jpg}
         \caption[High-pass filtered results]{High-pass filtered test tile and its upsampled counterparts.
-        The cut-off for the high-pass Butterworth filter was selected with wavelength equal to the Nyquist wavelength of the LR grid, i.e.,\ four times the HR Nyquist wavelength.
+            The cut-off for the high-pass Butterworth filter was selected with wavelength equal to the Nyquist wavelength of the LR grid, i.e.,\ 4 times the HR Nyquist wavelength.
         }
@@
     \end{figure}
+\end{landscape}
 
-\begin{table}
-    \begin{tblr}{
-            colspec={
-                    r
-                    Q[si={table-format=2.3},r]
-                    Q[si={table-format=2.3},l]
-                    Q[si={table-format=2.3},r]
-                    Q[si={table-format=2.3},l]
-                    Q[si={table-format=2.3},r]
-                    Q[si={table-format=2.3},l]
-                },
-            row{1-2} = {guard}
-        }
-                & Bicubic &           & RDN\textdaggerdbl{} &                 & ESRGAN+ &        \\
-        \hline{}
-                & Mean    & {Standard                                                            \\Deviation} & Mean & {Standard\\Deviation} & Mean & {Standard\\Deviation}                                                                         \\
-        RMSE    & 13.545  & 26.576    & \textbf{7.265}      & \textbf{13.741} & 11.120  & 21.670 \\
-        SISM    & 0.924   & 0.047     & \textbf{0.959}      & \textbf{0.037}  & 0.922   & 0.054  \\
-        MS-SSIM & 0.971   & 0.018     & \textbf{0.988}      & \textbf{0.012}  & 0.976   & 0.020  \\
-    \end{tblr}
-
-    \caption[Accuracy Metrics]{Accuracy metrics for each upsampling method. The best performing method for each metric is bolded.}
-    \label{tab:metrics}
-\end{table}
-
-\subsection{Jasper Hill / Lord Byron super-resolution}
+\subsection{Case study super-resolution}
 A low-resolution TMI extent from the \qty{80}{\metre} state map over the Jasper Hill major resource project was selected for detailed investigation.
@@
 
+\begin{landscape}
     \begin{figure}[hbtp]
+        \centering
         \includegraphics[width=\linewidth,trim={0 0 0 0},clip]{fig/p1/1vd.jpg}
@@
     \end{figure}
+\end{landscape}
 
 \begin{figure}[hbtp]
+    \centering
     \includegraphics[width=\linewidth,trim={0 0 0 5mm},clip]{fig/p1/jhilldykes.png}
-    \centering
     \includegraphics[width=0.7\linewidth]{fig/p1/transectp.png}
@@
 Based on this, RDN\textdaggerdbl{} shows the best performance for super-resolution CNN upsampling of magnetic grids, to assist in the interpretation of low-resolution grids.
+
 The deep learning methods used here can be trained with data from other geospatial extents, either from scratch or by initialising the training with pre-existing model weights \parencite[e.g.][]{wangMineGANEffectiveKnowledge2020}.
@@
 This applies also to grids that do not have a cell size of \qty{80}{\metre}.
+
 An example use case for either the method or trained models is super-resolving the Total Magnetic Intensity (TMI) Grid of Australia 2019 --- seventh edition which is published by Geoscience Australia in only \qty{80}{\metre} and \qty{40}{\metre} cell size.

### 2023-10-12 paper2.tex
Figure tweaks

@@
     However, despite the widespread success of super-resolution upscaling of natural photographs, its application to low-resolution geophysical surveys remains to be fully investigated.
-    Previous applications to geophysical survey data generate training data pairs of low- and high-resolution grids by downsampling the high-resolution grid with standard image filters, which is a poor approximation to real-world low-resolution aeromagnetic grids constructed from sparsely sampled survey data.
+    Previous applications to geophysical survey data generate training data pairs of low- and high-resolution grids by downsampling the high-resolution grid with standard image filters.
+    These are a poor approximation to real-world low-resolution aeromagnetic grids constructed from sparsely sampled survey data.
     Moreover, the structural variation within the survey data depends entirely on the geological domain which is surveyed.
-    This paper proposes an approach to super-resolution of aeromagnetic survey data using transfer learning from synthetic data that represents a wide range of realistic geological domains, to imrpove the generalisability of the resulting model.
+    This paper proposes an approach to super-resolution of aeromagnetic survey data using transfer learning from synthetic data that represents a wide range of realistic geological domains, to improve the generalisability of the resulting model.
     The approach uses realistic high-resolution and low-resolution pairs of gridded survey data, obtained by simulating aeromagnetic surveys of the data at close and wide line spacings.
-    Structural accuracy of the method is improved using a secondary fine-tuning stage incorporating real-world survey data.
+    The structural accuracy of the method is improved using a secondary fine-tuning stage incorporating real-world survey data.
     The Local Texture Estimator neural network architecture was used, and qualitative and quantitative measures of the super-resolution performance are reported.
@@
 Gridding at a finer cell size preserves higher frequencies present in the sampled data, resulting in greater detail.
-This resolvable detail is termed resolution, and high-resolution details better define structures apparent in the data which are contextually important to interpretation.
+This resolvable detail is termed resolution, and high-resolution better defines structures apparent in the data which are contextually important to interpretation.
 When the cell size covers a quantified distance, the smallest resolvable detail can be expressed in terms of wavelength.
@@
 Addressing costly data acquisition, common in geoscience \parencite{dawsonImpactDatasetSize2023}, can be done by transfer learning.
-This assists example-based methods by using a larger source dataset which shares properties with the target dataset.
+This assists example-based methods by initially using a larger source dataset which shares properties with the target dataset.
+
 In order to improve the generalisation of an example-based neural network for regions without high-resolution coverage, we propose transfer learning \parencite{tanSurveyDeepTransfer2018} by first training a baseline model trained with synthetic data containing a broad set of geological domains, which is then fine-tuned with high-resolution survey grid data.
 The synthetic geophysical data \parencite{jessellNoddyverseMassiveData2022} are forward modelled from 3D petrographic voxel models with varied geological histories.
-These provide a diverse set of features, but these lack truly realistic characteristics, such as high frequency near surface magnetisation, and features from complex geological processes such as metasomatism or remnant magnetisation.
+These provide a diverse set of features, but these lack truly realistic characteristics, such as high frequency near-surface magnetisation, and features from complex geological processes such as metasomatism or remnant magnetisation.
 
@@
 The method of \textcite{smithMagneticGridResolution2022} demonstated SR methods are capable of upsampling low-resolution magnetic textures and predicting accurate short wavelengths for these data.
-Comparison was made compared with numerical filters such as the bicubic filter.
+Comparison was made against numerical filters such as the bicubic filter.
 However, the low-resolution data were created using a polynomial filter that suppressed high frequencies, rather than a real-world low-resolution geophysical sampling process.
@@
 
-Implicit functions aim to learn a specific function parameterised entirely by the weights of a neural network.
+An implicit function aims to learn a specific function parameterised entirely by the weights of a neural network.
 In an image or geophysical grid context, the function may map grid coordinates to the value at those coordinates.
@@
 The encoder in LTE can use the feature extraction capability of traditional SR CNNs such as EDSR \parencite{limEnhancedDeepResidual2017} or RDN \parencite{zhangResidualDenseNetwork2018}, or a SwinIR \parencite{liangSwinIRImageRestoration2021} transformer-based encoder.
-In the original implementation of the CNN SR networks, the extracted image features are upsampled and returned to the image domain by convolutional layers.
+In the original implementation of the SR CNN networks, the extracted image features are upsampled and returned to the image domain by convolutional layers.
 In LTE, the latent extracted features are further processed by the LTE network component before reconstruction to image space by an MLP\@.
@@
 \Cref{fig:lrdata} presents data generated with the proposed low-resolution transform for a range of geological histories.
-\Cref{fig:lrdata}A shows a synthetic tile with the geological history ``stratigraphy, tilt, fold, tilt, fold''.
+\Cref{fig:lrdata}(a, b, c) shows a synthetic tile with the geological history ``stratigraphy, tilt, fold, tilt, fold''.
 The forward model contains a long-wavelength linear magnetic structure, and a sharply defined high intensity magnetic unit.
 The high frequencies required to define the second feature are not captured by the LR grid sampling, resulting in aliasing.
-\Cref{fig:lrdata}B is recorded with a geological history of ``stratigraphy, tilt, fold, fold, fold'', and presents two folded negative anomalies that converge to the south.
+\Cref{fig:lrdata}(d, e, f) is recorded with a geological history of ``stratigraphy, tilt, fold, fold, fold'', and presents two folded negative anomalies that converge to the south.
 Insufficient sampling in the LR grid causes the spatial relation to be incorrectly interpreted as converging in the centre of the figure, which may be interpreted differently than in the target high-resolution grid.
@@
     \centering
-    \includegraphics[width=0.75\linewidth]{fig/p2/temp_lr1.png}
-    \includegraphics[width=0.75\linewidth]{fig/p2/temp_lr2.png}
+    \includegraphics[width=\linewidth,trim={0 0 0 5mm},clip]{fig/p2/inp_data_Noddy_169.pdf}
+    \includegraphics[width=\linewidth,trim={0 0 0 5mm},clip]{fig/p2/inp_data_Noddy_165.pdf}
     \caption[Low-resolution geophysics grids]{
-        The result of the proposed sampling and gridding on a selection of synthetic tiles loaded from the collection of \parencite{jessellNoddyverseMassiveData2022} at 4x scale.
-        Note the coloured lines and accompanying tick marks in the ground-truth grid (GT, left) indicate cells which are sampled and used for gridding in the low-resolution grid (LR, right).
-        High-resolution (HR, middle) is sampled and gridded from GT, with survey lines indicated by minor tick marks.
+        The result of the proposed sampling and gridding on a two synthetic tiles loaded from the collection of \textcite{jessellNoddyverseMassiveData2022} at 4x scale.
+        Note the coloured lines and accompanying tick marks in the ground-truth grid (GT, a., d.)) indicate cells which are sampled and used for gridding in the low-resolution grid (LR, c., and f.).
+        High-resolution (HR, b., and e.)) is sampled and gridded from GT, with survey lines indicated by minor tick marks.
         The minimum curvature gridding process results creates a variety of low-resolution degradations.
@@
 Because total magnetic intensity data are single channel, the input and output channel count are set to one.
-The SwinIR feature encoder implementation by is used, and the MLP decoder retains the same configuration as the authors.
+The SwinIR feature encoder implementation by is used, and the MLP decoder retains the same configuration as the authors \parencite{leeLocalTextureEstimator2022}.
 
@@
 In addition to mean-square error, FSIM \parencite{linzhangFSIMFeatureSimilarity2011} is used to quantify the quality of the super-resolved image.
-FSIM is a full reference image similarity metric that quantifies structural similarity, rather than individual cell values.
+FSIM is a full reference image similarity metric that quantifies structural similarity, rather than individual cell values, with highly similar structural content causing the metric to approach 1.0.
 %TODO complain about SSIM Structural Similarity (SIM) \parencite{wangImageQualityAssessment2004}
-Model performance is quantified using FSIMi in Cref{tab:2metrics}, and it is seen that fine-tune training increases FSIM score for the task of super-resolution for aeromagnetic grids over the baseline model.
+Model performance is quantified using SSIM in Cref{tab:2metrics}, and it is seen that fine-tune training increases FSIM score for the task of super-resolution for aeromagnetic grids over the baseline model.
 
-% \begin{table}[hbtp]
-% %     % \includegraphics[width=\linewidth]{fig/p2/temp_tbl.png}
-% % \begin{tblr}{ll}
-% %                 & Reserved Synthetic Dataset & Reserved Aeromagnetic Dataset \\
-% %                 & Mean / Standard Dev.       & Mean / Standard Dev.          \\
-% %     \hline{}
-% %     Baseline   & 0                          & 0                             \\
-% %     Fine-Tuned & 0                          & 0                             \\
-% % \end{tblr}
-%     \caption[Accuracy Metrics]{Accuracy metrics for each upsampling method. The best performing method for each metric is bolded.}
-%     \label{tab:2metrics}
-% \end{table}
+\begin{table}[hbtp]
+    \begin{tblr}{
+            colspec={
+                    r |
+                    Q[si={table-format=2.3},r]
+                    Q[si={table-format=2.3},l] |
+                    Q[si={table-format=2.3},r]
+                    Q[si={table-format=2.3},l] |
+                },
+            row{1} = {guard}
+        }
+                         & \SetCell[c=2]{c} Reserved synthetic test &            & \SetCell[c=2]{c} Aeromagnetic grid dataset              \\
+        \hline{}
+                         & \(\mu\)                                  & \(\sigma\) & \(\mu\)                                    & \(\sigma\) \\
+        Baseline model   & 0.9844                                   & 0.0296     & 0.9731                                     & 0.0086     \\
+        Fine-tuned model & 0.9838                                   & 0.0329     & 0.9754                                     & 0.0078     \\
+    \end{tblr}
+
+    \caption[Accuracy Metrics]{Mean-square error and FSIM for each upsampling method. $\mu$ is given as the mean, and $\sigma$ is given as the standard deviation. Fine-tuned }
+    \label{tab:2metrics}
+\end{table}
 
@@
 
+\begin{landscape}
     \begin{figure}[hbtp]
-    \includegraphics[width=0.9\linewidth]{fig/p2/srcomp_23.pdf}
+        \centering
+        \includegraphics[width=1\linewidth]{fig/p2/srcomp_23.pdf}
         \caption[Super-resolution geophysics grid results I]{Super-resolution predictions on open access data, prepared using the proposed method.
-        Explanation in-text.
-        Grid A is the super-resolution prediction using the baseline model, while grid B is the SR prediction using the fine-tuned model.}
+            a) Ground truth, b) High-resolution, c) Low-resolution, d) Baseline super-resolution, e) Fine-tuned super-resolution, full explanation in-text.
+        }  
         \label{fig:srdata23}
     \end{figure}
+\end{landscape}
 
+\begin{landscape}
     \begin{figure}[hbtp]
-    \includegraphics[width=0.9\linewidth]{fig/p2/srcomp_14.pdf}
-    \caption[Super-resolution geophysics grid results II]{Super-resolution predictions on open access data, prepared using the proposed method.
-        Explanation in-text.
-        Grid A is the super-resolution prediction using the baseline model, while grid B is the SR prediction using the fine-tuned model.}
+        \centering
+        \includegraphics[width=1\linewidth]{fig/p2/srcomp_14.pdf}
+        \caption[Super-resolution geophysics grid results I]{Super-resolution predictions on open access data, prepared using the proposed method.
+            a) Ground truth, b) High-resolution, c) Low-resolution, d) Baseline super-resolution, e) Fine-tuned super-resolution, full explanation in-text.
+        }  
         \label{fig:srdata14}
     \end{figure}
+\end{landscape}
 
+\begin{landscape}
     \begin{figure}[hbtp]
-    \includegraphics[width=0.9\linewidth]{fig/p2/srcomp_17.pdf}
-    \caption[Super-resolution geophysics grid results III]{Super-resolution predictions on open access data, prepared using the proposed method.
-        Explanation in-text.
-        Grid A is the super-resolution prediction using the baseline model, while grid B is the SR prediction using the fine-tuned model.}
+        \centering
+        \includegraphics[width=1\linewidth]{fig/p2/srcomp_17.pdf}
+        \caption[Super-resolution geophysics grid results I]{Super-resolution predictions on open access data, prepared using the proposed method.
+            a) Ground truth, b) High-resolution, c) Low-resolution, d) Baseline super-resolution, e) Fine-tuned super-resolution, full explanation in-text.
+        }  
         \label{fig:srdata17}
     \end{figure}
+\end{landscape}
 
+\begin{landscape}
     \begin{figure}[hbtp]
-    \includegraphics[width=0.9\linewidth]{fig/p2/srcomp_18.pdf}
-    \caption[Super-resolution geophysics grid results IV]{Super-resolution predictions on open access data, prepared using the proposed method.
-        Explanation in-text.
-        Grid A is the super-resolution prediction using the baseline model, while grid B is the SR prediction using the fine-tuned model.}
+        \centering
+        \includegraphics[width=1\linewidth]{fig/p2/srcomp_18.pdf}
+        \caption[Super-resolution geophysics grid results I]{Super-resolution predictions on open access data, prepared using the proposed method.
+            a) Ground truth, b) High-resolution, c) Low-resolution, d) Baseline super-resolution, e) Fine-tuned super-resolution, full explanation in-text.
+        }  
         \label{fig:srdata18}
     \end{figure}
+\end{landscape}
 

### 2023-10-12 paper3.tex
Short titles for figures, fix cites
Figure tweaks

@@
     \centering{}
-    \includegraphics[width=\linewidth]{fig/p3/P864_sample_locs.pdf}
-    \caption[Point samples]{Sample altitudes for the Wolfe Creek survey lines. The diverging colourmap has been centred at the nominal survey terrain clearance of \qty{40}{\m}.}
+    \includegraphics[width=\linewidth]{fig/p3/P864_sample_locs_raster.pdf}
+    \caption[The Wolfe Creek Meteorite Crater survey]{Sample altitudes for the Wolfe Creek survey lines.
+The diverging colourmap has been centred at the nominal survey terrain clearance of \qty{40}{\m}.}
     \label{fig:samples}
@@
     \centering
-    \includegraphics[width=0.5\linewidth]{fig/p3/loss_plot.pdf}
+    \includegraphics[width=0.75\linewidth]{fig/p3/loss_plot.pdf}
     \caption[Training convergence]{Train and validation loss for the duration of the experiment.}
@@
 A good qualitative match is achieved between the GA reference grid and the grid queried from the implicit representation, which successfully reconstructs the linear dune features and circular rim features.
-This high performance is quantified by the residuals and peak signal to noise ratio (PSNR) of \qty{40.12}{\dB}, with mean residuals of \qty{0.4} and \qty{0.8}{\nano\tesla\per\m}
+This high performance is quantified by the residuals and peak signal to noise ratio (PSNR) of \qty{39.97}{\dB}, with mean residuals of \qty{0.4} and \qty{0.8}{\nano\tesla\per\m}
 % Further level grids from other survey extents are included in Appendix A.
 
+\begin{landscape}
     \begin{figure}[hbtp]
@@
 
+\begin{landscape}
     \begin{figure}[hbtp]
         \centering
-    \includegraphics[width=1.0\linewidth]{fig/p3/35_level_grid.pdf}
+        \includegraphics[width=1.0\linewidth]{fig/p3/P864_grid_comparison_35m.pdf}
         \caption[Grid prediction outside the nominal altitude]{A constant level grid queried from the INR at the height of \qty{35}{\m}.}
@@
 This is interpreted as the presented model having a limited capacity to extrapolate beyond the flown data extent, and learning a poor representation of the vertical component of the potential field, which we further discuss in \Cref{sec:3discussion}.
+
+\begin{landscape}
     \begin{figure}[hbtp]
@@
     \centering{}
-    \includegraphics[width=1.0\linewidth]{fig/p3/P864_dv_comparison.pdf}
+    \includegraphics[width=0.9\linewidth]{fig/p3/P864_dv_comparison.pdf}
     \caption[Vertical derivative]{Vertical derivative grids queried from AD differentiated INR (left) and calculated numerically (right) on the \qty{40}{\m} level grid queried from the INR\@.

### 2023-10-12 paper2.tex
Final tweak for first submittable draft

@@
         \includegraphics[width=1\linewidth]{fig/p2/srcomp_14.pdf}
-        \caption[Super-resolution geophysics grid results I]{Super-resolution predictions on open access data, prepared using the proposed method.
+        \caption[Super-resolution geophysics grid results II]{Super-resolution predictions on open access data, prepared using the proposed method.
             a) Ground truth, b) High-resolution, c) Low-resolution, d) Baseline super-resolution, e) Fine-tuned super-resolution, full explanation in-text.
@@
         \includegraphics[width=1\linewidth]{fig/p2/srcomp_17.pdf}
-        \caption[Super-resolution geophysics grid results I]{Super-resolution predictions on open access data, prepared using the proposed method.
+        \caption[Super-resolution geophysics grid results III]{Super-resolution predictions on open access data, prepared using the proposed method.
             a) Ground truth, b) High-resolution, c) Low-resolution, d) Baseline super-resolution, e) Fine-tuned super-resolution, full explanation in-text.
@@
         \includegraphics[width=1\linewidth]{fig/p2/srcomp_18.pdf}
-        \caption[Super-resolution geophysics grid results I]{Super-resolution predictions on open access data, prepared using the proposed method.
+        \caption[Super-resolution geophysics grid results IV]{Super-resolution predictions on open access data, prepared using the proposed method.
             a) Ground truth, b) High-resolution, c) Low-resolution, d) Baseline super-resolution, e) Fine-tuned super-resolution, full explanation in-text.

### 2023-10-12 paper3.tex
Final tweak for first submittable draft

@@
 A good qualitative match is achieved between the GA reference grid and the grid queried from the implicit representation, which successfully reconstructs the linear dune features and circular rim features.
-This high performance is quantified by the residuals and peak signal to noise ratio (PSNR) of \qty{39.97}{\dB}, with mean residuals of \qty{0.4} and \qty{0.8}{\nano\tesla\per\m}
+This high performance is quantified by the residuals and peak signal to noise ratio (PSNR) of \qty{39.97}{\dB}, with mean residuals of \qty{0.4} and \qty{0.8}{\nano\tesla\per\m}.
 % Further level grids from other survey extents are included in Appendix A.
+
+The INR can be queried at arbitrary continuous coordinates, including out-of-range values beyond the training domain.
+As expected, the predicted field becomes unrealistic when extrapolating beyond this boundary, which can be seen in the periphery of the INR grid in \Cref{fig:grid40}.
+This boundary region (indicated by solid white in the reference grid) is excluded from PSNR calculation.
+
+Constant level grids can be queried from the INR at any height.
+\Cref{fig:grid35} shows the case study INR queried at \qty{35}{\m}, which is \qty{5}{\m} lower than the nominal survey altitude.
+While the rim feature can still be interpreted within this lower level grid, the INR fails to demonstrate physically realistic continuation of the field.
+% It is conjectured that successfully training a PINN criterion such as Laplace’s equation loss (equation 1.3) would improve the accuracy of these upward or downward extracted slices.
 
@@
 \end{landscape}
-
-The INR can be queried at arbitrary continuous coordinates, including out-of-range values beyond the training domain.
-As expected, the predicted field becomes unrealistic when extrapolating beyond this boundary, which can be seen in the periphery of the INR grid in \Cref{fig:grid40}.
-This boundary region (indicated by solid white in the reference grid) is excluded from PSNR calculation.
-
-Constant level grids can be queried from the INR at any height.
-\Cref{fig:grid35} shows the case study INR queried at \qty{35}{\m}, which is \qty{5}{\m} lower than the nominal survey altitude.
-While the rim feature can still be interpreted within this lower level grid, the INR fails to demonstrate physically realistic continuation of the field.
-% It is conjectured that successfully training a PINN criterion such as Laplace’s equation loss (equation 1.3) would improve the accuracy of these upward or downward extracted slices.
 
@@
         \centering{}
-        \includegraphics[width=1.0\linewidth]{fig/p3/P864_dh_comparison.pdf}
+        \includegraphics[width=0.8\linewidth]{fig/p3/P864_dh_comparison.pdf}
         \caption[Horizontal derivatives]{Horizontal gradients calculated using the proposed method and the reference numerical method.
@@
     \centering{}
-    \includegraphics[width=0.9\linewidth]{fig/p3/P864_dv_comparison.pdf}
+    \includegraphics[width=1\linewidth]{fig/p3/P864_dv_comparison.pdf}
     \caption[Vertical derivative]{Vertical derivative grids queried from AD differentiated INR (left) and calculated numerically (right) on the \qty{40}{\m} level grid queried from the INR\@.

### 2023-10-12 paper1.tex
Improve figures and tables

@@
     \centering
-    \includegraphics[width=\linewidth]{fig/p1/rdn.png}
+    \includegraphics[width=\linewidth]{fig/p1/rdn_vec.pdf}
     \caption[The RDN architecture]{The RDN architecture, which acts as the ESRGAN generator.
@@
     \centering
-    \includegraphics[width=\linewidth]{fig/p1/rdb.png}
+    \includegraphics[width=\linewidth]{fig/p1/rdb_vec.pdf}
     \caption[Basic blocks]{Each Basic Block (\Cref{fig:rdn}, orange) comprises three weighted Residual Dense Blocks (\Cref{fig:convs}).
@@
     \centering
-    \includegraphics[width=0.75\linewidth]{fig/p1/convs.png}
+    \includegraphics[width=0.75\linewidth]{fig/p1/convs_vec.pdf}
     \caption[RDB convolutional layers]{Each Residual Dense Block (\Cref{fig:rdb}, purple) comprises four convolutional layers, with additional learning pathways present as residual connections (black), and dense connections (green).
@@
                     Q[si={table-format=2.3},r]
-                    Q[si={table-format=2.3},l] |
+                    Q[si={table-format=2.3},l]
                 },

### 2023-10-12 discussion.tex
Consolidate bibliography at end of doc

@@
 
-\printbibliography{}
+% \printbibliography{}
 
@@
 
-To the best of my knowledge, \Cref{ch:paper1} presents the first investigation in the literature of the super-resolution enhancement of gridded aerogeophysical data.
+To the best of the author's knowledge, \Cref{ch:paper1} presents the first investigation in the literature of the super-resolution enhancement of gridded aerogeophysical data.
 Prior to this work, it was unknown how well SR methods developed for natural images would adapt to the features and high dynamic range present within magnetic grids, or the challenges faced in developing a training dataset for these data.
@@
 The contribution in \Cref{ch:paper3} used coordinate multilayer perceptron neural networks to learn a representation of the function that describes a surveyed potential field extent.
-To my knowledge, this is the first time implicit neural representation of aerogeophysical survey data has been reported in the literature.
+To the author's knowledge, this is the first time implicit neural representation of aerogeophysical survey data has been reported in the literature.
 It was seen that these networks are highly suited for processing spatial data such as point sampled geophysics surveys.

### 2023-10-12 discussion.tex
Write concluding remarks

@@
 
-We identify opportunities in \Cref{ch:futurework} for future work stemming from our contribution  of enhancing potential field methods in geophysics.
+\Cref{ch:futurework} discussed future work arising from the contributions of this thesis for enhancing potential field methods in geophysics, with a focus on possible approaches to characterise and improve the confidence in the use of  these methods by the geophysics community.
+In summary, this thesis explored how advances in deep learning may be adapted and extended to enhance the processing of potential field geophysical data.
+The presented approaches, results, and considerations have established the capacity for these contemporary methods in deep learning to overcome current challenges in geoscience.
 

### 2023-10-12 paper2.tex
Consolidate bibliography at end of doc
Update vector figures

@@
 \begin{figure}[hbtp]
-    \includegraphics[width=\linewidth]{fig/p2/temp_lte.png}
+    \includegraphics[width=\linewidth]{fig/p2/ltenet.pdf}
     \caption[The LTE architecture]{
-        A simplified representation of the super-resolution LTE network.
-        The encoder is marked as \(E_\phi{}\).
-        \(f_\Theta{}\) is an MLP network used as the decoder for image reconstruction.
-        A long-range skip connection with simple upscaling is marked with an arrow.
+        The LTE super-resolution network is structured as an autoencoder.
+        The encoder can take the form of RDN (prior the upsampling and reconstruction, see \Cref{fig:rdn}), or transformer-based networks.
+        The decoder is an MLP network, and is used for image reconstruction.
+        A long-range skip connection with simple upscaling allows low-resolution features common to both LR and SR to bypass the network.
         The LTE network block performs high-resolution upscaling of extracted features in the Frequency domain.
-        Simplified from \textcite{leeLocalTextureEstimator2022}.
+        Simplified from \textcite{leeLocalTextureEstimator2022}, where the LTE block is further detailed.
     }

### 2023-10-12 intro.tex
Figure tweaks
Consolidate bibliography at end of doc
Write results for paper 2, small tweaks

@@
 
-The definition of resolution throughout this thesis is:
+The following definition of resolution is adopted throughout this thesis:
 
@@
 If the network architecture provides the capacity to store and retrieve learning, the data and training architecture provide the actual instruction and mode of delivery.
-There are broadly two classes of training; supervised and unsupervised learning.
+There are broadly two classes of training: supervised and unsupervised learning.
 The super-resolution and representation learning tasks in this thesis are both supervised tasks, where a reference is provided for the network to calculate an objective function of its performance on.
@@
 Beyond the applications investigated in this thesis, many other machine learning methods have been investigated in geoscience.
-These include: clustering of geophysical textures \parencite{grujicGeophysicsNeuralNetworks2019}, prediction of geological map event history \parencite{guo3DGeologicalStructure2021}, automated interpretation of geological data \parencite{waldelandConvolutionalNeuralNetworks2018, babakhinSemisupervisedSegmentationSalt2019,dawsonImpactDatasetSize2023}, seismic data interpolation \parencite{wangDeeplearningbasedSeismicData2018}, and 3D structure, joint inversion, or modelling \parencite{guo3DGeologicalStructure2021},
+These include: clustering of geophysical textures \parencite{grujicGeophysicsNeuralNetworks2019}, prediction of geological map event history \parencite{guo3DGeologicalStructure2021}, automated interpretation of geological data \parencite{waldelandConvolutionalNeuralNetworks2018, babakhinSemisupervisedSegmentationSalt2019,dawsonImpactDatasetSize2023}, seismic data interpolation \parencite{wangDeeplearningbasedSeismicData2018}, and 3D structure, joint inversion, or modelling \parencite{guo3DGeologicalStructure2021}.
 

### 2023-10-12 manuscript.tex
Fix hyphenation issue
Consolidate bibliography at end of doc
Write results for paper 2, small tweaks

@@
 \documentclass[12pt,a4paper,notitlepage]{report} %,openright,twoside scrbook
-% \includeonly{}
+% \includeonly{paper1}
 \usepackage{thesisstyle}
 \addbibresource{bib/PhD.bib}
+\hyphenation{ESRGAN+}
+\uchyph=0 % prevent uppercase hyphenation
 
@@
     \vspace*{48 pt}
-    {\large\textbf{Potential Field Geophysics Enhancement Using Contemporary Deep Learning Approaches}}
+    {\large\textbf{Potential Field Geophysics Enhancement Using Contemporary Deep Learning}}
 
@@
 \label{ch:intro}
-\newrefsection{}
+% \newrefsection{}
 \input{intro}
@@
 \label{ch:paper1}
-\newrefsection{}
+% \newrefsection{}
 This chapter has been reproduced from the following peer reviewed publication. Formatting has been adjusted for consistency.
@@
 Ore Geology Reviews 150, 105119.
-https://doi.org/10.1016/j.oregeorev.2022.105119
+\url{https://doi.org/10.1016/j.oregeorev.2022.105119}
 \input{paper1}
@@
 \label{ch:paper2}
-\newrefsection{}
+% \newrefsection{}
 \input{paper2}
@@
 \label{ch:paper3}
-\newrefsection{}
+% \newrefsection{}
 \input{paper3}
 
-\newrefsection{}
+% \newrefsection{}
 \input{discussion}
 
+\printbibliography{}
+
 \end{document}

### 2023-10-12 paper1.tex
Consolidate bibliography at end of doc
Write results for paper 2, small tweaks

@@
 
-\begin{figure}[hbtp]
-    \centering
-    \includegraphics[width=\linewidth]{fig/p1/rdb_vec.pdf}
-    \caption[Basic blocks]{Each Basic Block (\Cref{fig:rdn}, orange) comprises three weighted Residual Dense Blocks (\Cref{fig:convs}).
-        ESRGAN+ extends ESRGAN with the addition of Gaussian Noise after each basic RDB block (black vectors).
-        Weight factors are indicated by \(\beta{}\) and \(\gamma{}\).
-        Noise injection is not used in RDN\@.
-        Adapted from \textcite{rakotonirinaESRGANFurtherImproving2020}.
-    }
-    \label{fig:rdb}
-\end{figure}
-
-\begin{figure}[hbtp]
-    \centering
-    \includegraphics[width=0.75\linewidth]{fig/p1/convs_vec.pdf}
-    \caption[RDB convolutional layers]{Each Residual Dense Block (\Cref{fig:rdb}, purple) comprises four convolutional layers, with additional learning pathways present as residual connections (black), and dense connections (green).
-LReLU refers to the Leaky-ReLU activation function.
-Adapted from \textcite{rakotonirinaESRGANFurtherImproving2020}.}
-    \label{fig:convs}
-\end{figure}
-
 \subsection{Interpolation}
@@
 
+\begin{figure}[hbtp]
+    \centering
+    \includegraphics[width=\linewidth]{fig/p1/rdb_vec.pdf}
+    \caption[Basic blocks]{Each Basic Block (\Cref{fig:rdn}, orange) comprises three weighted Residual Dense Blocks (\Cref{fig:convs}).
+        ESRGAN+ extends ESRGAN with the addition of Gaussian Noise after each basic RDB block (black vectors).
+        Weight factors are indicated by \(\beta{}\) and \(\gamma{}\).
+        Noise injection is not used in RDN\@.
+        Adapted from \textcite{rakotonirinaESRGANFurtherImproving2020}.
+    }
+    \label{fig:rdb}
+\end{figure}
+
+\begin{figure}[hbtp]
+    \centering
+    \includegraphics[width=0.75\linewidth]{fig/p1/convs_vec.pdf}
+    \caption[RDB convolutional layers]{Each Residual Dense Block (\Cref{fig:rdb}, purple) comprises four convolutional layers, with additional learning pathways present as residual connections (black), and dense connections (green).
+LReLU refers to the Leaky-ReLU activation function.
+Adapted from \textcite{rakotonirinaESRGANFurtherImproving2020}.}
+    \label{fig:convs}
+\end{figure}
+
 ESRGAN+, based on ESRGAN \parencite{wangESRGANEnhancedSuperresolution2018}, was chosen as the primary super-resolution CNN architecture for this task due to its reported success in other super-resolution tasks (especially \textcite{bodeUsingPhysicsInformedSuperResolution2019} and \textcite{leongDeepBedMapDeepNeural2020}) and state of the art results for its original application in image super-resolution.
@@
 
-G is analogous in design to the RDN architecture described above (\Cref{fig:rdn}), and is trained to upscale a low-resolution input, creating a super-resolution prediction.
-The Discriminator network used in ESRGAN is based on a prevalent image classification architecture known as VGG \parencite{simonyanVeryDeepConvolutional2015}.
-D is trained to classify its inputs as being either an example of the super-resolved G prediction, or high-resolution ground truth data.
+The generator (G) is analogous in design to the RDN architecture described above (\Cref{fig:rdn}), and is trained to upscale a low-resolution input, creating a super-resolution prediction.
+The discriminator network (D) used in ESRGAN is based on a prevalent image classification architecture known as VGG \parencite{simonyanVeryDeepConvolutional2015}.
+The discriminator is trained to classify its inputs as being either an example of the super-resolved G prediction, or high-resolution ground truth data.
 This is used to provide a loss-feedback to G based on G's ability to create realistic SR predictions.

### 2023-10-12 paper2.tex
Write results for paper 2, small tweaks

@@
 \begin{figure}[hbtp]
-    \includegraphics[width=\linewidth]{fig/p2/ltenet.pdf}
+    \centering
+    \includegraphics[width=0.75\linewidth]{fig/p2/ltenet.pdf}
     \caption[The LTE architecture]{
@@
         The decoder is an MLP network, and is used for image reconstruction.
-        A long-range skip connection with simple upscaling allows low-resolution features common to both LR and SR to bypass the network.
-        The LTE network block performs high-resolution upscaling of extracted features in the Frequency domain.
+        A long-range skip connection with nearest neighbour upsampling allows low-resolution features, common to both LR and the HR target, to bypass the network.
+        The LTE network block performs high-resolution upscaling of extracted features in the frequency domain.
         Simplified from \textcite{leeLocalTextureEstimator2022}, where the LTE block is further detailed.
@@
 The proposed dataset methodology uses synthetic forward modelled potential field data to train a selected performant super-resolution network, and the resulting baseline model is subsequently used for transfer learning to fine-tune train the model with real aeromagnetic survey grid data.
-The performance of the method is qualitatively described on real survey grid extents, and quantitatively described with standard image quality metrics.
+The performance of the method is qualitatively described on real survey grid extents, and quantitatively described with image quality metrics.
 
@@
         The result of the proposed sampling and gridding on a two synthetic tiles loaded from the collection of \textcite{jessellNoddyverseMassiveData2022} at 4x scale.
-        Note the coloured lines and accompanying tick marks in the ground-truth grid (GT, a., d.)) indicate cells which are sampled and used for gridding in the low-resolution grid (LR, c., and f.).
-        High-resolution (HR, b., and e.)) is sampled and gridded from GT, with survey lines indicated by minor tick marks.
+        Note the coloured lines and accompanying major tick marks in the ground-truth grid (GT a., d.,) indicate cells which are sampled and used for gridding in the low-resolution grid (LR c., and f.,).
+        High-resolution (HR b., e.,) is sampled and gridded from GT, with survey lines indicated by minor tick marks.
         The minimum curvature gridding process results creates a variety of low-resolution degradations.
@@
 \label{sec:2results}
-\subsubsection{Quantitative measure}
 Due to the dynamic range of magnetic anomaly grids and the relative importance of structural accuracy for gridded data, image quality assessment methods typically used for RGB images such as peak signal-to-noise ratio or mean-squared error are an inadequate quantitative measure of upscaling performance for geophysics.
@@
 %TODO complain about SSIM Structural Similarity (SIM) \parencite{wangImageQualityAssessment2004}
-Model performance is quantified using SSIM in Cref{tab:2metrics}, and it is seen that fine-tune training increases FSIM score for the task of super-resolution for aeromagnetic grids over the baseline model.
+Model performance is quantified using SSIM in \Cref{tab:2metrics}.
+It is seen that fine-tune training increases FSIM score for the task of super-resolution for aeromagnetic grids, over the baseline model.
 
@@
         \hline{}
-                         & \(\mu\)                                  & \(\sigma\) & \(\mu\)                                    & \(\sigma\) \\
+                         & \(\mu{}\)                                & \(\sigma{}\) & \(\mu{}\)                                  & \(\sigma{}\) \\
         Baseline model   & 0.9844                                   & 0.0296       & 0.9731                                     & 0.0086       \\
@@
 
-    \caption[Accuracy Metrics]{Mean-square error and FSIM for each upsampling method. $\mu$ is given as the mean, and $\sigma$ is given as the standard deviation. Fine-tuned }
+    \caption[Accuracy Metrics]{Mean (\(\mu{}\)) and standard deviation (\(\sigma{}\)) of the FSIM metric for each upsampling method over the test set.}
     \label{tab:2metrics}
@@
 
-Qualitative results are shown to compare the outputs from the two models, the baseline model that is trained with synthetic data and the fine-tuned model trained with open access survey data.
+Qualitative results are shown to compare the outputs from the baseline model that is trained with synthetic data, and the fine-tuned model trained with open access survey data.
 
 \Cref{fig:srdata23,fig:srdata14,fig:srdata17,fig:srdata18} contain open access grid data from the Eastern Goldfields Superterrane of Western Australia, prepared using the proposed method.
-Each figure follows the following layout for the grids; a) the ground truth (GT) \numproduct{200 x 200} cell tile is presented with low-resolution sampled data indicated in colour.
+Each figure follows the following layout for the grids.
+The ground truth (GT) \numproduct{200 x 200} cell tile is presented  in a), with low-resolution data sampling indicated in colour.
 The target high-resolution grid (HR), created from sampling and gridding GT at \qty{80}{\m} line spacing, is shown in b) for comparison.
@@
 The baseline model prediction (Baseline SR), using an input of LR with the proposed method, is shown in d) with the corresponding SSIM metric between HR and SR\@.
-The fine-tuned model prediction is shown in e).
+The fine-tuned model prediction is shown in e), using the same LR input.
 
-Strong line-perpendicular smearing in LR is reduced in both SR predictions, and fine structural divisions are better delineated.
-NW striking features around in HR are aliased in LR and subsequently incorrectly rotated by 90 degrees in the baseline SR prediction (\Cref{fig:srdata23} d).
-The fine-tuned model (\Cref{fig:srdata23} e) resolves the correct strike, and separates the two features present.
-The enhanced structural similarity is reflected by the higher SSIM score in the fine-tuned model.
+In \Cref{fig:srdata23}, strong line-perpendicular artefacts and loss of high-frequency detail in LR is lessened in both SR predictions, and fine structural divisions are better delineated.
+However, northwest striking features in HR are aliased in LR, and here subsequently incorrectly rotated by 90 degrees in the baseline SR prediction (\Cref{fig:srdata23} d).
+The fine-tuned model (\Cref{fig:srdata23} e) resolves the correct strike, and separates the two linear features present.
+The enhanced structural similarity is reflected by the higher FSIM score of in the fine-tuned model. 
+Similar structural inaccuracies are seen in\Cref{fig:srdata17}, where severe aliasing again fails to be corrected using the baseline model, but is resolved by fune-tuning.
+
+In \Cref{fig:srdata14}, the edges of the central feature defined by a magnetic high are poorly defined by the low-resolution grid in \Cref{fig:srdata14} c.
+Both models more clearly define the shape of the feature, however the fine-tuned model additionally separates the adjacent North-South striking feature.
+
+The North-South striking geology in \Cref{fig:srdata18} presents a worst-case scenario for aeromagnetic surveying, where the magnetic intensity varies strongly in the low sampling, line-perpendicular direction.
+The low-resolution sampling completely fails to sample all but the largest features with enough lines to represent them in the resulting grid.
+Despite this, both models refine the width of these features, approaching the true width represented in HR\@.
+The fine structures in HR appear to have limited importance to the SSIM calculation, because the LR and SR grids are reported with a SSIM of 0.9998 or higher.
+This suggests that SSIM may be an innapropriate IQA metric in comparing resolution in potential field grids.
 
@@
         \caption[Super-resolution geophysics grid results I]{Super-resolution predictions on open access data, prepared using the proposed method.
-            a) Ground truth, b) High-resolution, c) Low-resolution, d) Baseline super-resolution, e) Fine-tuned super-resolution, full explanation in-text.
+            a) Ground truth, b) High-resolution, c) Low-resolution, d) Baseline super-resolution, e) Fine-tuned super-resolution.
         }
@@
         \centering
+        \includegraphics[width=1\linewidth]{fig/p2/srcomp_17.pdf}
+        \caption[Super-resolution geophysics grid results II]{Super-resolution predictions on open access data, prepared using the proposed method.
+            a) Ground truth, b) High-resolution, c) Low-resolution, d) Baseline super-resolution, e) Fine-tuned super-resolution.
+        }
+        \label{fig:srdata17}
+    \end{figure}
+\end{landscape}
+
+\begin{landscape}
+    \begin{figure}[hbtp]
+        \centering
         \includegraphics[width=1\linewidth]{fig/p2/srcomp_14.pdf}
-        \caption[Super-resolution geophysics grid results II]{Super-resolution predictions on open access data, prepared using the proposed method.
-            a) Ground truth, b) High-resolution, c) Low-resolution, d) Baseline super-resolution, e) Fine-tuned super-resolution, full explanation in-text.
+        \caption[Super-resolution geophysics grid results III]{Super-resolution predictions on open access data, prepared using the proposed method.
+            a) Ground truth, b) High-resolution, c) Low-resolution, d) Baseline super-resolution, e) Fine-tuned super-resolution.
         }
@@
         \centering
-        \includegraphics[width=1\linewidth]{fig/p2/srcomp_17.pdf}
-        \caption[Super-resolution geophysics grid results III]{Super-resolution predictions on open access data, prepared using the proposed method.
-            a) Ground truth, b) High-resolution, c) Low-resolution, d) Baseline super-resolution, e) Fine-tuned super-resolution, full explanation in-text.
-        }  
-        \label{fig:srdata17}
-    \end{figure}
-\end{landscape}
-
-\begin{landscape}
-    \begin{figure}[hbtp]
-        \centering
         \includegraphics[width=1\linewidth]{fig/p2/srcomp_18.pdf}
         \caption[Super-resolution geophysics grid results IV]{Super-resolution predictions on open access data, prepared using the proposed method.
-            a) Ground truth, b) High-resolution, c) Low-resolution, d) Baseline super-resolution, e) Fine-tuned super-resolution, full explanation in-text.
+            a) Ground truth, b) High-resolution, c) Low-resolution, d) Baseline super-resolution, e) Fine-tuned super-resolution.
         }

### 2023-10-12 paper3.tex
Improve figures and tables
Write results for paper 2, small tweaks

@@
 
-The current method could include additional target dimensions, which would allow representation learning of vector fields \(\mathbb{R}^{3}\) in three dimensions \(\mathbb{R}^{3}\).
-This has applications in tensor fields and data integration tasks, and these remain for future work.
+The current method could include additional target dimensions, which may allow representation learning of vector fields \(\mathbb{R}^{3}\) in three dimensions \(\mathbb{R}^{3}\).
+This has applications in tensor field processing, and data integration tasks, and these remain for future work.
 
@@
 Resolution in the representation is limited by network capacity, rather than initial grid cell size selection during regularisation.
-Level grids can be extracted from these representations, emerging as a novel method for regularising scattered geophysical sample data.
+Regular grids can be extracted from these representations, emerging as a novel method for regularising scattered geophysical sample data.
 Spatial gradients can be calculated directly from the learned representation, and can be queried at arbitrary locations.
@@
 
-\section{Acknowledgements}
-This project is funded by a Rio Tinto Iron Ore PhD scholarship.
+% \section{Acknowledgements}
+% This project is funded by a Rio Tinto Iron Ore PhD scholarship.
 
-\printbibliography{}
+% \printbibliography{}
 

### 2023-10-13 discussion.tex
Final touch ups for typesetting and wording

@@
 For supervised tasks, a full reference metric can be calculated between the super-resolution prediction and the high-resolution target.
-In the works presented in \Cref{ch:paper1,ch:paper2,ch:paper3}, PSNR and SSIM are used to quantify the performance of the proposed methods in transforming low-resolution grids to high resolution.
+In the works presented in \Cref{ch:paper1,ch:paper2,ch:paper3}, PSNR and SSIM or FSIM  are used to quantify the performance of the proposed methods in transforming low-resolution grids to high resolution.
 However, properties of magnetic grid data are distinct to the images for which these metrics are designed.
 %   While SSIM uses structural information present in the Fourier transformed input in combination with local gradient magnitude for value accuracy,
-Consistently high SSIM scores are assigned to grids that are perceptually poor matches to the target.
+Consistently high SSIM and FSIM scores are assigned to grids that are perceptually poor matches to the target, including the low-resolution grids.
 High SSIM values are noted in other geophysical grid investigations which report SSIM metrics \parencite{wangDeeplearningbasedSeismicData2018,bavandsavadkoohiHighresolutionAeromagneticMap2023}.
 An investigation to identify a more appropriate IQA for potential field grids is required, which accounts for the distinct nature of these data and better reflects the predicted quality of geological interpretation.
-This may be benefit by automated analysis methods as mentioned above.
+This may be benefit by the automated analysis methods also mentioned above.
 

### 2023-10-13 paper2.tex
Final touch ups for typesetting and wording

@@
 
-Local texture estimator (LTE) \parencite{leeLocalTextureEstimator2022} is implemented in this work for its higher performance in the task of image super-resolution.
+Local texture estimator (LTE) \parencite{leeLocalTextureEstimator2022} is implemented in this work for its performance in the task of image super-resolution.
 The encoder in LTE can use the feature extraction capability of traditional SR CNNs such as EDSR \parencite{limEnhancedDeepResidual2017} or RDN \parencite{zhangResidualDenseNetwork2018}, or a SwinIR \parencite{liangSwinIRImageRestoration2021} transformer-based encoder.
@@
 \label{sec:2lte}
-Local Texture Estimator \parencite{leeLocalTextureEstimator2022} is implemented to super-resolve synthetic and real potential field geophysical data with low resolution resulting from line spacing.
+LTE \parencite{leeLocalTextureEstimator2022} is implemented to super-resolve synthetic and real potential field geophysical data with low resolution resulting from line spacing.
 The LTE component of the LTE network transforms the encoded latent features to frequency and amplitude features using trainable convolutions.
@@
 Finally, the decoding MLP restores these frequency domain features to the spatial image domain.
-To precondition the network toward learning high-resolution features, a long-range skip connection with bilinear upscaling passes low-resolution content common between the upsampled LR and the HR counterpart to the output of the MLP\@.
-Because total magnetic intensity data are single channel, the input and output channel count are set to one.
-The SwinIR feature encoder implementation by is used, and the MLP decoder retains the same configuration as the authors \parencite{leeLocalTextureEstimator2022}.
+To precondition the network for learning high-resolution features, a long-range skip connection with simple upscaling passes low-resolution content common between the upsampled LR and the HR target to the output of the MLP\@.
+Because TMI data are single channel, the input and output channel count are set to one.
+The SwinIR encoder implementation by is used, and the MLP decoder retains the same configuration as the authors \parencite{leeLocalTextureEstimator2022}.
 
@@
 \label{sec:2results}
-Due to the dynamic range of magnetic anomaly grids and the relative importance of structural accuracy for gridded data, image quality assessment methods typically used for RGB images such as peak signal-to-noise ratio or mean-squared error are an inadequate quantitative measure of upscaling performance for geophysics.
-In addition to mean-square error, FSIM \parencite{linzhangFSIMFeatureSimilarity2011} is used to quantify the quality of the super-resolved image.
+Due to the variable dynamic range of magnetic anomaly grids and the relative importance of structural accuracy for gridded data, image quality assessment methods typically used for RGB images such as peak signal-to-noise ratio or mean-squared error are an inadequate quantitative measure of upscaling performance for geophysics.
+In addition FSIM \parencite{linzhangFSIMFeatureSimilarity2011} is used to quantify the quality of the super-resolved image.
 FSIM is a full reference image similarity metric that quantifies structural similarity, rather than individual cell values, with highly similar structural content causing the metric to approach 1.0.
 %TODO complain about SSIM Structural Similarity (SIM) \parencite{wangImageQualityAssessment2004}
-Model performance is quantified using SSIM in \Cref{tab:2metrics}.
+Model performance is quantified using FSIM in \Cref{tab:2metrics}.
 It is seen that fine-tune training increases FSIM score for the task of super-resolution for aeromagnetic grids, over the baseline model.
@@
 
-    \caption[Accuracy Metrics]{Mean (\(\mu{}\)) and standard deviation (\(\sigma{}\)) of the FSIM metric for each upsampling method over the test set.}
+    \caption[Accuracy Metrics]{Mean (\(\mu{}\)) and standard deviation (\(\sigma{}\)) of the FSIM metric for each upsampling method, for each test set.
+    While the performance of the fine-tuned model is lower on synthetic data, the performance on real-world aeromagnetic grids is increased.}
     \label{tab:2metrics}
@@
 
-Qualitative results are shown to compare the outputs from the baseline model that is trained with synthetic data, and the fine-tuned model trained with open access survey data.
+Qualitative results are shown to provide examples of structural improvement when using the fine-tuned model trained with open access survey data, compared to the baseline model trained with synthetic data.
 

### 2023-10-13 paper3.tex
Final touch ups for typesetting and wording

@@
         \caption[Grid prediction at the nominal altitude]{Comparison between the reference grid processed by Geoscience Australia (left) and the constant level grid queried from the INR at \qty{40}{\m} (middle).
-The residuals are shown for areas containing reference data (right), with a range of ±2 standard deviations of values in the reference grid.}
+The residuals are shown (right) for areas containing reference data, with a range of ±2 standard deviations of values in the reference grid.}
         \label{fig:grid40}
@@
     \includegraphics[width=1\linewidth]{fig/p3/P864_dv_comparison.pdf}
-    \caption[Vertical derivative]{Vertical derivative grids queried from AD differentiated INR (left) and calculated numerically (right) on the \qty{40}{\m} level grid queried from the INR\@.
-        The proposed method has poor vertical gradient representation, possibly due to the single height sampled in aeromagnetic survey design.}
+    \caption[Vertical derivative]{Vertical derivative grids calculated numerically on the \qty{40}{\m} level grid queried from the INR (left) and queried from AD differentiated INR (right).
+        The proposed method has poor vertical gradient representation, possibly due to the low range of altitudes when sampling in aeromagnetic survey design.}
     \label{fig:vertgrad}
@@
 \end{equation}
-where \(S_i\) indicates the \(i^{th}\) sample point of the field survey \(\phi(x, y, z)\), implicitly represented by the model \(f\).
+where \(S\) indicates the number of sample points in the field survey \(\phi(x, y, z)\), implicitly represented by the model \(f\).
 This criterion penalises outputs where Laplace's equation is not satisfied because the sum of partial second derivatives is not close to zero.

### 2024-06-01 discussion.tex
Address reviewer 2's annotated thesis

@@
 
-Super-resolution for geophysics is not yet characterised and requires further efforts towards improving reliability before wide-spread adoption in practice.
-This section proposes four avenues for future research:
+Super-resolution for geophysics requires further efforts towards improving its reliability before wide-spread adoption in practice.
+This section proposes four avenues for future research to enhance its effectiveness and characterise potential pitfalls:
 \begin{enumerate}

### 2024-06-01 intro.tex
Address reviewer 2's annotated thesis

@@
 In geophysics and throughout this thesis, these are referred to as cells, and the property is a measure of the strength of the magnetic field at a specific location.
-The field strength measured is the total magnetic intensity (TMI), which is the magnitude of the vector sum of each directional vector of the potential \parencite{blakelyPotentialTheoryGravity1996}.
-This scalar value is recorded in nanotesla (nT) and may be negative with an unbounded range that can exceed \qty{50000}{\nano\tesla} in the Earth's environment.
+The field strength measured is the total magnetic intensity (TMI), which is the magnitude of vector potential \parencite{blakelyPotentialTheoryGravity1996}, recorded in nanotesla (nT).
+It is useful in exploration geophysics to communicate the magnetic anomaly, which is the residual between the International Geomagnetic Reference Field (IGRF) model of the Earth's magnetic field, and the measured TMI at the location.
+Magnetic anomaly may be negative, and can exceed several thousand nanotesla in the Earth's environment.
 The location recorded at a sample point is the geographic latitude and longitude, and altitude, acquired with high-precision differential GPS, alongside radar altimeter elevation.
-These data may be transformed to a flat projected system, where spatial dimensions are expressed in metres.
+These data may be transformed to a projected coordinate system, where spatial dimensions are expressed in metres.
 
@@
 A method known as kriging is used in other areas of geoscience, such as geochemical mapping, and makes use of statistical properties of the known distribution \parencite{hansenInterpretiveGriddingAnisotropic1993,davis1986statistics}.
-Some recently proposed gridding methods include the methods of \textcite{naprstekNewMethodInterpolating2019}, \textcite{xuGravityAnomalyReconstruction2019}, or \textcite{chenPotentialFieldData2022}.
+A review of established spatial interpolation methods is provided in \textcite{liReviewComparativeStudies2011}.
+More recently proposed gridding methods include the methods of \textcite{naprstekNewMethodInterpolating2019}, \textcite{xuGravityAnomalyReconstruction2019}, or \textcite{chenPotentialFieldData2022}.
 Each interpolation method attempts to predict regularly spaced grids by leveraging properties intrinsic to the data, with the possible explicit integration of \emph{a priori} knowledge such as geophysical laws or geological context.
-A review of spatial interpolation methods is provided in \textcite{liReviewComparativeStudies2011}.
 
@@
 Further survey design considerations for airborne geophysics are outlined in \textcite{goodwinAirborneMagneticRadiometric2023,islesGeologicalInterpretationAeromagnetic2013,reidAeromagneticSurveyDesign1980}.
-Each gridding method includes a final cell size parameter selectable by the geophysicist, with a long-standing guideline of one third to one fifth the line spacing.
+Each gridding method includes a final cell size parameter selectable by the geophysicist, with a long-standing guideline of being one third to one fifth the line spacing.
 This sufficiently preserves detail in areas of high sampling, while avoiding excessive interpolated cells in areas of low sampling, which may lead to artefacts.
@@
 
-The following definition of resolution is adopted throughout this thesis:
+The following definition of geophysical resolution is adopted throughout this thesis:
 
@@
 \subsection{Traditional methods for enhancing resolution}
-As outlined in \Cref{sec:introgrids}, resolution is a product of sample distance and sampling density, and gridded rasters have a specific number of cells in each axis depending on the spatial extent.
-Upsampling raster data to larger height and width dimensions is commonplace, and generally performed by numerical image filters such as the cubic spline \parencite{keysCubicConvolutionInterpolation1981} or Lanczos filter \parencite{lanczos1988applied}.
+As outlined in \Cref{sec:introgrids}, geophysical resolution is a product of sample distance and sampling density, and gridded rasters have a specific number of cells in each axis depending on the spatial extent.
+Upsampling raster data to greater cell counts in the height and width dimensions by interpolation is commonplace, and often described as an increase in resolution, however no attempt is made by these operations to increase geophysical resolution.
+Upsampling is generally performed by numerical image filters such as the cubic spline \parencite{keysCubicConvolutionInterpolation1981} or Lanczos filter \parencite{lanczos1988applied}.
 Some of these interpolation methods are the basis of the gridding methods previously outlined, and simply selecting a smaller cell size during gridding is sufficient to achieve a larger image raster.
 These filters are adept at imputing the required cell values while preserving the frequency content of the original raster.
-However, no attempt is made at accurately increasing the high-frequency components of the raster, which are required by our definition for high-resolution geophysics.
+However, without the inclusion of new or supporting information such as additional sampling, supporting datasets, or other \emph{a priori}, no reasonable attempt can be made to increase geophysical resolution.
 
-Without sampling at a smaller separation or closer line spacing, it is still possible to increase the high-frequency content of aeromagnetic grids.
+Using known physical properties of the potential field, is possible to increase the high-frequency content of aeromagnetic grids.
 The rate at which the power of the component frequencies of the potential field diminish with increasing source-sensor distance is well known.
@@
 The other primary descriptor of a neural network is its architecture, referring to the configuration of its intermediate layers between the input and output.
-Key architectures used in this thesis are described below.
-If the network architecture provides the capacity to store and retrieve learning, the data and training architecture provide the actual instruction and mode of delivery.
+% If the network architecture provides the capacity to store and retrieve learning, the data and training architecture provide the actual instruction and mode of delivery.
+The input and output layer configuration is dependent on the dimensionality of the data, but the parameters of the intermediate layers are constrained only by computational resources.
+In addition to the shape and count of the intermediate layers, the style of connection between individual neurons is fundamental to the architecture. 
+These connection styles and their application within this thesis are described below.
+
+The second key determinant of a Neural Network is the training.
 There are broadly two classes of training: supervised and unsupervised learning.
-The super-resolution and representation learning tasks in this thesis are both supervised tasks, where a reference is provided for the network to calculate an objective function of its performance on.
+The super-resolution and representation learning tasks in this thesis are both supervised tasks, where a reference is provided for the network to calculate an objective loss function of its performance.
 Unsupervised learning does not have a ground truth or target, and instead learns to identify patterns within the data for tasks in clustering, density estimation, and visualisation \parencite{bishopPatternRecognitionMachine2006}.
@@
 Recently, CNNs have been surpassed by coordinate multilayer perceptron (CMLP) neural networks in some representation learning tasks, including SR \parencite{chenLearningContinuousImage2021}.
-CMLPs specifically use a dataset containing individual input values corresponding to coordinate features, and train to predict individual output feature vectors at those coordinates \parencite[e.g.][]{mildenhallNeRFRepresentingScenes2020}.
+CMLPs specifically use a dataset containing individual input values corresponding to coordinate features, and train to predict individual output feature vectors at those coordinates \parencite[e.g.][]{mildenhallNERFRepresentingScenes2020}.
 Key to the performance of these networks are implicit functions, which parameterise a function learned from training dataset with a neural network analogue.
@@
 To our knowledge, this chapter presents the first investigation of deep learning super-resolution of gridded magnetic potential field data within the literature.
-Two convolutional neural network models, namely RDN and ESRGAN+, from the contemporary literature are implemented \parencite{zhangResidualDenseNetwork2018,limEnhancedDeepResidual2017}.
+Two convolutional neural network models, namely RDN and ESRGAN+ \parencite{zhangResidualDenseNetwork2018,limEnhancedDeepResidual2017}, are adapted to suit geophysical data.
 With uncertainty on the amount of data required to train a SR model for magnetic grids, a dataset comprising readily available high- and low-resolution TMI grid pairs is formed using published state magnetic compilation maps of Western Australia \parencite{brett20MagneticMerged2020}.
@@
 It subsequently fine-tune trains the baseline model on real-world high-resolution state magnetic data.
-Furthermore, it adopts advances in the machine learning literature by implementing the LTE network \parencite{leeLocalTextureEstimator2022}.
+Furthermore, it adopts advances in the machine learning literature by adapting the LTE network \parencite{leeLocalTextureEstimator2022} for the geophysical task.
 The proposed method simulates aeromagnetic line sampling of a potential field extent at \qty{320}{\m} and \qty{80}{\m}, which are in the regional and prospect scales respectively.
@@
 
-\Cref{ch:paper3} reports the use of coordinate multilayer perceptron (CMLP) neural networks for representation learning of a surveyed potential field extent.
-With the proposed method, scattered line data can be encoded into the grid, and cells queried at interpolating coordinates to predict regularised grids.
+\Cref{ch:paper3} reports the use of coordinate multilayer perceptron (CMLP) neural networks for implicit neural representation (INR) of a surveyed potential field extent.
+With the proposed method, scattered line data can be encoded into a neural network model, and grids created by querying cells at regular coordinates.
 % CMLP networks are highly suited for processing spatial data such as point sampled geophysics surveys.
@@
 Both tasks are fundamental to interpretation and processing in geophysics, and by commencing the methods from point sample data, the number of individual processing steps is reduced, and the application is fully trainable.
-To our knowledge, this research is the first description of deep learning implicit neural representation for aeromagnetic potential field data in the literature.
+To our knowledge, this research is the first of its kind in geophysical literature.
 

### 2024-06-01 manuscript.tex
Add RTP declaration
Address reviewer 2's annotated thesis

@@
 
-\shipout\null
+% \shipout\null
 
@@
 My first floor colleagues and fellow tech geeks, David, Daniel, Chris, Minh, and Peter --- Your friendship and knowledge has been a wonderful environment to grow in as a geodata scientist.
-And all my SES, CET, and friends beyond: Alex, Anne, Ben, France, Jackson, Jules, Kailah, Lauren, Lauri, Liam, Lilly, Maddie, Maria, Malvina, Nicolas, Ravi, Sean, Sumail, Vickie, and Ze --- Thank you for years of lunches, dinners, beaches, rock climbing, yoga, and all the opportunities to talk rocks that I've been missing.
+And all my SES, CET, and friends beyond: Alex, Anne, Ben, France, Jackson, Jess, Jules, Kailah, Lauren, Lauri, Liam, Lilly, Maddie, Maria, Malvina, Nicolas, Ravi, Sean, Sumail, Vickie, and Ze --- Thank you for years of lunches, dinners, beaches, rock climbing, yoga, and all the opportunities to talk rocks that I've been missing.
 
@@
 
-\bigskip
-\noindent This research was supported by a Rio Tinto Iron Ore PhD Scholarship.
+\smallskip
+\medskip
+\noindent This research was supported by a Rio Tinto Iron Ore PhD Scholarship, and an Australian Government Research Training Program Scholarship.
+\vfill{}
 
-\vfill{}
 \epigraph{
@@
 \newpage{}
-% Fix incorrect page numbering on the signed form
-\includepdf[pages=-,templatesize={595.276pt}{841.89pt},nup=1x1,scale=1,clip,trim=5mm 36.5mm 5mm 20mm,fitpaper=true,pagecommand={\pagestyle{plain}}]{authorship_declaration_signed.pdf}
+\input{authorship_declaration}
+% Fix incorrect page numbering on the signed form:
+% \includepdf[pages=-,templatesize={595.276pt}{841.89pt},nup=1x1,scale=1,clip,trim=5mm 36.5mm 5mm 20mm,fitpaper=true,pagecommand={\pagestyle{plain}}]{authorship_declaration_signed.pdf}
 

### 2024-06-01 paper2.tex
Address reviewer 2's annotated thesis

@@
 \begin{abstract}
-    Contemporary super-resolution is a deep learning technique to increase the resolution and high-frequency details of raster data.
+    Super-resolution is a contemporary deep learning technique to increase the resolution and high-frequency content of gridded data.
     However, despite the widespread success of super-resolution upscaling of natural photographs, its application to low-resolution geophysical surveys remains to be fully investigated.
@@
     Moreover, the structural variation within the survey data depends entirely on the geological domain which is surveyed.
-    This paper proposes an approach to super-resolution of aeromagnetic survey data using transfer learning from synthetic data that represents a wide range of realistic geological domains, to improve the generalisability of the resulting model.
-    The approach uses realistic high-resolution and low-resolution pairs of gridded survey data, obtained by simulating aeromagnetic surveys of the data at close and wide line spacings.
+    The proposed super-resolution method uses realistic high-resolution and low-resolution pairs of gridded survey data, obtained by simulating aeromagnetic surveys of the data at close and wide line spacings.
+    Additionally, transfer learning from synthetic data that represents a wide range of realistic geological domains is used to improve the generalisability of the resulting model.
     The structural accuracy of the method is improved using a secondary fine-tuning stage incorporating real-world survey data.
-    The Local Texture Estimator neural network architecture was used, and qualitative and quantitative measures of the super-resolution performance are reported.
+    The Local Texture Estimator neural network architecture is adapted for this task, and qualitative and quantitative measures of the super-resolution performance are reported.
     The results demonstrate that the proposed method is capable of transforming regional scale aeromagnetic surveys to high-resolution for a wide range of geological features.
@@
 We propose a method for super-resolution (SR) upscaling of aeromagnetic geophysics data from diverse geological provenance.
-This method uses transfer learning \parencite{tanSurveyDeepTransfer2018} from magnetic data forward modelled from a collection of synthetic geological models with varied histories \parencite{jessellNoddyverseMassiveData2022}, and fine tuning with real-world data.
-SR employed in this work leverages a contemporary neural network \parencite{leeLocalTextureEstimator2022}, with a realistic method for sampling and gridding high- and low- resolution data.
+This method uses transfer learning \parencite{tanSurveyDeepTransfer2018} from magnetic data forward modelled from a collection of synthetic geological models with realistic structures and petrophysical properties \parencite{jessellNoddyverseMassiveData2022}, and fine tuning with real-world data.
+SR employed in this work leverages the contemporary Local Texture Estimator neural network \parencite{leeLocalTextureEstimator2022}, with a realistic method for sampling and gridding high- and low- resolution data.
 The method is suitable for typical low-resolution regional aeromagnetic surveys in Australia.
@@
 Minimum Curvature gridding \parencite{briggsMachineContouringUsing1974} is routinely applied in industry applications, as it gives well characterised results in rapid time, with minimal manual intervention.
-A comprehensive review of alternative spatial interpolation methods is presented by \textcite{liReviewComparativeStudies2011}.
-Each method of gridding has characteristic interpolation traits (which when undesired are termed artefacts), but irrespective of the gridding process the detail resolvable in the output grid is a product of the sample height, sampling density, and the final cell size at which the grids are rendered.
+A comprehensive review of traditional spatial interpolation methods is presented by \textcite{liReviewComparativeStudies2011}.
+Each method of gridding has characteristic interpolation traits (which when undesired are termed artefacts), but irrespective of the gridding process the detail resolvable in the output grid is a function of the sample height, sampling density, and the final cell size at which the grids are rendered.
 Gridding at a finer cell size preserves higher frequencies present in the sampled data, resulting in greater detail.
@@
 
-In order to improve the generalisation of an example-based neural network for regions without high-resolution coverage, we propose transfer learning \parencite{tanSurveyDeepTransfer2018} by first training a baseline model trained with synthetic data containing a broad set of geological domains, which is then fine-tuned with high-resolution survey grid data.
+In order to improve the generalisation of an example-based neural network for regions without high-resolution coverage, we propose using transfer learning \parencite{tanSurveyDeepTransfer2018} to fine-tune a synthetic data baseline model with high-resolution, real-world survey grid data.
 The synthetic geophysical data \parencite{jessellNoddyverseMassiveData2022} are forward modelled from 3D petrographic voxel models with varied geological histories.
@@
 
-Thus, the approach made in this study to address the challenges of training an example-based model with limited suitable geophysical data is to make use of geologically diverse synthetic data, with a realistic sampling and gridding method to generate low-resolution data for training.
+Thus, two approaches are made in this study to address the challenges of training an example-based model with limited suitable geophysical data.
+Firstly, to make use of geologically diverse synthetic data, with a realistic sampling and gridding method to generate low-resolution data for training.
+Secondly, to fine-tune this model using real-world grid data prepared with the same sampling method.
 
@@
 At large source-sensor distances, high frequencies are diminished below the noise floor to the point of unobservability, resulting in grids that show only broad scale features, typically representing spatially extensive features deep in the crust.
-It is common for noise in the sampled grid product to be significantly increased in the downward continued product, limiting the useful vertical extent of the method to six times the cell size \parencite{dampneyEquivalentSourceTechnique1969,zuoDownwardContinuationTransformation2020}.
-Downward continuation can be performed with field- or source-based methods \parencite{pilkingtonPotentialFieldContinuation2017}.
-Resolution enhancement through neural network approaches to downward continuation \parencite{liStableDownwardContinuation2023,yeHighprecisionDownwardContinuation2022} is a promising research direction in super-resolution geophysics, but is distinct from the proposed line-spacing based method due to its use of paired vertically continued training data.
+Downward continuation can be performed with the grid representation of the field, or by modelling causative sources and forward modelling the response at another height \parencite{pilkingtonPotentialFieldContinuation2017}.
+In either approach, it is common for noise in the sampled grid product to be significantly increased in the downward continued product, limiting the useful vertical continuation extent of of the method to six times the cell size \parencite{dampneyEquivalentSourceTechnique1969,zuoDownwardContinuationTransformation2020}.
+Resolution enhancement through neural network approaches to downward continuation \parencite{liStableDownwardContinuation2023,yeHighprecisionDownwardContinuation2022} is a promising research direction in super-resolution geophysics, but the training data are distinct.
+The proposed line-spacing based methods use data prepared using high- and low-resolution survey designs, while neural network continuation approaches prepare data using the above numerical continuation methods.
 
 Recently, aeromagnetic resolution enhancement has been performed with deep learning SR \parencite{bavandsavadkoohiHighresolutionAeromagneticMap2023,smithMagneticGridResolution2022}.
-Both methods operate on regional aeromagnetic data at four times scale, using variants of the SRGAN convolutional neural network originally by \textcite{ledigPhotorealisticSingleImage2017}.
+The method of \textcite{smithMagneticGridResolution2022} is presented in \Cref{ch:paper1} of this thesis.
+These two approaches operate on regional aeromagnetic data at four times scale, using variants of the SRGAN convolutional neural network originally by \textcite{ledigPhotorealisticSingleImage2017}.
 The method of \textcite{smithMagneticGridResolution2022} demonstated SR methods are capable of upsampling low-resolution magnetic textures and predicting accurate short wavelengths for these data.
@@
 However, the low-resolution data were created using a polynomial filter that suppressed high frequencies, rather than a real-world low-resolution geophysical sampling process.
-The method of \textcite{bavandsavadkoohiHighresolutionAeromagneticMap2023} uses low- and high-resolution aeromagnetic data from regional surveys, with a realistic low-resolution transform from line spacing and sample altitude differences.
-The dataset contains \qty{267} sample grids from surveys in Quebec, Canada, prepared from surveys with a low-resolution line spacing of \qty{800}{\m}.
+The method of \textcite{bavandsavadkoohiHighresolutionAeromagneticMap2023} uses low- and high-resolution aeromagnetic data from regional surveys in Quebec, Canada, with a realistic low-resolution transform from line spacing and sample altitude differences.
+% The dataset contains \qty{267} sample grids from surveys in Quebec, Canada, prepared from surveys with a low-resolution line spacing of \qty{800}{\m}.
 The proposed method is distinct from these prior works with its use of extensive and geologically varied synthetic data in coordination with real survey data to improve generalisation for regional aeromagnetics in Australia, and the use of a modern MLP-based SR network.
@@
 For photographs and natural image rasters with large representative training corpuses available, such as ImageNet \parencite{dengImageNetLargescaleHierarchical2009} and DIV2K \parencite{agustssonNTIRE2017Challenge2017}, SR methods have progressed to the point that high quality enhancement at four times scale is readily accessible to end-users \parencite[e.g.][]{wangRealESRGANTrainingRealWorld2021}.
-Contemporary work with low-resolution transforms for natural images \parencite[reviewed in][]{moserHitchhikerGuideSuperResolution2023} has well characterised the research space and expected performance for upscaling photographs and digital images.
+The performance of SR for photographs and digital images has been intensely explored \parencite[see a review in][]{moserHitchhikerGuideSuperResolution2023}.
 Prior work specific to this study are reviewed in \Cref{sec:2nnsr}.
@@
 Photographs and other natural images of interest to computer vision are typically created by capturing light from an image sensor or are explicitly mapped on a grid using a raster graphics program.
-In these rasters, each pixel is regularly distributed, and the resolution is isotropic and a factor of the pixel density of the sampling sensor or the software defined grid.
+In these rasters each pixel is regularly distributed and the resolution is a factor of the pixel density of the sampling sensor or the software defined grid.
 These data are encoded to regular arrays of pixel values, commonly as three-channel rasters representing the red, green, and blue intensities of each pixel.
@@
 
-An implicit function aims to learn a specific function parameterised entirely by the weights of a neural network.
+An implicit function aims to learn a specific function and parameterise it within a neural network model.
 In an image or geophysical grid context, the function may map grid coordinates to the value at those coordinates.
@@
 
-Local texture estimator (LTE) \parencite{leeLocalTextureEstimator2022} is implemented in this work for its performance in the task of image super-resolution.
+The local texture estimator (LTE) of \parencite{leeLocalTextureEstimator2022} is adapted for this work due to its performance in the task of image super-resolution.
 The encoder in LTE can use the feature extraction capability of traditional SR CNNs such as EDSR \parencite{limEnhancedDeepResidual2017} or RDN \parencite{zhangResidualDenseNetwork2018}, or a SwinIR \parencite{liangSwinIRImageRestoration2021} transformer-based encoder.
@@
 Due to the variable dynamic range of magnetic anomaly grids and the relative importance of structural accuracy for gridded data, image quality assessment methods typically used for RGB images such as peak signal-to-noise ratio or mean-squared error are an inadequate quantitative measure of upscaling performance for geophysics.
-In addition FSIM \parencite{linzhangFSIMFeatureSimilarity2011} is used to quantify the quality of the super-resolved image.
-FSIM is a full reference image similarity metric that quantifies structural similarity, rather than individual cell values, with highly similar structural content causing the metric to approach 1.0.
+FSIM \parencite{linzhangFSIMFeatureSimilarity2011} is a full reference image similarity metric that quantifies structural similarity, rather than individual cell values.
+% FSIM is used to quantify the quality of the super-resolved image.
 %TODO complain about SSIM Structural Similarity (SIM) \parencite{wangImageQualityAssessment2004}
-Model performance is quantified using FSIM in \Cref{tab:2metrics}.
+Model performance is quantified using FSIM in \Cref{tab:2metrics}, with increasing similarity causing the metric to approach 1.0.
 It is seen that fine-tune training increases FSIM score for the task of super-resolution for aeromagnetic grids, over the baseline model.

### 2024-06-01 paper3.tex
Address reviewer 2's annotated thesis

@@
 Neural networks can be considered as universal function approximators.
-The recent technique of deep learning implicit neural representation (INR) \parencite{mildenhallNeRFRepresentingScenes2020}, built on a network architecture known as a coordinate multilayer perceptron (CMLP;\ see \textcite{ramasinghePeriodicityUnifyingFramework2022} for a recent introduction), represents a signal as a function of its coordinates.
+The recent technique of deep learning implicit neural representation (INR) \parencite{mildenhallNERFRepresentingScenes2020}, built on a network architecture known as a coordinate multilayer perceptron (CMLP;\ see \textcite{ramasinghePeriodicityUnifyingFramework2022} for a recent introduction), represents a signal as a function of its coordinates.
 By parameterising the function in coordinate space, novel values of the function can be queried at arbitrary coordinates within the learned continuous spatial domain.
@@
 
-Seminal work by \textcite{mildenhallNeRFRepresentingScenes2020} demonstrated INR of volume density and colour radiance, learned from five dimensions of spatial coordinates and orientation.
+Seminal work by \textcite{mildenhallNERFRepresentingScenes2020} demonstrated INR of volume density and colour radiance, learned from five dimensions of spatial coordinates and orientation.
 Their approach uses positional encoding to improve the learning capacity of high-frequency content, addressing the issue of spectral bias in deep learning \parencite{rahamanSpectralBiasNeural2019}.
 When replacing positional encoding and the ReLU activation with periodic activation functions such as the sinusoid \parencite{sitzmann2019siren} the high frequency representation of CMLP networks is significantly enhanced.
-Periodic activation functions differ from typical non-linear activations by comprising the neuron with an activation function that repeats periodically, allowing for continuous differentiation throughout the depth of the network.
+Periodic activation functions differ from typical non-linear activations by scaling the response of the neuron with an activation function that repeats periodically, allowing for continuous differentiation throughout the depth of the network.
 Work by \textcite{ramasinghePeriodicityUnifyingFramework2022} revealed that it is the magnitude of the first and second derivatives of the activation that enhanced high-frequency representation learning capacity, rather than the periodicity, leading to Gaussian \parencite{ramasinghePeriodicityUnifyingFramework2022} and wavelet \parencite{saragadamWIREWaveletImplicit2023} activation functions for CMLP\@.

### 2024-06-02 manuscript.tex
Add header and chapter numbers to sections
De-number authorship declaration because including signed pdf copy, fixes TOC page length
Adjust chapter titles
Prompted by reviewer 2 to better present the thesis

@@
 \setcounter{section}{0}
-\renewcommand{\thesection}{\arabic{section}}
+% \renewcommand{\thesection}{\arabic{section}}
 
+\newpagestyle{body}{
+    \headrule
+    \sethead[][][]{}{\textsc{\thesection}\ --- \sectiontitle}{}
+    \setfoot[][][]{}{\thepage}{}
+}
+
+\pagestyle{body}
 \chapter{Introduction}
@@
 
-\chapter[Magnetic Grid Resolution Enhancement Using ML]{Magnetic Grid Resolution Enhancement Using Machine Learning}
+% \chapter[Magnetic Grid Resolution Enhancement Using ML]{Magnetic Grid Resolution Enhancement Using Machine Learning}
+\chapter{Super-resolution for enhancing magnetic grids}
 \label{ch:paper1}
@@
 
-\chapter{Super-resolution of Aeromagnetic Survey Data}
+% \chapter{Super-resolution of Aeromagnetic Survey Data}
+\chapter[Fine-tuning SR for real-world aeromagnetic surveys]{Fine-tuning super-resolution for real-world aeromagnetic surveys}
 \label{ch:paper2}
@@
 
-\chapter{Implicit Neural Representation for Potential Field Geophysics}
+% \chapter{Implicit Neural Representation for Potential Field Geophysics}
+\chapter[Implicit neural representation of potential fields]{Implicit neural representation of potential fields}
 \label{ch:paper3}

### 2024-06-02 paper3.tex
Adjust chapter titles
Prompted by reviewer 2 to better present the thesis

@@
 
-\title{Implicit Neural Representation for Potential Field Geophysics}
+\title{Implicit neural representation of potential fields}
 \author[1*]{Luke Thomas Smith}
@@
     % Using this new paradigm of encoding spatial information within a neural network enables new methods for working with potential field survey data.
-    We present a novel method for implicit neural representation of potential fields, demonstrate the quality of the learned implicit function by encoding real airborne geophysical survey line data, predict constant level grids, and compare the result to grid data processed with a traditional workflow.
+    We present a novel method for implicit neural representation (INR) of potential fields, demonstrate the quality of the learned implicit function by encoding real airborne geophysical survey line data, predict constant level grids, and compare the result to grid data processed with a traditional workflow.
     We further demonstrate the analytical calculation of gradients directly in the continuous domain using automatic differentiation, with the same framework used to train the neural network representation.

### 2024-06-02 manuscript.tex
Adjust sentiment in thesis abstract

@@
 The data-driven approach can extract high-resolution grids from the learned representation, as well as calculate analytical spatial gradients.
-Grid rasters and horizontal gradients calculated with the method very closely match their numerical counterparts, however, vertical gradients do not.
+Grid rasters and horizontal gradients calculated with the proposed method closely match their numerical counterparts from existing methods, presenting exciting avenues for further work in neural networks for geophysics.
 

### 2024-06-02 manuscript.tex
Fix page numbering
And tweak acknowledgements

@@
 Lu, for sharing your incredible amount of geophysics knowledge, incredible cooking, and love of tennis with me.
-Matilda, for being a wonderful friend and the best housemate --- Thanks for being silly with me.
+Matilda, for being a wonderful friend and the best housemate --- thanks for being silly with me.
 
 My first floor colleagues and fellow tech geeks, David, Daniel, Chris, Minh, and Peter --- Your friendship and knowledge has been a wonderful environment to grow in as a geodata scientist.
-And all my SES, CET, and friends beyond: Alex, Anne, Ben, France, Jackson, Jess, Jules, Kailah, Lauren, Lauri, Liam, Lilly, Maddie, Maria, Malvina, Nicolas, Ravi, Sean, Sumail, Vickie, and Ze --- Thank you for years of lunches, dinners, beaches, rock climbing, yoga, and all the opportunities to talk rocks that I've been missing.
+And all my SES, CET, and friends beyond: Alex, Anne, Ben, France, Jackson, Jess, Jules, Kailah, Lauren, Lauri, Liam, Lilly, Maddie, Malvina, Maria, Nicolas, Ravi, Sean, Sumail, Vickie, and Ze --- Thank you for years of lunches, dinners, beaches, rock climbing, yoga, and all the opportunities to talk rocks that I've been missing.
 
@@
 
-\pagenumbering{arabic}
-\setcounter{page}{1}
-\setcounter{section}{0}
 % \renewcommand{\thesection}{\arabic{section}}
@@
 \pagestyle{body}
+
 \chapter{Introduction}
 \label{ch:intro}
+
+\pagenumbering{arabic}
+\setcounter{page}{1}
+\setcounter{section}{0}
 % \newrefsection{}

### 2024-06-04 intro.tex
Add section on magnetic field theory

@@
 
+\section{Magnetic potential fields}
+The Earth has a naturally occuring magnetic force field, approximating a dipole oriented toward the top and bottom of the planet.
+Several properties of the magnetic field are important to the machine learning methods in this thesis.
+First, that a field refers to a set of functions of space and time, and a vector field such as the magnetic field has three orthogonal components, with a function for each component.
+Neural networks with sufficient parameters are recognised as universal function approximators \parencite{hornikMultilayerFeedforwardNetworks1989}, and should therefore be capable of approximating these functions of the magnetic field.
+Second, the magnetic field has a force function with continuous derivatives, and is conservative \parencite{kelloggFoundationsPotentialTheory1967}.
+The force function is known as the potential field, and the magnetic field is the gradient of the potential field.
+This property is important later in this thesis, when calculating spatial derivatives and considering constraining neural networks with physics informed loss functions.
+
+The magnitude of the magnetic field is the total magnetic intensity (TMI) \parencite{blakelyPotentialTheoryGravity1996}, with the unit nanotesla (nT).
+Magnetic surveys in exploration geophysics generally create TMI products, and it may be measured directly or calculated from measurements of each orthogonal component.
+To support various scientific endeavours, a model of this field is periodically constructed --- the International Geomagnetic Reference Field (IGRF).
+The residual between the IGRF and measured TMI at a specific time and location is termed magnetic anomaly.
+It may be negative, and can exceed several thousand nanotesla in the Earth's environment.
+One of the key petrophysical properties influencing the magnetic anomaly is magnetic susceptibility, itself predominantly influenced by magnetite, a mineral commonly present across geological settings \parencite{clarkNotesRockMagnetization1991}.
+Rocks may also be intrinsicly magnetised with remnant magnetisation.
+Because of these known petrophysical variations in rock magnetisation, stratigraphies can be differentiated and delineated in magnetic maps, and their composition interpreted.
+
 \section{Aeromagnetic surveys}
 \label{sec:introgeo}
-Airborne surveys of the Earth's magnetic or gravitational potential fields are routinely acquired at a range of scales at different stages of exploration, from pre-competitive regional data to stimulate exploration \parencite{howardAirborneGeophysicalCoverage2004}, to targeted investigations by the exploration industry at the prospect scale of up to several square kilometres.
+Airborne surveys of the Earth's magnetic or gravitational potential fields are routinely acquired at a range of scales at different stages of exploration, from pre-competitive regional data to stimulate exploration \parencite{howardAirborneGeophysicalCoverage2004}, through to targeted investigations by the exploration industry at the prospect scale of up to several square kilometres.
 Surveys may also be collected on the ground, or less commonly in exploration by ship or satellite, with most processing methods and interpretation shared between all forms of acquisition.
 Aeromagnetic surveys are among the lowest cost geophysical method \parencite{dentithGeophysicsMineralExploration2014}.
-
 There are many aspects of survey design controlling the resolvable detail within survey data.
 When acquiring data, aircraft fly straight transect lines at a safe elevation above topography, known as the topography drape.
-Higher frequencies within potential field data diminish with increasing source-sensor distance, therefore the lower the height, the more high-frequency components will be captured by the sensor.
+The power of higher frequencies in potential fields falls off with increasing source-sensor distance.
+As such the lower the survey elevation, the more high-frequency components present in the potential field will be captured by the sensor.
 Surveys are flown with a heading in which data will be acquired along line.
@@
 \label{sec:introgrids}
-Survey data can be interpreted as one-dimensional flight line transects, but more commonly they are regularised to a two-dimensional grid raster for interpretation in a process termed gridding.
-The resulting interpolated array contains uniformly spaced nodes and is referred to as a grid.
+Survey data can be interpreted as one-dimensional flight line transects, but more commonly they are regularised to a two-dimensional raster for interpretation, in a process termed gridding.
+The resulting interpolated array contains uniformly spaced cells and is referred to as a grid.
 Grids are raster data, where each pixel stores a scalar measurement of a specific property.
-In geophysics and throughout this thesis, these are referred to as cells, and the property is a measure of the strength of the magnetic field at a specific location.
-The field strength measured is the total magnetic intensity (TMI), which is the magnitude of vector potential \parencite{blakelyPotentialTheoryGravity1996}, recorded in nanotesla (nT).
-It is useful in exploration geophysics to communicate the magnetic anomaly, which is the residual between the International Geomagnetic Reference Field (IGRF) model of the Earth's magnetic field, and the measured TMI at the location.
-Magnetic anomaly may be negative, and can exceed several thousand nanotesla in the Earth's environment.
-The location recorded at a sample point is the geographic latitude and longitude, and altitude, acquired with high-precision differential GPS, alongside radar altimeter elevation.
+In the case of the aeromagnetic data used in this thesis, the property measured is TMI, and is processed to convey magnetic anomaly.
+The location recorded at a sample point is the geographic latitude, longitude, and altitude, acquired with high-precision differential GPS, alongside radar altimeter elevation.
 These data may be transformed to a projected coordinate system, where spatial dimensions are expressed in metres.
@@
 In interpolated grids the spatial dimension of each cell is referred to as the cell size.
-As previously stated, resolvable detail in geophysical surveys is a product of the distance between the causative magnetic body and the sensor, and the line spacing \parencite{islesRelationshipsGeologicalResolution1992,islesGeologicalInterpretationAeromagnetic2013,dentithGeophysicsMineralExploration2014}.
+As previously stated, resolvable detail in geophysical surveys is a product of the height between the causative magnetic body and the sensor, and the line spacing \parencite{islesRelationshipsGeologicalResolution1992,islesGeologicalInterpretationAeromagnetic2013,dentithGeophysicsMineralExploration2014}.
 Height is controlled by flying the lowest safe and sufficiently smooth topography drape, and along-line sampling is performed at a constant high rate, so the key factor controlling resolution in aeromagnetic survey design is the line spacing.

### 2024-06-06 authorship_declaration.tex
Address reviewer 2's annotated thesis
Add header and chapter numbers to sections
De-number authorship declaration because including signed pdf copy, fixes TOC page length
Drop line from declaration per EJ email

@@
-\documentclass[manuscript.tex]{subfiles}
-\begin{document}
+% \documentclass[manuscript.tex]{subfiles}
+% \begin{document}
 
-\addsec{Authorship Declaration}
+\addsec*{Authorship Declaration}
 This research was carried out at the University of Western Australia.
@@
 
-\noindent{}The possible application of super-resolution for geophysical grid data was suggested by E.J. Holden.
+% \noindent{}The possible application of super-resolution for geophysical grid data was suggested by E.J. Holden.
 
@@
 \begin{itemize}
-      \item{}\textbf{Location in thesis}: Chapter 1
+      \item{}\textbf{Location in thesis}: Chapter 2
 
@@
 Ore Geology Reviews 150, 105119.
-https://doi.org/10.1016/j.oregeorev.2022.105119
+            \url{https://doi.org/10.1016/j.oregeorev.2022.105119}
 
@@
       \item{}
-            \textbf{Location in thesis}: Chapter 2
+            \textbf{Location in thesis}: Chapter 3
 
@@
       \item{}
-            \textbf{Location in thesis}: Chapter 3
+            \textbf{Location in thesis}: Chapter 4
 

### 2024-06-06 intro.tex
Address team comments

@@
 \section{Magnetic potential fields}
-The Earth has a naturally occuring magnetic force field, approximating a dipole oriented toward the top and bottom of the planet.
+The Earth has a naturally occuring magnetic field, approximating a dipole oriented toward the top and bottom of the planet.
 Several properties of the magnetic field are important to the machine learning methods in this thesis.
-First, that a field refers to a set of functions of space and time, and a vector field such as the magnetic field has three orthogonal components, with a function for each component.
-Neural networks with sufficient parameters are recognised as universal function approximators \parencite{hornikMultilayerFeedforwardNetworks1989}, and should therefore be capable of approximating these functions of the magnetic field.
-Second, the magnetic field has a force function with continuous derivatives, and is conservative \parencite{kelloggFoundationsPotentialTheory1967}.
-The force function is known as the potential field, and the magnetic field is the gradient of the potential field.
-This property is important later in this thesis, when calculating spatial derivatives and considering constraining neural networks with physics informed loss functions.
-
-The magnitude of the magnetic field is the total magnetic intensity (TMI) \parencite{blakelyPotentialTheoryGravity1996}, with the unit nanotesla (nT).
-Magnetic surveys in exploration geophysics generally create TMI products, and it may be measured directly or calculated from measurements of each orthogonal component.
+First, that a field refers to a set of functions of space and time.
+The magnetic field is a vector field, with three orthogonal components.
+Neural networks with sufficient parameters are recognised as universal function approximators \parencite{hornikMultilayerFeedforwardNetworks1989}, and should therefore be capable of approximating the functions of the magnetic field.
+Second, the curl of the magnetic vector field is a force function known as the magnetic potential field \parencite{kelloggFoundationsPotentialTheory1967}.
+The magnitude of the magnetic vector field is the total magnetic intensity (TMI) \parencite{blakelyPotentialTheoryGravity1996}, with the unit nanotesla (nT).
+Magnetic surveys in exploration geophysics generally create TMI products, where TMI may be measured directly or calculated from measurements of each vector component.
 To support various scientific endeavours, a model of this field is periodically constructed --- the International Geomagnetic Reference Field (IGRF).
@@
 Rocks may also be intrinsicly magnetised with remnant magnetisation.
-Because of these known petrophysical variations in rock magnetisation, stratigraphies can be differentiated and delineated in magnetic maps, and their composition interpreted.
+Because of these known petrophysical variations in rock magnetisation, surveys of the magnetic field can delineate and differentiate stratigraphic units and infer their composition.
 
@@
 \Cref{ch:paper3} reports the use of coordinate multilayer perceptron (CMLP) neural networks for implicit neural representation (INR) of a surveyed potential field extent.
-With the proposed method, scattered line data can be encoded into a neural network model, and grids created by querying cells at regular coordinates.
+With the proposed method, scattered line data can be encoded into a neural network model, and grids are created by querying cells at regular coordinates.
 % CMLP networks are highly suited for processing spatial data such as point sampled geophysics surveys.

### 2024-06-06 paper2.tex
Adjust chapter titles
Prompted by reviewer 2 to better present the thesis
Address team comments

@@
 
-\title{Super-resolution of Aeromagnetic Survey Data}
+\title{Fine-tuning super-resolution for real-world aeromagnetic surveys}
 \author[1*]{Luke Thomas Smith}
@@
 
-In order to improve the generalisation of an example-based neural network for regions without high-resolution coverage, we propose using transfer learning \parencite{tanSurveyDeepTransfer2018} to fine-tune a synthetic data baseline model with high-resolution, real-world survey grid data.
+In order to improve the generalisation of an example-based neural network for regions without high-resolution coverage, we propose using transfer learning \parencite{tanSurveyDeepTransfer2018} to fine-tune a synthetic data baseline model with high-resolution real-world survey grid data.
 The synthetic geophysical data \parencite{jessellNoddyverseMassiveData2022} are forward modelled from 3D petrographic voxel models with varied geological histories.
@@
 In either approach, it is common for noise in the sampled grid product to be significantly increased in the downward continued product, limiting the useful vertical continuation extent of of the method to six times the cell size \parencite{dampneyEquivalentSourceTechnique1969,zuoDownwardContinuationTransformation2020}.
-Resolution enhancement through neural network approaches to downward continuation \parencite{liStableDownwardContinuation2023,yeHighprecisionDownwardContinuation2022} is a promising research direction in super-resolution geophysics, but the training data are distinct.
-The proposed line-spacing based methods use data prepared using high- and low-resolution survey designs, while neural network continuation approaches prepare data using the above numerical continuation methods.
+Resolution enhancement through neural network approaches to downward continuation \parencite{liStableDownwardContinuation2023,yeHighprecisionDownwardContinuation2022} is a promising research direction in super-resolution geophysics, but the problem formulation is distinct.
+The proposed method attempts to predict missing high frequencies with example based learning from similar geologies, while the prior methods attempt to vertically continue grid data using deep learning methods.
 
@@
 For photographs and natural image rasters with large representative training corpuses available, such as ImageNet \parencite{dengImageNetLargescaleHierarchical2009} and DIV2K \parencite{agustssonNTIRE2017Challenge2017}, SR methods have progressed to the point that high quality enhancement at four times scale is readily accessible to end-users \parencite[e.g.][]{wangRealESRGANTrainingRealWorld2021}.
-The performance of SR for photographs and digital images has been intensely explored \parencite[see a review in][]{moserHitchhikerGuideSuperResolution2023}.
+The performance of SR for photographs and digital images has been extensively explored \parencite[see a review in][]{moserHitchhikerGuideSuperResolution2023}.
 Prior work specific to this study are reviewed in \Cref{sec:2nnsr}.

### 2024-06-06 intro.tex
Try to enhance Nyquist explanation

@@
 Each gridding method includes a final cell size parameter selectable by the geophysicist, with a long-standing guideline of being one third to one fifth the line spacing.
-This sufficiently preserves detail in areas of high sampling, while avoiding excessive interpolated cells in areas of low sampling, which may lead to artefacts.
-If the sampling frequency is nominally \qty{7}{\m} in the flight line direction, and up to \qty{400}{\m} in the line-perpendicular direction, the resulting grid resolution will be anisotropic at best, and uniformly low-resolution at worst.
+This sufficiently preserves detail in areas of high sampling, while avoiding excessive interpolated cells in areas of low sampling, which may lead to artefacts and misrepresentation of the measured field.
 
+% If the sampling frequency is nominally \qty{7}{\m} in the flight line direction, and up to \qty{400}{\m} in the line-perpendicular direction, the resulting grid resolution will be anisotropic at best, and uniformly low-resolution at worst.
 An important property of sampled data is the Nyquist frequency, \[f_{Nyquist} = f_{sampling} / 2.\]
 This is the lowest frequency \(f\) at which a bandwidth limited signal may be sufficiently sampled, below which higher frequencies will be incorrectly recorded as aliasing.
-An aliased signal contains spurious low-frequency features caused by the sampling, not the underlying signal.
-This limiting frequency applies to each sampling direction in surveys, as well as the cell size of the grid.
+An aliased signal contains spurious features not present in the original signal.
+A Nyquist frequency applies to each sampling axis in surveys, as well as to the spacing of cells in the output grid.
 The smallest resolvable feature in each of these can be spatially described by wavelength, as the inverse of Nyquist frequency.
-For example, in low-resolution aeromagnetic surveys of \qty{400}{\m} line spacing, strong variations of magnetic intensity in the line-perpendicular direction  that occur over a distance shorter than \qty{800}{\m} will be aliased.
-When gridded at \qty{80}{\m} cell size, the corresponding limit on resolvable detail is features as small as \qty{160}{\m}.
+For example, in low-resolution aeromagnetic surveys with \qty{400}{\m} line spacing, rapid variations of magnetic intensity in the line-perpendicular direction that occur over a distance shorter than \qty{800}{\m} will be aliased.
+When gridded at \qty{80}{\m} cell size, the smallest accurately resolvable detail is \qty{160}{\m}.
 % This choice of cell size will effectively filter out features in the line-parallel direction that vary strongly, from those possibly present at \qty{14}{\m} through to \qty{160}{\m}.

### 2024-06-06 authorship_declaration.tex
Restore signed declarations page

@@
 
-\newpage{}
-\noindent{}The contributions of the author have been truthfully stated, and permission from
-each author has been sought to include the published material in this thesis.
+% \newpage{}
+% \noindent{}The contributions of the author have been truthfully stated, and permission from
+% each author has been sought to include the published material in this thesis.
 
-% \vspace*{20 mm}
+% % \vspace*{20 mm}
 
-\noindent\begin{tabular}{ll}
-                                            &                           \\[8ex]
-      \makebox[100 mm]{\dotfill}            & \makebox[30 mm]{\dotfill} \\
-      Eun-Jung Holden                       & Date                      \\
-      Principal and Coordinating Supervisor &                           \\[8ex]
-      \makebox[100 mm]{\dotfill}            & \makebox[30 mm]{\dotfill} \\
-      Daniel Wedge                          & Date                      \\
-      Co-supervisor                         &                           \\[8ex]
-      \makebox[100 mm]{\dotfill}            & \makebox[30 mm]{\dotfill} \\
-      Tom Horrocks                          & Date                      \\
-      Co-supervisor                         &                           \\[8ex]
-      \makebox[100 mm]{\dotfill}            & \makebox[30 mm]{\dotfill} \\
-      Naveed Akhtar                         & Date                      \\
-      Co-supervisor                         &                           \\
-\end{tabular}
+% \noindent\begin{tabular}{ll}
+%                                             &                           \\[8ex]
+%       \makebox[100 mm]{\dotfill}            & \makebox[30 mm]{\dotfill} \\
+%       Eun-Jung Holden                       & Date                      \\
+%       Principal and Coordinating Supervisor &                           \\[8ex]
+%       \makebox[100 mm]{\dotfill}            & \makebox[30 mm]{\dotfill} \\
+%       Daniel Wedge                          & Date                      \\
+%       Co-supervisor                         &                           \\[8ex]
+%       \makebox[100 mm]{\dotfill}            & \makebox[30 mm]{\dotfill} \\
+%       Tom Horrocks                          & Date                      \\
+%       Co-supervisor                         &                           \\[8ex]
+%       \makebox[100 mm]{\dotfill}            & \makebox[30 mm]{\dotfill} \\
+%       Naveed Akhtar                         & Date                      \\
+%       Co-supervisor                         &                           \\
+% \end{tabular}
 

### 2024-06-06 manuscript.tex
Make TOC neater
Restore signed declarations page

@@
 \newpage{}
-\addsec[Declarations]{Thesis Declaration}
+\addsec*[Declarations]{Thesis Declaration}
 I, Luke Thomas Smith, certify that:
@@
 % Fix incorrect page numbering on the signed form:
-% \includepdf[pages=-,templatesize={595.276pt}{841.89pt},nup=1x1,scale=1,clip,trim=5mm 36.5mm 5mm 20mm,fitpaper=true,pagecommand={\pagestyle{plain}}]{authorship_declaration_signed.pdf}
+\includepdf[pages=2,templatesize={595.276pt}{841.89pt},nup=1x1,scale=1,clip,trim=5mm 36.5mm 5mm 20mm,fitpaper=true,pagecommand={\pagestyle{plain}}]{authorship_declaration_signed.pdf}
 

### 2024-06-06 intro.tex
Final read-through changes

@@
 The magnitude of the magnetic vector field is the total magnetic intensity (TMI) \parencite{blakelyPotentialTheoryGravity1996}, with the unit nanotesla (nT).
+
 Magnetic surveys in exploration geophysics generally create TMI products, where TMI may be measured directly or calculated from measurements of each vector component.
@@
 It may be negative, and can exceed several thousand nanotesla in the Earth's environment.
+
 One of the key petrophysical properties influencing the magnetic anomaly is magnetic susceptibility, itself predominantly influenced by magnetite, a mineral commonly present across geological settings \parencite{clarkNotesRockMagnetization1991}.
@@
 Aeromagnetic surveys are among the lowest cost geophysical method \parencite{dentithGeophysicsMineralExploration2014}.
+Low-resolution regional surveys funded by government geoscience agencies are a key driver in greenfields exploration and are released as open file data.
+
 There are many aspects of survey design controlling the resolvable detail within survey data.
@@
 Acquisition along flight lines is sampled at a rate of \qty{10}{\hertz} or greater, which corresponds to an interval of \qty{7}{\m} or shorter at nominal flight speeds of \qty{70}{\m\per\s} \parencite{goodwinAirborneMagneticRadiometric2023}.
+
 The spacing between lines is a factor of the scale of investigation and the cost of acquisition, and regional pre-competitive data in Australia targets state-wide coverage at \qty{400}{\m}, which is generally regarded as the upper limit of usefulness to exploration \parencite{howardAirborneGeophysicalCoverage2004}.
-These low-resolution surveys, funded by government geoscience agencies, are a key driver in greenfields exploration and are released as open file data.
 Survey cost rapidly increases when surveying at higher resolution, due to overheads in flight line sampling.

### 2024-06-06 paper1.tex
Final touch ups for typesetting and wording
Adjust chapter titles
Prompted by reviewer 2 to better present the thesis
Final read-through changes

@@
 
-\title{Magnetic grid resolution enhancement using machine learning: A case study from the Eastern Goldfields Superterrane}
+\title{Super-resolution for enhancing magnetic grids}
 \author[1*]{Luke Thomas Smith}
@@
     \caption[RDB convolutional layers]{Each Residual Dense Block (\Cref{fig:rdb}, purple) comprises four convolutional layers, with additional learning pathways present as residual connections (black), and dense connections (green).
-LReLU refers to the Leaky-ReLU activation function.
+LReLU refers to the Leaky-ReLU activation.
 Adapted from \textcite{rakotonirinaESRGANFurtherImproving2020}.}
@@
 
-ESRGAN+, based on ESRGAN \parencite{wangESRGANEnhancedSuperresolution2018}, was chosen as the primary super-resolution CNN architecture for this task due to its reported success in other super-resolution tasks (especially \textcite{bodeUsingPhysicsInformedSuperResolution2019} and \textcite{leongDeepBedMapDeepNeural2020}) and state of the art results for its original application in image super-resolution.
+ESRGAN+, based on ESRGAN \parencite{wangESRGANEnhancedSuperresolution2018}, was chosen as the primary super-resolution CNN architecture for this task due to its reported success in other super-resolution tasks (especially \textcite{bodeUsingPhysicsinformedEnhanced2021} and \textcite{leongDeepBedMapDeepNeural2020}) and state of the art results for its original application in image super-resolution.
 As a Generative Adversarial Network (GAN), it comprises two iteratively trained neural networks, a Generator (G) used to upscale low-resolution inputs, and Discriminator (D), which is trained to improve the performance of the generator.
@@
 
+% \begin{landscape}
+    \begin{figure}[hbtp]
+        \centering
+        \includegraphics[width=\linewidth,trim={0 0 0 -5mm},clip]{fig/p1/hpfilt.jpg}
+        \caption[High-pass filtered results]{High-pass filtered test tile and its upsampled counterparts.
+            The cut-off for the high-pass Butterworth filter was selected with wavelength equal to the Nyquist wavelength of the LR grid, i.e.,\ 4 times the HR Nyquist wavelength.
+        }
+        \label{fig:filtered}
+    \end{figure}
+% \end{landscape}
+
 \begin{table}[hbtp]
@@
         RMSE    & 13.545                   & 26.576     & \textbf{7.265}                       & \textbf{13.741} & 11.120                   & 21.670     \\
-        SISM    & 0.924                    & 0.047      & \textbf{0.959}                       & \textbf{0.037}  & 0.922                    & 0.054      \\
+        SSIM    & 0.924                    & 0.047      & \textbf{0.959}                       & \textbf{0.037}  & 0.922                    & 0.054      \\
         MS-SSIM & 0.971                    & 0.018      & \textbf{0.988}                       & \textbf{0.012}  & 0.976                    & 0.020      \\
@@
 The effect of this texture occasionally reveals features matching the high-resolution groundtruth that are not predicted by the bicubic or RDN\textdaggerdbl{} upsampling, but the excess of “noisy” features present in ESRGAN+ predictions will likely limit its applicability when interpreting low-resolution grids with no corresponding groundtruth.
-
-\begin{landscape}
-    \begin{figure}[hbtp]
-        \centering
-        \includegraphics[width=\linewidth,trim={0 0 0 -5mm},clip]{fig/p1/hpfilt.jpg}
-        \caption[High-pass filtered results]{High-pass filtered test tile and its upsampled counterparts.
-            The cut-off for the high-pass Butterworth filter was selected with wavelength equal to the Nyquist wavelength of the LR grid, i.e.,\ 4 times the HR Nyquist wavelength.
-        }
-        \label{fig:filtered}
-    \end{figure}
-\end{landscape}
 

### 2024-06-06 paper3.tex
Mention vertical gradient follow-on
Final read-through changes

@@
 
-Both the line data and grid raster netCDFs for the Wolfe Creek survey were downloaded from Geoscience Australia (GA) \footnote{https://pid.geoscience.gov.au/dataset/ga/142694} and used without further processing.
+Both the line data and grid raster netCDFs for the Wolfe Creek survey were downloaded from Geoscience Australia (GA)\footnote{https://pid.geoscience.gov.au/dataset/ga/142694} and used without further processing.
 The line data netCDF contains tie-levelled, micro-levelled, and AWAGS levelled magnetic variables, in increasing stages of processing respectively.
 The micro-levelled magnetic data are used in this case study because the originally recorded sample altitude is uncertain in the available levelled data.
-Either a geographic and projected coordinate system can be used, provided for consistency between the query coordinates for inference and those used during training.
+Either a geographic or projected coordinate system can be used, provided for consistency between the query coordinates for inference and those used during training.
 The three spatial coordinate dimensions are independently and linearly min-max normalised between \num{-1} and \num{1}.
@@
 This is conjectured to be caused by aeromagnetic sampling being carried out on a nominally horizontal planar drape surface, without sufficient repeat measurements at other heights to train the network for the vertical field component.
+Initial experiments with synthetic data evenly sampled across the vertical extent learn a vertical gradient with similar performance to the horizontal gradients, supporting this conjecture.
 

### 2024-06-06 intro.tex
Run spell check

@@
 
-The subsurface continuation of exposed geology can be extrapolated and interpolated using structures mapped in surveys of the Earth's naturally occuring potential fields.
+The subsurface continuation of exposed geology can be extrapolated and interpolated using structures mapped in surveys of the Earth's naturally occurring potential fields.
 Potential field surveys offer low-cost investigations over a large spatial extent, and are routinely used for geological mapping and interpretation \parencite{nabighian75thAnniversaryHistorical2005}.
@@
 \section{Magnetic potential fields}
-The Earth has a naturally occuring magnetic field, approximating a dipole oriented toward the top and bottom of the planet.
+The Earth has a naturally occurring magnetic field, approximating a dipole oriented toward the top and bottom of the planet.
 Several properties of the magnetic field are important to the machine learning methods in this thesis.
@@
 One of the key petrophysical properties influencing the magnetic anomaly is magnetic susceptibility, itself predominantly influenced by magnetite, a mineral commonly present across geological settings \parencite{clarkNotesRockMagnetization1991}.
-Rocks may also be intrinsicly magnetised with remnant magnetisation.
+Rocks may also be intrinsically magnetised with remnant magnetisation.
 Because of these known petrophysical variations in rock magnetisation, surveys of the magnetic field can delineate and differentiate stratigraphic units and infer their composition.
@@
 \begin{itemize}
-    \item{} Spatio-temporal structure: Aeromagnetic grids are spatially corellated, neighbouring cells contain similar values arising from the same causative volume.
+    \item{} Spatio-temporal structure: Aeromagnetic grids are spatially correlated, neighbouring cells contain similar values arising from the same causative volume.
     \item{} Multi-source multi-resolution data: One location may be covered by multiple aeromagnetic surveys with different resolutions, or the same survey may be presented with different levels of processing.
@@
 A mathematical model of a neuron forms the basis of these networks, and the number of neurons within the network and their arrangement are one primary descriptor of a neural network.
-Neurons are paremeterised by a multiplicative weight term, an additive bias term, and an activation function which transforms the result.
+Neurons are parameterised by a multiplicative weight term, an additive bias term, and an activation function which transforms the result.
 Each neuron applies these operations to the input, which may either be the input data, or the output of earlier neurons.

### 2024-06-06 manuscript.tex
Fix header in bibliography
Just going to ignore header in conclusion reading bibliography.
Run spell check

@@
 My first floor colleagues and fellow tech geeks, David, Daniel, Chris, Minh, and Peter --- Your friendship and knowledge has been a wonderful environment to grow in as a geodata scientist.
-And all my SES, CET, and friends beyond: Alex, Anne, Ben, France, Jackson, Jess, Jules, Kailah, Lauren, Lauri, Liam, Lilly, Maddie, Malvina, Maria, Nicolas, Ravi, Sean, Sumail, Vickie, and Ze --- Thank you for years of lunches, dinners, beaches, rock climbing, yoga, and all the opportunities to talk rocks that I've been missing.
+All my SES, CET, and friends beyond: Alex, Anne, Ben, France, Jackson, Jess, Joel, Jules, Kailah, Lauren, Lauri, Liam, Lilly, Maddie, Malvina, Maria, Nicolas, Ravi, Sean, Sumail, Vickie, and Ze --- Thank you for years of lunches, dinners, beaches, rock climbing, yoga, and all the opportunities to talk rocks that I've been missing.
 
@@
 \smallskip
-\medskip
 \noindent This research was supported by a Rio Tinto Iron Ore PhD Scholarship, and an Australian Government Research Training Program Scholarship.
@@
 
+\newpagestyle{bib}{
+    \headrule
+    \sethead[][][]{}{Bibliography}{}
+    \setfoot[][][]{}{\thepage}{}
+}
+
+\pagestyle{bib}
+
 \printbibliography{}

### 2024-06-06 paper2.tex
Run spell check

@@
 Downward continuation can be performed with the grid representation of the field, or by modelling causative sources and forward modelling the response at another height \parencite{pilkingtonPotentialFieldContinuation2017}.
-In either approach, it is common for noise in the sampled grid product to be significantly increased in the downward continued product, limiting the useful vertical continuation extent of of the method to six times the cell size \parencite{dampneyEquivalentSourceTechnique1969,zuoDownwardContinuationTransformation2020}.
+In either approach, it is common for noise in the sampled grid product to be significantly increased in the downward continued product, limiting the useful vertical continuation extent of the method to six times the cell size \parencite{dampneyEquivalentSourceTechnique1969,zuoDownwardContinuationTransformation2020}.
 Resolution enhancement through neural network approaches to downward continuation \parencite{liStableDownwardContinuation2023,yeHighprecisionDownwardContinuation2022} is a promising research direction in super-resolution geophysics, but the problem formulation is distinct.
@@
 These two approaches operate on regional aeromagnetic data at four times scale, using variants of the SRGAN convolutional neural network originally by \textcite{ledigPhotorealisticSingleImage2017}.
-The method of \textcite{smithMagneticGridResolution2022} demonstated SR methods are capable of upsampling low-resolution magnetic textures and predicting accurate short wavelengths for these data.
+The method of \textcite{smithMagneticGridResolution2022} demonstrated SR methods are capable of upsampling low-resolution magnetic textures and predicting accurate short wavelengths for these data.
 Comparison was made against numerical filters such as the bicubic filter.
@@
 The enhanced structural similarity is reflected by the higher FSIM score of in the fine-tuned model. 
-Similar structural inaccuracies are seen in\Cref{fig:srdata17}, where severe aliasing again fails to be corrected using the baseline model, but is resolved by fune-tuning.
+Similar structural inaccuracies are seen in\Cref{fig:srdata17}, where severe aliasing again fails to be corrected using the baseline model, but is resolved by fine-tuning.
 
@@
 The fine structures in HR appear to have limited importance to the SSIM calculation, because the LR and SR grids are reported with a SSIM of 0.9998 or higher.
-This suggests that SSIM may be an innapropriate IQA metric in comparing resolution in potential field grids.
+This suggests that SSIM may be an inappropriate IQA metric in comparing resolution in potential field grids.
 

### 2024-06-06 paper3.tex
Run spell check

@@
 The cell size can be selected using a finer or coarser \(x,\ y\) spacing, including variable or anisotropic cell sizes.
-Contemporary super-resolution research can leverage this continual representation as a framework for high quality arbitrary scale factor high-frequency signal prediction \parencite[e.g][]{chenLearningContinuousImage2021}.
+Contemporary super-resolution research can leverage this continual representation as a framework for high quality arbitrary scale factor high-frequency signal prediction \parencite[e.g.][]{chenLearningContinuousImage2021}.
 However, the potential field representation task here does not attempt to predict additional high-frequency information and resolution remains determined by the neural network's capacity to represent high frequencies sampled by the survey line spacing.
